### 2016-04-14 definitions.tex
Initial Draft

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps. We use $t_i$ to denote the $i^{th}$ entry in a time sequence.

Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence and $T.s,T.e$ be the start and end of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
if and only if $\forall T.s \leq t_i < T.e$, $t_{i+1} = t_i + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $l$-consecutiveness as follows:

\begin{definition}[$l$-consecutive]
A time sequence $T$ is $l$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq l$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ is a maximally consecutive subsequence with cardinality less than $3$. $T$ is $2$-consecutive since both its two maximally consecutive subsequences are of the sizes greater or equal to $2$. It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping. Therefore, we are able to order the maximally consecutive subsequences. Let $T^m_{i}$ denote the $i^{th}$ maximally consecutive sequences wrt. $T$, then we can define the $g$-separated of $T$ as follows:

\begin{definition}[$g$-separated]
A time sequence $T$ is $g$-separated iff $\forall T^m_{i+1}.s - T^m_{i}.e \leq g$
\end{definition}

Take $T={1,2,3,5,6}$ as an example. $T$ is $2$-separated since the gap between its maximally consecutive subsequnces is $5-3=2$. However, $T$ is not $1$-separated. Indeed, $1$-separated infers that $T$ is fully consecutive.

Given a time sequence $t$, objects locations at $t$ collectively forms a \emph{snapshot}\footnote{Missing timestamps can be interpreted using linear interpolation~\cite{jeung2008convoy}}.Objects in a snapshot can thus be clustered based on the
closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, we can then define the generalized co-moving pattern as follows:

\begin{definition}[Generalized Co-Movement Pattern]
A \emph{generalized co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a sequence $T \subseteq \mathbb{T}$, with the following constraints:
\begin{enumerate}
\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
\item{Significance: $|O| \geq M$}
\item{Duration: $|T| \geq K$}
\item{Consecutiveness: $T$ is $L$-consecutive}
\item{Separateness: $T$ is $G$-separated}
\end{enumerate} 
\end{definition}

The generalized co-movement pattern retains the patterns that discovered by existing techniques (convoy, swarm and platoon). In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} pattern. In addition to covering existing patterns, the generalized co-movement pattern avoids the \emph{miss-pattern} problem in \emph{platoon} pattern. As suggested in Figure~\ref{fig:platoon_weakpoint}, $\{100,101\}$ will be included in the platoon pattern, however since they're too far away in temporal domain, this pattern is not prominent. By setting appropriate $G$, we are able to prune these two snapshots. Notice that such a new pattern cannot be modeled by existing patterns.

It is notable that the number of patterns in GCMP is exponential. To control the number of output patterns, we noticed that, for two pattern result $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Based on this observation, we define the \emph{closed generalized co-movement pattern} as follows:
\begin{definition}[Closed Generalized Co-moving Pattern]
A generalized co-moving pattern $P=\langle O, T \rangle$ is a closed generalized co-moving pattern if and only if there does not exists another generalized co-moving pattern $P'$ s.t. $P'.O \supseteq P.O$.
\end{definition}
For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern.The closed pattern avoids to output duplicate information, thus making the result patterns more compact. 
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters.

The goal of this paper is to present a parallel solution for discovering GCMP from large-scale trajectory data.

### 2016-04-14 optimization.tex
Initial Draft

\section{Optimization}
We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
lies in two factors. The size of each $Sr_s$ and the level the apriori runs.
In this section, we describe to optimization to reduce the two factors
respectively.

\subsection{Edge Simplification}
Each edge $e(s,t)$ in $Sr_s$ contains a time sequence $T$ 
which represent the co-occurrence of $s$ and $t$. We notice that the edge
between $s$ and $t$ is not always necessary. For example, if an edge has a
cardinality less than $K$, then it is not necessary to include this edge to $Sr_s$.
This motivates to simplify the edges in $Sr_s$ to boost the overall performance.

We first define a \emph{partly candidate} sequence as follows:
\begin{definition}[Partly Candidate Sequence]
Given a set of pattern parameters $M,L,K,G$, a sequence $T$ is 
a \emph{partly candidate} sequence if and only if exists a interval $(i,j)$
such that $T'=T[i:j]$ is a sequence conforming to $L,K,G$.
\end{definition}

For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,9,10,11)$ 
is a \emph{partly candidate sequence} since $T_1[0:3] = (1,2,4,5)$ is a valid
pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid pattern.

Observing that only partly candidate sequence can be potential included in a 
pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
candidate sequence, then this edge can be pruned from $Sr_s$. To efficiently
test whether a given sequence is partly candidate, we define the \emph{pseudo-consecutiveness} 
of a sequence as follows:

\begin{definition}[Pseudo-consecutiveness]
Given a parameter $G$, a sequence $T$ is \emph{pseudo-consecutive} if and only
if for any $i\in (0, |T|)$, $T[i] - T[i-1] \leq G$
\end{definition}

For example, let $G = 2$, then the sequence $T_1=\{1, 2, 4, 5\}$ is pseudo-consecutive
while $T_2=\{1,4,5,6,8\}$ is not pseudo-consecutive.

Based on the pseudo-consecutiveness, our edge simplification and prune process takes
two scan of an input $T$ as shown in Algorithm~\ref{algo:simp_prune}. In the 
first round of scan, the consecutive portion of $T$ with size less than $L$ is removed.
In the second round of scan, the pseudo-consecutive portion of $T$ with size less than $K$
is removed. Clearly the simplification algorithm runs in $O(|T|)$ time.

\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}
\Require $T$
\State{Remove the consecutive portion with size less than $L$}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] != 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{Remove the pseduo-consecutive portion with size less than $K$}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
		\State $s \gets 1$
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

### 2016-04-14 relatedworks.tex
Initial Draft

\section{Related Works}
\label{sec:related_works}
There are many works has been done on patterns mining in trajectory databases. We loosely classify these patterns into \emph{General Trajectory Pattern}s and \emph{Co-movement Pattern}s. The difference is that \emph{Co-movement Pattern}s require all members of a cluster stay together during the pattern lifetime. We summarize the related works as follows:

\subsection{General Trajectory Pattern}
General Trajectory pattern mining a hot field in trajectory analysis. Previous works
define various patterns~\cite{
kalnis2005movingclusters,
li2010periodicpattern,zheng2013gathering,jinno2012paralleltpattern,li2013onlinegroup} over trajectory data, which have proven their usefulness under different applications~\cite{giannotti2007survey}.

Kalnis et al. proposed \emph{moving clusters} pattern~\cite{kalnis2005movingclusters}. In such a pattern, objects form clusters at each snapshot. For consecutive snapshots, the clusters in the pattern should have a Jaccard index greater than a threshold. Under such a scheme, the difference between cluster members in snapshots accumulates, therefore the clusters at later snapshot may be very different from those in previous snapshots. The online extension is studied by Li et al.~\cite{li2013onlinegroup}.

Li et al. considered the \emph{periodic} pattern in~\cite{li2010periodicpattern}. This pattern mines the objects with periodic behaviors. An example of such a pattern is that individuals go to work together every day. 
It is commented in~\cite{giannotti2007survey} that \emph{periodic} pattern is unsuitable for discovering movements, since it is unreasonable to expect an object to repeat its behavior exactly during each time period considered.

Zhang et al. proposed the \emph{gathering} pattern in \cite{zheng2013gathering}. It is similar to \emph{flock} pattern~\cite{gudmundsson2004flock} but with the relaxation on the members of clusters. Instead of fixing the members in clusters as in~\cite{gudmundsson2004flock}, \emph{gathering} pattern allows members in clusters leave and join during the pattern duration. Since it relaxes the member constraints, it is unable to model co-movement patterns.

\subsection{Co-movement Pattern}
The work most related to ours is those on \emph{co-movement} patterns. We summarize the typical patterns as follows:
\subsubsection{group}
Wang et al. defined \emph{group pattern}~\cite{wang2006grouppattern}, which aims to find the set of objects travelling together at certain time intervals. In \emph{group pattern}, groups at each snapshot is identified by a disc-based clustering method, where each cluster forms a circle within a radius. It is argued in later works~\cite{jeung2008convoy,li2010swarm} that such disc-based clustering is not effective as \emph{density}-based clustering where the later one may find clusters of arbitrary shapes.

\subsubsection{flock}
Gudmunsson et al. proposed \emph{flock} pattern in 
\cite{gudmundsson2004flock,gudmundsson2006flock} and Vieria et al. followed up with an online version in~\cite{
vieira2009onlineflock}. A \emph{flock} pattern tries to find the set of objects that stay in a circular ranged cluster for a minimum duration. Such a pattern is useful in detecting the moving companions. However, similar as \emph{group pattern}, it uses disc-based clustering, which suffers the same deficiency in discovering arbitrary shaped clusters. \emph{Flock} pattern has many derivatives. In \cite{benkert2006meet}, Benkert et al. studied \emph{meet} pattern, which require the clusters in the pattern to be geographically stationary. Giannotti et al. studied \emph{leadership} pattern~\cite{andersson2007leadership} which requires a leader object exists for each flock cluster.
%In \cite{benkert2006meet}, Benkert et al. studied \emph{meet} pattern. A \emph{meet} pattern aims to find a set of objects stay
%stationary with in a circular range for some durations. This pattern does not consider the temporal movement of objects. Giannotti et al. studied \emph{leadership} pattern~\cite{andersson2007leadership} which requires a set of objects stay relatively within a circular range at each snapshots for some durations and there is at least one object is heading (leader). It is shown in~\cite{giannotti2007survey} that both \emph{Meet} and \emph{leadership} patterns are special cases of the \emph{flock} pattern~\cite{gudmundsson2004flock}.

\subsubsection{convoy}
Jeung et al. proposed \emph{convoy} pattern that extends \emph{flock} pattern by replacing the disc-based clustering with \emph{density}-based clustering. Such an relaxation brings a high complexity of repeatedly running DBSCAN~\cite{birant2007st} at every snapshot. To reduced the complexity, Jeung et al. designed a filter-refine approach which first uses simplification technique~\cite{douglas1973linesimplification} to filter far away objects, and then uses coherent moving method~\cite{kalnis2005movingclusters} to find the exact convoy patterns. Along with \emph{convoy} pattern, Aung et al. proposed \emph{dynamic convoy} and \emph{evolving convoy} patterns. In \emph{dynamic convoy}, the cluster members are allowed to be absent briefly during the convoy lifetime, while \emph{evolving convoy} allows the convoy to grow or shrink in cardinality during the life time. Tang et al. also addresses the online extension in~\cite{tang2012onlineconvoy}.
\subsubsection{swarm}
The major argument on \emph{convoy} pattern is that \emph{convoy} requires the consecutiveness in the lifetime, which may lose many interesting patterns. To remedy, Li et al. proposed the \emph{swarm} pattern~\cite{li2010swarm} which completely relaxes the consecutiveness in \emph{convoy}. In \emph{swarm}, objects can collectively leave the cluster for a long time and then join back in later time. The only requirement in \emph{swarm} is that each member in the cluster needs to accumulate to a certain duration. In~\cite{li2010swarm}, the authors proposed a depth-first search based pruning algorithm to efficiently discover \emph{swarm} patterns.
\subsubsection{platoon}
Recently Li et al. argued that \emph{swarm} is to loose in the temporal consecutiveness and proposed \emph{platoon} pattern in~\cite{li2015platoon}. In \emph{platoon} pattern, the clusters should lasts for at least a certain during before dismiss. Meanwhile, \emph{platoon} allow the clusters to form again at future times. Li et al. demonstrated the such extension is more general and can support swarm and convoy patterns by setting appropriate parameters. Li et al. also provide a similar depth-first search approach as in~\cite{li2010swarm}. In addition, they adapted a prefix pruning method to further improve efficiency. It is notable that in both \cite{li2010swarm} and \cite{li2015platoon}, authors consider the input to be the clusters at each snapshot, which ignores the clustering time.

\subsection{Pattern Mining Frameworks}
Jinno et al. recently studied the problem of processing \emph{T}- pattern~\cite{giannotti2007survey} in parallel platform \cite{jinno2012paralleltpattern}. A \emph{T}-pattern discovers a set of objects visiting the same the place in a close time interval. Such a pattern differs from moving object pattern in that \emph{T}-pattern does not consider the movement of objects. Jinno et al. in~\cite{jinno2012paralleltpattern} designed a MapReduce based algorithm for efficiently support \emph{T}-pattern discovery. However, as the nature of differences between the patterns, their work cannot directly applied on the co-moving object pattern discovery. Li et al. recently proposed a framework of processing online \emph{evolving group} pattern~\cite{li2013onlinegroup}. The \emph{evolving group} is similar to \emph{moving cluster} pattern with focus on the member updates in clusters, which is different with \emph{co-movement} pattern. Moreover the framework is developed for centralized system, thus is different with our work.

\subsection{Trajectory Clustering}
Another field that is related to our work is trajectory clustering~\cite{he2011mrdbscan,lee2007partitionandgroup,
li2004clusteringmovingobjects}. Lee et al. proposed a partition and group algorithm in~\cite{lee2007partitionandgroup}. Their clustering method does not consider the temporal constraint and groups trajectories from different time points together. Li et al. proposed a \emph{micro-clustering} technique~\cite{li2004clusteringmovingobjects} for cluster moving objects based on their moving directions. However, such a technique clusters moving objects based on entire trajectories, thus is not able to identify patterns that are at local trajectories. He et al. proposed a parallel DBSCAN algorithm in~\cite{he2011mrdbscan} running on MapReduce platform. Their method uses a four-stage process to decouple the dependencies in DBSCAN. However their method only focuses on DBSCAN for one datasets, where exploiting the relationship between multiple DBSCANs remains unexplored.

### 2016-04-14 system.tex
Initial Draft

\section{Preliminary on Apache Spark}
Apache Spark is the modern parallel processing platform
based on Resilient-Distributed-Dataset (RDD), which
is open-sourced by UC Berkeley. Spark differs from
traditional MapReduce framework (e.g., Hadoop) in the 
following features:
\begin{enumerate}
\item{It supports general computation DAGs beyond the two-stage MapReduce topologcy.}
\item{The execution engine can tolerate the loss of any works}
\item{It provides an in-memory storage abstraction called Resilient Distributed Datasets (RDDs). that 
lets applications keep data in memory, and automatically reconstructs the lost partitions upon failures.}
\end{enumerate}

In MapReduce-like systems, the major bottleneck is the \emph{shuffle} operation. 
In the \emph{shuffle} operation, data are re-partitioned and send to executors
via networks. Such operation is more costly than CPU and disk I/Os, which contribute
most in MapReduce-like applications.

TO BE ADDED....

\section{Mining Generalized Co-moving Pattern}
The outline of GCMP mining is to first cluster objects at
each snapshots and followed by mining the patterns among clusters
of different snapshots. In Spark scenario, 
the first step can be easily performed in parallel. 
This is because the objects at each snapshots are independent. Therefore, we
can partition the trajectories based on snapshots to achieve parallelism. 
In contrast, naively design the 
the second step may suffer from inter-executor communications.

\subsection{Temporal Replication and Mining}
The straightforward method of parallelizing GCMP mining is to partition
the trajectories in the temporal domain. A simple but effective method
is to group neighborhood snapshots in to a partition, such that all patterns
can be mined within a partition. In order to achieve the \emph{completeness},
some of the snapshots need to be replicated on multiple executors.
We thus call this method the \emph{Temporal Replication and Mining} approach. 
The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}
\Require list of $\langle t, S_t \rangle$ pairs
\State {Map Phase}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...(K-1)*G+K$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor 
\EndFor
\State {Shuffle Phase}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$,
\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(K-1)*G+K}\} $
\EndFor
\State {Reduce Phase}
\ForAll{$\langle t,Par_t \rangle$}
\State minePattern($Par_t$)
\EndFor

\end{algorithmic}
\end{algorithm}

\subsubsection{Temporal Replication Partition}
In order to reduce the shuffling cost, the data to be replicated should be
kept to a minimum. To control the number of snapshots that are replicated, 
we use the following theorem to facilitate a partition:

\begin{theorem}[Completeness of Replication Partition]
\label{thm:replication_partition}
For each snapshot $S_t$, a partition $Par_t = \{S_t, S_{t+1},...,S_{t+(K-1)*G+K}\}$ 
is created. Then, for any global pattern $P$, there must exist at least one partition $Par_i$
such that $P$ is also a pattern in $Par_i$.
\end{theorem}
\begin{proof}
PROOF BY CONTRADICTION, OMITTED FOR NOW
\end{proof}

Utilizing Theorem~\ref{thm:replication_partition}, we create, for each snapshot $S_t$, 
a partition containing its next $(K-1)*G+K$ snapshots. Each partition is then
sending to the executors as a task. Since any global pattern must exists in 
one of the partitions, we can mine the patterns from each partitions independently.

\subsubsection{Temporal Replication Mining}
After replication, each task in Spark will process an interval of snapshots $Par_i$. The next
step is to mine the GCMPs from $Par_i$. We notice that, for each 
partition, we only need to find the patterns that
are contained in the first snapshots. Therefore we design a line-sweep method for mining 
such patterns. DETAILS OMITTED FOR NOW.

The Temporal Replication and Mining approach though achieves parallelism from independent
partitions, it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $(K-1)*G+K$ times. In swarm
case, $G$ is as large as $|T|$. Then, it is equivalent to shuffle entire dataset 
to each executor, which is clearly inefficient.

\subsection{Star Partition and Mining}
To develop a method that achieves parallelism under any pattern parameters, 
we propose a solution called \emph{Star Partition and Mining}. In SPM,
we design a novel object-based partition method named star partition. In star partition,
instead of partitioning trajectories in temporal domain, we partition trajectories 
in object domain. After partitioning, we use the \emph{Apriori}-like 
method to mine the patterns out of each partition. 
The outline of the start partition and mining is as in Algorithm~\ref{algo:spm_overview}

\begin{algorithm}
\caption{Star Partition and Mining}
\label{algo:spm_overview}
\begin{algorithmic}
\Require list of $\langle t, S_t \rangle$ pairs
\State {Map phase}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
		\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
	\EndFor
\EndFor

\State {Shuffle phase}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
	\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
\EndFor

\State {Reduce phase}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State Apriori($Sr_o$)
\EndFor

\end{algorithmic}
\end{algorithm}

\subsubsection{Star Partition}
The purpose of star partition is to find the group of object that 
could potentially form a pattern. In order to achieve parallelism, 
we find and group, for each object $o$, all other objects that connect to $o$ in some
snapshots. By so doing, the patterns containing $o$ can be discovered within
each groups. Technically, we create a connection graph to represent the
connectivity among objects. A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= T$ 
represents the connection between vertex $s,t$ at all times in $T$, 
i.e. $\forall t \in T, C_t(s) = C_t(t)$. 
Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$.
In star partition, the trajectories are partitioned based on objects and their stars. Then
each partition is send to an executor as a task.
We state the completeness of star-partition as in the following theorem:
\begin{theorem}[Completeness of Star Partition]
Given a connection graph $G$, for any global pattern $P$, there exists a $s \in G.V$ such 
that $P$ is a pattern in $Sr_s$.
\end{theorem}

\begin{proof}
OMITTED FOR NOW
\end{proof}

Based on the above theorem, each task can be processed independently by executors. 
Thus, the inter-executor communication is avoided during the mining phase. It is notable that, the 
replication of data is $O(|\mathbb{O}|^2|T|)$, which is regardless the parameters of patterns.
In later sections, we will describe optimization techniques to reduce the replications.

\subsubsection{Apriori Mining}
For each task, in the mining phase, we need to find the patterns that conform to the parameter
setting. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to frequent item mining. If a candidate pattern's object set is of size $R$, we call
this candidate a $R$-pattern. Our apriori mining algorithm tries to generate all $R$-pattern in
each iteration. As a start, the $2$-pattern is generated from edges in $Sr_s$. In particular,
for each $e(s,t)=T$, pattern $p=(\{s,t\}, T)$ is formed. During each iteration $R$, 
we generate $R+2$-cluster pattern by joining $(R+1)$-cluster patterns with $2$-cluster patterns. 
The join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}
\Require{$Sr_s$}
\State { Lv $\gets \{\}$}
\State { Lv2 $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Lv2.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Lv2;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in Lv2$}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is partly valid} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
are two major factors dragging the performance. First, the size of $Sr_s$ affects
the number initial size of $2$-patterns. Second, the level that apriori runs. In later
sections, we exploit the property of GCMP to reduce the two factors.

### 2016-04-14 optimization.tex
Example and Proofs needed

@@
 
-We first define a \emph{partly candidate} sequence as follows:
-\begin{definition}[Partly Candidate Sequence]
-Given a set of pattern parameters $M,L,K,G$, a sequence $T$ is 
-a \emph{partly candidate} sequence if and only if exists a interval $(i,j)$
-such that $T'=T[i:j]$ is a sequence conforming to $L,K,G$.
-\end{definition}
-
-For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,9,10,11)$ 
-is a \emph{partly candidate sequence} since $T_1[0:3] = (1,2,4,5)$ is a valid
-pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid pattern.
-
-Observing that only partly candidate sequence can be potential included in a 
-pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
-candidate sequence, then this edge can be pruned from $Sr_s$. To efficiently
-test whether a given sequence is partly candidate, we define the \emph{pseudo-consecutiveness} 
-of a sequence as follows:
-
+We first define the \emph{Pseudo-consecutiveness} of a time sequence as follows:
 \begin{definition}[Pseudo-consecutiveness]
@@
 \end{definition}
-
 For example, let $G = 2$, then the sequence $T_1=\{1, 2, 4, 5\}$ is pseudo-consecutive
@@
 
-Based on the pseudo-consecutiveness, our edge simplification and prune process takes
-two scan of an input $T$ as shown in Algorithm~\ref{algo:simp_prune}. In the 
-first round of scan, the consecutive portion of $T$ with size less than $L$ is removed.
+A pseudo-consecutive subsequence of $T$ is a subsequence $T' \subseteq T$
+and $T'$ is pseudo-consecutive. A maximal pseudo-consecutive subsequence 
+$T^m$ of $T$ is a pseudo-consecutive subsequence of $T$ and there is 
+no superset of $T^m$ that is also a pseudo-consecutive subsequence of $T$.
+Clearly, a sequence $T$ can be decomposed into several maximally pseudo-consecutive 
+subsequences. We then define a \emph{partly candidate} sequence as follows:
+
+\begin{definition}[Partly Candidate Sequence]
+Given the pattern parameters: $L,K,G$, a sequence $T$ is 
+a \emph{partly candidate} sequence if exist one of its maximal pseudo-consecutive
+subsequence $T'$ such that $T'$ confirms to $L,K,G$.
+\end{definition}
+
+For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ 
+is a \emph{partly candidate sequence} since $T_1[0:3] = (1,2,4,5,6)$ is a valid
+pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid partly candidate sequence.
+
+Observing that only partly candidate sequence can be potentially included in a 
+pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
+candidate sequence, then this edge can be pruned from $Sr_s$. To efficiently
+test whether a given sequence is partly candidate, we define the \emph{Fully Candidate Sequence}:
+
+\begin{definition}[Fully Candidate Sequence]
+Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Fully Candidate} 
+if and only if for any of its maximal pseudo-consecutive sequence $T'$, $T'$ 
+is partly consecutive.
+\end{definition}
+
+For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ is 
+not a fully candidate sequence since one of its maximal pseudo-consecutive sequence $(9,10,11)$
+is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
+a fully candidate sequence.
+
+Based on the fully candidate sequence, we can reduce an sequence $T$ to a 
+fully candidate sequence by striping out its non-partly candidate maximal pseudo-consecutive 
+sequences. The reduction works as in Algorithm~\ref{algo:simp_prune}. It takes two
+rounds of scan of an input $T$. In the first round of scan,
+the consecutive portion of $T$ with size less than $L$ is removed.
 In the second round of scan, the pseudo-consecutive portion of $T$ with size less than $K$
@@
 \end{algorithm}
+
+We use the following theorem to state the completeness and correctness of our 
+edge reduction algorithm.
+\begin{theorem}[Completeness of Algorithm~\ref{algo:simp_prune}]
+For a sequence $T$, let $T_1$ be the result of $T$ after algorithm~\ref{algo:simp_prune},
+if $\exists T' \subseteq T$ and $T'$ is included in a pattern $P$, then $T' \subseteq T_1$.
+\end{theorem}
+
+\begin{proof}
+OMITTED FOR NOW
+\end{proof}
+By utilizing the edge simplification technique, the size of $Sr_s$ can be greatly reduced. If
+an edge cannot be reduced to a full candidate sequence, then it is directly removed from $Sr_s$.
+If an edge can be reduced to a full candidate sequence, replacing itself with its full candidate sequence 
+would result in a more compact storage.
+
+\subsection{Pruning Apriori Mining}
+During the apriori phase, we are repeatedly join candidate pattern in different levels to generate a larger set
+of a pattern. We notice that, such joins can be early terminated 
+by utilizing the property of GCMP. The intuition is that when we are trying to store a level of candidate, if its
+temporal sequence is not a \emph{partly candidate} sequence, then it should able to generate new candidates and thus it
+can be removed from that level of candidate. This \emph{apriori property} 
+is explicitly described as in the follow theorem:
+
+\begin{theorem}[Apriori Property of GCMP]
+Given the temporal parameters $L,G,K$ of GCMP, for a candidate $cand$ in Algorithm~\ref{algo:apriori_mining},
+if $cand.T$ cannot be reduced to a full candidate sequence, then $cand$ can be pruned.
+\end{theorem}
+\begin{proof}
+OMITTED FOR NOW
+\end{proof}
+
+Utilizing the \emph{Apriori Property}, the new candidate in each level is greatly reduced, which is shown in
+the experiment session.

### 2016-04-26 definitions.tex
With Comments
With Dongxiang's comments

@@
 Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps.
-We use $t_i$ to denote the $i^{th}$ entry in a time sequence.
+We use $T[i]$ to denote the $i^{th}$ entry in a time sequence.
 
-Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence and $T.s,T.e$ be the start and end of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
-if and only if $\forall T.s \leq t_i < T.e$, $t_{i+1} = t_i + 1$.
+Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
+if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$.
 A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt.
@@
 $T$.
-We then define the $l$-consecutiveness as follows:
+We then define the $L$-consecutiveness as follows:
 
-\begin{definition}[$l$-consecutive]
-A time sequence $T$ is $l$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq l$.
+\begin{definition}[$L$-consecutive]
+A time sequence $T$ is $L$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq L$.
 \end{definition}
@@
 It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping.
-Therefore, we are able to order the maximally consecutive subsequences.
-Let $T^m_{i}$ denote the $i^{th}$ maximally consecutive sequences wrt.
-$T$, then we can define the $g$-separated of $T$ as follows:
 
-\begin{definition}[$g$-separated]
-A time sequence $T$ is $g$-separated iff $\forall T^m_{i+1}.s - T^m_{i}.e \leq g$
+We then define the $G$-separateness as follows:
+
+\begin{definition}[$G$-separated]
+A time sequence $T$ is $G$-separated iff $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$
 \end{definition}
@@
 Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters.
+Therefore in this paper, we mainly consider density-based clustering.
 
 The goal of this paper is to present a parallel solution for discovering GCMP from large-scale trajectory data.
+
+Before we move on to the algorithmic part, we list the notations that are used in the following sections.
+
+\begin{table}
+\begin{tabular}{|c|c|}
+\hline 
+$Tr_i$ & Trajectory of object $i$\\ 
+\hline
+$S_t$ & Snapshot of objects at time $t$ \\
+\hline 
+$\mathbb{O}$ & Set of objects \\ 
+\hline 
+$\mathbb{T}$ & Global time sequence \\
+\hline
+$C_t(o)$ & the cluster of object $o$ at time $t$ \\
+\hline 
+$Sr_i $ &  The star structure of object $i$ \\
+\hline 
+\end{tabular} 
+\caption{Notions that will be used}
+\end{table}

### 2016-04-26 introduction_bak.tex
With Comments
With Dongxiang's comments

\section{Introduction}
Positioning devices are becoming increasingly popular in nowadays. For instances, telemetry chips on animals record animal herding histories; GPS equipment on cars records the vehicle movements; Mobile phones and wearable devices carried by people record pedestrians activities; Location-based web services (e.g., Foursquare, Facebook etc.) record user locations. These position data are often time-stamped and can be viewed as trajectories. Data analysis on trajectory data benefits a range of application area and services, including traffic planning, animal analysis, and social recommendations just to name a few.

An important data analysis on trajectories is to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing} can be viewed as a set of objects that travel together for some duration. In practice, we can descritize the temporal domain of trajectories into snapshots, where each snapshot contains the geographical information of all objects. Formally, given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern is found when there exists a cluster with at least $n$ objects which appears for at least $k$ snapshots. Recent works have studied various co-movement patterns with different level of temporal constraints. Jeung et al. proposed \emph{convoy} pattern, which require the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern which relax the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
\begin{figure} [h]
\center
\includegraphics[width=0.5\textwidth]{related_work.eps}
\caption{Co-moving patterns in related works}
\label{fig:related_work}
\end{figure}

\begin{example}
Figure~\ref{fig:related_work} presents a hypothetical set of trajectories involving seven objects. Temporal domain is sliced into 5 snapshots. At each snapshot, objects belonging to the same clusters are marked in the same shape and color. Different patterns discovered are highlighted in the table. In particular:\\
\emph{Convoy} pattern requires the duration of a pattern to be \emph{consecutive}. In Figure~\ref{fig:related_work} only one convoy pattern is found, which is $\{o_3,o_4\}\{t_1,t_2,t_3\}$\\
\emph{Swarm} pattern relaxes the consecutiveness of duration, thus there are three patterns discovered.\\
\emph{Platoon} pattern requires that each local consecutive duration needs to have at least certain length, which is identified by the additional parameter $l$. When $l$ equals 2, there are two patterns discovered. Note that $\{o_6,o_7\}\{t_1,t_4,t_5\}$ is not included in the platoon pattern since $t_1$ is the local consecutive snapshot with duration 1, which is less than $l$.
\end{example}

We notice that, \emph{platoon} pattern is more general than \emph{convoy} and \emph{swarm}. This is because by setting appropriate $l$, \emph{platoon} can be reduced to \emph{convoy} and \emph{swarm} respectively~\cite{li2015platoon}. However, we observe that \emph{platoon} pattern is to loose on the temporal domain thus may result in less significant patterns. For example in Figure~\ref{fig:platoon_weakpoint}.

\begin{figure}[h]
\center
\includegraphics[width=0.5\textwidth]{platoon_weakpoint.eps}
\caption{Miss-pattern in platoon}
\label{fig:platoon_weakpoint}
\end{figure}

In platoon, a pattern for $n=2,k=4,l=2$ could be $\{o_1, o_2\}\{t_1,t_2,t_4,t_5,t_{100},t_{101}\}$. However, the snapshots $t_{100}$ and $t_{101}$ is too far away from previous snapshots. Such two snapshots are in less relation with previous snapshots and thus should be removed from the pattern. Based on this observation, we defined a \emph{generalized co-moving} pattern (as in Section~\ref{sec:definition}) to provide a more fine granular control of the pattern.
In \emph{generalized co-moving} pattern, a parameter $g$ is introduce the control the \emph{maximum gap} allowed between consecutive snapshots. By so doing our generalized co-moving pattern is more expressive and can represent all the existing co-moving patterns.

In step with the advances in localization technologies, the growth in the volume of trajectory data is rapid. Traditional single-machine methods face severe scalability problem in handling large trajectory data. For example, as reported in~\cite{li2015platoon}, a \emph{Swarm} pattern takes around 100 seconds to discover for 100k trajectories. With upto billions of trajectories in nowadays datasets, such approaches apparently become unfeasible. To tackle this challenge, we propose a 
paralleled solution for discovering \emph{generalized co-moving} patterns. We then deploy our idea on the modern MapReduce platform. As our experiments show, our solution achieves well load-balance and can process billions of trajectories in XXX seconds. Several optimizations are also designed to boost our solution to be orders of magnitudes faster than baseline algorithms.

### 2016-04-26 introduction_part2.tex
With Comments
With Dongxiang's comments

\section{Introduction}
The prevalence of positioning devices has drastically boosted the scale of trajectory data collection. Instances include telemetry chips for animal herding histories, GPS devices for urban transportations and wearable devices for personal moving activities. These positional data are often time-stamped and can be viewed as trajectories. Data analysis on large-scale trajectory data can benefit a wide range of applications and services, including traffic planning, animal analysis, and social recommendations, just to name a few. CITATIONS FOR THE ABOVE APPLICATIONS.

An important task of data analysis on trajectories is to discover co-moving objects. Intuitively, a \emph{co-movement} pattern~\cite{li2013managing} consists of a set of objects that travel together for some duration. To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.

%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.

Figure~\ref{fig:related_work} summarizes the differences among various co-movement patterns with an illustrative example. The temporal dimension is sliced into 5 snapshots. By setting $n=2$, the spatial clusters with at least $2$ objects are displayed with the same shape. Since \emph{Convoy} pattern requires the set of objects to be clustered for $k$ \emph{consecutive} snapshots, there results in only one such pattern ($\{o_3,o_4\}\{t_1,t_2,t_3\}$) when $k$ is set to $3$. \emph{Swarm} pattern relaxes the consecutiveness of duration, thus there are three patterns discovered. \emph{Platoon} pattern requires that each local consecutive duration needs to have at least certain length, which is indicated by an additional parameter $l$. When $l$ equals 2, there are two patterns discovered. Note that $\{o_6,o_7\}\{t_1,t_4,t_5\}$ is not included in the platoon pattern since $t_1$ is the local consecutive snapshot with duration 1, which is less than $l$. CAN WE SUPPORT THE GROUP AND FLOCK PATTERN? IF YES, WHY NOT PUT THEM IN THE FIGURE?

FOR THE FIGURE: 1) ENLARGE THE FONT SIZE IN THE FIGURE 2) WHY THERE IS NO $o_5$. 3) WHY OBJECTS IN DIFFERENT COLORS AND SHAPES ARE NOT CLEAR. YOU CAN REMOVE COLOR. 4) PUT THE OBJECTS BELONGING TO THE SAME CLUSTER IN THE SAME LINE.

\begin{figure} [t]
\center
\includegraphics[width=0.5\textwidth]{related_work.eps}
\caption{Co-moving patterns in related works}
\label{fig:related_work}
\end{figure}

%We notice that, \emph{platoon} pattern is more general than \emph{convoy} and \emph{swarm}. This is because by setting appropriate $l$, \emph{platoon} can be reduced to \emph{convoy} and \emph{swarm} respectively~\cite{li2015platoon}. However, we observe that \emph{platoon} pattern is to loose on the temporal domain thus may result in less significant patterns. For example in Figure~\ref{fig:platoon_weakpoint}.

\begin{figure}[h]
\center
\includegraphics[width=0.5\textwidth]{platoon_weakpoint.eps}
\caption{Miss-pattern in platoon}
\label{fig:platoon_weakpoint}
\end{figure}

%In platoon, a pattern for $n=2,k=4,l=2$ could be $\{o_1, o_2\}\{t_1,t_2,t_4,t_5,t_{100},t_{101}\}$. However, the snapshots $t_{100}$ and $t_{101}$ is too far away from previous snapshots. Such two snapshots are in less relation with previous snapshots and thus should be removed from the pattern. Based on this observation, we defined a \emph{generalized co-moving} pattern (as in Section~\ref{sec:definition}) to provide a more fine granular control of the pattern. In \emph{generalized co-moving} pattern, a parameter $g$ is introduce the control the \emph{maximum gap} allowed between consecutive snapshots. By so doing our generalized co-moving pattern is more expressive and can represent all the existing co-moving patterns.

%In step with the advances in localization technologies, the growth in the volume of trajectory data is rapid. Traditional single-machine methods face severe scalability problem in handling large trajectory data. For example, as reported in~\cite{li2015platoon}, a \emph{Swarm} pattern takes around 100 seconds to discover for 100k trajectories. With upto billions of trajectories in nowadays datasets, such approaches apparently become unfeasible. To tackle this challenge, we propose a  paralleled solution for discovering \emph{generalized co-moving} patterns. We then deploy our idea on the modern MapReduce platform. As our experiments show, our solution achieves well load-balance and can process billions of trajectories in XXX seconds. Several optimizations are also designed to boost our solution to be orders of magnitudes faster than baseline algorithms.

%In practice, it is cumbersome to design tailed solutions to different types of co-movement pattern discovery.

%In reality, it is cumbersome to design tailed solutions to support 
%generality and scalability

%In this paper, our primary objectives are solving two

### 2016-04-26 optimization.tex
With Comments
With Dongxiang's comments

@@
 We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
-lies in two factors. The size of each $Sr_s$ and the level the apriori runs.
-In this section, we describe to optimization to reduce the two factors
-respectively.
+lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
+In this section, we provide several optimizations to boost the bottlenecks.
+
+\subsection{Edge Reduction by Direction}
+The first spot for reducing the size of $Sr_s$ is to remove the replicated edges.
+As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure.
+The purpose of replication is to ensure the completeness of star partition.
+However, this replication can be avoided if we choose an appropriate way of partitioning.
+
+We design the edge partitioning method by edge direction.
+Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number.
+Then
+for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$.
+It is easy to see that the directed conceptual graph is a DAG.
+We then create each $Sr_u$ by including all the outgoing edges of $u$.
+By so doing, each edge is assigned to only one star, thus avoids the replications.
+We use the following theorem to ensure the completeness of the edge direction method.
+
+\begin{theorem}[Sound and Completeness of Edge Direction]
+Star partition with edge direction is sound and complete.
+\end{theorem}
+\begin{proof}
+It is notable that each star is a subset of original trajectories, thus the soundness is trivially true.
+For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$.
+Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$.
+Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
+\end{proof}
+An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
+by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.
 
 \subsection{Edge Simplification}
-Each edge $e(s,t)$ in $Sr_s$ contains a time sequence $T$ 
-which represent the co-occurrence of $s$ and $t$. We notice that the edge
-between $s$ and $t$ is not always necessary. For example, if an edge has a
-cardinality less than $K$, then it is not necessary to include this edge to $Sr_s$.
-This motivates to simplify the edges in $Sr_s$ to boost the overall performance.
+Each edge $e(s,t)$ in $Sr_s$ contains a time sequence $ET$ 
+which represent the co-occurrence of $s$ and $t$. We notice that the edge between $s$ and $t$ is not always necessary. For example, if an edge has a
+cardinality less than $K$, it is unnecessary to include this edge to $Sr_s$ since it cannot contribute to any patterns.
+This motivates us to simplify the edges in $Sr_s$ to boost the overall performance.
 
@@
 Given a parameter $G$, a sequence $T$ is \emph{pseudo-consecutive} if and only
-if for any $i\in (0, |T|)$, $T[i] - T[i-1] \leq G$
+if for any $i\in [1, |T|]$, $T[i] - T[i-1] \leq G$
 \end{definition}
@@
 Given the pattern parameters: $L,K,G$, a sequence $T$ is 
-a \emph{partly candidate} sequence if exist one of its maximal pseudo-consecutive
+a \emph{partly candidate} sequence if exists one of its maximal pseudo-consecutive
 subsequence $T'$ such that $T'$ confirms to $L,K,G$.
@@
 For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ 
-is a \emph{partly candidate sequence} since $T_1[0:3] = (1,2,4,5,6)$ is a valid
+is a \emph{partly candidate sequence} since $T_1[1:5] = (1,2,4,5,6)$ is a valid
 pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid partly candidate sequence.
 
-Observing that only partly candidate sequence can be potentially included in a 
+Observing that only partly candidate sequence can be potentially contribute to a 
 pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
-candidate sequence, then this edge can be pruned from $Sr_s$. To efficiently
+candidate sequence, it can be pruned from $Sr_s$. To efficiently
 test whether a given sequence is partly candidate, we define the \emph{Fully Candidate Sequence}:
@@
 edge reduction algorithm.
-\begin{theorem}[Completeness of Algorithm~\ref{algo:simp_prune}]
-For a sequence $T$, let $T_1$ be the result of $T$ after algorithm~\ref{algo:simp_prune},
-if $\exists T' \subseteq T$ and $T'$ is included in a pattern $P$, then $T' \subseteq T_1$.
+\begin{theorem}[Soundness and Completeness Edge Simplification]
+Star partition with edge simplification is sound and complete.
 \end{theorem}
@@
 \begin{proof}
-OMITTED FOR NOW
+Soundness of the star partition is not affected by edge simplification since each star is a subset of original trajectory.
+For completeness, consider a sequence $T$, let $T_1$ be the result of $T$ after first round of simplification.
+By the nature of the first round of simplification, if $P.T \subseteq T$, then $P.T \subseteq T_1$.
+In the second round of simplification, only the pseudoconsecutive parts with size less than $K$ are removed.
+This means, the removed parts is not able to contribute to any patterns.
+Thus if $P.T \subseteq T$, then $P.T \subseteq T'$.
 \end{proof}
-By utilizing the edge simplification technique, the size of $Sr_s$ can be greatly reduced. If
+By leveraging the edge simplification, the size of $Sr_s$ can be greatly reduced. If
 an edge cannot be reduced to a full candidate sequence, then it is directly removed from $Sr_s$.
-If an edge can be reduced to a full candidate sequence, replacing itself with its full candidate sequence 
-would result in a more compact storage.
+If an edge can be reduced to a full candidate sequence, replacing itself by the full candidate sequence results in a more compact storage.
 
 \subsection{Pruning Apriori Mining}
-During the apriori phase, we are repeatedly join candidate pattern in different levels to generate a larger set
-of a pattern. We notice that, such joins can be early terminated 
-by utilizing the property of GCMP. The intuition is that when we are trying to store a level of candidate, if its
-temporal sequence is not a \emph{partly candidate} sequence, then it should able to generate new candidates and thus it
-can be removed from that level of candidate. This \emph{apriori property} 
+During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
+of a patterns. We notice that, such joins can be early terminated 
+by utilizing the monotonic property of GCMP. The intuition is that when we are trying to store a candidate, if its
+temporal sequence is not a \emph{partly candidate} sequence, then it cannot generate full candidate and thus it
+can be pruned. This \emph{monotonic property} 
 is explicitly described as in the follow theorem:
 
-\begin{theorem}[Apriori Property of GCMP]
-Given the temporal parameters $L,G,K$ of GCMP, for a candidate $cand$ in Algorithm~\ref{algo:apriori_mining},
-if $cand.T$ cannot be reduced to a full candidate sequence, then $cand$ can be pruned.
+\begin{theorem}[Monotonic Property of GCMP]
+Given the temporal parameters $L,G,K$, for a candidate $cand$ in Algorithm~\ref{algo:apriori_mining},
+if $cand.T$ cannot be reduced to a partly candidate sequence, then $cand$ can be pruned.
 \end{theorem}
 \begin{proof}
-OMITTED FOR NOW
+Let $cand_i$ be a $i$-pattern.
+If $cand_i$ is generated from $cand_j$ where $j < i$, then if $cand_j.T \subseteq cand_i.T$.
+That is as the level goes up, the time sequence set of a candidate shrinks.
+Therefore, if $cand_j.T$ is not a partly candidate sequence, $cand_i.T$ cannot be a partly candidate sequence.
 \end{proof}
 
-Utilizing the \emph{Apriori Property}, the new candidate in each level is greatly reduced, which is shown in
-the experiment session.
+With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.

### 2016-04-26 system.tex
With Comments
With Dongxiang's comments

@@
 \section{Preliminary on Apache Spark}
-Apache Spark is the modern parallel processing platform
-based on Resilient-Distributed-Dataset (RDD), which
-is open-sourced by UC Berkeley. Spark differs from
-traditional MapReduce framework (e.g., Hadoop) in the 
-following features:
-\begin{enumerate}
-\item{It supports general computation DAGs beyond the two-stage MapReduce topologcy.}
-\item{The execution engine can tolerate the loss of any works}
-\item{It provides an in-memory storage abstraction called Resilient Distributed Datasets (RDDs). that 
-lets applications keep data in memory, and automatically reconstructs the lost partitions upon failures.}
-\end{enumerate}
+Apache Spark is an open sourced modern parallel processing platform
+based on Resilient-Distributed-Dataset (RDD).
+Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD.
+Algorithms in Spark is implemented by supplying various actions to an input RDD.
+Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.
 
-In MapReduce-like systems, the major bottleneck is the \emph{shuffle} operation. 
-In the \emph{shuffle} operation, data are re-partitioned and send to executors
-via networks. Such operation is more costly than CPU and disk I/Os, which contribute
-most in MapReduce-like applications.
-
-TO BE ADDED....
+Compared to MapReduce, Spark 
+utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}.
+In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
+Due to threading, there is a paradigm shift from MapReduce to Spark.
+In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process.
+While in Spark, the cost of starting a task is negligible since each task is done by a thread.
+Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.
 
 \section{Mining Generalized Co-moving Pattern}
-The outline of GCMP mining is to first cluster objects at
-each snapshots and followed by mining the patterns among clusters
-of different snapshots. In Spark scenario, 
-the first step can be easily performed in parallel. 
-This is because the objects at each snapshots are independent. Therefore, we
-can partition the trajectories based on snapshots to achieve parallelism. 
-In contrast, naively design the 
-the second step may suffer from inter-executor communications.
+There are two stages in mining GCMP.
+The first stage is to cluster objects in each snapshots.
+Then the seconds stage is to mine patterns from clusters in parallel.
+The overview of the parallel approach is
+shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
+read trajectories and cluster objects in the same snapshots.
+Since the objects at each snapshots are independent, this stage can be easily performed in parallel.
+The first stage involves network IO.
+Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.
+In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.
+
+\begin{definition}[Completeness and Soundness]
+Let a partitioning method $\mathbb{P}$ partitions original trajectories $TR$ into multiple parts, $Par_1,...,Par_m$.
+$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $TR$, $\exists Par_i$ such that $P$ is valid in $Par_i$.
+$\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
+\end{definition}
+The completeness ensures that no real patterns are missed out.
+The soundness ensures that no false patterns are reported.
+If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel.
+
+Depends on the pattern mining strategy, the size of shuffle and replication may differ.
+We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.
+
+\begin{figure} [h]
+\center
+\includegraphics[width=0.5\textwidth]{system_layout.jpg}
+\caption{System Flow of Mining GCMP}
+\label{fig:overview}
+\end{figure}
 
 \subsection{Temporal Replication and Mining}
-The straightforward method of parallelizing GCMP mining is to partition
-the trajectories in the temporal domain. A simple but effective method
-is to group neighborhood snapshots in to a partition, such that all patterns
-can be mined within a partition. In order to achieve the \emph{completeness},
+The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
+A simple but effective method
+is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
 some of the snapshots need to be replicated on multiple executors.
-We thus call this method the \emph{Temporal Replication and Mining} approach. 
+We call this method the \emph{Temporal Replication and Mining} approach. 
 The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.
@@
 In order to reduce the shuffling cost, the data to be replicated should be
-kept to a minimum. To control the number of snapshots that are replicated, 
-we use the following theorem to facilitate a partition:
+kept to a minimum. However, as suggested in the following theorem, the minimum replication of a snapshot is not small:
 
-\begin{theorem}[Completeness of Replication Partition]
+\begin{theorem}[Soundness and Completeness of Replication]
 \label{thm:replication_partition}
-For each snapshot $S_t$, a partition $Par_t = \{S_t, S_{t+1},...,S_{t+(K-1)*G+K}\}$ 
-is created. Then, for any global pattern $P$, there must exist at least one partition $Par_i$
-such that $P$ is also a pattern in $Par_i$.
+For each snapshot $S_t$, a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K)}\}$ 
+is created. Such a partition method is sound and complete.
 \end{theorem}
 \begin{proof}
-PROOF BY CONTRADICTION, OMITTED FOR NOW
+The soundness of partition is trivially true by definition.
+Given a valid pattern $P$, let $T' \subseteq P.T$ be a subsequence of $P.T$ which conforms to $K,L,G$. Note that there could be many qualified $T'$ of $T$. Then, 
+let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$.
+Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$.
+Since $T'$ conforms to $K,L,G$, then $\Sigma_i (l_i) \geq K$, and $K \geq l_i \geq L$, $g_i \leq G$.
+Therefore, among all possible $T'$s, the minimum size is $\lfloor \frac{K}{L}-1\rfloor *G+K$.
+Thus ensuring each $Par_t$ to be of that size would capture one of the $T'$s, therefore the pattern $P$ is valid in $Par_t$.
+This proves the completeness of the partitioning method.
 \end{proof}
@@
 Utilizing Theorem~\ref{thm:replication_partition}, we create, for each snapshot $S_t$, 
-a partition containing its next $(K-1)*G+K$ snapshots. Each partition is then
-sending to the executors as a task. Since any global pattern must exists in 
-one of the partitions, we can mine the patterns from each partitions independently.
+a partition containing its next $\lfloor \frac{K}{L}-1\rfloor *G+K$ snapshots. Each partition is then
+sent to the executors as a task. Since any global pattern must exists in one of the partitions, we can mine the patterns from each partitions independently, without loss of patterns.
 
 \subsubsection{Temporal Replication Mining}
-After replication, each task in Spark will process an interval of snapshots $Par_i$. The next
+After replication, each task in Spark will process an partition $Par_i$. The next
 step is to mine the GCMPs from $Par_i$. We notice that, for each 
@@
 are contained in the first snapshots. Therefore we design a line-sweep method for mining 
-such patterns. DETAILS OMITTED FOR NOW.
+such patterns, which is the variant of the Coherent-Moving-Clustering method in~\cite{jeung2008convoy}.
 
@@
 Specifically, each snapshots are copied $(K-1)*G+K$ times. In swarm
-case, $G$ is as large as $|T|$. Then, it is equivalent to shuffle entire dataset 
+case, $G$ is as large as $|\mathbb{T}|$. In such a case, it is equivalent to replicate the entire dataset 
 to each executor, which is clearly inefficient.
@@
 To develop a method that achieves parallelism under any pattern parameters, 
-we propose a solution called \emph{Star Partition and Mining}. In SPM,
-we design a novel object-based partition method named star partition. In star partition,
-instead of partitioning trajectories in temporal domain, we partition trajectories 
-in object domain. After partitioning, we use the \emph{Apriori}-like 
-method to mine the patterns out of each partition. 
-The outline of the start partition and mining is as in Algorithm~\ref{algo:spm_overview}
+we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
+we design a novel object-based partition method named star partition.
+A start partition partitions trajectories in the object domain rather than temporal domain.
+After partitioning, we design the \emph{Apriori}-like
+method to mine the patterns out of each partition independently. 
+The overview of the star partition and mining is as in Algorithm~\ref{algo:spm_overview}.
 
@@
 \subsubsection{Star Partition}
-The purpose of star partition is to find the group of object that 
+The purpose of star partition is to find the group of objects that 
 could potentially form a pattern. In order to achieve parallelism, 
-we find and group, for each object $o$, all other objects that connect to $o$ in some
-snapshots. By so doing, the patterns containing $o$ can be discovered within
-each groups. Technically, we create a connection graph to represent the
+we group, for each object $o$, all other objects that connect to $o$ in some snapshots. By so doing, the patterns containing $o$ can be discovered within each groups. 
+Technically, we create a connection graph to represent the
 connectivity among objects. A connection graph is an undirected graph $G=(V:E)$, where 
-each $v \in V$ represents an object. An edge $e(s,t)= T$ 
-represents the connection between vertex $s,t$ at all times in $T$, 
-i.e. $\forall t \in T, C_t(s) = C_t(t)$. 
-Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$.
-In star partition, the trajectories are partitioned based on objects and their stars. Then
+each $v \in V$ represents an object. An edge $e(s,t)= ET$ 
+contains all the timestamps where $s,t$ are in the same cluster,
+i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
+Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$. An example of star partition is shown in Figure~\ref{fig:star_partition}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{star_partition.jpg}
+\caption{Example of Star Partition}
+\label{fig:star_partition}
+\end{figure}
+
+In star partition, trajectories are partitioned based on objects and their stars. Then
 each partition is send to an executor as a task. 
-We state the completeness of star-partition as in the following theorem:
-\begin{theorem}[Completeness of Star Partition]
-Given a connection graph $G$, for any global pattern $P$, there exists a $s \in G.V$ such 
-that $P$ is a pattern in $Sr_s$.
+Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories.
+This is done by treating each vertex in $Sr_s$ as an object.
+For $s$, the time sequence is the union of all edges in $Sr_s$.
+For vertex $v \neq s$, the time sequence is the edge $(s,v)$.
+Then, we state the completeness of star-partition as in the following theorem:
+\begin{theorem}[Soundness and Completeness of Star Partition]
+Star partition is sound and complete.
 \end{theorem}
@@
 \begin{proof}
-OMITTED FOR NOW
+For the soundness,
+if $P$ is a valid pattern in $Sr_s$, then for every object $v\neq s, v \in P.O$, and for every timestamp $t\in P.T$, $C_t(v) = C_t(s)$.
+This means, for every snapshot $t$, all object in $P.O$ belongs to the same cluster.
+Thus, $P$ is a valid pattern in original trajectories.
+
+For the completeness,
+if $P$ is a valid pattern in original trajectories, for an arbitrary object $s \in P.O$, it follows $P.O \equiv S_r$.
+Since for any time $t$, $C_s(t) = C_v(t) \forall v \in P.O$, every time in $P.T$ appears in edges in $Sr_s$, thus $P$ is valid pattern in $Sr_s$.
 \end{proof}
 
-Based on the above theorem, each task can be processed independently by executors. 
-Thus, the inter-executor communication is avoided during the mining phase. It is notable that, the 
-replication of data is $O(|\mathbb{O}|^2|T|)$, which is regardless the parameters of patterns.
+Based on the above theorem, each star can be processed independently by executors, which avoids the inter-executor communication during the mining phase. It is notable that, the 
+replication of data is $O(|\mathbb{O}|^2|\mathbb{T}|)$, which is free from the parameters of patterns.
 In later sections, we will describe optimization techniques to reduce the replications.
@@
 \subsubsection{Apriori Mining}
-For each task, in the mining phase, we need to find the patterns that conform to the parameter
-setting. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
-is similar to frequent item mining. If a candidate pattern's object set is of size $R$, we call
-this candidate a $R$-pattern. Our apriori mining algorithm tries to generate all $R$-pattern in
-each iteration. As a start, the $2$-pattern is generated from edges in $Sr_s$. In particular,
-for each $e(s,t)=T$, pattern $p=(\{s,t\}, T)$ is formed. During each iteration $R$, 
-we generate $R+2$-cluster pattern by joining $(R+1)$-cluster patterns with $2$-cluster patterns. 
-The join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
+For each task, in the mining phase, we need to find the patterns that conform to the parameters. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
+is similar to frequent item mining. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $|R|$. 
+Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
+for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
+we generate $(R+1)$-cluster patterns by joining $R$-cluster patterns with $2$-cluster patterns. Specifically,
+the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
+Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-cluster at most to a $(R+1)$-cluster.
 Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
@@
 \State { Lv $\gets \{\}$}
-\State { Lv2 $\gets \{\}$}
+\State { Ground $\gets \{\}$}
 \ForAll{$e(s,t) = T \in Sr_s$}
-\State Lv2.add($\langle \{s,t\}, T \rangle$);
-\State Lv $\gets$ Lv2;
+\State Ground.add($\langle \{s,t\}, T \rangle$);
+\State Lv $\gets$ Ground;
 \EndFor
@@
 		\ForAll{$cand_v \in Lv$}
-			\ForAll{$cand \in Lv2$}
+			\ForAll{$cand \in $Ground}
 				\State $p \gets cand_v$ join $cand$
@@
 are two major factors dragging the performance. First, the size of $Sr_s$ affects
-the number initial size of $2$-patterns. Second, the level that apriori runs. In later
+the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
 sections, we exploit the property of GCMP to reduce the two factors.

### 2016-05-01 definitions.tex
Fixed first 4 sections

@@
 \label{sec:definition}
-Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps.
-We use $T[i]$ to denote the $i^{th}$ entry in a time sequence.
+Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern. 
+We use $T \subseteq \{1,2,...,m\}$ to denote a descritized sequence of timestamps, where
+$T[i]$ denotes the $i^{th}$ entry in the sequence and $|T|$ is the 
+cardinality of the sequence.
 
-Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
-if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$.
+A time sequence is consecutive if the difference between any of its neighboring entries
+is 1, that is $\forall T[i], T[i+1] \in T, T[i+1] = T[i] + 1$. For any time sequence,
+it can be decomposed into at least one consecutive portion(s). Therefore we can define the 
+$L$-consecutiveness as follows:
+%
+%
+%We say a sequence $T$ is \emph{(fully)consecutive}
+%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$.
 A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt.
@@
 
-\begin{definition}[$L$-consecutive]
-A time sequence $T$ is $L$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq L$.
+\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
+A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
+has cardinality greater or equal to $L$.
 \end{definition}
@@
 Take $T=\{1,2,3,5,6\}$ as an example.
-$T$ is not $3$-consecutive since $\{5,6\}$ is a maximally consecutive subsequence with cardinality less than $3$.
-$T$ is $2$-consecutive since both its two maximally consecutive subsequences are of the sizes greater or equal to $2$.
-It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping.
+$T$ is not $3$-consecutive since $\{5,6\}$ has a cardinality less than $3$.
+$T$ is $2$-consecutive since both of its consecutive portions are of sizes at least $2$.
+To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows:
 
-We then define the $G$-separateness as follows:
-
-\begin{definition}[$G$-separated]
-A time sequence $T$ is $G$-separated iff $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$
+\begin{definition}[$G$-connected]
+A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
+ $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$.
 \end{definition}
 
-Take $T={1,2,3,5,6}$ as an example.
-$T$ is $2$-separated since the gap between its maximally consecutive subsequnces is $5-3=2$.
-However, $T$ is not $1$-separated.
-Indeed, $1$-separated infers that $T$ is fully consecutive.
+Take $T=\{1,2,3,5,6\}$ as an example.
+$T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
+However, $T$ is not $1$-connected.
+Indeed, $1$-connection infers that $T$ is consecutive.
 
-Given a time sequence $t$, objects locations at $t$ collectively forms a \emph{snapshot}\footnote{Missing timestamps can be interpreted using linear interpolation~\cite{jeung2008convoy}}.Objects in a snapshot can thus be clustered based on the
-closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, we can then define the generalized co-moving pattern as follows:
-
-\begin{definition}[Generalized Co-Movement Pattern]
-A \emph{generalized co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a sequence $T \subseteq \mathbb{T}$, with the following constraints:
-\begin{enumerate}
-\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
-\item{Significance: $|O| \geq M$}
-\item{Duration: $|T| \geq K$}
-\item{Consecutiveness: $T$ is $L$-consecutive}
-\item{Separateness: $T$ is $G$-separated}
-\end{enumerate} 
+Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the
+closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
+\begin{definition}[General Co-Movement Pattern]
+A \emph{General co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a time sequence $T$, with the following constraints: (1)Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$.
+(2) Significance: $|O| \geq M$.
+(3) Duration: $|T| \geq K$.
+(4) Consecutiveness: $T$ is $L$-consecutive, and (5)Connection: $T$ is $G$-connected.
+%\begin{enumerate}
+%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
+%\item{Significance: $|O| \geq M$}
+%\item{Duration: $|T| \geq K$}
+%\item{Consecutiveness: $T$ is $L$-consecutive}
+%\item{Separateness: $T$ is $G$-separated}
+%\end{enumerate} 
 \end{definition}
 
-The generalized co-movement pattern retains the patterns that discovered by existing techniques (convoy, swarm and platoon).
+The general co-movement pattern retains the patterns that discovered by all 
+existing techniques (group, flock, convoy, swarm and platoon). 
+The relationships between general co-movement pattern and other patterns are summarized in Table~\ref{tbl:patterns}.
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline 
+Pattern & $L$ & $G$ & $M$ & $K$ \\ 
+\hline
+Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
+\hline
+Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
+\hline 
+Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
+\hline 
+Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
+\hline 
+Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
+\hline 
+\end{tabular} 
+\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
+\label{tbl:patterns}
+\end{table}
+
 In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern.
 By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern.
-Finally by setting $G=1$, we achieve the \emph{convoy} pattern.
-In addition to covering existing patterns, the generalized co-movement pattern avoids the \emph{miss-pattern} problem in \emph{platoon} pattern.
-As suggested in Figure~\ref{fig:platoon_weakpoint}, $\{100,101\}$ will be included in the platoon pattern, however since they're too far away in temporal domain, this pattern is not prominent.
-By setting appropriate $G$, we are able to prune these two snapshots.
-Notice that such a new pattern cannot be modeled by existing patterns.
+By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
+Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern.
+In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern.
+As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
+By setting appropriate $G$, we are able to prune this anomaly.
+It is notable that GCMP is not able to be modeled by existing patterns.
 
-It is notable that the number of patterns in GCMP is exponential.
-To control the number of output patterns, we noticed that, for two pattern result $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
-Based on this observation, we define the \emph{closed generalized co-movement pattern} as follows:
-\begin{definition}[Closed Generalized Co-moving Pattern]
-A generalized co-moving pattern $P=\langle O, T \rangle$ is a closed generalized co-moving pattern if and only if there does not exists another generalized co-moving pattern $P'$ s.t.
-$P'.O \supseteq P.O$.
+It is also observable that the number of patterns in GCMP is exponential. To control the size of output, 
+we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
+Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:
+
+\begin{definition}[Closed General Co-Movement Pattern]
+A general co-moving pattern $P=\langle O, T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
 \end{definition}
-For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern.The closed pattern avoids to output duplicate information, thus making the result patterns more compact.
+
+For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern.
+The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
+
+LETS KEEP THE CLOSENESS INFORMATION AT THE MOMENT. IF NO CLOSENESS IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
 %For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.
 
-Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters.
+%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes.
 Therefore in this paper, we mainly consider density-based clustering.
+Our definition of GCMP is free from clustering method.
+Users are able to supply different clustering method to facilitate different needs.
+We currently expose both disk-region based clustering and DBSCAN as APIs to the user.
 
-The goal of this paper is to present a parallel solution for discovering GCMP from large-scale trajectory data.
+In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory data.
 
@@
 
-\begin{table}
+\begin{table}[h]
+\centering
 \begin{tabular}{|c|c|} 
+\hline
+Symbols & Meanings \\
 \hline 
@@
 \hline 
-$\mathbb{T}$ & Global time sequence \\
+$T$ & Time sequence \\
 \hline

### 2016-05-01 introduction.tex
Fixed first 4 sections

\section{Introduction}
The prevalence of positioning devices has drastically boosted the scale of trajectory data collection. 
Instances include telemetry chips for animal herding histories, 
GPS devices for urban transportation and wearable devices for personal moving activities. 
These positional data are timestamped and can be viewed as trajectories. 
Data analysis on large-scale trajectories benefits a wide range of applications and services, including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, just to name a few.% CITATIONS FOR THE ABOVE APPLICATIONS.

An important task of data analysis on trajectories is to discover co-moving objects. 
As its name suggests, a \emph{co-movement} pattern~\cite{li2013managing} consists 
of a group of objects that travel together for some duration, where the group is formed
by certain clustering methods. A pattern is prominent 
if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$
are user specified parameters. Depends on further constraints on object clustering
and time duration, several specific patterns are proposed in the literature.

Specifically, on the aspect of object clustering, \emph{flock}~\cite{gudmundsson2006flock} and \emph{group}~\cite{wang2006grouppattern} patterns require objects to be within a disk region.
In contrast, \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} and
\emph{platoon}~\cite{li2015platoon} patterns require objects to be densely connected. 
In terms of the constraints on time duration, \emph{flock}~\cite{gudmundsson2006flock} and \emph{convoy}~\cite{jeung2008convoy}
require the timestamps to be consecutive. \emph{Swarm}~\cite{li2010swarm}, on the
other hand, do not impose any restrictions. \emph{Group}~\cite{wang2006grouppattern} 
and \emph{platoon}~\cite{li2015platoon} introduce the parameter $L$ to control the minimum length of the local-consecutive
timestamps. 
The compare and contrast of these co-movement patterns are presented in Table~\ref{tbl:existing_co_patterns}.

%Specifically, a \emph{flock}~\cite{gudmundsson2006flock} requires the group to be within a disk region of
%the user specified size.  A \emph{convoy}~\cite{jeung2008convoy} requires a group to be densely connected. Both \emph{flock}
%and \emph{convoy} require a group to appear for at least $k$ consecutive times.  
%\emph{Group}~\cite{wang2006grouppattern} and 
%\emph{Swarm}~\cite{li2010swarm} patterns relax the consecutiveness constraint, where non-consecutive timestamps are allowed in a pattern duration. \emph{Group} pattern require objects in a group to be within a disk region, while \emph{swarm}require the objects in a group to be densely connected.
%Recently,
%\emph{platoon}~\cite{li2015platoon} pattern is proposed to impose a fine-grained control on the consecutiveness of the duration. In \emph{platoon}, the duration of a group needs to have the local-consecutive portion of size no less than the user-specified $L$.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Pattern & Clustering Method & Consecutiveness on Duration \\ 
\hline 
Flock~\cite{gudmundsson2004flock} & Disk region &  Consecutive \\ 
\hline 
Convoy~\cite{jeung2008convoy} & Density &   Consecutive \\ 
\hline 
Group~\cite{wang2006grouppattern} & Disk region &  Local consecutive $\geq L$ \\ 
\hline 
Swarm~\cite{li2010swarm} & Density  & No constraint \\ 
\hline 
Platoon~\cite{li2015platoon} & Density &  Local consecutive $\geq L$ \\ 
\hline 
\end{tabular} 
\caption{Existing Co-movement Patterns}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.

%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of five trajectories.
First, the temporal domain is discretized into five snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ can be reduced to $\langle\{O_5,O_6\}\{4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

% we achieve two \emph{platoon} patterns.
% 
%By setting $M=2$, the spatial clusters with at least $2$ objects are displayed with the same shape. Since \emph{Convoy} pattern requires the set of objects to be clustered for $k$ \emph{consecutive} snapshots, there results in only one such pattern ($\{o_3,o_4\}\{t_1,t_2,t_3\}$) when $k$ is set to $3$. \emph{Swarm} pattern relaxes the consecutiveness of duration, thus there are three patterns discovered. \emph{Platoon} pattern requires that each local consecutive duration needs to have at least certain length, which is indicated by an additional parameter $l$. When $l$ equals 2, there are two patterns discovered. Note that $\{o_6,o_7\}\{t_1,t_4,t_5\}$ is not included in the platoon pattern since $t_1$ is the local consecutive snapshot with duration 1, which is less than $l$. CAN WE SUPPORT THE GROUP AND FLOCK PATTERN? IF YES, WHY NOT PUT THEM IN THE FIGURE?
%
%FOR THE FIGURE: 1) ENLARGE THE FONT SIZE IN THE FIGURE 2) WHY THERE IS NO $o_5$. 3) WHY OBJECTS IN DIFFERENT COLORS AND SHAPES ARE NOT CLEAR. YOU CAN REMOVE COLOR. 4) PUT THE OBJECTS BELONGING TO THE SAME CLUSTER IN THE SAME LINE.

\begin{figure} [h]
\center
\includegraphics[width=0.5\textwidth]{related_work.eps}
\caption{Trajectories and Co-Movement Patterns}
\label{fig:related_work}
\end{figure}

%We notice that, \emph{platoon} pattern is more general than \emph{convoy} and \emph{swarm}. This is because by setting appropriate $l$, \emph{platoon} can be reduced to \emph{convoy} and \emph{swarm} respectively~\cite{li2015platoon}. However, we observe that \emph{platoon} pattern is to loose on the temporal domain thus may result in less significant patterns. For example in Figure~\ref{fig:platoon_weakpoint}.

%
%\begin{figure}[h]
%\center
%\includegraphics[width=0.5\textwidth]{platoon_weakpoint.eps}
%\caption{Miss-pattern in platoon}
%\label{fig:platoon_weakpoint}
%\end{figure}

%In platoon, a pattern for $n=2,k=4,l=2$ could be $\{o_1, o_2\}\{t_1,t_2,t_4,t_5,t_{100},t_{101}\}$. However, the snapshots $t_{100}$ and $t_{101}$ is too far away from previous snapshots. Such two snapshots are in less relation with previous snapshots and thus should be removed from the pattern. Based on this observation, we defined a \emph{generalized co-moving} pattern (as in Section~\ref{sec:definition}) to provide a more fine granular control of the pattern. In \emph{generalized co-moving} pattern, a parameter $g$ is introduce the control the \emph{maximum gap} allowed between consecutive snapshots. By so doing our generalized co-moving pattern is more expressive and can represent all the existing co-moving patterns.

%In step with the advances in localization technologies, the growth in the volume of trajectory data is rapid. Traditional single-machine methods face severe scalability problem in handling large trajectory data. For example, as reported in~\cite{li2015platoon}, a \emph{Swarm} pattern takes around 100 seconds to discover for 100k trajectories. With upto billions of trajectories in nowadays datasets, such approaches apparently become unfeasible. To tackle this challenge, we propose a  paralleled solution for discovering \emph{generalized co-moving} patterns. We then deploy our idea on the modern MapReduce platform. As our experiments show, our solution achieves well load-balance and can process billions of trajectories in XXX seconds. Several optimizations are also designed to boost our solution to be orders of magnitudes faster than baseline algorithms.

%In practice, it is cumbersome to design tailed solutions to different types of co-movement pattern discovery.

%In reality, it is cumbersome to design tailed solutions to support 
%generality and scalability

%In this paper, our primary objectives are solving two

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is an urgent demand for a general platform to support all these co-movement patterns. Another issue with existing methods is that they are built on top of centralized indexes that are not scalable. The maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect millions of trajectories. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. None of them can handle millions of trajectories efficiently.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other. Such a pattern is likely to be induced by periodic movements of unrelated objects thus is of low interests. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to reduce to existing patterns by setting appropriate parameters.

Second, we propose a parallel solution based on Spark for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance.

Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:solution} and Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.

### 2016-05-01 system.tex
Fixed first 4 sections

@@
-\section{Preliminary on Apache Spark}
-Apache Spark is an open sourced modern parallel processing platform
-based on Resilient-Distributed-Dataset (RDD).
+\section{Overview of Mining GCMP in Parallel}
+\label{sec:system_overview}
+We adapt the MapReduce paradigm for designing
+a parallel solution of mining GCMP. MapReduce was proposed by Dean et. cl.~\cite{}
+and has become a mature parallel platform for large-scaled data processing. 
+Current open source MapReduce systems provide handy programming APIs with fault tolerances
+in backends. Such systems 
+include Apache Hadoop, Apache Shark and Apache Spark to name a few.
+
+In simple words, there are two types of cluster nodes in MapReduce, namely the 
+\emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
+three stages: First, input data
+are partitioned and read by a \emph{map} function on each mapper. Then, mappers
+emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
+reducers process received data using a \emph{reduce} function then write the
+outputs.
+Since the \emph{shuffle} stage needs to transfer data over network, 
+an important attention to pay during designing MapReduce algorithms is 
+to minimize the shuffle amounts and shuffle counts.
+
+Our GCMP mining workflow follows the MapReduce style which consists of five stages
+as illustrated in the Figures~\ref{fig:overview} (a)-(e).
+As shown, in stage (a), trajectory data 
+are read from various sources and partitioned based on objects timestamps, where objects
+of the same timestamps form a snapshots. After partitioning, snapshots are send to workers
+prior to stage (b). In stage (b), objects belonging to the same snapshots are clustered
+based on the user supplied clustering method. Then those clusters are shuffled to 
+workers prior to stage (c). In stage (c), each worker collects the clusters sent to its partition
+and discover the GCMP from these local clusters. A post-check is required to remove
+duplicate patterns. In stage (d), patterns discovered in previous stages are write to output.
+
+\begin{figure} [t]
+\center
+\includegraphics[width=0.5\textwidth]{system_layout.eps}
+\caption{System Flow of Mining GCMP}
+\label{fig:overview}
+\end{figure}
+
+The first two stages of our solution could be straightforward. 
+However, it is challenging to design the partition and mining methods
+to in stage (c) and (d). Intuitively, A reasonable partition strategy 
+needs to meet the following requirements: first, the result partitions need
+to preserve enough information so that real patterns can be discovered
+in stage (d). Second, the result partitions need to ensure that
+the patterns that discovered in stage (d) are real patterns so that
+no further validation is required after stage (d). We formalize the two 
+properties using \emph{completeness} and \emph{soundness} as follows:
+
+\begin{definition}[Completeness and Soundness]
+Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$.
+$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$.
+$\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
+\end{definition}
+The completeness ensures that no real patterns are missed out.
+The soundness ensures that no false patterns are reported.
+If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel in stage (d).
+
+Apparently replicating entire data set to each partition meets the \emph{soundness} and \emph{completeness}, however, it burdens the network shuffle and GCMP mining.
+Our objective is thus to design a complete and sound partition method that
+minimize the network shuffles.
+
+%Depends on the pattern mining strategy, the size of shuffle and replication may differ.
+We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.
+
+%
+%In particular, we need
+%the number of partitions to be reasonably large in order to achieve
+%good parallelism in stage (d). Meanwhile, we need to ensure a partition 
+%of snapshots containing enough information so that patterns discovered 
+%in stage (d) are complete.  Furthermore, we have to ensure that the
+%patterns that discovered in stage (d) are real patterns.
+
+%However, there are two conflicting requirements that restrain us from 
+%designing a simple and effective solution. 
+%On one hand, we need to partition snapshots in stage (c) as many as possible 
+%so that good parallelism could be achieved in stage (d). 
+%On the other hand, in stage (d), 
+%we require each partition containing enough information in order to discover
+%proper GCMP patterns. This prevents us from arbitrarily partition snapshots in
+%stage (d). To design a working algorithm, find the minimum size of partition is
+%crucial. In the following section, we first design a naive approach that
+%partitions snapshots by allowing overlapping among partitions. Such a partition strategy
+%although has overhead in shuffling, it corrects find GCMPs in parallel in stage (d).
+%In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.
+
+%\section{Temporal Replication and Mining}
+%
+%
+%%It is notable that some patterns 
+%%may be very long in duration (e.g., when discovering \emph{swarm}) or some patterns 
+%%may contain a large set of objects (e.g., when discover \emph{group} patterns with small $L$).
+%%Therefore, we require the size of partition to be large enough. Reaching the
+%%balance between the two requirement is crucial. In the following sections, we will
+%%describe a naive partition scheme which meets the two requirements.
+%
+%%Our parallel solution incurs two rounds of shuffles. The first round of shuffle happens in step (a). This
+%%is because that the trajectories stored in HDFS needs to be regrouped to form snapshots. 
+%%The second round of shuffle occurs in step(d). This is because that 
+%% the clusters need to be regrouped so that subsequent pattern detection can be performed.
+%% Despite the simpleness of our parallel solution, it is actually nontrivial to work out a scalable solution.
+%% The major challenge lies in the step (d) and (e). 
+%
+%
+%%\section{Preliminary on Apache Spark}
+%%\label{sec:system_overview}
+%%Apache Spark is an open sourced modern parallel processing platform
+%%based on Resilient-Distributed-Dataset (RDD).
 Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD.
@@
 Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.
-
-Compared to MapReduce, Spark 
-utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}.
+%%
+%%Compared to MapReduce, Spark 
+%%utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}.
 In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
-Due to threading, there is a paradigm shift from MapReduce to Spark.
+%Due to threading, there is a paradigm shift from MapReduce to Spark.
 In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process.
@@
 
-\section{Mining Generalized Co-moving Pattern}
-There are two stages in mining GCMP.
+%\section{Mining Generalized Co-moving Pattern}
+%\label{sec:solution}
+%There are two stages in mining GCMP.
 The first stage is to cluster objects in each snapshots.
@@
 The overview of the parallel approach is
-shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
-read trajectories and cluster objects in the same snapshots.
+%shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
+%read trajectories and cluster objects in the same snapshots.
 Since the objects at each snapshots are independent, this stage can be easily performed in parallel.
@@
 Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.
-In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.
 
-\begin{definition}[Completeness and Soundness]
-Let a partitioning method $\mathbb{P}$ partitions original trajectories $TR$ into multiple parts, $Par_1,...,Par_m$.
-$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $TR$, $\exists Par_i$ such that $P$ is valid in $Par_i$.
-$\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
-\end{definition}
-The completeness ensures that no real patterns are missed out.
-The soundness ensures that no false patterns are reported.
-If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel.
-
-Depends on the pattern mining strategy, the size of shuffle and replication may differ.
-We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.
-
-\begin{figure} [h]
-\center
-\includegraphics[width=0.5\textwidth]{system_layout.jpg}
-\caption{System Flow of Mining GCMP}
-\label{fig:overview}
-\end{figure}
-
-\subsection{Temporal Replication and Mining}
+\section{Temporal Replication and Mining}
 The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 

### 2016-05-05 sec1_introduction.tex
Stage 1
First Draft 0.1

--- 2016-05-01 introduction.tex
@@
 \section{Introduction}
-The prevalence of positioning devices has drastically boosted the scale of trajectory data collection. 
-Instances include telemetry chips for animal herding histories, 
-GPS devices for urban transportation and wearable devices for personal moving activities. 
-These positional data are timestamped and can be viewed as trajectories. 
-Data analysis on large-scale trajectories benefits a wide range of applications and services, including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, just to name a few.% CITATIONS FOR THE ABOVE APPLICATIONS.
+The prevalence of positioning devices has drastically boosted 
+the scale and spectrum of trajectory collection to an unprecedented level. 
+Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
+records, are continually generated from animal telemetry chips, 
+vehicle GPSs and wearable devices. Data analysis on large-scale 
+trajectories benefits a wide range of applications and services, 
+including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, to name just a few.
 
-An important task of data analysis on trajectories is to discover co-moving objects. 
-As its name suggests, a \emph{co-movement} pattern~\cite{li2013managing} consists 
-of a group of objects that travel together for some duration, where the group is formed
-by certain clustering methods. A pattern is prominent 
-if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$
-are user specified parameters. Depends on further constraints on object clustering
-and time duration, several specific patterns are proposed in the literature.
+A crucial task of data analysis on top of trajectories is 
+to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
+refers to a group of objects traveling together for a certain period of time 
+and the group is normally determined according to spatial proximity. 
+A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
+and driven by different mining applications, there are a bunch of variants 
+of co-moving patterns that have been developed with more advanced constraints.
 
-Specifically, on the aspect of object clustering, \emph{flock}~\cite{gudmundsson2006flock} and \emph{group}~\cite{wang2006grouppattern} patterns require objects to be within a disk region.
-In contrast, \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} and
-\emph{platoon}~\cite{li2015platoon} patterns require objects to be densely connected. 
-In terms of the constraints on time duration, \emph{flock}~\cite{gudmundsson2006flock} and \emph{convoy}~\cite{jeung2008convoy}
-require the timestamps to be consecutive. \emph{Swarm}~\cite{li2010swarm}, on the
-other hand, do not impose any restrictions. \emph{Group}~\cite{wang2006grouppattern} 
-and \emph{platoon}~\cite{li2015platoon} introduce the parameter $L$ to control the minimum length of the local-consecutive
-timestamps. 
-The compare and contrast of these co-movement patterns are presented in Table~\ref{tbl:existing_co_patterns}.
+Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
+with different constraints in the attributes of clustering method and length of temporal duration. 
+In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
+and \emph{group}~\cite{wang2006grouppattern} patterns require 
+all the objects in a group to be enclosed by a disk with radius $r$; 
+whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
+and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
+spatial clustering in determining groups. 
+In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
+and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
+of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
+whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
+The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}.
+They introduce a parameter $L$ to control the minimum length of each local consecutive segment.
 
@@
 
-\begin{table}
+\begin{table} \scriptsize
 \centering
@@
 \hline 
-Pattern & Clustering Method & Consecutiveness on Duration \\ 
+ & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
 \hline 
-Flock~\cite{gudmundsson2004flock} & Disk region &  Consecutive \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
 \hline 
-Convoy~\cite{jeung2008convoy} & Density &   Consecutive \\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
 \hline 
-Group~\cite{wang2006grouppattern} & Disk region &  Local consecutive $\geq L$ \\ 
+group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
 \hline 
-Swarm~\cite{li2010swarm} & Density  & No constraint \\ 
+swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
 \hline 
-Platoon~\cite{li2015platoon} & Density &  Local consecutive $\geq L$ \\ 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
 \hline 
 \end{tabular} 
-\caption{Existing Co-movement Patterns}
+\caption{Existing co-movement patterns.
+The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
 \label{tbl:existing_co_patterns}
@@
 %PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.45\textwidth]{related_work.eps}
+\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
+clusters of objects in each snapshots are denoted using dotted circles.}
+\label{fig:related_work}
+\end{figure}
 
-%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
-We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of five trajectories.
-First, the temporal domain is discretized into five snapshots. 
+%%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
+%UPDATE THE FIGURE TO CONTAIN SIX SNAPSHOTS. USE A NEW REPRESENTATION OF THE PATTERN. I DON'T LIKE $\{o_1,o_2\}\{1,2,3\}$. USE ONE PAIR OF $\{\}$ ONLY.
+
+We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
+The temporal dimension is discretized into six snapshots. 
 In each snapshot, the objects are clustered as shown in the dotted circle.
@@
 If further set $M=2,K=3$, two \emph{platoon} patterns are found.
-It is observable that the pattern $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e.
+It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e.
 $\{1\}$) is less than $2$.
-However, $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ can be reduced to $\langle\{O_5,O_6\}\{4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.
+However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.
 
@@
 4) PUT THE OBJECTS BELONGING TO THE SAME CLUSTER IN THE SAME LINE.
-
-\begin{figure} [h]
-\center
-\includegraphics[width=0.5\textwidth]{related_work.eps}
-\caption{Trajectories and Co-Movement Patterns}
-\label{fig:related_work}
-\end{figure}
 
@@
 As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type.
-Hence, there is an urgent demand for a general platform to support all these co-movement patterns.
-Another issue with existing methods is that they are built on top of centralized indexes that are not scalable.
-The maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories.
-In practice, it is rather common to collect millions of trajectories.
+Hence, there is a particular demand for a general platform to support all these co-movement patterns.
+The other issue with existing methods is that they are built on top of centralized indexes that are not scalable.
+To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories.
+In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown.
 We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}.
 The results show that their performance degrades dramatically as the dataset size scales up.
-None of them can handle millions of trajectories efficiently.
+In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity.
+For instance, the
+complexities of \emph{swarm} and \emph{platoon} are already exponential. 
+Therefore, none of them can handle millions of trajectories efficiently. 
+%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
 
@@
 We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem.
-This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
-connected.
-For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
-Such a pattern is likely to be induced by periodic movements of unrelated objects thus is of low interests.
+The \emph{loose connection} problem refers to the patterns that discovered 
+are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
+would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
+duration is $98$ timestamps apart, making the co-movement behavior very weak.
+%
+%
+%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
+%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
+In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
 To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$.
@@
 Meanwhile, the general co-movement pattern does not concede its expressiveness.
-As we show in later sections, the general co-movement pattern is able to reduce to existing patterns by setting appropriate parameters.
+As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters.
+%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
 
-Second, we propose a parallel solution based on Spark for scalable pattern mining. Our
+%
+\begin{figure}[h]
+\center
+\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
+\caption{Loosely connected pattern in platoon and swarm.
+The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
+\label{fig:platoon_weakpoint}
+\end{figure}
+
+Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
 solution is a three-step MapReduce alike approach. First, trajectories are partitioned
@@
 belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
-largely improve the system performance.
+largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
 
@@
 The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
-trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:solution} and Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.
+trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}.
+Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.

### 2016-05-05 sec3_definitions.tex
Stage 1
First Draft 0.1

--- 2016-05-01 definitions.tex
@@
 \label{sec:definition}
-Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern. 
-We use $T \subseteq \{1,2,...,m\}$ to denote a descritized sequence of timestamps, where
-$T[i]$ denotes the $i^{th}$ entry in the sequence and $|T|$ is the 
-cardinality of the sequence.
+Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =\{1,2,...,m\}$ be the descritized temporal dimension.
+A time sequence $T$ is defined as a subset of $\mathbb{T}$, i.e., $T \subseteq \mathbb{T}$, and we use $|T|$ to denote sequence length.
+Let $T_i$ be $i$-th entry in $T$ and we say $T$ is consecutive if $\forall 1\leq i\leq |T|-1$, $T_{i+1} = T_i + 1$.
+It is obvious that any time sequence $T$ can be decomposed into consecutive segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} if the length of all the consecutive segments is no smaller than $L$.
 
-A time sequence is consecutive if the difference between any of its neighboring entries
-is 1, that is $\forall T[i], T[i+1] \in T, T[i+1] = T[i] + 1$. For any time sequence,
-it can be decomposed into at least one consecutive portion(s). Therefore we can define the 
-$L$-consecutiveness as follows:
+To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
+
 %
@@
 
-\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
-A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
-has cardinality greater or equal to $L$.
-\end{definition}
-
-Take $T=\{1,2,3,5,6\}$ as an example.
-$T$ is not $3$-consecutive since $\{5,6\}$ has a cardinality less than $3$.
-$T$ is $2$-consecutive since both of its consecutive portions are of sizes at least $2$.
-To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows:
+%\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
+%A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
+%has cardinality greater or equal to $L$.
+%\end{definition}
 
@@
 
-Take $T=\{1,2,3,5,6\}$ as an example.
-$T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
-However, $T$ is not $1$-connected.
-Indeed, $1$-connection infers that $T$ is consecutive.
+We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$.
+$T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$.
+Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive.
+On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
+It is worth noting that $T$ is not $1$-connected because XXX.
 
-Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the
-closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
+%Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the closeness of their locations.
+Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
+Given a trajectory database descritized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity.
+Let $T$ be the set of timestamps in which a group of objects $O$ are clustered.
+We are ready to define a more general co-movement pattern:
 \begin{definition}[General Co-Movement Pattern]
-A \emph{General co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a time sequence $T$, with the following constraints: (1)Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$.
-(2) Significance: $|O| \geq M$.
-(3) Duration: $|T| \geq K$.
-(4) Consecutiveness: $T$ is $L$-consecutive, and (5)Connection: $T$ is $G$-connected.
+A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.
+
 %\begin{enumerate}
@@
 \end{definition}
+There are XXX parameters in our general co-movement pattern, including XXX.
+By customizing these parameters, our pattern can be reduced to the patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}.
+In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern.
+By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern.
+By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
+Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern.
+In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern.
+As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
+By setting appropriate $G$, we are able to prune this anomaly.
+It is notable that GCMP is not able to be modeled by existing patterns.
+AS MENTIONED IN WECHAT, POLISH THIS PART.
 
-The general co-movement pattern retains the patterns that discovered by all 
-existing techniques (group, flock, convoy, swarm and platoon). 
-The relationships between general co-movement pattern and other patterns are summarized in Table~\ref{tbl:patterns}.
+%The general co-movement pattern retains the patterns that discovered by all 
+%existing techniques (group, flock, convoy, swarm and platoon). 
+%The relationships between general co-movement pattern and other patterns are summarized 
 \begin{table}
@@
 
-In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern.
-By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern.
-By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
-Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern.
-In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern.
-As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
-By setting appropriate $G$, we are able to prune this anomaly.
-It is notable that GCMP is not able to be modeled by existing patterns.
-
 It is also observable that the number of patterns in GCMP is exponential. To control the size of output, 
@@
 
-LETS KEEP THE CLOSENESS INFORMATION AT THE MOMENT. IF NO CLOSENESS IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
+LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
 %For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.
@@
 Users are able to supply different clustering method to facilitate different needs.
-We currently expose both disk-region based clustering and DBSCAN as APIs to the user.
+We currently expose both disk-region based clustering and DBSCAN as options to the user.
 

### 2016-05-05 sec4_system.tex
Stage 1
First Draft 0.1

--- 2016-05-01 system.tex
@@
 We adapt the MapReduce paradigm for designing
-a parallel solution of mining GCMP. MapReduce was proposed by Dean et. cl.~\cite{}
+a parallel solution of mining GCMP. 
+MapReduce was proposed by Dean et. cl.~\cite{dean2008mapreduce}
 and has become a mature parallel platform for large-scaled data processing. 
 Current open source MapReduce systems provide handy programming APIs with fault tolerances
-in backends. Such systems 
-include Apache Hadoop, Apache Shark and Apache Spark to name a few.
+in backends. Such systems include Hadoop, Shark and Spark to name a few.
 
-In simple words, there are two types of cluster nodes in MapReduce, namely the 
-\emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
+In simple words, there are two types of computing nodes in MapReduce,
+namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
 three stages: First, input data
@@
 Since the \emph{shuffle} stage needs to transfer data over network, 
-an important attention to pay during designing MapReduce algorithms is 
+an important attention to pay during designing MapReduce an algorithm is 
 to minimize the shuffle amounts and shuffle counts.
 
-Our GCMP mining workflow follows the MapReduce style which consists of five stages
-as illustrated in the Figures~\ref{fig:overview} (a)-(e).
-As shown, in stage (a), trajectory data 
-are read from various sources and partitioned based on objects timestamps, where objects
-of the same timestamps form a snapshots. After partitioning, snapshots are send to workers
-prior to stage (b). In stage (b), objects belonging to the same snapshots are clustered
-based on the user supplied clustering method. Then those clusters are shuffled to 
-workers prior to stage (c). In stage (c), each worker collects the clusters sent to its partition
-and discover the GCMP from these local clusters. A post-check is required to remove
-duplicate patterns. In stage (d), patterns discovered in previous stages are write to output.
+Our GCMP mining framework consists of two MapReduce jobs which
+are constituted of four MapReduce stages as illlustrated in Figure~\ref{fig:overview}.
+The first MapReduce job corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
+of the first job is to cluster trajectories based on snapshots (i.e., computing $\forall t, o, C_t(o)$).
+As illustrated in (a), input trajectories are read in by mappers 
+and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
+form a snapshot. Then, a user defined clustering method is applied on the objects
+in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. The second
+MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
+of the second job is to mine the GCMP from the snapshots computed in the first job. We design
+two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
+are first fed to mappers and different partition strategies may be selected to create
+partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
+The final computed results are then outputted to the end users. Although we need two MapReduce
+jobs for a complete GCMP mining framework, we may pipeline the two jobs to exploit the data locality.
+Specifically, the reducer output at step (b) can be directly reused as the input to mappers at step (c). Therefore
+we do not need to transfer data from step (b) to step (c). Modern MapReduce platforms, especially Spark, have
+already supported such a kind of pipeline.
 
@@
 \includegraphics[width=0.5\textwidth]{system_layout.eps}
-\caption{System Flow of Mining GCMP}
+\caption{System flow of mining GCMP}
 \label{fig:overview}
@@
 
-The first two stages of our solution could be straightforward. 
-However, it is challenging to design the partition and mining methods
-to in stage (c) and (d). Intuitively, A reasonable partition strategy 
-needs to meet the following requirements: first, the result partitions need
-to preserve enough information so that real patterns can be discovered
-in stage (d). Second, the result partitions need to ensure that
-the patterns that discovered in stage (d) are real patterns so that
-no further validation is required after stage (d). We formalize the two 
-properties using \emph{completeness} and \emph{soundness} as follows:
+The first MapReduce job to compute clusters in each snapshot
+is easy to work in parallel. This is because a clustering method only needs
+to access data within in a snapshot. 
+In contrast, it is challenging
+to design a partition-and-mining methods for the second job. This is because
+valid patterns may spray across multiple snapshots, where inappropraite partition
+may fail to discover some valid patterns.
+Formally, a reasonable partition strategy 
+needs to meet the following requirements: first, the resulted partitions need
+to preserve enough information so that real patterns can be discovered in the reduce phase. 
+Second, the resulted partitions need to ensure that
+the patterns discovered in the reduce phase are real patterns so that
+no further validation is required. We formalize the two 
+properties as \emph{completeness} and \emph{soundness} as follows:
 
@@
 \end{definition}
-The completeness ensures that no real patterns are missed out.
-The soundness ensures that no false patterns are reported.
-If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel in stage (d).
+The completeness ensures that no true patterns are missed out. The soundness ensures that no false patterns are reported. 
+If a partition method is both sound and complete, we are then able to design a MapReduce algorithm to facilitate the second job
+of our framework.
 
-Apparently replicating entire data set to each partition meets the \emph{soundness} and \emph{completeness}, however, it burdens the network shuffle and GCMP mining.
-Our objective is thus to design a complete and sound partition method that
-minimize the network shuffles.
+Apparently, replicating the entire trajectories to each 
+partition meets the \emph{soundness} and \emph{completeness}. However, 
+it burdens the network shuffle and limits the parallelism. 
+Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
+In the following sections, we first present a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining.
+Then,
+we further present a novel \emph{object-based} partition-and-mining method
+called \emph{Star Partition and Mining} (SPM) which resolves
+the deficiency of TRM method.
 
@@
 Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.
-
-\section{Temporal Replication and Mining}
-The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
-A simple but effective method
-is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
-some of the snapshots need to be replicated on multiple executors.
-We call this method the \emph{Temporal Replication and Mining} approach. 
-The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.
-
-\begin{algorithm}
-\caption{Temporal Replication and Mining}
-\label{algo:trm_overview}
-\begin{algorithmic}
-\Require list of $\langle t, S_t \rangle$ pairs
-\State {Map Phase}
-\ForAll{$\langle t, S_t \rangle$}
-	\ForAll{$i \in 1...(K-1)*G+K$}
-		\State emit a $\langle t-i, S_t \rangle$ pair
-	\EndFor 
-\EndFor
-\State {Shuffle Phase}
-\ForAll{$\langle t, S \rangle$ pair} 
-\State group-by $t$, emit a $\langle t, Par_t\rangle$,
-\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(K-1)*G+K}\} $
-\EndFor
-\State {Reduce Phase}
-\ForAll{$\langle t,Par_t \rangle$}
-\State minePattern($Par_t$)
-\EndFor
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Temporal Replication Partition}
-In order to reduce the shuffling cost, the data to be replicated should be
-kept to a minimum. However, as suggested in the following theorem, the minimum replication of a snapshot is not small:
-
-\begin{theorem}[Soundness and Completeness of Replication]
-\label{thm:replication_partition}
-For each snapshot $S_t$, a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K)}\}$ 
-is created. Such a partition method is sound and complete.
-\end{theorem}
-\begin{proof}
-The soundness of partition is trivially true by definition.
-Given a valid pattern $P$, let $T' \subseteq P.T$ be a subsequence of $P.T$ which conforms to $K,L,G$. Note that there could be many qualified $T'$ of $T$. Then, 
-let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$.
-Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$.
-Since $T'$ conforms to $K,L,G$, then $\Sigma_i (l_i) \geq K$, and $K \geq l_i \geq L$, $g_i \leq G$.
-Therefore, among all possible $T'$s, the minimum size is $\lfloor \frac{K}{L}-1\rfloor *G+K$.
-Thus ensuring each $Par_t$ to be of that size would capture one of the $T'$s, therefore the pattern $P$ is valid in $Par_t$.
-This proves the completeness of the partitioning method.
-\end{proof}
-
-Utilizing Theorem~\ref{thm:replication_partition}, we create, for each snapshot $S_t$, 
-a partition containing its next $\lfloor \frac{K}{L}-1\rfloor *G+K$ snapshots. Each partition is then
-sent to the executors as a task. Since any global pattern must exists in one of the partitions, we can mine the patterns from each partitions independently, without loss of patterns.
-
-\subsubsection{Temporal Replication Mining}
-After replication, each task in Spark will process an partition $Par_i$. The next
-step is to mine the GCMPs from $Par_i$. We notice that, for each 
-partition, we only need to find the patterns that
-are contained in the first snapshots. Therefore we design a line-sweep method for mining 
-such patterns, which is the variant of the Coherent-Moving-Clustering method in~\cite{jeung2008convoy}.
-
-The Temporal Replication and Mining approach though achieves parallelism from independent
-partitions, it requires to replicate the data multiple times. 
-Specifically, each snapshots are copied $(K-1)*G+K$ times. In swarm
-case, $G$ is as large as $|\mathbb{T}|$. In such a case, it is equivalent to replicate the entire dataset 
-to each executor, which is clearly inefficient.
-
-\subsection{Star Partition and Mining}
-To develop a method that achieves parallelism under any pattern parameters, 
-we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
-we design a novel object-based partition method named star partition.
-A start partition partitions trajectories in the object domain rather than temporal domain.
-After partitioning, we design the \emph{Apriori}-like
-method to mine the patterns out of each partition independently. 
-The overview of the star partition and mining is as in Algorithm~\ref{algo:spm_overview}.
-
-\begin{algorithm}
-\caption{Star Partition and Mining}
-\label{algo:spm_overview}
-\begin{algorithmic}
-\Require list of $\langle t, S_t \rangle$ pairs
-\State {Map phase}
-\ForAll{$C \in S_t$}
-	\ForAll {$(o_1 ,o_2) \in C \times C$}
-		\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
-	\EndFor
-\EndFor
-
-\State {Shuffle phase}
-\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
-	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
-	\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
-\EndFor
-
-\State {Reduce phase}
-\ForAll{$\langle o, Sr_{o} \rangle$}
-\State Apriori($Sr_o$)
-\EndFor
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Star Partition}
-The purpose of star partition is to find the group of objects that 
-could potentially form a pattern. In order to achieve parallelism, 
-we group, for each object $o$, all other objects that connect to $o$ in some snapshots. By so doing, the patterns containing $o$ can be discovered within each groups. 
-Technically, we create a connection graph to represent the
-connectivity among objects. A connection graph is an undirected graph $G=(V:E)$, where 
-each $v \in V$ represents an object. An edge $e(s,t)= ET$ 
-contains all the timestamps where $s,t$ are in the same cluster,
-i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
-Given a vertex $s$, the star of $s$, $Sr_s$ is the set of incidental edges of $s$ in $G$. An example of star partition is shown in Figure~\ref{fig:star_partition}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\textwidth]{star_partition.jpg}
-\caption{Example of Star Partition}
-\label{fig:star_partition}
-\end{figure}
-
-In star partition, trajectories are partitioned based on objects and their stars. Then
-each partition is send to an executor as a task. 
-Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories.
-This is done by treating each vertex in $Sr_s$ as an object.
-For $s$, the time sequence is the union of all edges in $Sr_s$.
-For vertex $v \neq s$, the time sequence is the edge $(s,v)$.
-Then, we state the completeness of star-partition as in the following theorem:
-\begin{theorem}[Soundness and Completeness of Star Partition]
-Star partition is sound and complete.
-\end{theorem}
-
-\begin{proof}
-For the soundness,
-if $P$ is a valid pattern in $Sr_s$, then for every object $v\neq s, v \in P.O$, and for every timestamp $t\in P.T$, $C_t(v) = C_t(s)$.
-This means, for every snapshot $t$, all object in $P.O$ belongs to the same cluster.
-Thus, $P$ is a valid pattern in original trajectories.
-
-For the completeness,
-if $P$ is a valid pattern in original trajectories, for an arbitrary object $s \in P.O$, it follows $P.O \equiv S_r$.
-Since for any time $t$, $C_s(t) = C_v(t) \forall v \in P.O$, every time in $P.T$ appears in edges in $Sr_s$, thus $P$ is valid pattern in $Sr_s$.
-\end{proof}
-
-Based on the above theorem, each star can be processed independently by executors, which avoids the inter-executor communication during the mining phase. It is notable that, the 
-replication of data is $O(|\mathbb{O}|^2|\mathbb{T}|)$, which is free from the parameters of patterns.
-In later sections, we will describe optimization techniques to reduce the replications.
-
-\subsubsection{Apriori Mining}
-For each task, in the mining phase, we need to find the patterns that conform to the parameters. To systematically discover the patterns, we design the \emph{Apriori Mining} method which
-is similar to frequent item mining. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $|R|$. 
-Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
-for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
-we generate $(R+1)$-cluster patterns by joining $R$-cluster patterns with $2$-cluster patterns. Specifically,
-the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
-Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-cluster at most to a $(R+1)$-cluster.
-Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
-
-\begin{algorithm}
-\caption{Apriori Mining}
-\label{algo:apriori_mining}
-\begin{algorithmic}
-\Require{$Sr_s$}
-\State { Lv $\gets \{\}$}
-\State { Ground $\gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State Ground.add($\langle \{s,t\}, T \rangle$);
-\State Lv $\gets$ Ground;
-\EndFor
-\While{true}
-	\If{Lv is not empty} 
-		\State{LvCand $\gets \{\}$ }
-		\ForAll{$cand_v \in Lv$}
-			\ForAll{$cand \in $Ground}
-				\State $p \gets cand_v$ join $cand$
-				\If{$p.T$ is partly valid} 
-					\State LvCand.add($p$)
-				\EndIf
-			\EndFor
-		\EndFor
-		\State {Lv $\gets$ LvCand}
-	\Else
-		\State{break}
-	\EndIf
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-
-Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
-are two major factors dragging the performance. First, the size of $Sr_s$ affects
-the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
-sections, we exploit the property of GCMP to reduce the two factors.

### 2016-05-05 sec5_baseline.tex
Stage 1
First Draft 0.1

\section{Temporal Replication and Mining}
\label{sec:trm_solution}
The \emph{temporal-based} method of mining GCMP follows the solution framework 
as in Figure~\ref{fig:overview}. The idea of the \emph{temporal-based} method 
is to group temporally closed snapshots together, such that patterns can be
mined on each group of the snapshot.
In order to achieve the \emph{completeness}
and \emph{soundness} during partitioning, we design a \emph{Temporal Replication
and Mining} (TRM) algorithm as shown in Algorithm~\ref{algo:trm_overview}.

%%The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
%A simple but effective method
%is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
%some of the snapshots need to be replicated on multiple executors.
%We call this method the \emph{Temporal Replication and Mining} approach. 
%The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...(K-1)*G+K$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor 
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$,
\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(\lfloor \frac{K}{L} \rfloor -1)*G+K+L}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the \emph{Temporal Replication and Mining} (TRM) algorithm takes
three steps. First, in map phase, each snapshots is keyed with is timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is determined. Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.

\subsubsection{Temporal Replication Partition}
The size of replication is critical for the performance of TRM algorithm.
If the size of replication is too large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if the size of replication is too small, the \emph{completeness} and \emph{soundness}
properties cannot be satisfied. In the Algorithm~\ref{algo:trm_overview}, 
the partition size is chosen as $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$. As stated in the following
theorem, such a partition method is sound and complete.
\begin{theorem}[Soundness and Completeness of Replication]
\label{thm:replication_partition}
Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K + L )}\}$. Then $\mathbb{P}$ is sound and complete.
\end{theorem}
\begin{proof}
The soundness of partition is trivial.
Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
Since $T'$ conforms to $K,L,G$, then $K+L \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq \lfloor \frac{K}{L}-1\rfloor *G+K+L$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would valid in $Par_t$. This proves the completeness of the partitioning method.
\end{proof}

\subsubsection{Line Sweep Mining}
After partition, each task in the reduce phase processes a partition $Par_i$, which contains
$\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ snapshots starting from snapshot $S_i$. With such a 
partition method, we observe that within $Par_i$, only the 
patterns whose object sets are contained in the first snapshot are necessary to be reported.
Therefore, we design a simple \emph{line-sweep mining}(LSM) method for discover
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

\begin{algorithm}
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $Par_t = \{S_t, S_{t+1}, ...\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\For{$c \in S_t$} 
\label{code:ls-init-start}
\State $C$.add($\langle c, t \rangle $)
\EndFor
\label{code:ls-init-end}
\For{$i=1; i < |Par_t|;i++$}
\State $N \gets S_i \oplus C$ \label{code:ls-join}
	\ForAll {$n \in N$}
		\If{$|n.O| \geq M$}
			$C$.add($n$).
			\label{code:ls-add}
		\EndIf
	\EndFor
\State{remove unqualified candidate from $C$}
	\label{code:ls-remove}
\EndFor
\State{output qualified candidate in $C$}
\end{algorithmic}
\end{algorithm}

The algorithm scans the snapshots in a partition in the sequential order.During the scan it
maintains a candidate set $C$ which could potentially be a valid pattern (line~\ref{code:ls-can-set}).
The algorithm starts by inserting clusters at $S_1$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
a new set of patterns $N$(lines~\ref{code:ls-join}). Any valid new patterns are inserted back to $C$
and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{trm_process.eps}
\caption{Work flow of trajectory replication and mining}
\label{fig:trm_process}
\end{figure}

\begin{example}
We illustrate the process of \emph{Trajectory Replication and Mining} in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
for each partition, which equals to $\lfloor \frac{K}{L}-1 \rfloor *G+K+L = 4$. Therefore, in (b), every four snapshots
are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
$C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1,2\}$ which is neither
a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
sweep finishes, only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

### 2016-05-05 sec6_spm.tex
Stage 1
First Draft 0.1

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to develop a method that achieves good parallelism under any pattern parameters, 
we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we design an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a 3-uple(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, 3-uples with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

\begin{algorithm}
\caption{Star Partition and Mining}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
		\EndIf
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Partition and Shuffle phase---}
\label{code:spm-shuffle-start}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
\EndFor
\label{code:spm-shuffle-end}

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State Apriori($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

\end{algorithmic}
\end{algorithm}

\subsubsection{Star Partition}
The intuition of star partition is that, if two objects are part of
the same pattern, then at some snapshots, they must belong to the same 
cluster. Therefore, we may link objects that belong to the same cluster
at some snapshots to form a \emph{connection graph}. Objects that are
not connected surely do not belong to a pattern. We may further
partition the connection graph so that mining proper patterns can be
done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

It is notable that we require vertices in a star to be greater than its central vertex. This 
effectively avoids replicating edges. \emph{Connection graph} and \emph{star} examples are 
shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
based on the example in Figure~\ref{fig:related_work}.
In (b), 5 stars are presented. It is easy to see that, by requiring the center vertex to be
the smallest vertex in a star, there are no edges been replicated. In implementation,
as stated in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
comparison between vertices/objects are based on the vertex/object ID.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{spm.eps}
\caption{Star partition and mining of trajectories in Figure~\ref{fig:related_work}}
\label{fig:star_partition}
\end{figure}

%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.
Although star partition is performed based on the object connections, each star
can be effectively viewed as a subset of trajectories. To see this, each vertex
in a star can be viewed as an object. The timestamps of center vertex $s$ is the
union of all the edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
edge $e(s,v)$. Therefore, we are able to define and mine GCMP on the stars. 
Before describing the mining strategy, we first state in the following theorem that 
the star-partition is complete and sound:
\begin{theorem}[Soundness and Completeness of Star Partition]
Star partition is sound and complete.
\end{theorem}

\begin{proof}
For the soundness,
if $P$ is a valid pattern in $Sr_s$, then at every time $t$, $\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
By definition, $P$ is valid in the original trajectories.
For the completeness,
if $P$ is a valid pattern in original trajectories, let $s$ be the object with smallest ID in $P.O$. 
Then by the definition of pattern, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
\end{proof}

Based on the above theorem, we can mine GCMP from each partition independently.
It is notable that, in star partition, original data is replicated for $O(\mathbb{O})$ times
as each object may be sent to $O(\mathbb{O})$ partitions. Since this complexity is free
from pattern parameters, the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.

\subsubsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$}
\State { Ground $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Ground.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Ground;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in $Ground}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is partly valid} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
higher level candidates are generated by joining lower level candidates. When no more candidates 
can be generated, the algorithm stops by outputting the valid patterns.

It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
are two major factors dragging down the performance. First, the size of $Sr_s$ affects
the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
sections, we exploit the property of GCMP to reduce the two factors.

### 2016-05-05 sec7_optimization.tex
Stage 1
First Draft 0.1

\section{Optimization}
\label{sec:optimization}
In this section, we describe several optimizations to the star-partition and mining algorithm.
In addition, we also address some practical issues when deploying the SPM algorithm
to real MapReduce based systems.

%We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
%lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
%In this section, we provide several optimizations to boost the bottlenecks.
%\subsection{Edge Reduction by Direction}
%The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning. 
%
%We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
%for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.
%
%\begin{theorem}[Sound and Completeness of Edge Direction]
%Star partition with edge direction is sound and complete.
%\end{theorem}
%\begin{proof}
%It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
%\end{proof}
%An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
%by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

\subsection{Edge Simplification}
Each edge $e(s,v)$ in $Sr_s$ contains a time sequence $ET$ 
which represents the co-occurrence of $s$ and $v$. We notice that the edge 
between $s$ and $t$ is not always necessary. For example, if an edge has a
cardinality less than $K$, it is unnecessary to include this edge to 
$Sr_s$ since it cannot contribute to any patterns.
This motivates us to simplify the edges in $Sr_s$ 
to boost the overall performance.

Our goal of edge simplification is to, given a time sequence $T$, find a subsequence
of $T' \subseteq T$, such that $T'$ is potentially conforms to $K,L,G$. And we
wish $|T'|$ to be as small as possible.  
We star-off by observing that for every time sequence $T$, $T$ can be 
divided into a set of maximally $G$-connected subsequences. Note that
a maximally $G$-connected subsequence can potentially contribute to
a pattern if it conforms to $K,L$.
Therefore, we are able to reduce $T$
to its maximally $G$-connected subseuqnces which conform to $K,L$.

To formally describe the idea, we define the a \emph{candidate sequence} as follows:

%\begin{definition}[Candidate Sequence]
%Given the pattern parameters: $K,L,G$, a sequence $T$ is 
%a \emph{partly candidate} sequence if exists one of its maximal $G$-connected
%subsequence $T'$ such that $T'$ confirms to $L,K$.
%\end{definition}

%For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11)$ 
%is a \emph{partly candidate sequence} since $T_1[1:5] = (1,2,4,5,6)$ is a valid
%pattern wrt. $L,K,G$. In contrast, $T_2=(1,2,5,6,7)$ is not a valid partly candidate sequence.
%
%Observing that only partly candidate sequence can be potentially contribute to a 
%pattern. Therefore, given an edge $e(s,t)=T \in Sr_s$, if $T$ is not a partly
%candidate sequence, it can be pruned from $Sr_s$. To efficiently
%test whether a given sequence is partly candidate, we define the \emph{Fully Candidate Sequence}:

\begin{definition}[Candidate Sequence]
Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$.
\end{definition}

For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
not a fully candidate sequence since one of its maximal $G$-connected sequence $(9,10,11)$
is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
a fully candidate sequence.

To reduce a sequence $T$ to a candidate sequence, we need to strip out its 
maximal $G$-connected subsequences which does not form to $K,L$. Such a reduction
takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. In the 
first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are
removed. Clearly the simplification algorithm runs in $O(|T|)$ time.
\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---Remove the consecutive portion with size less than $L$---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] != 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---Remove the pseduo-consecutive portion with size less than $K$---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{example}
Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
is removed by $L=2$. $T_1$ has two maximal $G$-consecutive subsequences, which 
are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$.
\end{example}

%
%Based on the fully candidate sequence, we can reduce an sequence $T$ to a 
%fully candidate sequence by striping out its non-partly candidate maximal pseudo-consecutive 
%sequences. The reduction works as in Algorithm~\ref{algo:simp_prune}. It takes two
%rounds of scan of an input $T$. In the first round of scan,
%the consecutive portion of $T$ with size less than $L$ is removed.
%In the second round of scan, the pseudo-consecutive portion of $T$ with size less than $K$
%is removed.

By leveraging the edge simplification technique, 
the size of the edges in $Sr_s$ can be greatly reduced. If
an edge cannot be reduced to a candidate sequence, then it is directly removed from $Sr_s$.
If an edge can be reduced to a candidate sequence, replacing itself 
by the candidate sequence results in a more compact storage.

%We use the following theorem to state the completeness and correctness of the 
%edge reduction algorithm.
%\begin{theorem}[Soundness and Completeness Edge Simplification]
%Star partition with edge simplification is sound and complete.
%\end{theorem}
%
%\begin{proof}
%Soundness of the star partition is not affected by edge simplification since each star is a subset of original trajectory. For completeness, notice that given a time sequence $T$, and any of its maximal $G$-connected subsequence $T'$, if $T'$ does not conform to $L,K$, then $T'$ cannot contribute to any patterns. 
%\end{proof}

\subsection{Candidate Pruning via Temporal Monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

The intuition is that if a candidate $P_1.T$ cannot be reduce to a \emph{candidate sequence}, then $P_1$ cannot 
be valid pattern. Furthermore, any candidate $P_2$, with $P_1.O \subset P_2.O$ cannot be a valid pattern.
This \emph{temporal monotonic property} 
is explicitly described as in the follow theorem:

\begin{theorem}[Temporal Monotonic Property of GCMP]
Given the temporal parameters $L,G,K$, for a candidate $c$ in Algorithm~\ref{algo:apriori_mining},
if $c.T$ cannot be reduced to a candidate sequence, then for any candidate $c'$ with $c.O \subset c'.O$, $c'$ can be pruned.
\end{theorem}
\begin{proof}
Let $c_1$, $c_2$ be two candidates with $c_1.O \subset c_2.O$. It is easy to see that $c_1.T \supseteq c_2.T$.
If $c_1.T$ cannot be reduced to a candidate sequence, then any subset of $c_1.T$ cannot
be reduced. It follows that $c_2.T$ cannot be reduced neither. Thus,
if $c_1.T$ cannot be reduced to a candidate sequence, $c_2$ can be pruned. 
\end{proof}

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning. As shown, at the initial stage, $\{3,6\}\{1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence. By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned. Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
\end{example}
%
%With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
\subsection{Load Balancing}

\subsection{Duplication Detection}

### 2016-05-07 sec1_introduction_bk.tex
Some modifications
Need revise sec 1 and 3

--- 2016-05-05 sec1_introduction.tex
@@
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
+group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
 \hline 
-swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
+swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
@@
 \caption{Existing co-movement patterns.
-The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
+The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the total number of timestamps.}
 \label{tbl:existing_co_patterns}
@@
 We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}.
-The results show that their performance degrades dramatically as the dataset size scales up.
+The results show that their performances degrade dramatically as the dataset size scales up.
 In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity.
@@
 
-Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
-solution is a three-step MapReduce alike approach. First, trajectories are partitioned
-into snapshots where clusters from each snapshots are formed in parallel. Second, 
-clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
-are mined from each group. The challenge here is to ensure that
-the patterns mined at step three is complete. If not, further shuffles and computations are required which 
-significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
-shuffle amount at each stage to a minimum, 
-we design a novel star-based partition scheme to efficiently partition objects based on their
-belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
-largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
+Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
+The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
+In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
+of the partitions. Such properties ensure that neither false-patterns 
+nor miss-patterns are possible in our solution. To meet such partition requirements
+as well as to keep the shuffle amount to a minimum,
+% 
+%%Second, we propose a . Our
+%%solution is a three-step MapReduce alike approach. First, trajectories are partitioned
+%%into snapshots where clusters from each snapshots are formed in parallel. Second, 
+%%clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
+%%are mined from each group. 
+%
+%The challenge here is to ensure that
+%the patterns mined at step three is complete. If not, further shuffles and computations are required which 
+%significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
+%shuffle amount at each stage to a minimum, 
+we first design a naive \emph{Temporal Replication and Mining} (TRM)
+approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
+method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
+Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
+as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
+a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
+GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$.
+Moreover, we utilize \emph{temporal monotonicity} in GCMP to further reduce the shuffling and mining cost in SPM.
+Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in
+Apache Spark which is one of the most popular MapReduce platforms.
+
+%we design a novel star-based partition scheme to efficiently partition objects based on their
+%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
+%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
 

### 2016-05-07 sec3_definitions.tex
Some modifications
Need revise sec 1 and 3

@@
 
-To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
-
+As illustrate in Figure~\ref{fig:platoon_weakpoint}, patterns adapting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from \emph{loose connection} problem. 
+To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
+timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:
+%To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
 %
@@
 A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
- $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$.
+ $\forall T_i,T_{i+1} \in T, T_{i+1}-T_{i} \leq G$.
 \end{definition}
@@
 On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
-It is worth noting that $T$ is not $1$-connected because XXX.
+It is worth noting that $T$ is not $1$-connected because the gap between $T_3$ and $T_4$ is 2 (i.e., 5-3=2).
 
@@
 \end{definition}
-There are XXX parameters in our general co-movement pattern, including XXX.
-By customizing these parameters, our pattern can be reduced to the patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}.
+There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. By customizing these parameters, our pattern can 
+express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
 In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern.
@@
 Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern.
-In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern.
-As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
+In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
+%In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. 
+%
+%As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
 By setting appropriate $G$, we are able to prune this anomaly.
-It is notable that GCMP is not able to be modeled by existing patterns.
-AS MENTIONED IN WECHAT, POLISH THIS PART.
+It is notable that GCMP cannot be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.
 
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|c|}
 \hline 
-Pattern & $L$ & $G$ & $M$ & $K$ \\ 
+Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
 \hline
-Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
+Group & $2$ & $1$ & $2$ & $|T|$ & Disk-based\\
 \hline
-Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
+Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
 \hline 
-Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
+Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
 \hline 
-Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
+Swarm & $\cdot$ & $\cdot$ & $1$ & $|T|$ & Density-based \\ 
 \hline 
-Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
+Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|T|$ & Density-based\\ 
 \hline 
 \end{tabular} 
-\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
+\caption{Expressing other patterns using GCMP. $\cdot$ indicate a user specified value. $M$ represents the 
+object \emph{size} constraints. $K$ represents \emph{duration} constraint. $L$ represents \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraints.}
 \label{tbl:patterns}
@@
 
-It is also observable that the number of patterns in GCMP is exponential. To control the size of output, 
+It is also observable that the number of patterns in GCMP is exponential. To reduce the size of output, 
 we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
@@
 \begin{definition}[Closed General Co-Movement Pattern]
-A general co-moving pattern $P=\langle O, T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
+A general co-moving pattern $P=\langle O:T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
 \end{definition}
 
-For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern.
+For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
+the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern.
+This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern and $P_2.O \supset P_1.O$.
 The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
@@
 Therefore in this paper, we mainly consider density-based clustering.
-Our definition of GCMP is free from clustering method.
-Users are able to supply different clustering method to facilitate different needs.
+Our definition of GCMP is free from clustering method. Users are able to supply different clustering methods to facilitate different application needs. 
 We currently expose both disk-region based clustering and DBSCAN as options to the user.
@@
 \centering
-\begin{tabular}{|c|c|} 
+\begin{tabular}{|c|l|} 
 \hline
@@
 $\mathbb{O}$ & Set of objects \\ 
+\hline 
+$K$ & Duration constraint\\
+\hline
+$M$ & Object size constraint \\
+\hline
+$L$ & Consecutiveness constraint\\
+\hline
+$G$ & Connection constraint \\
 \hline

### 2016-05-07 sec4_system.tex
Some modifications
Need revise sec 1 and 3

@@
 We adapt the MapReduce paradigm for designing
-a parallel solution of mining GCMP. 
-MapReduce was proposed by Dean et. cl.~\cite{dean2008mapreduce}
-and has become a mature parallel platform for large-scaled data processing. 
-Current open source MapReduce systems provide handy programming APIs with fault tolerances
-in backends. Such systems include Hadoop, Shark and Spark to name a few.
+a parallel solution of mining GCMP. In this section,
+we briefly cover the preliminary on MapReduce and then describe
+the overview of our framework in mining GCMP.
 
-In simple words, there are two types of computing nodes in MapReduce,
-namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
-three stages: First, input data
+\subsection{Preliminary on MapReduce}
+MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
+and has subsequently implemented by many open source systems. Those systems
+provide handy APIs with fualt tolerances and are popularly
+used as large-scale data processing platforms. 
+% become a ubiquitous parallel platform for large-scaled data processing. 
+%Current open source MapReduce systems provide handy programming APIs with fault tolerances
+%in backends. Such systems include Hadoop, Shark and Spark to name a few.
+In simple words, there are two conceptual types of computing nodes in MR,
+namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
+algorithm consists of three stages: First, input data
 are partitioned and read by a \emph{map} function on each mapper. Then, mappers
@@
 outputs.
-Since the \emph{shuffle} stage needs to transfer data over network, 
-an important attention to pay during designing MapReduce an algorithm is 
-to minimize the shuffle amounts and shuffle counts.
 
-Our GCMP mining framework consists of two MapReduce jobs which
-are constituted of four MapReduce stages as illlustrated in Figure~\ref{fig:overview}.
-The first MapReduce job corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
-of the first job is to cluster trajectories based on snapshots (i.e., computing $\forall t, o, C_t(o)$).
-As illustrated in (a), input trajectories are read in by mappers 
-and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
-form a snapshot. Then, a user defined clustering method is applied on the objects
-in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. The second
-MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
-of the second job is to mine the GCMP from the snapshots computed in the first job. We design
-two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
-are first fed to mappers and different partition strategies may be selected to create
-partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
-The final computed results are then outputted to the end users. Although we need two MapReduce
-jobs for a complete GCMP mining framework, we may pipeline the two jobs to exploit the data locality.
-Specifically, the reducer output at step (b) can be directly reused as the input to mappers at step (c). Therefore
-we do not need to transfer data from step (b) to step (c). Modern MapReduce platforms, especially Spark, have
+Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
+First, since it requires reducers to be independent, partitioning  
+data to fit the independence could be challenging. Second, since the \emph{shuffle}
+stage requires network access, the data been shuffled should be minimized. 
+We take these concerns in consideration in designing our solutions for mining GCMP.
+%We would bare this concerns in designing our GCMP mining algorithm.
+%a natural
+%problem is how to partition the data in map and shuffle phase so that reducers 
+%achieve the independence.
+%
+%A critical question in designing a MapReduce algorithm is how to make 
+%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
+%requires data processed at each reducer to be independent.
+%
+%Since the \emph{shuffle} stage needs to transfer data over network, 
+%an important attention to pay during designing MapReduce an algorithm is 
+%to minimize the shuffle amounts and shuffle counts.
+
+\subsection{MapReduce Processing for Mining GCMP}
+Our GCMP mining process consists of two MR jobs. The two jobs
+contains four MR stages as illustrated in Figure~\ref{fig:overview}.
+The first MR job is to cluster objects at each snapshot (i.e.,
+computing $\forall t, o, C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
+trajectories are first reorganized by timestamps in map phase and object locations
+at the same timestamps form a cluster. The clustering takes place in reduce phase, where
+each snapshot is processed independently. The second MR job is to mine GCMPs from 
+clusters at each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
+the purpose of comparison. Both the two algorithms would partition snapshots in map phase
+(as in Figure~\ref{fig:overview}(c))
+and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).
+
+% corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
+%of the first job is to cluster trajectories based on snapshots (i.e.,).
+%As illustrated in (a), input trajectories are read in by mappers 
+%and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
+%form a snapshot. Then, a user defined clustering method is applied on the objects
+%in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. 
+%The second
+%MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
+%of the second job is to mine the GCMP from the snapshots computed in the first job. We design
+%two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
+%are first fed to mappers and different partition strategies may be selected to create
+%partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
+%The final computed results are then outputted to the end users.
+
+Although we need two MR jobs to complete the GCMP mining task, 
+it is easy to pipeline the two jobs to exploit data locality.
+Specifically, the reducer output at step (b) can be directly reused 
+as the input to mappers at step (c). Therefore we do not need to 
+transfer data from (b) to (c). Modern MR platforms, especially Spark, have
 already supported such a kind of pipeline.
@@
 \includegraphics[width=0.5\textwidth]{system_layout.eps}
-\caption{System flow of mining GCMP}
+\caption{System flow of mining GCMP. (a)(b) correspond to the first MR job which compute the clusters at each snapshot; 
+(c)(d) correspond to the second MR jobs which mines GCMP in parrallel.}
 \label{fig:overview}
@@
 
-The first MapReduce job to compute clusters in each snapshot
-is easy to work in parallel. This is because a clustering method only needs
-to access data within in a snapshot. 
-In contrast, it is challenging
-to design a partition-and-mining methods for the second job. This is because
-valid patterns may spray across multiple snapshots, where inappropraite partition
-may fail to discover some valid patterns.
+We note that the first MR job is easy to design since each reducer only
+needs one snapshot for clustering.
+In contrast, it is challenging to design the second job. 
+This is because valid patterns may spray across multiple snapshots, where inappropriate partitioning
+of snapshots may fail to discover certain valid patterns.
 Formally, a reasonable partition strategy 
-needs to meet the following requirements: first, the resulted partitions need
+needs to meet the following requirements: (a) the resulted partitions need
 to preserve enough information so that real patterns can be discovered in the reduce phase. 
-Second, the resulted partitions need to ensure that
-the patterns discovered in the reduce phase are real patterns so that
-no further validation is required. We formalize the two 
+(b) the resulted partitions need to ensure that
+the patterns discovered in the reduce phase are valid patterns so that
+no further verification is required. We formalize the two 
 properties as \emph{completeness} and \emph{soundness} as follows:
@@
 \end{definition}
-The completeness ensures that no true patterns are missed out. The soundness ensures that no false patterns are reported. 
-If a partition method is both sound and complete, we are then able to design a MapReduce algorithm to facilitate the second job
-of our framework.
+The completeness ensures that no true patterns are missed out. 
+The soundness ensures that no false patterns are reported. 
+If a partition method is both sound and complete, then it can be used
+in the second MR job to facilitate GCMP mining.
 
 Apparently, replicating the entire trajectories to each 
-partition meets the \emph{soundness} and \emph{completeness}. However, 
-it burdens the network shuffle and limits the parallelism. 
+partition meets the \emph{soundness} and \emph{completeness} requirements. 
+However, it burdens the network shuffle and limits the parallelism. 
 Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
-In the following sections, we first present a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining.
-Then,
-we further present a novel \emph{object-based} partition-and-mining method
+In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
+we present a novel \emph{object-based} partition-and-mining method
 called \emph{Star Partition and Mining} (SPM) which resolves
-the deficiency of TRM method.
+the deficiencies of TRM method.
 

### 2016-05-09 sec1_introduction.tex
Further edits on Sec1 and sec4

@@
 refers to a group of objects traveling together for a certain period of time 
-and the group is normally determined according to spatial proximity. 
+and the group is normally determined by spatial proximity. 
 A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
 and driven by different mining applications, there are a bunch of variants 
-of co-moving patterns that have been developed with more advanced constraints.
+of co-movement patterns that have been developed with more advanced constraints.
 
 Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
-with different constraints in the attributes of clustering method and length of temporal duration. 
+with different constraints in the attributes of clustering in spatial proximity,
+consecutiveness in temporal duration and computational complexity. 
 In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
@@
 whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
-and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
-spatial clustering in determining groups. 
+and \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
+spatial clustering. 
 In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
 and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
-of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
+of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
 whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
-The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}.
+The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
+arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
 They introduce a parameter $L$ to control the minimum length of each local consecutive segment.
@@
 \hline 
- & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
+ & Proximity & Consecutiveness &  Time Complexity\\ 
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
+group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
 \hline 
-swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
+swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
 \hline 
 \end{tabular} 
-\caption{Existing co-movement patterns.
-The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
+\caption{Constraints and complexity of co-movement patterns.
+The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
 \label{tbl:existing_co_patterns}
@@
 \caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
-clusters of objects in each snapshots are denoted using dotted circles.}
+clusters of objects in each snapshots are denoted using dotted circles. Each type of pattern has its parameters. 
+$M$ denotes the minimum size of objects.
+$K$ denotes the minimum size of timestamps.
+$L$ denotes the minimum size of locally consecutive timestamps.}
 \label{fig:related_work}
@@
 
-We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
-The temporal dimension is discretized into six snapshots. 
-In each snapshot, the objects are clustered as shown in the dotted circle.
-By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
-It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
-the same constraints on the time duration. 
-\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
-does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
-If further set $M=2,K=3$, two \emph{platoon} patterns are found.
+To better illustrate the temporal constraints of these 
+co-movement patterns, we design a scenario with six example trajectories in Figure~\ref{fig:related_work}.
+In the setting, the temporal dimension  is discretized into six snapshots. 
+In each snapshot, objects are clustered as shown in the dotted circles. We use $M$ to denote
+the minimum size of a object group, $K$ to denote the minimum number 
+of timestamps in a duration, $L$ to denote the minimum size of local-consecutive segments in a duration.
+
+\noindent\textbf{Global consecutiveness}: \emph{Flock} and \emph{convoy} patterns enforce the pattern duration to be \emph{global consecutive}.
+We discover one \emph{flock} and one \emph{convoy} pattern, which both correspond to $\{o_3,o_4:1,2,3\}$.
+It can be verified that no other object groups appears in more than three consecutive timestamps.
+
+\noindent\textbf{Local consecutiveness}: \emph{Group} and \emph{platoon} patterns require the duration to be \emph{locally consecutive}. When setting $L = 2$,
+we observe three \emph{group} patterns and three \emph{platoon} patterns. Specifically, \emph{group} aims to find the
+pattern with maximal object set whose duration conforms to $L$ consecutiveness.
+Taking the pattern $\{o_3,o_4,o_5:2,3\}$ as an example.
+$\{o_3,o_4,o_5\}$ is indeed maximal.
+If another object, say $o_2$, is added to the group, the duration reduces to $\{3\}$ which is not $L$-consecutive.
+In fact, adding any other object to this group invalidates the $L$-consecutiveness.
+In contrary, \emph{platoon} finds the maximal object set whose duration is not only $L$-consecutive but also with size no less than $K$.
+Therefore, \emph{platoon} finds a different set of patterns.
+For example, $\{o_4,o_5:2,3,5,6\}$ is a \emph{platoon} pattern but not a \emph{group} pattern.
+This is because the object set $\{o_4,o_5\}$ is not maximal wrt.
+\emph{group}, as we can see that adding $o_3$ to the object set results in a larger \emph{group} pattern.
+Therefore, $\{o_4,o_5:2,3,5,6\}$ is not a \emph{group}.
+
+\noindent\textbf{No consecutiveness}: \emph{Swarm} pattern relaxes the consecutiveness in the duration.
+Thus as shown in the Figure, \emph{swarm} discover the most number of patterns.
+In particular, given the same $M$ and $K$, \emph{swarm} result covers all patterns discovered in \emph{flock}, \emph{convoy} and \emph{platoon}.
+Furthermore, it finds more patterns that are not covered by \emph{flock}, \emph{convoy} and \emph{platoon}.
+For instance, $\{o_5,o_6, 1,4,5\}$ is a \emph{swarm} but is neither a \emph{platoon} (with $L=2$) nor a \emph{convoy}.
+
+%Therefore, patterns $\{o_1,o_2:1,2,4,5\}$,
+%$\{o_3,o_4,o_5:2,3\}$ and $\{o_5,o_6,4,5\}$ are found. Taking
+
+%We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
+%The temporal dimension is discretized into six snapshots. 
+%In each snapshot, the objects are clustered as shown in the dotted circle.
+%By setting $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
+%\emph{Convoy} pattern finds the objects that travels in consecutive timestamps. Only one object group $\{o_3,o_4\}$
+%matches the criteria with the timestamps $\{1,2,3\}$. Since the example treats the clusters as given, \emph{flock}
+%shares the same pattern result \emph{convoy}.  When the consecutiveness constraint is relax, we discover more patterns.
+%By setting $L = 2$, we find three \emph{group} patterns. For example $\{o_1,o_2\}$ forms a \emph{group} pattern
+%since they appear together in $\{1,2,4,5\}$, where the local consecutiveness of size $2$ ($L = 2$) is met.
+
+%It is worth noting that \emph{convoy} and \emph{flock} have the same result pattern because both patterns share 
+%the same constraints on the time duration. I DON'T UNDERSTAND WHY YOU EMPHASIZE THIS. WHEN WILL THEY BE DIFFERENT?
+%The groups detected by \emph{Swarm} are superset of \emph{convoy} and \emph{flock} patterns, as \emph{Swarm} imposes no constraint on temporal consecutiveness.
+By setting $L=2$, we find three \emph{group} patterns.
+%If further set $M=2,K=3$, two \emph{platoon} patterns are found.
 It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e.
@@
 However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.
+TOO UGLY!
+NEED TO EXPLAIN THE FIGURE BASED ON TABLE $1$.
+AT LEAST READERS CAN HAVE A ROUGH IDEA HOW YOU OBTAIN THE RESULT GROUPS.
 
@@
 As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. 
-Hence, there is a particular demand for a general platform to support all these co-movement patterns.
+%Besides, we observe that, the number of co-movement patterns could be nearly exponential. 
+%For instance, in the small example in Figure~\ref{fig:related_work}, \emph{swarm} already discovers 5 patterns.
+We further identify that existing patterns either miss out interesting patterns (i.e, \emph{convoy}) 
+or likely contain non-interesting patterns (i.e., \emph{swarm}, \emph{platoon}).
+Hence, there is a particular demand for a new pattern model to fine control the pattern result without losing expressiveness. 
 The other issue with existing methods is that they are built on top of centralized indexes that are not scalable.
@@
 In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown.
-We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}.
-The results show that their performance degrades dramatically as the dataset size scales up.
-In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity.
-For instance, the
-complexities of \emph{swarm} and \emph{platoon} are already exponential. 
-Therefore, none of them can handle millions of trajectories efficiently. 
+We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns} as well as an experimental evaluation with million-scale cardinality of a trajectory database (as shown in Figure~\ref{}).
+Results show that their performances degrade dramatically as the dataset size scales up and none of the existing solutions is scalable to handle large-scale trajectories.
+%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
+%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
+%Therefore, none of them can handle millions of trajectories efficiently. 
 %CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
@@
 Therefore, our primary contributions in this paper are to close these two gaps. 
-First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature.
-We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem.
-The \emph{loose connection} problem refers to the patterns that discovered 
-are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
+First, we summarize two anomalies from existing patterns, namely, \emph{missing-pattern} and \emph{loose-connection}.
+The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
+Figure~\ref{fig:platoon_weakpoint} (a). if the duration size is set to be $K=4$, neither \emph{flock}s nor \emph{convoy}s
+can be discovered. As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
+the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
+be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
+\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
+as \emph{loose-connection}~\cite{li2015platoon} anomaly. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
+the two objects $o_1, o_2$ 
 would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
@@
 In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
-To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$.
-By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem.
+In current literature,
+users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
+%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
+To cope with both of the two anomalies, we propose the \emph{general co-movement pattern} 
+by introducing the gap parameter $G$, which requires the distance of 
+timestamps in the duration to be no larger than $G$. 
+By so doing, we gain a fine-grained control over the pattern duration, which alleviates both the \emph{missing-pattern} and the \emph{loose connection} problem.
 Meanwhile, the general co-movement pattern does not concede its expressiveness.
 As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters.
+Therefore, users are still able to exclude non-consecutive patterns
+or include loosely-connected patterns when they feel necessary.
 %IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
@@
 \center
-\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
-\caption{Loosely connected pattern in platoon and swarm.
+\includegraphics[width=0.4\textwidth]{platoon_weakpoint.eps}
+\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
+in \emph{flock} and \emph{convoy}.
+When $K=4$, none of the two patterns can be discovered.
+(b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}.
 The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
@@
 
-Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
-solution is a three-step MapReduce alike approach. First, trajectories are partitioned
-into snapshots where clusters from each snapshots are formed in parallel. Second, 
-clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
-are mined from each group. The challenge here is to ensure that
-the patterns mined at step three is complete. If not, further shuffles and computations are required which 
-significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
-shuffle amount at each stage to a minimum, 
-we design a novel star-based partition scheme to efficiently partition objects based on their
-belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
-largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
+Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
+The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
+In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
+of the partitions. Such properties ensure that neither false-patterns 
+nor miss-patterns are possible in our solution. To meet such partition requirements
+as well as to keep the shuffle amount to a minimum,
+% 
+%%Second, we propose a . Our
+%%solution is a three-step MapReduce alike approach. First, trajectories are partitioned
+%%into snapshots where clusters from each snapshots are formed in parallel. Second, 
+%%clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
+%%are mined from each group. 
+%
+%The challenge here is to ensure that
+%the patterns mined at step three is complete. If not, further shuffles and computations are required which 
+%significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
+%shuffle amount at each stage to a minimum, 
+we first design a naive \emph{Temporal Replication and Mining} (TRM)
+approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
+method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
+Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
+as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
+a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
+GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$.
+Moreover, we utilize \emph{temporal monotonicity} in GCMP to further reduce the shuffling and mining cost in SPM.
+Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in
+Apache Spark which is one of the most popular MapReduce platforms.
 
-Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
+%we design a novel star-based partition scheme to efficiently partition objects based on their
+%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
+%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
+
+We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
 

### 2016-05-09 sec3_definitions.tex
Further edits on Sec1 and sec4

@@
 
-It is also observable that the number of patterns in GCMP is exponential. To reduce the size of output, 
-we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
-Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:
+It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
+when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
+size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
+which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:
+%
+%To reduce the size of output, 
+%we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
 
@@
 the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern.
-This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern and $P_2.O \supset P_1.O$.
+This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$.
 The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
-
-LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
+%LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
 %For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.
@@
 \hline
+$M$ & Object size constraint \\
+\hline 
 $K$ & Duration constraint\\
-\hline
-$M$ & Object size constraint \\
 \hline

### 2016-05-09 sec4_system.tex
Further edits on Sec1 and sec4

@@
 a parallel solution of mining GCMP. In this section,
-we briefly cover the preliminary on MapReduce and then describe
+we briefly describe the preliminaries on MapReduce and then describe
 the overview of our framework in mining GCMP.
@@
 namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
-algorithm consists of three stages: First, input data
-are partitioned and read by a \emph{map} function on each mapper. Then, mappers
-emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
-reducers process received data using a \emph{reduce} function then write the
+algorithm consists of two stages: First, input data
+are partitioned and read by a \emph{map} function on each mapper. Mappers
+emit key-value pairs which are \emph{shuffle}d over the network to reducers. Second,
+reducers process the received data using a \emph{reduce} function then write the
 outputs.
@@
 Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
-First, since it requires reducers to be independent, partitioning  
+First, since reducers are required to be independent, partitioning  
 data to fit the independence could be challenging. Second, since the \emph{shuffle}
 stage requires network access, the data been shuffled should be minimized. 
-We take these concerns in consideration in designing our solutions for mining GCMP.
+We take these concerns in consideration when designing our solutions for mining GCMP.
 %We would bare this concerns in designing our GCMP mining algorithm.
@@
 \subsection{MapReduce Processing for Mining GCMP}
-Our GCMP mining process consists of two MR jobs. The two jobs
-contains four MR stages as illustrated in Figure~\ref{fig:overview}.
+Our GCMP mining process consists of two MR jobs, which are further
+divided into four MR stages as illustrated in Figure~\ref{fig:overview}.
 The first MR job is to cluster objects at each snapshot (i.e.,
-computing $\forall t, o, C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
-trajectories are first reorganized by timestamps in map phase and object locations
-at the same timestamps form a cluster. The clustering takes place in reduce phase, where
-each snapshot is processed independently. The second MR job is to mine GCMPs from 
-clusters at each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
+ $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
+in map phase, trajectories are first reorganized by timestamps and object locations
+at the same timestamps form a cluster. In reduce phase, clustering of objects at each
+snapshot is processed independently. The second MR job is to mine GCMPs from 
+clusters in each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
 the purpose of comparison. Both the two algorithms would partition snapshots in map phase
@@
 Specifically, the reducer output at step (b) can be directly reused 
-as the input to mappers at step (c). Therefore we do not need to 
-transfer data from (b) to (c). Modern MR platforms, especially Spark, have
-already supported such a kind of pipeline.
+as the input to the mappers at step (c). Therefore we do not need to 
+transfer data between the two jobs. Modern MR platforms, especially Spark, have
+already supported such a kind of pipeline by default.
 
@@
 In contrast, it is challenging to design the second job. 
-This is because valid patterns may spray across multiple snapshots, where inappropriate partitioning
+This is because valid patterns may spray across multiple snapshots or contain different object sets, where inappropriate partitioning
 of snapshots may fail to discover certain valid patterns.
-Formally, a reasonable partition strategy 
+Formally, a valid partition strategy 
 needs to meet the following requirements: (a) the resulted partitions need
@@
 the patterns discovered in the reduce phase are valid patterns so that
-no further verification is required. We formalize the two 
+no further verification is required. We formalize these two 
 properties as \emph{completeness} and \emph{soundness} as follows:
@@
 Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$.
-$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$.
-$\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
+$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t.
+$P$ is valid in $Par_i$.
+$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
 \end{definition}

### 2016-05-09 sec5_baseline.tex
Further edits on Sec1 and sec4

@@
 \label{sec:trm_solution}
-The \emph{temporal-based} method of mining GCMP follows the solution framework 
-as in Figure~\ref{fig:overview}. The idea of the \emph{temporal-based} method 
+The idea of \emph{Temporal Replication and Mining} (TRM)
 is to group temporally closed snapshots together, such that patterns can be
-mined on each group of the snapshot.
-In order to achieve the \emph{completeness}
-and \emph{soundness} during partitioning, we design a \emph{Temporal Replication
-and Mining} (TRM) algorithm as shown in Algorithm~\ref{algo:trm_overview}.
+mined on each group of the snapshot. In order to achieve the \emph{completeness}
+and \emph{soundness} during partitioning, we allow replication of
+snapshots among groups. The TRM is described in Algorithm~\ref{algo:trm_overview}.
 
@@
 
-As shown in Algorithm~\ref{algo:trm_overview}, the \emph{Temporal Replication and Mining} (TRM) algorithm takes
+As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm takes
 three steps.
-First, in map phase, each snapshots is keyed with is timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}).
+First, in the map phase, each snapshot is keyed with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}).
 Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}).
@@
 Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}).
-It is easy to see that this method replicates a snapshots $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.
+It is easy to see that this method replicates a snapshots at most $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.
 

### 2016-05-14 sec1_introduction_bk.tex
Introduction Almost Done
Need resolve comments

@@
 \hline 
- & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
+ & Proximity & Consecutiveness &  Time Complexity\\ 
 \hline 
@@
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
@@
 \hline 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
+\hline 
 swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
-\hline 
 \end{tabular} 
-\caption{Existing co-movement patterns.
-The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the total number of timestamps.}
+\caption{Constraints and complexity of co-movement patterns.
+The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
 \label{tbl:existing_co_patterns}
@@
 
-We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
-The temporal dimension is discretized into six snapshots. 
-In each snapshot, the objects are clustered as shown in the dotted circle.
-By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
-It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
-the same constraints on the time duration. 
-\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
-does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
-If further set $M=2,K=3$, two \emph{platoon} patterns are found.
+We compare and contrast these patterns using Figure~\ref{fig:related_work} as an example. 
+In Figure~\ref{fig:related_work}, six trajectories are presented and 
+the temporal domain is discretized into six snapshots. In each snapshots,
+the objects are clustered as shown in the dotted circles. In this example, we
+do not distinguish how the cluster is generated but focus on the 
+differences on the pattern constraints. There are at most three parameters
+required for each pattern, where $M$ is the minimum cardinality  of the object set;
+$K$ is the minimum duration; $L$ is the minimum length for each locally consecutive
+timestamps.
+
+Both \emph{flock} and \emph{convoy} require two parameters $M$ and $K$. They
+further enforce the duration of a pattern to be consecutive. As shown in the
+Figure~\ref{fig:related_work}, $\{o_3,o_4:1,2,3\}$ are the only pattern that matches the requirement.
+Differently, \emph{group} does not have the constraint for the minimum object size nor minimum duration. 
+Indeed, \emph{group} aims to find the maximal set of objects whose duration is 
+locally consecutive.
+In Figure~\ref{fig:related_work}, three patterns are discovered to conform to $L$.  \emph{Platoon}
+similarly uses $L$ as pattern parameter, but it further requires $M$ and $K$. In Figure~\ref{fig:related_work}, 
+three patterns are discovered as \emph{platoon}s. It is notable that, due the differences in semantics,
+\emph{platoon} discovers a different set of patterns from \emph{group}. For instance, a \emph{platoon} $\{o_3,o_4:1,2,3\}$
+is not a \emph{group} since $\{o_3,o_4,o_5:2,3\}$ is already a \emph{group} making $\{o_3,o_4:1,2,3\}$ not maximal in object size.
+On the other hand, although $\{o_3,o_4,o_5:2,3,\}$ is a \emph{group}, its
+duration only consists of two timestamps, making it not a \emph{platoon}. \emph{Swarm} requires
+$M$ and $K$ but it does not enforce any consecutiveness in the pattern duration. 
+Due to such a relaxation, \emph{swarm} is able to find more results that
+are not discovered by \emph{convoy} or \emph{platoon}. For instance, $\{o_2,o_3:3,4,6\}$ is a \emph{swarm}
+with $M=2,K=3$. However, since its duration is not locally consecutive with size $2$, it is not a \emph{platoon}.
+Similarly, since the duration is not even consecutive, it is not a \emph{convoy} neither.
+
+%To better illustrate the temporal constraints of these 
+%co-movement patterns, we design a scenario with six example trajectories in Figure~\ref{fig:related_work}.
+%In the setting, the temporal dimension  is discretized into six snapshots. 
+%In each snapshot, objects are clustered as shown in the dotted circles. We use $M$ to denote
+%the minimum size of a object group, $K$ to denote the minimum number 
+%of timestamps in a duration, $L$ to denote the minimum size of local-consecutive segments in a duration.
+%
+%\noindent\textbf{Global consecutiveness}: \emph{Flock} and \emph{convoy} patterns enforce the pattern duration to be \emph{global consecutive}.
+We discover one \emph{flock} and one \emph{convoy} pattern, which both correspond to $\{o_3,o_4:1,2,3\}$.
+It can be verified that no other object groups appears in more than three consecutive timestamps.
+%
+%\noindent\textbf{Local consecutiveness}: \emph{Group} and \emph{platoon} patterns require the duration to be \emph{locally consecutive}. When setting $L = 2$,
+%we observe three \emph{group} patterns and three \emph{platoon} patterns. Specifically, \emph{group} aims to find the
+%pattern with maximal object set whose duration conforms to $L$ consecutiveness.
+Taking the pattern $\{o_3,o_4,o_5:2,3\}$ as an example.
+$\{o_3,o_4,o_5\}$ is indeed maximal.
+If another object, say $o_2$, is added to the group, the duration reduces to $\{3\}$ which is not $L$-consecutive.
+In fact, adding any other object to this group invalidates the $L$-consecutiveness.
+In contrary, \emph{platoon} finds the maximal object set whose duration is not only $L$-consecutive but also with size no less than $K$.
+Therefore, \emph{platoon} finds a different set of patterns.
+For example, $\{o_4,o_5:2,3,5,6\}$ is a \emph{platoon} pattern but not a \emph{group} pattern.
+This is because the object set $\{o_4,o_5\}$ is not maximal wrt.
+\emph{group}, as we can see that adding $o_3$ to the object set results in a larger \emph{group} pattern.
+Therefore, $\{o_4,o_5:2,3,5,6\}$ is not a \emph{group}.
+%
+%\noindent\textbf{No consecutiveness}: \emph{Swarm} pattern relaxes the consecutiveness in the duration.
+Thus as shown in the Figure, \emph{swarm} discover the most number of patterns.
+In particular, given the same $M$ and $K$, \emph{swarm} result covers all patterns discovered in \emph{flock}, \emph{convoy} and \emph{platoon}.
+Furthermore, it finds more patterns that are not covered by \emph{flock}, \emph{convoy} and \emph{platoon}.
+For instance, $\{o_5,o_6, 1,4,5\}$ is a \emph{swarm} but is neither a \emph{platoon} (with $L=2$) nor a \emph{convoy}.
+
+%Therefore, patterns $\{o_1,o_2:1,2,4,5\}$,
+%$\{o_3,o_4,o_5:2,3\}$ and $\{o_5,o_6,4,5\}$ are found. Taking
+
+%We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
+%The temporal dimension is discretized into six snapshots. 
+%In each snapshot, the objects are clustered as shown in the dotted circle.
+%By setting $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
+%\emph{Convoy} pattern finds the objects that travels in consecutive timestamps. Only one object group $\{o_3,o_4\}$
+%matches the criteria with the timestamps $\{1,2,3\}$. Since the example treats the clusters as given, \emph{flock}
+%shares the same pattern result \emph{convoy}.  When the consecutiveness constraint is relax, we discover more patterns.
+%By setting $L = 2$, we find three \emph{group} patterns. For example $\{o_1,o_2\}$ forms a \emph{group} pattern
+%since they appear together in $\{1,2,4,5\}$, where the local consecutiveness of size $2$ ($L = 2$) is met.
+
+%It is worth noting that \emph{convoy} and \emph{flock} have the same result pattern because both patterns share 
+%the same constraints on the time duration. I DON'T UNDERSTAND WHY YOU EMPHASIZE THIS. WHEN WILL THEY BE DIFFERENT?
+%The groups detected by \emph{Swarm} are superset of \emph{convoy} and \emph{flock} patterns, as \emph{Swarm} imposes no constraint on temporal consecutiveness.
+By setting $L=2$, we find three \emph{group} patterns.
+%If further set $M=2,K=3$, two \emph{platoon} patterns are found.
 It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e.
@@
 In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown.
-We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}.
-The results show that their performances degrade dramatically as the dataset size scales up.
-In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity.
-For instance, the
-complexities of \emph{swarm} and \emph{platoon} are already exponential. 
-Therefore, none of them can handle millions of trajectories efficiently. 
+We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns} as well as an experimental evaluation with million-scale cardinality of a trajectory database (as shown in Figure~\ref{}).
+Results show that their performances degrade dramatically as the dataset size scales up and none of the existing solutions is scalable to handle large-scale trajectories.
+%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
+%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
+%Therefore, none of them can handle millions of trajectories efficiently. 
 %CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
@@
 
-Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
+We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
 

### 2016-05-14 sec4_system.tex
Introduction Almost Done
Need resolve comments

@@
 \subsection{Preliminary on MapReduce}
-MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
+MapReduce (MR) was formally proposed by Dean et.al.~\cite{dean2008mapreduce}
 and has subsequently implemented by many open source systems. Those systems
-provide handy APIs with fualt tolerances and are popularly
+provide handy APIs with fault tolerances and are popularly
 used as large-scale data processing platforms. 
@@
 namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
-algorithm consists of two stages: First, input data
-are partitioned and read by a \emph{map} function on each mapper. Mappers
-emit key-value pairs which are \emph{shuffle}d over the network to reducers. Second,
-reducers process the received data using a \emph{reduce} function then write the
-outputs.
+algorithm consists of three major steps: First, input data
+are partitioned and read by a \emph{map} function on each mapper. Then, mappers
+emit key-value pairs which are \emph{shuffle}d over the network to reducers. Lastly,
+reducers process the received data using a \emph{reduce} function.
 
@@
 data to fit the independence could be challenging. Second, since the \emph{shuffle}
-stage requires network access, the data been shuffled should be minimized. 
+step requires network access, the data been shuffled should be minimized. 
 We take these concerns in consideration when designing our solutions for mining GCMP.
@@
 \subsection{MapReduce Processing for Mining GCMP}
-Our GCMP mining process consists of two MR jobs, which are further
-divided into four MR stages as illustrated in Figure~\ref{fig:overview}.
+Our GCMP mining process consists of two MR jobs as illustrated in Figure~\ref{fig:overview}.
 The first MR job is to cluster objects at each snapshot (i.e.,
  $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
-in map phase, trajectories are first reorganized by timestamps and object locations
-at the same timestamps form a cluster. In reduce phase, clustering of objects at each
+in map phase, trajectories are firstly reorganized by timestamps and object locations
+at the same timestamps form a snapshot. In reduce phase, clustering of objects at each
 snapshot is processed independently. The second MR job is to mine GCMPs from 
-clusters in each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
-the purpose of comparison. Both the two algorithms would partition snapshots in map phase
+clusters in each snapshot. We design and compare two MR algorithms (i.e., TRM and SPM)for 
+GCMP mining. Both the two algorithms would partition snapshots in map phase
 (as in Figure~\ref{fig:overview}(c))
@@
 transfer data between the two jobs. Modern MR platforms, especially Spark, have
-already supported such a kind of pipeline by default.
+already supported such a kind of pipeline.
 
@@
 In contrast, it is challenging to design the second job. 
-This is because valid patterns may spray across multiple snapshots or contain different object sets, where inappropriate partitioning
+This is because valid patterns may spray across multiple snapshots 
+or contain different object sets, where inappropriate partitioning
 of snapshots may fail to discover certain valid patterns.
@@
 the deficiencies of TRM method.
-
-%Depends on the pattern mining strategy, the size of shuffle and replication may differ.
-We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.
-
-%
-%In particular, we need
-%the number of partitions to be reasonably large in order to achieve
-%good parallelism in stage (d). Meanwhile, we need to ensure a partition 
-%of snapshots containing enough information so that patterns discovered 
-%in stage (d) are complete.  Furthermore, we have to ensure that the
-%patterns that discovered in stage (d) are real patterns.
-
-%However, there are two conflicting requirements that restrain us from 
-%designing a simple and effective solution. 
-%On one hand, we need to partition snapshots in stage (c) as many as possible 
-%so that good parallelism could be achieved in stage (d). 
-%On the other hand, in stage (d), 
-%we require each partition containing enough information in order to discover
-%proper GCMP patterns. This prevents us from arbitrarily partition snapshots in
-%stage (d). To design a working algorithm, find the minimum size of partition is
-%crucial. In the following section, we first design a naive approach that
-%partitions snapshots by allowing overlapping among partitions. Such a partition strategy
-%although has overhead in shuffling, it corrects find GCMPs in parallel in stage (d).
-%In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.
-
-%\section{Temporal Replication and Mining}
-%
-%
-%%It is notable that some patterns 
-%%may be very long in duration (e.g., when discovering \emph{swarm}) or some patterns 
-%%may contain a large set of objects (e.g., when discover \emph{group} patterns with small $L$).
-%%Therefore, we require the size of partition to be large enough. Reaching the
-%%balance between the two requirement is crucial. In the following sections, we will
-%%describe a naive partition scheme which meets the two requirements.
-%
-%%Our parallel solution incurs two rounds of shuffles. The first round of shuffle happens in step (a). This
-%%is because that the trajectories stored in HDFS needs to be regrouped to form snapshots. 
-%%The second round of shuffle occurs in step(d). This is because that 
-%% the clusters need to be regrouped so that subsequent pattern detection can be performed.
-%% Despite the simpleness of our parallel solution, it is actually nontrivial to work out a scalable solution.
-%% The major challenge lies in the step (d) and (e). 
-%
-%
-%%\section{Preliminary on Apache Spark}
-%%\label{sec:system_overview}
-%%Apache Spark is an open sourced modern parallel processing platform
-%%based on Resilient-Distributed-Dataset (RDD).
-Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD.
-Algorithms in Spark is implemented by supplying various actions to an input RDD.
-Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.
-%%
-%%Compared to MapReduce, Spark 
-%%utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}.
-In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
-%Due to threading, there is a paradigm shift from MapReduce to Spark.
-In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process.
-While in Spark, the cost of starting a task is negligible since each task is done by a thread.
-Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.
-
-%\section{Mining Generalized Co-moving Pattern}
-%\label{sec:solution}
-%There are two stages in mining GCMP.
-The first stage is to cluster objects in each snapshots.
-Then the seconds stage is to mine patterns from clusters in parallel.
-The overview of the parallel approach is
-%shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
-%read trajectories and cluster objects in the same snapshots.
-Since the objects at each snapshots are independent, this stage can be easily performed in parallel.
-The first stage involves network IO.
-Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.

### 2016-05-14 sec5_baseline.tex
Introduction Almost Done
Need resolve comments

@@
 The idea of \emph{Temporal Replication and Mining} (TRM)
-is to group temporally closed snapshots together, such that patterns can be
-mined on each group of the snapshot. In order to achieve the \emph{completeness}
+is to group temporally contiguous snapshots together, s.t. patterns can be
+mined from each group of snapshots. In order to achieve the \emph{completeness}
 and \emph{soundness} during partitioning, we allow replication of
-snapshots among groups. The TRM is described in Algorithm~\ref{algo:trm_overview}.
-
-%%The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
-%A simple but effective method
-%is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
-%some of the snapshots need to be replicated on multiple executors.
-%We call this method the \emph{Temporal Replication and Mining} approach. 
-%The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.
+snapshots among groups. The TRM is outlined in Algorithm~\ref{algo:trm_overview}.
 
@@
 \State group-by $t$, emit a $\langle t, Par_t\rangle$,
-\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(\lfloor \frac{K}{L} \rfloor -1)*G+K+L}\} $
+\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(\lceil \frac{K}{L} \rceil -1)*G+2K}\} $
 \EndFor
@@
 
-As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm takes
-three steps.
-First, in the map phase, each snapshot is keyed with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}).
-Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}).
-We will shortly discuss how the group size is determined.
-Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}).
-It is easy to see that this method replicates a snapshots at most $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.
+As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
+three steps. First, in the map phase, each snapshot is keyed 
+with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
+Second, in the partition phase, every snapshot is grouped with its next 
+$(\lceil \frac{K}{L} \rceil -1)*G+2K$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is derived. 
+Third, in the reduce phase, a lineSweepMining method is invoked 
+to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
+It is easy to see that this method replicates a snapshots 
+at most $(\lceil \frac{K}{L} \rceil -1)*G+2K$ times.
 
@@
 properties cannot be satisfied. In the Algorithm~\ref{algo:trm_overview}, 
-the partition size is chosen as $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$. As stated in the following
+the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
 theorem, such a partition method is sound and complete.
@@
 \label{thm:replication_partition}
-Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K + L )}\}$. Then $\mathbb{P}$ is sound and complete.
+Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
 \end{theorem}
 \begin{proof}
-The soundness of partition is trivial.
+The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
 Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
 Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
-Since $T'$ conforms to $K,L,G$, then $K+L \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$.
-Therefore, $\Sigma_i(l_i+g_i) \leq \lfloor \frac{K}{L}-1\rfloor *G+K+L$.
-Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would valid in $Par_t$.
+Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$.
+Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$.
+Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$.
 This proves the completeness of the partitioning method.
@@
 After partition, each task in the reduce phase processes a partition $Par_i$, which contains
-$\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ snapshots starting from snapshot $S_i$. With such a 
+$(\lceil \frac{K}{L} \rceil -1) *G+2K$ snapshots starting from snapshot $S_i$. With such a 
 partition method, we observe that within $Par_i$, only the 
@@
 
-The algorithm scans the snapshots in a partition in the sequential order.During the scan it
+The algorithm scans the snapshots in a partition in sequential order. During the scan, it
 maintains a candidate set $C$ which could potentially be a valid pattern (line~\ref{code:ls-can-set}).
@@
 \begin{example}
-We illustrate the process of \emph{Trajectory Replication and Mining} in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$.
-In (a), snapshots are clustered and these snapshots are the input to the TRM.
-Then, we compute the size
-for each partition, which equals to $\lfloor \frac{K}{L}-1 \rfloor *G+K+L = 4$. Therefore, in (b), every four snapshots
+We illustrate the process of TRM in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
+for each partition, which equals to $(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Therefore, in (b), every four snapshots
 are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
@@
 patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
-their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1,2\}$ which is neither
+their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1\}$ which is neither
 a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
@@
 it requires to replicate the data multiple times. 
-Specifically, each snapshots are copied $\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ times. 
+Specifically, each snapshots are copied $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
 In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 

### 2016-05-14 sec6_spm.tex
Introduction Almost Done
Need resolve comments

@@
 \label{sec:spm_solution}
-In order to develop a method that achieves good parallelism under any pattern parameters, 
-we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
+In order to develop a method that achieves good parallelism 
+under any pattern parameters, we propose 
+the \emph{Star Partition and Mining} (SPM) method. In SPM,
 we first design a novel object-based partition method named \emph{star partition}. 
-Then, we design an \emph{Apriori}-like 
+Then, we adapt an \emph{Apriori}-like 
 method to mine GCMP patterns out of each partition.
@@
 The object-object pairs are then paired up with the timestamp of 
-the snapshot to form a 3-uple(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
-In the partition phase, 3-uples with the same leading object form a \emph{star} which will be explained shortly 
+the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
+In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
 (lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
@@
 \subsubsection{Star Partition}
-The intuition of star partition is that, if two objects are part of
-the same pattern, then at some snapshots, they must belong to the same 
-cluster. Therefore, we may link objects that belong to the same cluster
-at some snapshots to form a \emph{connection graph}. Objects that are
-not connected surely do not belong to a pattern. We may further
-partition the connection graph so that mining proper patterns can be
-done in parallel. We define the \emph{connection graph} and \emph{star}
+The intuition of star partition is that, if two objects are part 
+of the same pattern, they must belong to the same cluster at 
+some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
+not connected surely fail to form a pattern. We may then
+partition the connection graph based on vertex connectivity
+s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
 as follows:
@@
 Based on the above theorem, we can mine GCMP from each partition independently.
-It is notable that, in star partition, original data is replicated for $O(\mathbb{O})$ times
-as each object may be sent to $O(\mathbb{O})$ partitions. Since this complexity is free
+It is notable that, in star partition, original data is replicated for $O(|\mathbb{O}|)$ times
+as each object may be sent to $O(|\mathbb{O}|)$ partitions. Since this complexity is free
 from pattern parameters, the star partition is more scalable than the temporal replication.
@@
 we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
-the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$.
+the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$.
 Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.

### 2016-05-14 sec7_optimization.tex
Further edits on Sec1 and sec4
Introduction Almost Done
Need resolve comments

@@
 
-\subsection{Candidate Pruning via Temporal Monotonicity}
+\subsection{Candidate Pruning}
+\subsubsection{Temporal monotonicity}
 During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
@@
 
+\subsubsection{Forward closure checking}
+
 \begin{example}
 We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning.
-As shown, at the initial stage, $\{3,6\}\{1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence.
+As shown, at the initial stage, $\{3,6:1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence.
 By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned.
@@
 \subsection{Duplication Detection}
+
+\subsection{Handling Overlapping Clusters}

### 2016-05-28 sec1_introduction.tex
Added intro part

--- 2016-05-05 sec1_introduction.tex
@@
 refers to a group of objects traveling together for a certain period of time 
-and the group is normally determined according to spatial proximity. 
+and the group is normally determined by spatial proximity. 
 A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
 and driven by different mining applications, there are a bunch of variants 
-of co-moving patterns that have been developed with more advanced constraints.
+of co-movement patterns that have been developed with more advanced constraints.
 
 Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
-with different constraints in the attributes of clustering method and length of temporal duration. 
+with different constraints in the attributes of clustering in spatial proximity,
+consecutiveness in temporal duration and computational complexity. 
 In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
-and \emph{group}~\cite{wang2006grouppattern} patterns require 
+and the \emph{group}~\cite{wang2006grouppattern} patterns require 
 all the objects in a group to be enclosed by a disk with radius $r$; 
-whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
-and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
-spatial clustering in determining groups. 
-In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
-and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
-of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
-whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
-The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}.
+whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
+and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
+spatial clustering. 
+In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
+and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
+of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
+whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
+The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
+arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
 They introduce a parameter $L$ to control the minimum length of each local consecutive segment.
-
-%Specifically, a \emph{flock}~\cite{gudmundsson2006flock} requires the group to be within a disk region of
-%the user specified size.  A \emph{convoy}~\cite{jeung2008convoy} requires a group to be densely connected. Both \emph{flock}
-%and \emph{convoy} require a group to appear for at least $k$ consecutive times.  
-%\emph{Group}~\cite{wang2006grouppattern} and 
-%\emph{Swarm}~\cite{li2010swarm} patterns relax the consecutiveness constraint, where non-consecutive timestamps are allowed in a pattern duration.
-\emph{Group} pattern require objects in a group to be within a disk region, while \emph{swarm}require the objects in a group to be densely connected.
-%Recently,
-%\emph{platoon}~\cite{li2015platoon} pattern is proposed to impose a fine-grained control on the consecutiveness of the duration.
-In \emph{platoon}, the duration of a group needs to have the local-consecutive portion of size no less than the user-specified $L$.
 
@@
 \hline 
- & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
+ & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
+swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
 \hline 
-swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
+group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
 \hline 
 \end{tabular} 
-\caption{Existing co-movement patterns.
-The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
+\caption{Constraints and complexity of co-movement patterns.
+The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
 \label{tbl:existing_co_patterns}
@@
 
-%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
-% 
-%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
-%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots.
-%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints.
-For instance, Jeung et al.
-proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al.
-proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al.
-proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots.
-%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
 \begin{figure}[h]
@@
 \includegraphics[width=0.45\textwidth]{related_work.eps}
-\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
-clusters of objects in each snapshots are denoted using dotted circles.}
+\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots.
+Objects in spatial clusters are enclosed by dotted circles.
+$M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
 \label{fig:related_work}
@@
 
-%%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
-%UPDATE THE FIGURE TO CONTAIN SIX SNAPSHOTS. USE A NEW REPRESENTATION OF THE PATTERN. I DON'T LIKE $\{o_1,o_2\}\{1,2,3\}$. USE ONE PAIR OF $\{\}$ ONLY.
+Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns.
+The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots.
+In each snapshot, we treat the clustering methods as a black-box and assume that they generate the same clusters.
+Objects in proximity are grouped in the dotted circles.
+As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$.
+Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps.
+Hence,$\{o_3,o_4\}$ and $\{o_5,o_6\}$  remains the only two candidates matching the patterns.
+The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint.
+Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}.
+The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns.
+For instance, $\{o_1,o_2:1,2,4,5\}$ is a pattern matching local consecutiveness because timestamps $\{1,2\}$ and $\{4,5\}$ are two segments with length no smaller than $L=2$.
+The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters.
+This explains why $\{o_3,o_4,o_5:2,3\}$ is a  \textit{group} pattern but not a \textit{platoon} pattern.
 
-We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
-The temporal dimension is discretized into six snapshots. 
-In each snapshot, the objects are clustered as shown in the dotted circle.
-By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
-It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
-the same constraints on the time duration. 
-\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
-does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
-If further set $M=2,K=3$, two \emph{platoon} patterns are found.
-It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e.
-$\{1\}$) is less than $2$.
-However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.
+As can be seen, there are various co-movement patterns requested by different 
+applications and it is cumbersome to design a tailored solution for each type. 
+In addition, existing pattern definitions are not expressive enough and may miss 
+interesting patterns or return noisy results. We summarize 
+the two scenarios as \emph{missing-pattern} anomaly
+and \emph{loose-connection} anomaly.
+A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
+As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
+neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
+$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
+the traffic control or the clustering inaccuracy at time $4$. On the other hand,
+the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
+the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
+the two objects $o_1, o_2$ form a \emph{platoon} pattern 
+$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
+making the co-moving behavior very weak.
+In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
+such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
+It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.
 
-% we achieve two \emph{platoon} patterns.
+\begin{figure}[h]
+\center
+\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
+\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
+in \emph{flock} and \emph{convoy}.
+When $K=4$, none of the two patterns can be discovered.
+(b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}.
+The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
+\label{fig:platoon_weakpoint}
+\end{figure}
+
+%In current literature,
+%users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
 %
-%By setting $M=2$, the spatial clusters with at least $2$ objects are displayed with the same shape.
-Since \emph{Convoy} pattern requires the set of objects to be clustered for $k$ \emph{consecutive} snapshots, there results in only one such pattern ($\{o_3,o_4\}\{t_1,t_2,t_3\}$) when $k$ is set to $3$.
-\emph{Swarm} pattern relaxes the consecutiveness of duration, thus there are three patterns discovered.
-\emph{Platoon} pattern requires that each local consecutive duration needs to have at least certain length, which is indicated by an additional parameter $l$.
-When $l$ equals 2, there are two patterns discovered.
-Note that $\{o_6,o_7\}\{t_1,t_4,t_5\}$ is not included in the platoon pattern since $t_1$ is the local consecutive snapshot with duration 1, which is less than $l$.
-CAN WE SUPPORT THE GROUP AND FLOCK PATTERN?
-IF YES, WHY NOT PUT THEM IN THE FIGURE?
 %
-%FOR THE FIGURE: 1) ENLARGE THE FONT SIZE IN THE FIGURE 2) WHY THERE IS NO $o_5$.
-3) WHY OBJECTS IN DIFFERENT COLORS AND SHAPES ARE NOT CLEAR.
-YOU CAN REMOVE COLOR.
-4) PUT THE OBJECTS BELONGING TO THE SAME CLUSTER IN THE SAME LINE.
-
-%We notice that, \emph{platoon} pattern is more general than \emph{convoy} and \emph{swarm}.
-This is because by setting appropriate $l$, \emph{platoon} can be reduced to \emph{convoy} and \emph{swarm} respectively~\cite{li2015platoon}.
-However, we observe that \emph{platoon} pattern is to loose on the temporal domain thus may result in less significant patterns.
-For example in Figure~\ref{fig:platoon_weakpoint}.
-
-%
-%\begin{figure}[h]
-%\center
-%\includegraphics[width=0.5\textwidth]{platoon_weakpoint.eps}
-%\caption{Miss-pattern in platoon}
-%\label{fig:platoon_weakpoint}
-%\end{figure}
-
-%In platoon, a pattern for $n=2,k=4,l=2$ could be $\{o_1, o_2\}\{t_1,t_2,t_4,t_5,t_{100},t_{101}\}$.
-However, the snapshots $t_{100}$ and $t_{101}$ is too far away from previous snapshots.
-Such two snapshots are in less relation with previous snapshots and thus should be removed from the pattern.
-Based on this observation, we defined a \emph{generalized co-moving} pattern (as in Section~\ref{sec:definition}) to provide a more fine granular control of the pattern.
-In \emph{generalized co-moving} pattern, a parameter $g$ is introduce the control the \emph{maximum gap} allowed between consecutive snapshots.
-By so doing our generalized co-moving pattern is more expressive and can represent all the existing co-moving patterns.
-
-%In step with the advances in localization technologies, the growth in the volume of trajectory data is rapid.
-Traditional single-machine methods face severe scalability problem in handling large trajectory data.
-For example, as reported in~\cite{li2015platoon}, a \emph{Swarm} pattern takes around 100 seconds to discover for 100k trajectories.
-With upto billions of trajectories in nowadays datasets, such approaches apparently become unfeasible.
-To tackle this challenge, we propose a  paralleled solution for discovering \emph{generalized co-moving} patterns.
-We then deploy our idea on the modern MapReduce platform.
-As our experiments show, our solution achieves well load-balance and can process billions of trajectories in XXX seconds.
-Several optimizations are also designed to boost our solution to be orders of magnitudes faster than baseline algorithms.
-
-%In practice, it is cumbersome to design tailed solutions to different types of co-movement pattern discovery.
-
-%In reality, it is cumbersome to design tailed solutions to support 
-%generality and scalability
-
-%In this paper, our primary objectives are solving two
-
-As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type.
-Hence, there is a particular demand for a general platform to support all these co-movement patterns.
-The other issue with existing methods is that they are built on top of centralized indexes that are not scalable.
-To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories.
-In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown.
-We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}.
-The results show that their performance degrades dramatically as the dataset size scales up.
-In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity.
-For instance, the
-complexities of \emph{swarm} and \emph{platoon} are already exponential. 
-Therefore, none of them can handle millions of trajectories efficiently. 
-%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
-
-Therefore, our primary contributions in this paper are to close these two gaps.
-First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature.
-We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem.
-The \emph{loose connection} problem refers to the patterns that discovered 
-are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
-would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
-duration is $98$ timestamps apart, making the co-movement behavior very weak.
+% we summarize two anomalies 
+%The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
+%Figure~\ref{fig:platoon_weakpoint} (a).  As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
+%the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
+%be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
+%\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
+%as \emph{loose-connection}~\cite{li2015platoon} anomaly. 
 %
@@
 %connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
-In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
-To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$.
-By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem.
-Meanwhile, the general co-movement pattern does not concede its expressiveness.
-As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters.
-%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
 
-%
+%For instance, PUT THE FIGURE AND EXPLANATION HERE.
+
+%\begin{figure}[h]
+%\center
+%\includegraphics[width=0.35\textwidth]{rw_perf_O.eps}
+%\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
+%in \emph{flock} and \emph{convoy}.
+When $K=4$, none of the two patterns can be discovered.
+(b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}.
+The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
+%\label{fig:platoon_weakpoint}
+%\end{figure}
+
+The other issue with existing methods is that they are 
+built on top of centralized indexes that are not scalable. 
+To the best of our knowledge, the maximum number of trajectories 
+ever evaluated is up to hundreds of trajectories. 
+In practice, it is rather common to collect at least hundreds of thousands of trajectories 
+and their scalability is left unknown.
+We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns}) as well as an experimental evaluation with a real trajectory database including million-scale points(as shown in Figure~\ref{fig:related_work_scalability}).
+Results show that their performances degrade dramatically as the dataset size scales up. For instances,
+performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
+performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.5k} to \emph{2.4k}.
+It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which may include billion-scale points.
+%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
+%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
+%Therefore, none of them can handle millions of trajectories efficiently. 
+%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
 \begin{figure}[h]
-\center
-\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
-\caption{Loosely connected pattern in platoon and swarm.
-The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
-\label{fig:platoon_weakpoint}
+    \centering
+    \begin{subfigure}[b]{0.23\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{rw_perf_O.eps}
+		\subcaption{$1k$ objects}
+    \label{fig:fig1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{rw_perf_T.eps}
+         \subcaption{$1.2k$ timestamps}
+    \label{fig:fig2}
+    \end{subfigure}
+    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
+    is used with over 2 million points.}
+    \label{fig:related_work_scalability}
 \end{figure}
 
-Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
-solution is a three-step MapReduce alike approach. First, trajectories are partitioned
-into snapshots where clusters from each snapshots are formed in parallel. Second, 
-clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
-are mined from each group. The challenge here is to ensure that
-the patterns mined at step three is complete. If not, further shuffles and computations are required which 
-significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
-shuffle amount at each stage to a minimum, 
-we design a novel star-based partition scheme to efficiently partition objects based on their
-belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
-largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
+Therefore, our primary contributions in this paper are to close these two gaps. 
+First, we propose the \emph{general co-movement pattern} (GCMP) which models
+various co-moment patterns in a unified way while avoids 
+the two identified anomalies. In GCMP, we gain a
+fine-grained control over pattern duration by introducing the gap 
+parameter $G$, which enforces the gap between 
+timestamps to be no larger than $G$.  
+The adoption of $G$ seamlessly integrates with other pattern parameters,
+which preserves the expressiveness while
+alleviates both the \emph{missing-pattern} and the \emph{loose connection} anomalies.
 
-Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
+%Therefore, users are 
+%still able to exclude non-consecutive patterns 
+%or include loosely-connected patterns when they feel necessary.
+
+%We introduce the gap parameter $G$,
+%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
+%To cope with both of the two anomalies, we propose 
+%by introducing the gap parameter $G$,
+
+%By so doing, we gain a fine-grained control s, which As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
+%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
+%
+
+Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
+The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
+In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
+of the partitions. Such properties ensure that neither false-patterns 
+nor miss-patterns are possible in our solution. To meet such partition requirements
+as well as to keep the shuffle amount to a minimum, 
+we first design a naive \emph{Temporal Replication and Mining} (TRM)
+approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
+method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
+Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
+as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
+a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
+GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
+Despite the simpleness of star partition, we theoretically prove its optimality.
+Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
+shuffling and mining cost in SPM. 
+%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
+%Apache Spark which is one of the most popular MapReduce platforms.
+
+%we design a novel star-based partition scheme to efficiently partition objects based on their
+%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
+%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
+
+We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
 

### 2016-05-28 sec5_baseline.tex
Added intro part

@@
 $C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
-patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
-their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1\}$ which is neither
-a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
-sweep finishes, only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
+patterns whose object set is in $S_1$. When scanning the snapshots, patterns in $C_1$ grow
+their timestamps. At $S_4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
+are both $\{1,2,4\}$ which is neither a qualified set of timestamps nor matches $G$ constraint, 
+thus the two candidates are removed from $C_4$. After all snapshots are scanned, 
+only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
 \end{example}

### 2016-05-28 sec6_spm.tex
Added intro part

@@
 \label{sec:spm_solution}
-In order to develop a method that achieves good parallelism 
+In order to achieve a good parallelism 
 under any pattern parameters, we propose 
@@
 \subsubsection{Star Partition}
-The intuition of star partition is that, if two objects are part 
+The intuition of the star partition is that, if two objects are part 
 of the same pattern, they must belong to the same cluster at 
@@
 \Require{$Sr_s$}
-\State { Lv $\gets \{\}$}
-\State { Ground $\gets \{\}$}
+\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
 \ForAll{$e(s,t) = T \in Sr_s$}
@@
 				\State $p \gets cand_v$ join $cand$
-				\If{$p.T$ is partly valid} 
+				\If{$p.T$ is a candidate sequence} 
 					\State LvCand.add($p$)
@@
 		\EndFor
+		\If{$Lv$ is a pattern}
+			\State{Output.add($Lv$)}
+			\State{break}			 
+		\EndIf
 		\State {Lv $\gets$ LvCand}
@@
 \EndWhile
+\State output.addAll($Lv$)
+\State \Return output
 \end{algorithmic}

### 2016-05-28 sec7_optimization.tex
Added intro part

@@
 
-To formally describe the idea, we define the a \emph{candidate sequence} as follows:
+To formally describe the idea, we define the \emph{candidate sequence} as follows:
 
@@
 In the second round, the maximal $G$-connected sequences of size less than $K$ are
-removed. Clearly the simplification algorithm runs in $O(|T|)$ time.
+removed. Clearly the simplification algorithm runs in linear time.
 \begin{algorithm}
@@
 \Require $T$
-\State{---Remove the consecutive portion with size less than $L$---}
+\State{---Remove the consecutive segment with size less than $L$---}
 \State $c \gets 0$
@@
 \EndFor
-\State{---Remove the pseduo-consecutive portion with size less than $K$---}
+\State{---Remove the $G$-connected segment with size less than $K$---}
 \State $s\gets 1$, $c\gets 0$
@@
 \subsubsection{Forward closure checking}
+Although leveraging \emph{temporal monotonicity} could largely prune false candidates and reduce
+the apriori search space, it is ineffective when a \textit{true} pattern exists. 
+For example, if a final pattern of a star $Sr_s$ is the \textit{union of all vertices} in the star, 
+then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
+each level $i$. This results in an exponential search space while
+the output only contains one pattern.  
+In general, when candidates at level $i$ collectively forms a true pattern, 
+running aprior produces many wasted candidates.
+
+Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
+we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
+all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
+\begin{theorem}[Forward Closure Checking Rule]
+Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
+if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
+and directly output $FC_i$.
+\end{theorem}
+
+\begin{proof}
+We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, let 
+$X=P.O - FC_i \neq \emptyset$.
+Consider a subset of $P$ which contains $X$ with size $i+1$, (i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$).
+Since $P$ is a proper pattern, then $P_1$ is also a proper pattern.
+Therefore $P_1 \in Lv_i$.
+Then it follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+\end{proof}
+
+It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
+reduces, thus the pruning power of $FC$ would be stronger.
+
+%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
+%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
+%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
+%all candidates. Then, the following \emph{forward closure checking} rule can be used:
+%
+%\begin{theorem}[Forward Closure Checking Rule]
+%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
+%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
+%$FC_i$ forms a valid GCMP .
+%\end{theorem}
 
 \begin{example}
-We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning.
-As shown, at the initial stage, $\{3,6:1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence.
-By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned.
-Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
+timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
 \end{example}
@@
 %With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
-\subsection{Load Balancing}
 
-\subsection{Duplication Detection}
+\subsection{Optimal Star Partition and Load Balance}
+As we see in Section~\ref{sec:spm_solution}, the apriori phase in SPM may
+take exponential time. An important factor affecting the performance of
+SPM is the size of stars. We notice that, the
+size of star is related to the way the vertexes are numbered.
 
-\subsection{Handling Overlapping Clusters}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{star-alt.eps}
+\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
+\label{fig:star-alt}
+\end{figure}
+
+For example,
+Figure~\ref{fig:star-alt} gives an alternative numbering of vertexes 
+in connection graph thus produces a different set of stars. This partitioning constructs
+four stars with the maximum star consisting of 5 edges. Compared to the partitioning
+in Figure~\ref{fig:star_partition}(b) where five stars are produced with maximum star of 3 edges, this
+partition is inferior in two aspects. First, this partition lacks of one star, which
+results in a smaller number of parallelism. Second, this partition has a larger size
+of maximum edges. With the exponential time complexity in Apriori, the largest star takes
+much more time to compute.
+
+The example shows that different numbering of vertexes in connection graph indeed affects
+the SPM performance. Therefore we wish to find a numbering scheme of connection graph
+such that the edges in each star are best distributed. Notice that the sum of edges 
+is invariant for any numbering scheme of the graph. Thus, our goal is equivalent to find
+a numbering such that the maximum edge size from all stars is minimized.
+
+To formalize the objective, we design an linear algebra model as follows: Let $G$ denote a connection graph.
+Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
+Let $(A:a_{i,j})$ be the matrix representing the induced graph wrt. $\mathbb{A}$. Let vector $\vec{b}$
+be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} vector. Let $\vec{c}:c_j$ be the
+vector equals to $A\vec{b}$. It is easy to see that each $c_j$ denotes the size of star for vertex $j$.
+Therefore, the objective of load balancing can be formalized as follows:
+\begin{equation}
+\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+\end{equation}
+
+Though the objective is well-defined as above, it is challenging to directly optimize
+the equation. First, suppose there are $n$ vertex in $G$, enumerating
+all possible $\mathbb{A}$s leads to $n!$ combinations. 
+Such a high complexity is trivially unpractical. Second,
+since $G$ is constructed at runtime, 
+the load planning can only start after $G$ is created. 
+The planning time are thus required to be short enough otherwise the benefit cannot payoff the planning time.
+
+Despite these challenges, we observe that there is a 
+$O(1)$ time solution which is good enough as stated in the 
+following theorem.
+
+\begin{theorem}[Balance of Star Partition]
+Let $G$ be a connection graph with degree $d$ and $n$ vertexes.
+Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
+For any numbering, $\mathbb{A}$, with high probability, the 
+absolute difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
+That is, it is very likely that 
+$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
+\end{theorem}
+
+\begin{proof}
+Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
+for each object, by the pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
+Next, let $e_{i,j}$ be a 0-1 indicator variable determining whether vertex $i$ connects vertex $j$
+in $G$. Note that edges in $G$ are independent. We use $d_i$ 
+to denote the degree of object $i$ in $G$.  It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
+Since in the star partition, each edge is assigned to the ending vertex
+with lower ID, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
+\begin{equation*}
+a_{i,j} = \begin{cases}
+			e_{i,j}, i>j \\
+			0, otherwise
+		  \end{cases}  
+\end{equation*}
+There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
+$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
+$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
+
+By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
+is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
+we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
+$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
+\begin{equation*}
+\begin{split}
+	Pr(c_i \geq \mu + t) 
+						&\leq \exp(\frac{-2t^2}{n}) \\
+						&= \exp(-2\log n) = n^{-2}
+\end{split}
+\end{equation*}
+
+The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
+Next, since the event $(\max_{1\leq j \leq n}(c_j) > \mu + t)$ can be viewed as
+$\cup_{c_i} (c_i > \mu + t )$, by Union Bound, we achieve the following:
+\begin{equation*}
+\begin{split}
+	Pr(||A\vec{b}||_\infty > \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) > \mu + t)  \\
+		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
+		& = n^{-1} = 1/n
+\end{split}
+\end{equation*}
+Substitute $t$ and $\mu$, we achieve the following concise form:
+\begin{equation*}
+	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{n\log n})) \leq 1/n
+\end{equation*}
+This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$.
+With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
+with probability greater than $(1-1/n)$, 
+the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
+\end{proof}
+
+In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
+the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
+equation holds:
+\begin{equation*}
+Pr(||A\vec{b}||_\infty > (d/2 + O(\sqrt{d\log n})) \leq 1/n
+\end{equation*}
+
+Induced by the Theorem 5, taking object IDs as the numbering (i.e., in Algorithm~\ref{algo:spm_overview})
+would be guaranteed to produce a partition which is almost optimal.
+%By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.
+%Taking expectation on both sides, we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
+Let $\mu =E[c_i] = d/2$, $\delta = \sqrt{12\log n/d}$, by Chernoff Bound,
+%the following holds:
+%\begin{equation*}
+%\begin{split}
+%	Pr(c_i \geq (1+ \delta)\mu) & \leq \exp(-\mu \delta^2 / 3) \\
+%						&= \exp(-d/2 \times 12 \log n / 3d ) \\
+%						&= \exp(-2\log n) = n^{-2}
+%\end{split}
+%\end{equation*}
+%
+%Next, since the event $\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu$ can be viewed as
+%$\cup_{c_i} (c_i > (1+ \delta)\mu )$, by Union Bound, we achieve the following:
+%\begin{equation*}
+%\begin{split}
+%	Pr(||A\vec{b}||_\infty > (1+ \delta)\mu)) &=Pr(\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu)  \\
+%		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq (1+ \delta)\mu) \\
+%		& = n^{-1} = 1/n
+%\end{split}
+%\end{equation*}
+%Substitute $\mu$ and $\delta$, we achieve the following concise form:
+%\begin{equation*}
+%	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{3 d\log n})) \leq 1/n
+%\end{equation*}
+%This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than $ O(\sqrt{d\log n})$ is $(1-1/n)$.
+Notice that $||A^*\vec{b}||_\infty \geq d/2$, therefore, with probability greater than $(1-1/n)$, the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{d\log n})$.
+%\end{proof} 
+%
+%Theorem 5 is powerful enough to induce the following lemma:
+%\begin{theorem}[Load Balance of Algorithm~\ref{algo:spm_overview}]
+%The partitioning in Algorithm~\ref{algo:spm_overview} differs at most $O(\sqrt{d\log |\mathbb{O}|})$ 
+%from optimal partitioning with probability $(1-1/|\mathbb{O}|)$.
+%\end{theorem}

### 2016-05-28 sec8_experiment.tex
Added intro part

\section{Experimental Study}
\label{sec:experiment}
\subsection{Implementation Issues}
We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
platform. Spark is one of the most popular MapReduce-like platform which
uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. Since
Spark directly supports the MapReduce paradigm, our algorithm is able to 
be easily implemented in Spark. In order to help reproduce our experiments,
we further address some implementation issues.
\subsubsection{Task Assignment}
In spark, each task in reduce phase is an Apriori mining phase of 
a star.
Although our star partition method is theoretically balanced, 
it is still necessary to assign equal number of tasks to each executors. 
Spark naturally uses hashing to partition data into tasks, where such
a partitioning does not care on the tasks size. In order to
fully utilize the clusters, it is important to perform a weight-aware
partition. In our implementation, we collect the number of edges
in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
where we assign stars in decreasing order with their sizes and each star
is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
between map and reduce phase can be naturally implemented in Spark, where the 
map result can be cached and the reduce phase can be paused until when the
partition strategy is ready.

\subsubsection{Duplication Detection}
It is notable that the patterns discovered from different tasks (stars) could
be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
from the star $Sr_b$. Though in most applications, such a duplicate pattern
is permitted, we offer an option to eliminate these patterns. The strategy is 
to broadcast each reducers output to every other reducers. This can be
efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
whether any resulted patterns are subsumed and thus filter those patterns.
Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
deal with the duplication detection. However, as the number of final patterns are
normally quit small, we leave the exploration for those techniques to the future.

\subsubsection{Handling Overlapping Clusters}
When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
on objects are applied. Such a clustering method may result one object belonging to
multiple clusters. In such a case, just keeping the timestamps in the edge
of connection graph is insufficient. Instead, we extend every timestemp $t$
to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
belong to at time $t$. The only adaption we need to take the join during
apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
still holds under this new setting.

\subsection{Experimental Setup}
Our experiments run on a 9-node cluster, with Apache Yarn as
the cluster manager. We use 1 node for Yarn resource manager, 
and use the remaining 8 nodes as executors in Spark. In the 
cluster, each node is uniformly equipped with a 2.2GHz quad-core CPU
with 32 GB memory. Inter-node communication is carried by 
the 1Gbps Ethernet.  Some critical configuration of Spark is 
as follows:
\begin{table} [h]
\centering
\begin{tabular}{|l|c|}
\hline 
Parameter & Value  \\ 
\hline 
Java Version & 1.7.0 \\ 
\hline 
spark.driver.memory & 2GB \\ 
\hline 
spark.executor.cores & 2  \\ 
\hline 
spark.executor.instances & 11 \\ 
\hline 
spark.executor.memory & 7GB \\ 
\hline 
spark.master & yarn-cluster \\ 
\hline 
spark.serializer & KryoSerializer \\ 
\hline 
\end{tabular} 
\end{table}

We setup HDFS on the same cluster and all trajectory data
are initially stored in the HDFS. We prepare two set of
large-scaled trajectories with the following properties:

### 2016-06-01 sec1_introduction.tex
Updated Introduction charts
need to simplify part of the introduction

@@
 
-Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
+Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving pattern s 
 with different constraints in the attributes of clustering in spatial proximity,

### 2016-06-01 sec7_optimization.tex
Updated Introduction charts
need to simplify part of the introduction

@@
 \begin{theorem}[Balance of Star Partition]
-Let $G$ be a connection graph with degree $d$ and $n$ vertexes.
+Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
 Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
@@
 Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
-for each object, by the pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
+for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
 Next, let $e_{i,j}$ be a 0-1 indicator variable determining whether vertex $i$ connects vertex $j$
@@
 The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
-Next, since the event $(\max_{1\leq j \leq n}(c_j) > \mu + t)$ can be viewed as
-$\cup_{c_i} (c_i > \mu + t )$, by Union Bound, we achieve the following:
+Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
+$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
 \begin{equation*}
 \begin{split}
-	Pr(||A\vec{b}||_\infty > \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) > \mu + t)  \\
+	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
+		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
 		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
@@
 \begin{equation*}
-	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{n\log n})) \leq 1/n
+	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
 \end{equation*}
@@
 \begin{equation*}
-Pr(||A\vec{b}||_\infty > (d/2 + O(\sqrt{d\log n})) \leq 1/n
+Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
 \end{equation*}

### 2016-06-01 sec1_introduction.tex
Revise a bit
Do do do do ...

@@
 applications and it is cumbersome to design a tailored solution for each type. 
-In addition, existing pattern definitions are not expressive enough and may miss 
-interesting patterns or return noisy results. We summarize 
-the two scenarios as \emph{missing-pattern} anomaly
-and \emph{loose-connection} anomaly.
-A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
-As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
-neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
-$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
-the traffic control or the clustering inaccuracy at time $4$. On the other hand,
-the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
-the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
-the two objects $o_1, o_2$ form a \emph{platoon} pattern 
+As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns.
+However, we observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which introduce noisy results and unnecessary computations.
+We name this scenario as \emph{loose-connection} anomaly.
+To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern
 $\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
-making the co-moving behavior very weak.
-In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
+making the co-moving behavior very loose.
+In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
 such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
-It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.
+Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) is able to avoid such an anomaly directly.
+
+%In addition, existing pattern definitions are not expressive enough and may miss 
+%interesting patterns or return noisy results. We summarize 
+%the two scenarios as \emph{missing-pattern} anomaly
+%and \emph{loose-connection} anomaly.
+%A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
+%As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
+%neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
+%$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
+%the traffic control or the clustering inaccuracy at time $4$. On the other hand,
+%the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
+%the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
+%the two objects $o_1, o_2$ form a \emph{platoon} pattern 
+%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
+%making the co-moving behavior very weak.
+%In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
+%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
+%It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.
 
@@
 \includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
-\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
-in \emph{flock} and \emph{convoy}.
-When $K=4$, none of the two patterns can be discovered.
-(b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}.
-The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
+\caption{\emph{Loose-connection} anomaly.
+The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in \emph{platoon}, \emph{swarm} and \emph{group} results.}
 \label{fig:platoon_weakpoint}
@@
 various co-moment patterns in a unified way while avoids 
-the two identified anomalies. In GCMP, we gain a
+the \emph{loose-connection} anomaly. In GCMP, we gain a
 fine-grained control over pattern duration by introducing the gap 
@@
 which preserves the expressiveness while
-alleviates both the \emph{missing-pattern} and the \emph{loose connection} anomalies.
+alleviates the \emph{loose connection} anomalies.
 

### 2016-06-07 sec1_introduction.tex
Need to rewrite Section 4,5
According to Zhang's comments

@@
 applications and it is cumbersome to design a tailored solution for each type. 
-As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns.
-However, we observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which introduce noisy results and unnecessary computations.
+It is notable that \emph{platoon} pattern is able to represent other
+patterns by setting appropriate parameters. However, we observe
+that such a pattern definition, due to its overly-relaxed temporal constraints,
+loses the fine control of a pattern
+which leads to noisy results and unnecessary computations. We name this
+scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
+$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
+making the co-moving behavior very weak. In reality, 
+such an anomaly is likely induced by the periodic movements of unrelated objects 
+such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
+In fact, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) 
+are able to directly avoid such an anomaly.
+
+%As can be seen, there are various co-movement patterns requested by different 
+%applications and it is cumbersome to design a tailored solution for each type. 
+%As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns. However, we 
+%further observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which lead to noisy results and unnecessary computations.
 We name this scenario as \emph{loose-connection} anomaly.
 To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern
-$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
-making the co-moving behavior very loose.
-In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
-such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
-Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) is able to avoid such an anomaly directly.
+%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
+%making the co-moving behavior very loose.
+%In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
+%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
+Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) are able to directly avoid such an anomaly.
 
@@
 \caption{\emph{Loose-connection} anomaly.
-The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in \emph{platoon}, \emph{swarm} and \emph{group} results.}
+The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is valid in \emph{platoon}, \emph{swarm} and \emph{group} results.}
 \label{fig:platoon_weakpoint}
@@
 The other issue with existing methods is that they are 
-built on top of centralized indexes that are not scalable. 
+built on top of centralized indexes which face scalability challenges. 
 To the best of our knowledge, the maximum number of trajectories
-ever evaluated is up to hundreds of trajectories. 
-In practice, it is rather common to collect at least hundreds of thousands of trajectories 
-and their scalability is left unknown.
-We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns}) as well as an experimental evaluation with a real trajectory database including million-scale points(as shown in Figure~\ref{fig:related_work_scalability}).
-Results show that their performances degrade dramatically as the dataset size scales up. For instances,
-performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
-performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.5k} to \emph{2.4k}.
-It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which may include billion-scale points.
+ever evaluated is up to a million data points.
+In practice, it is rather common to collect hundreds of millions data points
+and the scalabilities of current solutions are left unknown. 
+We conduct a theoretical analysis on the worst-case complexity 
+(as listed in Table~\ref{tbl:existing_co_patterns}) as well as 
+an experimental evaluation with a real trajectory database 
+with upto 2.4 million points (as shown in Figure~\ref{fig:related_work_scalability}). 
+Results show that their performances degrade dramatically as the dataset scales up. For instances,
+the performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
+the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
+Therefore, directly applying these patterns on billion-scale real trajectories is impractical.
+
+%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
 %In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
@@
     \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
-    is used with over 2 million points.}
+    is used with up two 2.4 million data points.}
     \label{fig:related_work_scalability}

### 2016-06-09 sec1_introduction.tex
Some revisement
Section 4, Section 5 needs to merge

@@
 
-As can be seen, there are various co-movement patterns requested by different 
-applications and it is cumbersome to design a tailored solution for each type. 
-It is notable that \emph{platoon} pattern is able to represent other
-patterns by setting appropriate parameters. However, we observe
-that such a pattern definition, due to its overly-relaxed temporal constraints,
-loses the fine control of a pattern
-which leads to noisy results and unnecessary computations. We name this
-scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
-$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
-making the co-moving behavior very weak. In reality, 
-such an anomaly is likely induced by the periodic movements of unrelated objects 
-such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
-In fact, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) 
-are able to directly avoid such an anomaly.
+As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type.
+In addition, despite the generality of the \emph{platoon} (i.e., it can be reduced to other types of patterns via proper parameter settings), it suffers from the so-called \emph{loose-connection} anomaly.
+We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario.
+These two objects form a \emph{platoon} pattern in timestamps $\{1,2,3,102,103,104\}$.
+However, the two consecutive segments are $98$ timestamps apart, resulting in a false positive co-movement pattern.
+In reality, such an anomaly may be caused  by the periodic movements of unrelated objects, such as vehicles stopping at the same petrol station or animals pausing at the same water source.
+Unfortunately, none of the existing patterns have directly addressed this anomaly.
 
@@
 \caption{\emph{Loose-connection} anomaly.
-The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is valid in \emph{platoon}, \emph{swarm} and \emph{group} results.}
+Even though $\{o_1, o_2: 1,2,3,102,103,104\}$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
+% in \emph{platoon}, \emph{swarm} and \emph{group} results.
+}
 \label{fig:platoon_weakpoint}
@@
 
-The other issue with existing methods is that they are 
-built on top of centralized indexes which face scalability challenges. 
-To the best of our knowledge, the maximum number of trajectories
-ever evaluated is up to a million data points.
-In practice, it is rather common to collect hundreds of millions data points
-and the scalabilities of current solutions are left unknown. 
-We conduct a theoretical analysis on the worst-case complexity 
-(as listed in Table~\ref{tbl:existing_co_patterns}) as well as 
-an experimental evaluation with a real trajectory database 
-with upto 2.4 million points (as shown in Figure~\ref{fig:related_work_scalability}). 
-Results show that their performances degrade dramatically as the dataset scales up. For instances,
-the performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
+The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable.
+Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects.
+In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown.
+Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability.
+Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up.
+For instance,
+the detection time of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
 the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
-Therefore, directly applying these patterns on billion-scale real trajectories is impractical.
+These observations imply that existing methods are not scalable to support large-scale trajectory databases.
 
@@
 First, we propose the \emph{general co-movement pattern} (GCMP) which models
-various co-moment patterns in a unified way while avoids 
-the \emph{loose-connection} anomaly. In GCMP, we gain a
-fine-grained control over pattern duration by introducing the gap 
-parameter $G$, which enforces the gap between 
-timestamps to be no larger than $G$.  
-The adoption of $G$ seamlessly integrates with other pattern parameters,
-which preserves the expressiveness while
-alleviates the \emph{loose connection} anomalies.
+various co-moment patterns in a unified way and can avoid 
+the \emph{loose-connection} anomaly.
+In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments.
+By setting a feasible $G$, the loose-connection anomaly can be avoided.
+In addition, our GCMP is both general and expressive.
+It can be reduced to any of the previous patterns by customizing the parameters.
 
@@
 
-Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
-The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
-In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
-of the partitions. Such properties ensure that neither false-patterns 
-nor miss-patterns are possible in our solution. To meet such partition requirements
-as well as to keep the shuffle amount to a minimum, 
-we first design a naive \emph{Temporal Replication and Mining} (TRM)
-approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
-method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
-Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
-as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
-a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
-GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
-Despite the simpleness of star partition, we theoretically prove its optimality.
-Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
-shuffling and mining cost in SPM. 
+Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue.
+Our technical contributions are three-fold.
+First, we replicate the snapshots in multiple data chunks to support efficient parallel processing.
+Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance.
+For each star, an Apriori method is adopted to mine the co-movement patterns.
+Third, we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and
+\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.
+
+%
+%Second, we investigate on deploying our GCMP detector to facilitate scalable pattern mining.
+%In order to support large real trajectories, to the best of our knowledge, we
+%are the first to study GCMP mining in MapReduce (MR) systems. There are a
+%few challengers associated with designing an efficient MR-based pattern 
+%detection algorithms. 
+%
+%First, in order to support effective parallelism, we need
+%to partition the trajectory database with almost equal sizes. Our initial attempts
+%develops a temporal based partition approached named as 
+%\emph{Temporal Replication and Mining} (TRM). In TRM, neighboring snapshots form
+%a equal-sized partition such that co-movement patterns can be mined independently.
+%However, such a scheme require $O(|\mathbb{T}|)$ replication of input, which is 
+%inefficient for large-scale trajectories. To support efficient mining, 
+%we design a novel \emph{Star Partition and Mining} (SPM) approach which utilize
+%the potential co-movement relationship among objects.
+%
+%Our initial attempt develops a naive but effective 
+%\emph{Temporal Replication and Mining} (TRM) approach 
+%which requires to replicate entire data set $O(|\mathbb{T}|)$ times. Such a 
+%large set of
+
+%There
+%are a few challenges arises in designing the MR based pattern detection algorithm.
+%First, we
+
+%The major challenge
+%we face is to make proper data partitions such
+%that each partition can be efficiently processed independently. Our initial attempt develops
+%a naive but effective \emph{Temporal Replication and Mining} (TRM) approach which requires to replicate
+%entire data set $O(|\mathbb{T}|)$ times. To improve the efficiency, we design a novel \emph{Star Partition and Mining} (SPM)
+%algorithm. In SPM, potential co-moving objects are first grouped into partitions. Subsequently,
+%an apriori based method is applied to discover the patterns from each partition.
+%Despite the simpleness of the star partition, we theoretically prove its correctness
+%and optimality. Using SPM as the foundation, we develop and integrate
+%a series of optimization techniques including \emph{edge simplification}, \emph{candidate pruning}
+%and \emph{forward closure checking} to further boost the
+%performances.
+%
+
+%
+%Second, we investigate how to deploy our GCMP detector  on Spark for scalable pattern mining.
+%The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
+%In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
+%of the partitions. Such properties ensure that neither false-patterns 
+%nor miss-patterns are possible in our solution. To meet such partition requirements
+%as well as to keep the shuffle amount to a minimum, 
+%we first design a naive \emph{Temporal Replication and Mining} (TRM)
+%approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
+%method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
+%Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
+%as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
+%a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
+%GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
+%Despite the simpleness of star partition, we theoretically prove its optimality.
+%Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
+%shuffling and mining cost in SPM. 
 %Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
@@
 
-We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.
+We conduct a set of extensive experiments on XXX datasets with billion-scale trajectory points. The results show that XXX.
 
 The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
-trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}.
-Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.
+trajectory pattern mining.
+Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining.
+Section~\ref{sec:system_overview} provides an overview of our parallel architecture.
+Solutions to mining the general co-movement patterns are presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}.
+Section~\ref{sec:optimization} discusses various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to verify the usefulness and efficiency of our system.
+Finally Section~\ref{sec:conclusion} concludes the paper.

### 2016-06-09 sec4_system.tex
Some revisement
Section 4, Section 5 needs to merge

@@
-\section{Overview of Mining GCMP in Parallel}
-\label{sec:system_overview}
-We adapt the MapReduce paradigm for designing
-a parallel solution of mining GCMP. In this section,
-we briefly describe the preliminaries on MapReduce and then describe
-the overview of our framework in mining GCMP.
+\section{Temporal Replication and Mining}
+\label{sec:trm}
+We resort to the MapReduce (MR) paradigm for designing 
+a parallel solution in mining GCMP. It is straightforward 
+to partition the trajectory database into equal-sized 
+temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
+patterns may cross multiple temporal segments. In order to ensure
+the correctness of results, we need to guarantee that
+every valid patterns can be mined within at least 
+one partitions.
+Thus, some snapshots need to be 
+replicated several times in multiple partitions. This
+leads us to design the \emph{Temporal Replication and Mining}
+(TRM) algorithm.
 
-\subsection{Preliminary on MapReduce}
-MapReduce (MR) was formally proposed by Dean et.al.~\cite{dean2008mapreduce}
-and has subsequently implemented by many open source systems. Those systems
-provide handy APIs with fault tolerances and are popularly
-used as large-scale data processing platforms. 
-% become a ubiquitous parallel platform for large-scaled data processing. 
-%Current open source MapReduce systems provide handy programming APIs with fault tolerances
-%in backends. Such systems include Hadoop, Shark and Spark to name a few.
-In simple words, there are two conceptual types of computing nodes in MR,
-namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
-algorithm consists of three major steps: First, input data
-are partitioned and read by a \emph{map} function on each mapper. Then, mappers
-emit key-value pairs which are \emph{shuffle}d over the network to reducers. Lastly,
-reducers process the received data using a \emph{reduce} function.
+The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
+In brief, there are two pipeline MR jobs which further consist of four stages. 
+The first MR job is considered as a preprocessing, where input trajectories
+are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
+The output is shown as in Figure~\ref{fig:trm}(b). The second
+MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
+(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
+into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
+a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
+patterns from different partitions are then collected to form the output.
 
-Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
-First, since reducers are required to be independent, partitioning  
-data to fit the independence could be challenging. Second, since the \emph{shuffle}
-step requires network access, the data been shuffled should be minimized. 
-We take these concerns in consideration when designing our solutions for mining GCMP.
-%We would bare this concerns in designing our GCMP mining algorithm.
-%a natural
-%problem is how to partition the data in map and shuffle phase so that reducers 
-%achieve the independence.
-%
-%A critical question in designing a MapReduce algorithm is how to make 
-%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
-%requires data processed at each reducer to be independent.
-%
-%Since the \emph{shuffle} stage needs to transfer data over network, 
-%an important attention to pay during designing MapReduce an algorithm is 
-%to minimize the shuffle amounts and shuffle counts.
+\begin{figure*} [t]
+\center
+\includegraphics[width=\textwidth]{trm.eps}
+\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first MR job which computes the clusters at each snapshot; 
+(c)(d) correspond to the second MR job which uses TRM to mine GCMP in parallel.}
+\label{fig:trm}
+\end{figure*}
 
-\subsection{MapReduce Processing for Mining GCMP}
-Our GCMP mining process consists of two MR jobs as illustrated in Figure~\ref{fig:overview}.
-The first MR job is to cluster objects at each snapshot (i.e.,
- $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
-in map phase, trajectories are firstly reorganized by timestamps and object locations
-at the same timestamps form a snapshot. In reduce phase, clustering of objects at each
-snapshot is processed independently. The second MR job is to mine GCMPs from 
-clusters in each snapshot. We design and compare two MR algorithms (i.e., TRM and SPM)for 
-GCMP mining. Both the two algorithms would partition snapshots in map phase
-(as in Figure~\ref{fig:overview}(c))
-and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).
+Since in the first MR job, each partition contains only one snapshot
+for clustering, it is not necessary to replicate any snapshot. Thus, we
+focus on describing the second MR job which is the \emph{Temporal
+Replication and Mining} algorithm. We use $R$ to denote the replication factor.
+The outline of TRM is 
+shown in Algorithm~\ref{algo:trm_overview}.
 
-% corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
-%of the first job is to cluster trajectories based on snapshots (i.e.,).
-%As illustrated in (a), input trajectories are read in by mappers 
-%and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
-%form a snapshot. Then, a user defined clustering method is applied on the objects
-%in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. 
-%The second
-%MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
-%of the second job is to mine the GCMP from the snapshots computed in the first job. We design
-%two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
-%are first fed to mappers and different partition strategies may be selected to create
-%partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
-%The final computed results are then outputted to the end users.
+\begin{algorithm}
+\caption{Temporal Replication and Mining}
+\label{algo:trm_overview}
+\begin{algorithmic}[1]
+\Require list of $\langle t, S_t \rangle$ pairs
+\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
+\State {---Map Phase---}
+\label{code:trm-map-start}
+\ForAll{$\langle t, S_t \rangle$}
+	\ForAll{$i \in 1...R$}
+		\State emit a $\langle t-i, S_t \rangle$ pair
+	\EndFor  
+\EndFor
+\label{code:trm-map-end}
+\State {---Partition and Shuffle Phase---}
+\label{code:trm-par-start}
+\ForAll{$\langle t, S \rangle$ pair} 
+\State group-by $t$, emit a $\langle t, Par_t\rangle$
+\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
+\EndFor
+\label{code:trm-par-end}
+\State {---Reduce Phase---}
+\label{code:trm-red-start}
+\ForAll{$\langle t,Par_t \rangle$}
+\State lineSweepMining($Par_t$)
+\label{code:trm-red-end}
+\EndFor
+\end{algorithmic}
+\end{algorithm}
 
-Although we need two MR jobs to complete the GCMP mining task, 
-it is easy to pipeline the two jobs to exploit data locality.
-Specifically, the reducer output at step (b) can be directly reused 
-as the input to the mappers at step (c). Therefore we do not need to 
-transfer data between the two jobs. Modern MR platforms, especially Spark, have
-already supported such a kind of pipeline.
+As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
+three steps. First, in the map phase, each snapshot is keyed 
+with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
+Second, in the partition phase, every snapshot is grouped with its next 
+$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
+We will shortly discuss how the $R$ value is derived. 
+Third, in the reduce phase, a line sweeping method is invoked 
+to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
+It is easy to see that this method replicates a snapshots at most $R$ times.
+%\subsubsection{Temporal Replication Partition}
+The replication factor $R$ is critical for the performance of TRM.
+If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
+On the contrary, if $R$ is small, valid patterns may
+be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
+$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
+later the correctness of this value.
 
-\begin{figure} [t]
-\center
-\includegraphics[width=0.5\textwidth]{system_layout.eps}
-\caption{System flow of mining GCMP. (a)(b) correspond to the first MR job which compute the clusters at each snapshot; 
-(c)(d) correspond to the second MR jobs which mines GCMP in parrallel.}
-\label{fig:overview}
-\end{figure}
+%In the Algorithm~\ref{algo:trm_overview}, 
+%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
+%theorem, such a partition method is sound and complete.
+%\begin{theorem}[Soundness and Completeness of Replication]
+%\label{thm:replication_partition}
+%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
+%\end{theorem}
+%\begin{proof}
+%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
+%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
+%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
+%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$.
+Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$.
+Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$.
+This proves the completeness of the partitioning method.
+%\end{proof}
 
-We note that the first MR job is easy to design since each reducer only
-needs one snapshot for clustering.
-In contrast, it is challenging to design the second job. 
-This is because valid patterns may spray across multiple snapshots 
-or contain different object sets, where inappropriate partitioning
-of snapshots may fail to discover certain valid patterns.
-Formally, a valid partition strategy 
-needs to meet the following requirements: (a) the resulted partitions need
-to preserve enough information so that real patterns can be discovered in the reduce phase. 
-(b) the resulted partitions need to ensure that
-the patterns discovered in the reduce phase are valid patterns so that
-no further verification is required. We formalize these two 
+\subsection{Line Sweep Mining}
+Each task in the reduce phase processes a partition $Par_i$, which contains
+$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
+only the patterns whose object sets are contained in the first snapshot 
+are necessary to be reported. Therefore, we design a simple 
+\emph{line-sweep mining}(LSM) method for discovering
+GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.
+
+\begin{algorithm}
+\caption{Line Sweep Mining}
+\label{algo:line-sweep}
+\begin{algorithmic}[1]
+\Require $Par_t = \{S_t, S_{t+1}, ...\}$
+\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
+\For{$c \in S_t$} 
+\label{code:ls-init-start}
+\State $C$.add($\langle c, t \rangle $)
+\EndFor
+\label{code:ls-init-end}
+\ForAll{$i \in [1,R]$}
+\State $N \gets S_{t+i} \oplus C$ \label{code:ls-join}
+	\ForAll {$n \in N$}
+		\If{$|n.O| \geq M$}
+			$C$.add($n$).
+			\label{code:ls-add}
+		\EndIf
+	\EndFor
+\State{remove unqualified candidate from $C$}
+	\label{code:ls-remove}
+\EndFor
+\State{output qualified candidate in $C$}
+\end{algorithmic}
+\end{algorithm}
+
+The algorithm scans snapshots in a partition in sequence. During the scan, it
+maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
+The algorithm starts by inserting clusters at $S_i$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
+Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
+a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
+form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).
+
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=0.5\textwidth]{trm_process.eps}
+%\caption{Work flow of trajectory replication and mining}
+%\label{fig:trm_process}
+%\end{figure}
+
+\subsection{Correctness of TRM}
+We prove the correctness of TRM from two aspects. First,
+the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
+not miss out any valid patterns. Second, no false patterns
+are reported in any partitions. We formalize these two 
 properties as \emph{completeness} and \emph{soundness} as follows:
@@
 \begin{definition}[Completeness and Soundness]
-Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$.
+Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
+into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
+if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
+$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
+\end{definition}
+
+Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
+meets the \emph{soundness} and \emph{completeness} requirements.
+However, it burdens the network shuffle and limits the parallelism.
+We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
+the following theorem to state the correctness:
+
+\begin{theorem}[Correctness of Replication]
+\label{thm:replication_partition}
+Temporal replication partition is sound and complete.
+\end{theorem}
+\begin{proof}
+The soundness of partition can be observed from the fact 
+that each partition represents a consecutive segments of trajectories. 
+Therefore patterns in a partition can be directly mapped 
+back to original trajectories. For completeness, with a
+valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
+with the smallest length. Note that there could be many qualified $T'$s. 
+Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
+let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
+be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
+then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
+It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
+If every partition is of at least such a size, then $T'$ must be
+captured by at least one of the partition. Thus, the pattern $P$ would 
+be valid in that partition. This proves the completeness.
+\end{proof}
+
+\begin{example}
+We illustrate the entire TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
+In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
+$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
+for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
+Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
+As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
+are both $\{1,2,4\}$ which violate the $G$ constraint, 
+thus the two candidates are removed from $C_4$. After all snapshots are swept, 
+$\{o_3,o_4\}$ is the qualified pattern and is outputted.
+\end{example}
+
+The TRM approach though achieves good parallelism, 
+it requires to replicate the data multiple times. 
+Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
+In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
+Handling those cases is equivalent to replicate the entire snapshots to each partition, 
+which surrenders the benefit of parallelism.
+
+%IMPORTANT!!!
+%In contrast, it is challenging to design the second job. 
+%This is because valid patterns may spray across multiple snapshots 
+%or contain different object sets, where inappropriate partitioning
+%of snapshots may fail to discover certain valid patterns.
+%Formally, a valid partition strategy 
+%needs to meet the following requirements: (a) the resulted partitions need
+%to preserve enough information so that real patterns can be discovered in the reduce phase. 
+%(b) the resulted partitions need to ensure that
+%the patterns discovered in the reduce phase are valid patterns so that
+%no further verification is required. We formalize these two 
+%properties as \emph{completeness} and \emph{soundness} as follows:
+%
+%\begin{definition}[Completeness and Soundness]
+%Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$.
 $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t.
@@
 $\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
-\end{definition}
-The completeness ensures that no true patterns are missed out. 
-The soundness ensures that no false patterns are reported. 
-If a partition method is both sound and complete, then it can be used
-in the second MR job to facilitate GCMP mining.
-
-Apparently, replicating the entire trajectories to each 
-partition meets the \emph{soundness} and \emph{completeness} requirements. 
-However, it burdens the network shuffle and limits the parallelism. 
-Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
-In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
-we present a novel \emph{object-based} partition-and-mining method
-called \emph{Star Partition and Mining} (SPM) which resolves
-the deficiencies of TRM method.
+%\end{definition}
+%The completeness ensures that no true patterns are missed out. 
+%The soundness ensures that no false patterns are reported. 
+%If a partition method is both sound and complete, then it can be used
+%in the second MR job to facilitate GCMP mining.
+%
+%Apparently, replicating the entire trajectories to each 
+%partition meets the \emph{soundness} and \emph{completeness} requirements. 
+%However, it burdens the network shuffle and limits the parallelism. 
+%Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
+%In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
+%we present a novel \emph{object-based} partition-and-mining method
+%called \emph{Star Partition and Mining} (SPM) which resolves
+%the deficiencies of TRM method.

### 2016-06-09 sec6_spm.tex
Some revisement
Section 4, Section 5 needs to merge

@@
 under any pattern parameters, we propose 
-the \emph{Star Partition and Mining} (SPM) method. In SPM,
-we first design a novel object-based partition method named \emph{star partition}. 
-Then, we adapt an \emph{Apriori}-like 
-method to mine GCMP patterns out of each partition.
-The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
+the \emph{Star Partition and Mining} (SPM) method. 
+In SPM, we first design a novel object-based partition 
+method named \emph{star partition}. Then, we adapt
+an \emph{Apriori} method to mine GCMP patterns
+out of each partition.
+
+ The overview of the SPM method 
+is presented in Algorithm~\ref{algo:spm_overview}.
 As shown, the SPM method takes three phases. 
@@
 
-\subsubsection{Star Partition}
+\subsection{Star Partition}
 The intuition of the star partition is that, if two objects are part 
@@
 
-\begin{figure}[h]
+\begin{figure*}[t]
 \centering
-\includegraphics[width=0.4\textwidth]{spm.eps}
-\caption{Star partition and mining of trajectories in Figure~\ref{fig:related_work}}
+\includegraphics[width=0.9\textwidth]{spm.eps}
+\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
+(c) Apriori Mining with various pruning techniques.}
 \label{fig:star_partition}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsubsection{Apriori Mining}
+\subsection{Apriori Mining}
 In the mining phase, we need to find the patterns within each star. 

### 2016-06-10 sec6_spm.tex
Further changes
Also reorganizing

@@
 \label{sec:spm_solution}
-In order to achieve a good parallelism 
-under any pattern parameters, we propose 
-the \emph{Star Partition and Mining} (SPM) method. 
-In SPM, we first design a novel object-based partition 
-method named \emph{star partition}. Then, we adapt
-an \emph{Apriori} method to mine GCMP patterns
-out of each partition.
+TRM approach requires to replicate entire
+trajectories $O(|\mathbb{T}|)$ times, which is inefficient
+in parallelism. To overcome this limitation, we 
+propose the \emph{Star Partition and Mining} (SPM) method.
+In SPM, we design a graph model, named \emph{connection graph}, to capture 
+the co-moving behavior among objects. In such a way, 
+given an object $u$, all the objects potentially
+co-moved with $u$ are captured in $u$'s neighborhood, which
+forms a \emph{star} structure in graph terms. SPM utilizes
+such structures to partition objects and then adapts an Apriori 
+algorithm to discover true GCMPs from each partition.
 
- The overview of the SPM method 
-is presented in Algorithm~\ref{algo:spm_overview}.
-As shown, the SPM method takes three phases. 
-In the map phase, objects from the same cluster forms object-object pairs. 
-The object-object pairs are then paired up with the timestamp of 
-the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
-In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
-(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
-Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).
+The flow of SPM method is presented in Figure~\ref{fig:star_partition}.
+SPM utilizes the same preprocessing as TRM, thus the flow starts
+from clusters in each snapshot. Conceptually, the clusters 
+in each snapshot forms a graph as shown in Figure~\ref{fig:star_partition} (a).
+In the map phase of \emph{SPM}, a vertex together with its neighborhood 
+vertexes form a star. Every star is indeed an independent partition.
+Then, stars are shuffled to reducers. As in
+Figure~\ref{fig:star_partition} (c), Apriori mining algorithm is adapted
+to mine the GCMP patterns. The overview implementation of SPM is shown 
+in Algorithm~\ref{algo:spm_overview}.
+
+%The overview of the SPM method is presented in 
+%Algorithm~\ref{algo:spm_overview}. As shown, SPM takes three phases. 
+%In the map phase, objects from the same cluster form object-object pairs. 
+%The object-object pairs are then paired up with the timestamp of 
+%the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
+%In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
+%(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
+%Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).
 
@@
 of the same pattern, they must belong to the same cluster at 
-some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
+those snapshots. Therefore, we may link objects that belong to 
+the same cluster to form the \emph{connection graph}. Objects that are
 not connected surely fail to form a pattern. We may then
 partition the connection graph based on vertex connectivity
-s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
-as follows:
-\begin{definition}[Connection Graph and Star]
+such that mining GCMPs can be done in parallel. 
+We formally define the \emph{connection graph} as follows:
+\begin{definition}[Connection Graph]
 A connection graph is an undirected graph $G=(V:E)$, where 
 each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
-contains all the timestamps at which $s,t$ are in the same cluster,
+contains the timestamp sequence at which $s,t$ are in the same cluster,
 i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
-A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
-another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
+\end{definition}
+
+In graph theory, a \emph{star} of a vertex $u$ is the
+the set of neighborhood vertexes of $u$. To utilize \emph{star}
+partition, since a vertex may appear in multiple stars, 
+some replications of vertexes are required. In order to avoid replication 
+of edges, we use the \emph{directed star} as follows:
+
+\begin{definition}[Directed Star]
+Assign each vertex in $G$ an ID, a direct star of a vertex $s$, denoted as $Sr_s$, 
+is the set of incidental edges on $s$
+such that $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
 as the \emph{central vertex} of $Sr_s$.
@@
 
-It is notable that we require vertices in a star to be greater than its central vertex. This 
-effectively avoids replicating edges. \emph{Connection graph} and \emph{star} examples are 
+By leveraging the \emph{directed star}, we avoids replicating the edges. 
+A \emph{Connection graph} and \emph{star} examples are 
 shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
 based on the example in Figure~\ref{fig:related_work}.
-In (b), 5 stars are presented. It is easy to see that, by requiring the center vertex to be
-the smallest vertex in a star, there are no edges been replicated. In implementation,
-as stated in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
-comparison between vertices/objects are based on the vertex/object ID.
+In (b), 5 stars are presented. It can be figured out that by leveraging directed star, 
+no edges are replicated. In implementation,
+as show in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
+comparison between vertices/objects are based on the vertex/object IDs.
 
@@
 %are able to mine stars from the similar trajectory concepts.
-Although star partition is performed based on the object connections, each star
-can be effectively viewed as a subset of trajectories. To see this, each vertex
-in a star can be viewed as an object. The timestamps of center vertex $s$ is the
-union of all the edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
-edge $e(s,v)$. Therefore, we are able to define and mine GCMP on the stars. 
-Before describing the mining strategy, we first state in the following theorem that 
-the star-partition is complete and sound:
-\begin{theorem}[Soundness and Completeness of Star Partition]
-Star partition is sound and complete.
-\end{theorem}
-
-\begin{proof}
-For the soundness,
-if $P$ is a valid pattern in $Sr_s$, then at every time $t$, $\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
-By definition, $P$ is valid in the original trajectories.
-For the completeness,
-if $P$ is a valid pattern in original trajectories, let $s$ be the object with smallest ID in $P.O$. 
-Then by the definition of pattern, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
-\end{proof}
-
-Based on the above theorem, we can mine GCMP from each partition independently.
-It is notable that, in star partition, original data is replicated for $O(|\mathbb{O}|)$ times
-as each object may be sent to $O(|\mathbb{O}|)$ partitions. Since this complexity is free
-from pattern parameters, the star partition is more scalable than the temporal replication.
-In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
 
 \subsection{Apriori Mining}
-In the mining phase, we need to find the patterns within each star. 
-To systematically discover the patterns, we design the \emph{Apriori Mining} method which
-is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
-Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
-for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
-we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
-the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$.
-Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
-Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+To systematically discover valid patterns in each star, 
+we design the \emph{Apriori Mining} algorithm. 
+To describe the  algorithm, we call a candidate pattern $R$-pattern 
+if the size of its object set is $R$.  Therefore, each edge
+in the star is effectively a $2$-pattern. The intuition of Apriori mining
+is the observation that $(R+1)$-patterns can be generated
+from $R$-patterns and $2$ patterns. Thus, we may iteratively 
+enumerate pattern candidates with all possible sizes.
+In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
+During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
+with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
+generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
+each $R$-pattern contains the object $s$, thus the join only 
+grow a $R$-pattern at most to a $(R+1)$-pattern.
+Our mining algorithm stops where no further patterns are generated. 
+The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
 
@@
 
-It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
-are two major factors dragging down the performance. First, the size of $Sr_s$ affects
-the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
-sections, we exploit the property of GCMP to reduce the two factors.
+It is notable that, in star partition, original data is 
+replicated for $O(|\mathbb{O}|)$ times as each object may 
+be sent to $O(|\mathbb{O}|)$ stars. Since in reality, $|\mathbb{T}| \gg |\mathbb{O}|$, 
+the star partition is more scalable than the temporal replication.
+In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
+%It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
+%time to mine GCMP. There are two major factors dragging 
+%down the performance. First, the size of $Sr_s$ affects the initial 
+%size of $2$-patterns. Second, the candidates generated in each 
+%level affects the join performance. In later
+%sections, we exploit some properties of GCMP to reduce the two factors.
+
+\subsection{Analysis of SPM}
+The analysis of SPM contains two parts. We first prove the correctness
+of SPM. Then, we analyze the work load distribution of the star sizes.
+
+\subsubsection{Correctness}
+Although star partition is performed based on the connection graph, 
+each star is indeed a projection of original trajectories.
+To see this, each vertex can be viewed as an object. 
+The timestamps of center vertex $s$ is the union of all the 
+edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
+edge $e(s,v)$. Therefore, stars can be viewed as a trajectory
+database, where GCMP can be similarly defined. Using the same 
+notions as Definition 4, we state the correctness
+of star partition as follows:
+
+\begin{theorem}[Soundness and Completeness of Star Partition]
+Star partition is sound and complete.
+\end{theorem}
+
+\begin{proof}
+For the soundness,
+if $P$ is a valid pattern in $Sr_s$, then at every time $t$, 
+$\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
+By definition, $P$ is valid in the original trajectories.
+For the completeness,
+if $P$ is a valid pattern in original trajectories, 
+let $s$ be the object with smallest ID in $P.O$. 
+Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
+It follows that all object $o \in P.O$ are in $Sr_s$. 
+Furthermore, every timestamp in $P.T$ is included
+in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
+\end{proof}
+
+\subsubsection{Optimal Star Partition}
+An important concern in design parallel algorithms is 
+the distribution of work loads. Unlike TRM where each partition
+contains equal-sized snapshot, the size distribution 
+of stars remains SPM unknown. 
+Traditionally, the quality of a partition strategy 
+is measured based on two aspects: (1) the number of result partition, which
+affects the maximum parallelism
+(2) the balance of partition sizes, which affects the finishing
+time of a job. We notice that, in star partition, the total sizes of 
+stars are invariant. Therefore, the quality of a partition strategy
+can be formalized as the \emph{skewness}, which is the maximum star size
+among all stars. Smaller \emph{skewness} naturally results in more partitions
+and less imbalance.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{star-alt.eps}
+\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
+\label{fig:star-alt}
+\end{figure}
+
+Interestingly, we note that the \emph{skewness} of star partition is affected by
+the way the vertexes are numbered in the connection graph. For example,
+Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
+in the same connection graph, but produces two different set of stars. 
+The upper partitioning constructs four stars with the maximum star consisting of 5 edges.
+The lower partitioning constructs five stars with the maximum star consisting of 3 edges.
+Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
+lower one's \emph{skewness} is 3.
+
+Ideally we wish to find a numbering scheme of connection graph
+that minimize the \emph{skewness}.
+To quantify the objective, we design an linear algebra model as follows: Let $G$ denote a connection graph.
+Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
+Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$ (i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). Let vector $\vec{b}$
+be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} vector. Let $\vec{c} = A\vec{b}$, then
+each $c_i \in \vec{c}$ denotes the size of star for vertex $i$.
+Therefore, minimizing the \emph{skewness} can be formulated as follows:
+\begin{equation}
+\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+\end{equation}
+
+It is challenging to directly optimize the above equation. 
+First, suppose there are $n$ vertexes in $G$, enumerating
+all possible $\mathbb{A}$s leads to $n!$ combinations. 
+Such a high complexity is trivially unpractical. Second,
+since $G$ is only conceptual at runtime, 
+the load planning cannot be done beforehand. 
+Despite these challenges, we observe that there is a 
+$O(1)$ time solution which is good enough as stated in the 
+following theorem.
+
+\begin{theorem}[Balance of Star Partition]
+Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
+Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
+For any numbering, $\mathbb{A}$, with high probability, the 
+absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
+That is, it is very likely that 
+$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
+\end{theorem}
+
+\begin{proof}
+Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
+for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
+Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
+Let $d_i$ denote the degree of vertex $i$ in $G$. 
+It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
+Since in the star partition, each edge is assigned to the vertex
+with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
+\begin{equation*}
+a_{i,j} = \begin{cases}
+			e_{i,j}, i>j \\
+			0, otherwise
+		  \end{cases}  
+\end{equation*}
+There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
+$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
+$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
+
+By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
+is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
+we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
+$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
+\begin{equation*}
+\begin{split}
+	Pr(c_i \geq \mu + t) 
+						&\leq \exp(\frac{-2t^2}{n}) \\
+						&= \exp(-2\log n) = n^{-2}
+\end{split}
+\end{equation*}
+
+The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
+Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
+$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
+\begin{equation*}
+\begin{split}
+	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
+		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
+		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
+		& = n^{-1} = 1/n
+\end{split}
+\end{equation*}
+Substitute $t$ and $\mu$, we achieve the following concise form:
+\begin{equation*}
+	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
+\end{equation*}
+This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$.
+With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
+with probability greater than $(1-1/n)$, 
+the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
+\end{proof}
+
+In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
+the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
+equation holds:
+\begin{equation*}
+Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
+\end{equation*}

### 2016-06-10 sec7_optimization.tex
Some revisement
Section 4, Section 5 needs to merge
Further changes
Also reorganizing

--- 2016-05-14 sec7_optimization.tex
@@
-\section{Optimization}
+\section{Optimizing SPM}
 \label{sec:optimization}
-In this section, we describe several optimizations to the star-partition and mining algorithm.
-In addition, we also address some practical issues when deploying the SPM algorithm
-to real MapReduce based systems.
-
+It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
+time to mine GCMP. There are two major factors dragging 
+down the performance. First, the size of $Sr_s$ affects the initial 
+size of $2$-patterns. Second, the candidates generated in each 
+level affects the join performance.
+In this section, we describe several practical techniques to boost the performance
+of SPM.
 %We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
@@
 
-\subsection{Candidate Pruning}
-\subsubsection{Temporal monotonicity}
+\subsection{Temporal monotonicity}
 During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
@@
 
-\subsubsection{Forward closure checking}
+\subsection{Forward closure checking}
+Although leveraging \emph{temporal monotonicity} could largely prune false candidates and reduce
+the apriori search space, it is ineffective when a \textit{true} pattern exists. 
+For example, if a final pattern of a star $Sr_s$ is the \textit{union of all vertices} in the star, 
+then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
+each level $i$. This results in an exponential search space while
+the output only contains one pattern.  
+In general, when candidates at level $i$ collectively forms a true pattern, 
+running aprior produces many wasted candidates.
+
+Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
+we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
+all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
+\begin{theorem}[Forward Closure Checking Rule]
+Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
+if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
+and directly output $FC_i$.
+\end{theorem}
+
+\begin{proof}
+We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, let 
+$X=P.O - FC_i \neq \emptyset$.
+Consider a subset of $P$ which contains $X$ with size $i+1$, (i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$).
+Since $P$ is a proper pattern, then $P_1$ is also a proper pattern.
+Therefore $P_1 \in Lv_i$.
+Then it follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+\end{proof}
+
+It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
+reduces, thus the pruning power of $FC$ would be stronger.
+
+%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
+%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
+%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
+%all candidates. Then, the following \emph{forward closure checking} rule can be used:
+%
+%\begin{theorem}[Forward Closure Checking Rule]
+%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
+%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
+%$FC_i$ forms a valid GCMP .
+%\end{theorem}
 
 \begin{example}
-We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning.
-As shown, at the initial stage, $\{3,6:1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence.
-By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned.
-Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
+timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
 \end{example}
@@
 %With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
-\subsection{Load Balancing}
 
-\subsection{Duplication Detection}
-
-\subsection{Handling Overlapping Clusters}
+Induced by the Theorem 5, taking object IDs as the numbering (i.e., in Algorithm~\ref{algo:spm_overview})
+would be guaranteed to produce a partition which is almost optimal.
+%By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.
+%Taking expectation on both sides, we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
+Let $\mu =E[c_i] = d/2$, $\delta = \sqrt{12\log n/d}$, by Chernoff Bound,
+%the following holds:
+%\begin{equation*}
+%\begin{split}
+%	Pr(c_i \geq (1+ \delta)\mu) & \leq \exp(-\mu \delta^2 / 3) \\
+%						&= \exp(-d/2 \times 12 \log n / 3d ) \\
+%						&= \exp(-2\log n) = n^{-2}
+%\end{split}
+%\end{equation*}
+%
+%Next, since the event $\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu$ can be viewed as
+%$\cup_{c_i} (c_i > (1+ \delta)\mu )$, by Union Bound, we achieve the following:
+%\begin{equation*}
+%\begin{split}
+%	Pr(||A\vec{b}||_\infty > (1+ \delta)\mu)) &=Pr(\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu)  \\
+%		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq (1+ \delta)\mu) \\
+%		& = n^{-1} = 1/n
+%\end{split}
+%\end{equation*}
+%Substitute $\mu$ and $\delta$, we achieve the following concise form:
+%\begin{equation*}
+%	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{3 d\log n})) \leq 1/n
+%\end{equation*}
+%This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than $ O(\sqrt{d\log n})$ is $(1-1/n)$.
+Notice that $||A^*\vec{b}||_\infty \geq d/2$, therefore, with probability greater than $(1-1/n)$, the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{d\log n})$.
+%\end{proof} 
+%
+%Theorem 5 is powerful enough to induce the following lemma:
+%\begin{theorem}[Load Balance of Algorithm~\ref{algo:spm_overview}]
+%The partitioning in Algorithm~\ref{algo:spm_overview} differs at most $O(\sqrt{d\log |\mathbb{O}|})$ 
+%from optimal partitioning with probability $(1-1/|\mathbb{O}|)$.
+%\end{theorem}

### 2016-06-11 sec1_introduction.tex
Checkpoint
Saved algo part

@@
 \hline 
- & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
+Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
 \hline 
@@
 Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up.
-For instance,
-the detection time of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
-the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
+For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}.
+Similarly,
+the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
 These observations imply that existing methods are not scalable to support large-scale trajectory databases.
@@
             \includegraphics[width=\textwidth]{rw_perf_O.eps}
-		\subcaption{$1k$ objects}
+		\subcaption{$1k$ timestamps}
     \label{fig:fig1}
@@
             \includegraphics[width=\textwidth]{rw_perf_T.eps}
-         \subcaption{$1.2k$ timestamps}
+         \subcaption{$1k$ objects}
     \label{fig:fig2}
@@
     \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
-    is used with up two 2.4 million data points.}
+    is used with up two 2.4 million data points. Default parameters are $M=10$ $K=20$ $L=10$.}
     \label{fig:related_work_scalability}
@@
 Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining.
-Section~\ref{sec:system_overview} provides an overview of our parallel architecture.
-Solutions to mining the general co-movement patterns are presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}.
-Section~\ref{sec:optimization} discusses various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to verify the usefulness and efficiency of our system.
-Finally Section~\ref{sec:conclusion} concludes the paper.
+Section~\ref{sec:trm} provides a naive \emph{temporal replication and mining} solution.
+An advanced solution named
+\emph{star partition and mining} is presented in Section~\ref{sec:spm}.
+Section~\ref{sec:opt} discusses various optimization techniques.
+Section~\ref{sec:exp} conducts extensive experiments to verify the usefulness and efficiency of our system.
+Finally Section~\ref{sec:concl} concludes the paper.

### 2016-06-11 sec4_baseline.tex
Checkpoint
Saved algo part

--- 2016-06-09 sec4_system.tex
@@
 We resort to the MapReduce (MR) paradigm for designing 
-a parallel solution in mining GCMP. It is straightforward 
+a scalable parallel solution in mining GCMP. It is straightforward 
 to partition the trajectory database into equal-sized 
 temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
-patterns may cross multiple temporal segments. In order to ensure
-the correctness of results, we need to guarantee that
-every valid patterns can be mined within at least 
+patterns may cross multiple temporal segments. To ensure
+the correctness, we need to guarantee that
+every valid pattern can be mined within at least 
 one partitions.
@@
 Temporal replication partition is sound and complete.
-\end{theorem}
+\end{theorem}z
 \begin{proof}
@@
 \begin{example}
-We illustrate the entire TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
+We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
 In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 

### 2016-06-11 sec5_spm.tex
Checkpoint
Saved algo part

--- 2016-06-10 sec6_spm.tex
@@
 \section{Star Partition and Mining}
-\label{sec:spm_solution}
+\label{sec:spm}
 TRM approach requires to replicate entire
@@
 \ForAll{$e(s,t) = T \in Sr_s$}
-\State Ground.add($\langle \{s,t\}, T \rangle$);
-\State Lv $\gets$ Ground;
+\State{Simply $e(s,t)$} \Comment{Edge Simplification}
+\State {Ground.add($\langle \{s,t\}, T \rangle$)}
+\State {Lv $\gets$ Ground}
 \EndFor
-\While{true}
-	\If{Lv is not empty} 
-		\State{LvCand $\gets \{\}$ }
-		\ForAll{$cand_v \in Lv$}
-			\ForAll{$cand \in $Ground}
-				\State $p \gets cand_v$ join $cand$
-				\If{$p.T$ is a candidate sequence} 
-					\State LvCand.add($p$)
-				\EndIf
-			\EndFor
-		\EndFor
-		\If{$Lv$ is a pattern}
-			\State{Output.add($Lv$)}
-			\State{break}			 
-		\EndIf
-		\State {Lv $\gets$ LvCand}
-	\Else
+\While{Lv is not empty}
+		\State {Lv $\gets$ Lv $\oplus $ Ground}
+		\State {Remove false patterns in Lv}
+		\Comment{Temporal Monotonicity}
+		\If{union of Lv is a valid patter}
+			\State{output.add(Lv)} \Comment{Forward Closure}
 			\State{break}
@@
 An important concern in design parallel algorithms is 
-the distribution of work loads. Unlike TRM where each partition
-contains equal-sized snapshot, the size distribution 
-of stars remains SPM unknown. 
+the distribution of work loads.  
 Traditionally, the quality of a partition strategy 
@@
 affects the maximum parallelism
-(2) the balance of partition sizes, which affects the finishing
-time of a job. We notice that, in star partition, the total sizes of 
-stars are invariant. Therefore, the quality of a partition strategy
+(2) the size balance of partitions, which affects the finishing
+time of a job. Unlike TRM where each partition
+contains equal-sized snapshots, the size distribution 
+of stars in SPM remains unknown.
+Nevertheless, we notice that, in SPM, the total sizes of 
+stars are invariant. Therefore, the quality of a star partition
 can be formalized as the \emph{skewness}, which is the maximum star size
@@
 \centering
-\includegraphics[width=0.4\textwidth]{star-alt.eps}
+\includegraphics[width=0.5\textwidth]{star-alt.eps}
 \caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
@@
 Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
-in the same connection graph, but produces two different set of stars. 
-The upper partitioning constructs four stars with the maximum star consisting of 5 edges.
-The lower partitioning constructs five stars with the maximum star consisting of 3 edges.
+of the same connection graph, but produces two different set of stars. 
+The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
+The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
 Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
@@
 that minimize the \emph{skewness}.
-To quantify the objective, we design an linear algebra model as follows: Let $G$ denote a connection graph.
+To quantify, we use an linear algebra model as follows: 
+Let $G$ denote a connection graph.
 Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
-Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$ (i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). Let vector $\vec{b}$
-be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} vector. Let $\vec{c} = A\vec{b}$, then
-each $c_i \in \vec{c}$ denotes the size of star for vertex $i$.
+Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$
+(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). 
+Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
+vector. Let $\vec{c} = A\vec{b}$, then each $c_i \in \vec{c}$ 
+denotes the size of the star $Sr_i$.
 Therefore, minimizing the \emph{skewness} can be formulated as follows:
@@
 Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
-For any numbering, $\mathbb{A}$, with high probability, the 
+For an random numbering, $\mathbb{A}$, with high probability, the 
 absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
@@
 \begin{proof}
-Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
+Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
 for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
@@
 The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
-Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
+Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
 $\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
@@
 \end{equation*}
-Substitute $t$ and $\mu$, we achieve the following concise form:
+Substitute back $t$ and $\mu$, we achieve the following concise form:
 \begin{equation*}
@@
 \end{equation*}
+
+Utilizing Theorem 3, in SPM, it is safe to choose the object IDs as 
+the vertex number. This because in reality, object IDs are often 
+hashed and can be deemed as random.

### 2016-06-11 sec6_optimization.tex
Checkpoint
Saved algo part

--- 2016-06-10 sec7_optimization.tex
@@
 \section{Optimizing SPM}
-\label{sec:optimization}
-It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
-time to mine GCMP. There are two major factors dragging 
-down the performance. First, the size of $Sr_s$ affects the initial 
+\label{sec:opt}
+In Algorithm~\ref{algo:apriori_mining}, there are
+ two major factors affecting the performance.
+First, the edges in $Sr_s$ affects the initial 
 size of $2$-patterns. Second, the candidates generated in each 
 level affects the join performance.
-In this section, we describe several practical techniques to boost the performance
-of SPM.
+In this section, we describe several practical 
+techniques to boost the performance.
 %We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
@@
 which represents the co-occurrence of $s$ and $v$. We notice that the edge 
-between $s$ and $t$ is not always necessary. For example, if an edge has a
+between $s$ and $v$ is not always necessary. For example, if an edge has a
 cardinality less than $K$, it is unnecessary to include this edge to 
 $Sr_s$ since it cannot contribute to any patterns.
-This motivates us to simplify the edges in $Sr_s$ 
-to boost the overall performance.
+This motivates us to simplify the edges in $Sr_s$.
 
-Our goal of edge simplification is to, given a time sequence $T$, find a subsequence
-of $T' \subseteq T$, such that $T'$ is potentially conforms to $K,L,G$. And we
-wish $|T'|$ to be as small as possible.  
-We star-off by observing that for every time sequence $T$, $T$ can be 
-divided into a set of maximally $G$-connected subsequences. Note that
-a maximally $G$-connected subsequence can potentially contribute to
-a pattern if it conforms to $K,L$.
-Therefore, we are able to reduce $T$
-to its maximally $G$-connected subseuqnces which conform to $K,L$.
+Our intuition is thus to, remove the unnecessary timestamps among 
+the edges in a star, such that the valid patterns
+would not be affected. To realize this idea,
+we formally design the concept of \emph{candidate sequence} as follows:
 
-To formally describe the idea, we define the \emph{candidate sequence} as follows:
+\begin{definition}[Candidate Sequence]
+Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
+if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$. 
+\end{definition}
+For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
+not a candidate sequence since one of its maximal $2$-connected sequence $(9,10,11,13)$
+does not conform to $L$. In contrast, sequence $T_2=(1,2,4,5,6,8,9)$ is 
+a candidate sequence.
+
+Not that, although $T_1$ is not a candidate sequence, it can be simplified
+to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
+if it does not contain a \emph{candidate sequence}, then it cannot contribute
+to any valid patterns. In fact, only the candidate sequence inside $T$ affects
+the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
+a star. During the simplification, if an edge results in a candidate
+sequence of size zero, then it is removed from the star. Otherwise,
+the simplified edge is kept. By so doing, the size of the new star
+is much smaller.
+
+We design an efficient linear time algorithm for the simplification process.
+It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
+In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
+In the second round, the maximal $G$-connected sequences of size less than $K$ are
+removed. Clearly the simplification algorithm takes $O(T)$ time.
+
+%Our goal of edge simplification is to, given a time sequence $T$, find a 
+%subsequence of $T' \subseteq T$, such that $T'$ conforms to $K,L,G$. And we
+%wish $|T'|$ to be as small as possible.  
+%We star-off by observing that for every time sequence $T$, $T$ can be 
+%divided into a set of maximally $G$-connected subsequences. Note that
+%a maximally $G$-connected subsequence can potentially contribute to
+%a pattern if it conforms to $K,L$.
+%Therefore, we are able to reduce $T$
+%to its maximally $G$-connected subseuqnces which conform to $K,L$.
+
+%To formally describe the idea, we define the \emph{candidate sequence} as follows:
 
@@
 
-\begin{definition}[Candidate Sequence]
-Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
-if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$.
-\end{definition}
+%\begin{definition}[Candidate Sequence]
+%Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
+%if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$.
+%\end{definition}
+%
+%For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
+%not a fully candidate sequence since one of its maximal $G$-connected sequence $(9,10,11)$
+%is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
+%a fully candidate sequence.
 
-For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
-not a fully candidate sequence since one of its maximal $G$-connected sequence $(9,10,11)$
-is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
-a fully candidate sequence.
-
-To reduce a sequence $T$ to a candidate sequence, we need to strip out its 
-maximal $G$-connected subsequences which does not form to $K,L$. Such a reduction
-takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. In the 
-first round, the consecutive portions of $T$ with size less than $L$ are removed.
-In the second round, the maximal $G$-connected sequences of size less than $K$ are
-removed. Clearly the simplification algorithm runs in linear time.
 \begin{algorithm}
@@
 \Require $T$
-\State{---Remove the consecutive segment with size less than $L$---}
+\State{---$L$ Phase---}
 \State $c \gets 0$
 \For {$i \in (0,...,|T|)$}
-	\If{$T[i] - T[i-1] != 1$} 
+	\If{$T[i] - T[i-1] > 1$} 
 		\If{$i - c < L$} 
@@
 \EndFor
-\State{---Remove the $G$-connected segment with size less than $K$---}
+\State{---$G$-$K$ Phase---}
 \State $s\gets 1$, $c\gets 0$
@@
 In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
-is removed by $L=2$. $T_1$ has two maximal $G$-consecutive subsequences, which 
+is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
 are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
-from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$.
+from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
 \end{example}
@@
 
-By leveraging the edge simplification technique, 
-the size of the edges in $Sr_s$ can be greatly reduced. If
-an edge cannot be reduced to a candidate sequence, then it is directly removed from $Sr_s$.
-If an edge can be reduced to a candidate sequence, replacing itself 
-by the candidate sequence results in a more compact storage.
+%
+%By leveraging the edge simplification technique, 
+%the size of the edges in $Sr_s$ can be greatly reduced. If
+%an edge cannot be reduced to a candidate sequence, then it is directly removed from $Sr_s$.
+%If an edge can be reduced to a candidate sequence, replacing itself 
+%by the candidate sequence results in a more compact storage.
 
@@
 
-\subsection{Temporal monotonicity}
-During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
-of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
-hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
-a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
-we may form another monotonic property based on the \emph{candidate sequence} such that
-the Apriori algorithm could still benefit.
+\subsection{Temporal Monotonicity}
+In Apriori, we repeatedly join candidate patterns with different sizes.
+We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
+hold in GCMP mining. Specifically, given two candidates $P_1, P_2$, 
+if $P_1.O \subset P_2.O$ and $P_1$ is not a valid pattern, 
+then $P_2$ may or may not be a valid pattern. However, we notice that
+we may form another monotonic property based on the \emph{candidate sequence}.
 
-The intuition is that if a candidate $P_1.T$ cannot be reduce to a \emph{candidate sequence}, then $P_1$ cannot 
-be valid pattern. Furthermore, any candidate $P_2$, with $P_1.O \subset P_2.O$ cannot be a valid pattern.
-This \emph{temporal monotonic property} 
-is explicitly described as in the follow theorem:
+The intuition is that if a candidate $P_1.T$ cannot be simplified to 
+a \emph{candidate sequence}, then $P_1$ cannot be valid pattern. 
+Furthermore, any candidate $P_2$, with $P_1.O \subset P_2.O$ cannot be a valid pattern.
+This \emph{temporal monotonic property} is explicitly described as in the follow theorem:
 
-\begin{theorem}[Temporal Monotonic Property of GCMP]
-Given the temporal parameters $L,G,K$, for a candidate $c$ in Algorithm~\ref{algo:apriori_mining},
-if $c.T$ cannot be reduced to a candidate sequence, then for any candidate $c'$ with $c.O \subset c'.O$, $c'$ can be pruned.
+\begin{theorem}[Temporal Monotonicity]
+Given the temporal parameters $L,G,K$, for a candidate pattern $P$,
+if $P.T$ cannot be simplified to a candidate sequence,
+then, for any candidate $P'$ with $P.O \subseteq P'.O$, $P'$ cannot be a true pattern.
 \end{theorem}
 \begin{proof}
-Let $c_1$, $c_2$ be two candidates with $c_1.O \subset c_2.O$. It is easy to see that $c_1.T \supseteq c_2.T$.
-If $c_1.T$ cannot be reduced to a candidate sequence, then any subset of $c_1.T$ cannot
-be reduced. It follows that $c_2.T$ cannot be reduced neither. Thus,
-if $c_1.T$ cannot be reduced to a candidate sequence, $c_2$ can be pruned. 
+Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
+Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
+by proof of contradiction, any subset of $P_1.T$ cannot
+be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
+In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
 \end{proof}
@@
 \subsection{Forward closure checking}
-Although leveraging \emph{temporal monotonicity} could largely prune false candidates and reduce
-the apriori search space, it is ineffective when a \textit{true} pattern exists. 
-For example, if a final pattern of a star $Sr_s$ is the \textit{union of all vertices} in the star, 
+Although leveraging \emph{temporal monotonicity} could largely prune
+false candidates and reduce the apriori search space, 
+it is ineffective when a \textit{true} pattern exists. 
+In an extreme case, if a final pattern of a star $Sr_s$ is 
+the \textit{union of all vertices} in the star,
 then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
@@
 the output only contains one pattern.  
-In general, when candidates at level $i$ collectively forms a true pattern, 
+Generally, when candidates at level $i$ collectively forms a true pattern, 
 running aprior produces many wasted candidates.
@@
 all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
-\begin{theorem}[Forward Closure Checking Rule]
+\begin{theorem}[Forward Closure Checking]
 Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
@@
 \begin{proof}
-We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, let 
-$X=P.O - FC_i \neq \emptyset$.
-Consider a subset of $P$ which contains $X$ with size $i+1$, (i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$).
-Since $P$ is a proper pattern, then $P_1$ is also a proper pattern.
-Therefore $P_1 \in Lv_i$.
-Then it follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
+let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
+(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
+then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
+It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
 \end{proof}
@@
 It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
-reduces, thus the pruning power of $FC$ would be stronger.
-
+reduces, thus the pruning power of $FC$ would be stronger. We give hybrid example of the three
+optimization as follows:
 %To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
@@
 
-Induced by the Theorem 5, taking object IDs as the numbering (i.e., in Algorithm~\ref{algo:spm_overview})
-would be guaranteed to produce a partition which is almost optimal.
 %By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.

### 2016-06-13 sec4_baseline.tex
Some more updates
Fighting

@@
 \Require list of $\langle t, S_t \rangle$ pairs
-\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
+\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
 \State {---Map Phase---}
@@
 be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
-$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
+$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will show
 later the correctness of this value.
@@
 \subsection{Correctness of TRM}
-We prove the correctness of TRM from two aspects. First,
-the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
-not miss out any valid patterns. Second, no false patterns
-are reported in any partitions. We formalize these two 
+We prove the correctness of TRM from three aspects. First,
+setting $R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
+would not miss any valid patterns. Second, no false patterns
+are reported in any partitions. Third, the choice of $R$ is
+minimum. We formalize the first two 
 properties as \emph{completeness} and \emph{soundness} as follows:
@@
 Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
-meets the \emph{soundness} and \emph{completeness} requirements.
-However, it burdens the network shuffle and limits the parallelism.
-We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
-the following theorem to state the correctness:
+meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We prove in the following theorem 
+that the minimum $R$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
+to ensure the correctness:
 
-\begin{theorem}[Correctness of Replication]
+%We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
+%the following theorem to state the correctness:
+
+\begin{theorem}[Correctness of Temporal Replication]
 \label{thm:replication_partition}
-Temporal replication partition is sound and complete.
+The minimum $R$ to ensure sound and complete of the temporal replication 
+is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
 \end{theorem}z
@@
 Therefore patterns in a partition can be directly mapped 
-back to original trajectories. For completeness, with a
-valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
-with the smallest length. Note that there could be many qualified $T'$s. 
-Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
-let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
-be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
-then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
-It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
-If every partition is of at least such a size, then $T'$ must be
-captured by at least one of the partition. Thus, the pattern $P$ would 
-be valid in that partition. This proves the completeness.
+back to original trajectories. 
+For completeness, let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
+of a valid sequence $T$. Let $R$ be the upper bound for all $T'$s among 
+all possible valid sequence. It is easy to see that, under such a setting,
+any valid sequence would be captured by one of the partitions in temporal
+replication. This proves the completeness. Now, we compute the minimum value
+of $R$ as follows:
+$T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
+and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Therefore $R$ is formulated 
+as follows:
+\begin{equation}
+R = \max_{n} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
+\end{equation}
+With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
+$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
+(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
+validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
+Observe that, constraints (1)-(4) form a convex polygon and $R$ is monotone
+increasing wrt. $n$, the maximum value of $R$ is thus taken at the boundaries. Further
+observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
+conditions naturally derive
+$R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
+%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
+%with the smallest length. Note that there could be many qualified $T'$s. 
+%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
+%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
+%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
+%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
+%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
+%If every partition is of at least such a size, then $T'$ must be
+%captured by at least one of the partition. Thus, the pattern $P$ would 
+%be valid in that partition. This proves the completeness.
 \end{proof}
@@
 \begin{example}
-We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
+We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=3, L = 2, G=2$. 
 In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
-$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
+$(\lceil \frac{K}{L} \rceil-1) *G+2K - 2 = 4$. Then a line sweep method is performed in (d) 
 for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
@@
 As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
-are both $\{1,2,4\}$ which violate the $G$ constraint, 
+are both $\{1,2\}$ which violate the $G$ constraint, 
 thus the two candidates are removed from $C_4$. After all snapshots are swept, 

### 2016-06-13 sec7_experiment.tex
Checkpoint
Saved algo part
Some more updates
Fighting

--- 2016-05-28 sec8_experiment.tex
@@
 \section{Experimental Study}
-\label{sec:experiment}
+\label{sec:exp}
 \subsection{Implementation Issues}
 We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
-platform. Spark is one of the most popular MapReduce-like platform which
-uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. Since
-Spark directly supports the MapReduce paradigm, our algorithm is able to 
-be easily implemented in Spark. In order to help reproduce our experiments,
-we further address some implementation issues.
-\subsubsection{Task Assignment}
-In spark, each task in reduce phase is an Apriori mining phase of 
-a star.
-Although our star partition method is theoretically balanced, 
-it is still necessary to assign equal number of tasks to each executors. 
-Spark naturally uses hashing to partition data into tasks, where such
-a partitioning does not care on the tasks size. In order to
-fully utilize the clusters, it is important to perform a weight-aware
-partition. In our implementation, we collect the number of edges
-in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
-where we assign stars in decreasing order with their sizes and each star
-is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
-FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
-between map and reduce phase can be naturally implemented in Spark, where the 
-map result can be cached and the reduce phase can be paused until when the
-partition strategy is ready.
-
-\subsubsection{Duplication Detection}
-It is notable that the patterns discovered from different tasks (stars) could
-be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
-can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
-from the star $Sr_b$. Though in most applications, such a duplicate pattern
-is permitted, we offer an option to eliminate these patterns. The strategy is 
-to broadcast each reducers output to every other reducers. This can be
-efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
-whether any resulted patterns are subsumed and thus filter those patterns.
-Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
-deal with the duplication detection. However, as the number of final patterns are
-normally quit small, we leave the exploration for those techniques to the future.
-
-\subsubsection{Handling Overlapping Clusters}
-When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
-on objects are applied. Such a clustering method may result one object belonging to
-multiple clusters. In such a case, just keeping the timestamps in the edge
-of connection graph is insufficient. Instead, we extend every timestemp $t$
-to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
-belong to at time $t$. The only adaption we need to take the join during
-apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
-$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
-it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
-It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
-still holds under this new setting.
+platform. Spark is one of the most popular MapReduce platform which
+uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
+Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
+In order to help reproduce our experiments, we further address some implementation issues.
+%\subsubsection{Task Assignment}
+%In spark, each task in reduce phase is an Apriori mining phase of 
+%a star.
+%Although our star partition method is theoretically balanced, 
+%it is still necessary to assign equal number of tasks to each executors. 
+%Spark naturally uses hashing to partition data into tasks, where such
+%a partitioning does not care on the tasks size. In order to
+%fully utilize the clusters, it is important to perform a weight-aware
+%partition. In our implementation, we collect the number of edges
+%in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
+%where we assign stars in decreasing order with their sizes and each star
+%is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
+%FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
+%between map and reduce phase can be naturally implemented in Spark, where the 
+%map result can be cached and the reduce phase can be paused until when the
+%partition strategy is ready.
+%
+%\subsubsection{Duplication Detection}
+%It is notable that the patterns discovered from different tasks (stars) could
+%be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
+%can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
+%from the star $Sr_b$. Though in most applications, such a duplicate pattern
+%is permitted, we offer an option to eliminate these patterns. The strategy is 
+%to broadcast each reducers output to every other reducers. This can be
+%efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
+%whether any resulted patterns are subsumed and thus filter those patterns.
+%Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
+%deal with the duplication detection. However, as the number of final patterns are
+%normally quit small, we leave the exploration for those techniques to the future.
+%
+%\subsubsection{Handling Overlapping Clusters}
+%When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
+%on objects are applied. Such a clustering method may result one object belonging to
+%multiple clusters. In such a case, just keeping the timestamps in the edge
+%of connection graph is insufficient. Instead, we extend every timestemp $t$
+%to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
+%belong to at time $t$. The only adaption we need to take the join during
+%apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
+%$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
+%it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
+%It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
+%still holds under this new setting.
 
@@
 
-We setup HDFS on the same cluster and all trajectory data
-are initially stored in the HDFS. We prepare two set of
-large-scaled trajectories with the following properties:
+The clusters is managed by Yarn 2.7.1 and we use HDFS
+as the distributed storage. We prepare three real data
+set as follows:
+\begin{itemize}
+\item{Geolife}:
+\item{ACTShopping}:
+\item{SingTaxi}:
+\end{itemize}
+
+The summary of statistics are presented as in the following table:
+
+\begin{table}
+\center
+\caption{Statistics of data set}
+\begin{tabular}{|c|c|c|c|}
+\hline
+ & Geolife & ACTShopping & SingTaxi \\ 
+\hline 
+\# objects & a & a & a\\ 
+\hline
+\# timestamps & a & a & a\\ 
+\hline
+\# data points & a & a & a\\ 
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Effectiveness of GCMP}
+
+\subsection{Performance Comparison}
+\subsubsection{Effects of clusters $\epsilon$, $minPt$}
+\subsubsection{Effects of pattern parameters $M,L,K,G$}
+
+\subsection{SPM Analysis}
+\subsubsection{Load Balance}
+\subsubsection{Scalability}

### 2016-06-13 sec4_baseline.tex
Some updates
On sec4

@@
 a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
-patterns from different partitions are then collected to form the output.
+patterns from different partitions are then collected to form the final output.
 
@@
 
-Since in the first MR job, each partition contains only one snapshot
-for clustering, it is not necessary to replicate any snapshot. Thus, we
+In the first MR job, each partition contains only one snapshot
+for clustering, thus it is unnecessary to replicate any snapshots. Therefore, we
 focus on describing the second MR job which is the \emph{Temporal
-Replication and Mining} algorithm. We use $R$ to denote the replication factor.
+Replication and Mining} algorithm. We use $\eta$ to denote the replication factor.
 The outline of TRM is 
@@
 \Require list of $\langle t, S_t \rangle$ pairs
-\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
+\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
 \State {---Map Phase---}
@@
 Second, in the partition phase, every snapshot is grouped with its next 
-$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
-We will shortly discuss how the $R$ value is derived. 
+$\eta$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
 Third, in the reduce phase, a line sweeping method is invoked 
 to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
-It is easy to see that this method replicates a snapshots at most $R$ times.
-%\subsubsection{Temporal Replication Partition}
-The replication factor $R$ is critical for the performance of TRM.
-If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
-On the contrary, if $R$ is small, valid patterns may
+It is easy to see that this method replicates a snapshots at most $\eta$ times.
+The replication factor $\eta$ is critical for the performance of TRM.
+If the $\eta$ is large, the shuffle cost as well as the reduce cost would be high. 
+On the contrary, if $\eta$ is small, valid patterns may
 be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
-$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will show
-later the correctness of this value.
+$\eta$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will shortly show that this is the minimum $\eta$ to guarantee the correctness.
 
@@
 Each task in the reduce phase processes a partition $Par_i$, which contains
-$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
-only the patterns whose object sets are contained in the first snapshot 
-are necessary to be reported. Therefore, we design a simple 
+$\eta$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
+only the patterns whose object sets are contained in the first snapshot are necessary to be reported. Therefore, we design a simple 
 \emph{line-sweep mining}(LSM) method for discovering
@@
 \subsection{Correctness of TRM}
-We prove the correctness of TRM from three aspects. First,
-setting $R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
+We prove the correctness of TRM in three aspects. First,
+setting $\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
 would not miss any valid patterns. Second, no false patterns
-are reported in any partitions. Third, the choice of $R$ is
+are reported in any partitions. Third, the choice of $\eta$ is
 minimum. We formalize the first two 
@@
 if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
-$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
+$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $Tr$.
 \end{definition}
 
-Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
+Apparently, in TRM, replicating the entire trajectories (i.e., $\eta=\mathbb{|T|}$)
 meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We prove in the following theorem 
-that the minimum $R$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
+that the minimum $\eta$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
 to ensure the correctness:
@@
 \label{thm:replication_partition}
-The minimum $R$ to ensure sound and complete of the temporal replication 
+The minimum $\eta$ to ensure sound and complete of the temporal replication 
 is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
-\end{theorem}z
+\end{theorem}
 \begin{proof}
@@
 For completeness, let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
-of a valid sequence $T$. Let $R$ be the upper bound for all $T'$s among 
+of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
 all possible valid sequence. It is easy to see that, under such a setting,
@@
 replication. This proves the completeness. Now, we compute the minimum value
-of $R$ as follows:
-$T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
-and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Therefore $R$ is formulated 
+of $\eta$ as follows:
+any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
+and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
 as follows:
 \begin{equation}
-R = \max_{n} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
+\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
 \end{equation}
@@
 validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
-Observe that, constraints (1)-(4) form a convex polygon and $R$ is monotone
-increasing wrt. $n$, the maximum value of $R$ is thus taken at the boundaries. Further
+Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
+increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
 observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
 conditions naturally derive
-$R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
+$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
 %valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
@@
 Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
-As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
-are both $\{1,2\}$ which violate the $G$ constraint, 
-thus the two candidates are removed from $C_4$. After all snapshots are swept, 
-$\{o_3,o_4\}$ is the qualified pattern and is outputted.
+As line sweeps, at snapshot $3$, since the timestamps of  $\{o_5,o_6\}$ is $\{1\}$, which violates both the $L$,and $G$ constraints, this candidate is eliminated.
+At snapshot $4$, since the timestamps of $\{o_1,o_2\}$ is $\{1,2\}$, which violates the $L$ constraints, thus it is removed. Therefore, $\{o_3,o_4\}$ is the qualified pattern and is outputted.
 \end{example}
@@
 The TRM approach though achieves good parallelism, 
-it requires to replicate the data multiple times. 
-Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
-In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
-Handling those cases is equivalent to replicate the entire snapshots to each partition, 
+it requires to replicate the data $\eta$ times. 
+In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $\eta$ meeds to be as large as $|\mathbb{T}|$. 
+Handling those cases are equivalent to replicate the entire snapshots to each partition, 
 which surrenders the benefit of parallelism.

### 2016-06-18 appendix.tex
Need to update \eta
Need to describe \eta

--- 2016-06-09 sec6_spm.tex
@@
-\section{Star Partition and Mining}
-\label{sec:spm_solution}
-In order to achieve a good parallelism 
-under any pattern parameters, we propose 
-the \emph{Star Partition and Mining} (SPM) method. 
-In SPM, we first design a novel object-based partition 
-method named \emph{star partition}. Then, we adapt
-an \emph{Apriori} method to mine GCMP patterns
-out of each partition.
+\appendix
+\section{Proofs of Theorems}
+\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
+%\begin{proof}
+%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
+%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
+%all possible valid sequence. It is easy to see that, under such a setting,
+%any valid sequence would be captured by one of the partitions in temporal
+%replication. This proves the completeness. Now, we compute the minimum value
+%of $\eta$ as follows:
+%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
+%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
+%as follows:
+%\begin{equation}
+%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
+%\end{equation}
+%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
+%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
+%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
+%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
+%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
+%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
+%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
+%conditions naturally derive
+%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
+%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
+%%with the smallest length. Note that there could be many qualified $T'$s. 
+%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
+%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
+%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
+%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
+%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
+%%If every partition is of at least such a size, then $T'$ must be
+%%captured by at least one of the partition. Thus, the pattern $P$ would 
+%%be valid in that partition. This proves the completeness.
+%\end{proof}
 
- The overview of the SPM method 
-is presented in Algorithm~\ref{algo:spm_overview}.
-As shown, the SPM method takes three phases. 
-In the map phase, objects from the same cluster forms object-object pairs. 
-The object-object pairs are then paired up with the timestamp of 
-the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
-In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
-(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
-Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).
-
-\begin{algorithm}
-\caption{Star Partition and Mining}
-\label{algo:spm_overview}
-\begin{algorithmic}[1]
-\Require list of $\langle t, S_t \rangle$ pairs
-\State {---Map phase---}
-\label{code:spm-map-start}
-\ForAll{$C \in S_t$}
-	\ForAll {$(o_1 ,o_2) \in C \times C$}
-		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
-			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
-		\EndIf
-	\EndFor
-\EndFor
-\label{code:spm-map-end}
-
-\State {---Partition and Shuffle phase---}
-\label{code:spm-shuffle-start}
-\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
-	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
-	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
-\EndFor
-\label{code:spm-shuffle-end}
-
-\State {---Reduce phase---}
-\label{code:spm-reduce-start}
-\ForAll{$\langle o, Sr_{o} \rangle$}
-\State Apriori($Sr_o$)
-\EndFor
-\label{code:spm-reduce-end}
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Star Partition}
-The intuition of the star partition is that, if two objects are part 
-of the same pattern, they must belong to the same cluster at 
-some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
-not connected surely fail to form a pattern. We may then
-partition the connection graph based on vertex connectivity
-s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
-as follows:
-\begin{definition}[Connection Graph and Star]
-A connection graph is an undirected graph $G=(V:E)$, where 
-each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
-contains all the timestamps at which $s,t$ are in the same cluster,
-i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
-A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
-another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
-as the \emph{central vertex} of $Sr_s$.
-\end{definition}
-
-It is notable that we require vertices in a star to be greater than its central vertex. This 
-effectively avoids replicating edges. \emph{Connection graph} and \emph{star} examples are 
-shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
-based on the example in Figure~\ref{fig:related_work}.
-In (b), 5 stars are presented. It is easy to see that, by requiring the center vertex to be
-the smallest vertex in a star, there are no edges been replicated. In implementation,
-as stated in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
-comparison between vertices/objects are based on the vertex/object ID.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.9\textwidth]{spm.eps}
-\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
-(c) Apriori Mining with various pruning techniques.}
-\label{fig:star_partition}
-\end{figure*}
-
-%After computing the star, each partition is applied with a reduce task. 
-%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
-%This is done by treating each vertex in $Sr_s$ as an object. 
-%The time sequence of $s$ is the union of all edges in $Sr_s$. 
-%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
-%are able to mine stars from the similar trajectory concepts.
-Although star partition is performed based on the object connections, each star
-can be effectively viewed as a subset of trajectories. To see this, each vertex
-in a star can be viewed as an object. The timestamps of center vertex $s$ is the
-union of all the edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
-edge $e(s,v)$. Therefore, we are able to define and mine GCMP on the stars. 
-Before describing the mining strategy, we first state in the following theorem that 
-the star-partition is complete and sound:
-\begin{theorem}[Soundness and Completeness of Star Partition]
-Star partition is sound and complete.
-\end{theorem}
-
+\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
 \begin{proof}
-For the soundness,
-if $P$ is a valid pattern in $Sr_s$, then at every time $t$, $\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
-By definition, $P$ is valid in the original trajectories.
-For the completeness,
-if $P$ is a valid pattern in original trajectories, let $s$ be the object with smallest ID in $P.O$. 
-Then by the definition of pattern, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
+If $P$ is a valid pattern in original trajectories, 
+let $s$ be the object with smallest ID in $P.O$. 
+Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
+It follows that all object $o \in P.O$ are in $Sr_s$. 
+Furthermore, every timestamp in $P.T$ is included
+in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This completes the proof of Theorem~\ref{THM:SPM_CORRECT}.
+The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
+let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
+Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
+therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
 \end{proof}
 
-Based on the above theorem, we can mine GCMP from each partition independently.
-It is notable that, in star partition, original data is replicated for $O(|\mathbb{O}|)$ times
-as each object may be sent to $O(|\mathbb{O}|)$ partitions. Since this complexity is free
-from pattern parameters, the star partition is more scalable than the temporal replication.
-In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
+\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
+\begin{proof}
+Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
+for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
+Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
+Let $d_i$ denote the degree of vertex $i$ in $G$. 
+It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
+Since in the star partition, each edge is assigned to the vertex
+with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
+\begin{equation*}
+a_{i,j} = \begin{cases}
+			e_{i,j}, i>j \\
+			0, otherwise
+		  \end{cases}  
+\end{equation*}
+There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
+$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
+$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
 
-\subsection{Apriori Mining}
-In the mining phase, we need to find the patterns within each star. 
-To systematically discover the patterns, we design the \emph{Apriori Mining} method which
-is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
-Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
-for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
-we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
-the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$.
-Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
-Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
+is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
+we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
+$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
+\begin{equation*}
+\begin{split}
+	Pr(c_i \geq \mu + t) 
+						&\leq \exp(\frac{-2t^2}{n}) \\
+						&= \exp(-2\log n) = n^{-2}
+\end{split}
+\end{equation*}
 
-\begin{algorithm}
-\caption{Apriori Mining}
-\label{algo:apriori_mining}
-\begin{algorithmic}[1]
-\Require{$Sr_s$}
-\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State Ground.add($\langle \{s,t\}, T \rangle$);
-\State Lv $\gets$ Ground;
-\EndFor
-\While{true}
-	\If{Lv is not empty} 
-		\State{LvCand $\gets \{\}$ }
-		\ForAll{$cand_v \in Lv$}
-			\ForAll{$cand \in $Ground}
-				\State $p \gets cand_v$ join $cand$
-				\If{$p.T$ is a candidate sequence} 
-					\State LvCand.add($p$)
-				\EndIf
-			\EndFor
-		\EndFor
-		\If{$Lv$ is a pattern}
-			\State{Output.add($Lv$)}
-			\State{break}			 
-		\EndIf
-		\State {Lv $\gets$ LvCand}
-	\Else
-		\State{break}
-	\EndIf
-\EndWhile
-\State output.addAll($Lv$)
-\State \Return output
-\end{algorithmic}
-\end{algorithm}
+The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
+Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
+$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
+\begin{equation*}
+\begin{split}
+	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
+		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
+		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
+		& = n^{-1} = 1/n
+\end{split}
+\end{equation*}
+Substitute back $t$ and $\mu$, we achieve the following concise form:
+\begin{equation*}
+	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
+\end{equation*}
+This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$.
+With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
+with probability greater than $(1-1/n)$, 
+the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
+\end{proof}
 
-An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-higher level candidates are generated by joining lower level candidates. When no more candidates 
-can be generated, the algorithm stops by outputting the valid patterns.
+\subsection{Proof of Theorem~\ref{THM:SPM_TM}}
+\begin{proof}
+Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
+Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
+by proof of contradiction, any subset of $P_1.T$ cannot
+be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
+In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
+\end{proof}
 
-It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
-are two major factors dragging down the performance. First, the size of $Sr_s$ affects
-the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
-sections, we exploit the property of GCMP to reduce the two factors.
+\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
+\begin{proof}
+We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
+let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
+(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
+then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
+It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+\end{proof}

### 2016-06-18 sec4_baseline-bk.tex
Need to update \eta
Need to describe \eta

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
We resort to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining.
Since a GCMP pattern may cross multiple temporal segments, 
we cannot simply split the trajectory database into disjoint partitions and conduct parallel mining within each partition. Instead, we need certain data replication to guarantee that no matching patterns are missing.

We propose a framework named \emph{Temporal Replication and ParallelMining} (TRPM), 
as illustrated in Figure~\ref{fig:trm}. The mining procedure consists of 
two cycles of map-reduce jobs connected in a pipeline manner. In the first 
map-reduce cycle, input trajectories are grouped into snapshots and then clustered. 
In particular, object locations at the same timestamps form
a snapshot in the map-phase. In the reduce phase, objects in a snapshot
are clustered by the supplied clustering methods (e.g., DBSCAN or disk-based) in parallel.
The reducers finally output clusters of objects in each snapshot, 
represented by a list of $\langle t, S_t \rangle$ 
where $t$ is the timestamp and $S_t$ is a set of clustered object at snapshot $t$. 
The outputs will be fed into the second cycle of map-reduce jobs, whose details are presented in Algorithm~\ref{algo:trm_overview}. Intuitively, we first replicate each snapshot and each consecutive segment with $\eta$ snapshots is considered as one data partition. Then, a \emph{Line Sweeping} method is developed to discover GCMP within each partition in the reduce stage. The final patterns from all partitions are then stored into external storage (e.g, HDFS). In the following, we are interested to examine the minimum $\eta$ and introduce the \emph{Line Sweeping} algorithm in details.

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
\label{fig:trm}
\end{figure*}

\begin{algorithm}
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,\lambda_t \rangle$}
\State lineSweepMining($\lambda_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

%\subsection{Temporal Replication}
In temporal replication, every partition
contains $\eta$ consecutive snapshots.
Therefore, determining $\eta$ is critical in ensuring the
correctness and efficiency of TRPM.
If $\eta$ is too small, some cross-partition patterns may be missed out. 
On the other hand, if $\eta$ is too large, the shuffle and reduce
stage of TRPM would incur expensive costs.
To guarantee the \emph{complete} discovery of all patterns, we enforce the
following statement on $\eta$: \emph{Let $T'$ be the \emph{shortest} 
valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
Finding the \emph{minimum} $\eta$ is not
straightforward. We notice the minimum $\eta$ is related to the temporal
parameters $K,L,G$ by making the following observation on $G=1$:

\emph{
Let $T$ be an arbitrary valid temporal sequence. Since $G$ equals to 1,
$T$ can be represented as $T=(t_1, t_2,...,t_m)$, where
$t_i +1 = t_{i+1}$ and $m \geq K$. Let $T' = (t_1,...,t_k)$, $T'$ is the shortest
valid temporal sequence of $T$. Note that $T'$ is fully contained
in the partition $\lambda_{t_1} = \{S_{t_1},...,S_{t_k}\}$, therefore it can be
mined in $\lambda_{t_1}$. 
Since $T$ is an arbitrary valid temporal sequence, the minimum $\eta$ is thus $K$.
}

Inspired by the observation, we generalize the relationship between
the minimum $\eta$ and temporal parameters using the following theorem:
%
%
%Given any partition method, its correctness can be defined
%using \emph{completeness} and \emph{soundness} as follows: 
%
%\begin{definition}[Completeness and Soundness]
%Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
%into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
%if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
%$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $Tr$.
%\end{definition}

%Intuitively, \emph{soundness} avoids any false patterns in any partitions; while \emph{completeness}
%ensures no patterns are missed out by the partitions. In temporal replication, 
%the replication factor $\eta$ is critical. If $\eta$ is to small, such 
%partition may not be \emph{complete}. On the other hand, a large $\eta$ would incur
%expensive costs in the shuffle and reduce stages. Therefore, we need to find
%the \emph{minimum} $\eta$ such that the \emph{completeness} and \emph{soundness} are
%satisfied. Such an $\eta$ value is as stated in the following theorem:

\begin{theorem}
\label{THM:RP_ETA}
The minimum $\eta$ to ensure the completeness of the temporal replication is:
\[
   \eta = 
\begin{cases}
    (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2, & \text{if } G \geq 2\\
    K,              & \text{if } G = 1
\end{cases}
\]
, where $K,L,G$ are the temporal parameters.
\end{theorem}

\begin{proof}
When $G = 1$, we have demonstrated $\eta=K$
in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
as follows:
\begin{equation}
\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
where $g_i = G-1$, 
$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
\end{proof}

Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
form a partition. In particular, for every snapshot $S_t$, there is
a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. With this partition strategy,
when discovering GCMPS in $\lambda_t$, we only need to keep the pattern candidates whose
object set are in $S_t$. This motivates to design an efficient 
\emph{line-sweep} mining (LSM) method for each partition. The intuition of LSM is 
to sequentially scan all snapshots. During scanning, a set of pattern candidates is maintained.
When all snapshots are scanned, the remaining candidates are the true patterns.
The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
% To discover
%valid patterns from each partition, we design a \emph{line-sweep} mining (LSM) method as 
%shown in Algorithm~\ref{algo:line-sweep}. 
%The algorithm sequentially scans snapshots in a partition. 
%During the scan, it
A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
false patterns are deleted (line~\ref{code:ls-remove}). 
Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.

%It maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
%The algorithm starts by inserting clusters at $S_t$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
%Subsequently, when scanning $S_j$, clusters in $C$ are joined with clusters at $S_j$ to generate
%a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
%form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

%$\eta$ is firstly determined based on pattern parameters.
%In the map phase, $\eta$ snapshots form a partition, followed by the reduce phase where 
%the line sweep algorithm is applied on each partition.

%MOVE THE PROOF TO APPENDIX

%In the Algorithm~\ref{algo:trm_overview}, 
%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
%theorem, such a partition method is sound and complete.
%\begin{theorem}[Soundness and Completeness of Replication]
%\label{thm:replication_partition}
%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
%\end{theorem}
%\begin{proof}
%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$. This proves the completeness of the partitioning method.
%\end{proof}

%\subsection{Line Sweep Mining}
%Each job in the reduce phase handles a partition $\lambda_t$, 
%which contains $\eta$ snapshots starting from snapshot $S_t$. 
%We observe that within each partition, only the patterns whose object sets are contained in the first snapshot are necessary to be reported. %YOU CAN FORMALIZE THIS STATEMENT AS A LEMMA AND PROVIDES A RIGOROUS PROOF. 
%Therefore, we design a 
%\emph{line-sweep mining}(LSM) method in Algorithm~\ref{algo:line-sweep} to discover GCMPs. 
\begin{algorithm}
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\For{$c \in S_t$} 
\label{code:ls-init-start}
\State $C$.add($\langle c, t \rangle $)
\EndFor
\label{code:ls-init-end}
\ForAll{$j \in [t+1,t+\eta-1]$}
\State $C \gets S_{j} \oplus C$ \label{code:ls-join}
	\State{remove false candidates from $C$}
	\label{code:ls-remove}
\EndFor
\State{output true candidates in $C$}
\end{algorithmic}
\end{algorithm}

%\begin{figure}[h]
%\centering
%\includegraphics[width=0.5\textwidth]{trm_process.eps}
%\caption{Work flow of trajectory replication and mining}
%\label{fig:trm_process}
%\end{figure}

\begin{example}
We illustrate the work flow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
during sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns whose object set is in snapshot $S_1$.
As line sweeps, the patterns in $C_i$ grows. At snapshot $S_4$, the candidate
$\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$ constraint.
Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
because its local consecutive timestamps $\{4\}$ has only size $1$,
which violates the $L$ constraint.
Finally, $\{o_3,o_4\}$ is the qualified pattern and is outputted. Note that the minimum $\eta$
under this setting is $5$. If $\eta$ is chosen as $4$, the pattern $\{o_3,o_4\}$ would be excluded. 
\end{example}

%
%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
%When $\eta$ is small, TRM perform good parallelism. However, wh
%
%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
%%which surrenders the benefit of parallelism.
Although TRPM works in a parallel way, we observe two inefficiencies. First, the
performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
the parallel execution of line sweep algorithm may discover the same pattern from
multiple partitions, which introduces redundant work. To resolve the two limitations,
we design a novel \emph{Star Partition and Mining} algorithm.

### 2016-06-18 sec4_baseline.tex
Need to update \eta
Need to describe \eta

--- 2016-06-11 sec4_baseline.tex
@@
-\section{Temporal Replication and Mining}
+\section{Baseline: Temporal Replication and Parallel Mining}
 \label{sec:trm}
-We resort to the MapReduce (MR) paradigm for designing 
-a scalable parallel solution in mining GCMP. It is straightforward 
-to partition the trajectory database into equal-sized 
-temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
-patterns may cross multiple temporal segments. To ensure
-the correctness, we need to guarantee that
-every valid pattern can be mined within at least 
-one partitions.
-Thus, some snapshots need to be 
-replicated several times in multiple partitions. This
-leads us to design the \emph{Temporal Replication and Mining}
-(TRM) algorithm.
+In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining.
+The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
+There are two cycles of map-reduce jobs connected in a pipeline manner.
+The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining.
+In particular, the timestamp is treated as the key in the map phrase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phrase.
+Finally, the reducers output clusters of objects in each snapshot, represented by a list of $S_t$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
 
-The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
-In brief, there are two pipeline MR jobs which further consist of four stages. 
-The first MR job is considered as a preprocessing, where input trajectories
-are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
-The output is shown as in Figure~\ref{fig:trm}(b). The second
-MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
-(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
-into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
-a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
-patterns from different partitions are then collected to form the output.
+Our focus in this paper is the second map-reduce cycle of parallel mining, which essentially consists of two key questions to solve.
+The first is how to employ effective data partitioning such that the mining can be conducted independently; and the second is how to efficiently mine the valid patterns within each partition.
+
+It is obvious that we cannot simply split the trajectory database into disjoint partitions because a GCMP pattern requires $L$-consecutive and the corresponding segments may cross multiple partitions.
+Our strategy is to use data replication to enable parallel mining.
+Each snapshot will replicate its clusters to $\eta$ preceding snapshots.
+In other words, the partition for the snapshot $S_t$ contains clusters in $S_t$, $S_{t+1}\ldots,S_{t+\eta}$.
+Determining a proper $\eta$ is critical in ensuring the
+correctness and efficiency of TRPM.
+If $\eta$ is too small, certain cross-partition patterns may be missed.
+If $\eta$ is set too large, expensive network communication and CPU processing costs would be incurred in the map and reduce phrases respectively.
+
+To guarantee that no valid pattern is missing, we enforce the
+following statement on $\eta$:
+I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
+ \emph{Let $T'$ be the \emph{shortest} 
+valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
+Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
+Finding the \emph{minimum} $\eta$ is not
+straightforward. We notice the minimum $\eta$ is related to the temporal
+parameters $K,L,G$ by making the following observation on $G=1$:
 
@@
 \includegraphics[width=\textwidth]{trm.eps}
-\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first MR job which computes the clusters at each snapshot; 
-(c)(d) correspond to the second MR job which uses TRM to mine GCMP in parallel.}
+\caption{Work flow of Temporal Replication and Mining.
+(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
 \label{fig:trm}
@@
 
-Since in the first MR job, each partition contains only one snapshot
-for clustering, it is not necessary to replicate any snapshot. Thus, we
-focus on describing the second MR job which is the \emph{Temporal
-Replication and Mining} algorithm. We use $R$ to denote the replication factor.
-The outline of TRM is 
-shown in Algorithm~\ref{algo:trm_overview}.
+\emph{
+Let $T$ be an arbitrary valid temporal sequence. Since $G$ equals to 1,
+$T$ can be represented as $T=(t_1, t_2,...,t_m)$, where
+$t_i +1 = t_{i+1}$ and $m \geq K$. Let $T' = (t_1,...,t_k)$, $T'$ is the shortest
+valid temporal sequence of $T$. Note that $T'$ is fully contained
+in the partition $\lambda_{t_1} = \{S_{t_1},...,S_{t_k}\}$, therefore it can be
+mined in $\lambda_{t_1}$. 
+Since $T$ is an arbitrary valid temporal sequence, the minimum $\eta$ is thus $K$.
+}
 
-\begin{algorithm}
-\caption{Temporal Replication and Mining}
-\label{algo:trm_overview}
-\begin{algorithmic}[1]
-\Require list of $\langle t, S_t \rangle$ pairs
-\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
-\State {---Map Phase---}
-\label{code:trm-map-start}
-\ForAll{$\langle t, S_t \rangle$}
-	\ForAll{$i \in 1...R$}
-		\State emit a $\langle t-i, S_t \rangle$ pair
-	\EndFor  
-\EndFor
-\label{code:trm-map-end}
-\State {---Partition and Shuffle Phase---}
-\label{code:trm-par-start}
-\ForAll{$\langle t, S \rangle$ pair} 
-\State group-by $t$, emit a $\langle t, Par_t\rangle$
-\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
-\EndFor
-\label{code:trm-par-end}
-\State {---Reduce Phase---}
-\label{code:trm-red-start}
-\ForAll{$\langle t,Par_t \rangle$}
-\State lineSweepMining($Par_t$)
-\label{code:trm-red-end}
-\EndFor
-\end{algorithmic}
-\end{algorithm}
+Inspired by the observation, we generalize the relationship between
+the minimum $\eta$ and temporal parameters using the following theorem:
 
-As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
-three steps. First, in the map phase, each snapshot is keyed 
-with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
-Second, in the partition phase, every snapshot is grouped with its next 
-$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
-We will shortly discuss how the $R$ value is derived. 
-Third, in the reduce phase, a line sweeping method is invoked 
-to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
-It is easy to see that this method replicates a snapshots at most $R$ times.
-%\subsubsection{Temporal Replication Partition}
-The replication factor $R$ is critical for the performance of TRM.
-If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
-On the contrary, if $R$ is small, valid patterns may
-be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
-$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
-later the correctness of this value.
+\begin{theorem}
+\label{THM:RP_ETA}
+The minimum $\eta$ to ensure the completeness of the temporal replication is:
+\[
+   \eta = 
+\begin{cases}
+    (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2, & \text{if } G \geq 2\\
+    K,              & \text{if } G = 1
+\end{cases}
+\]
+, where $K,L,G$ are the temporal parameters.
+\end{theorem}
 
-%In the Algorithm~\ref{algo:trm_overview}, 
-%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
-%theorem, such a partition method is sound and complete.
-%\begin{theorem}[Soundness and Completeness of Replication]
-%\label{thm:replication_partition}
-%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
-%\end{theorem}
-%\begin{proof}
-%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
-%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
-%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
-%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$.
-Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$.
-Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$.
-This proves the completeness of the partitioning method.
-%\end{proof}
+\begin{proof}
+When $G = 1$, we have demonstrated $\eta=K$
+in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
+any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
+and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
+Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
+as follows:
+\begin{equation}
+\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
+\end{equation}
+With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
+$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
+(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
+validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
+Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
+Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
+increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
+where $g_i = G-1$, 
+$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
+and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
+\end{proof}
 
-\subsection{Line Sweep Mining}
-Each task in the reduce phase processes a partition $Par_i$, which contains
-$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
-only the patterns whose object sets are contained in the first snapshot 
-are necessary to be reported. Therefore, we design a simple 
-\emph{line-sweep mining}(LSM) method for discovering
-GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.
+Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
+form a partition. In particular, for every snapshot $S_t$, there is
+a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. With this partition strategy,
+when discovering GCMPS in $\lambda_t$, we only need to keep the pattern candidates whose
+object set are in $S_t$. This motivates to design an efficient 
+\emph{line-sweep} mining (LSM) method for each partition. The intuition of LSM is 
+to sequentially scan all snapshots. During scanning, a set of pattern candidates is maintained.
+When all snapshots are scanned, the remaining candidates are the true patterns.
+The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
+A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
+is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
+During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
+the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
+false patterns are deleted (line~\ref{code:ls-remove}). 
+Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
 
@@
 \begin{algorithmic}[1]
-\Require $Par_t = \{S_t, S_{t+1}, ...\}$
+\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
 \State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
@@
 \label{code:ls-init-end}
-\ForAll{$i \in [1,R]$}
-\State $N \gets S_{t+i} \oplus C$ \label{code:ls-join}
-	\ForAll {$n \in N$}
-		\If{$|n.O| \geq M$}
-			$C$.add($n$).
-			\label{code:ls-add}
-		\EndIf
-	\EndFor
-\State{remove unqualified candidate from $C$}
+\ForAll{$j \in [t+1,t+\eta-1]$}
+\State $C \gets S_{j} \oplus C$ \label{code:ls-join}
+	\State{remove false candidates from $C$}
 	\label{code:ls-remove}
 \EndFor
-\State{output qualified candidate in $C$}
+\State{output true candidates in $C$}
 \end{algorithmic}
 \end{algorithm}
-
-The algorithm scans snapshots in a partition in sequence. During the scan, it
-maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
-The algorithm starts by inserting clusters at $S_i$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
-Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
-a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
-form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).
 
@@
 
-\subsection{Correctness of TRM}
-We prove the correctness of TRM from two aspects. First,
-the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
-not miss out any valid patterns. Second, no false patterns
-are reported in any partitions. We formalize these two 
-properties as \emph{completeness} and \emph{soundness} as follows:
+The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}.
+We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
+parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
+as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
+in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
+into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
+method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
+during sweeping snapshot $S_i$.
+Initially, $C_1$ contains patterns whose object set is in snapshot $S_1$.
+As line sweeps, the patterns in $C_i$ grows. At snapshot $S_4$, the candidate
+$\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
+and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$ constraint.
+Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
+because its local consecutive timestamps $\{4\}$ has only size $1$,
+which violates the $L$ constraint.
+Finally, $\{o_3,o_4\}$ is the qualified pattern and is outputted. Note that the minimum $\eta$
+under this setting is $5$. If $\eta$ is chosen as $4$, the pattern $\{o_3,o_4\}$ would be excluded.
 
-\begin{definition}[Completeness and Soundness]
-Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
-into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
-if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
-$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
-\end{definition}
-
-Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
-meets the \emph{soundness} and \emph{completeness} requirements.
-However, it burdens the network shuffle and limits the parallelism.
-We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
-the following theorem to state the correctness:
-
-\begin{theorem}[Correctness of Replication]
-\label{thm:replication_partition}
-Temporal replication partition is sound and complete.
-\end{theorem}z
-\begin{proof}
-The soundness of partition can be observed from the fact 
-that each partition represents a consecutive segments of trajectories. 
-Therefore patterns in a partition can be directly mapped 
-back to original trajectories. For completeness, with a
-valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
-with the smallest length. Note that there could be many qualified $T'$s. 
-Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
-let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
-be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
-then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
-It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
-If every partition is of at least such a size, then $T'$ must be
-captured by at least one of the partition. Thus, the pattern $P$ would 
-be valid in that partition. This proves the completeness.
-\end{proof}
-
-\begin{example}
-We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
-In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
-$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
-for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
-Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
-As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
-are both $\{1,2,4\}$ which violate the $G$ constraint, 
-thus the two candidates are removed from $C_4$. After all snapshots are swept, 
-$\{o_3,o_4\}$ is the qualified pattern and is outputted.
-\end{example}
-
-The TRM approach though achieves good parallelism, 
-it requires to replicate the data multiple times. 
-Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
-In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
-Handling those cases is equivalent to replicate the entire snapshots to each partition, 
-which surrenders the benefit of parallelism.
-
-%IMPORTANT!!!
-%In contrast, it is challenging to design the second job. 
-%This is because valid patterns may spray across multiple snapshots 
-%or contain different object sets, where inappropriate partitioning
-%of snapshots may fail to discover certain valid patterns.
-%Formally, a valid partition strategy 
-%needs to meet the following requirements: (a) the resulted partitions need
-%to preserve enough information so that real patterns can be discovered in the reduce phase. 
-%(b) the resulted partitions need to ensure that
-%the patterns discovered in the reduce phase are valid patterns so that
-%no further verification is required. We formalize these two 
-%properties as \emph{completeness} and \emph{soundness} as follows:
-%
-%\begin{definition}[Completeness and Soundness]
-%Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$.
-$\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t.
-$P$ is valid in $Par_i$.
-$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
-%\end{definition}
-%The completeness ensures that no true patterns are missed out. 
-%The soundness ensures that no false patterns are reported. 
-%If a partition method is both sound and complete, then it can be used
-%in the second MR job to facilitate GCMP mining.
-%
-%Apparently, replicating the entire trajectories to each 
-%partition meets the \emph{soundness} and \emph{completeness} requirements. 
-%However, it burdens the network shuffle and limits the parallelism. 
-%Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
-%In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
-%we present a novel \emph{object-based} partition-and-mining method
-%called \emph{Star Partition and Mining} (SPM) which resolves
-%the deficiencies of TRM method.
+\begin{algorithm}
+\caption{Temporal Replication and Parallel Mining}
+\label{algo:trm_overview}
+\begin{algorithmic}[1]
+\Require list of $\langle t, S_t \rangle$ pairs
+\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
+\State {---Map Phase---}
+\label{code:trm-map-start}
+\ForAll{$\langle t, S_t \rangle$}
+	\ForAll{$i \in 1...{\eta-1}$}
+		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
+	\EndFor  
+\EndFor
+\label{code:trm-map-end}
+\State {---Partition and Shuffle Phase---}
+\label{code:trm-par-start}
+\ForAll{$\langle t, S \rangle$ pair} 
+\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
+\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
+\EndFor
+\label{code:trm-par-end}
+\State {---Reduce Phase---}
+\label{code:trm-red-start}
+\ForAll{$\langle t,\lambda_t \rangle$}
+\State lineSweepMining($\lambda_t$)
+\label{code:trm-red-end}
+\EndFor
+\end{algorithmic}
+\end{algorithm}

### 2016-06-18 sec5_spm.tex
Need to update \eta
Need to describe \eta

@@
 \label{sec:spm}
-TRM approach requires to replicate entire
-trajectories $O(|\mathbb{T}|)$ times, which is inefficient
-in parallelism. To overcome this limitation, we 
+To resolve the two limitations of TRM, we 
 propose the \emph{Star Partition and Mining} (SPM) method.
-In SPM, we design a graph model, named \emph{connection graph}, to capture 
+Instead of partition trajectory database in the temporal domain,
+SPM partition the trajectory database in the object domain.
+Specifically, we design a graph model, named \emph{connection graph}, to capture 
 the co-moving behavior among objects. In such a way, 
@@
 It is notable that, in star partition, original data is 
-replicated for $O(|\mathbb{O}|)$ times as each object may 
-be sent to $O(|\mathbb{O}|)$ stars. Since in reality, $|\mathbb{T}| \gg |\mathbb{O}|$, 
-the star partition is more scalable than the temporal replication.
-In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
+replicated at most $O(|\mathbb{O}|)$ times.
+In later sections, we will describe several 
+more optimization techniques to further reduce the amount of replicated data.
 %It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
@@
 \subsubsection{Correctness}
-Although star partition is performed based on the connection graph, 
-each star is indeed a projection of original trajectories.
-To see this, each vertex can be viewed as an object. 
-The timestamps of center vertex $s$ is the union of all the 
-edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
-edge $e(s,v)$. Therefore, stars can be viewed as a trajectory
-database, where GCMP can be similarly defined. Using the same 
-notions as Definition 4, we state the correctness
-of star partition as follows:
-
-\begin{theorem}[Soundness and Completeness of Star Partition]
-Star partition is sound and complete.
+An important concern in star partition is that
+whether any valid patterns are missed out by 
+such a partition. We assert the correctness by 
+the following theorem:
+\begin{theorem}[Correctness of Star Partition]
+\label{THM:SPM_CORRECT}
+Star partition is complete.
 \end{theorem}
 
-\begin{proof}
-For the soundness,
-if $P$ is a valid pattern in $Sr_s$, then at every time $t$, 
-$\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
-By definition, $P$ is valid in the original trajectories.
-For the completeness,
-if $P$ is a valid pattern in original trajectories, 
-let $s$ be the object with smallest ID in $P.O$. 
-Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. 
-Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
-\end{proof}
+In fact, besides that every valid patterns can be
+mined in some stars, star partition further ensures
+that patterns discovered
+from different star partitions cannot be the same. 
+This can be formulated as:
+
+\begin{lemma}[Unique Patterns in Star Partition]
+\label{LEM:SPM_CORRECT}
+Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two stars. Let $P_i$ (resp. $P_j$) be 
+the patterns discovered from $Sr_i$ (resp. $P_j$). 
+Then, $\forall p_i \in P_i, \forall p_j \in P_j, p_i.O \not\equiv p_j.O$.
+\end{lemma}
+
+This lemma indicates that every star partition discovers different patterns,
+thus less redundant work could exist as opposed to the line sweep method in TRM.
 
@@
 \begin{theorem}[Balance of Star Partition]
+\label{THM:SPM_LB}
 Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
@@
 absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
-That is, it is very likely that 
+That is, it is with probability $1-1/n$, 
 $||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
 \end{theorem}
-
-\begin{proof}
-Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
-for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
-Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
-Let $d_i$ denote the degree of vertex $i$ in $G$. 
-It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
-Since in the star partition, each edge is assigned to the vertex
-with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
-\begin{equation*}
-a_{i,j} = \begin{cases}
-			e_{i,j}, i>j \\
-			0, otherwise
-		  \end{cases}  
-\end{equation*}
-There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
-$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
-$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
-
-By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
-is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
-we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
-$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
-\begin{equation*}
-\begin{split}
-	Pr(c_i \geq \mu + t) 
-						&\leq \exp(\frac{-2t^2}{n}) \\
-						&= \exp(-2\log n) = n^{-2}
-\end{split}
-\end{equation*}
-
-The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
-Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
-$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
-\begin{equation*}
-\begin{split}
-	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
-		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
-		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
-		& = n^{-1} = 1/n
-\end{split}
-\end{equation*}
-Substitute back $t$ and $\mu$, we achieve the following concise form:
-\begin{equation*}
-	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
-\end{equation*}
-This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$.
-With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
-with probability greater than $(1-1/n)$, 
-the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
-\end{proof}
 

### 2016-06-18 sec6_optimization.tex
Need to update \eta
Need to describe \eta

@@
 \begin{theorem}[Temporal Monotonicity]
+\label{THM:SPM_TM}
 Given the temporal parameters $L,G,K$, for a candidate pattern $P$,
@@
 \end{theorem}
-\begin{proof}
-Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
-Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
-by proof of contradiction, any subset of $P_1.T$ cannot
-be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
-In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
-\end{proof}
 
@@
 \begin{theorem}[Forward Closure Checking]
+\label{THM:SPM_FCC}
 Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
@@
 \end{theorem}
-
-\begin{proof}
-We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
-let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
-(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
-then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
-It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
-\end{proof}
 

### 2016-06-18 sec7_experiment.tex
Need to update \eta
Need to describe \eta

@@
 \label{sec:exp}
-\subsection{Implementation Issues}
-We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
-platform. Spark is one of the most popular MapReduce platform which
-uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
-Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
-In order to help reproduce our experiments, we further address some implementation issues.
+%\subsection{Implementation Issues}
+%We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
+%platform. Spark is one of the most popular MapReduce platform which
+%uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
+%Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
+%In order to help reproduce our experiments, we further address some implementation issues.
 %\subsubsection{Task Assignment}
@@
 \subsection{Experimental Setup}
+We adapt one of the most popular MapReduce platform, Apache Spark, 
+to conduct experiments on mining GCMPs. 
 Our experiments run on a 9-node cluster, with Apache Yarn as
 the cluster manager. We use 1 node for Yarn resource manager, 
-and use the remaining 8 nodes as executors in Spark. In the 
-cluster, each node is uniformly equipped with a 2.2GHz quad-core CPU
-with 32 GB memory. Inter-node communication is carried by 
+and use the remaining 8 nodes as executors. Each node in the cluster
+is uniformly equipped with a 2.2GHz quad-core CPU with 32 GB memory. 
+Inter-node communication is carried by 
 the 1Gbps Ethernet.  Some critical configuration of Spark is 
@@
 
-The clusters is managed by Yarn 2.7.1 and we use HDFS
-as the distributed storage. We prepare three real data
-set as follows:
+We prepare three real datasets for study. The details of the datasets are as follows:
 \begin{itemize}
-\item{Geolife}:
-\item{ACTShopping}:
-\item{SingTaxi}:
+\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: contains 18,670 
+GPS trajectories for passengers in Beijing over three years. The data are collected per 1~5 seconds.
+We use linear interpretation for missing data in short-intervals (i.e., 5 seconds), since interpolating
+big intervals introduces large errors.
+\item{ACTShopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: contains visitors trajectories in ATC shopping center in Osaka from October 24, 2012 to November 29, 2013.
+There are in total 18670 trajectories, with 41 million data points.
+\item{SingTaxi}: contains 15,054 Singapore taxi trajectories in August 2012.
 \end{itemize}
@@
 
-\begin{table}
+\begin{table} [h]
 \center
 \caption{Statistics of data set}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|l|l|l|l|}
 \hline
@@
 \hline 
-\# objects & a & a & a\\ 
+\# objects & 18,670 & 13,183 & 15,054\\ 
 \hline
-\# timestamps & a & a & a\\ 
+\# average ts & 2,924 & 3,114 & 19,667 \\ 
 \hline
-\# data points & a & a & a\\ 
+\# longest ts & 17,281 & 24,407 & 43,717 \\
+\hline
+\# data points & 54,594,696 & 41,052,242 & 296,075,837\\ 
 \hline
@@
 
-\subsection{Effectiveness of GCMP}
+\begin{figure*}[t]
+\centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
+        \caption{Geolife}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
+        \caption{ACTShopping}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
+        \caption{SingTaxi}
+    \end{subfigure}
+\caption{Effectiveness of GCMP model on sampled datasets.}
+\label{exp:effectiveness}
+\end{figure*}
+
+\subsection{Effects of $G$ on GCMP}
+We study the effects of the gap parameter $G$ on discovering co-movement patterns. 
+As shown in Figure~\ref{fig:related_work_scalability},
+existing works are not able to handle large trajectories, we sample and cluster $1$ million  
+trajectory points from the three real data. We use two instances of GCMPs, GCMP-L where the
+$L$ value is default and GCMP where $L = 1$.  We measure the number
+of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
+
+We can see from Figures~\ref{exp:effectiveness} that the number of patterns
+discovered by GCMP is a positively related to $G$. When $G =1$, the number
+of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
+the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
+patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
+when $G$ is $50$. The reason is that when $G$ is large enough,
+ all consecutive segments in \emph{platoon} satisfy the $G$-connectivity. Similar
+ trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
+ patterns converge at $G=50$; while in (b) and (c) the two patterns converge
+ at $G=60$ and $G=40$ respectively. We further
+ note that, existing patterns has different granularity in temporal domain. As we seen
+ from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
+ \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
+ the temporal domain of patterns, GCMP can discover the patterns more precisely. 
+ These results confirms the usefulness of GCMP in expressing other patterns.
 
 \subsection{Performance Comparison}
-\subsubsection{Effects of clusters $\epsilon$, $minPt$}
+We now study the performance of our GCMP methods. We use TRPM as
+the baseline algorithm and implement SPM and SPM+.
+
+\begin{table}
+\begin{tabular}{c|c|l}
+\hline 
+\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
+\hline 
+M & min size of object set &  20, 40, \textbf{60},80,100 \\ 
+\hline 
+K & min duration & 60, 120, \textbf{180}, 240, 300 \\ 
+\hline 
+L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
+\hline 
+G & max gap & 5,10,\textbf{15},20,25 \\ 
+\hline 
+$\epsilon$ & DBSCAN parameter & 3,6,\textbf{9},12 \\ 
+\hline 
+minPt & DBSCAN parameter & 3,6,\textbf{9},12 \\ 
+\hline 
+\end{tabular} 
+\caption{Pattern Parameters and their default values.}
+\end{table}
+
+\subsubsection{Effects of clusters $\epsilon$, minPt}
 \subsubsection{Effects of pattern parameters $M,L,K,G$}

### 2016-06-19 appendix.tex
Except experiments
dan teng

@@
 \subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
-\begin{proof}
-If $P$ is a valid pattern in original trajectories, 
-let $s$ be the object with smallest ID in $P.O$. 
-Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. 
-Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This completes the proof of Theorem~\ref{THM:SPM_CORRECT}.
-The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
-let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
-Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
-therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
-\end{proof}
 
@@
 \begin{proof}
-Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
-for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
-Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
-Let $d_i$ denote the degree of vertex $i$ in $G$. 
-It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
-Since in the star partition, each edge is assigned to the vertex
-with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
+Let $B*$ be the assignment matrix wrt the optimal numbering.
+Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
+$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
+Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
+edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
+let $d_i$ denote the degree of vertex $i$, 
+then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
+vertexes does not affect the average degree.
+Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
 \begin{equation*}
-a_{i,j} = \begin{cases}
+b_{i,j} = \begin{cases}
 			e_{i,j}, i>j \\
@@
 \end{equation*}
-There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
-$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
-$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
+There are two observations made. First, since $e_{i,j}$s are independent,
+$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
+$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
 
-By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
+By definition, $c_i = \Sigma_{1\leq j \leq n} b_{i,j}$, 
 is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
-we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
+we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
+ Let $\mu =E[c_i] = d/2$, 
 $t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
@@
 
-The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
+The first step is due to the fact that all $b_{i,j}$ are bounded in the range of [0,1]. 
 Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
@@
 \begin{split}
-	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
+	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
 		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
@@
 \begin{equation*}
-	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
+	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
 \end{equation*}
-This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$.
-With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
+This indicates that, the probability of $(\Gamma-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
+With the fact that $\Gamma^* \geq d/2$, we conclude that
 with probability greater than $(1-1/n)$, 
-the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
+the difference between $\Gamma$ and $\Gamma^*$ is less than $O(\sqrt{n\log n})$.
+When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$), we may use
+the Chernoff Bound instead of Hoeffding's Inequality to derive a tighter bound of 
+$O(\sqrt{\log n}) $ with the similar reasoning.
 \end{proof}
 
-\subsection{Proof of Theorem~\ref{THM:SPM_TM}}
-\begin{proof}
-Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
-Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
-by proof of contradiction, any subset of $P_1.T$ cannot
-be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
-In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
-\end{proof}
+%\subsection{Proof of Theorem~\ref{THM:SPM_TM}}
+%\begin{proof}
+%Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
+%Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
+%by proof of contradiction, any subset of $P_1.T$ cannot
+%be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
+%In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
+%\end{proof}
 

### 2016-06-19 sec1_introduction.tex
Need to update \eta
Need to describe \eta
Except experiments
dan teng

@@
 For each star, an Apriori method is adopted to mine the co-movement patterns.
-Third, we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and
-\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.
+Third, we leverage the \emph{temporal monotonicity} property of GCMP to design several optimization techniques including \emph{edge-simplification} to prune initial candidates, \emph{temporal apriori pruning} and \emph{forward closure checking} to reduce the number of enumerated candidates in the Apriori algorithm.
+%
+%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
+%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.
 
-%
-%Second, we investigate on deploying our GCMP detector to facilitate scalable pattern mining.
-%In order to support large real trajectories, to the best of our knowledge, we
-%are the first to study GCMP mining in MapReduce (MR) systems. There are a
-%few challengers associated with designing an efficient MR-based pattern 
-%detection algorithms. 
-%
-%First, in order to support effective parallelism, we need
-%to partition the trajectory database with almost equal sizes. Our initial attempts
-%develops a temporal based partition approached named as 
-%\emph{Temporal Replication and Mining} (TRM). In TRM, neighboring snapshots form
-%a equal-sized partition such that co-movement patterns can be mined independently.
-%However, such a scheme require $O(|\mathbb{T}|)$ replication of input, which is 
-%inefficient for large-scale trajectories. To support efficient mining, 
-%we design a novel \emph{Star Partition and Mining} (SPM) approach which utilize
-%the potential co-movement relationship among objects.
-%
-%Our initial attempt develops a naive but effective 
-%\emph{Temporal Replication and Mining} (TRM) approach 
-%which requires to replicate entire data set $O(|\mathbb{T}|)$ times. Such a 
-%large set of
-
-%There
-%are a few challenges arises in designing the MR based pattern detection algorithm.
-%First, we
-
-%The major challenge
-%we face is to make proper data partitions such
-%that each partition can be efficiently processed independently. Our initial attempt develops
-%a naive but effective \emph{Temporal Replication and Mining} (TRM) approach which requires to replicate
-%entire data set $O(|\mathbb{T}|)$ times. To improve the efficiency, we design a novel \emph{Star Partition and Mining} (SPM)
-%algorithm. In SPM, potential co-moving objects are first grouped into partitions. Subsequently,
-%an apriori based method is applied to discover the patterns from each partition.
-%Despite the simpleness of the star partition, we theoretically prove its correctness
-%and optimality. Using SPM as the foundation, we develop and integrate
-%a series of optimization techniques including \emph{edge simplification}, \emph{candidate pruning}
-%and \emph{forward closure checking} to further boost the
-%performances.
-%
-
-%
-%Second, we investigate how to deploy our GCMP detector  on Spark for scalable pattern mining.
-%The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
-%In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
-%of the partitions. Such properties ensure that neither false-patterns 
-%nor miss-patterns are possible in our solution. To meet such partition requirements
-%as well as to keep the shuffle amount to a minimum, 
-%we first design a naive \emph{Temporal Replication and Mining} (TRM)
-%approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
-%method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
-%Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
-%as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
-%a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
-%GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
-%Despite the simpleness of star partition, we theoretically prove its optimality.
-%Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
-%shuffling and mining cost in SPM. 
-%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
-%Apache Spark which is one of the most popular MapReduce platforms.
-
-%we design a novel star-based partition scheme to efficiently partition objects based on their
-%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
-%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!
-
-We conduct a set of extensive experiments on XXX datasets with billion-scale trajectory points. The results show that XXX.
+We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
+temporal points. 
+The results show that our parallel scheme efficiently supports GCMP mining in large datasets.
+In particular, with near 200 million trajectory points, 
+our scheme runs within 10 minutes using 135 cores. Whereas centralized solution takes near 7 hours for 
+1 million trajectory points.
+Moreover, our optimized SPM methods achieves upto XXX times efficiency
+as compared to the baseline algorithm with near linear scalability.
 
@@
 Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining.
-Section~\ref{sec:trm} provides a naive \emph{temporal replication and mining} solution.
+Section~\ref{sec:trm} provides a baseline solution.
 An advanced solution named
@@
 Section~\ref{sec:opt} discusses various optimization techniques.
-Section~\ref{sec:exp} conducts extensive experiments to verify the usefulness and efficiency of our system.
+Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system.
 Finally Section~\ref{sec:concl} concludes the paper.

### 2016-06-19 sec5_spm-bk.tex
Except experiments
dan teng

--- 2016-06-18 sec5_spm.tex
@@
 \subsubsection{Optimal Star Partition}
-An important concern in design parallel algorithms is 
-the distribution of work loads.  
-Traditionally, the quality of a partition strategy 
-is measured based on two aspects: (1) the number of result partition, which
-affects the maximum parallelism
-(2) the size balance of partitions, which affects the finishing
-time of a job. Unlike TRM where each partition
-contains equal-sized snapshots, the size distribution 
-of stars in SPM remains unknown.
-Nevertheless, we notice that, in SPM, the total sizes of 
-stars are invariant. Therefore, the quality of a star partition
-can be formalized as the \emph{skewness}, which is the maximum star size
-among all stars. Smaller \emph{skewness} naturally results in more partitions
-and less imbalance.
+An important concern in designing a partition 
+algorithm is the skewed execution times for
+each partition. If there are partitions
+taking significant long time to execute, they would become
+the bottleneck of the entire system. Such long time-taken partitions
+are referred as \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}. In TRPM, where
+each partition contains a equal-sized snapshots, the \emph{straggler}
+is not a concern. However, in SPM, the size distribution of
+stars remains unknown. It is necessary to analyze the 
+distribution of SPM workloads. We use $\Gamma$ to indicate
+the size of \emph{straggler} in star partition. Intuitively,
+a large $\Gamma$ means the system has a more prominent bottleneck. 
+And smaller $\Gamma$ is always preferred.
+
+% As we shown in Algorithm~\ref{algo:apriori_mining},
+%the running time of a star partition is correlated with the number of edges.
+%Therefore, we use the number of edges to measure the \emph{straggler}, where
+%the \emph{straggler} refers to the largest star. W.L.O.G, we use $\Gamma$ to
+%denote the size of the \emph{straggler}. Intuitively, a large $\Gamma$ indicates
+%a large straggler
+
+%
+%We use the conventional indicator \emph{straggler} to analyze the distribution of SPM, where 
+%the \emph{straggler} is determined by the largest size of stars 
+%in the SPM. Intuitively, a large \emph{straggler}
+
+%An important concern in design 
+%the distribution of work loads. 
+%Traditionally, the quality of a partition strategy 
+%is measured based on two aspects: (1) the number of result partition, which
+%affects the maximum parallelism
+%(2) the size balance of partitions, which affects the finishing
+%time of a job. 
+%
+%Unlike TRM where each partition
+%contains equal-sized snapshots, the size distribution 
+%of stars in SPM remains unknown. To formally analyze
+%the distribution of SPM workloads, we use the concept 
+%of \emph{strangler}
+
+%Nevertheless, we notice that, in SPM, the total sizes of 
+%stars are invariant. Therefore, the quality of a star partition
+%can be formalized as the \emph{skewness}, which is the maximum star size
+%among all stars. Smaller \emph{skewness} naturally results in more partitions
+%and less imbalance.
 
@@
 
-Interestingly, we note that the \emph{skewness} of star partition is affected by
-the way the vertexes are numbered in the connection graph. For example,
+Interestingly, we note that the size of \emph{straggler} (i.e., $\Gamma$) 
+of star partition is affected by
+the way the vertexes are numbered in the aggregate graph. For example,
 Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
-of the same connection graph, but produces two different set of stars. 
+of the same aggregate graph, but produces two different set of stars. 
 The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
 The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
-Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
-lower one's \emph{skewness} is 3.
+Apparently the upper partitioning is inferior because its $\Gamma$ is 5 while the
+lower one's $\Gamma$ is 3.
 
-Ideally we wish to find a numbering scheme of connection graph
-that minimize the \emph{skewness}.
+Ideally we wish to find a numbering scheme of aggregate graph
+that minimize the size of straggler, (i.e, $\Gamma$).
 To quantify, we use an linear algebra model as follows: 
-Let $G$ denote a connection graph.
-Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
-Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$
-(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). 
-Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
-vector. Let $\vec{c} = A\vec{b}$, then each $c_i \in \vec{c}$ 
-denotes the size of the star $Sr_i$.
-Therefore, minimizing the \emph{skewness} can be formulated as follows:
+Let $G$ be an aggregate graph, with a $n \times n$ adjacent matrix $A$.
+A numbering scheme is in fact a permutation of $A$. Therefore,
+the adjacent matrix of a numbered graph can be represented as $PAP^T$
+where $P \in \mathbb{P}$ is a 
+\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
+Since in SPM we assign each edge $e(i,j)$ to the lower vertex, 
+then the matrix $B=\text{triu}(PAP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+%Let $P \in \mathbb{P}$ be a \emph{permutation matrix} with dimension $n$.
+%Then numbering with $P$ generates an adjacent matrix $B = PAP^T$.
+%Let $\mathbb{A}$ be
+%the set of all numbering schemes. A numbering scheme
+%$A \in \mathbb{A}$ is a boolean assignment matrix 
+%(i.e., $a_{i,j} \in A $ indicates whether vertex $j$ is included in $Sr_i$. Apparently, $a_{i,j} \neq a_{j,i}$).
+%%Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
+%Given a numbering scheme, let $(A:a_{i,j})$ be a boolean assignment matrix
+%(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$).
+Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+vector. Let $\vec{c} = B\vec{b}$, then each $c_i \in \vec{c}$ 
+denotes the size of the star $Sr_i$. Thus, $\Gamma$ can be represented
+as the infinity norm of $B\vec{b}$. The minimum size of straggle, $\Gamma^*$
+can then be formulated as follows:
 \begin{equation}
-\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
 \end{equation}
@@
 It is challenging to directly optimize the above equation. 
-First, suppose there are $n$ vertexes in $G$, enumerating
-all possible $\mathbb{A}$s leads to $n!$ combinations. 
+First, suppose there are $n!$ permutation matrices. 
 Such a high complexity is trivially unpractical. Second,
-since $G$ is only conceptual at runtime, 
+since $G$ is unknown in prior,
 the load planning cannot be done beforehand. 
@@
 \label{THM:SPM_LB}
-Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
-Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
-For an random numbering, $\mathbb{A}$, with high probability, the 
-absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
-That is, it is with probability $1-1/n$, 
-$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
+Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
+Let $\Gamma^*$ be optimal size of straggler.
+Let $\Gamma$ be the size of straggler wrt an random numbering $P$. 
+With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
+That is,  with probability $1-1/n$, 
+$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
 \end{theorem}
 
-In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
-the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
-equation holds:
-\begin{equation*}
-Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
-\end{equation*}
-
-Utilizing Theorem 3, in SPM, it is safe to choose the object IDs as 
+In fact, we have a tighter bound of $\Gamma - \Gamma^*$ if 
+the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
+high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
+Utilizing Theorem~\label{THM:SPM_LB}, in SPM, it is safe to choose the object IDs as 
 the vertex number. This because in reality, object IDs are often 

### 2016-06-19 sec5_spm.tex
Except experiments
dan teng

@@
-\section{Star Partition and Mining}
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.9\textwidth]{spm.eps}
+\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
+(c) Apriori Mining with various pruning techniques.}
+\label{fig:star_partition}
+\end{figure*}
+
+\section{SPARE: Star Partitioning and Apriori Enumerator}
 \label{sec:spm}
-To resolve the two limitations of TRM, we 
-propose the \emph{Star Partition and Mining} (SPM) method.
-Instead of partition trajectory database in the temporal domain,
-SPM partition the trajectory database in the object domain.
-Specifically, we design a graph model, named \emph{connection graph}, to capture 
-the co-moving behavior among objects. In such a way, 
-given an object $u$, all the objects potentially
-co-moved with $u$ are captured in $u$'s neighborhood, which
-forms a \emph{star} structure in graph terms. SPM utilizes
-such structures to partition objects and then adapts an Apriori 
-algorithm to discover true GCMPs from each partition.
+The aforementioned replicate partitioning is based on the temporal dimension 
+and results in groups of snapshots in each partition. 
+To resolve the limitations caused by the replicate partitioning, 
+we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
+to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
+Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
+Its input is the set of clusters generated in each snapshot and the output 
+are mined GCMP patterns. In the following, we explain the two major components: 
+star partitioning and apriori enumerator.
 
-The flow of SPM method is presented in Figure~\ref{fig:star_partition}.
-SPM utilizes the same preprocessing as TRM, thus the flow starts
-from clusters in each snapshot. Conceptually, the clusters 
-in each snapshot forms a graph as shown in Figure~\ref{fig:star_partition} (a).
-In the map phase of \emph{SPM}, a vertex together with its neighborhood 
-vertexes form a star. Every star is indeed an independent partition.
-Then, stars are shuffled to reducers. As in
-Figure~\ref{fig:star_partition} (c), Apriori mining algorithm is adapted
-to mine the GCMP patterns. The overview implementation of SPM is shown 
-in Algorithm~\ref{algo:spm_overview}.
+\subsection{Star Partitioning}
+Let $G_t$ be a graph for snapshot $S_t$, in which each node 
+is a moving object and two objects are connected if they appear 
+in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
+Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
+cluster relationship among all the snapshots. In $G_A$, two objects
+form an edge if they are connected in any $G_t$s. Furthermore, 
+we attach an inverted list for each edge, 
+storing the associated timestamps in which the two objects are connected. 
+An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
+is shown in Figure~\ref{fig:star_partition} (a). 
+As long as two objects are clustered in any timestamp, they are connected in $G_A$. 
+The object pair $(o_1,o_2)$ appears in two clusters at timestamps 
+$2$ and $3$ and is thus associated with an inverted list $\{2,3\}$.
 
-%The overview of the SPM method is presented in 
-%Algorithm~\ref{algo:spm_overview}. As shown, SPM takes three phases. 
-%In the map phase, objects from the same cluster form object-object pairs. 
-%The object-object pairs are then paired up with the timestamp of 
-%the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
-%In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
-%(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
-%Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).
+We use \emph{star} as the data structure to capture the pair relationships. 
+To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
+we enforce a global ordering among the objects and propose a concept named \textit{directed star}.
 
+\begin{definition}[Directed Star]
+Given a vertex with global id $s$, its directed star $Sr_s$ is defined as the set of neighboring vertices with global id $t>s$. $s$ is also called star id.
+\end{definition}
+
+Given an aggregated graph $G_A$, we can enumerate all the possible stars, 
+as shown in  Figure~\ref{fig:star_partition} (b). These stars are emitted 
+from mappers to different reducers. The key is the star ID and the value 
+is the neighbors in the star as well as the associated inverted lists. 
+The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.
+
+Before we introduce the Apriori enumerator, we are interested to 
+examine the issue of global ordering on the moving objects.
+This is because assigning different IDs to the objects will result in 
+different star partitioning results, which will eventually affect the workload 
+balance among the map-reduce jobs. Specifically, we intended to 
+measure the size of the \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
+in star partition. Intuitively, the \emph{stragglers} are the partitions that
+takes the most time to execute. We use $\Gamma$ to indicate the number of edges
+of the \emph{straggler} in star partition. And smaller $\Gamma$ is always preferred.
+%Specifically, if there are partitions
+%taking significant long time to execute, they would become
+%the bottleneck of the entire system. Such long time-taken partitions
+%are referred as \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
+%We use $\Gamma$ to indicate the number of edges
+%of the largest \emph{straggler} in star partition. Intuitively,
+%a large $\Gamma$ means the system has a more prominent bottleneck. 
+%And smaller $\Gamma$ is always preferred.
+For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
+different vertex ordering on the same graph. The top one has the $\Gamma = 5$ while
+the bottom one has the $\Gamma = 3$.
+It is obvious that the bottom one is much more balanced in terms of the size of each partition.
+
+%An important concern in design parallel algorithms is the distribution of work loads.  
+%Traditionally, the quality of a partition strategy 
+%is measured based on two aspects: (1) the number of result partition, which
+%affects the maximum parallelism
+%(2) the size balance of partitions, which affects the finishing
+%time of a job. Unlike TRM where each partition
+%contains equal-sized snapshots, the size distribution 
+%of stars in SPM remains unknown.
+%Nevertheless, we notice that, in SPM, the total sizes of 
+%stars are invariant. Therefore, the quality of a star partition
+%can be formalized as the \emph{skewness}, which is the maximum star size
+%among all stars. Smaller \emph{skewness} naturally results in more partitions
+%and less imbalance.
+%}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{star-alt.eps}
+\caption{Examples of star partitioning with different vertex ordering.}
+\label{fig:star-alt}
+\end{figure}
+
+To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
+we can use a linear algebra model as follows:  
+Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
+A vertex order is in fact a permutation of $J$. Therefore,
+the adjacent matrices of any reordered graphs can be represented as $PJP^T$
+where $P \in \mathbb{P}$ is a 
+\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
+Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
+denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
+as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
+$\Gamma^*$ can then be formulated as follows:
+\begin{equation}
+\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+\end{equation}
+
+It is challenging to directly optimize the above equation. 
+First, suppose there are $n!$ permutation matrices. 
+Such a high complexity is trivially unpractical. Second,
+since $G$ is unknown in prior,
+the vertex order cannot be planned beforehand. 
+Despite these challenges, we find a simple $O(1)$ time 
+solution which is good enough as stated in the 
+following theorem.
+
+\begin{theorem}[Balance of Star Partition]
+\label{THM:SPM_LB}
+Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
+Let $\Gamma^*$ be optimal size of straggler among all vertex orders.
+Let $\Gamma$ be the size of straggler wrt an random vertex order $P$. 
+With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
+That is,  with probability $1-1/n$, 
+$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
+\end{theorem}
+
+In fact, we have a tighter bound of $(\Gamma - \Gamma^*)$ if 
+the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
+high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
+Utilizing Theorem~\label{THM:SPM_LB}, in star partition, it is safe 
+to choose the object IDs as the vertex order. This because real object IDs are often 
+hashed and can be deemed as random.
+
+%
+%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
+%When $\eta$ is small, TRM perform good parallelism. However, wh
+%
+%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
+%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
+%%which surrenders the benefit of parallelism.
+\eat{
+Although TRPM works in a parallel way, we observe two inefficiencies. First, the
+performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
+When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
+the parallel execution of line sweep algorithm may discover the same pattern from
+multiple partitions, which introduces redundant work. To resolve the two limitations,
+we design a novel \emph{Star Partition and Mining} algorithm.
+}
+%After computing the star, each partition is applied with a reduce task. 
+%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
+%This is done by treating each vertex in $Sr_s$ as an object. 
+%The time sequence of $s$ is the union of all edges in $Sr_s$. 
+%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
+%are able to mine stars from the similar trajectory concepts.
+
+\subsection{Apriori Enumerator}
+Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must be connected in the associated temporal graphs $\{G_t\}$.
+This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects.
+However, we observe that the monotonicity property does not hold between an object set and its supersets.
+
+\begin{example}
+In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
+Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
+Let $L=2,K=3,G=2$, then both candidates are not valid patterns. 
+However, the timestamps of their super set $\{o_1,o_2,o_3\}$ is $P_1.T \cap P_2.T=\{1,2,3\}$, which
+conform to $L,K,G$. This indicates that even though $P_1.O$ and $P_2.O$ are not valid patterns, they
+cannot be pruned. Otherwise, $\{o_1,o_2,o_3\}$ would be missed out.
+\end{example}
+
+\subsubsection{Monotonicity}
+To ensure monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
+For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
+To generalize the idea, we propose two concepts named \textit{maximal $G$-connected subsequence} and \emph{candidate sequence}.
+
+\begin{definition}[Maximal $G$-connected Subsequence]
+A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, i.e., $\exists i\leq j, T' = T(i,\ldots,j)$ , (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
+\end{definition}
+%Hence, our idea is to examine the validity of object pairs.
+If $(o_i,o_j)$ itself is not a valid GCMP pattern, then all the supersets containing $(o_i,o_j)$ can be pruned.
+For instance, $(XXX,XXX)$ are not connected in Figure~\ref{} and all its supersets can be pruned.
+
+\begin{example}
+Let $G=2$, consider $T_1=(1,2,4,5,6,9,10,11,13)$. $T$ has two maximal $2$-connected subsequences:
+$T_1^A=\{1,2,4,5,6\}$ and $T_1^B=\{9,10,11,13\}$. Consider $T_2=(1,2,4,5,6,8,9)$,
+it can be verified that it is $2$-connected, thus $T_2$ has only one maximal $2$-connected subsequence which is
+itself.
+%Let $G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$
+%%
+% XXX EXPLAIN HOW TO DERIVE THE MAXIMAL G-CONNECTED SUBSEQUENCES OF $T_1$ and $T_2$. 
+\end{example}
+
+\begin{definition}[Candidate Sequence]
+$T$ is a candidate sequence if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
+\end{definition}
+
+\begin{example}
+Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a candidate sequence
+since one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
+In contrast, $T_2$ is a candidate sequence because it has one maximal $2$-connected subsequence
+and it is $L$-connected with size greater than $2$.
+\end{example}
+
+%Not that, although $T_1$ is not a candidate sequence, it can be simplified
+%to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
+%if it does not contain a \emph{candidate sequence}, then it cannot contribute
+%to any valid patterns. In fact, only the candidate sequence inside $T$ affects
+%the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
+%a star. During the simplification, if an edge results in a candidate
+%sequence of size zero, then it is removed from the star. Otherwise,
+%the simplified edge is kept. By so doing, the size of the new star
+%is much smaller.
+
+\begin{definition}[Sequence Simplification]
+Given a sequence $T$ and the GCMP parameters $G,L,K$, a $T^\#$ is
+the simplified sequence of $T$ if (1) $T^\#$ is contained in $T$, i.e., $T\# \subseteq T$.
+(2) $T^\#$ is a candidate sequence, and (3) no other candidate sequence
+$T^\#_1$ is contained in $T$ and contains $T^\#$.
+%GIVEN A SEQUENCE, PLEASE UNIQUELY DEFINE ITS SIMPLIFICATION OUTPUT.
+\end{definition}
+Note that, not every $T$ has the simplified sequence.  For example, if $L =3$,
+then the simplified sequence of $(1,2,5,6)$ does not exists.
+Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
+as stated in the following theorem:
+\begin{theorem}
+For any sequence $T$, if $T$'s simplified sequence is not empty, then
+there exists a unique $T^\#$ wrt $T$.
+\end{theorem}
+
+\begin{proof}
+We prove by contradiction.
+Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$.
+We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction.
+For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
+Consider the timestamps $T_C=T_B^\# - T_A^\#$.
+If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.
+Next, consider an arbitrary consecutive segment $\overline{ef}$ in $T_C$.
+Without loss of generality, we assume the next $G$-connected segment of $\overline{ef}$ in $T_B^\#$ is $\overline{cd}$ and the previous $G$-connected segment is $\overline{gh}$.
+There are four cases to be considered.
+We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.45\textwidth]{thm3proof.eps}
+\caption{Proof of theorem 3.}
+\label{fig:proof_thm_3}
+\end{figure}
+\begin{itemize}
+\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$.
+Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by adding $\overline{ef}$.
+\item Case (b): $G \geq c-f> 1$.
+In this case, since $c\geq a$, then $a-f \leq G$.
+Since the size of $\overline{ef}$ is greater or equal to $L$, adding $\overline{ef}$ to $\overline{ab}$ would still result in a valid candidate sequence.
+\item Case (c): $c-f > G$ and $e-h \leq G$.
+In this case, $\overline{ef}$ belongs to a $G$-connected sequence $\overline{gf}$ in $T_B^\#$.
+Observe that $\overline{gh}$ has no intersection with $T_A^\#$ (otherwise, it backs to case (a)), adding $\overline{gf}$ to $T_A^\#$ is equivalent in adding another candidate sequence to $T_A^\#$, making $T_A^\#$ still a valid simplified sequence.
+\item Case (d): $c-f > G$ and $ e- h > G$.
+In this case, since $\overline{ef}$ is part of $T_B^\#$ and there is no segments $G$-connected with $\overline{ef}$, $\overline{ef}$ itself must be a candidate sequence.
+Therefore adding $\overline{ef}$ to $T_A^\#$ would still enlarge $T_A^\#$.
+\end{itemize}
+\end{proof}
+
+Next, we design an efficient simplification process with linear complexity.
+It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
+In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
+In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.
+
+\begin{algorithm}
+\caption{Edge Simplification}
+\label{algo:simp_prune}
+\begin{algorithmic}[1]
+\Require $T$
+\State{---$L$ Phase---}
+\State $c \gets 0$
+\For {$i \in (0,...,|T|)$}
+	\If{$T[i] - T[i-1] > 1$} 
+		\If{$i - c < L$} 
+			\State $T$ remove $[c:i)$
+		\EndIf
+		\State $c \gets i$
+	\EndIf
+\EndFor
+\State{---$G$-$K$ Phase---}
+\State $s\gets 1$, $c\gets 0$
+\For{$i \in (0: |T|)$}
+	\If{$T[i] - T[i-1] > G$}
+		\If{$s < K$}   
+			\State $T$ remove $[c:i)$
+		\EndIf
+		\State {$c \gets i$, $s \gets 1$}
+	\Else
+		\State $s++$
+	\EndIf
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\begin{example}
+Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
+In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
+is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
+are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
+from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
+\end{example}
+
+With the concepts of \textit{candidate sequence} and \textit{sequence simplification}, we are ready to define the monotonic property that can be used for pruning.
+\begin{theorem}\label{THM:SPM_TM}
+Given a candidate pattern $P=\{O:T\}$, if sequence $P.T$ cannot be simplified to a candidate sequence, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
+\end{theorem}
+
+\begin{proof}
+Let $P_2$ be a true pattern with $P_2.O \supseteq P.O$.
+It is easy to see that $P_2.T \subseteq P.T$.
+Since $P_2.T$ conforms to $G,L,K$.
+This indicates that $P_2.T$ is indeed a candidate sequence.
+Since $P_2.T \subseteq P.T$, $P.T$ can be simplified to candidate sequence (i.e., to $P_2.T$) which contradict with the fact that $P$ cannot be simplified.
+Thus no such true pattern exists.
+\end{proof}
+
+%IN THE PROOF, YOU NEED TO SHOW 1) $P$ IS NOT VALID 2) ALL THE SUPERSETS OF $P.O$ ARE NOT VALID.
+
+\subsubsection{Apriori Algorithm}
+
+To systematically discover valid patterns in each star, 
+we design the \emph{Apriori Mining} algorithm. 
+To describe the  algorithm, we call a candidate pattern $R$-pattern 
+if the size of its object set is $R$.  Therefore, each edge
+in the star is effectively a $2$-pattern. The intuition of Apriori mining
+is the observation that $(R+1)$-patterns can be generated
+from $R$-patterns and $2$ patterns. Thus, we may iteratively 
+enumerate pattern candidates with all possible sizes.
+In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
+During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
+with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
+generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
+each $R$-pattern contains the object $s$, thus the join only 
+grow a $R$-pattern at most to a $(R+1)$-pattern.
+Our mining algorithm stops where no further patterns are generated. 
+The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+
+\begin{algorithm}
+\caption{Apriori Mining}
+\label{algo:apriori_mining}
+\begin{algorithmic}[1]
+\Require{$Sr_s$}
+\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
+\ForAll{$e(s,t) = T \in Sr_s$}
+\State{Simply $e(s,t)$} \Comment{ Simplification}
+\State {Ground.add($\langle \{s,t\}, T \rangle$)}
+\State {Lv $\gets$ Ground}
+\EndFor
+\While{Lv is not empty}
+		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
+		\State {Remove false patterns in Lv}
+		\Comment{Monotonicity}
+		\If{union of Lv is a valid pattern}
+			\State{output.add(Lv)} \Comment{Forward Closure}
+			\State{break}
+		\EndIf
+\EndWhile
+\State output.addAll($Lv$)
+\State \Return output
+\end{algorithmic}
+\end{algorithm}
+
+An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
+As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
+higher level candidates are generated by joining lower level candidates. When no more candidates 
+can be generated, the algorithm stops by outputting the valid patterns.
+%
+%It is notable that, in star partition, original data is 
+%replicated at most $O(|\mathbb{O}|)$ times.
+%In later sections, we will describe several 
+%more optimization techniques to further reduce the amount of replicated data.
+
+%In such a way, 
+%given an object $u$, all the objects potentially
+%co-moved with $u$ are captured in $u$'s neighborhood, which
+%forms a \emph{star} structure in graph terms. SPM utilizes
+%such structures to partition objects and then adapts an Apriori 
+%algorithm to discover true GCMPs from each partition.
+
+EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.
+
+Although leveraging \emph{temporal monotonicity} could largely prune
+false candidates and reduce the apriori search space, 
+it is ineffective when a \textit{true} pattern exists. 
+In an extreme case, if a final pattern of a star $Sr_s$ is 
+the \textit{union of all vertices} in the star,
+then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
+each level $i$. This results in an exponential search space while
+the output only contains one pattern.  
+Generally, when candidates at level $i$ collectively forms a true pattern, 
+running aprior produces many wasted candidates.
+
+Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
+we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
+all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
+\begin{theorem}[Forward Closure Checking]
+\label{THM:SPM_FCC}
+Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
+if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
+and directly output $FC_i$.
+\end{theorem}
+
+It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
+reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
+optimization as follows:
+%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
+%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
+%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
+%all candidates. Then, the following \emph{forward closure checking} rule can be used:
+%
+%\begin{theorem}[Forward Closure Checking Rule]
+%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
+%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
+%$FC_i$ forms a valid GCMP .
+%\end{theorem}
+
+\begin{example}
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
+timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+\end{example}
+
+\subsection{Correctness of SPARE}
+We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
+After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
+In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+Each reducer is an Apriori Enumerator.
+When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
+Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
+Then the Apriori algorithm enumerate the true patterns from the candidate patterns.
+Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
+\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}
+
+\eat{
 \begin{algorithm}
@@
 \end{algorithm}
+}
 
-\subsection{Star Partition}
-The intuition of the star partition is that, if two objects are part 
-of the same pattern, they must belong to the same cluster at 
-those snapshots. Therefore, we may link objects that belong to 
-the same cluster to form the \emph{connection graph}. Objects that are
-not connected surely fail to form a pattern. We may then
-partition the connection graph based on vertex connectivity
-such that mining GCMPs can be done in parallel. 
-We formally define the \emph{connection graph} as follows:
-\begin{definition}[Connection Graph]
-A connection graph is an undirected graph $G=(V:E)$, where 
-each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
-contains the timestamp sequence at which $s,t$ are in the same cluster,
-i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
-\end{definition}
-
-In graph theory, a \emph{star} of a vertex $u$ is the
-the set of neighborhood vertexes of $u$. To utilize \emph{star}
-partition, since a vertex may appear in multiple stars, 
-some replications of vertexes are required. In order to avoid replication 
-of edges, we use the \emph{directed star} as follows:
-
-\begin{definition}[Directed Star]
-Assign each vertex in $G$ an ID, a direct star of a vertex $s$, denoted as $Sr_s$, 
-is the set of incidental edges on $s$
-such that $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
-as the \emph{central vertex} of $Sr_s$.
-\end{definition}
-
-By leveraging the \emph{directed star}, we avoids replicating the edges. 
-A \emph{Connection graph} and \emph{star} examples are 
-shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
-based on the example in Figure~\ref{fig:related_work}.
-In (b), 5 stars are presented. It can be figured out that by leveraging directed star, 
-no edges are replicated. In implementation,
-as show in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
-comparison between vertices/objects are based on the vertex/object IDs.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.9\textwidth]{spm.eps}
-\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
-(c) Apriori Mining with various pruning techniques.}
-\label{fig:star_partition}
-\end{figure*}
-
-%After computing the star, each partition is applied with a reduce task. 
-%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
-%This is done by treating each vertex in $Sr_s$ as an object. 
-%The time sequence of $s$ is the union of all edges in $Sr_s$. 
-%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
-%are able to mine stars from the similar trajectory concepts.
-
-\subsection{Apriori Mining}
-To systematically discover valid patterns in each star, 
-we design the \emph{Apriori Mining} algorithm. 
-To describe the  algorithm, we call a candidate pattern $R$-pattern 
-if the size of its object set is $R$.  Therefore, each edge
-in the star is effectively a $2$-pattern. The intuition of Apriori mining
-is the observation that $(R+1)$-patterns can be generated
-from $R$-patterns and $2$ patterns. Thus, we may iteratively 
-enumerate pattern candidates with all possible sizes.
-In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
-During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
-with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
-generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
-each $R$-pattern contains the object $s$, thus the join only 
-grow a $R$-pattern at most to a $(R+1)$-pattern.
-Our mining algorithm stops where no further patterns are generated. 
-The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
-
-\begin{algorithm}
-\caption{Apriori Mining}
-\label{algo:apriori_mining}
-\begin{algorithmic}[1]
-\Require{$Sr_s$}
-\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State{Simply $e(s,t)$} \Comment{Edge Simplification}
-\State {Ground.add($\langle \{s,t\}, T \rangle$)}
-\State {Lv $\gets$ Ground}
-\EndFor
-\While{Lv is not empty}
-		\State {Lv $\gets$ Lv $\oplus $ Ground}
-		\State {Remove false patterns in Lv}
-		\Comment{Temporal Monotonicity}
-		\If{union of Lv is a valid patter}
-			\State{output.add(Lv)} \Comment{Forward Closure}
-			\State{break}
-		\EndIf
-\EndWhile
-\State output.addAll($Lv$)
-\State \Return output
-\end{algorithmic}
-\end{algorithm}
-
-An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-higher level candidates are generated by joining lower level candidates. When no more candidates 
-can be generated, the algorithm stops by outputting the valid patterns.
-
-It is notable that, in star partition, original data is 
-replicated at most $O(|\mathbb{O}|)$ times.
-In later sections, we will describe several 
-more optimization techniques to further reduce the amount of replicated data.
-%It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
-%time to mine GCMP. There are two major factors dragging 
-%down the performance. First, the size of $Sr_s$ affects the initial 
-%size of $2$-patterns. Second, the candidates generated in each 
-%level affects the join performance. In later
-%sections, we exploit some properties of GCMP to reduce the two factors.
-
-\subsection{Analysis of SPM}
-The analysis of SPM contains two parts. We first prove the correctness
-of SPM. Then, we analyze the work load distribution of the star sizes.
-
-\subsubsection{Correctness}
-An important concern in star partition is that
-whether any valid patterns are missed out by 
-such a partition. We assert the correctness by 
-the following theorem:
-\begin{theorem}[Correctness of Star Partition]
+In the following, we show the correctness of the SPARE framework.
+\begin{theorem}
 \label{THM:SPM_CORRECT}
-Star partition is complete.
+The SPARE framework guarantees completeness and soundness.
 \end{theorem}
+\begin{proof}
+If $P$ is a valid pattern in original trajectories, 
+let $s$ be the object with smallest ID in $P.O$. 
+Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
+It follows that all object $o \in P.O$ are in $Sr_s$. 
+Furthermore, every timestamp in $P.T$ is included
+in $Sr_s$.
+Therefore, $P$ is a valid pattern in $Sr_s$.
+This ensures the \emph{completeness}.
+For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$.
+This ensure the \emph{soundness}.
+\end{proof}.
 
@@
 
-\begin{lemma}[Unique Patterns in Star Partition]
+\eat{It is also interesting to observe that no duplicate patterns will be generated from the star partitions.}
+\begin{lemma}[Pattern Uniqueness of Star Partition]
 \label{LEM:SPM_CORRECT}
-Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two stars. Let $P_i$ (resp. $P_j$) be 
-the patterns discovered from $Sr_i$ (resp. $P_j$). 
-Then, $\forall p_i \in P_i, \forall p_j \in P_j, p_i.O \not\equiv p_j.O$.
+Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
+the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
+Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
 \end{lemma}
+\begin{proof}
+The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
+let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
+Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
+therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
+\end{proof}
 
-This lemma indicates that every star partition discovers different patterns,
-thus less redundant work could exist as opposed to the line sweep method in TRM.
-
-\subsubsection{Optimal Star Partition}
-An important concern in design parallel algorithms is 
-the distribution of work loads.  
-Traditionally, the quality of a partition strategy 
-is measured based on two aspects: (1) the number of result partition, which
-affects the maximum parallelism
-(2) the size balance of partitions, which affects the finishing
-time of a job. Unlike TRM where each partition
-contains equal-sized snapshots, the size distribution 
-of stars in SPM remains unknown.
-Nevertheless, we notice that, in SPM, the total sizes of 
-stars are invariant. Therefore, the quality of a star partition
-can be formalized as the \emph{skewness}, which is the maximum star size
-among all stars. Smaller \emph{skewness} naturally results in more partitions
-and less imbalance.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\textwidth]{star-alt.eps}
-\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
-\label{fig:star-alt}
-\end{figure}
-
-Interestingly, we note that the \emph{skewness} of star partition is affected by
-the way the vertexes are numbered in the connection graph. For example,
-Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
-of the same connection graph, but produces two different set of stars. 
-The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
-The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
-Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
-lower one's \emph{skewness} is 3.
-
-Ideally we wish to find a numbering scheme of connection graph
-that minimize the \emph{skewness}.
-To quantify, we use an linear algebra model as follows: 
-Let $G$ denote a connection graph.
-Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
-Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$
-(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). 
-Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
-vector. Let $\vec{c} = A\vec{b}$, then each $c_i \in \vec{c}$ 
-denotes the size of the star $Sr_i$.
-Therefore, minimizing the \emph{skewness} can be formulated as follows:
-\begin{equation}
-\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
-\end{equation}
-
-It is challenging to directly optimize the above equation. 
-First, suppose there are $n$ vertexes in $G$, enumerating
-all possible $\mathbb{A}$s leads to $n!$ combinations. 
-Such a high complexity is trivially unpractical. Second,
-since $G$ is only conceptual at runtime, 
-the load planning cannot be done beforehand. 
-Despite these challenges, we observe that there is a 
-$O(1)$ time solution which is good enough as stated in the 
-following theorem.
-
-\begin{theorem}[Balance of Star Partition]
-\label{THM:SPM_LB}
-Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
-Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
-For an random numbering, $\mathbb{A}$, with high probability, the 
-absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
-That is, it is with probability $1-1/n$, 
-$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
-\end{theorem}
-
-In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
-the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
-equation holds:
-\begin{equation*}
-Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
-\end{equation*}
-
-Utilizing Theorem 3, in SPM, it is safe to choose the object IDs as 
-the vertex number. This because in reality, object IDs are often 
-hashed and can be deemed as random.
+This lemma verifies the superiority of the SPARE framework over the TRPM framework.

### 2016-06-22 appendix.tex
Commit first
Updates on Experiments Graphs

@@
 \subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
+\label{appx:proof-rp-eta}
+\begin{proof}
+We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
+In the following, when no ambiguity, we use $\rho(T)$ to represent
+$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
+be viewed as interleaving segments and gaps. 
+We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
+segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
+Then the
+range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
+Since $\rho(T)$ is valid, the following constraints holds: 
+(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
+(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
+$n \leq \lceil \frac{K}{L}\rceil$. 
+This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
+by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
+then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
+$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
+since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
+Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
+the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.
+
+For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
+be the optimal value. Then consider the sequence $T$ generated 
+by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
+stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
+It is easy to see that the minimum $\range(\rho(T))$ 
+is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
+$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
+\end{proof}
+%\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
 %\begin{proof}
@@
 
-\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
+%\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
 
@@
 \begin{proof}
-Let $B*$ be the assignment matrix wrt the optimal numbering.
+We formalize optimization of $\Gamma$ using a linear algebra model as follows:  
+Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
+A vertex order is in fact a permutation of $J$. Therefore,
+the adjacent matrices of any reordered graphs can be represented as $PJP^T$
+where $P \in \mathbb{P}$ is a 
+\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
+Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
+denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
+as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
+$\Gamma^*$ can then be formulated as follows:
+\begin{equation}
+\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+\end{equation}
+
+Let $B*$ be the assignment matrix wrt the optimal vertex order.
 Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 

### 2016-06-22 sec3_definitions.tex
Some revisement
Section 4, Section 5 needs to merge
Checkpoint
Saved algo part
Some updates
On sec4
Need to update \eta
Need to describe \eta
Commit first
Updates on Experiments Graphs

@@
 \label{sec:definition}
-Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =\{1,2,...,m\}$ be the descritized temporal dimension.
-A time sequence $T$ is defined as a subset of $\mathbb{T}$, i.e., $T \subseteq \mathbb{T}$, and we use $|T|$ to denote sequence length.
-Let $T_i$ be $i$-th entry in $T$ and we say $T$ is consecutive if $\forall 1\leq i\leq |T|-1$, $T_{i+1} = T_i + 1$.
-It is obvious that any time sequence $T$ can be decomposed into consecutive segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} if the length of all the consecutive segments is no smaller than $L$.
+Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,m)$ be the discretized temporal dimension. 
+A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$. 
+Let $T[i]$ be the $i$-th entry of the sequence $T$ and $i$ starts from 1.
+We allow the traditional set operators 
+such as \emph{membership}, \emph{union}, \emph{intersect},
+\emph{difference}, \emph{candinality}, \emph{min},  \emph{max} and  \emph{range} on 
+sequences without changing their semantics. 
+Since sequences are ordered, we distinguish the concept of \emph{subset}
+and \emph{subsequence}. Given two sequence $T_1$ and $T_2$, 
+$T_1$ is a \emph{subset} of $T_2$, if $\forall t \in T_1$ implies $t \in T_2$.
+$T_1$ is a \emph{subsequence} of $T_2$, if $\exists i \in (0,..,|T_2|), \forall j \in (1,..,|T_1|),  T_1[j]=T_2[i+j]$.
+It is notable that a subsequence is always a subset, but not vice versa. We use $T[i:j]$ to denote
+the subsequence of $T$ from $i$-th entry to $j$-th entry inclusively.
 
-As illustrate in Figure~\ref{fig:platoon_weakpoint}, patterns adapting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from \emph{loose connection} problem. 
+We say a sequence $T$ is consecutive 
+if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer a consecutive
+portion of $T$ as a \emph{segment}.
+It is obvious that any time sequence $T$ can be decomposed into
+segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
+if the length of every segment is no smaller than $L$.
+
+As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem.
 To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
 timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:
-%To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
-%
-%
-%We say a sequence $T$ is \emph{(fully)consecutive}
-%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$.
-A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt.
-$T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive.
-For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt.
-$T$.
-We then define the $L$-consecutiveness as follows:
-
-%\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
-%A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
-%has cardinality greater or equal to $L$.
-%\end{definition}
 
@@
 A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
- $\forall T_i,T_{i+1} \in T, T_{i+1}-T_{i} \leq G$.
+ $\forall i \in (1,...,|T|-1), T[i+1]-T[i] \leq G$.
 \end{definition}
 
-We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$.
-$T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$.
+We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$.
+$T$ is not $3$-consecutive since the length of $(5,6)$ is $2$.
 Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive.
 On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
-It is worth noting that $T$ is not $1$-connected because the gap between $T_3$ and $T_4$ is 2 (i.e., 5-3=2).
+It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is 2 (i.e., 5-3=2).
 
-%Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the closeness of their locations.
-Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
-Given a trajectory database descritized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity.
+Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity.
 Let $T$ be the set of timestamps in which a group of objects $O$ are clustered.
@@
 A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.
-
-%\begin{enumerate}
-%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
-%\item{Significance: $|O| \geq M$}
-%\item{Duration: $|T| \geq K$}
-%\item{Consecutiveness: $T$ is $L$-consecutive}
-%\item{Separateness: $T$ is $G$-separated}
-%\end{enumerate} 
 \end{definition}
@@
 express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
-In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern.
-By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern.
-By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
-Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern.
+In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern.
+By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern.
+By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
+Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns.
 In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
-%In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. 
-%
-%As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent.
-By setting appropriate $G$, we are able to prune this anomaly.
-It is notable that GCMP cannot be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.
-
-%The general co-movement pattern retains the patterns that discovered by all 
-%existing techniques (group, flock, convoy, swarm and platoon). 
-%The relationships between general co-movement pattern and other patterns are summarized 
+It is notable that GCMP cannot be modeled by existing patterns. 
 \begin{table}
@@
 \hline
-Group & $2$ & $1$ & $2$ & $|T|$ & Disk-based\\
+Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
 \hline
@@
 \hline 
-Swarm & $\cdot$ & $\cdot$ & $1$ & $|T|$ & Density-based \\ 
+Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
 \hline 
-Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|T|$ & Density-based\\ 
+Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
 \hline 
 \end{tabular} 
-\caption{Expressing other patterns using GCMP. $\cdot$ indicate a user specified value. $M$ represents the 
-object \emph{size} constraints. $K$ represents \emph{duration} constraint. $L$ represents \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraints.}
+\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
+object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
 \label{tbl:patterns}
@@
 which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:
-%
-%To reduce the size of output, 
-%we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.
 
@@
 The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
-%LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
-%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.
 
-%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes.
-Therefore in this paper, we mainly consider density-based clustering.
-Our definition of GCMP is free from clustering method. Users are able to supply different clustering methods to facilitate different application needs. 
-We currently expose both disk-region based clustering and DBSCAN as options to the user.
+Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
+We currently expose both disc-region based clustering and DBSCAN as options to the users.
 
-In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory data.
+In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory datasets.
 
@@
 \hline
-$Tr_i$ & Trajectory of object $i$\\ 
+$S_t$ & snapshot of objects at time $t$ \\
 \hline
-$S_t$ & Snapshot of objects at time $t$ \\
+$M$ & object size constraint \\
 \hline 
-$\mathbb{O}$ & Set of objects \\ 
+$K$ & duration constraint\\
 \hline
-$M$ & Object size constraint \\
+$L$ & consecutiveness constraint\\
 \hline
-$K$ & Duration constraint\\
+$G$ & connection constraint \\
 \hline
-$L$ & Consecutiveness constraint\\
+$P=(O:T)$ & pattern with object set $O$, time sequence $T$\\
 \hline
-$G$ & Connection constraint \\
-\hline
-$T$ & Time sequence \\
+$\eta$ & replication factor in TRM\\
 \hline
@@
 \hline 
-$Sr_i $ &  The star structure of object $i$ \\
+$S_t$ & the set of clusters at time $t$\\
+\hline 
+$\lambda_i$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
+\hline
+$Sr_i $ &  the star of object $i$ \\
 \hline 
 \end{tabular} 
-\caption{Notions that will be used}
+\caption{Symbols and notions used}
 \end{table}

### 2016-06-22 sec4_baseline.tex
Commit first
Updates on Experiments Graphs

@@
+\begin{figure*} [t]
+\center
+\includegraphics[width=\textwidth]{trm.eps}
+\caption{Work flow of Temporal Replication and Mining.
+(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
+\label{fig:trm}
+\end{figure*}
+
 \section{Baseline: Temporal Replication and Parallel Mining}
@@
 
-It is obvious that we cannot simply split the trajectory database into disjoint partitions because a GCMP pattern requires $L$-consecutive and the corresponding segments may cross multiple partitions.
+It is obvious that we cannot simply split the trajectory database 
+into disjoint partitions because a GCMP pattern requires $L$-consecutiveness 
+and the corresponding segments may cross multiple partitions. 
 Our strategy is to use data replication to enable parallel mining. 
-Each snapshot will replicate its clusters to $\eta$ preceding snapshots.
-In other words, the partition for the snapshot $S_t$ contains clusters in $S_t$, $S_{t+1}\ldots,S_{t+\eta}$.
+Each snapshot will replicate its clusters to $\eta-1$ preceding snapshots.
+In other words, the partition for the snapshot $S_t$ contains clusters 
+in $S_t$, $S_{t+1}\ldots,S_{t+\eta-1}$. 
 Determining a proper $\eta$ is critical in ensuring the
-correctness and efficiency of TRPM.
-If $\eta$ is too small, certain cross-partition patterns may be missed.
-If $\eta$ is set too large, expensive network communication and CPU processing costs would be incurred in the map and reduce phrases respectively.
+correctness and efficiency of TRPM. If $\eta$ is too small, 
+certain cross-partition patterns may be missed. 
+If $\eta$ is set too large, expensive network communication and 
+CPU processing costs would be incurred in the map and reduce phrases respectively.
 
-To guarantee that no valid pattern is missing, we enforce the
+Before moving on to find the value of $\eta$, 
+we first use $\rho_{G,L,K}(T)$ to define the \emph{min-spanned valid subsequence} 
+of a sequence $T$. In simple words, $\rho_{G,L,K}(T)$ is the 
+subsequence of $T$ with the smallest range and is valid wrt. $K,L,G$. 
+%Let $\eta_T$ denote
+%the range of $\rho_{G,L,K}(T)$.
+To guarantee that no valid patterns are missing, $\eta$ needs
+to be greater than the range of $\rho_{G,L,K}(T)$ for any
+valid sequence $T$. To see this, consider an arbitrary valid sequence $T$.
+Since each partition contains $\eta$ snapshots,
+if $\eta \geq \range(\rho_{G,L,K}(T))$ holds, $\rho_{G,L,K}(T)$ must be completely located in one partition. Therefore, the patterns associated with $T$ would not be missing.
+Formally, $\eta$ can be computed as:
+\begin{equation}
+\eta = \max\{\range(\rho_{G,L,K}(T)) | T \text{ is valid wrt. } G,L,K\}
+\end{equation}
+
+Directly compute such $\eta$ is challenging. However,
+we provide the following theorem which states a bounded estimation on $\eta$: 
+\begin{theorem}
+\label{THM:RP_ETA}
+Let $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$. Then it guarantees 
+the completeness of the partition. Further:
+let $\eta^*$ be the optimal value for a given $G,L,K$, then the following holds:
+$\eta \leq \eta^* + L-1$.
+\end{theorem}
+\begin{proof}
+See Appendix.
+\end{proof}
+\eat{
+In order to formally compute the minimum value of $\eta$,
+we enforce the
 following statement on $\eta$:
-I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
+%I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
  \emph{Let $T'$ be the \emph{shortest} 
@@
 parameters $K,L,G$ by making the following observation on $G=1$:
-
-\begin{figure*} [t]
-\center
-\includegraphics[width=\textwidth]{trm.eps}
-\caption{Work flow of Temporal Replication and Mining.
-(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
-\label{fig:trm}
-\end{figure*}
 
@@
 \end{proof}
+}
 
@@
 \Require list of $\langle t, S_t \rangle$ pairs
-\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
+\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
 \State {---Map Phase---}

### 2016-06-22 sec5_spm-bk.tex
Commit first
Updates on Experiments Graphs

--- 2016-06-18 sec5_spm.tex
@@
-\section{Star Partition and Mining}
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.9\textwidth]{spm.eps}
+\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
+(c) Apriori Mining with various pruning techniques.}
+\label{fig:star_partition}
+\end{figure*}
+
+\section{SPARE: Star Partitioning and Apriori Enumerator}
 \label{sec:spm}
-To resolve the two limitations of TRM, we 
-propose the \emph{Star Partition and Mining} (SPM) method.
-Instead of partition trajectory database in the temporal domain,
-SPM partition the trajectory database in the object domain.
-Specifically, we design a graph model, named \emph{connection graph}, to capture 
-the co-moving behavior among objects. In such a way, 
-given an object $u$, all the objects potentially
-co-moved with $u$ are captured in $u$'s neighborhood, which
-forms a \emph{star} structure in graph terms. SPM utilizes
-such structures to partition objects and then adapts an Apriori 
-algorithm to discover true GCMPs from each partition.
+The aforementioned replicate partitioning is based on the temporal dimension 
+and results in groups of snapshots in each partition. 
+To resolve the limitations caused by the replicate partitioning, 
+we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
+to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
+Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
+Its input is the set of clusters generated in each snapshot and the output 
+are mined GCMP patterns. In the following, we explain the two major components: 
+star partitioning and apriori enumerator.
 
-The flow of SPM method is presented in Figure~\ref{fig:star_partition}.
-SPM utilizes the same preprocessing as TRM, thus the flow starts
-from clusters in each snapshot. Conceptually, the clusters 
-in each snapshot forms a graph as shown in Figure~\ref{fig:star_partition} (a).
-In the map phase of \emph{SPM}, a vertex together with its neighborhood 
-vertexes form a star. Every star is indeed an independent partition.
-Then, stars are shuffled to reducers. As in
-Figure~\ref{fig:star_partition} (c), Apriori mining algorithm is adapted
-to mine the GCMP patterns. The overview implementation of SPM is shown 
-in Algorithm~\ref{algo:spm_overview}.
+\subsection{Star Partitioning}
+Let $G_t$ be a graph for snapshot $S_t$, in which each node 
+is a moving object and two objects are connected if they appear 
+in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
+Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
+cluster relationship among all the snapshots. In $G_A$, two objects
+form an edge if they are connected in any $G_t$s. Furthermore, 
+we attach an inverted list for each edge, 
+storing the associated timestamps in which the two objects are connected. 
+An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
+is shown in Figure~\ref{fig:star_partition} (a). 
+As long as two objects are clustered in any timestamp, they are connected in $G_A$. 
+The object pair $(o_1,o_2)$ appears in two clusters at timestamps 
+$2$ and $3$ and is thus associated with an inverted list $\{2,3\}$.
 
-%The overview of the SPM method is presented in 
-%Algorithm~\ref{algo:spm_overview}. As shown, SPM takes three phases. 
-%In the map phase, objects from the same cluster form object-object pairs. 
-%The object-object pairs are then paired up with the timestamp of 
-%the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
-%In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
-%(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
-%Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).
+We use \emph{star} as the data structure to capture the pair relationships. 
+To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
+we enforce a global ordering among the objects and propose a concept named \textit{directed star}.
 
+\begin{definition}[Directed Star]
+Given a vertex with global id $s$, its directed star $Sr_s$ is defined as the set of neighboring vertices with global id $t>s$. $s$ is also called star id.
+\end{definition}
+
+Given an aggregated graph $G_A$, we can enumerate all the possible stars, 
+as shown in  Figure~\ref{fig:star_partition} (b). These stars are emitted 
+from mappers to different reducers. The key is the star ID and the value 
+is the neighbors in the star as well as the associated inverted lists. 
+The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.
+
+Before we introduce the Apriori enumerator, we are interested to 
+examine the issue of global ordering on the moving objects.
+This is because assigning different IDs to the objects will result in 
+different star partitioning results, which will eventually affect the workload 
+balance among the map-reduce jobs. Specifically, we intended to 
+measure the size of the \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
+in star partition. Intuitively, the \emph{stragglers} are the partitions that
+takes the most time to execute. We use $\Gamma$ to indicate the number of edges
+of the \emph{straggler} in star partition. And smaller $\Gamma$ is always preferred.
+%Specifically, if there are partitions
+%taking significant long time to execute, they would become
+%the bottleneck of the entire system. Such long time-taken partitions
+%are referred as \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
+%We use $\Gamma$ to indicate the number of edges
+%of the largest \emph{straggler} in star partition. Intuitively,
+%a large $\Gamma$ means the system has a more prominent bottleneck. 
+%And smaller $\Gamma$ is always preferred.
+For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
+different vertex ordering on the same graph. The top one has the $\Gamma = 5$ while
+the bottom one has the $\Gamma = 3$.
+It is obvious that the bottom one is much more balanced in terms of the size of each partition.
+
+%An important concern in design parallel algorithms is the distribution of work loads.  
+%Traditionally, the quality of a partition strategy 
+%is measured based on two aspects: (1) the number of result partition, which
+%affects the maximum parallelism
+%(2) the size balance of partitions, which affects the finishing
+%time of a job. Unlike TRM where each partition
+%contains equal-sized snapshots, the size distribution 
+%of stars in SPM remains unknown.
+%Nevertheless, we notice that, in SPM, the total sizes of 
+%stars are invariant. Therefore, the quality of a star partition
+%can be formalized as the \emph{skewness}, which is the maximum star size
+%among all stars. Smaller \emph{skewness} naturally results in more partitions
+%and less imbalance.
+%}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{star-alt.eps}
+\caption{Examples of star partitioning with different vertex ordering.}
+\label{fig:star-alt}
+\end{figure}
+
+%To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
+%we can use a linear algebra model as follows:  
+%Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
+%A vertex order is in fact a permutation of $J$. Therefore,
+%the adjacent matrices of any reordered graphs can be represented as $PJP^T$
+%where $P \in \mathbb{P}$ is a 
+%\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
+%Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+%Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+%vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
+%denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
+%as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
+%$\Gamma^*$ can then be formulated as follows:
+%\begin{equation}
+%\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+%\end{equation}
+
+It is challenging to directly find the optimal $\Gamma$. 
+First, suppose there are $n!$ permutation matrices. 
+Such a high complexity is trivially unpractical. Second,
+since $G$ is unknown in prior,
+the vertex order cannot be planned beforehand. 
+Despite these challenges, we find a simple $O(1)$ time 
+solution which is good enough as stated in the 
+following theorem.
+
+\begin{theorem}[Balance of Star Partition]
+\label{THM:SPM_LB}
+Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
+Let $\Gamma^*$ be optimal size of straggler among all vertex orders.
+Let $\Gamma$ be the size of straggler wrt an random vertex order $P$. 
+With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
+That is,  with probability $1-1/n$, 
+$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
+\end{theorem}
+
+In fact, we have a tighter bound of $(\Gamma - \Gamma^*)$ if 
+the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
+high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
+Utilizing Theorem~\label{THM:SPM_LB}, in star partition, it is safe 
+to choose the object IDs as the vertex order. This because real object IDs are often 
+hashed and can be deemed as random.
+
+%
+%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
+%When $\eta$ is small, TRM perform good parallelism. However, wh
+%
+%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
+%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
+%%which surrenders the benefit of parallelism.
+\eat{
+Although TRPM works in a parallel way, we observe two inefficiencies. First, the
+performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
+When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
+the parallel execution of line sweep algorithm may discover the same pattern from
+multiple partitions, which introduces redundant work. To resolve the two limitations,
+we design a novel \emph{Star Partition and Mining} algorithm.
+}
+%After computing the star, each partition is applied with a reduce task. 
+%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
+%This is done by treating each vertex in $Sr_s$ as an object. 
+%The time sequence of $s$ is the union of all edges in $Sr_s$. 
+%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
+%are able to mine stars from the similar trajectory concepts.
+
+\subsection{Apriori Enumerator}
+Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must be connected in the associated temporal graphs $\{G_t\}$.
+This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects.
+However, we observe that the monotonicity property does not hold between an object set and its supersets.
+
+\begin{example}
+In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
+Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
+Let $L=2,K=3,G=2$, then both candidates are not valid patterns. 
+However, the timestamps of their super set $\{o_1,o_2,o_3\}$ is $P_1.T \cap P_2.T=\{1,2,3\}$, which
+conform to $L,K,G$. This indicates that even though $P_1.O$ and $P_2.O$ are not valid patterns, they
+cannot be pruned. Otherwise, $\{o_1,o_2,o_3\}$ would be missed out.
+\end{example}
+
+\subsubsection{Monotonicity}
+To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
+For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
+To generalize the idea, we propose two concepts named \textit{maximal $G$-connected subsequence} and \emph{candidate sequence}.
+
+\begin{definition}[Maximal $G$-connected Subsequence]
+A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, i.e., $\exists i\leq j, T' = T(i,\ldots,j)$ , (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
+\end{definition}
+%Hence, our idea is to examine the validity of object pairs.
+If $(o_i,o_j)$ itself is not a valid GCMP pattern, then all the supersets containing $(o_i,o_j)$ can be pruned.
+For instance, $(XXX,XXX)$ are not connected in Figure~\ref{} and all its supersets can be pruned.
+
+\begin{example}
+Let $G=2$, consider $T_1=(1,2,4,5,6,9,10,11,13)$. $T_1$ has two maximal $2$-connected subsequences:
+$T_1^A=\{1,2,4,5,6\}$ and $T_1^B=\{9,10,11,13\}$. Consider $T_2=(1,2,4,5,6,8,9)$,
+since $T_2$ is $2$-connected, thus $T_2$ has only one maximal $2$-connected subsequence which is
+itself.
+%Let $G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$
+%%
+% XXX EXPLAIN HOW TO DERIVE THE MAXIMAL G-CONNECTED SUBSEQUENCES OF $T_1$ and $T_2$. 
+\end{example}
+
+\begin{definition}[Candidate Sequence]
+$T$ is a candidate sequence if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
+\end{definition}
+
+\begin{example}
+Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a candidate sequence
+since one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
+In contrast, $T_2$ is a candidate sequence because it has one maximal $2$-connected subsequence
+and it is $2$-consecutive with size greater than $4$.
+\end{example}
+
+%Not that, although $T_1$ is not a candidate sequence, it can be simplified
+%to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
+%if it does not contain a \emph{candidate sequence}, then it cannot contribute
+%to any valid patterns. In fact, only the candidate sequence inside $T$ affects
+%the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
+%a star. During the simplification, if an edge results in a candidate
+%sequence of size zero, then it is removed from the star. Otherwise,
+%the simplified edge is kept. By so doing, the size of the new star
+%is much smaller.
+
+\begin{definition}[Sequence Simplification]
+Given a sequence $T$ and the GCMP parameters $G,L,K$, a $T^\#$ is
+the simplified sequence of $T$ if (1) $T^\#$ is contained in $T$, i.e., $T^\# \subseteq T$.
+(2) $T^\#$ is a candidate sequence, and (3) no other candidate sequence
+$T^\#_1$ is contained in $T$ and contains $T^\#$.
+%GIVEN A SEQUENCE, PLEASE UNIQUELY DEFINE ITS SIMPLIFICATION OUTPUT.
+\end{definition}
+Note that, not every $T$ has the simplified sequence.  For example, if $L =3$,
+then the simplified sequence of $(1,2,5,6)$ does not exists.
+Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
+as stated in the following theorem:
+\begin{theorem}
+For any sequence $T$, if $T$'s simplified sequence is not empty, then
+there exists a unique $T^\#$ wrt $T$.
+\end{theorem}
+\begin{proof}
+We prove by contradiction.
+Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$.
+We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction.
+For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
+Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.
+
+Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$.
+Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
+is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
+there are four cases to be considered. 
+We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.46\textwidth]{thm3proof.eps}
+\caption{Proof of theorem 3 with the four cases.}
+\label{fig:proof_thm_3}
+\end{figure}
+\begin{itemize}
+\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$.
+Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
+\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
+consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$.
+Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
+\item Case (c): $c-f > G$ and $e-h \leq G$.
+In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.
+Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
+\item Case (d): $c-f > G$ and $ e- h > G$.
+In this case,  $\overline{ef}$ has to be a candidate sequence.
+Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
+\end{itemize}
+In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
+\end{proof}
+
+Next, we design an efficient simplification process with linear complexity.
+It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
+In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
+In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.
+
+\begin{algorithm}
+\caption{Edge Simplification}
+\label{algo:simp_prune}
+\begin{algorithmic}[1]
+\Require $T$
+\State{---$L$ Phase---}
+\State $c \gets 0$
+\For {$i \in (0,...,|T|)$}
+	\If{$T[i] - T[i-1] > 1$} 
+		\If{$i - c < L$} 
+			\State $T$ remove $[c:i)$
+		\EndIf
+		\State $c \gets i$
+	\EndIf
+\EndFor
+\State{---$G$-$K$ Phase---}
+\State $s\gets 1$, $c\gets 0$
+\For{$i \in (0: |T|)$}
+	\If{$T[i] - T[i-1] > G$}
+		\If{$s < K$}   
+			\State $T$ remove $[c:i)$
+		\EndIf
+		\State {$c \gets i$, $s \gets 1$}
+	\Else
+		\State $s++$
+	\EndIf
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\begin{example}
+Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
+In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
+is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
+are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
+from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
+\end{example}
+
+With the concepts of \textit{candidate sequence} and \textit{sequence simplification}, we are ready to define the monotonic property that can be used for pruning.
+\begin{theorem}\label{THM:SPM_TM}
+Given a candidate pattern $P=\{O:T\}$, if sequence $P.T$ cannot be simplified to a candidate sequence, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
+\end{theorem}
+
+\begin{proof}
+Let $P_2$ be a true pattern with $P_2.O \supseteq P.O$.
+It is easy to see that $P_2.T \subseteq P.T$.
+Since $P_2.T$ conforms to $G,L,K$.
+This indicates that $P_2.T$ is indeed a candidate sequence.
+Since $P_2.T \subseteq P.T$, $P.T$ can be simplified to candidate sequence (i.e., to $P_2.T$) which contradict with the fact that $P$ cannot be simplified.
+Thus no such true pattern exists.
+\end{proof}
+
+%IN THE PROOF, YOU NEED TO SHOW 1) $P$ IS NOT VALID 2) ALL THE SUPERSETS OF $P.O$ ARE NOT VALID.
+
+\subsubsection{Apriori Algorithm}
+
+To systematically discover valid patterns in each star, 
+we design the \emph{Apriori Mining} algorithm. 
+To describe the  algorithm, we call a candidate pattern $R$-pattern 
+if the size of its object set is $R$.  Therefore, each edge
+in the star is effectively a $2$-pattern. The intuition of Apriori mining
+is the observation that $(R+1)$-patterns can be generated
+from $R$-patterns and $2$ patterns. Thus, we may iteratively 
+enumerate pattern candidates with all possible sizes.
+In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
+During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
+with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
+generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
+each $R$-pattern contains the object $s$, thus the join only 
+grow a $R$-pattern at most to a $(R+1)$-pattern.
+Our mining algorithm stops where no further patterns are generated. 
+The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+
+\begin{algorithm}
+\caption{Apriori Mining}
+\label{algo:apriori_mining}
+\begin{algorithmic}[1]
+\Require{$Sr_s$}
+\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
+\ForAll{$e(s,t) = T \in Sr_s$}
+\State{Simply $e(s,t)$} \Comment{ Simplification}
+\State {Ground.add($\langle \{s,t\}, T \rangle$)}
+\State {Lv $\gets$ Ground}
+\EndFor
+\While{Lv is not empty}
+		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
+		\State {Remove false patterns in Lv}
+		\Comment{Monotonicity}
+		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
+			\State{output.add(Lv)} 
+			\State{break}
+		\EndIf
+\EndWhile
+\State output.addAll($Lv$)
+\State \Return output
+\end{algorithmic}
+\end{algorithm}
+
+An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
+As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
+higher level candidates are generated by joining lower level candidates. When no more candidates 
+can be generated, the algorithm stops by outputting the valid patterns.
+%
+%It is notable that, in star partition, original data is 
+%replicated at most $O(|\mathbb{O}|)$ times.
+%In later sections, we will describe several 
+%more optimization techniques to further reduce the amount of replicated data.
+
+%In such a way, 
+%given an object $u$, all the objects potentially
+%co-moved with $u$ are captured in $u$'s neighborhood, which
+%forms a \emph{star} structure in graph terms. SPM utilizes
+%such structures to partition objects and then adapts an Apriori 
+%algorithm to discover true GCMPs from each partition.
+
+EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.
+
+Although leveraging \emph{temporal monotonicity} could largely prune
+false candidates and reduce the apriori search space, 
+it is ineffective when a \textit{true} pattern exists. 
+In an extreme case, if a final pattern of a star $Sr_s$ is 
+the \textit{union of all vertices} in the star,
+then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
+each level $i$. This results in an exponential search space while
+the output only contains one pattern.  
+Generally, when candidates at level $i$ collectively forms a true pattern, 
+running aprior produces many wasted candidates.
+
+Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
+we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
+all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
+\begin{theorem}[Forward Closure Checking]
+\label{THM:SPM_FCC}
+Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
+if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
+and directly output $FC_i$.
+\end{theorem}
+
+It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
+reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
+optimization as follows:
+%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
+%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
+%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
+%all candidates. Then, the following \emph{forward closure checking} rule can be used:
+%
+%\begin{theorem}[Forward Closure Checking Rule]
+%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
+%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
+%$FC_i$ forms a valid GCMP .
+%\end{theorem}
+
+\begin{example}
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
+timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+\end{example}
+
+\subsection{Correctness of SPARE}
+We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
+After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
+In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+Each reducer is an Apriori Enumerator.
+When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
+Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
+Then the Apriori algorithm enumerate the true patterns from the candidate patterns.
+Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
+\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}
+
+\eat{
 \begin{algorithm}

### 2016-06-22 sec5_spm.tex
Commit first
Updates on Experiments Graphs

@@
 The aforementioned replicate partitioning is based on the temporal dimension 
-and results in groups of snapshots in each partition. 
+and results in groups of snapshots in each partition. ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
 To resolve the limitations caused by the replicate partitioning, 
@@
 Its input is the set of clusters generated in each snapshot and the output 
-are mined GCMP patterns. In the following, we explain the two major components: 
+contains all the valid GCMP patterns. In the following, we explain the two major components: 
 star partitioning and apriori enumerator.
@@
 \begin{definition}[Directed Star]
-Given a vertex with global id $s$, its directed star $Sr_s$ is defined as the set of neighboring vertices with global id $t>s$. $s$ is also called star id.
+Given a vertex with global id $s$, its directed star $Sr_s$ is defined as the set of neighboring vertices with global id $t>s$. We call $s$ the star ID.
 \end{definition}
 
-Given an aggregated graph $G_A$, we can enumerate all the possible stars, 
-as shown in  Figure~\ref{fig:star_partition} (b). These stars are emitted 
-from mappers to different reducers. The key is the star ID and the value 
-is the neighbors in the star as well as the associated inverted lists. 
+With the global ordering, we can guarantee that each edge is contained in a unique star partition.
+Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition} (a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition} (b).
+These stars are emitted from mappers to different reducers.
+The key is the star ID and the value is the neighbors in the star as well as the associated inverted lists.
 The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.
@@
 different star partitioning results, which will eventually affect the workload 
-balance among the map-reduce jobs. Specifically, we intended to 
-measure the size of the \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
-in star partition. Intuitively, the \emph{stragglers} are the partitions that
-takes the most time to execute. We use $\Gamma$ to indicate the number of edges
-of the \emph{straggler} in star partition. And smaller $\Gamma$ is always preferred.
-%Specifically, if there are partitions
-%taking significant long time to execute, they would become
-%the bottleneck of the entire system. Such long time-taken partitions
-%are referred as \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}
-%We use $\Gamma$ to indicate the number of edges
-%of the largest \emph{straggler} in star partition. Intuitively,
-%a large $\Gamma$ means the system has a more prominent bottleneck. 
-%And smaller $\Gamma$ is always preferred.
+balance among the map-reduce jobs.
+The job incurring performance bottleneck is often known as \emph{straggler}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}.
+In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition.
+We use $\Gamma$ to denote the size of a partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}.
+It is straightforward that a star partitioning with small $\Gamma$ is preferred.
 For example, Figure~\ref{fig:star-alt} gives two star partitioning results under
-different vertex ordering on the same graph. The top one has the $\Gamma = 5$ while
-the bottom one has the $\Gamma = 3$.
-It is obvious that the bottom one is much more balanced in terms of the size of each partition.
+different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.
 
@@
 
-To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
-we can use a linear algebra model as follows:  
-Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
-A vertex order is in fact a permutation of $J$. Therefore,
-the adjacent matrices of any reordered graphs can be represented as $PJP^T$
-where $P \in \mathbb{P}$ is a 
-\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
-Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
-then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
-represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
-Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
-vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
-denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
-as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
-$\Gamma^*$ can then be formulated as follows:
-\begin{equation}
-\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
-\end{equation}
+%To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
+%we can use a linear algebra model as follows:  
+%Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
+%A vertex order is in fact a permutation of $J$. Therefore,
+%the adjacent matrices of any reordered graphs can be represented as $PJP^T$
+%where $P \in \mathbb{P}$ is a 
+%\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
+%Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+%Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+%vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
+%denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
+%as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
+%$\Gamma^*$ can then be formulated as follows:
+%\begin{equation}
+%\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
+%\end{equation}
 
-It is challenging to directly optimize the above equation. 
-First, suppose there are $n!$ permutation matrices. 
-Such a high complexity is trivially unpractical. Second,
-since $G$ is unknown in prior,
-the vertex order cannot be planned beforehand. 
-Despite these challenges, we find a simple $O(1)$ time 
-solution which is good enough as stated in the 
-following theorem.
+Although it is very challenging to find the optimal vertex id ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
 
-\begin{theorem}[Balance of Star Partition]
+\begin{theorem}
 \label{THM:SPM_LB}
-Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
-Let $\Gamma^*$ be optimal size of straggler among all vertex orders.
-Let $\Gamma$ be the size of straggler wrt an random vertex order $P$. 
-With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
-That is,  with probability $1-1/n$, 
-$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
+Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering.
+With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
 \end{theorem}
-
-In fact, we have a tighter bound of $(\Gamma - \Gamma^*)$ if 
-the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
-high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
-Utilizing Theorem~\label{THM:SPM_LB}, in star partition, it is safe 
-to choose the object IDs as the vertex order. This because real object IDs are often 
-hashed and can be deemed as random.
+\begin{proof}
+In Appendix XXX.
+\end{proof}
+If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
+\begin{theorem}
+\label{THM:SPM_LB_INC}
+Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
+high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
+\end{theorem}
+\begin{proof}
+In Appendix XXXX.
+\end{proof}
+Hence, we can simply use object id to determine the vertex ordering in our implementation.
 
@@
 \subsection{Apriori Enumerator}
-Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must be connected in the associated temporal graphs $\{G_t\}$.
+Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, 
+all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must 
+be connected in the associated temporal graphs $\{G_t\}$.
 This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects.
@@
 Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
-Let $L=2,K=3,G=2$, then both candidates are not valid patterns. 
-However, the timestamps of their super set $\{o_1,o_2,o_3\}$ is $P_1.T \cap P_2.T=\{1,2,3\}$, which
-conform to $L,K,G$. This indicates that even though $P_1.O$ and $P_2.O$ are not valid patterns, they
-cannot be pruned. Otherwise, $\{o_1,o_2,o_3\}$ would be missed out.
+Let $L=2,K=3$ and $G=2$. Both candidates are not valid patterns because the constraint on $L$ is not satisfied. 
+However, when considering their object superset $\{o_1,o_2,o_3\}$, we can infer that their co-clustering timestamps are in $(1,2,3)$.
+This is a valid pattern conforming to the constraints of $L,K,G$.
+Thus, we need a new type of monotonicity to facilitate pruning.
 \end{example}
@@
 \subsubsection{Monotonicity}
-To ensure monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
+To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
 For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
-To generalize the idea, we propose two concepts named \textit{maximal $G$-connected subsequence} and \emph{candidate sequence}.
+To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.
 
@@
 \begin{example}
-Let $G=2$, consider $T_1=(1,2,4,5,6,9,10,11,13)$. $T$ has two maximal $2$-connected subsequences:
-$T_1^A=\{1,2,4,5,6\}$ and $T_1^B=\{9,10,11,13\}$. Consider $T_2=(1,2,4,5,6,8,9)$,
-it can be verified that it is $2$-connected, thus $T_2$ has only one maximal $2$-connected subsequence which is
+Suppose $G=2$ and consider two sequences $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$.
+$T_1$ has two maximal $2$-connected subsequences:$T_1^A=(1,2,4,5,6)$ and $T_1^B=(9,10,11,13)$.
+This is because the gap between $T_1^A$ and $T_1^B$ is $3$ and it is impossible for the timestamps from  $T_1^A$ and $T_1^B$ to form a new subsequence with $G\leq 2$.
+Since $T_2$ is $2$-connected, $T_2$ has only one maximal $2$-connected subsequence which is
 itself. 
-%Let $G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$
-%%
-% XXX EXPLAIN HOW TO DERIVE THE MAXIMAL G-CONNECTED SUBSEQUENCES OF $T_1$ and $T_2$. 
 \end{example}
 
-\begin{definition}[Candidate Sequence]
-$T$ is a candidate sequence if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
+The maximal $G$-connected subsequence has the following two properties:
+\begin{lemma}\label{lemma:union-property}
+Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
+\end{lemma}
+\begin{proof}
+We assume $T_i\cap T_j\neq \emptyset$.
+Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$.
+Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$.
+Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$.
+Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$.
+Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected.
+Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected.
+This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.
+
+To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$.
+Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$.
+Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$.
+If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected.
+If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$.
+Both cases lead to contradiction.
+\end{proof}
+
+\begin{lemma}\label{lemma:subset-property}
+If $T_1$ is a subset of $T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that $T_1'$ is a subset of $T_2'$.
+\end{lemma}
+\begin{proof}
+Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$.
+Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$.
+If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction.
+Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
+\end{proof}
+
+\begin{definition}[Decomposable Sequence]
+$T$ is decomposable if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
 \end{definition}
@@
 \begin{example}
-Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a candidate sequence
-since one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
-In contrast, $T_2$ is a candidate sequence because it has one maximal $2$-connected subsequence
-and it is $L$-connected with size greater than $2$.
+Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
+because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
+In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than than $4$.
 \end{example}
@@
 \begin{definition}[Sequence Simplification]
-Given a sequence $T$ and the GCMP parameters $G,L,K$, a $T^\#$ is
-the simplified sequence of $T$ if (1) $T^\#$ is contained in $T$, i.e., $T\# \subseteq T$.
-(2) $T^\#$ is a candidate sequence, and (3) no other candidate sequence
-$T^\#_1$ is contained in $T$ and contains $T^\#$.
-%GIVEN A SEQUENCE, PLEASE UNIQUELY DEFINE ITS SIMPLIFICATION OUTPUT.
+Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
+\begin{enumerate}
+\item $f$-step: remove segments of $T$ that are not $L$-consecutive;
+\item $g$-step: among the maximal $G$-connected subsequences of $f_L(T)$, remove those with size smaller than $K$.
+\end{enumerate}
 \end{definition}
-Note that, not every $T$ has the simplified sequence.  For example, if $L =3$,
-then the simplified sequence of $(1,2,5,6)$ does not exists.
+
+\begin{example}
+Take $T=(1,2,4,5,6,9,10,11,13)$ as an example for sequence simplification. 
+Let $L = 2, K = 4$ and $G = 2$. In the $f$-step, $T$ is reduced to $f_2(T)=(1,2,4,5,6,9,10,11)$. 
+The segment $(13)$ is removed due to the constraint of $L=2$. 
+$f_2(T)$ has two maximal $2$-consecutive subsequences: $(1,2,4,5,6)$ and $(9,10,11)$. 
+Since $K=4$, we will remove $(9,10,11)$ in the $g$-step. Finally, the output is $\mathtt{sim}(T)=(1,2,4,5,6)$.
+\end{example}
+
+It is possible that the simplified sequence $\mathtt{sim}(T)=\emptyset$. For example, Let $T=(1,2,5,6)$ 
+and $L=3$. All the segments will be removed in the $f$-step and the output is $\emptyset$.
+We define $\emptyset$ to be not decomposable. 
+%Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
+We provide an important property of the sequence simplification process as follows:
+\begin{lemma}\label{lemma:decom-sim}
+If sequence $T$ is a superset of any decomposable sequence, then $\mathtt{sim}(T) \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+It is obvious that $\mathtt{sim}(T)$ is a one-to-one function.
+Given an input sequence T, there is a unique  $\mathtt{sim}(T)$.
+Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.
+
+Suppose $T_p$ can be decomposed into a set of maximal $G$-connected
+subsequences $T_p^1, \ldots, T_p^m$ ($m \geq 1$).
+Since $T_p$ is a subset of $T$, all the $T_p^i$ are also subsets of $T$.
+By definition, each $T_p^i$ is $L$-consecutive.
+Thus, in the $f$-step of $\mathtt{sim}(T)$, none of $T_p^i$ will be removed.
+In the $g$-step, based on Lemma~\ref{lemma:subset-property}, we know that each $T_p^i$ has a superset in the maximal $G$-connected subsequences of $f_L(T)$.
+Since $|T_p^i|\geq K$, none of $T_p^i$ will be removed in the $g$-step.
+Therefore, all the $T_p^i$ will be retained after the simplification process and $\mathtt{sim}(T) \neq \emptyset$.
+\end{proof}
+
+\eat{
 Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
@@
 \end{theorem}
-
 \begin{proof}
@@
 For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
-Consider the timestamps $T_C=T_B^\# - T_A^\#$.
-If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.
-Next, consider an arbitrary consecutive segment $\overline{ef}$ in $T_C$.
-Without loss of generality, we assume the next $G$-connected segment of $\overline{ef}$ in $T_B^\#$ is $\overline{cd}$ and the previous $G$-connected segment is $\overline{gh}$.
-There are four cases to be considered.
+Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.
+
+Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$.
+Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
+is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
+there are four cases to be considered. 
 We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
@@
 \centering
-\includegraphics[width=0.45\textwidth]{thm3proof.eps}
-\caption{Proof of theorem 3.}
+\includegraphics[width=0.46\textwidth]{thm3proof.eps}
+\caption{Proof of theorem 3 with the four cases.}
 \label{fig:proof_thm_3}
@@
 \item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$.
-Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by adding $\overline{ef}$.
-\item Case (b): $G \geq c-f> 1$.
-In this case, since $c\geq a$, then $a-f \leq G$.
-Since the size of $\overline{ef}$ is greater or equal to $L$, adding $\overline{ef}$ to $\overline{ab}$ would still result in a valid candidate sequence.
+Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
+\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
+consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$.
+Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
 \item Case (c): $c-f > G$ and $e-h \leq G$.
-In this case, $\overline{ef}$ belongs to a $G$-connected sequence $\overline{gf}$ in $T_B^\#$.
-Observe that $\overline{gh}$ has no intersection with $T_A^\#$ (otherwise, it backs to case (a)), adding $\overline{gf}$ to $T_A^\#$ is equivalent in adding another candidate sequence to $T_A^\#$, making $T_A^\#$ still a valid simplified sequence.
+In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.
+Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
 \item Case (d): $c-f > G$ and $ e- h > G$.
-In this case, since $\overline{ef}$ is part of $T_B^\#$ and there is no segments $G$-connected with $\overline{ef}$, $\overline{ef}$ itself must be a candidate sequence.
-Therefore adding $\overline{ef}$ to $T_A^\#$ would still enlarge $T_A^\#$.
+In this case,  $\overline{ef}$ has to be a candidate sequence.
+Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
 \end{itemize}
+In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
 \end{proof}
+}
 
+\eat{
 Next, we design an efficient simplification process with linear complexity.
@@
 \end{algorithm}
+}
 
-\begin{example}
-Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
-In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
-is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
-are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
-from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
-\end{example}
+With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
+sequences to facilitate the pruning in the Apriori algorithm.
 
-With the concepts of \textit{candidate sequence} and \textit{sequence simplification}, we are ready to define the monotonic property that can be used for pruning.
 \begin{theorem}\label{THM:SPM_TM}
-Given a candidate pattern $P=\{O:T\}$, if sequence $P.T$ cannot be simplified to a candidate sequence, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
+Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
 \end{theorem}
@@
 \begin{proof}
-Let $P_2$ be a true pattern with $P_2.O \supseteq P.O$.
-It is easy to see that $P_2.T \subseteq P.T$.
-Since $P_2.T$ conforms to $G,L,K$.
-This indicates that $P_2.T$ is indeed a candidate sequence.
-Since $P_2.T \subseteq P.T$, $P.T$ can be simplified to candidate sequence (i.e., to $P_2.T$) which contradict with the fact that $P$ cannot be simplified.
-Thus no such true pattern exists.
+We prove by contradiction.
+Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$.
+It is obvious that $P_2.T \subseteq P.T$.
+Based on the Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected.
+(2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive.
+Note that the entire $P_2.T$ is $G$-connected.
+Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence.
+Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable.
+Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable.
+This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
 \end{proof}
@@
 
-\subsubsection{Apriori Algorithm}
+\subsubsection{Apriori Enumeration}
+We then design the Apriori enumeration method to
+systematically discover all valid patterns in a star.
+During the enumeration, we refer a candidate pattern
+$P$ as a $R$-candidate if $|P.O|=R$. The enumeration
+method discover patterns in ``bottom-up'' order:
+in iteration $i$,  all $(i+1)$-candidates grows
+to $(i+2)$-candidates. Enumeration ends if no
+further candidates can be generated.
+
+The process of enumeration is shown 
+in Algorithm~\ref{algo:apriori_mining}. As a start, 
+each edge is treated as a $2$-candidate pattern, with the 
+inverted list as the time sequence. These $2$-candidates
+are kept in $\mathbf{G}$ as the ground set. During the algorithm,
+we maintain a set of candidates $\mathbf{C}$. $\mathbf{C}$
+is initialized as $\mathbf{G}$.
+
+As a start, each edge is treated as
 
 To systematically discover valid patterns in each star,
-we design the \emph{Apriori Mining} algorithm. 
+
+we enumerate all valid patterns in ``bottom-up" order: 
+pattern candidates with smallest object sizes are enumerated
+first and grew to pattern candidates with larger object sizes.
+During the enumeration, we call a candidate pattern
+$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
+a star as input, and treat each edge as a $2$-pattern.
+
+The input of
+the enumerator is a star. Each edge
+in the star is treated a $2$-candidate, with the inverted
+list to be the time sequence.
+
+we design the \emph{Apriori Mining} algorithm. We borrow
+the terminologies in classic Aprirori algorithm: a candidate
+pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
+candidates grows from $2$-pattern level by level.
+
 To describe the algorithm, we call a candidate pattern $R$-pattern 
@@
 \Require{$Sr_s$}
-\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
+\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
 \ForAll{$e(s,t) = T \in Sr_s$}
-\State{Simply $e(s,t)$} \Comment{ Simplification}
-\State {Ground.add($\langle \{s,t\}, T \rangle$)}
-\State {Lv $\gets$ Ground}
+\State {$T' \gets \mathtt{sim}(e(s,t))$}
+%\State{ $\mathtt{sim}(e(s,t)) $} 
+\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}
 \EndFor
-\While{Lv is not empty}
+\State {$\mathbf{C} \gets \mathbf{G}$}
+\While{$\mathbf{C} \neq \emptyset$}
+		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
+		\ForAll{$(c,g)\in \mathbf{C}$}
+			\ForAll {$g \in \mathbf{G}$ }
+				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$}
+				\State {$\mathbf{N}.add(c')$, unless $c'.T \neq \emptyset$}
+			\EndFor
+			\State $\mathbf{OT}.\mathtt{add}(c)$, if $c$ is not extended.
+		\EndFor	
+		\State $U \gets $ union of $n_i \in \mathbf{N}$
+		\ForAll{$n \in \mathbf{N}$}
+			\State $U.O \gets$,  $U.T \gets U.T \cap n.T$
+		\EndFor
+		\If{$U$ is valid}
+			\State $\mathbf{Output}.\mathbf{add}(U)$
+			\State break;
+		\EndIf
+		\State {$\mathbf{C} \gets \mathbf{N}$}
 		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
@@
 		\Comment{Monotonicity}
-		\If{union of Lv is a valid pattern}
-			\State{output.add(Lv)} \Comment{Forward Closure}
+		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
+			\State{output.add(Lv)} 
 			\State{break}
@@
 timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
-are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
+are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
 of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a

### 2016-06-22 sec7_experiment.tex
Commit first
Updates on Experiments Graphs

@@
 \label{sec:exp}
+In this section, we present our experimental findings on
+deploying our GCMP detectors to large-scaled real trajectories.
+All algorithms are were implemented in Java 1.7., and all the 
+experiments are carried out on our in-house cluster: Dianwei. The cluster
+includes 12 nodes, each of which has four quad-core 2.2GHz Intel processor,
+32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
+operating system, Java 1.7.0 VM.
+
+\textbf{Experiment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
+to manage the cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
+Yarn processes. We use Apache Spark~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
+the remaining 11 nodes as the computing nodes.
+To fully utilize the computing power of the cluster, 
+we assign each node to run five executors, each executor takes three cores and 5 GB memory. We use "yarn-cluster" mode
+for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
+at the same time. We use HDFS as our storage engine with replicator factor of 1.
+The configurations of important parameters are summaries in the table below:
+
 %\subsection{Implementation Issues}
@@
 %still holds under this new setting.
-
-\subsection{Experimental Setup}
-We adapt one of the most popular MapReduce platform, Apache Spark, 
-to conduct experiments on mining GCMPs. 
-Our experiments run on a 9-node cluster, with Apache Yarn as
-the cluster manager. We use 1 node for Yarn resource manager, 
-and use the remaining 8 nodes as executors. Each node in the cluster
-is uniformly equipped with a 2.2GHz quad-core CPU with 32 GB memory. 
-Inter-node communication is carried by 
-the 1Gbps Ethernet.  Some critical configuration of Spark is 
-as follows:
+%
+%
+%\subsection{Experimental Setup}
+%We adapt one of the most popular MapReduce platform, Apache Spark, 
+%to conduct experiments on mining GCMPs. 
+%Our experiments run on a 9-node cluster, with Apache Yarn as
+%the cluster manager. We use 1 node for Yarn resource manager, 
+%and use the remaining 8 nodes as executors. Each node in the cluster
+%is uniformly equipped with a 2.2GHz quad-core CPU with 32 GB memory. 
+%Inter-node communication is carried by 
+%the 1Gbps Ethernet.  Some critical configuration of Spark is 
+%as follows:
 \begin{table} [h]
@@
 \hline 
-spark.executor.cores & 2  \\ 
+spark.executor.cores & 3  \\ 
 \hline 
-spark.executor.instances & 11 \\ 
+spark.executor.instances & 54 \\ 
 \hline 
-spark.executor.memory & 7GB \\ 
+spark.executor.memory & 5GB \\ 
 \hline 
@@
 \hline 
+spark.shuffle.spill & true \\ 
+\hline 
 \end{tabular} 
@@
 
-We prepare three real datasets for study. The details of the datasets are as follows:
+\textbf{Datasets}: We prepare three real datasets for study. The details of the datasets are as follows:
 \begin{itemize}
-\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: contains 18,670 
-GPS trajectories for passengers in Beijing over three years. The data are collected per 1~5 seconds.
-We use linear interpretation for missing data in short-intervals (i.e., 5 seconds), since interpolating
-big intervals introduces large errors.
-\item{ACTShopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: contains visitors trajectories in ATC shopping center in Osaka from October 24, 2012 to November 29, 2013.
-There are in total 18670 trajectories, with 41 million data points.
-\item{SingTaxi}: contains 15,054 Singapore taxi trajectories in August 2012.
+\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: this dataset collects 
+18,670 trajectories for passengers in Beijing over three years. The data are collected
+per around 5 seconds. Each data point records a trajectory ID and the latitude/longitude information.
+\item{Shopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: this dataset contains
+ visitors trajectories in ATC shopping center in Osaka. The samples are taken per
+ around 0.5 seconds. There are in total 13,183 trajectories. Each data point is a 
+ trajectory ID with in-door coordinates.
+\item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
+rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude.
 \end{itemize}
 
-The summary of statistics are presented as in the following table:
+\textbf{Preprocessing}: We replace timestamps with a global sequence for each dataset. The sequence number
+$0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
+each dataset as the tick of the sequence number and every data point is mapped to the nearest ticks. If
+several points mapped to the same tick, they are merged by averaging the location coordinates.
+For missing data within small intervals (i.e., sequence difference less than 10), 
+we use linear interpolation to fill them. 
+We then use DBSCAN ($\epsilon=5, minPt=10$ for GeoLife and Shopping, $\epsilon=20, minPt=10$ for Taxi)
+as the clustering algorithm for preprocessing.  
+Note that both our TRPM and SPARSE algorithms treat the preprocessing as a black box and other
+spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
+$t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
+After preprocessing, the summary of statistics are presented as in Table~\ref{exp:dataset}. 
+%But they are affected by the number of clusters at each snapshot. We measure the 
+%effect of different clustering parameters later.
 
@@
 \center
-\caption{Statistics of data set}
+\small
 \begin{tabular}{|l|l|l|l|}
 \hline
- & Geolife & ACTShopping & SingTaxi \\ 
+ \textbf{Attributes}& \textbf{Geolife} & \textbf{ACTShopping} & \textbf{SingTaxi} \\ 
 \hline 
@@
 \hline
-\# longest ts & 17,281 & 24,407 & 43,717 \\
-\hline
 \# data points & 54,594,696 & 41,052,242 & 296,075,837\\ 
 \hline
+\# snapshots & 10,699 & 16,931 & 44,364\\ 
+\hline
+\# clusters & 206,704 & 211,403 & 536,804\\
+\hline
+avg. cluster size & 223 & 171 & 484\\
+\hline
+\# of patterns & 441 & 369 & 585 \\
+\hline
 \end{tabular}
+\caption{Statistics of data set}
+\label{exp:dataset}
 \end{table}
 
+\textbf{Parameters}: We study the performance of 
+the GCMP detectors under various conditions. The variables
+to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
+The default values are highlighted in bold.
+\begin{table}[h]
+\small
+\begin{tabular}{c|l|l}
+\hline 
+\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
+\hline 
+M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
+\hline 
+K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
+\hline 
+L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
+\hline 
+G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
+\hline
+N & number of executors & 1, 14, 24, 34, 44, \textbf{54}\\ 
+\hline 
+\end{tabular} 
+\caption{Variables and their default values during experiments.}
+\label{tbl:parameters}
+\end{table}
+
+\subsection{Effects of $G$ on GCMP}
 \begin{figure*}[t]
@@
 \end{figure*}
-
-\subsection{Effects of $G$ on GCMP}
-We study the effects of the gap parameter $G$ on discovering co-movement patterns. 
+We first study the effects of introducing gap parameter $G$ on pattern discovery.
 As shown in Figure~\ref{fig:related_work_scalability},
-existing works are not able to handle large trajectories, we sample and cluster $1$ million  
-trajectory points from the three real data. We use two instances of GCMPs, GCMP-L where the
-$L$ value is default and GCMP where $L = 1$.  We measure the number
+existing works are not able to handle large trajectories, 
+we sample and cluster $1$ million trajectory points from the three real data.
+We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
 of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
@@
 We can see from Figures~\ref{exp:effectiveness} that the number of patterns
-discovered by GCMP is a positively related to $G$. When $G =1$, the number
+discovered by GCMP is positively related to $G$. When $G =1$, the number
 of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
@@
 when $G$ is $50$. The reason is that when $G$ is large enough,
- all consecutive segments in \emph{platoon} satisfy the $G$-connectivity. Similar
+ all \emph{platoon}s are $G$-connected. Similar
  trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
@@
 \subsection{Performance Comparison}
-We now study the performance of our GCMP methods. We use TRPM as
-the baseline algorithm and implement SPM and SPM+.
+%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
+%parameter settings. Under the default parameter settings,
+%the performance of TRPM and SPARE is shown as in the 
+%following table:
+%\begin{table}
+%\small
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline 
+%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
+%\hline 
+% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
+%\hline 			
+%Shopping &55 & 279 & 183 &414 &369\\ 
+%\hline
+%GeoLife &72 & 408 & 162 &585 &441  \\
+%\hline
+%Taxi &193 & 619 & 562 &3086 &585 \\
+%\hline 
+%\end{tabular} 
+%\caption{Detail performance of TRPM and SPARE under default parameters.}
+%\end{table}
+%
+%As can be seen from the above table, the number of patterns
+%discovered by the default parameters are up to five hundreds.
+%Thus, the parameter settings are reasonable. Besides, we 
+%can see that TRPM suffers from shuffle and mining process. 
+%This is because $\eta$ is set to be $309$ under default parameters.
+%As a comparison, SPARE takes only in average
+% 36\% of TRPM's shuffle time. 
+To study the performance of TRMP and SPARE, we run both algorithms 
+in all three datasets under different parameter settings. We report
+their overall performance as in Figures~\ref{exp:performance_vary}.
+In brief, both algorithms are able to handle the large-scaled real
+datasets. However, we observe that TRMP's performance is very
+dependent on the pattern parameters.
+In cases when $G$ is large, TRMP takes near three hours (e.g., in Taxi dataset).
+In contrast, SPARE performs quite stable. Another general observation
+is that both algorithms run slower in the Taxi dataset as compared to in
+other two datasets. This is because Taxi dataset contains
+the most number of temporal data points, which is around 7 times of Shopping
+dataset and 5 times of geolife dataset. We observe that, 
+in almost all cases, SPARE outperforms TRMP and analyze the detail
+of each scenario separately:
 
-\begin{table}
-\begin{tabular}{c|c|l}
-\hline 
-\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
-\hline 
-M & min size of object set &  20, 40, \textbf{60},80,100 \\ 
-\hline 
-K & min duration & 60, 120, \textbf{180}, 240, 300 \\ 
-\hline 
-L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
-\hline 
-G & max gap & 5,10,\textbf{15},20,25 \\ 
-\hline 
-$\epsilon$ & DBSCAN parameter & 3,6,\textbf{9},12 \\ 
-\hline 
-minPt & DBSCAN parameter & 3,6,\textbf{9},12 \\ 
-\hline 
-\end{tabular} 
-\caption{Pattern Parameters and their default values.}
-\end{table}
+\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
+present the performance of TRPM and SPARE when $M$ changes under three datasets.
+As the figures show, SPARE runs much faster than TRPM. We can see that SPARE
+speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
+7 times in Taxi data. Another observation is that, the running times
+of both algorithms slightly decrease as $M$ grows. This is
+because when $M$ becomes bigger, smaller clusters (stars) in 
+the reduce phase of TRPM and SPARE can be directly pruned.
 
-\subsubsection{Effects of clusters $\epsilon$, minPt}
+\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
+presents the performance of TRPM and SPARE when $K$ changes under three datasets. 
+There are two interesting findings in study the performance wrt. $K$. 
+First, SPARE and TRPM takes different trends as $K$ increases. 
+Whe $K$ increases, SPARE tends to have faster performances 
+while TRPM's performances continuously slow down. For SPARE, the 
+good performances result from more pruning powers brought
+by $K$. When $K$ increases, many shorter time sequences in the reduce phase
+are pruned. In contrast, $K$ does not bring much pruning power
+during the reduce phase of TRPM. Even $K$ is very large, each reducers in TRPM
+still has to sweep the entire partition to determine whether a pattern exists.
+Moreover, $\eta$ in TRPM grows linearly with $K$. This indicates that
+more data are shuffled and more snapshots are need to
+be swept in each partition. This explains the low performance of TRPM as $K$
+increases. Another interesting finding is that, when $K$ is small,
+TRPM tends to outperform SPARE. This is because that when $K$ is small, shuffle
+data of TRPM is comparable to SPARE. Meanwhile, small $K$ indicates small
+size of partition in TRPM but low pruning power in SPARE. This explains the
+superiority of TRPM. Note that, when $K$ is small, TRPM is at most 1.3 times
+faster than SPARE and the absolute time is less than three minutes.
+
+\textbf{Vary $L$}:Figure~\ref{} presents the performance
+of TRPM and SPARE when $L$ changes under three datasets.
+
+\textbf{Vary $G$}:Figure~\ref{} presents the performance
+of TRPM and SPARE when $G$ changes under three datasets.
+
+%\subsubsection{Effects of clusters $\epsilon$, minPt}
+
+\begin{figure*}[t]
+\centering
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
+        \caption{Shopping Vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
+        \caption{Shopping Vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
+        \caption{Shopping Vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
+        \caption{Shopping Vary $G$}
+    \end{subfigure}
+
+	\begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
+        \caption{Geolife Vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
+        \caption{Geolife Vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
+        \caption{Geolife Vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
+        \caption{Geolife Vary $G$}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
+        \caption{Taxi Vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
+        \caption{Taxi Vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
+        \caption{Taxi Vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
+        \caption{Taxi Vary $G$}
+    \end{subfigure}       
+\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
+\label{exp:performance_vary}
+\end{figure*}
+
 \subsubsection{Effects of pattern parameters $M,L,K,G$}
 
-\subsection{SPM Analysis}
+\subsection{SPARE Analysis}
 \subsubsection{Load Balance}

### 2016-06-22 appendix.tex
Revised section 5
fff

@@
 
-\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
+\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
 \begin{proof}
-We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
-let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
-(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
-then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
-It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+For soundness, let $P$ be a pattern enumerated by SPARE, then $\forall o_1, o_2 \in P.O$ they belongs to the same star.
+As the enumerate algorithm only reduce the time sequences, $P.T \subset e(o_1,o_2)$.
+This indicates that, $\forall t \in P.T$, $t\in e(o_1,o_2)$.
+By the definition of star, $C_t(o_1) = C_t(o_2)$.
+Since $P.T$ conforms to $K,L,G$,  by the definition of GCMP, $P.T$ is a true pattern.
+For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with $Sr_s$. 
+First, based on the definition of star partition, every object in $P.O$ appears in $Sr_s$.
+Note that $P.T$ conforms to $K,L,G$, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence.
+This indicates that any $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.
+Next, we prove in iterations $(1,\ldots,P.|O|-2)$, $P.O \subset U_i$, where $U_i$ is the forward closure.
+We prove by induction.
+When $i$ = 2, it obviously holds.
+If $P.O \subset U_i$ at iteration $i$, then any subset of $P.O$ with size $i+2$ are in the candidate set.
+In iteration $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$).
+This suggests that no subsets are removed by Line~\ref{code:output1}.
+Then, $P.O \subset U_{i+1}$ holds.
+In summary, $P.O$ does not pruned by simplification and monotonicity and forward closure, therefore $P$ can be returned by SPARE.
+%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated.
+Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$.
+This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking.
+Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
+%
+%\begin{theorem}[Forward Closure Checking]
+%\label{THM:SPM_FCC}
+%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
+%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
+%and directly output $FC_i$.
+%\end{theorem}
+
+%
+%If $P$ is a valid pattern in original trajectories, 
+%let $s$ be the object with smallest ID in $P.O$. 
+%Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
+%It follows that all object $o \in P.O$ are in $Sr_s$. 
+%Furthermore, every timestamp in $P.T$ is included
+%in $Sr_s$.
+Therefore, $P$ is a valid pattern in $Sr_s$.
+This ensures the \emph{completeness}.
+For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$.
+This ensure the \emph{soundness}.
 \end{proof}
+
+%\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
+%\begin{proof}
+%We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
+%let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
+%(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
+%then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
+%It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
+%\end{proof}

### 2016-06-22 sec5_spm.tex
Revised section 5
fff

@@
 \label{sec:spm}
-The aforementioned replicate partitioning is based on the temporal dimension 
-and results in groups of snapshots in each partition. ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
+The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks.
+First, the replication relies on $\eta$ which could be large.
+Second, the same valid pattern may be discovered from different partitions which results in redundant work.
+%and results in groups of snapshots in each partition.
+% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
 To resolve the limitations caused by the replicate partitioning, 
@@
 
-\begin{theorem}\label{THM:SPM_TM}
+\begin{theorem}\label{THM:SPARE_MONO}
 Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
@@
 systematically discover all valid patterns in a star.
-During the enumeration, we refer a candidate pattern
-$P$ as a $R$-candidate if $|P.O|=R$. The enumeration
-method discover patterns in ``bottom-up'' order:
-in iteration $i$,  all $(i+1)$-candidates grows
-to $(i+2)$-candidates. Enumeration ends if no
+%During the enumeration, we refer a candidate pattern
+%$P$ as a $R$-candidate if $|P.O|=R$.
+The enumeration method discover patterns iteratively using ``bottom-up'' order:
+candidates with smaller objects set grow one object per iteration.
+%
+%in iteration $i$,  all $(i+1)$-candidates grows
+%to $(i+2)$-candidates.
+%
+Enumeration ends if no
 further candidates can be generated.
 
-The process of enumeration is shown 
+ Due the \emph{monotoniciy} proved in Theorem~\label{THM:SPARE_MONO}, we are able to use the \emph{monotonicity pruning} and \emph{forward closure checking} techniques to boost the enumeration process.
+We show the detail of the process
 in Algorithm~\ref{algo:apriori_mining}. As a start, 
-each edge is treated as a $2$-candidate pattern, with the 
-inverted list as the time sequence. These $2$-candidates
-are kept in $\mathbf{G}$ as the ground set. During the algorithm,
-we maintain a set of candidates $\mathbf{C}$. $\mathbf{C}$
-is initialized as $\mathbf{G}$.
+each input edge is treated as a candidate pattern, with the 
+inverted list as the time sequence. These candidates
+are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}).
+During the initialization of $\mathbf{G}$, the inverted list are simplified (Line~\ref{code:simp1}) and unqualified edges are pruned (Line~\ref{code:init-prune}).
+Throughout the algorithm, we maintain a set of candidates denoted as $\mathbf{C}$ which is initialized to be the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).
 
-As a start, each edge is treated as
+In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}).
+The join of two candidate $c$ and $g$ creates a
+new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}).
+During the join, we use \emph{sequence simplification} to detect unqualified candidates.
+By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}).
+If a candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).
+
+After the join process has finished, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}).
+The forward closure checking is to test whether the union of all the candidates in $\mathbf{C}$ form a pattern.
+If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).
+
+\eat{
+to union all the candidates in the current candidate set, and quickly check whether the
 
@@
 The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+}
 
 \begin{algorithm}
-\caption{Apriori Mining}
+\caption{Apriori Enumerator}
 \label{algo:apriori_mining}
@@
 \State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State {$T' \gets \mathtt{sim}(e(s,t))$}
-%\State{ $\mathtt{sim}(e(s,t)) $} 
-\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}
+\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
+\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
+\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
+\EndFor\label{code:init-end}
+\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
+\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
+		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
+		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
+			\ForAll {$g \in \mathbf{G}$}		
+				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
+				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
 			\EndFor
-\State {$\mathbf{C} \gets \mathbf{G}$}
-\While{$\mathbf{C} \neq \emptyset$}
-		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
-		\ForAll{$(c,g)\in \mathbf{C}$}
-			\ForAll {$g \in \mathbf{G}$ }
-				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$}
-				\State {$\mathbf{N}.add(c')$, unless $c'.T \neq \emptyset$}
-			\EndFor
-			\State $\mathbf{OT}.\mathtt{add}(c)$, if $c$ is not extended.
-		\EndFor	
-		\State $U \gets $ union of $n_i \in \mathbf{N}$
-		\ForAll{$n \in \mathbf{N}$}
-			\State $U.O \gets$,  $U.T \gets U.T \cap n.T$
-		\EndFor
-		\If{$U$ is valid}
-			\State $\mathbf{Output}.\mathbf{add}(U)$
+			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
+		\EndFor	\label{code:join-ends}
+		\State $U \gets $ union of $n_i \in \mathbf{N}$	\label{code:fc-checking-start}
+		\If {$U$ is a valid pattern}
+			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
 			\State break;
-		\EndIf
+		\EndIf \label{code:fc-checking-ends}
 		\State {$\mathbf{C} \gets \mathbf{N}$}
-		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
-		\State {Remove false patterns in Lv}
-		\Comment{Monotonicity}
-		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
-			\State{output.add(Lv)} 
-			\State{break}
-		\EndIf
-\EndWhile
-\State output.addAll($Lv$)
-\State \Return output
+\EndWhile\label{code:level-ends}
+\State $\mathbf{OT}$.addAll$(\mathbf{C})$
+\State \Return $\mathbf{OT}$
 \end{algorithmic}
@@
 
-An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-higher level candidates are generated by joining lower level candidates. When no more candidates 
-can be generated, the algorithm stops by outputting the valid patterns.
+%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
+%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
+%higher level candidates are generated by joining lower level candidates. When no more candidates 
+%can be generated, the algorithm stops by outputting the valid patterns.
+%
+
+\begin{example}
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
+timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+\end{example}
+
 %
@@
 %algorithm to discover true GCMPs from each partition.
+
+\eat{
 
@@
 %\end{theorem}
+}
 
-\begin{example}
-We use Figure~\ref{fig:star_partition} (c) to 
-demonstrate the power of candidate pruning. 
-As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
-timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
-are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
-of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
-valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
-\end{example}
+\subsection{Put It Together}
+With the star partition and the Apriori enumerator, we are ready to assemble the Star Partition and ApRiori Enumerator (SPARE). 
+We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
+After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
+In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+Each reducer is an Apriori Enumerator.
+When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
+Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
+Then the Apriori algorithm enumerate the true patterns from the candidate patterns.
+The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
+Note that we do not need to create an actual aggregate graph.
+Instead, we only to emitted the directed edges (Line~\ref{code:spm-edge-direct}).
 
-\subsection{Correctness of SPARE}
+\begin{algorithm}
+\caption{Star Partition and ApRiori Enumerator}
+\label{algo:spm_overview}
+\begin{algorithmic}[1]
+\Require list of $\langle t, S_t \rangle$ pairs
+\State {---Map phase---}
+\label{code:spm-map-start}
+\ForAll{$C \in S_t$}
+	\ForAll {$(o_1 ,o_2) \in C \times C$}
+	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet, if $o_1 < o_2$~\label{code:spm-edge-direct}
+	\EndFor
+\EndFor
+\label{code:spm-map-end}
+
+\State {---Partition and Shuffle phase---}
+\label{code:spm-shuffle-start}
+\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
+	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
+	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
+\EndFor
+\label{code:spm-shuffle-end}
+
+\State {---Reduce phase---}
+\label{code:spm-reduce-start}
+\ForAll{$\langle o, Sr_{o} \rangle$}
+\State AprioriEnumerator($Sr_o$)
+\EndFor
+\label{code:spm-reduce-end}
+
+\end{algorithmic}
+\end{algorithm}
+
+Our SPARE framework does not rely on the pattern parameters to determine the partition size,
+which is more stable than TRMP. In addition, we observe that the patterns mined from each
+reducer are unique. This property is stated as follows:
+\begin{theorem}[Pattern Uniqueness of Star Partition]
+\label{LEM:SPM_CORRECT}
+Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
+the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
+Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
+\end{theorem}
+\begin{proof}
+We prove by contradiction. Suppose exists $p_i \in P_i$ and $p_j \in P_j$ s.t. $p_i.O \equiv p_j.O$.
+Let $o_i$ (resp. $o_j$) be the object with smallest ID in $p_i.O$ (resp. $p_j.O$).
+Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$,  which contradicts with
+the assumption $p_i.O \not\equiv p_j.O$. 
+\end{proof}
+
+Theorem~\ref{LEM:SPM_CORRECT} confirms the superiority of SPARE to TRPM. In TRPM, a pattern
+may be repeatedly discovered from different partitions, while in SPARE a pattern is only discovered once.
+This suggests that SPARE require less redundant works.
+We finally conclude this section with the following theorem:
+
+\begin{theorem}
+\label{THM:SPM_CORRECT}
+The SPARE framework guarantees completeness and soundness.
+\end{theorem}
+\begin{proof}
+See Appendix XXXX.
+\end{proof}
+
+\eat{ \subsection{Correctness of SPARE}
 We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
@@
 Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
-\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}
+ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.
 
@@
 This ensure the \emph{soundness}.
-\end{proof}.
+\end{proof}
 
@@
 This lemma verifies the superiority of the SPARE framework over the TRPM framework.
+}

### 2016-06-23 appendix.tex
Revise Sec 5 last portion and Appendix

@@
 \section{Proofs of Theorems}
-\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
-\label{appx:proof-rp-eta}
-\begin{proof}
-We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
-In the following, when no ambiguity, we use $\rho(T)$ to represent
-$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
-be viewed as interleaving segments and gaps. 
-We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
-segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
-Then the
-range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
-Since $\rho(T)$ is valid, the following constraints holds: 
-(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
-(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
-$n \leq \lceil \frac{K}{L}\rceil$. 
-This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
-by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
-then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
-$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
-since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
-Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
-the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.
-
-For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
-be the optimal value. Then consider the sequence $T$ generated 
-by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
-stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
-It is easy to see that the minimum $\range(\rho(T))$ 
-is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
-$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
-\end{proof}
+%\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
+%\label{appx:proof-rp-eta}
+%\begin{proof}
+%We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
+%In the following, when no ambiguity, we use $\rho(T)$ to represent
+%$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
+%be viewed as interleaving segments and gaps. 
+%We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
+%segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
+%Then the
+%range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
+%Since $\rho(T)$ is valid, the following constraints holds: 
+%(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
+%(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
+%$n \leq \lceil \frac{K}{L}\rceil$. 
+%This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+%If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
+%by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
+%then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
+%$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+%Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
+%since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
+%Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
+%the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
+%Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.
+%
+%For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
+%be the optimal value. Then consider the sequence $T$ generated 
+%by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
+%stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
+%It is easy to see that the minimum $\range(\rho(T))$ 
+%is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
+%$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
+%\end{proof}
 %\subsection{Proof of Theorem~\ref{THM:RP_ETA}}

### 2016-06-23 sec3_definitions.tex
Revise Sec 5 last portion and Appendix

@@
 \label{sec:definition}
-Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,m)$ be the discretized temporal dimension. 
+Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension.
 A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$.
-Let $T[i]$ be the $i$-th entry of the sequence $T$ and $i$ starts from 1.
-We allow the traditional set operators 
-such as \emph{membership}, \emph{union}, \emph{intersect},
-\emph{difference}, \emph{candinality}, \emph{min},  \emph{max} and  \emph{range} on 
-sequences without changing their semantics. 
-Since sequences are ordered, we distinguish the concept of \emph{subset}
-and \emph{subsequence}. Given two sequence $T_1$ and $T_2$, 
-$T_1$ is a \emph{subset} of $T_2$, if $\forall t \in T_1$ implies $t \in T_2$.
-$T_1$ is a \emph{subsequence} of $T_2$, if $\exists i \in (0,..,|T_2|), \forall j \in (1,..,|T_1|),  T_1[j]=T_2[i+j]$.
-It is notable that a subsequence is always a subset, but not vice versa. We use $T[i:j]$ to denote
-the subsequence of $T$ from $i$-th entry to $j$-th entry inclusively.
+Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.
+
+\begin{table}[h] \scriptsize
+\centering
+\begin{tabular}{|c|l|}
+\hline 
+\textbf{Operator} & \textbf{Definition} \\ 
+\hline
+$T[i]$ & the $i$-th element in the sequence $T$ \\ 
+\hline
+$|T|$ & the number of elements in $T$\\
+\hline
+$\max(T)$ & the maximum element in $T$\\
+\hline
+$\min(T)$ & the minimum element in $T$\\
+\hline
+$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
+\hline 
+$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
+\hline
+$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
+$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
+\hline
+$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
+\hline
+\end{tabular}
+\caption{Operators on time sequence.} \label{tbl:operators}
+\end{table}
 
 We say a sequence $T$ is consecutive 
-if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer a consecutive
-portion of $T$ as a \emph{segment}.
+if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer each consecutive subsequence of $T$ as a \emph{segment}.
 It is obvious that any time sequence $T$ can be decomposed into
@@
 if the length of every segment is no smaller than $L$.
-
 As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem.
@@
 \begin{definition}[General Co-Movement Pattern]
-A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.
+A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is L-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
 \end{definition}
@@
 It is notable that GCMP cannot be modeled by existing patterns. 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 \hline 
-Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
+\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
 \hline
@@
 \end{table}
-
+\eat{ 
 It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
@@
 The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
+}
 
@@
 We currently expose both disc-region based clustering and DBSCAN as options to the users.
-
-In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory datasets.
-
+In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMP from large-scale trajectory datasets.
 Before we move on to the algorithmic part, we list the notations that are used in the following sections.
 
-\begin{table}[h]
+\begin{table}[h]\scriptsize
 \centering
@@
 \hline
-Symbols & Meanings \\
+Symbol & Meaning \\
 \hline
@@
 \hline
-$P=(O:T)$ & pattern with object set $O$, time sequence $T$\\
+$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
 \hline
-$\eta$ & replication factor in TRM\\
+$\eta$ & replication factor in the TRPM framework\\
 \hline
@@
 \hline 
-$\lambda_i$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
+$\lambda_t$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
 \hline
-$Sr_i $ &  the star of object $i$ \\
+$Sr_i $ &  the star partition for object $i$ \\
 \hline 

### 2016-06-23 sec7_experiment.tex
Revised section 5
fff
Revise Sec 5 last portion and Appendix

@@
 experiments are carried out on our in-house cluster: Dianwei. The cluster
-includes 12 nodes, each of which has four quad-core 2.2GHz Intel processor,
+includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors,
 32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
-operating system, Java 1.7.0 VM.
+operating system and Java 1.7.0 VM.
 
@@
 \hline 
-spark.shuffle.spill & true \\ 
-\hline 
 \end{tabular} 
@@
 \hline
- \textbf{Attributes}& \textbf{Geolife} & \textbf{ACTShopping} & \textbf{SingTaxi} \\ 
+ \textbf{Attributes}& \textbf{ACTShopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
 \hline 
-\# objects & 18,670 & 13,183 & 15,054\\ 
+\# objects  & 13,183 & 18,670 & 15,054\\ 
 \hline
-\# average ts & 2,924 & 3,114 & 19,667 \\ 
+\# average ts & 3,114  & 2,924 & 19,667 \\ 
 \hline
-\# data points & 54,594,696 & 41,052,242 & 296,075,837\\ 
+\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
 \hline
-\# snapshots & 10,699 & 16,931 & 44,364\\ 
+\# snapshots  & 16,931 & 10,699 & 44,364\\ 
 \hline
-\# clusters & 206,704 & 211,403 & 536,804\\
+\# clusters  & 211,403  & 206,704& 536,804\\
 \hline
-avg. cluster size & 223 & 171 & 484\\
+avg. cluster size  & 171 & 223 & 484\\
 \hline
-\# of patterns & 441 & 369 & 585 \\
-\hline
+%\# of patterns & 3,741 & 4,369  & 7,585 \\
+%\hline
 \end{tabular}
@@
 
-\subsection{Effects of $G$ on GCMP}
-\begin{figure*}[t]
-\centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
-        \caption{Geolife}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
-        \caption{ACTShopping}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
-        \caption{SingTaxi}
-    \end{subfigure}
-\caption{Effectiveness of GCMP model on sampled datasets.}
-\label{exp:effectiveness}
-\end{figure*}
-We first study the effects of introducing gap parameter $G$ on pattern discovery.
-As shown in Figure~\ref{fig:related_work_scalability},
-existing works are not able to handle large trajectories, 
-we sample and cluster $1$ million trajectory points from the three real data.
-We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
-of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
-
-We can see from Figures~\ref{exp:effectiveness} that the number of patterns
-discovered by GCMP is positively related to $G$. When $G =1$, the number
-of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
-the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
-patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
-when $G$ is $50$. The reason is that when $G$ is large enough,
- all \emph{platoon}s are $G$-connected. Similar
- trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
- patterns converge at $G=50$; while in (b) and (c) the two patterns converge
- at $G=60$ and $G=40$ respectively. We further
- note that, existing patterns has different granularity in temporal domain. As we seen
- from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
- \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
- the temporal domain of patterns, GCMP can discover the patterns more precisely. 
- These results confirms the usefulness of GCMP in expressing other patterns.
+%\subsection{Effects of $G$ on GCMP}
+%\begin{figure*}[t]
+%\centering
+%    \begin{subfigure}[b]{0.3\textwidth}
+%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
+%        \caption{Geolife}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.33\textwidth}
+%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
+%        \caption{ACTShopping}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.3\textwidth}
+%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
+%        \caption{SingTaxi}
+%    \end{subfigure}
+%\caption{Effectiveness of GCMP model on sampled datasets.}
+%\label{exp:effectiveness}
+%\end{figure*}
+%We first study the effects of introducing gap parameter $G$ on pattern discovery.
+%As shown in Figure~\ref{fig:related_work_scalability},
+%existing works are not able to handle large trajectories, 
+%we sample and cluster $1$ million trajectory points from the three real data.
+%We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
+%of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
+%
+%We can see from Figures~\ref{exp:effectiveness} that the number of patterns
+%discovered by GCMP is positively related to $G$. When $G =1$, the number
+%of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
+%the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
+%patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
+%when $G$ is $50$. The reason is that when $G$ is large enough,
+% all \emph{platoon}s are $G$-connected. Similar
+% trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
+% patterns converge at $G=50$; while in (b) and (c) the two patterns converge
+% at $G=60$ and $G=40$ respectively. We further
+% note that, existing patterns has different granularity in temporal domain. As we seen
+% from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
+% \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
+% the temporal domain of patterns, GCMP can discover the patterns more precisely. 
+% These results confirms the usefulness of GCMP in expressing other patterns.
+%  
+%
 
 \subsection{Performance Comparison}
+Since the both TRPM and SPARE utlizes pruning rules that related to the 
+pattern parameters $M$,$L$,$G$,$K$. It is interesting to
+see the performance of TRPM and SPARE under different parameter settings.
 %\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
@@
 % 36\% of TRPM's shuffle time. 
-To study the performance of TRMP and SPARE, we run both algorithms 
-in all three datasets under different parameter settings. We report
-their overall performance as in Figures~\ref{exp:performance_vary}.
+%To study the performance of TRMP and SPARE, we run both algorithms 
+%in all three datasets under different parameter settings. 
+We run both of the two algorithms in all three dataset and report
+their overall performances as in Figures~\ref{exp:performance_vary}.
 In brief, both algorithms are able to handle the large-scaled real
-datasets. However, we observe that TRMP's performance is very
-dependent on the pattern parameters.
-In cases when $G$ is large, TRMP takes near three hours (e.g., in Taxi dataset).
+datasets. However, we observe that TRMP's performance largely depends
+on the pattern parameters. In cases when $G$ is large, 
+TRMP takes near three hours (e.g., in Taxi dataset).
 In contrast, SPARE performs quite stable. Another general observation
-is that both algorithms run slower in the Taxi dataset as compared to in
+is that both algorithms run slower in the Taxi dataset as compared to
 other two datasets. This is because Taxi dataset contains
@@
 in almost all cases, SPARE outperforms TRMP and analyze the detail
-of each scenario separately:
+of each scenario separately.
 
+\subsubsection{Effects of pattern parameters M,L,K,G}
 \textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
@@
 size of partition in TRPM but low pruning power in SPARE. This explains the
-superiority of TRPM. Note that, when $K$ is small, TRPM is at most 1.3 times
+superiority of TRPM. Note that, when $K$ is small, TRPM is 30\% 
 faster than SPARE and the absolute time is less than three minutes.
 
-\textbf{Vary $L$}:Figure~\ref{} presents the performance
-of TRPM and SPARE when $L$ changes under three datasets.
+\textbf{Vary $L$}:Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performance
+of TRPM and SPARE when $L$ changes under three datasets. We can see that $L$
+provides good pruning power from $10$ to $20$ for both TRPM and SPARE. For TRPM,
+the benefit of increasing $L$ is bi-folded. First, when $L$ increases from $10-50$, 
+the $\eta$ decreases, which reduces the shuffle and partition sizes. Second, when
+$L$ increases, the initial pruning in line-sweep is more beneficial. For SPARE,
+increasing $L$ does not affect the shuffling, but benefits the simplification.
+It is also observed that when $L$ increases, the pruning power increases marginally.
+This is because that many patterns contains short segments, when $L$ increases,
+these patterns are largely pruned.
 
-\textbf{Vary $G$}:Figure~\ref{} presents the performance
-of TRPM and SPARE when $G$ changes under three datasets.
+\textbf{Vary $G$}:Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performance
+of TRPM and SPARE when $G$ changes under three datasets. In general, both TRPM and SPARE
+runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
+exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
+that there is an burst of TRPM as $G$ increases. The major reason is that 
+during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
+This makes the candidate set exponentially grows and 
+the join operation becomes very expensive.
+Unlike TRPM, SPARE is although affected by the increase of $G$, 
+but the impact is marginal as compared
+to TRPM. This is because, although true patterns may become 
+exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
+can quickly output true patterns without enumerating every of its subset.
+%\subsubsection{Effects of clusters $\epsilon$, minPt}
 
-%\subsubsection{Effects of clusters $\epsilon$, minPt}
+\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary}
+\begin{figure}[h]
+\centering
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
+        \caption{Number of patterns vary $L$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
+        \caption{Number of patterns vary $G$}
+    \end{subfigure}    
+\caption{Number of patterns discovered in three datasets on different parameters}
+\label{exp:patterns_vary}
+\end{figure}
 
@@
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
-        \caption{Shopping Vary $M$}
+        \caption{Shopping vary $M$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
-        \caption{Shopping Vary $K$}
+        \caption{Shopping vary $K$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
-        \caption{Shopping Vary $L$}
+        \caption{Shopping vary $L$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
-        \caption{Shopping Vary $G$}
+        \caption{Shopping vary $G$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
-        \caption{Geolife Vary $M$}
+        \caption{Geolife vary $M$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
-        \caption{Geolife Vary $K$}
+        \caption{Geolife vary $K$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
-        \caption{Geolife Vary $L$}
+        \caption{Geolife vary $L$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
-        \caption{Geolife Vary $G$}
+        \caption{Geolife vary $G$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
-        \caption{Taxi Vary $M$}
+        \caption{Taxi vary $M$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
-        \caption{Taxi Vary $K$}
+        \caption{Taxi vary $K$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
-        \caption{Taxi Vary $L$}
+        \caption{Taxi vary $L$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
-        \caption{Taxi Vary $G$}
+        \caption{Taxi vary $G$}
     \end{subfigure}       
@@
 
-\subsubsection{Effects of pattern parameters $M,L,K,G$}
+\subsubsection{Detail comparison between SPARE and TRPM}
 
 \subsection{SPARE Analysis}
+
+\subsubsection{Scalability}
+\begin{figure}[h]
+\centering
+   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
+\caption{Scalability of SPARE vary. $N$ under different datasets.}
+\label{exp:patterns_vary}
+\end{figure}
+
 \subsubsection{Load Balance}
-\subsubsection{Scalability}

### 2016-06-23 appendix.tex
Lets fix sec 6!!
aaaaa

@@
 \begin{proof}
-For soundness, let $P$ be a pattern enumerated by SPARE, then $\forall o_1, o_2 \in P.O$ they belongs to the same star.
-As the enumerate algorithm only reduce the time sequences, $P.T \subset e(o_1,o_2)$.
-This indicates that, $\forall t \in P.T$, $t\in e(o_1,o_2)$.
-By the definition of star, $C_t(o_1) = C_t(o_2)$.
-Since $P.T$ conforms to $K,L,G$,  by the definition of GCMP, $P.T$ is a true pattern.
-For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with $Sr_s$. 
-First, based on the definition of star partition, every object in $P.O$ appears in $Sr_s$.
-Note that $P.T$ conforms to $K,L,G$, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence.
-This indicates that any $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.
-Next, we prove in iterations $(1,\ldots,P.|O|-2)$, $P.O \subset U_i$, where $U_i$ is the forward closure.
+For soundness, let $P$ be a pattern enumerated by SPARE.
+Since the enumerate algorithm only reduces the time sequences, for any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$.
+By the definition of star, $\forall t \in T, C_t(o_1) = C_t(o_2)$.
+As $T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
+For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with input $Sr_s$. 
+First, based on the definition of star, every object in $P.O$ appears in $Sr_s$.
+Since $P.T$ is decomposable, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence.
+This indicates that $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.
+Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure.
 We prove by induction.
-When $i$ = 2, it obviously holds.
-If $P.O \subset U_i$ at iteration $i$, then any subset of $P.O$ with size $i+2$ are in the candidate set.
-In iteration $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$).
-This suggests that no subsets are removed by Line~\ref{code:output1}.
+When $level$ = 2, it obviously holds.
+If $P.O \subset O_u$ at \emph{level=$i$}, then any subset of $P.O$ with size $i$ are in the candidate set.
+In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$).
+This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}.
 Then, $P.O \subset U_{i+1}$ holds.
-In summary, $P.O$ does not pruned by simplification and monotonicity and forward closure, therefore $P$ can be returned by SPARE.
+In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
 %Next, observe that at each iteration $i$, candidates with size $i+2$ are generated.

### 2016-06-23 sec5_spm-bk.tex
Lets fix sec 6!!
aaaaa

@@
 \label{sec:spm}
-The aforementioned replicate partitioning is based on the temporal dimension 
-and results in groups of snapshots in each partition. 
+The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks.
+First, the replication relies on $\eta$ which could be large.
+Second, the same valid pattern may be discovered from different partitions which results in redundant work.
+%and results in groups of snapshots in each partition.
+% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
 To resolve the limitations caused by the replicate partitioning, 
@@
 
-It is challenging to directly find the optimal $\Gamma$. 
-First, suppose there are $n!$ permutation matrices. 
-Such a high complexity is trivially unpractical. Second,
-since $G$ is unknown in prior,
-the vertex order cannot be planned beforehand. 
-Despite these challenges, we find a simple $O(1)$ time 
-solution which is good enough as stated in the 
-following theorem.
+Although it is very challenging to find the optimal vertex id ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
 
-\begin{theorem}[Balance of Star Partition]
+\begin{theorem}
 \label{THM:SPM_LB}
-Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
-Let $\Gamma^*$ be optimal size of straggler among all vertex orders.
-Let $\Gamma$ be the size of straggler wrt an random vertex order $P$. 
-With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
-That is,  with probability $1-1/n$, 
-$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
+Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering.
+With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
 \end{theorem}
-
-In fact, we have a tighter bound of $(\Gamma - \Gamma^*)$ if 
-the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
-high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
-Utilizing Theorem~\label{THM:SPM_LB}, in star partition, it is safe 
-to choose the object IDs as the vertex order. This because real object IDs are often 
-hashed and can be deemed as random.
+\begin{proof}
+In Appendix XXX.
+\end{proof}
+If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
+\begin{theorem}
+\label{THM:SPM_LB_INC}
+Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
+high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
+\end{theorem}
+\begin{proof}
+In Appendix XXXX.
+\end{proof}
+Hence, we can simply use object id to determine the vertex ordering in our implementation.
 
@@
 For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
-To generalize the idea, we propose two concepts named \textit{maximal $G$-connected subsequence} and \emph{candidate sequence}.
+To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.
 
@@
 \begin{example}
-Let $G=2$, consider $T_1=(1,2,4,5,6,9,10,11,13)$. $T_1$ has two maximal $2$-connected subsequences:
-$T_1^A=\{1,2,4,5,6\}$ and $T_1^B=\{9,10,11,13\}$. Consider $T_2=(1,2,4,5,6,8,9)$,
-since $T_2$ is $2$-connected, thus $T_2$ has only one maximal $2$-connected subsequence which is
+Suppose $G=2$ and consider two sequences $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$.
+$T_1$ has two maximal $2$-connected subsequences:$T_1^A=(1,2,4,5,6)$ and $T_1^B=(9,10,11,13)$.
+This is because the gap between $T_1^A$ and $T_1^B$ is $3$ and it is impossible for the timestamps from  $T_1^A$ and $T_1^B$ to form a new subsequence with $G\leq 2$.
+Since $T_2$ is $2$-connected, $T_2$ has only one maximal $2$-connected subsequence which is
 itself. 
-%Let $G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$
-%%
-% XXX EXPLAIN HOW TO DERIVE THE MAXIMAL G-CONNECTED SUBSEQUENCES OF $T_1$ and $T_2$. 
 \end{example}
 
-\begin{definition}[Candidate Sequence]
-$T$ is a candidate sequence if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
+The maximal $G$-connected subsequence has the following two properties:
+\begin{lemma}\label{lemma:union-property}
+Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
+\end{lemma}
+\begin{proof}
+We assume $T_i\cap T_j\neq \emptyset$.
+Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$.
+Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$.
+Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$.
+Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$.
+Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected.
+Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected.
+This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.
+
+To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$.
+Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$.
+Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$.
+If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected.
+If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$.
+Both cases lead to contradiction.
+\end{proof}
+
+\begin{lemma}\label{lemma:subset-property}
+If $T_1$ is a subset of $T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that $T_1'$ is a subset of $T_2'$.
+\end{lemma}
+\begin{proof}
+Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$.
+Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$.
+If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction.
+Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
+\end{proof}
+
+\begin{definition}[Decomposable Sequence]
+$T$ is decomposable if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
 \end{definition}
@@
 \begin{example}
-Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a candidate sequence
-since one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
-In contrast, $T_2$ is a candidate sequence because it has one maximal $2$-connected subsequence
-and it is $2$-consecutive with size greater than $4$.
+Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
+because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
+In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than than $4$.
 \end{example}
@@
 \begin{definition}[Sequence Simplification]
-Given a sequence $T$ and the GCMP parameters $G,L,K$, a $T^\#$ is
-the simplified sequence of $T$ if (1) $T^\#$ is contained in $T$, i.e., $T^\# \subseteq T$.
-(2) $T^\#$ is a candidate sequence, and (3) no other candidate sequence
-$T^\#_1$ is contained in $T$ and contains $T^\#$.
-%GIVEN A SEQUENCE, PLEASE UNIQUELY DEFINE ITS SIMPLIFICATION OUTPUT.
+Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
+\begin{enumerate}
+\item $f$-step: remove segments of $T$ that are not $L$-consecutive;
+\item $g$-step: among the maximal $G$-connected subsequences of $f_L(T)$, remove those with size smaller than $K$.
+\end{enumerate}
 \end{definition}
-Note that, not every $T$ has the simplified sequence.  For example, if $L =3$,
-then the simplified sequence of $(1,2,5,6)$ does not exists.
+
+\begin{example}
+Take $T=(1,2,4,5,6,9,10,11,13)$ as an example for sequence simplification. 
+Let $L = 2, K = 4$ and $G = 2$. In the $f$-step, $T$ is reduced to $f_2(T)=(1,2,4,5,6,9,10,11)$. 
+The segment $(13)$ is removed due to the constraint of $L=2$. 
+$f_2(T)$ has two maximal $2$-consecutive subsequences: $(1,2,4,5,6)$ and $(9,10,11)$. 
+Since $K=4$, we will remove $(9,10,11)$ in the $g$-step. Finally, the output is $\mathtt{sim}(T)=(1,2,4,5,6)$.
+\end{example}
+
+It is possible that the simplified sequence $\mathtt{sim}(T)=\emptyset$. For example, Let $T=(1,2,5,6)$ 
+and $L=3$. All the segments will be removed in the $f$-step and the output is $\emptyset$.
+We define $\emptyset$ to be not decomposable. 
+%Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
+We provide an important property of the sequence simplification process as follows:
+\begin{lemma}\label{lemma:decom-sim}
+If sequence $T$ is a superset of any decomposable sequence, then $\mathtt{sim}(T) \neq \emptyset$.
+\end{lemma}
+\begin{proof}
+It is obvious that $\mathtt{sim}(T)$ is a one-to-one function.
+Given an input sequence T, there is a unique  $\mathtt{sim}(T)$.
+Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.
+
+Suppose $T_p$ can be decomposed into a set of maximal $G$-connected
+subsequences $T_p^1, \ldots, T_p^m$ ($m \geq 1$).
+Since $T_p$ is a subset of $T$, all the $T_p^i$ are also subsets of $T$.
+By definition, each $T_p^i$ is $L$-consecutive.
+Thus, in the $f$-step of $\mathtt{sim}(T)$, none of $T_p^i$ will be removed.
+In the $g$-step, based on Lemma~\ref{lemma:subset-property}, we know that each $T_p^i$ has a superset in the maximal $G$-connected subsequences of $f_L(T)$.
+Since $|T_p^i|\geq K$, none of $T_p^i$ will be removed in the $g$-step.
+Therefore, all the $T_p^i$ will be retained after the simplification process and $\mathtt{sim}(T) \neq \emptyset$.
+\end{proof}
+
+\eat{
 Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
@@
 \end{proof}
+}
 
+\eat{
 Next, we design an efficient simplification process with linear complexity.
@@
 \end{algorithm}
+}
 
-\begin{example}
-Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
-In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
-is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
-are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
-from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
-\end{example}
+With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
+sequences to facilitate the pruning in the Apriori algorithm.
 
-With the concepts of \textit{candidate sequence} and \textit{sequence simplification}, we are ready to define the monotonic property that can be used for pruning.
-\begin{theorem}\label{THM:SPM_TM}
-Given a candidate pattern $P=\{O:T\}$, if sequence $P.T$ cannot be simplified to a candidate sequence, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
+\begin{theorem}[Monotonicity]\label{THM:SPARE_MONO}
+Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
 \end{theorem}
@@
 
-\subsubsection{Apriori Algorithm}
+\subsubsection{Apriori Enumeration}
+We then design the Apriori enumeration method to
+systematically discover all valid patterns in a star.
+%During the enumeration, we refer a candidate pattern
+%$P$ as a $R$-candidate if $|P.O|=R$.
+The enumeration method discover patterns iteratively using ``bottom-up'' order:
+candidates with smaller objects set grow one object per iteration.
+%
+%in iteration $i$,  all $(i+1)$-candidates grows
+%to $(i+2)$-candidates.
+%
+Enumeration ends if no
+further candidates can be generated.
+
+ Due the \emph{monotonicity} proved in Theorem~\ref{THM:SPARE_MONO}, we are able to use the \emph{monotonic pruning} and \emph{forward closure check} to boost the enumeration process.
+We show the detail of the process
+in Algorithm~\ref{algo:apriori_mining}. As a start, 
+each input edge is treated as a candidate pattern, with the 
+inverted list as the time sequence. These candidates
+are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}).
+In initialization, the inverted lists are simplified (Line~\ref{code:simp1}) and unqualified lists are pruned (Line~\ref{code:init-prune}).
+Throughout the algorithm, we maintain a set of candidates $\mathbf{C}$ which is initialized to the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).
+
+In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}).
+The join of two candidates $c$ and $g$ creates a
+new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}). During the join,
+we use \emph{sequence simplification} to detect unqualified candidates.
+By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}).
+If a valid candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).
+
+After the join finishes, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}).
+We test whether the union of all candidates in $\mathbf{C}$ forms a valid pattern.
+If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).
+
+\eat{
+to union all the candidates in the current candidate set, and quickly check whether the
 
 To systematically discover valid patterns in each star,
-we design the \emph{Apriori Mining} algorithm. 
+
+we enumerate all valid patterns in ``bottom-up" order: 
+pattern candidates with smallest object sizes are enumerated
+first and grew to pattern candidates with larger object sizes.
+During the enumeration, we call a candidate pattern
+$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
+a star as input, and treat each edge as a $2$-pattern.
+
+The input of
+the enumerator is a star. Each edge
+in the star is treated a $2$-candidate, with the inverted
+list to be the time sequence.
+
+we design the \emph{Apriori Mining} algorithm. We borrow
+the terminologies in classic Aprirori algorithm: a candidate
+pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
+candidates grows from $2$-pattern level by level.
+
 To describe the algorithm, we call a candidate pattern $R$-pattern 
@@
 \Require{$Sr_s$}
-\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State{Simply $e(s,t)$} \Comment{ Simplification}
-\State {Ground.add($\langle \{s,t\}, T \rangle$)}
-\State {Lv $\gets$ Ground}
+\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
+\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
+\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
+\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
+\EndFor\label{code:init-end}
+\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
+\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
+		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
+		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
+			\ForAll {$g \in \mathbf{G}$}		
+				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
+				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
 			\EndFor
-\While{Lv is not empty}
-		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
-		\State {Remove false patterns in Lv}
-		\Comment{Monotonicity}
-		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
-			\State{output.add(Lv)} 
-			\State{break}
-		\EndIf
-\EndWhile
-\State output.addAll($Lv$)
-\State \Return output
+			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
+		\EndFor	\label{code:join-ends}
+		\State {$\mathbf{C} \gets \mathbf{N}$}
+		\State $U \gets $ union of $n_i \in \mathbf{C}$	\label{code:fc-checking-start}
+		\If {$U$ is a valid pattern}
+			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
+			\State break;
+		\EndIf \label{code:fc-checking-ends}
+\EndWhile\label{code:level-ends}
+\State $\mathbf{OT}$.addAll$(\mathbf{C})$
+\State \Return $\mathbf{OT}$
 \end{algorithmic}
@@
 
-An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-higher level candidates are generated by joining lower level candidates. When no more candidates 
-can be generated, the algorithm stops by outputting the valid patterns.
+%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
+%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
+%higher level candidates are generated by joining lower level candidates. When no more candidates 
+%can be generated, the algorithm stops by outputting the valid patterns.
+%
+
+\begin{example}
+We use Figure~\ref{fig:star_partition} (c) to 
+demonstrate the power of candidate pruning. 
+As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{simplification}. 
+Subsequently, all further candidates containing $\{3,6\}$ 
+are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
+of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
+valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+\end{example}
+
 %
@@
 %\end{theorem}
+}
 
-\begin{example}
-We use Figure~\ref{fig:star_partition} (c) to 
-demonstrate the power of candidate pruning. 
-As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
-timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
-are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
-of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
-valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
-\end{example}
+\subsection{Put It Together}
+With the star partition and the Apriori enumerator, we are ready to assemble the Star Partition and ApRiori Enumerator (SPARE) framework. 
+We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows: After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
+In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+Each reducer is an Apriori Enumerator.
+When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
+Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
+Then it enumerates all true patterns from the candidate patterns.
+The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
+Note that we do not need to create an actual aggregate graph.
+Instead, we only to emitted the directed edges (Line~\ref{code:spm-edge-direct}).
 
-\subsection{Correctness of SPARE}
+\begin{algorithm}
+\caption{Star Partition and ApRiori Enumerator}
+\label{algo:spm_overview}
+\begin{algorithmic}[1]
+\Require list of $\langle t, S_t \rangle$ pairs
+\State {---Map phase---}
+\label{code:spm-map-start}
+\ForAll{$C \in S_t$}
+	\ForAll {$(o_1 ,o_2) \in C \times C$}
+	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet, if $o_1 < o_2$~\label{code:spm-edge-direct}
+	\EndFor
+\EndFor
+\label{code:spm-map-end}
+
+\State {---Partition and Shuffle phase---}
+\label{code:spm-shuffle-start}
+\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
+	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
+	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
+\EndFor
+\label{code:spm-shuffle-end}
+
+\State {---Reduce phase---}
+\label{code:spm-reduce-start}
+\ForAll{$\langle o, Sr_{o} \rangle$}
+\State AprioriEnumerator($Sr_o$)
+\EndFor
+\label{code:spm-reduce-end}
+
+\end{algorithmic}
+\end{algorithm}
+
+Our SPARE framework does not rely on the pattern parameters to determine the partition size,
+which is more stable than TRMP. In addition, we observe that the patterns mined from each
+reducer are unique. This property is stated as follows:
+\begin{theorem}[Pattern Uniqueness]
+\label{LEM:SPM_CORRECT}
+Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
+the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
+Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
+\end{theorem}
+\begin{proof}
+We prove by contradiction. Suppose exists $p_i \in P_i$ and $p_j \in P_j$ s.t. $p_i.O \equiv p_j.O$.
+Let $o_i$ (resp. $o_j$) be the object with smallest ID in $p_i.O$ (resp. $p_j.O$).
+Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$,  which contradicts with
+the assumption $p_i.O \not\equiv p_j.O$. 
+\end{proof}
+
+Theorem~\ref{LEM:SPM_CORRECT} confirms the superiority of SPARE to TRPM. In TRPM, a pattern
+may be repeatedly discovered from different partitions, while in SPARE a pattern is only discovered once.
+This suggests that SPARE require less redundant works.
+We finally conclude this section with the following theorem:
+
+\begin{theorem}
+\label{THM:SPM_CORRECT}
+The SPARE framework guarantees completeness and soundness.
+\end{theorem}
+\begin{proof}
+See Appendix XXXX.
+\end{proof}
+
+\eat{ \subsection{Correctness of SPARE}
 We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.

### 2016-06-23 sec7_experiment.tex
Lets fix sec 6!!
aaaaa

@@
 
+\textbf{Algorithms}: We implement TRPM, SPARE and SPARE+ for comparison study.
+TRPM and SPARE are implement as described in Section 4 and 5.
+In SPARE+, we hook an additional load balance stage to the map phase.
+When the map phase completes, SPARE+ collects the size of stars from all mappers.
+Then we use the best-fit strategy for task allocation.
+In best-fit, tasks are assigned in decreasing order of
+their sizes, and the biggest unassigned task is allocated to the current most empty reducer.
+Our task size is estimated on the edges of stars, that is we try to balance the edges processed by each reducers.
+
 %\subsection{Effects of $G$ on GCMP}
@@
 \subsection{Performance Comparison}
-Since the both TRPM and SPARE utlizes pruning rules that related to the 
+Since the both TRPM and SPARE utilizes pruning rules that related to the 
 pattern parameters $M$,$L$,$G$,$K$. It is interesting to
@@
 
-\subsubsection{Detail comparison between SPARE and TRPM}
+%\subsubsection{Anatomy of SPARE and TRPM}
 
 \subsection{SPARE Analysis}
+Since SPARE is superior than TRPM, we further study the \emph{load balance} and \emph{scalability} of SPARE.
+
+\subsection{Pruning Power}
+
+\subsubsection{Load Balance}
+We first compare SPARE and SPARE+ by analyzing the running time at
+each map-reduce stage. The detail anatomy is shown in Figure~\ref{}
+
+To further study the superior performance of SPARE+, we compare load distribution from all executors. We display the result in Figure~\ref{}.
 
 \subsubsection{Scalability}
+We then test the performance of SPARE under different number of executors.
+The result on the three dataset is presented in Figure~\ref{exp:scalability}.
+We can see from the Figure that SPARE achieves good scalability under all three cases.
+For instance, for Taxi dataset, when the executors rises from 14 to 54, the performance improves 3.5 times which is almost linear to the increase of executors.
+Such a pattern also holds for other two datasets.
+
 \begin{figure}[h]
@@
 \caption{Scalability of SPARE vary. $N$ under different datasets.}
-\label{exp:patterns_vary}
+\label{exp:scalability}
 \end{figure}
-
-\subsubsection{Load Balance}

### 2016-06-24 sec1_introduction.tex
Commit first
Updates on Experiments Graphs
Revise Sec 5 last portion and Appendix
Lets fix sec 6!!
aaaaa
An almost finished version
Continue to revise

@@
     \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
-    is used with up two 2.4 million data points. Default parameters are $M=10$ $K=20$ $L=10$.}
+    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
     \label{fig:related_work_scalability}
@@
 First, we replicate the snapshots in multiple data chunks to support efficient parallel processing.
-Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance.
-For each star, an Apriori method is adopted to mine the co-movement patterns.
-Third, we leverage the \emph{temporal monotonicity} property of GCMP to design several optimization techniques including \emph{edge-simplification} to prune initial candidates, \emph{temporal apriori pruning} and \emph{forward closure checking} to reduce the number of enumerated candidates in the Apriori algorithm.
+Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance.
+For each star, an Apriori Enumerator is adopted to mine the co-movement patterns.
+Third, we leverage the \emph{temporal monotonicity} property of of GCMP
+to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
 %
@@
 temporal points. 
-The results show that our parallel scheme efficiently supports GCMP mining in large datasets.
+The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
 In particular, with near 200 million trajectory points, 
-our scheme runs within 10 minutes using 135 cores. Whereas centralized solution takes near 7 hours for 
-1 million trajectory points.
-Moreover, our optimized SPM methods achieves upto XXX times efficiency
-as compared to the baseline algorithm with near linear scalability.
+SPARE runs in 15 minutes using 172 cores. Whereas
+centralized solutions take near 7 hours 
+for 1 million trajectory points.
+Moreover, our optimized SPARE methods achieves upto 10 times efficiency
+as compared to the baseline algorithm with almost linear scalability.
 
@@
 \emph{star partition and mining} is presented in Section~\ref{sec:spm}.
-Section~\ref{sec:opt} discusses various optimization techniques.
 Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system.

### 2016-06-24 sec4_baseline-bk.tex
An almost finished version
Continue to revise

@@
-\section{Baseline: Temporal Replication and Parallel Mining}
-\label{sec:trm}
-We resort to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining.
-Since a GCMP pattern may cross multiple temporal segments, 
-we cannot simply split the trajectory database into disjoint partitions and conduct parallel mining within each partition.
-Instead, we need certain data replication to guarantee that no matching patterns are missing.
-
-We propose a framework named \emph{Temporal Replication and ParallelMining} (TRPM), 
-as illustrated in Figure~\ref{fig:trm}. The mining procedure consists of 
-two cycles of map-reduce jobs connected in a pipeline manner. In the first 
-map-reduce cycle, input trajectories are grouped into snapshots and then clustered. 
-In particular, object locations at the same timestamps form
-a snapshot in the map-phase. In the reduce phase, objects in a snapshot
-are clustered by the supplied clustering methods (e.g., DBSCAN or disk-based) in parallel.
-The reducers finally output clusters of objects in each snapshot, 
-represented by a list of $\langle t, S_t \rangle$ 
-where $t$ is the timestamp and $S_t$ is a set of clustered object at snapshot $t$. 
-The outputs will be fed into the second cycle of map-reduce jobs, whose details are presented in Algorithm~\ref{algo:trm_overview}.
-Intuitively, we first replicate each snapshot and each consecutive segment with $\eta$ snapshots is considered as one data partition.
-Then, a \emph{Line Sweeping} method is developed to discover GCMP within each partition in the reduce stage.
-The final patterns from all partitions are then stored into external storage (e.g, HDFS).
-In the following, we are interested to examine the minimum $\eta$ and introduce the \emph{Line Sweeping} algorithm in details.
-
 \begin{figure*} [t]
@@
 
-\begin{algorithm}
-\caption{Temporal Replication and Parallel Mining}
-\label{algo:trm_overview}
-\begin{algorithmic}[1]
-\Require list of $\langle t, S_t \rangle$ pairs
-\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
-\State {---Map Phase---}
-\label{code:trm-map-start}
-\ForAll{$\langle t, S_t \rangle$}
-	\ForAll{$i \in 1...{\eta-1}$}
-		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
-	\EndFor  
-\EndFor
-\label{code:trm-map-end}
-\State {---Partition and Shuffle Phase---}
-\label{code:trm-par-start}
-\ForAll{$\langle t, S \rangle$ pair} 
-\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
-\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
-\EndFor
-\label{code:trm-par-end}
-\State {---Reduce Phase---}
-\label{code:trm-red-start}
-\ForAll{$\langle t,\lambda_t \rangle$}
-\State lineSweepMining($\lambda_t$)
-\label{code:trm-red-end}
-\EndFor
-\end{algorithmic}
-\end{algorithm}
+\section{Baseline: Temporal Replication and Parallel Mining}
+\label{sec:trm}
+In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining.
+The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
+There are two cycles of map-reduce jobs connected in a pipeline manner.
+The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining.
+In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase.
+Finally, the reducers output clusters of objects in each snapshot, represented by a list of $\langle t,S_t \rangle$ pairs, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
 
-%\subsection{Temporal Replication}
-In temporal replication, every partition
-contains $\eta$ consecutive snapshots.
-Therefore, determining $\eta$ is critical in ensuring the
-correctness and efficiency of TRPM.
-If $\eta$ is too small, some cross-partition patterns may be missed out. 
-On the other hand, if $\eta$ is too large, the shuffle and reduce
-stage of TRPM would incur expensive costs.
-To guarantee the \emph{complete} discovery of all patterns, we enforce the
-following statement on $\eta$: \emph{Let $T'$ be the \emph{shortest} 
+Our focus in this paper is the second map-reduce cycle of parallel mining, which essentially consists of two key questions to solve.
+The first is how to employ effective data partitioning such that the mining can be conducted independently; and the second is how to efficiently mine the valid patterns within each partition.
+
+It is obvious that we cannot simply split the trajectory database 
+into disjoint partitions because a GCMP pattern requires $L$-consecutiveness 
+and the corresponding segments may cross multiple partitions. 
+Our strategy is to use data replication to enable parallel mining. 
+Each snapshot will replicate its clusters to $\eta-1$ preceding snapshots.
+In other words, the partition for the snapshot $S_t$ contains clusters 
+in $S_t$, $S_{t+1}\ldots,S_{t+\eta-1}$. 
+Determining a proper $\eta$ is critical in ensuring the
+correctness and efficiency of TRPM. If $\eta$ is too small, 
+certain cross-partition patterns may be missed. 
+If $\eta$ is set too large, expensive network communication and 
+CPU processing costs would be incurred in the map and reduce phases respectively. Our objective is to find an $\eta$ that is not large but can guarantee correctness.
+
+In our implementation, we set $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$.
+Intuitively, $K$ timestamps generates at most $\lceil \frac{K}{L} \rceil - 1$ gaps as the length of each $L$-consecutive segment is at least $L$.
+Since the gap size is at most $G-1$, $(\lceil \frac{K}{L} \rceil - 1)*(G-1)$ is the upper bound of timestamps allocated to gaps.
+The remaining part $K+L-1$ is used to capture the upper bound allocated for the $L$-consecutive segments.
+We formally prove that $\eta$ can guarantee correctness.
+
+\eat{
+Before moving on to find the value of $\eta$, 
+we first use $\rho_{G,L,K}(T)$ to define the \emph{min-spanned valid subsequence} 
+of a sequence $T$. In simple words, $\rho_{G,L,K}(T)$ is the 
+subsequence of $T$ with the smallest range and is valid wrt. $K,L,G$. 
+%Let $\eta_T$ denote
+%the range of $\rho_{G,L,K}(T)$.
+To guarantee that no valid patterns are missing, $\eta$ needs
+to be greater than the range of $\rho_{G,L,K}(T)$ for any
+valid sequence $T$. To see this, consider an arbitrary valid sequence $T$.
+Since each partition contains $\eta$ snapshots,
+if $\eta \geq \range(\rho_{G,L,K}(T))$ holds, $\rho_{G,L,K}(T)$ must be completely located in one partition. Therefore, the patterns associated with $T$ would not be missing.
+Formally, $\eta$ can be computed as:
+\begin{equation}
+\eta = \max\{\range(\rho_{G,L,K}(T)) | T \text{ is valid wrt. } G,L,K\}
+\end{equation}
+
+Directly compute such $\eta$ is challenging. However,
+we provide the following theorem which states a bounded estimation on $\eta$: 
+}
+
+\begin{theorem}
+\label{THM:RP_ETA}
+$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
+\end{theorem}
+\begin{proof}
+Given a valid pattern $P$, consider its time sequence $T$. Since $T$ is valid wrt. $G,L,K$,
+we can always find a minimum valid subsequence of $T$ denoted as $T'$.
+We prove our theorem by showing that $\range(T') \leq \eta$.
+Since $T'$ is valid, we may view $T'$ as interleaving 
+segments and gaps. That is $T'$ can be written as $l_1,g_1,\ldots,l_{n-1},g_{n-1},l_n$ ($n \geq 1$),
+where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
+is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
+is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
+last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
+is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
+Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
+using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
+\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, consider the difference between $K$ and $K'$. Let 
+$\Delta = K- K'$. To ensure $T'$'s minimum validity, $l_n$ must equal to $\min(L, \Delta)$.
+Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. The last
+inequality dues to the fact that $\Delta \geq 1$.
+Therefore, $\range(T') \leq \eta$. It follows that, for every valid pattern $P$, there must
+exists a partition $\lambda$ with size $\eta$, such that $P$ is also valid in $\lambda$. This proves our theorem.
+\end{proof}
+
+Note that Theorem~\ref{THM:RP_ETA} does not state the optimal value of $\eta$
+for a given $G,L,K$. However, for any $G,L,K$, $\eta$ does not differ from
+the optimal value by at most $L-1$. To see this, for any $G,L,K$, we can
+generate a sequence $T$ by repeating the following pattern, a $L$-segment followed by $G$-gap. 
+The repetition stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
+It is easy to see that $T$ is minimal valid subsequence of itself, then $\eta^*  \geq \range(T) \geq (\lceil \frac{K}{L}\rceil -1)(G-1) + K$.
+Therefore $\eta-\eta^* \leq L-1$.
+
+\eat{
+In order to formally compute the minimum value of $\eta$,
+we enforce the
+following statement on $\eta$:
+%I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
+ \emph{Let $T'$ be the \emph{shortest} 
 valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
@@
 the minimum $\eta$ and temporal parameters using the following theorem:
-%
-%
-%Given any partition method, its correctness can be defined
-%using \emph{completeness} and \emph{soundness} as follows: 
-%
-%\begin{definition}[Completeness and Soundness]
-%Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
-%into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
-%if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
-%$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $Tr$.
-%\end{definition}
-
-%Intuitively, \emph{soundness} avoids any false patterns in any partitions; while \emph{completeness}
-%ensures no patterns are missed out by the partitions. In temporal replication, 
-%the replication factor $\eta$ is critical. If $\eta$ is to small, such 
-%partition may not be \emph{complete}. On the other hand, a large $\eta$ would incur
-%expensive costs in the shuffle and reduce stages. Therefore, we need to find
-%the \emph{minimum} $\eta$ such that the \emph{completeness} and \emph{soundness} are
-%satisfied. Such an $\eta$ value is as stated in the following theorem:
 
@@
 \end{proof}
+}
 
 Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
-form a partition. In particular, for every snapshot $S_t$, there is
-a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. With this partition strategy,
-when discovering GCMPS in $\lambda_t$, we only need to keep the pattern candidates whose
-object set are in $S_t$. This motivates to design an efficient 
-\emph{line-sweep} mining (LSM) method for each partition. The intuition of LSM is 
-to sequentially scan all snapshots. During scanning, a set of pattern candidates is maintained.
-When all snapshots are scanned, the remaining candidates are the true patterns.
-The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
-% To discover
-%valid patterns from each partition, we design a \emph{line-sweep} mining (LSM) method as 
-%shown in Algorithm~\ref{algo:line-sweep}. 
-%The algorithm sequentially scans snapshots in a partition. 
-%During the scan, it
-A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
-is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
-During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
-the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
-false patterns are deleted (line~\ref{code:ls-remove}). 
-Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
+form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. 
+Our next task is to design an efficient pattern mining strategy within each partition. 
+Since we have a partition $\lambda_t$ for every snapshot $S_t$,
+we only need to report the patterns that appears in $S_t$ for $\lambda_t$. This would largely
+reduce the overlapping computation between different partitions. To facilitate the goal,
+%
+%Since we have a partition $\lambda_t$ for every snapshot $S_t$, in the reduce phase, we only need to mine the patterns whose object set is in $S_t$ for partition $\lambda_t$.
+%
+%
+we propose a \emph{line-sweep} algorithm. In brief, we treat clusters in $S_t$ as initial candidate patterns.
+Then, we grow a candidate by intersecting it with clusters from next snapshots. When every snapshot is examined,
+we output all valid candidate patterns.
 
-%It maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
-%The algorithm starts by inserting clusters at $S_t$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
-%Subsequently, when scanning $S_j$, clusters in $C$ are joined with clusters at $S_j$ to generate
-%a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
-%form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).
+The detail of \emph{line-sweep} is presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $\mathbf{C}$ (Line~\ref{code:ls-can-set}) during the sweeping. In the beginning, 
+all clusters in $S_t$ with sizes greater than $M$ form the initial candidates (Lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
+Our algorithm then sequentially sweeps each snapshots (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}).
+During sweeping snapshot $S_j$, candidates in $\mathbf{C}$ join with clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}). 
+%The join of candidate $c$ and cluster $s$ creates a
+%new candidate $c'$ (Line~\ref{code:ls-join}).  
+After sweeping the entire partition, valid candidates in $\mathbf{C}$
+are reported (Line~\ref{code:ls-valid-check}). 
+It is notable that $\mathbf{C}$ continuously grows as we sweeping, thus we use three pruning rules to reduce the size 
+of $\mathbf{C}$. First, when sweeping snapshot $S_j$, new candidates with objects set less than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
+candidates in $\mathbf{C}$ with max time sequences no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
+Third, candidates in $\mathbf{C}$ with the size of first segment less than $L$
+are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size
+of $\mathbf{C}$ could be largely reduced.
 
-%$\eta$ is firstly determined based on pattern parameters.
-%In the map phase, $\eta$ snapshots form a partition, followed by the reduce phase where 
-%the line sweep algorithm is applied on each partition.
-
-%MOVE THE PROOF TO APPENDIX
-
-%In the Algorithm~\ref{algo:trm_overview}, 
-%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
-%theorem, such a partition method is sound and complete.
-%\begin{theorem}[Soundness and Completeness of Replication]
-%\label{thm:replication_partition}
-%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
-%\end{theorem}
-%\begin{proof}
-%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
-%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
-%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
-%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$.
-Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$.
-Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$.
-This proves the completeness of the partitioning method.
-%\end{proof}
-
-%\subsection{Line Sweep Mining}
-%Each job in the reduce phase handles a partition $\lambda_t$, 
-%which contains $\eta$ snapshots starting from snapshot $S_t$. 
-%We observe that within each partition, only the patterns whose object sets are contained in the first snapshot are necessary to be reported.
-%YOU CAN FORMALIZE THIS STATEMENT AS A LEMMA AND PROVIDES A RIGOROUS PROOF.
-%Therefore, we design a 
-%\emph{line-sweep mining}(LSM) method in Algorithm~\ref{algo:line-sweep} to discover GCMPs. 
-\begin{algorithm}
+%After join, there are two prunings. First, 
+%all new candidates with objects set less than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second,
+%existing candidates with max time sequences no greater 
+%than $j-G$ are pruned (Line~\ref{code:ls-m-prun}). 
+% 
+%
+%During the sweeping, candidates in $\mathbf{C}$ join with $S_j$.
+%
+% Initially, all the clusters 
+%
+%During scanning, a set of pattern candidates is maintained.
+%When all snapshots are scanned, the remaining candidates are the true patterns.
+%The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
+%A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
+%is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
+%During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
+%the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
+%false patterns are deleted (line~\ref{code:ls-remove}). 
+%Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
+\begin{algorithm}[t]
 \caption{Line Sweep Mining}
@@
 \Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
-\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
-\For{$c \in S_t$} 
+\State{$\mathbf{C} \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
+\For{$s \in S_t$} 
 \label{code:ls-init-start}
-\State $C$.add($\langle c, t \rangle $)
+\State $\mathbf{C}$.add($\langle s, t \rangle $), if $|s| \geq M$
 \EndFor
 \label{code:ls-init-end}
-\ForAll{$j \in [t+1,t+\eta-1]$}
-\State $C \gets S_{j} \oplus C$ \label{code:ls-join}
-	\State{remove false candidates from $C$}
-	\label{code:ls-remove}
+\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
+	\State $\mathbf{N} \gets \{\}$
+	\ForAll {$(c,s) \in \mathbf{C} \times S_j$} \label{code:ls-join-start}
+		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
+		\If {$c'.T$ is valid} 
+			\State output $c'$
+		\Else
+			\State $\mathbf{N}.\mathtt{add}(c')$, if  $|c'.O| \geq M$ \label{code:ls-m-prun}	
+		\EndIf
+	\EndFor \label{code:ls-join-ends}
+	\ForAll {$c \in \mathbf{C}$}
+		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
+			\State $\mathbf{C}.\mathtt{remove}(c)$ 
+			\State output $c$, if $c$ is a valid pattern
+		\EndIf  \label{code:ls-g-prune-ends}
+		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
+			\State $\mathbf{C}.\mathtt{remove}(c)$ 
+		\EndIf\label{code:ls-l-prune-ends}
 	\EndFor
-\State{output true candidates in $C$}
+	\State $\mathbf{C}.\mathtt{addAll}(\mathbf{N})$
+\EndFor\label{code:ls-sweep-ends}
+\State output valid patterns in  $\mathbf{C}$  \label{code:ls-valid-check}
 \end{algorithmic}
 \end{algorithm}
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=0.5\textwidth]{trm_process.eps}
-%\caption{Work flow of trajectory replication and mining}
-%\label{fig:trm_process}
-%\end{figure}
-
-\begin{example}
-We illustrate the work flow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
+The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}.
+We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
 parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
@@
 under this setting is $5$. If $\eta$ is chosen as $4$, the pattern $\{o_3,o_4\}$ would be excluded.
-\end{example}
 
-%
-%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
-%When $\eta$ is small, TRM perform good parallelism. However, wh
-%
-%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
-%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
-%%which surrenders the benefit of parallelism.
-Although TRPM works in a parallel way, we observe two inefficiencies. First, the
-performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
-When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
-the parallel execution of line sweep algorithm may discover the same pattern from
-multiple partitions, which introduces redundant work. To resolve the two limitations,
-we design a novel \emph{Star Partition and Mining} algorithm.
+\begin{algorithm}[h]
+\caption{Temporal Replication and Parallel Mining}
+\label{algo:trm_overview}
+\begin{algorithmic}[1]
+\Require list of $\langle t, S_t \rangle$ pairs
+\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
+\State {---Map Phase---}
+\label{code:trm-map-start}
+\ForAll{$\langle t, S_t \rangle$}
+	\ForAll{$i \in 1...{\eta-1}$}
+		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
+	\EndFor  
+\EndFor
+\label{code:trm-map-end}
+\State {---Partition and Shuffle Phase---}
+\label{code:trm-par-start}
+\ForAll{$\langle t, S \rangle$ pair} 
+\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
+\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
+\EndFor
+\label{code:trm-par-end}
+\State {---Reduce Phase---}
+\label{code:trm-red-start}
+\ForAll{$\langle t,\lambda_t \rangle$}
+\State lineSweepMining($\lambda_t$)
+\label{code:trm-red-end}
+\EndFor
+\end{algorithmic}
+\end{algorithm}

### 2016-06-24 sec4_baseline.tex
An almost finished version
Continue to revise

@@
 \includegraphics[width=\textwidth]{trm.eps}
-\caption{Work flow of Temporal Replication and Mining.
-(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
+\caption{Work flow of Temporal Replication and Parallel Mining.
+(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle uses TRPM to detect GCMP in parallel.}
 \label{fig:trm}
@@
 The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining.
-In particular, the timestamp is treated as the key in the map phrase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phrase.
-Finally, the reducers output clusters of objects in each snapshot, represented by a list of $S_t$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
+In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase.
+Finally, the reducers output clusters of objects in each snapshot, represented by a list of $\langle t,S_t \rangle$ pairs, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
 
@@
 If $\eta$ is set too large, expensive network communication and 
-CPU processing costs would be incurred in the map and reduce phrases respectively.
+CPU processing costs would be incurred in the map and reduce phases respectively. Our objective is to find an $\eta$ that is not large but can guarantee correctness.
 
+In our implementation, we set $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$.
+Intuitively, $K$ timestamps generates at most $\lceil \frac{K}{L} \rceil - 1$ gaps as the length of each $L$-consecutive segment is at least $L$.
+Since the gap size is at most $G-1$, $(\lceil \frac{K}{L} \rceil - 1)*(G-1)$ is the upper bound of timestamps allocated to gaps.
+The remaining part $K+L-1$ is used to capture the upper bound allocated for the $L$-consecutive segments.
+We formally prove that $\eta$ can guarantee correctness.
+
+\eat{
 Before moving on to find the value of $\eta$, 
@@
 we provide the following theorem which states a bounded estimation on $\eta$: 
-\begin{theorem}
-\label{THM:RP_ETA}
-Let $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$. Then it guarantees 
-the completeness of the partition. Further:
-let $\eta^*$ be the optimal value for a given $G,L,K$, then the following holds:
-$\eta \leq \eta^* + L-1$.
-\end{theorem}
-\begin{proof}
-See Appendix.
-\end{proof}
-\eat{
-In order to formally compute the minimum value of $\eta$,
-we enforce the
-following statement on $\eta$:
-%I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
- \emph{Let $T'$ be the \emph{shortest} 
-valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
-Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
-Finding the \emph{minimum} $\eta$ is not
-straightforward. We notice the minimum $\eta$ is related to the temporal
-parameters $K,L,G$ by making the following observation on $G=1$:
-
-\emph{
-Let $T$ be an arbitrary valid temporal sequence. Since $G$ equals to 1,
-$T$ can be represented as $T=(t_1, t_2,...,t_m)$, where
-$t_i +1 = t_{i+1}$ and $m \geq K$. Let $T' = (t_1,...,t_k)$, $T'$ is the shortest
-valid temporal sequence of $T$. Note that $T'$ is fully contained
-in the partition $\lambda_{t_1} = \{S_{t_1},...,S_{t_k}\}$, therefore it can be
-mined in $\lambda_{t_1}$. 
-Since $T$ is an arbitrary valid temporal sequence, the minimum $\eta$ is thus $K$.
 }
-
-Inspired by the observation, we generalize the relationship between
-the minimum $\eta$ and temporal parameters using the following theorem:
 
@@
 \label{THM:RP_ETA}
-The minimum $\eta$ to ensure the completeness of the temporal replication is:
-\[
-   \eta = 
-\begin{cases}
-    (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2, & \text{if } G \geq 2\\
-    K,              & \text{if } G = 1
-\end{cases}
-\]
-, where $K,L,G$ are the temporal parameters.
+$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
 \end{theorem}
+\begin{proof}
+Given a valid pattern $P$, we can always find at least one valid subsequence that is also valid.
+Let $T'$ denote the valid subsequence with the minimum length.
+In the worst case, $T'=P.T$.
+We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
+Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1},g_{n-1},l_n$ ($n \geq 1$),
+where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
+is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
+is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
+last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
+is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
+Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
+using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
+\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
+$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
+Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$.
+We finish showing $\range(T') \leq \eta$.
+Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
+\end{proof}
 
-\begin{proof}
-When $G = 1$, we have demonstrated $\eta=K$
-in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
-any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
-and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
-Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
-as follows:
-\begin{equation}
-\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
-\end{equation}
-With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
-$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
-(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
-validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
-Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
-Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
-increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
-where $g_i = G-1$, 
-$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
-and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
-\end{proof}
+\eat{
+Note that Theorem~\ref{THM:RP_ETA} does not state the optimal value of $\eta$
+for a given $G,L,K$. However, for any $G,L,K$, $\eta$ does not differ from
+the optimal value by at most $L-1$. To see this, for any $G,L,K$, we can
+generate a sequence $T$ by repeating the following pattern, a $L$-segment followed by $G$-gap. 
+The repetition stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
+It is easy to see that $T$ is minimal valid subsequence of itself, then $\eta^*  \geq \range(T) \geq (\lceil \frac{K}{L}\rceil -1)(G-1) + K$.
+Therefore $\eta-\eta^* \leq L-1$.
 }
 
-Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
-form a partition. In particular, for every snapshot $S_t$, there is
-a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. With this partition strategy,
-when discovering GCMPS in $\lambda_t$, we only need to keep the pattern candidates whose
-object set are in $S_t$. This motivates to design an efficient 
-\emph{line-sweep} mining (LSM) method for each partition. The intuition of LSM is 
-to sequentially scan all snapshots. During scanning, a set of pattern candidates is maintained.
-When all snapshots are scanned, the remaining candidates are the true patterns.
-The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
-A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
-is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
-During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
-the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
-false patterns are deleted (line~\ref{code:ls-remove}). 
-Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
-
-\begin{algorithm}
+\begin{algorithm}[h]
 \caption{Line Sweep Mining}
@@
 \State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
-\For{$c \in S_t$} 
+\ForAll{clusters $s$ in snapshot $S_t$} 
 \label{code:ls-init-start}
-\State $C$.add($\langle c, t \rangle $)
+\If{$|s| \geq M$}
+\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
+\EndIf
 \EndFor
 \label{code:ls-init-end}
-\ForAll{$j \in [t+1,t+\eta-1]$}
-\State $C \gets S_{j} \oplus C$ \label{code:ls-join}
-	\State{remove false candidates from $C$}
-	\label{code:ls-remove}
+\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
+	\State $N \gets \{\}$
+	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
+		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
+		\If {$c'.T$ is valid} 
+			\State output $c'$
+		\ElsIf{$|c'.O| \geq M$}
+			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
+		\EndIf
+	\EndFor \label{code:ls-join-ends}
+	\ForAll {$c \in C$}
+		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
+			\State $C\leftarrow C-\{c\}$ 
+			\State output $c$, if $c$ is a valid pattern
+		\EndIf  \label{code:ls-g-prune-ends}
+		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
+			\State $C\leftarrow C-\{c\}$ 
+		\EndIf\label{code:ls-l-prune-ends}
 	\EndFor
-\State{output true candidates in $C$}
+	\State $C\leftarrow C\cup N$
+\EndFor\label{code:ls-sweep-ends}
+\State output valid patterns in  $C$  \label{code:ls-valid-check}
 \end{algorithmic}
@@
 
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=0.5\textwidth]{trm_process.eps}
-%\caption{Work flow of trajectory replication and mining}
-%\label{fig:trm_process}
-%\end{figure}
+Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
+form a partition.
+In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$.
+Our next task is to design an efficient pattern mining strategy within each partition.
+We propose a line sweep algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and employ effective candidate pattern enumeration.
+
+Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}.
+We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process.
+It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot.
+Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
+In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}). 
+%The join of candidate $c$ and cluster $s$ creates a
+%new candidate $c'$ (Line~\ref{code:ls-join}).  
+After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
+It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
+early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, 
+in line sweep, only patterns that starts from timestamp $t$ (i.e., $S_t$) need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
+three pruning rules are as follows:
+First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
+candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
+Third, candidates in $C$ with the size of first segment smaller than $L$
+are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.
+
+%ADD EXPLANATIONS TO THE SECOND AND THIRD PRUNING RULES.
+
+%After join, there are two prunings. First, 
+%all new candidates with objects set less than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second,
+%existing candidates with max time sequences no greater 
+%than $j-G$ are pruned (Line~\ref{code:ls-m-prun}). 
+% 
+%
+%During the sweeping, candidates in $\mathbf{C}$ join with $S_j$.
+%
+% Initially, all the clusters 
+%
+%During scanning, a set of pattern candidates is maintained.
+%When all snapshots are scanned, the remaining candidates are the true patterns.
+%The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
+%A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
+%is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
+%During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
+%the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
+%false patterns are deleted (line~\ref{code:ls-remove}). 
+%Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
 
@@
 during sweeping snapshot $S_i$.
-Initially, $C_1$ contains patterns whose object set is in snapshot $S_1$.
-As line sweeps, the patterns in $C_i$ grows. At snapshot $S_4$, the candidate
+Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
+As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
 $\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
-and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$ constraint.
+and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
 Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
-because its local consecutive timestamps $\{4\}$ has only size $1$,
-which violates the $L$ constraint.
-Finally, $\{o_3,o_4\}$ is the qualified pattern and is outputted. Note that the minimum $\eta$
-under this setting is $5$. If $\eta$ is chosen as $4$, the pattern $\{o_3,o_4\}$ would be excluded.
+because its local consecutive segment $\{4\}$ has only $1$ element,
+which violates the $L$-consecutive constraint.
+Finally, $\{o_3,o_4\}$ is the valid pattern and is returned.
+Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness.
+If $\eta$ is set to $4$, the pattern $\{o_3,o_4\}$ would be missed.
 
-\begin{algorithm}
+\begin{algorithm}[h]
 \caption{Temporal Replication and Parallel Mining}
@@
 \label{code:trm-map-start}
-\ForAll{$\langle t, S_t \rangle$}
+\ForAll{snapshots $S_t$}
 	\ForAll{$i \in 1...{\eta-1}$}
-		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
+		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
 	\EndFor  
@@
 \label{code:trm-par-start}
-\ForAll{$\langle t, S \rangle$ pair} 
-\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
-\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
+\ForAll{key-value pairs $\langle t, S \rangle$ pair} 
+\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
 \EndFor
@@
 \label{code:trm-red-start}
-\ForAll{$\langle t,\lambda_t \rangle$}
-\State lineSweepMining($\lambda_t$)
+\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
+\State call line sweep algorithm for partition $\lambda_t$
 \label{code:trm-red-end}

### 2016-06-24 sec5_spm-bk.tex
An almost finished version
Continue to revise

@@
 First, the replication relies on $\eta$ which could be large.
-Second, the same valid pattern may be discovered from different partitions which results in redundant work.
+Second, the same valid pattern may be discovered from different partitions which results in redundant works.
 %and results in groups of snapshots in each partition.
@@
 \subsubsection{Apriori Enumeration}
-We then design the Apriori enumeration method to
-systematically discover all valid patterns in a star.
-%During the enumeration, we refer a candidate pattern
-%$P$ as a $R$-candidate if $|P.O|=R$.
-The enumeration method discover patterns iteratively using ``bottom-up'' order:
-candidates with smaller objects set grow one object per iteration.
-%
-%in iteration $i$,  all $(i+1)$-candidates grows
-%to $(i+2)$-candidates.
-%
-Enumeration ends if no
-further candidates can be generated.
+We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition.
+The principle of Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner.
+Its merit lies in the monotonic property such that if a candidate set is not valid, then all its supersets can be pruned.
+Thus, it works well in practice in spite of the exponential search space.
 
- Due the \emph{monotonicity} proved in Theorem~\ref{THM:SPARE_MONO}, we are able to use the \emph{monotonic pruning} and \emph{forward closure check} to boost the enumeration process.
-We show the detail of the process
-in Algorithm~\ref{algo:apriori_mining}. As a start, 
-each input edge is treated as a candidate pattern, with the 
-inverted list as the time sequence. These candidates
-are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}).
-In initialization, the inverted lists are simplified (Line~\ref{code:simp1}) and unqualified lists are pruned (Line~\ref{code:init-prune}).
-Throughout the algorithm, we maintain a set of candidates $\mathbf{C}$ which is initialized to the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).
-
-In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}).
-The join of two candidates $c$ and $g$ creates a
-new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}). During the join,
-we use \emph{sequence simplification} to detect unqualified candidates.
-By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}).
-If a valid candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).
-
-After the join finishes, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}).
-We test whether the union of all candidates in $\mathbf{C}$ forms a valid pattern.
-If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).
-
-\eat{
-to union all the candidates in the current candidate set, and quickly check whether the
-
-To systematically discover valid patterns in each star,
-
-we enumerate all valid patterns in ``bottom-up" order: 
-pattern candidates with smallest object sizes are enumerated
-first and grew to pattern candidates with larger object sizes.
-During the enumeration, we call a candidate pattern
-$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
-a star as input, and treat each edge as a $2$-pattern.
-
-The input of
-the enumerator is a star. Each edge
-in the star is treated a $2$-candidate, with the inverted
-list to be the time sequence.
-
-we design the \emph{Apriori Mining} algorithm. We borrow
-the terminologies in classic Aprirori algorithm: a candidate
-pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
-candidates grows from $2$-pattern level by level.
-
-To describe the algorithm, we call a candidate pattern $R$-pattern 
-if the size of its object set is $R$.  Therefore, each edge
-in the star is effectively a $2$-pattern. The intuition of Apriori mining
-is the observation that $(R+1)$-patterns can be generated
-from $R$-patterns and $2$ patterns. Thus, we may iteratively 
-enumerate pattern candidates with all possible sizes.
-In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
-During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
-with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
-generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
-each $R$-pattern contains the object $s$, thus the join only 
-grow a $R$-pattern at most to a $(R+1)$-pattern.
-Our mining algorithm stops where no further patterns are generated. 
-The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
-}
+Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}.
+Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and unqualified candidates are excluded (Line~\ref{code:simp1}).
+A indicator \emph{level} is used to control the object size of the current candidates.
+During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}).
+When two candidate sets $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}).
+To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$.
+If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}).
+This ensures that
+then all the candidates with $P.O\supseteq c'.O$ are excluded. If a candidate cannot generate any new candidates, then it is directly outputted (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
+To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
+If yes, we can early terminate the algorithm and output the results.
 
@@
 \Require{$Sr_s$}
-\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
-\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
-\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
+\State {$C \leftarrow \emptyset$}
+\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
+\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
+\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
+%\ElsIf{$c$ is a valid pattern}
+%\State{output $c$}
+\EndIf 
 \EndFor\label{code:init-end}
-\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
-\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
-		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
-		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
-			\ForAll {$g \in \mathbf{G}$}		
-				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
-				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
+\State $\mathrm{level} \gets 2$ \label{code:level}
+\While{$C\neq \emptyset$} \label{code:level-start}
+	\ForAll{$c_1 \in C$}
+		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
+			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
+			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
+					\State {$C'\leftarrow C'\cup \{c'\}$}
+			\EndIf			
+		\EndFor\label{code:join-end}
+		\If {no $c'$ is added to $C'$} \label{code:output1-start}
+			\If{$c_1$ is a valid pattern}
+				\State output $c_1$
+			\EndIf
+		\EndIf \label{code:output1-end}
 	\EndFor
-			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
-		\EndFor	\label{code:join-ends}
-		\State {$\mathbf{C} \gets \mathbf{N}$}
-		\State $U \gets $ union of $n_i \in \mathbf{C}$	\label{code:fc-checking-start}
-		\If {$U$ is a valid pattern}
-			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
+%	
+%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
+%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
+%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
+%					\State {$C'\leftarrow C'\cup \{c'\}$}
+%					\ElsIf{$c'$ is a valid pattern}
+%						\State{output $c'$}
+%				\EndIf
+%		\EndFor	\label{code:join-ends}
+	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
+	\State $T_u \gets $ intersection of $c.T$ in $C$	
+	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
+		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
 		\State break;
-		\EndIf \label{code:fc-checking-ends}
+	\EndIf \label{code:fc-checking-end}
+	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
 \EndWhile\label{code:level-ends}
-\State $\mathbf{OT}$.addAll$(\mathbf{C})$
-\State \Return $\mathbf{OT}$
+\State output $C$ \label{code:output2-end}
 \end{algorithmic}
@@
 
-%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-%higher level candidates are generated by joining lower level candidates. When no more candidates 
-%can be generated, the algorithm stops by outputting the valid patterns.
-%
-
 \begin{example}
-We use Figure~\ref{fig:star_partition} (c) to 
-demonstrate the power of candidate pruning. 
-As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{simplification}. 
-Subsequently, all further candidates containing $\{3,6\}$ 
-are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
-of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
-valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty.
+Thus, all the object sets containing $\{3,6\}$ can be pruned.
+The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid.
+By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
 \end{example}
 
-%
-%It is notable that, in star partition, original data is 
-%replicated at most $O(|\mathbb{O}|)$ times.
-%In later sections, we will describe several 
-%more optimization techniques to further reduce the amount of replicated data.
-
-%In such a way, 
-%given an object $u$, all the objects potentially
-%co-moved with $u$ are captured in $u$'s neighborhood, which
-%forms a \emph{star} structure in graph terms. SPM utilizes
-%such structures to partition objects and then adapts an Apriori 
-%algorithm to discover true GCMPs from each partition.
-
-\eat{
-
-EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.
-
-Although leveraging \emph{temporal monotonicity} could largely prune
-false candidates and reduce the apriori search space, 
-it is ineffective when a \textit{true} pattern exists. 
-In an extreme case, if a final pattern of a star $Sr_s$ is 
-the \textit{union of all vertices} in the star,
-then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
-each level $i$. This results in an exponential search space while
-the output only contains one pattern.  
-Generally, when candidates at level $i$ collectively forms a true pattern, 
-running aprior produces many wasted candidates.
-
-Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
-we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
-all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
-\begin{theorem}[Forward Closure Checking]
-\label{THM:SPM_FCC}
-Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
-if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
-and directly output $FC_i$.
-\end{theorem}
-
-It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
-reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
-optimization as follows:
-%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
-%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
-%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
-%all candidates. Then, the following \emph{forward closure checking} rule can be used:
-%
-%\begin{theorem}[Forward Closure Checking Rule]
-%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
-%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
-%$FC_i$ forms a valid GCMP .
-%\end{theorem}
-}
-
 \subsection{Put It Together}
-With the star partition and the Apriori enumerator, we are ready to assemble the Star Partition and ApRiori Enumerator (SPARE) framework. 
-We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows: After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
-In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows.
+After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship.
+However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.
+Instead, we simply need to emit the edges within a star partition to the same reducer.
 Each reducer is an Apriori Enumerator.
 When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
-Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
-Then it enumerates all true patterns from the candidate patterns.
+Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created.
+Then it enumerates all the valid patterns from the candidate patterns.
 The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
-Note that we do not need to create an actual aggregate graph.
-Instead, we only to emitted the directed edges (Line~\ref{code:spm-edge-direct}).
 
@@
 \ForAll{$C \in S_t$}
-	\ForAll {$(o_1 ,o_2) \in C \times C$}
-	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet, if $o_1 < o_2$~\label{code:spm-edge-direct}
+	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
+	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
 	\EndFor
@@
 
-Our SPARE framework does not rely on the pattern parameters to determine the partition size,
-which is more stable than TRMP. In addition, we observe that the patterns mined from each
-reducer are unique. This property is stated as follows:
+Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness.
+In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
 \begin{theorem}[Pattern Uniqueness]
@@
 the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
-Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
+Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
 \end{theorem}
 \begin{proof}
-We prove by contradiction. Suppose exists $p_i \in P_i$ and $p_j \in P_j$ s.t. $p_i.O \equiv p_j.O$.
-Let $o_i$ (resp. $o_j$) be the object with smallest ID in $p_i.O$ (resp. $p_j.O$).
-Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$,  which contradicts with
-the assumption $p_i.O \not\equiv p_j.O$. 
+We prove by contradiction.
+Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set.
+Note that the center vertex of the star is associated with the minimum id.
+Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$.
+However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction.
 \end{proof}
 
-Theorem~\ref{LEM:SPM_CORRECT} confirms the superiority of SPARE to TRPM. In TRPM, a pattern
-may be repeatedly discovered from different partitions, while in SPARE a pattern is only discovered once.
-This suggests that SPARE require less redundant works.
-We finally conclude this section with the following theorem:
-
+Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
+%that no replication is required 
+in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
 \begin{theorem}
@@
 \end{proof}
-
-\eat{ \subsection{Correctness of SPARE}
-We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
-After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
-In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
-Each reducer is an Apriori Enumerator.
-When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
-Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
-Then the Apriori algorithm enumerate the true patterns from the candidate patterns.
-Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
-ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.
-
-\eat{
-\begin{algorithm}
-\caption{Star Partition and Mining}
-\label{algo:spm_overview}
-\begin{algorithmic}[1]
-\Require list of $\langle t, S_t \rangle$ pairs
-\State {---Map phase---}
-\label{code:spm-map-start}
-\ForAll{$C \in S_t$}
-	\ForAll {$(o_1 ,o_2) \in C \times C$}
-		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
-			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
-		\EndIf
-	\EndFor
-\EndFor
-\label{code:spm-map-end}
-
-\State {---Partition and Shuffle phase---}
-\label{code:spm-shuffle-start}
-\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
-	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
-	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
-\EndFor
-\label{code:spm-shuffle-end}
-
-\State {---Reduce phase---}
-\label{code:spm-reduce-start}
-\ForAll{$\langle o, Sr_{o} \rangle$}
-\State Apriori($Sr_o$)
-\EndFor
-\label{code:spm-reduce-end}
-
-\end{algorithmic}
-\end{algorithm}
-}
-
-In the following, we show the correctness of the SPARE framework.
-\begin{theorem}
-\label{THM:SPM_CORRECT}
-The SPARE framework guarantees completeness and soundness.
-\end{theorem}
-\begin{proof}
-If $P$ is a valid pattern in original trajectories, 
-let $s$ be the object with smallest ID in $P.O$. 
-Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. 
-Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$.
-Therefore, $P$ is a valid pattern in $Sr_s$.
-This ensures the \emph{completeness}.
-For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$.
-This ensure the \emph{soundness}.
-\end{proof}
-
-In fact, besides that every valid patterns can be
-mined in some stars, star partition further ensures
-that patterns discovered
-from different star partitions cannot be the same. 
-This can be formulated as:
-
-\eat{It is also interesting to observe that no duplicate patterns will be generated from the star partitions.}
-\begin{lemma}[Pattern Uniqueness of Star Partition]
-\label{LEM:SPM_CORRECT}
-Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
-the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
-Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
-\end{lemma}
-\begin{proof}
-The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
-let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
-Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
-therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
-\end{proof}
-
-This lemma verifies the superiority of the SPARE framework over the TRPM framework.
-}

### 2016-06-24 sec5_spm.tex
An almost finished version
Continue to revise

--- 2016-06-22 sec5_spm.tex
@@
 \label{sec:spm}
-The aforementioned replicate partitioning is based on the temporal dimension 
-and results in groups of snapshots in each partition. ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
+The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks.
+First, the replication relies on $\eta$ which could be large.
+Second, the same valid pattern may be discovered from different partitions which results in redundant works.
+%and results in groups of snapshots in each partition.
+% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
 To resolve the limitations caused by the replicate partitioning, 
@@
 
-\begin{theorem}\label{THM:SPM_TM}
+\begin{theorem}[Monotonicity]\label{THM:SPARE_MONO}
 Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
@@
 \subsubsection{Apriori Enumeration}
-We then design the Apriori enumeration method to
-systematically discover all valid patterns in a star.
-During the enumeration, we refer a candidate pattern
-$P$ as a $R$-candidate if $|P.O|=R$. The enumeration
-method discover patterns in ``bottom-up'' order:
-in iteration $i$,  all $(i+1)$-candidates grows
-to $(i+2)$-candidates. Enumeration ends if no
-further candidates can be generated.
+We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition.
+The principle of Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner.
+Its merit lies in the monotonic property such that if a candidate set is not valid, then all its supersets can be pruned.
+Thus, it works well in practice in spite of the exponential search space.
 
-The process of enumeration is shown 
-in Algorithm~\ref{algo:apriori_mining}. As a start, 
-each edge is treated as a $2$-candidate pattern, with the 
-inverted list as the time sequence. These $2$-candidates
-are kept in $\mathbf{G}$ as the ground set. During the algorithm,
-we maintain a set of candidates $\mathbf{C}$. $\mathbf{C}$
-is initialized as $\mathbf{G}$.
-
-As a start, each edge is treated as
-
-To systematically discover valid patterns in each star,
-
-we enumerate all valid patterns in ``bottom-up" order: 
-pattern candidates with smallest object sizes are enumerated
-first and grew to pattern candidates with larger object sizes.
-During the enumeration, we call a candidate pattern
-$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
-a star as input, and treat each edge as a $2$-pattern.
-
-The input of
-the enumerator is a star. Each edge
-in the star is treated a $2$-candidate, with the inverted
-list to be the time sequence.
-
-we design the \emph{Apriori Mining} algorithm. We borrow
-the terminologies in classic Aprirori algorithm: a candidate
-pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
-candidates grows from $2$-pattern level by level.
-
-To describe the algorithm, we call a candidate pattern $R$-pattern 
-if the size of its object set is $R$.  Therefore, each edge
-in the star is effectively a $2$-pattern. The intuition of Apriori mining
-is the observation that $(R+1)$-patterns can be generated
-from $R$-patterns and $2$ patterns. Thus, we may iteratively 
-enumerate pattern candidates with all possible sizes.
-In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
-During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
-with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
-generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
-each $R$-pattern contains the object $s$, thus the join only 
-grow a $R$-pattern at most to a $(R+1)$-pattern.
-Our mining algorithm stops where no further patterns are generated. 
-The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
+Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}.
+Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}).
+An indicator \emph{level} is used to control the object size for candidate set join.
+During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}).
+When two candidate sets $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}).
+To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$.
+If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}).
+This ensures that
+then all the candidates with $P.O\supseteq c'.O$ are pruned.
+If a candidate cannot generate any new candidate, then it is directly reported as a valid closed pattern (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
+To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
+If yes, we can early terminate the algorithm and output the results.
 
 \begin{algorithm}
-\caption{Apriori Mining}
+\caption{Apriori Enumerator}
 \label{algo:apriori_mining}
@@
 \Require{$Sr_s$}
-\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
-\ForAll{$e(s,t) = T \in Sr_s$}
-\State {$T' \gets \mathtt{sim}(e(s,t))$}
-%\State{ $\mathtt{sim}(e(s,t)) $} 
-\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}
+\State {$C \leftarrow \emptyset$}
+\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
+\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
+\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
+%\ElsIf{$c$ is a valid pattern}
+%\State{output $c$}
+\EndIf 
+\EndFor\label{code:init-end}
+\State $\mathrm{level} \gets 2$ \label{code:level}
+\While{$C\neq \emptyset$} \label{code:level-start}
+	\ForAll{$c_1 \in C$}
+		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
+			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
+			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
+					\State {$C'\leftarrow C'\cup \{c'\}$}
+			\EndIf			
+		\EndFor\label{code:join-end}
+		\If {no $c'$ is added to $C'$} \label{code:output1-start}
+			\If{$c_1$ is a valid pattern}
+				\State output $c_1$
+			\EndIf
+		\EndIf \label{code:output1-end}
 	\EndFor
-\State {$\mathbf{C} \gets \mathbf{G}$}
-\While{$\mathbf{C} \neq \emptyset$}
-		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
-		\ForAll{$(c,g)\in \mathbf{C}$}
-			\ForAll {$g \in \mathbf{G}$ }
-				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$}
-				\State {$\mathbf{N}.add(c')$, unless $c'.T \neq \emptyset$}
-			\EndFor
-			\State $\mathbf{OT}.\mathtt{add}(c)$, if $c$ is not extended.
-		\EndFor	
-		\State $U \gets $ union of $n_i \in \mathbf{N}$
-		\ForAll{$n \in \mathbf{N}$}
-			\State $U.O \gets$,  $U.T \gets U.T \cap n.T$
-		\EndFor
-		\If{$U$ is valid}
-			\State $\mathbf{Output}.\mathbf{add}(U)$
+%	
+%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
+%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
+%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
+%					\State {$C'\leftarrow C'\cup \{c'\}$}
+%					\ElsIf{$c'$ is a valid pattern}
+%						\State{output $c'$}
+%				\EndIf
+%		\EndFor	\label{code:join-ends}
+	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
+	\State $T_u \gets $ intersection of $c.T$ in $C$	
+	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
+		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
 		\State break;
-		\EndIf
-		\State {$\mathbf{C} \gets \mathbf{N}$}
-		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
-		\State {Remove false patterns in Lv}
-		\Comment{Monotonicity}
-		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
-			\State{output.add(Lv)} 
-			\State{break}
-		\EndIf
-\EndWhile
-\State output.addAll($Lv$)
-\State \Return output
+	\EndIf \label{code:fc-checking-end}
+	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
+\EndWhile\label{code:level-ends}
+\State output $C$ \label{code:output2-end}
 \end{algorithmic}
@@
 
-An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
-As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
-higher level candidates are generated by joining lower level candidates. When no more candidates 
-can be generated, the algorithm stops by outputting the valid patterns.
-%
-%It is notable that, in star partition, original data is 
-%replicated at most $O(|\mathbb{O}|)$ times.
-%In later sections, we will describe several 
-%more optimization techniques to further reduce the amount of replicated data.
-
-%In such a way, 
-%given an object $u$, all the objects potentially
-%co-moved with $u$ are captured in $u$'s neighborhood, which
-%forms a \emph{star} structure in graph terms. SPM utilizes
-%such structures to partition objects and then adapts an Apriori 
-%algorithm to discover true GCMPs from each partition.
-
-EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.
-
-Although leveraging \emph{temporal monotonicity} could largely prune
-false candidates and reduce the apriori search space, 
-it is ineffective when a \textit{true} pattern exists. 
-In an extreme case, if a final pattern of a star $Sr_s$ is 
-the \textit{union of all vertices} in the star,
-then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
-each level $i$. This results in an exponential search space while
-the output only contains one pattern.  
-Generally, when candidates at level $i$ collectively forms a true pattern, 
-running aprior produces many wasted candidates.
-
-Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
-we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
-all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
-\begin{theorem}[Forward Closure Checking]
-\label{THM:SPM_FCC}
-Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
-if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
-and directly output $FC_i$.
-\end{theorem}
-
-It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
-reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
-optimization as follows:
-%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
-%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
-%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
-%all candidates. Then, the following \emph{forward closure checking} rule can be used:
-%
-%\begin{theorem}[Forward Closure Checking Rule]
-%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
-%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
-%$FC_i$ forms a valid GCMP .
-%\end{theorem}
-
 \begin{example}
-We use Figure~\ref{fig:star_partition} (c) to 
-demonstrate the power of candidate pruning. 
-As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
-timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
-are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
-of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
-valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
+As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty.
+Thus, all the object sets containing $\{3,6\}$ can be pruned.
+The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid.
+By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
 \end{example}
 
-\subsection{Correctness of SPARE}
-We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows.
-After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship.
-In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers.
+\subsection{Put It Together}
+We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows.
+After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship.
+However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.
+Instead, we simply need to emit the edges within a star partition to the same reducer.
 Each reducer is an Apriori Enumerator.
 When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
-Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created.
-Then the Apriori algorithm enumerate the true patterns from the candidate patterns.
-Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
-\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}
+Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created.
+Then it enumerates all the valid patterns from the candidate patterns.
+The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
 
-\eat{
 \begin{algorithm}
-\caption{Star Partition and Mining}
+\caption{Star Partition and ApRiori Enumerator}
 \label{algo:spm_overview}
@@
 \ForAll{$C \in S_t$}
-	\ForAll {$(o_1 ,o_2) \in C \times C$}
-		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
-			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
-		\EndIf
+	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
+	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
 	\EndFor
@@
 \ForAll{$\langle o, Sr_{o} \rangle$}
-\State Apriori($Sr_o$)
+\State AprioriEnumerator($Sr_o$)
 \EndFor
@@
 \end{algorithm}
-}
 
-In the following, we show the correctness of the SPARE framework.
+Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness.
+In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
+\begin{theorem}[Pattern Uniqueness]
+\label{LEM:SPM_CORRECT}
+Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
+the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
+Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
+\end{theorem}
+\begin{proof}
+We prove by contradiction.
+Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set.
+Note that the center vertex of the star is associated with the minimum id.
+Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$.
+However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction.
+\end{proof}
+
+Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
+%that no replication is required 
+in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
 \begin{theorem}
@@
 \begin{proof}
-If $P$ is a valid pattern in original trajectories, 
-let $s$ be the object with smallest ID in $P.O$. 
-Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-It follows that all object $o \in P.O$ are in $Sr_s$. 
-Furthermore, every timestamp in $P.T$ is included
-in $Sr_s$.
-Therefore, $P$ is a valid pattern in $Sr_s$.
-This ensures the \emph{completeness}.
-For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$.
-This ensure the \emph{soundness}.
-\end{proof}.
-
-In fact, besides that every valid patterns can be
-mined in some stars, star partition further ensures
-that patterns discovered
-from different star partitions cannot be the same. 
-This can be formulated as:
-
-\eat{It is also interesting to observe that no duplicate patterns will be generated from the star partitions.}
-\begin{lemma}[Pattern Uniqueness of Star Partition]
-\label{LEM:SPM_CORRECT}
-Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
-the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
-Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
-\end{lemma}
-\begin{proof}
-The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
-let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
-Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
-therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
+See Appendix XXXX.
 \end{proof}
-
-This lemma verifies the superiority of the SPARE framework over the TRPM framework.

### 2016-06-24 sec7_experiment.tex
An almost finished version
Continue to revise

--- 2016-06-23 sec7_experiment.tex
@@
 
+\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study.
+TRPM and SPARE are implement as described in Section 4 and 5.
+SPARE-LB extends SPARE by appending an additional load balance stage to the map phase.
+When the mapers complete, SPARE-LB collects the size of stars from all mappers. 
+Then the best-fit strategy is applied for task allocation. In best-fit, 
+tasks are assigned in decreasing order of their sizes, and the biggest 
+unassigned task is allocated to the current mostly empty reducer. 
+In SPARE-LB, we simply use the edge size of stars as an estimation of tasks. The other
+part of SPARE-LB is identical with SPARE.
+
+\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary} presents
+ the number of valid GCMP patterns exist in the three datasets. Since the $M$,$K$,$L$,$G$
+ impose different constraints on the patterns, the number of valid patterns changes as their 
+ values change. We observe that $L$ has a great initial impact on the number of patterns
+ discovered. As $L$ increases from $10$ to $20$, the number of patterns drops 50\%. As $L$
+ increases further, the number of patterns decreases slowly. Opposed to $L$, when $G$
+ is small, the number of patterns increases slowly. As $G$ reaches $30$, 
+ the number of patterns nearly doubles. The distribution of patterns under $G$ and $L$
+ reveals that there are many companions in real life which are short and repetitive. We can
+ either discover these patterns by adjusting property $L$ and $G$ in the GCMP model.
+
+\begin{figure}[h]
+\centering
+ 	 \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
+        \caption{Number of patterns vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
+        \caption{Number of patterns vary $K$}
+    \end{subfigure}  
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
+        \caption{Number of patterns vary $L$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
+        \caption{Number of patterns vary $G$}
+    \end{subfigure}    
+\caption{Number of patterns discovered in three datasets on different parameters}
+\label{exp:patterns_vary}
+\end{figure}
+
 %\subsection{Effects of $G$ on GCMP}
@@
 of each scenario separately.
+
+\begin{figure*}[t]
+\centering
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
+        \caption{Shopping vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
+        \caption{Shopping vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
+        \caption{Shopping vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
+        \caption{Shopping vary $G$}
+    \end{subfigure}
+
+	\begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
+        \caption{Geolife vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
+        \caption{Geolife vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
+        \caption{Geolife vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
+        \caption{Geolife vary $G$}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
+        \caption{Taxi vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
+        \caption{Taxi vary $K$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
+        \caption{Taxi vary $L$}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
+        \caption{Taxi vary $G$}
+    \end{subfigure}       
+\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
+\label{exp:performance_vary}
+\end{figure*}
 
@@
 
-\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary}
-\begin{figure}[h]
-\centering
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
-        \caption{Number of patterns vary $L$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
-        \caption{Number of patterns vary $G$}
-    \end{subfigure}    
-\caption{Number of patterns discovered in three datasets on different parameters}
-\label{exp:patterns_vary}
-\end{figure}
+%\subsubsection{Anatomy of SPARE and TRPM}
+
+\subsection{SPARE Analysis}
+Since SPARE is superior than TRPM,
+we further analyze the SPARE in terms of its power of pruning, load balance
+and scalablity.
+
+\subsubsection{Power of sequence simplification}
+One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
+As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
+to prune false candidates. To study the power of sequence simplification,
+we collect the total number of initial pairs that are pruned. The
+statistics are shown in Table~\ref{tbl:pruning} under default parameters. As the table
+shows, the \emph{sequence simplification} is a very powerful pruning technique.
+It cuts off near 90\% of the initial pairs, which significantly reduces the costs
+in Apriori Enumeration. This confirms the necessity of design such a technique.
+\begin{table}[h]
+\begin{tabular}{|l|c|c|c|}
+\hline 
+\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
+\hline 
+Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
+\hline 
+After pruning & 76,672 & 123,410 & 270,921 \\ 
+\hline 
+Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
+\hline 
+\end{tabular} 
+%
+%\begin{tabular}{|c|c|c|c|}
+%\hline 
+%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
+%\hline 
+%Shopping & 878,309 & 76,672 &  91.2\%\\ 
+%\hline 
+%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
+%\hline 
+%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
+%\hline 
+%\end{tabular} 
+\caption{Pruning power of SPARE}
+\label{tbl:pruning}
+\end{table}
+
+\subsubsection{Load Balance}
+We first compare SPARE and SPARE+ by analyzing the running time at
+each map-reduce stage. The detail anatomy is shown in Figure~\ref{exp:wl}(a).
+We can see that for both SPARE and SPARE-LB on three datasets, the reduce 
+time takes the majority. The overall improvement of SPARE-LB is around 10-13\%
+under default settings. We observe that the mapping and shuffle time
+of SPARE and SPARE-LB are identical, where SPARE-LB spends a very small portion 
+of extra time (4\% of the total time)
+in applying the best-fit strategy. The time spent is worthwhile
+as in the reduce phase SPARE-LB saves around 20\% of the time. However, since 
+the star sizes in SPARE is almost identical (due to Theorem~2), the best-fit
+strategy does not win too much.
+
+We then look at the workload distribution of SPARE and SPARE-LB on the
+real datasets. We collect the statistics from executors
+and report their reduce times in Figure~\ref{exp:wl}. The figure shows
+ that SPARE-LB is able to provide a more balanced task allocation
+ as compared to SPARE in all three cases. Since SPARE takes random assignment
+of stars, it is likely to incur skewed workloads as many large stars 
+may be assigned to the same executor. 
+However, as bounded by Theorem~2, the difference between
+SPARE-LB and SPARE is not very large. In general cases, SPARE-LB is preferred
+as it offers more efficiency while takes only a small extra time in planning.
 
@@
 \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
-        \caption{Shopping vary $M$}
+	\begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
+        \caption{Comparison between SPARE and SPARE-LB}
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
-        \caption{Shopping vary $K$}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
+        \caption{Workload distribution in Shopping}
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
-        \caption{Shopping vary $L$}
+    \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
+        \caption{Workload distribution in Geolife}
     \end{subfigure}  
-       \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
-        \caption{Shopping vary $G$}
+    \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
+        \caption{Workload distribution in Taxi}
     \end{subfigure}
-
-	\begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
-        \caption{Geolife vary $M$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
-        \caption{Geolife vary $K$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
-        \caption{Geolife vary $L$}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
-        \caption{Geolife vary $G$}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
-        \caption{Taxi vary $M$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
-        \caption{Taxi vary $K$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
-        \caption{Taxi vary $L$}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
-        \caption{Taxi vary $G$}
-    \end{subfigure}       
-\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
-\label{exp:performance_vary}
+\caption{Load balance of SPARE and SPARE-LB in real datasets}
+\label{exp:wl}
 \end{figure*}
 
-\subsubsection{Detail comparison between SPARE and TRPM}
+\subsubsection{Scalability}
+We then study the scalability of SPARE-LB from two aspects. First, given
+the number of executors, we sample a subset of data from three datasets
+and test the performance of SPARE-LB. The results are shown in Figures~\ref{fig:scalability-wl}.
+\begin{figure}[h]
+\begin{subfigure}[b]{0.22\textwidth}
+\centering
+    \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-O.eps}
+        \caption{Scalability vary $O$}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-T.eps}
+        \caption{Scalability vary $T$}
+    \end{subfigure}
+ \caption{Scalability of SPARE-LB wrt. different data sizes}
+ \label{fig:scalability-wl}
+\end{figure}
 
-\subsection{SPARE Analysis}
-
-\subsubsection{Scalability}
+We further test the scalalbility of SPARE under different number of executors. 
+The result on the three dataset is presented in Figure~\ref{exp:scalability}.
+We can see that SPARE achieves good scalability under all three cases. 
+For instance, for Taxi dataset, when the executors rises from 14 to 54, 
+the performance improves 3.5 times which is almost linear to the increase of executors. 
+Such a pattern also holds for other two datasets.
 \begin{figure}[h]
 \centering
-   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
-\caption{Scalability of SPARE vary. $N$ under different datasets.}
-\label{exp:patterns_vary}
+   \includegraphics[width=0.3\textwidth]{/exp/spare/scalability.eps}
+\caption{Scalability of SPARE-LB vary. $N$ under different datasets.}
+\label{exp:scalability}
 \end{figure}
-
-\subsubsection{Load Balance}

### 2016-06-25 sec6_experiment.tex
A new draft
Flighting

--- 2016-06-23 sec7_experiment.tex
@@
 deploying our GCMP detectors to large-scaled real trajectories.
-All algorithms are were implemented in Java 1.7., and all the 
-experiments are carried out on our in-house cluster: Dianwei. The cluster
-includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors,
-32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
-operating system and Java 1.7.0 VM.
+All the experiments are carried out on our in-house cluster: Dianwei.
+The cluster includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors, 32 GB memory and gigabit Ethernet.
+The cluster is installed with CentOS 5.5.
+operating system.
 
-\textbf{Experiment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
-to manage the cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
-Yarn processes. We use Apache Spark~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
+\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
+to manage our cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
+Yarn processes. We use Apache Spark 1.5.5~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
 the remaining 11 nodes as the computing nodes.
@@
 at the same time. We use HDFS as our storage engine with replicator factor of 1.
-The configurations of important parameters are summaries in the table below:
+The summary of the configuration is as in the following table:
 
-%\subsection{Implementation Issues}
-%We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
-%platform. Spark is one of the most popular MapReduce platform which
-%uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
-%Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
-%In order to help reproduce our experiments, we further address some implementation issues.
-%\subsubsection{Task Assignment}
-%In spark, each task in reduce phase is an Apriori mining phase of 
-%a star.
-%Although our star partition method is theoretically balanced, 
-%it is still necessary to assign equal number of tasks to each executors. 
-%Spark naturally uses hashing to partition data into tasks, where such
-%a partitioning does not care on the tasks size. In order to
-%fully utilize the clusters, it is important to perform a weight-aware
-%partition. In our implementation, we collect the number of edges
-%in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
-%where we assign stars in decreasing order with their sizes and each star
-%is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
-%FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
-%between map and reduce phase can be naturally implemented in Spark, where the 
-%map result can be cached and the reduce phase can be paused until when the
-%partition strategy is ready.
-%
-%\subsubsection{Duplication Detection}
-%It is notable that the patterns discovered from different tasks (stars) could
-%be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
-%can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
-%from the star $Sr_b$. Though in most applications, such a duplicate pattern
-%is permitted, we offer an option to eliminate these patterns. The strategy is 
-%to broadcast each reducers output to every other reducers. This can be
-%efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
-%whether any resulted patterns are subsumed and thus filter those patterns.
-%Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
-%deal with the duplication detection. However, as the number of final patterns are
-%normally quit small, we leave the exploration for those techniques to the future.
-%
-%\subsubsection{Handling Overlapping Clusters}
-%When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
-%on objects are applied. Such a clustering method may result one object belonging to
-%multiple clusters. In such a case, just keeping the timestamps in the edge
-%of connection graph is insufficient. Instead, we extend every timestemp $t$
-%to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
-%belong to at time $t$. The only adaption we need to take the join during
-%apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
-%$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
-%it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
-%It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
-%still holds under this new setting.
-%
-%
-%\subsection{Experimental Setup}
-%We adapt one of the most popular MapReduce platform, Apache Spark, 
-%to conduct experiments on mining GCMPs. 
-%Our experiments run on a 9-node cluster, with Apache Yarn as
-%the cluster manager. We use 1 node for Yarn resource manager, 
-%and use the remaining 8 nodes as executors. Each node in the cluster
-%is uniformly equipped with a 2.2GHz quad-core CPU with 32 GB memory. 
-%Inter-node communication is carried by 
-%the 1Gbps Ethernet.  Some critical configuration of Spark is 
-%as follows:
 \begin{table} [h]
@@
 Java Version & 1.7.0 \\ 
+\hline 
+Spark Version & 1.5.5 \\ 
 \hline 
@@
 
-\textbf{Datasets}: We prepare three real datasets for study. The details of the datasets are as follows:
+\textbf{Datasets}: We prepare three real datasets for experiments. The details of the datasets are as follows:
 \begin{itemize}
@@
 \item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
-rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude.
+rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude information.
 \end{itemize}
 
-\textbf{Preprocessing}: We replace timestamps with a global sequence for each dataset. The sequence number
+\textbf{Preprocessing}: We replace timestamps with global sequences for each dataset. The sequence number
 $0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
@@
 as the clustering algorithm for preprocessing.  
-Note that both our TRPM and SPARSE algorithms treat the preprocessing as a black box and other
+Note that both our TRPM and SPARE algorithms treat the preprocessing as a black box and other
 spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
 $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
-After preprocessing, the summary of statistics are presented as in Table~\ref{exp:dataset}. 
-%But they are affected by the number of clusters at each snapshot. We measure the 
-%effect of different clustering parameters later.
+After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.
 
@@
 
-\textbf{Parameters}: We study the performance of 
-the GCMP detectors under various conditions. The variables
+\textbf{Parameters}: To systematically study the performance of
+our algorithms, we conduct experiments on various conditions. The variables
 to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
-The default values are highlighted in bold.
+Default values are highlighted in bold.
 \begin{table}[h]
@@
 \end{tabular} 
-\caption{Variables and their default values during experiments.}
+\caption{Variables and their default values}
 \label{tbl:parameters}
 \end{table}
+
+\textbf{Number of patterns under different parameters}: We first 
+analyze the number of patterns exist in each dataset under different conditions.
+The results are presented in Figures~\ref{exp:patterns_vary}.
+As expected, the number of patterns differs under in different scenarios.
+Larger $M$, $L$, $K$ imply smaller number of patterns, because lesser patterns are able to meet stricter $M$, $L$, $K$ constraints.
+In contrast, larger $G$ implies larger number of patterns.
+This is because larger gaps relaxes the pattern constraint.
+Two interesting observations are made on $L$ and $G$.
+First, as $L$ increases from $10$ to $20$, the number of patterns drops quickly (50\% less).
+Second, opposed to $L$'s trend, as $G$ reaches to $30$ from $25$, the number of patterns bursts (near 50\% more).
+The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent.
+With GCMP, we can discover these patterns by adjusting property $L$ and $G$s.
+
+\begin{figure}[h]
+\centering
+ 	 \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
+        \caption{Number of patterns vary $M$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
+        \caption{Number of patterns vary $K$}
+    \end{subfigure}  
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
+        \caption{Number of patterns vary $L$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
+        \caption{Number of patterns vary $G$}
+    \end{subfigure}    
+\caption{Number of patterns discovered from real datasets}
+\label{exp:patterns_vary}
+\end{figure}
+
+\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study.
+TRPM and SPARE are implement as described in Section 4 and 5.
+SPARE-LB extends SPARE by appending an additional load balance stage to the map phase.
+When the mappers complete, SPARE-LB collects the size of stars from all mappers. 
+Then a best-fit strategy is applied for task allocation. In best-fit, 
+tasks are assigned in decreasing order of their sizes, and the most costly
+unassigned task is allocated to the current mostly empty reducer. 
+In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The other
+part of SPARE-LB is identical with SPARE.
 
@@
 \subsection{Performance Comparison}
-Since the both TRPM and SPARE utlizes pruning rules that related to the 
-pattern parameters $M$,$L$,$G$,$K$. It is interesting to
-see the performance of TRPM and SPARE under different parameter settings.
-%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
-%parameter settings. Under the default parameter settings,
-%the performance of TRPM and SPARE is shown as in the 
-%following table:
-%\begin{table}
-%\small
-%\begin{tabular}{|c|c|c|c|c|c|c|}
-%\hline 
-%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
-%\hline 
-% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
-%\hline 			
-%Shopping &55 & 279 & 183 &414 &369\\ 
-%\hline
-%GeoLife &72 & 408 & 162 &585 &441  \\
-%\hline
-%Taxi &193 & 619 & 562 &3086 &585 \\
-%\hline 
-%\end{tabular} 
-%\caption{Detail performance of TRPM and SPARE under default parameters.}
-%\end{table}
-%
-%As can be seen from the above table, the number of patterns
-%discovered by the default parameters are up to five hundreds.
-%Thus, the parameter settings are reasonable. Besides, we 
-%can see that TRPM suffers from shuffle and mining process. 
-%This is because $\eta$ is set to be $309$ under default parameters.
-%As a comparison, SPARE takes only in average
-% 36\% of TRPM's shuffle time. 
-%To study the performance of TRMP and SPARE, we run both algorithms 
-%in all three datasets under different parameter settings. 
-We run both of the two algorithms in all three dataset and report
-their overall performances as in Figures~\ref{exp:performance_vary}.
-In brief, both algorithms are able to handle the large-scaled real
-datasets. However, we observe that TRMP's performance largely depends
-on the pattern parameters. In cases when $G$ is large, 
-TRMP takes near three hours (e.g., in Taxi dataset).
-In contrast, SPARE performs quite stable. Another general observation
-is that both algorithms run slower in the Taxi dataset as compared to
+Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
+see their performances under different settings.
+We run the three algorithms using all three datasets 
+and report their overall performances in Figures~\ref{exp:performance_vary}.
+In brief, all of the three algorithms 
+are able to handle the large-scaled real
+datasets. However, SPARE algorithms are obviously more efficient than TRPM. 
+In the case when $G$ is large (i.e., $G=30$), 
+TRMP takes near three hours for Taxi dataset, which is 15 times slower than SPARE algorithms. Besides, SPARE-LB is consistently more efficient than SPARE, with an average of 20\% improvements.
+Another general observation
+is that all of the three algorithms run slower in the Taxi dataset as compared to
 other two datasets. This is because Taxi dataset contains
 the most number of temporal data points, which is around 7 times of Shopping
-dataset and 5 times of geolife dataset. We observe that, 
-in almost all cases, SPARE outperforms TRMP and analyze the detail
-of each scenario separately.
-
-\subsubsection{Effects of pattern parameters M,L,K,G}
-\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
-present the performance of TRPM and SPARE when $M$ changes under three datasets.
-As the figures show, SPARE runs much faster than TRPM. We can see that SPARE
-speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
-7 times in Taxi data. Another observation is that, the running times
-of both algorithms slightly decrease as $M$ grows. This is
-because when $M$ becomes bigger, smaller clusters (stars) in 
-the reduce phase of TRPM and SPARE can be directly pruned.
-
-\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
-presents the performance of TRPM and SPARE when $K$ changes under three datasets. 
-There are two interesting findings in study the performance wrt. $K$. 
-First, SPARE and TRPM takes different trends as $K$ increases. 
-Whe $K$ increases, SPARE tends to have faster performances 
-while TRPM's performances continuously slow down. For SPARE, the 
-good performances result from more pruning powers brought
-by $K$. When $K$ increases, many shorter time sequences in the reduce phase
-are pruned. In contrast, $K$ does not bring much pruning power
-during the reduce phase of TRPM. Even $K$ is very large, each reducers in TRPM
-still has to sweep the entire partition to determine whether a pattern exists.
-Moreover, $\eta$ in TRPM grows linearly with $K$. This indicates that
-more data are shuffled and more snapshots are need to
-be swept in each partition. This explains the low performance of TRPM as $K$
-increases. Another interesting finding is that, when $K$ is small,
-TRPM tends to outperform SPARE. This is because that when $K$ is small, shuffle
-data of TRPM is comparable to SPARE. Meanwhile, small $K$ indicates small
-size of partition in TRPM but low pruning power in SPARE. This explains the
-superiority of TRPM. Note that, when $K$ is small, TRPM is 30\% 
-faster than SPARE and the absolute time is less than three minutes.
-
-\textbf{Vary $L$}:Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performance
-of TRPM and SPARE when $L$ changes under three datasets. We can see that $L$
-provides good pruning power from $10$ to $20$ for both TRPM and SPARE. For TRPM,
-the benefit of increasing $L$ is bi-folded. First, when $L$ increases from $10-50$, 
-the $\eta$ decreases, which reduces the shuffle and partition sizes. Second, when
-$L$ increases, the initial pruning in line-sweep is more beneficial. For SPARE,
-increasing $L$ does not affect the shuffling, but benefits the simplification.
-It is also observed that when $L$ increases, the pruning power increases marginally.
-This is because that many patterns contains short segments, when $L$ increases,
-these patterns are largely pruned.
-
-\textbf{Vary $G$}:Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performance
-of TRPM and SPARE when $G$ changes under three datasets. In general, both TRPM and SPARE
-runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
-exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
-that there is an burst of TRPM as $G$ increases. The major reason is that 
-during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
-This makes the candidate set exponentially grows and 
-the join operation becomes very expensive.
-Unlike TRPM, SPARE is although affected by the increase of $G$, 
-but the impact is marginal as compared
-to TRPM. This is because, although true patterns may become 
-exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
-can quickly output true patterns without enumerating every of its subset.
-%\subsubsection{Effects of clusters $\epsilon$, minPt}
-
-\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary}
-\begin{figure}[h]
-\centering
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
-        \caption{Number of patterns vary $L$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
-        \caption{Number of patterns vary $G$}
-    \end{subfigure}    
-\caption{Number of patterns discovered in three datasets on different parameters}
-\label{exp:patterns_vary}
-\end{figure}
+dataset and 5 times of geolife dataset.
+ In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.
 
@@
 \end{figure*}
+%\subsubsection{Effects of pattern parameters M,L,K,G}
+\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
+present the performance when $M$ changes.
+As the figures show, SPARE based algorithms runs much faster than TRPM. We can see that SPARE
+speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
+7 times in Taxi data. An interesting observation is that, the running times
+of all algorithms slightly decrease as $M$ grows. This is
+because when $M$ becomes bigger, smaller clusters or stars can be directly pruned, which brings in the efficiency.
 
-\subsubsection{Detail comparison between SPARE and TRPM}
+\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
+presents the performances when $K$ changes. 
+There are two interesting findings. 
+First, SPARE based algorithms and TRPM takes different trends as $K$ increases. 
+When $K$ increases, SPARE and SPARE-LB tends to run faster
+while TRPM continuously slows down. For SPARE, the trends are resulted from more pruning powers brought
+by $K$. When $K$ increases, more sequences can be pruned by the \emph{sequence simplification}.
+Conversely, TRPM fails to utilize $K$ for pruning. Moreover, as $K$ increases, $\eta$ in TRPM grows, indicating more replication of snapshots. 
+This explains the low performance of TRPM.
+Second, when $K$ is small (i.e, $K$=120), TRPM could outperform SPARE.
+This is because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE.
+As a result, TRPM wins 10\% in Geolife dataset.
+However, by leveraging the load balancing, SPARE-LB is still faster than TRPM.
 
-\subsection{SPARE Analysis}
+\textbf{Vary $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performances when $L$ changes.
+We can see that SPARE based algorithms are still superior than TRPM, where SPARE-LB outperforms TRPM near 10 times when $L =10$.
+An interesting observation is that $L$
+provides good pruning power from $10$ to $20$ for both TRPM and SPARE based algorithms.
+The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.
+As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms.
+This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.
 
-\subsubsection{Scalability}
+\textbf{Vary $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performances when $G$ changes.
+Unlike other cases, when $G$ increases, both TRPM and SPARE based algorithms run slower.
+The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted.
+We observe that there is a burst in performance of TRPM when $G$ reach to $30$.
+The major reason is that when $G$ becomes to 30, the number of valid patterns almost doubles as shown in Figure~\ref{exp:patterns_vary} (d).
+This indicate that during TRPM's line sweep, very few patterns can be pruned, making the candidate set grows exponentially.
+Similarly, SPARE algorithms are also affected by the increase of $G$.
+However we do not observe such a burst for SPARE.
+The reason is bi-folded.
+First, SPARE can utilize $K$, $L$ to retain the power of pruning.
+Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
+%
+%
+% However, since SPARE algorithms are able to utilize $K$, $L$, $M$ in pruning, the 
+%
+%
+%In general, both TRPM and SPARE
+%runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
+%exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
+%that there is an burst of TRPM as $G$ increases. The major reason is that 
+%during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
+%This makes the candidate set exponentially grows and 
+%the join operation becomes very expensive.
+%Unlike TRPM, SPARE is although affected by the increase of $G$, 
+%but the impact is marginal as compared
+%to TRPM. This is because, although true patterns may become 
+%exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
+%can quickly output true patterns without enumerating every of its subset.
+%\subsubsection{Effects of clusters $\epsilon$, minPt}
+
+%\subsubsection{Anatomy of SPARE and TRPM}
+
+\subsection{Analysis of SPARE and SPARE-LB}
+As SPARE based algorithms are superior than TRPM,
+we further analyze several more aspects of SPARE namely, \emph{power of pruning}, \emph{load balance} and \emph{scalability}.
+
+\subsubsection{Power of sequence simplification}
+One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
+As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
+to prune false candidates. To study the power of sequence simplification,
+we collect the total number of pairs that are pruned before apriori enumeration. The
+statistics are shown in Table~\ref{tbl:pruning} under default parameters.
+The result states that the \emph{sequence simplification} is a very powerful pruning technique.
+It cuts off near 90\% of the initial pairs, which significantly reduces the costs
+of later enumerations. This confirms the necessity and usefulness of design such a technique.
+
+\begin{table}[h]
+\begin{tabular}{|l|c|c|c|}
+\hline 
+\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
+\hline 
+Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
+\hline 
+After pruning & 76,672 & 123,410 & 270,921 \\ 
+\hline 
+Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
+\hline 
+\end{tabular} 
+%
+%\begin{tabular}{|c|c|c|c|}
+%\hline 
+%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
+%\hline 
+%Shopping & 878,309 & 76,672 &  91.2\%\\ 
+%\hline 
+%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
+%\hline 
+%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
+%\hline 
+%\end{tabular} 
+\caption{Pruning power of SPARE}
+\label{tbl:pruning}
+\end{table}
+
 \begin{figure}[h]
 \centering
-   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
-\caption{Scalability of SPARE vary. $N$ under different datasets.}
-\label{exp:patterns_vary}
+	\begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
+        \caption{Decomposed running time}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
+        \caption{Workload in Shopping}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
+        \caption{Workload in Geolife}
+    \end{subfigure}  
+    \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
+        \caption{Workload in Taxi}
+    \end{subfigure}
+\caption{Load balance of SPARE and SPARE-LB}
+\label{exp:wl}
 \end{figure}
@@
 \subsubsection{Load Balance}
+To study why SPARE-LB is more efficient,
+we analyze the running time of  SPARE and SPARE-LB for 
+each map-reduce stage. 
+The detail anatomy is shown in Figure~\ref{exp:wl}(a).
+We can see that on all three datasets, the reduce phase for both SPARE and SPARE-LB takes the majority time. The overall improvement of SPARE-LB is around 10-13\%
+under the default settings. We observe that the map and shuffle time
+of SPARE and SPARE-LB are identical, where SPARE-LB spends a very small portion of extra time (4\% of the total time)
+in applying the best-fit strategy. The time spent is worthwhile
+as in the reduce phase SPARE-LB saves around 20\% of the time. However, since the star sizes in SPARE is almost identical (due to Theorem~2), the best-fit strategy does not win too significantly.
+
+We then look at the workload distribution of SPARE and SPARE-LB on real datasets. We collect the statistics from executors
+and report their reduce times in Figure~\ref{exp:wl}. The figure shows that SPARE-LB is able to provide a more balanced task allocation in all three cases. Since SPARE takes random assignment
+of stars, it is likely to assign many large stars to the same executor. As we can see the difference between stragglers in
+SPARE-LB and SPARE ranges from 60 seconds to 100 seconds. In general cases, SPARE-LB is recommended as it offers more efficiency while takes only a small extra time for planning.
+
+\subsubsection{Scalability}
+We then study the scalability of SPARE-LB from two aspects. 
+First, we fix the computing power and vary the size of dataset.
+We perform a random sample from the tree dataset and the results of SPARE-LB are shown in Figures~\ref{fig:scalability-wl}.
+As the figures show, SPARE-LB grows almost linearly wrt $|O|$ and $|T|$.
+This suggests a good scalability.
+Note that, as shown in Figure~\ref{fig:related_work_scalability}, a centralized algorithm runs more than a hundred times slower than SPARE for the same scale of data.
+This confirms the superiority of our parallel
+
+\begin{figure}[h]
+\begin{subfigure}[b]{0.22\textwidth}
+\centering
+    \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-O.eps}
+        \caption{Scalability vary $|O|$}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-T.eps}
+        \caption{Scalability vary $|T|$}
+    \end{subfigure}
+ \caption{Scalability of SPARE-LB wrt. different data sizes}
+ \label{fig:scalability-wl}
+\end{figure}
+
+Second, we fix the work load and vary the number of executors.
+The result are presented in Figure~\ref{exp:scalability}.
+We can see that SPARE achieves good scalability under all three cases. 
+For instance, for Taxi dataset, when the executors rises from 10 to 50, 
+the performance improves 4.8 times which is almost linear to the increase of executors.
+Such pattern also holds for the other two datasets.
+The reason for the good scalablity is that SPARE partitions the trajectories by objects and each partition is perfectly independent.
+Therefore, when the number of reducers $N << |O|$, SPARE can always speed up by adding more executors.
+\begin{figure}[h]
+\centering
+   \includegraphics[width=0.3\textwidth]{/exp/spare/scalability.eps}
+\caption{Scalability of SPARE-LB vary. $N$.}
+\label{exp:scalability}
+\end{figure}

### 2016-06-25 sec7_conclusion.tex
A new draft
Flighting

\section{Conclusion and Future Work}
\label{sec:concl}

### 2016-06-25 sec1_introduction.tex
A new draft
Flighting
Need to add three more experiments
Three more charts

@@
 \centering
-\includegraphics[width=0.45\textwidth]{related_work.eps}
+\includegraphics[width=0.46\textwidth]{related_work.eps}
 \caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots.
@@
 Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps.
-Hence,$\{o_3,o_4\}$ and $\{o_5,o_6\}$  remains the only two candidates matching the patterns.
+Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  remains the only two candidates matching the patterns.
 The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint.
@@
 The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns.
-For instance, $\{o_1,o_2:1,2,4,5\}$ is a pattern matching local consecutiveness because timestamps $\{1,2\}$ and $\{4,5\}$ are two segments with length no smaller than $L=2$.
+For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$.
 The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters.
-This explains why $\{o_3,o_4,o_5:2,3\}$ is a  \textit{group} pattern but not a \textit{platoon} pattern.
+This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.
 
@@
 We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario.
-These two objects form a \emph{platoon} pattern in timestamps $\{1,2,3,102,103,104\}$.
+These two objects form a \emph{platoon} pattern in timestamps $(1,2,3,102,103,104)$.
 However, the two consecutive segments are $98$ timestamps apart, resulting in a false positive co-movement pattern.
@@
 \caption{\emph{Loose-connection} anomaly.
-Even though $\{o_1, o_2: 1,2,3,102,103,104\}$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
+Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
 % in \emph{platoon}, \emph{swarm} and \emph{group} results.
@@
 In particular, with near 200 million trajectory points, 
-SPARE runs in 15 minutes using 172 cores. Whereas
+SPARE runs in 15 minutes using 162 cores. Whereas
 centralized solutions take near 7 hours 

### 2016-06-25 sec4_baseline.tex
Need to add three more experiments
Three more charts

@@
 In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase.
-Finally, the reducers output clusters of objects in each snapshot, represented by a list of $\langle t,S_t \rangle$ pairs, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
+Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
 
@@
 It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
-early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, 
-in line sweep, only patterns that starts from timestamp $t$ (i.e., $S_t$) need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
+early remove false candidates from $C$.
+Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered.
+Therefore, those patterns that does not appear in the $S_t$ are false candidates.
+Particularly, our
 three pruning rules are as follows:
@@
 As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
-$\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
+$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
 and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
-Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
-because its local consecutive segment $\{4\}$ has only $1$ element,
+Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
+because its local consecutive segment $(4)$ has only $1$ element,
 which violates the $L$-consecutive constraint.
-Finally, $\{o_3,o_4\}$ is the valid pattern and is returned.
+Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned.
 Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness.
-If $\eta$ is set to $4$, the pattern $\{o_3,o_4\}$ would be missed.
+If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.
 

### 2016-06-25 sec5_spm.tex
Need to add three more experiments
Three more charts

@@
 Second, the same valid pattern may be discovered from different partitions which results in redundant works.
-%and results in groups of snapshots in each partition.
-% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
 To resolve the limitations caused by the replicate partitioning, 
@@
 is shown in Figure~\ref{fig:star_partition} (a). 
-As long as two objects are clustered in any timestamp, they are connected in $G_A$. 
-The object pair $(o_1,o_2)$ appears in two clusters at timestamps 
-$2$ and $3$ and is thus associated with an inverted list $\{2,3\}$.
+As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
+The object pair $\langle o_1,o_2 \rangle$ appears in two clusters at timestamps 
+$2$ and $3$ and is thus associated with an inverted list $(2,3)$.
 
@@
 \begin{proof}
-In Appendix XXX.
+In Appendix~\ref{apx:thm2proof}.
 \end{proof}
@@
 \begin{proof}
-In Appendix XXXX.
+In Appendix~\ref{apx:thm2proof}.
 \end{proof}
@@
 %%which surrenders the benefit of parallelism.
-\eat{
-Although TRPM works in a parallel way, we observe two inefficiencies. First, the
-performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
-When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
-the parallel execution of line sweep algorithm may discover the same pattern from
-multiple partitions, which introduces redundant work. To resolve the two limitations,
-we design a novel \emph{Star Partition and Mining} algorithm.
-}
+%\eat{
+%Although TRPM works in a parallel way, we observe two inefficiencies. First, the
+%performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
+%When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
+%the parallel execution of line sweep algorithm may discover the same pattern from
+%multiple partitions, which introduces redundant work. To resolve the two limitations,
+%we design a novel \emph{Star Partition and Mining} algorithm.
+%}
 %After computing the star, each partition is applied with a reduce task. 
@@
 Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, 
-all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must 
+all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
 be connected in the associated temporal graphs $\{G_t\}$.
@@
 In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
-Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
+Consider two candidates $P_1=\langle o_1,o_2:1,2,3,6 \rangle$ and $P_2=\langle o_1,o_3:1,2,3,7 \rangle$. 
 Let $L=2,K=3$ and $G=2$. Both candidates are not valid patterns because the constraint on $L$ is not satisfied. 
-However, when considering their object superset $\{o_1,o_2,o_3\}$, we can infer that their co-clustering timestamps are in $(1,2,3)$.
+However, when considering their object superset $\langle o_1,o_2,o_3 \rangle$, we can infer that their co-clustering timestamps are in $(1,2,3)$.
 This is a valid pattern conforming to the constraints of $L,K,G$.
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
 \caption{Apriori Enumerator}
@@
 \begin{example}
-As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty.
-Thus, all the object sets containing $\{3,6\}$ can be pruned.
-The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid.
-By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
+As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\langle 3,6:3 \rangle $ is pruned because its simplified sequence is empty.
+Thus, all the object sets containing $\langle 3,6 \rangle $ can be pruned.
+The remaining two candidates (i.e., $\langle 3,4:1,2,3 \rangle$ and $\langle 3,5:2,3 \rangle$)  derive a new  $\langle 3,4,5:2,3 \rangle$ which is valid.
+By the forward closure checking, the algorithm can terminate and output $\langle 3,4,5:2,3 \rangle$ as the final closed pattern.
 \end{example}
@@
 After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship.
-However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.
-Instead, we simply need to emit the edges within a star partition to the same reducer.
+However, in the implementation of the map phase, there is no need to create $G_A$ in advance.
+Instead, we simply need to emit the edges within a star to the same reducer.
+Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation.
+In best-fit strategy, the most costly unallocated star is assigned to the most empty reducers, where we use the edges in the star as a cost estimation.
  Each reducer is an Apriori Enumerator.
 When receiving a star $Sr_i$, the reducer creates initial candidate patterns.
-Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created.
+Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created.
 Then it enumerates all the valid patterns from the candidate patterns.
@@
 \begin{proof}
-See Appendix XXXX.
+See Appendix~\ref{apx:spm_correct}.
 \end{proof}

### 2016-06-25 sec7_conclusion.tex
Need to add three more experiments
Three more charts

@@
-\section{Conclusion and Future Work}
+\section{Conclusion}
 \label{sec:concl}
+In this paper, we present our framework SPARE for detecting General Co-Movement Patterns (GCMP) over large-scale trajectories.
+Our GCMP is versatile in representing all existing co-movement patterns while being free from the \emph{loose-connection} anomaly.
+Our SPARE framework, comprising a novel star-partition with several optimization techniques, has shown superior performances and scalability in three real datasets with hundreds of millions trajectories.

### 2016-06-26 sec4_baseline.tex
A more complete one
hhah

@@
 \includegraphics[width=\textwidth]{trm.eps}
-\caption{Work flow of Temporal Replication and Parallel Mining.
-(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle uses TRPM to detect GCMP in parallel.}
+\caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
+(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle, which uses TRPM to detect GCMP in parallel.}
 \label{fig:trm}

### 2016-06-26 sec5_spm.tex
A more complete one
hhah

@@
 \includegraphics[width=0.9\textwidth]{spm.eps}
-\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
-(c) Apriori Mining with various pruning techniques.}
+\caption{Star partition and ApRiori Enumerator (SPARE).
+(a) Aggregate graph from Figure 1.
+(b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
+(c) Apriori Enumerator with various pruning techniques.}
 \label{fig:star_partition}

### 2016-06-26 sec6_experiment.tex
A more complete one
hhah

@@
 \label{sec:exp}
-In this section, we present our experimental findings on
-deploying our GCMP detectors to large-scaled real trajectories.
-All the experiments are carried out on our in-house cluster: Dianwei.
-The cluster includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors, 32 GB memory and gigabit Ethernet.
-The cluster is installed with CentOS 5.5.
-operating system.
+In this section, we evaluate the efficiency and scalability of our proposed distributed GCMP detectors on real trajectory datasets.
+All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet.
+%The cluster is installed with CentOS 5.5. operating system.
 
-\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
-to manage our cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
-Yarn processes. We use Apache Spark 1.5.5~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
-the remaining 11 nodes as the computing nodes.
-To fully utilize the computing power of the cluster, 
-we assign each node to run five executors, each executor takes three cores and 5 GB memory. We use "yarn-cluster" mode
-for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
-at the same time. We use HDFS as our storage engine with replicator factor of 1.
-The summary of the configuration is as in the following table:
+\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html} to manage our cluster.
+We pick one machine as the Yarn's master node, and the remainings reserve one core and $2$GB memory for Yarn processes.
+We deployed our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
+To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
+In Spark, one of the $55$ executor is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
+All our implementations as well as cluster setups are open-sourced in XXX.
+%can be referred in our 
+%We use ``yarn-cluster'' mode
+%for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
+%at the same time. We use HDFS as our storage engine with replicator factor of 1.
+%The summary of the configuration is as in the following table:
 
+\eat{
 \begin{table} [h]
@@
 \end{table}
+}
 
-\textbf{Datasets}: We prepare three real datasets for experiments. The details of the datasets are as follows:
+\textbf{Datasets}: We use three real trajectory datasets in different application scenarios:
 \begin{itemize}
-\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: this dataset collects 
-18,670 trajectories for passengers in Beijing over three years. The data are collected
-per around 5 seconds. Each data point records a trajectory ID and the latitude/longitude information.
-\item{Shopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: this dataset contains
- visitors trajectories in ATC shopping center in Osaka. The samples are taken per
- around 0.5 seconds. There are in total 13,183 trajectories. Each data point is a 
- trajectory ID with in-door coordinates.
-\item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
-rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude information.
+\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}. The dataset essentially keeps all the travel records of 182 users for a period
+of over three years, including multiple kinds of transportation modes (walking, driving and taking public
+transportation). For each user, the GPS information is collected periodically and 91 percent of the trajectories
+are sampled every 1 to 5 seconds.
+\item{Shopping}\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}. The dataset contains
+  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
+\item{Taxi}. The dataset tracks the trajectories of $15,054$ taxies in Singapore over August 2008. The sampling
+rate is around 30 seconds. 
 \end{itemize}
 
-\textbf{Preprocessing}: We replace timestamps with global sequences for each dataset. The sequence number
-$0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
-each dataset as the tick of the sequence number and every data point is mapped to the nearest ticks. If
-several points mapped to the same tick, they are merged by averaging the location coordinates.
-For missing data within small intervals (i.e., sequence difference less than 10), 
-we use linear interpolation to fill them. 
-We then use DBSCAN ($\epsilon=5, minPt=10$ for GeoLife and Shopping, $\epsilon=20, minPt=10$ for Taxi)
-as the clustering algorithm for preprocessing.  
-Note that both our TRPM and SPARE algorithms treat the preprocessing as a black box and other
-spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
-$t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
+\textbf{Preprocessing}: We replace timestamps with global sequences (starting from $1$) for each dataset. 
+We set a fixed sampling rate for each dataset (i.e., Geolife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
+and use linear interpolation to fill missing values.
+%For each dataset, we set a fixed sampling rate (CLEARLY STATE THE SAMPLING RATE FOR EACH DATASET) and use linear interpolation to fill missing values. 
+%Finally, we obtain a set of trajectories with equal length. 
+%Finally, we obtain a set of dense trajectories with equal length. 
+For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ and $minPt$~\footnote{$\epsilon$ is the maximum neighborhood range to be concerned, $minPt$ is the minimum number of objects to form a dense region.}.
+We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset.
+Note that other clustering methods and settings can also be applied.
+The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$.
 After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.
@@
 \hline
- \textbf{Attributes}& \textbf{ACTShopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
+ \textbf{Attributes}& \textbf{Shopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
 \hline 
@@
 \hline
-\# average ts & 3,114  & 2,924 & 19,667 \\ 
-\hline
+%\# average ts & 3,114  & 2,924 & 19,667 \\ 
+%\hline
 \# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
@@
 \textbf{Parameters}: To systematically study the performance of
-our algorithms, we conduct experiments on various conditions. The variables
-to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
-Default values are highlighted in bold.
+our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold. 
 \begin{table}[h]
@@
 \hline
-N & number of executors & 1, 14, 24, 34, 44, \textbf{54}\\ 
+$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
+$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
+N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
 \hline 
@@
 
+\eat{
 \textbf{Number of patterns under different parameters}: We first 
@@
 The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent.
-With GCMP, we can discover these patterns by adjusting property $L$ and $G$s.
+With GCMP, we can discover these patterns by properly adjusting $L$ and $G$s.
 
@@
 \end{figure}
+}
 
+\eat{
 \textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study.
@@
 unassigned task is allocated to the current mostly empty reducer. 
-In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The other
-part of SPARE-LB is identical with SPARE.
+In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The remaining
+parts of SPARE-LB are identical to SPARE.
+}
 
-%\subsection{Effects of $G$ on GCMP}
-%\begin{figure*}[t]
-%\centering
-%    \begin{subfigure}[b]{0.3\textwidth}
-%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
-%        \caption{Geolife}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.33\textwidth}
-%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
-%        \caption{ACTShopping}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.3\textwidth}
-%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
-%        \caption{SingTaxi}
-%    \end{subfigure}
-%\caption{Effectiveness of GCMP model on sampled datasets.}
-%\label{exp:effectiveness}
-%\end{figure*}
-%We first study the effects of introducing gap parameter $G$ on pattern discovery.
-%As shown in Figure~\ref{fig:related_work_scalability},
-%existing works are not able to handle large trajectories, 
-%we sample and cluster $1$ million trajectory points from the three real data.
-%We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
-%of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
-%
-%We can see from Figures~\ref{exp:effectiveness} that the number of patterns
-%discovered by GCMP is positively related to $G$. When $G =1$, the number
-%of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
-%the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
-%patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
-%when $G$ is $50$. The reason is that when $G$ is large enough,
-% all \emph{platoon}s are $G$-connected. Similar
-% trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
-% patterns converge at $G=50$; while in (b) and (c) the two patterns converge
-% at $G=60$ and $G=40$ respectively. We further
-% note that, existing patterns has different granularity in temporal domain. As we seen
-% from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
-% \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
-% the temporal domain of patterns, GCMP can discover the patterns more precisely. 
-% These results confirms the usefulness of GCMP in expressing other patterns.
-%  
-%
-
-\subsection{Performance Comparison}
+\subsection{Performance Evaluation}
+\eat{
 Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
@@
  In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.
-
+}
 \begin{figure*}[t]
@@
 %\subsubsection{Effects of pattern parameters M,L,K,G}
-\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
-present the performance when $M$ changes.
-As the figures show, SPARE based algorithms runs much faster than TRPM. We can see that SPARE
-speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
-7 times in Taxi data. An interesting observation is that, the running times
-of all algorithms slightly decrease as $M$ grows. This is
-because when $M$ becomes bigger, smaller clusters or stars can be directly pruned, which brings in the efficiency.
+\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
+present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
+$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.
 
-\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
-presents the performances when $K$ changes. 
-There are two interesting findings. 
-First, SPARE based algorithms and TRPM takes different trends as $K$ increases. 
-When $K$ increases, SPARE and SPARE-LB tends to run faster
-while TRPM continuously slows down. For SPARE, the trends are resulted from more pruning powers brought
-by $K$. When $K$ increases, more sequences can be pruned by the \emph{sequence simplification}.
-Conversely, TRPM fails to utilize $K$ for pruning. Moreover, as $K$ increases, $\eta$ in TRPM grows, indicating more replication of snapshots. 
-This explains the low performance of TRPM.
-Second, when $K$ is small (i.e, $K$=120), TRPM could outperform SPARE.
-This is because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE.
+\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(f),(j).
+SPARE tends to run faster, whereas the performance of TRPM degrades dramatically.
+This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$.
+However, the line sweep algorithm in TRPM does not utilize such property for pruning.
+It takes longer time because more replication data has to be handled in each partition.
+
+%Second, when $K$ is very small (i.e, $K=0.XXX|T|$), TRPM could outperform SPARE because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE.
 As a result, TRPM wins 10\% in Geolife dataset.
@@
 
-\textbf{Vary $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performances when $L$ changes.
-We can see that SPARE based algorithms are still superior than TRPM, where SPARE-LB outperforms TRPM near 10 times when $L =10$.
+\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) present the performances with varying $L$.
+When $L=10$, SPARE can outperform TRPM by around $10$ times.
+We also observe that there is a significant performance improvement for TPRM when $L$ increases from $10$ to $20$ and later the running time drops smoothly.
+This is because $\eta$ is proportional to $O(L + 1/L)$. When $L$ is small (i.e., from $10$ to $20$),
+$\eta$ decreases quickly (i.e., 30\%). As $L$ further increases (e.g, from $20$ to $30$),
+$\eta$ decreases steadily (e.g, 15\%).
+%CAN YOU EXPLAIN THIS FROM THE RELATIONSHIP between $\eta$ and $L$.
+
+\eat{
 An interesting observation is that $L$
@@
 The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.
-As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms.
-This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.
 
-\textbf{Vary $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performances when $G$ changes.
-Unlike other cases, when $G$ increases, both TRPM and SPARE based algorithms run slower.
+ As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms. This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.
+}
+
+\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) present the performances with increasing $G$.
+TRPM is rather sensitive to $G$.
+When $G$ is relaxed to larger values, more valid patterns would generate.
+TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$.
+In contrast, with much more effective pruning strategy, our SPARE scales very well with $G$.
+
+\eat{
+We can see that both TRPM and SPARE run slower.
 The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted.
@@
 Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
-%
-%
-% However, since SPARE algorithms are able to utilize $K$, $L$, $M$ in pruning, the 
-%
-%
-%In general, both TRPM and SPARE
-%runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
-%exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
-%that there is an burst of TRPM as $G$ increases. The major reason is that 
-%during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
-%This makes the candidate set exponentially grows and 
-%the join operation becomes very expensive.
-%Unlike TRPM, SPARE is although affected by the increase of $G$, 
-%but the impact is marginal as compared
-%to TRPM. This is because, although true patterns may become 
-%exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
-%can quickly output true patterns without enumerating every of its subset.
-%\subsubsection{Effects of clusters $\epsilon$, minPt}
+}
+\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary_OT} (a)(b)(c) present 
+the performances wrt. increasing number of total objects. The x-axis are the ratio
+of objects sampled from the corresponding datasets. We can see that the performance of
+both TRPM and SPARE decreases linearly to the the number of total objects. This
+is reasonable since larger $O_r$ results in more clusters per snapshot, which affects
+the line-sweep in TRPM and the aggregate graph in SPARE. However in all cases, SPARE
+consistently outperforms TRPM.
 
-%\subsubsection{Anatomy of SPARE and TRPM}
+\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary_OT} (d)(e)(f) present 
+the performances wrt. increasing number of total snapshots.  The x-axis represents the size of
+snapshots sampled from the corresponding datasets. We again observe the linear decrease of
+the performances wrt. the number of snapshots. In all cases, SPARE is faster than
+TRPM. We further observe that as $T_r$ grows, the gaps between SPARE and TRPM tends
+to be larger, this is because larger $T_r$ results larger partition size, and more 
+snapshots needs to be swept in TRPM.
 
-\subsection{Analysis of SPARE and SPARE-LB}
-As SPARE based algorithms are superior than TRPM,
-we further analyze several more aspects of SPARE namely, \emph{power of pruning}, \emph{load balance} and \emph{scalability}.
+\begin{figure}[h]
+\centering
+	\begin{subfigure}[b]{0.22\textwidth}
+	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
+        \caption{Shopping vary $O_r$}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
+        \caption{Geolife vary $O_r$}
+    \end{subfigure}
+    	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
+        \caption{Taxi vary $O_r$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.22\textwidth}
+	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
+        \caption{Shopping vary $T_r$}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
+        \caption{Geolife vary $T_r$}
+    \end{subfigure}
+    	 \begin{subfigure}[b]{0.22\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
+        \caption{Taxi vary $T_r$}
+    \end{subfigure}
+ \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
+ \label{exp:performance_vary_OT}
+\end{figure}
+
+\subsection{Analysis of SPARE framework}
+In this part, we extensively evaluate the advantage brought by 
+sequence simplification and load balancing techniques.
 
@@
 to prune false candidates. To study the power of sequence simplification,
-we collect the total number of pairs that are pruned before apriori enumeration. The
+we collect the following two statistics: (1) the number of pairs that
+are shuffled to reducers and (2) the number of pairs that
+are fed to the Apirori enumeration. The difference of the two quantities
+the the pairs that are pruned by the sequence simplification.
+%
+%we collect the total number of pairs that are pruned before apriori enumeration.
+%In particular, we compare the number of 
+%The number of pairs prior to pruning is counted in the load balance stage, while
+%the number of pairs after pruning is counted in the Apriori stage.
+The
 statistics are shown in Table~\ref{tbl:pruning} under default parameters.
@@
 \subsubsection{Load Balance}
-To study why SPARE-LB is more efficient,
-we analyze the running time of  SPARE and SPARE-LB for 
-each map-reduce stage. 
+To study why SPARE is more efficient,
+we analyze the running time of  SPARE
+each map-reduce stage.  To compare with, we use
+the SPARE-RD which is SPARE with random task allocation as a baseline.
 The detail anatomy is shown in Figure~\ref{exp:wl}(a).
-We can see that on all three datasets, the reduce phase for both SPARE and SPARE-LB takes the majority time. The overall improvement of SPARE-LB is around 10-13\%
+We can see that on all three datasets, the reduce phase for both SPARE and SPARE-RD takes the majority time. The overall improvement of SPARE is around 10-13\%
 under the default settings. We observe that the map and shuffle time
-of SPARE and SPARE-LB are identical, where SPARE-LB spends a very small portion of extra time (4\% of the total time)
+of SPARE and SPARE-RD are identical, where SPARE spends a very small portion of extra time (4\% of the total time)
 in applying the best-fit strategy. The time spent is worthwhile
-as in the reduce phase SPARE-LB saves around 20\% of the time. However, since the star sizes in SPARE is almost identical (due to Theorem~2), the best-fit strategy does not win too significantly.
+as in the reduce phase SPARE saves around 20\% of the time.
 
-We then look at the workload distribution of SPARE and SPARE-LB on real datasets. We collect the statistics from executors
-and report their reduce times in Figure~\ref{exp:wl}. The figure shows that SPARE-LB is able to provide a more balanced task allocation in all three cases. Since SPARE takes random assignment
-of stars, it is likely to assign many large stars to the same executor. As we can see the difference between stragglers in
-SPARE-LB and SPARE ranges from 60 seconds to 100 seconds. In general cases, SPARE-LB is recommended as it offers more efficiency while takes only a small extra time for planning.
+We then look at the workload distribution of SPARE and SPARE-RD on real datasets. 
+We collect the statistics from executors
+and report their reduce times in Figure~\ref{exp:wl}. 
+The figures show that SPARE is able to provide a more balanced 
+task allocation in all three cases. Since SPARE-RD takes random assignment
+of stars, it is likely to assign many large stars to the same executor. 
+In general cases, SPARE is recommended as 
+it offers more efficiency while takes only a small extra time for planning.
 
+\eat{
 \subsubsection{Scalability}
@@
 Such pattern also holds for the other two datasets.
-The reason for the good scalablity is that SPARE partitions the trajectories by objects and each partition is perfectly independent.
-Therefore, when the number of reducers $N << |O|$, SPARE can always speed up by adding more executors.
+The reason for the good scalablity is that SPARE partitions the trajectories by objects and partitions are perfectly independent.
+Therefore, when the number of executors $N << |O|$, SPARE can always speed up by adding more executors.
 \begin{figure}[h]
@@
 \end{figure}
+}
+
+\subsection{Scalability and Comparison with Existing Solutions}
+We then study the scalability of our schemes.
+Since existing solutions run on a single machine, it is interesting to compare their
+performances. We choose \emph{platoon} as the comparing scheme as it is
+generic and more efficient than \emph{swarm} and \emph{group}
+The results are presented in Figure~\ref{exp:scalability}. There are two observations.
+First, the centralized scheme (e.g. platoon) are not suitable for discover
+patterns in large-scale trajectories. It takes near 16 hours for discovering \emph{platoon}s
+in Taxi data. As a comparison, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup.
+This is because even there is only 1 machine, our TRPM and SPARE is still able to leverage
+the 15 cores in the machine for parallelism. Second, we see that both TRPM and SPARE
+demonstrate good scalability wrt. $N$. As the number of machines increases from 1 to 11 (i.e., 11 times),
+both TRPM and SPARE achieves near 11 times speedup. Note that SPARE at most achieves 94 times
+speedup as compared to \emph{platoon} using all 11 machines.
+
+\begin{figure*}[t]
+\centering
+\begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
+        \caption{Shopping vary $N$}
+    \end{subfigure}
+ 	 \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
+        \caption{Geolife vary $N$}
+    \end{subfigure}
+    	 \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
+        \caption{Taxi vary $N$}
+    \end{subfigure}
+ \caption{Scalability of SPARE and TRPM wrt. $N$}
+ \label{exp:scalability}
+\end{figure*}

### 2016-06-26 sec4_baseline.tex
A complete version

@@
 \center
-\includegraphics[width=\textwidth]{trm.eps}
+\includegraphics[width=0.9\textwidth]{trm.eps}
 \caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
@@
 
-\eat{
-Before moving on to find the value of $\eta$, 
-we first use $\rho_{G,L,K}(T)$ to define the \emph{min-spanned valid subsequence} 
-of a sequence $T$. In simple words, $\rho_{G,L,K}(T)$ is the 
-subsequence of $T$ with the smallest range and is valid wrt. $K,L,G$. 
-%Let $\eta_T$ denote
-%the range of $\rho_{G,L,K}(T)$.
-To guarantee that no valid patterns are missing, $\eta$ needs
-to be greater than the range of $\rho_{G,L,K}(T)$ for any
-valid sequence $T$. To see this, consider an arbitrary valid sequence $T$.
-Since each partition contains $\eta$ snapshots,
-if $\eta \geq \range(\rho_{G,L,K}(T))$ holds, $\rho_{G,L,K}(T)$ must be completely located in one partition. Therefore, the patterns associated with $T$ would not be missing.
-Formally, $\eta$ can be computed as:
-\begin{equation}
-\eta = \max\{\range(\rho_{G,L,K}(T)) | T \text{ is valid wrt. } G,L,K\}
-\end{equation}
-
-Directly compute such $\eta$ is challenging. However,
-we provide the following theorem which states a bounded estimation on $\eta$: 
-}
-
 \begin{theorem}
@@
 
-\eat{
-Note that Theorem~\ref{THM:RP_ETA} does not state the optimal value of $\eta$
-for a given $G,L,K$. However, for any $G,L,K$, $\eta$ does not differ from
-the optimal value by at most $L-1$. To see this, for any $G,L,K$, we can
-generate a sequence $T$ by repeating the following pattern, a $L$-segment followed by $G$-gap. 
-The repetition stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
-It is easy to see that $T$ is minimal valid subsequence of itself, then $\eta^*  \geq \range(T) \geq (\lceil \frac{K}{L}\rceil -1)(G-1) + K$.
-Therefore $\eta-\eta^* \leq L-1$.
-}
-
 \begin{algorithm}[h]
+\small
 \caption{Line Sweep Mining}
@@
 In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).
-%The join of candidate $c$ and cluster $s$ creates a
-%new candidate $c'$ (Line~\ref{code:ls-join}).  
+
 After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
@@
 are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.
-
-%ADD EXPLANATIONS TO THE SECOND AND THIRD PRUNING RULES.
-
-%After join, there are two prunings. First, 
-%all new candidates with objects set less than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second,
-%existing candidates with max time sequences no greater 
-%than $j-G$ are pruned (Line~\ref{code:ls-m-prun}). 
-% 
-%
-%During the sweeping, candidates in $\mathbf{C}$ join with $S_j$.
-%
-% Initially, all the clusters 
-%
-%During scanning, a set of pattern candidates is maintained.
-%When all snapshots are scanned, the remaining candidates are the true patterns.
-%The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
-%A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
-%is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
-%During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
-%the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
-%false patterns are deleted (line~\ref{code:ls-remove}). 
-%Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.
 
@@
 \begin{algorithm}[h]
+\small
 \caption{Temporal Replication and Parallel Mining}

### 2016-06-26 sec5_spm.tex
A complete version

@@
 
-%An important concern in design parallel algorithms is the distribution of work loads.  
-%Traditionally, the quality of a partition strategy 
-%is measured based on two aspects: (1) the number of result partition, which
-%affects the maximum parallelism
-%(2) the size balance of partitions, which affects the finishing
-%time of a job. Unlike TRM where each partition
-%contains equal-sized snapshots, the size distribution 
-%of stars in SPM remains unknown.
-%Nevertheless, we notice that, in SPM, the total sizes of 
-%stars are invariant. Therefore, the quality of a star partition
-%can be formalized as the \emph{skewness}, which is the maximum star size
-%among all stars. Smaller \emph{skewness} naturally results in more partitions
-%and less imbalance.
-%}
-
 \begin{figure}[h]
@@
 \end{figure}
-
-%To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
-%we can use a linear algebra model as follows:  
-%Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
-%A vertex order is in fact a permutation of $J$. Therefore,
-%the adjacent matrices of any reordered graphs can be represented as $PJP^T$
-%where $P \in \mathbb{P}$ is a 
-%\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
-%Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
-%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
-%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
-%Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
-%vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
-%denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
-%as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
-%$\Gamma^*$ can then be formulated as follows:
-%\begin{equation}
-%\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
-%\end{equation}
 
@@
 Hence, we can simply use object id to determine the vertex ordering in our implementation.
-
-%
-%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
-%When $\eta$ is small, TRM perform good parallelism. However, wh
-%
-%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
-%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
-%%which surrenders the benefit of parallelism.
-%\eat{
-%Although TRPM works in a parallel way, we observe two inefficiencies. First, the
-%performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
-%When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
-%the parallel execution of line sweep algorithm may discover the same pattern from
-%multiple partitions, which introduces redundant work. To resolve the two limitations,
-%we design a novel \emph{Star Partition and Mining} algorithm.
-%}
-%After computing the star, each partition is applied with a reduce task. 
-%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
-%This is done by treating each vertex in $Sr_s$ as an object. 
-%The time sequence of $s$ is the union of all edges in $Sr_s$. 
-%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
-%are able to mine stars from the similar trajectory concepts.
 
@@
 \end{definition}
-%Hence, our idea is to examine the validity of object pairs.
-If $(o_i,o_j)$ itself is not a valid GCMP pattern, then all the supersets containing $(o_i,o_j)$ can be pruned.
-For instance, $(XXX,XXX)$ are not connected in Figure~\ref{} and all its supersets can be pruned.
 
@@
 
-%Not that, although $T_1$ is not a candidate sequence, it can be simplified
-%to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
-%if it does not contain a \emph{candidate sequence}, then it cannot contribute
-%to any valid patterns. In fact, only the candidate sequence inside $T$ affects
-%the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
-%a star. During the simplification, if an edge results in a candidate
-%sequence of size zero, then it is removed from the star. Otherwise,
-%the simplified edge is kept. By so doing, the size of the new star
-%is much smaller.
-
 \begin{definition}[Sequence Simplification]
@@
 
-\eat{
-Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
-as stated in the following theorem:
-\begin{theorem}
-For any sequence $T$, if $T$'s simplified sequence is not empty, then
-there exists a unique $T^\#$ wrt $T$.
-\end{theorem}
-\begin{proof}
-We prove by contradiction.
-Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$.
-We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction.
-For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
-Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.
-
-Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$.
-Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
-is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
-there are four cases to be considered. 
-We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.46\textwidth]{thm3proof.eps}
-\caption{Proof of theorem 3 with the four cases.}
-\label{fig:proof_thm_3}
-\end{figure}
-\begin{itemize}
-\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$.
-Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
-\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
-consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$.
-Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
-\item Case (c): $c-f > G$ and $e-h \leq G$.
-In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.
-Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
-\item Case (d): $c-f > G$ and $ e- h > G$.
-In this case,  $\overline{ef}$ has to be a candidate sequence.
-Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
-\end{itemize}
-In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
-\end{proof}
-}
-
-\eat{
-Next, we design an efficient simplification process with linear complexity.
-It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
-In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
-In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.
-
-\begin{algorithm}
-\caption{Edge Simplification}
-\label{algo:simp_prune}
-\begin{algorithmic}[1]
-\Require $T$
-\State{---$L$ Phase---}
-\State $c \gets 0$
-\For {$i \in (0,...,|T|)$}
-	\If{$T[i] - T[i-1] > 1$} 
-		\If{$i - c < L$} 
-			\State $T$ remove $[c:i)$
-		\EndIf
-		\State $c \gets i$
-	\EndIf
-\EndFor
-\State{---$G$-$K$ Phase---}
-\State $s\gets 1$, $c\gets 0$
-\For{$i \in (0: |T|)$}
-	\If{$T[i] - T[i-1] > G$}
-		\If{$s < K$}   
-			\State $T$ remove $[c:i)$
-		\EndIf
-		\State {$c \gets i$, $s \gets 1$}
-	\Else
-		\State $s++$
-	\EndIf
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-}
-
 With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
@@
 \end{proof}
-
-%IN THE PROOF, YOU NEED TO SHOW 1) $P$ IS NOT VALID 2) ALL THE SUPERSETS OF $P.O$ ARE NOT VALID.
 
@@
 \State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
-%\ElsIf{$c$ is a valid pattern}
-%\State{output $c$}
 \EndIf 
@@
 	\EndFor
-%	
-%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
-%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
-%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
-%					\State {$C'\leftarrow C'\cup \{c'\}$}
-%					\ElsIf{$c'$ is a valid pattern}
-%						\State{output $c'$}
-%				\EndIf
-%		\EndFor	\label{code:join-ends}
 	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
@@
 \begin{algorithm}
+\small
 \caption{Star Partition and ApRiori Enumerator}
@@
 	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
-	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
 \EndFor

### 2016-06-26 sec6_experiment.tex
A complete version

@@
 All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet.
-%The cluster is installed with CentOS 5.5. operating system.
 
-\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html} to manage our cluster.
+\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster.
 We pick one machine as the Yarn's master node, and the remainings reserve one core and $2$GB memory for Yarn processes.
-We deployed our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
+We deploy our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
 To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
 In Spark, one of the $55$ executor is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
-All our implementations as well as cluster setups are open-sourced in XXX.
-%can be referred in our 
-%We use ``yarn-cluster'' mode
-%for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
-%at the same time. We use HDFS as our storage engine with replicator factor of 1.
-%The summary of the configuration is as in the following table:
-
-\eat{
-\begin{table} [h]
-\centering
-\begin{tabular}{|l|c|}
-\hline 
-Parameter & Value  \\ 
-\hline 
-Java Version & 1.7.0 \\ 
-\hline 
-Spark Version & 1.5.5 \\ 
-\hline 
-spark.driver.memory & 2GB \\ 
-\hline 
-spark.executor.cores & 3  \\ 
-\hline 
-spark.executor.instances & 54 \\ 
-\hline 
-spark.executor.memory & 5GB \\ 
-\hline 
-spark.master & yarn-cluster \\
-\hline 
-spark.serializer & KryoSerializer \\ 
-\hline 
-\end{tabular} 
-\end{table}
-}
+All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
 
@@
 \begin{itemize}
-\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}. The dataset essentially keeps all the travel records of 182 users for a period
+\item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}. The dataset contains
+  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
+\item{GeoLife}~\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}. The dataset essentially keeps all the travel records of 182 users for a period
 of over three years, including multiple kinds of transportation modes (walking, driving and taking public
@@
 are sampled every 1 to 5 seconds.
-\item{Shopping}\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}. The dataset contains
-  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
 \item{Taxi}. The dataset tracks the trajectories of $15,054$ taxies in Singapore over August 2008. The sampling
@@
 %Finally, we obtain a set of dense trajectories with equal length. 
-For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ and $minPt$~\footnote{$\epsilon$ is the maximum neighborhood range to be concerned, $minPt$ is the minimum number of objects to form a dense region.}.
+For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ (proximity threshold) and $minPt$ (the minimum number of points required to form a dense region).
 We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset.
-Note that other clustering methods and settings can also be applied.
-The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$.
-After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.
+Note that other clustering methods or settings can also be applied.
+%The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
+After preprocessing, the statistics of the three datasets are listed in Table~\ref{exp:dataset}.
 
@@
 \hline
- \textbf{Attributes}& \textbf{Shopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
+ \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{SingTaxi} \\ 
 \hline 
@@
 \hline
-%\# of patterns & 3,741 & 4,369  & 7,585 \\
-%\hline
 \end{tabular}
@@
 
-\eat{
-\textbf{Number of patterns under different parameters}: We first 
-analyze the number of patterns exist in each dataset under different conditions.
-The results are presented in Figures~\ref{exp:patterns_vary}.
-As expected, the number of patterns differs under in different scenarios.
-Larger $M$, $L$, $K$ imply smaller number of patterns, because lesser patterns are able to meet stricter $M$, $L$, $K$ constraints.
-In contrast, larger $G$ implies larger number of patterns.
-This is because larger gaps relaxes the pattern constraint.
-Two interesting observations are made on $L$ and $G$.
-First, as $L$ increases from $10$ to $20$, the number of patterns drops quickly (50\% less).
-Second, opposed to $L$'s trend, as $G$ reaches to $30$ from $25$, the number of patterns bursts (near 50\% more).
-The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent.
-With GCMP, we can discover these patterns by properly adjusting $L$ and $G$s.
-
-\begin{figure}[h]
-\centering
- 	 \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
-        \caption{Number of patterns vary $M$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
-        \caption{Number of patterns vary $K$}
-    \end{subfigure}  
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
-        \caption{Number of patterns vary $L$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
-        \caption{Number of patterns vary $G$}
-    \end{subfigure}    
-\caption{Number of patterns discovered from real datasets}
-\label{exp:patterns_vary}
-\end{figure}
-}
-
-\eat{
-\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study.
-TRPM and SPARE are implement as described in Section 4 and 5.
-SPARE-LB extends SPARE by appending an additional load balance stage to the map phase.
-When the mappers complete, SPARE-LB collects the size of stars from all mappers. 
-Then a best-fit strategy is applied for task allocation. In best-fit, 
-tasks are assigned in decreasing order of their sizes, and the most costly
-unassigned task is allocated to the current mostly empty reducer. 
-In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The remaining
-parts of SPARE-LB are identical to SPARE.
-}
-
 \subsection{Performance Evaluation}
-\eat{
-Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
-see their performances under different settings.
-We run the three algorithms using all three datasets 
-and report their overall performances in Figures~\ref{exp:performance_vary}.
-In brief, all of the three algorithms 
-are able to handle the large-scaled real
-datasets. However, SPARE algorithms are obviously more efficient than TRPM. 
-In the case when $G$ is large (i.e., $G=30$), 
-TRMP takes near three hours for Taxi dataset, which is 15 times slower than SPARE algorithms. Besides, SPARE-LB is consistently more efficient than SPARE, with an average of 20\% improvements.
-Another general observation
-is that all of the three algorithms run slower in the Taxi dataset as compared to
-other two datasets. This is because Taxi dataset contains
-the most number of temporal data points, which is around 7 times of Shopping
-dataset and 5 times of geolife dataset.
- In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.
-}
 \begin{figure*}[t]
@@
 \end{figure*}
-%\subsubsection{Effects of pattern parameters M,L,K,G}
 \textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
@@
 
-%Second, when $K$ is very small (i.e, $K=0.XXX|T|$), TRPM could outperform SPARE because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE.
-As a result, TRPM wins 10\% in Geolife dataset.
-However, by leveraging the load balancing, SPARE-LB is still faster than TRPM.
-
 \textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) present the performances with varying $L$.
@@
 We also observe that there is a significant performance improvement for TPRM when $L$ increases from $10$ to $20$ and later the running time drops smoothly.
-This is because $\eta$ is proportional to $O(L + 1/L)$. When $L$ is small (i.e., from $10$ to $20$),
-$\eta$ decreases quickly (i.e., 30\%). As $L$ further increases (e.g, from $20$ to $30$),
-$\eta$ decreases steadily (e.g, 15\%).
-%CAN YOU EXPLAIN THIS FROM THE RELATIONSHIP between $\eta$ and $L$.
-
-\eat{
-An interesting observation is that $L$
-provides good pruning power from $10$ to $20$ for both TRPM and SPARE based algorithms.
-The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.
-
- As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms. This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.
-}
+This is because $\eta$ is proportional to $O(K*G/L+L)$. When $L$ is small (i.e., from $10$ to $20$),
+$\eta$ decreases drastically. As $L$ further grows, $\eta$ varies less significantly.
 
@@
 
-\eat{
-We can see that both TRPM and SPARE run slower.
-The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted.
-We observe that there is a burst in performance of TRPM when $G$ reach to $30$.
-The major reason is that when $G$ becomes to 30, the number of valid patterns almost doubles as shown in Figure~\ref{exp:patterns_vary} (d).
-This indicate that during TRPM's line sweep, very few patterns can be pruned, making the candidate set grows exponentially.
-Similarly, SPARE algorithms are also affected by the increase of $G$.
-However we do not observe such a burst for SPARE.
-The reason is bi-folded.
-First, SPARE can utilize $K$, $L$ to retain the power of pruning.
-Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
-}
 \textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary_OT} (a)(b)(c) present 
-the performances wrt. increasing number of total objects. The x-axis are the ratio
-of objects sampled from the corresponding datasets. We can see that the performance of
-both TRPM and SPARE decreases linearly to the the number of total objects. This
-is reasonable since larger $O_r$ results in more clusters per snapshot, which affects
-the line-sweep in TRPM and the aggregate graph in SPARE. However in all cases, SPARE
-consistently outperforms TRPM.
+the performances with increasing number of moving objects.
+Both TRPM and SPARE take longer time to find patterns in a growing database.
+We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.
 
 \textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary_OT} (d)(e)(f) present 
-the performances wrt. increasing number of total snapshots.  The x-axis represents the size of
-snapshots sampled from the corresponding datasets. We again observe the linear decrease of
-the performances wrt. the number of snapshots. In all cases, SPARE is faster than
-TRPM. We further observe that as $T_r$ grows, the gaps between SPARE and TRPM tends
-to be larger, this is because larger $T_r$ results larger partition size, and more 
-snapshots needs to be swept in TRPM.
+the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.
 
@@
 \subsection{Analysis of SPARE framework}
-In this part, we extensively evaluate the advantage brought by 
+In this part, we extensively evaluate the advantage brought by the
 sequence simplification and load balancing techniques.
@@
 \subsubsection{Power of sequence simplification}
-One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
-As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
-to prune false candidates. To study the power of sequence simplification,
-we collect the following two statistics: (1) the number of pairs that
-are shuffled to reducers and (2) the number of pairs that
-are fed to the Apirori enumeration. The difference of the two quantities
-the the pairs that are pruned by the sequence simplification.
-%
-%we collect the total number of pairs that are pruned before apriori enumeration.
-%In particular, we compare the number of 
-%The number of pairs prior to pruning is counted in the load balance stage, while
-%the number of pairs after pruning is counted in the Apriori stage.
-The
-statistics are shown in Table~\ref{tbl:pruning} under default parameters.
-The result states that the \emph{sequence simplification} is a very powerful pruning technique.
-It cuts off near 90\% of the initial pairs, which significantly reduces the costs
-of later enumerations. This confirms the necessity and usefulness of design such a technique.
+To study the power of sequence simplification,
+we collect two types of statistics: (1) the number of pairs that
+are shuffled to the reducers and (2) the number of pairs that
+are fed to the Apirori enumeration. The difference between these two values is the number of size-$2$ candidates pruned by the sequence simplification.
+The results in Table~\ref{tbl:pruning} show that the \emph{sequence simplification} is very powerful and eliminates nearly 90 percent of the object pairs, which significantly reduces the overhead of subsequent Apriori enumerator.
 
 \begin{table}[h]
+\centering
 \begin{tabular}{|l|c|c|c|}
 \hline 
-\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
+\textbf{Data Set} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
 \hline 
@@
 \end{tabular}
-%
-%\begin{tabular}{|c|c|c|c|}
-%\hline 
-%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
-%\hline 
-%Shopping & 878,309 & 76,672 &  91.2\%\\ 
-%\hline 
-%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
-%\hline 
-%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
-%\hline 
-%\end{tabular} 
+
 \caption{Pruning power of SPARE}
@@
 \centering
-	\begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
-        \caption{Decomposed running time}
-    \end{subfigure}
- 	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
-        \caption{Workload in Shopping}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
-        \caption{Workload in Geolife}
-    \end{subfigure}  
-    \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
-        \caption{Workload in Taxi}
-    \end{subfigure}
-\caption{Load balance of SPARE and SPARE-LB}
+	  \includegraphics[width=0.3\textwidth]{/exp/spare/detail.eps}
+    \caption{Break-down cost of SPARE and SPARE-RD}
     \label{exp:wl}
+%	\begin{subfigure}[b]{0.3\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
+%        \caption{Decomposed running time}
+%    \end{subfigure}
+%    
+% 	\begin{subfigure}[b]{0.22\textwidth}
+%       \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
+%       \caption{Workload in Shopping}
+%   \end{subfigure}
+%    \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
+%        \caption{Workload in Geolife}
+%    \end{subfigure}  
+%    \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
+%        \caption{Workload in Taxi}
+%    \end{subfigure}
+%\caption{Load balance of SPARE and SPARE-LB}
 \end{figure}
 
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
+                         & Straggler        & STD        & Straggler       & STD      \\ \hline
+Shopping                 & 295              & 41         & 237             & 21       \\ \hline
+GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
+Taxi                     & 681              & 147        & 580             & 96       \\ \hline
+\end{tabular}
+  \caption{Statistics of execution time among executors,units are in seconds.}
+  \label{tbl:strags}
+\end{table}
+
 \subsubsection{Load Balance}
-To study why SPARE is more efficient,
-we analyze the running time of  SPARE
-each map-reduce stage.  To compare with, we use
-the SPARE-RD which is SPARE with random task allocation as a baseline.
-The detail anatomy is shown in Figure~\ref{exp:wl}(a).
-We can see that on all three datasets, the reduce phase for both SPARE and SPARE-RD takes the majority time. The overall improvement of SPARE is around 10-13\%
-under the default settings. We observe that the map and shuffle time
-of SPARE and SPARE-RD are identical, where SPARE spends a very small portion of extra time (4\% of the total time)
-in applying the best-fit strategy. The time spent is worthwhile
-as in the reduce phase SPARE saves around 20\% of the time.
+To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method.
+In best-fit, the largest unassigned star is allocated to the currently most empty reducers.
+Figure~\ref{exp:wl}(a) shows the break-down costs in the map-reduce stages for SPARE and SPARE-RD.
+We observe that the map and shuffle time of SPARE and SPARE-RD are identical.
+The difference is that SPARE spends additional time cost to make an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
+We also report the cost of straggler, i.e., the longest job, in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
 
-We then look at the workload distribution of SPARE and SPARE-RD on real datasets. 
-We collect the statistics from executors
-and report their reduce times in Figure~\ref{exp:wl}. 
-The figures show that SPARE is able to provide a more balanced 
-task allocation in all three cases. Since SPARE-RD takes random assignment
-of stars, it is likely to assign many large stars to the same executor. 
-In general cases, SPARE is recommended as 
-it offers more efficiency while takes only a small extra time for planning.
-
-\eat{
-\subsubsection{Scalability}
-We then study the scalability of SPARE-LB from two aspects. 
-First, we fix the computing power and vary the size of dataset.
-We perform a random sample from the tree dataset and the results of SPARE-LB are shown in Figures~\ref{fig:scalability-wl}.
-As the figures show, SPARE-LB grows almost linearly wrt $|O|$ and $|T|$.
-This suggests a good scalability.
-Note that, as shown in Figure~\ref{fig:related_work_scalability}, a centralized algorithm runs more than a hundred times slower than SPARE for the same scale of data.
-This confirms the superiority of our parallel
-
-\begin{figure}[h]
-\begin{subfigure}[b]{0.22\textwidth}
-\centering
-    \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-O.eps}
-        \caption{Scalability vary $|O|$}
-    \end{subfigure}
- 	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-T.eps}
-        \caption{Scalability vary $|T|$}
-    \end{subfigure}
- \caption{Scalability of SPARE-LB wrt. different data sizes}
- \label{fig:scalability-wl}
-\end{figure}
-
-Second, we fix the work load and vary the number of executors.
-The result are presented in Figure~\ref{exp:scalability}.
-We can see that SPARE achieves good scalability under all three cases. 
-For instance, for Taxi dataset, when the executors rises from 10 to 50, 
-the performance improves 4.8 times which is almost linear to the increase of executors.
-Such pattern also holds for the other two datasets.
-The reason for the good scalablity is that SPARE partitions the trajectories by objects and partitions are perfectly independent.
-Therefore, when the number of executors $N << |O|$, SPARE can always speed up by adding more executors.
-\begin{figure}[h]
-\centering
-   \includegraphics[width=0.3\textwidth]{/exp/spare/scalability.eps}
-\caption{Scalability of SPARE-LB vary. $N$.}
-\label{exp:scalability}
-\end{figure}
-}
-
-\subsection{Scalability and Comparison with Existing Solutions}
-We then study the scalability of our schemes.
-Since existing solutions run on a single machine, it is interesting to compare their
-performances. We choose \emph{platoon} as the comparing scheme as it is
-generic and more efficient than \emph{swarm} and \emph{group}
-The results are presented in Figure~\ref{exp:scalability}. There are two observations.
-First, the centralized scheme (e.g. platoon) are not suitable for discover
-patterns in large-scale trajectories. It takes near 16 hours for discovering \emph{platoon}s
-in Taxi data. As a comparison, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup.
-This is because even there is only 1 machine, our TRPM and SPARE is still able to leverage
-the 15 cores in the machine for parallelism. Second, we see that both TRPM and SPARE
-demonstrate good scalability wrt. $N$. As the number of machines increases from 1 to 11 (i.e., 11 times),
-both TRPM and SPARE achieves near 11 times speedup. Note that SPARE at most achieves 94 times
-speedup as compared to \emph{platoon} using all 11 machines.
+\subsection{Parallelism}
+Finally, we examine the parallelism of our proposed frameworks in both multi-core and multi-node environments.
+First, we use single-node mode and examine the performance with multi-cores.
+We also compare it with the  state-of-the-art solutions for swarm and platoon patterns since they were designed  to run in a centralized sever.
+Second, we examine the pattern detection time when more and more computing resources (number of machines) are available.
+The results are reported in Figure~\ref{exp:scalability}.
+First, the centralized schemes are not suitable to discover patterns in large-scale trajectory databases.
+It takes nearly $16$ hours to detect \emph{platoon}s in Taxi data in a single machine.
+In contrast, when utilizing the multi-core environment, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively.
+Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of machines available.
+The running time almost decreases linearly as more machines are used.
+When there are $11$ nodes in the cluster, the performance of SPARE is $94$ times better than the state-of-the-art \emph{platoon} detector in a centralized server.
 
@@
     \end{subfigure}
- \caption{Scalability of SPARE and TRPM wrt. $N$}
+ \caption{Comparisons among TRMP, SPARE and Platoon}
  \label{exp:scalability}

### 2016-06-26 sec7_conclusion.tex
A complete version

--- 2016-06-25 sec7_conclusion.tex
@@
-\section{Conclusion and Future Work}
+\section{Conclusions and Future Work}
 \label{sec:concl}
+In this paper, we proposed a generalized co-movement pattern to unify those proposed in the past literature.
+We also devised two types of parallel frameworks in Spark that can scale to support pattern detection in a trajectory database with hundreds of millions of points.
+The efficiency and scalability were verified by extensive experiments on three real datasets.
+In the future work, we are interested to examine co-movement pattern detection in streaming data for real-time monitoring.
+How to extend the current parallel framework to support other types of advanced patterns is also of interest.

### 2016-06-28 appendix.tex
Need to add three more experiments
Three more charts
A complete version
An almost complete version
Near Done

@@
 
-\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
+\subsection{Proof of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
+\label{apx:thm2proof}
 \begin{proof}
-We formalize optimization of $\Gamma$ using a linear algebra model as follows:  
+$\Gamma$ can be formalized in a linear algebra way:
 Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
-A vertex order is in fact a permutation of $J$. Therefore,
-the adjacent matrices of any reordered graphs can be represented as $PJP^T$
-where $P \in \mathbb{P}$ is a 
-\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
-Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+Since a vertex order is a permutation of $J$, the adjacent matrices 
+of any reordered graphs can be represented as $PJP^T$
+where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
+In star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
 then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
@@
 Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
-vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
+vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
 denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
-as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
-$\Gamma^*$ can then be formulated as follows:
+as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders, that is
+
 \begin{equation}
@@
 
-Let $B*$ be the assignment matrix wrt the optimal vertex order.
+Let $B^*$ be the assignment matrix wrt. the optimal vertex order.
 Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
 $\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
-Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
-edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
-let $d_i$ denote the degree of vertex $i$, 
-then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
-vertexes does not affect the average degree.
-Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
+Next, for a ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
+edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
+Let $d_i$ denote the degree of vertex $i$, since ordering of vertex does not
+affect the average degree,
+then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
+entries in $B$ can be written as :
+
 \begin{equation*}
@@
 \end{equation*}
-There are two observations made. First, since $e_{i,j}$s are independent,
+
+There are two observations. First, since $e_{i,j}$s are independent,
 $b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
 $E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
-
-By definition, $c_i = \Sigma_{1\leq j \leq n} b_{i,j}$, 
-is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
+As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s). By linearity 
+of expectations,
 we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
@@
 $t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
+
 \begin{equation*}
 \begin{split}
-	Pr(c_i \geq \mu + t) 
-						&\leq \exp(\frac{-2t^2}{n}) \\
-						&= \exp(-2\log n) = n^{-2}
+	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) \\
+	 & = \exp(-2\log n) = n^{-2}
 \end{split}
@@
 
-The first step is due to the fact that all $b_{i,j}$ are bounded in the range of [0,1]. 
-Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
-$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
+The first step holds since all $b_{i,j}$ are 0-1 variables. 
+Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
+$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
 \begin{equation*}
@@
 		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\ 
-		& = n^{-1} = 1/n
+		&= n^{-1} = 1/n
 \end{split}
@@
 \end{equation*}
-This indicates that, the probability of $(\Gamma-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
-With the fact that $\Gamma^* \geq d/2$, we conclude that
-with probability greater than $(1-1/n)$, 
-the difference between $\Gamma$ and $\Gamma^*$ is less than $O(\sqrt{n\log n})$.
-When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$), we may use
-the Chernoff Bound instead of Hoeffding's Inequality to derive a tighter bound of 
-$O(\sqrt{\log n}) $ with the similar reasoning.
+This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
+Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
+the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
+When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
+the Chernoff Bound can be used to derive a tighter bound of 
+$O(\sqrt{\log n}) $ following the similar reasoning.
 \end{proof}
@@
 \subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
+\label{apx:spm_correct}
 \begin{proof}
@@
 In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
-%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated.
-Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$.
-This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking.
-Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
-%
-%\begin{theorem}[Forward Closure Checking]
-%\label{THM:SPM_FCC}
-%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
-%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
-%and directly output $FC_i$.
-%\end{theorem}
-
-%
-%If $P$ is a valid pattern in original trajectories, 
-%let $s$ be the object with smallest ID in $P.O$. 
-%Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
-%It follows that all object $o \in P.O$ are in $Sr_s$. 
-%Furthermore, every timestamp in $P.T$ is included
-%in $Sr_s$.
-Therefore, $P$ is a valid pattern in $Sr_s$.
-This ensures the \emph{completeness}.
-For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$.
-This ensure the \emph{soundness}.
 \end{proof}
-
-%\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
-%\begin{proof}
-%We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
-%let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
-%(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
-%then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
-%It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
-%\end{proof}

### 2016-06-28 sec1_introduction.tex
A complete version
An almost complete version
Near Done

@@
 
-\begin{table} \scriptsize
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline 
-Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
-\hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
-\hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
-\hline 
-swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
-\hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
-\hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
-\hline 
-\end{tabular} 
-\caption{Constraints and complexity of co-movement patterns.
-The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
-\label{tbl:existing_co_patterns}
-\end{table}
-
 \begin{figure}[h]
 \centering
-\includegraphics[width=0.46\textwidth]{related_work.eps}
+\includegraphics[width=0.4\textwidth]{related_work.eps}
 \caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots.
@@
 
-%As can be seen, there are various co-movement patterns requested by different 
-%applications and it is cumbersome to design a tailored solution for each type. 
-%As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns. However, we 
-%further observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which lead to noisy results and unnecessary computations.
-We name this scenario as \emph{loose-connection} anomaly.
-To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern
-%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
-%making the co-moving behavior very loose.
-%In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
-%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.
-Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) are able to directly avoid such an anomaly.
-
-%In addition, existing pattern definitions are not expressive enough and may miss 
-%interesting patterns or return noisy results. We summarize 
-%the two scenarios as \emph{missing-pattern} anomaly
-%and \emph{loose-connection} anomaly.
-%A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
-%As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
-%neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
-%$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
-%the traffic control or the clustering inaccuracy at time $4$. On the other hand,
-%the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
-%the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
-%the two objects $o_1, o_2$ form a \emph{platoon} pattern 
-%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
-%making the co-moving behavior very weak.
-%In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
-%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
-%It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.
-
 \begin{figure}[h]
 \center
-\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
+\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
 \caption{\emph{Loose-connection} anomaly.
 Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
-% in \emph{platoon}, \emph{swarm} and \emph{group} results.
 }
@@
 
-%In current literature,
-%users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
-%
-%
-% we summarize two anomalies 
-%The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
-%Figure~\ref{fig:platoon_weakpoint} (a).  As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
-%the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
-%be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
-%\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
-%as \emph{loose-connection}~\cite{li2015platoon} anomaly. 
-%
-%
-%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
-%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
-
-%For instance, PUT THE FIGURE AND EXPLANATION HERE.
-
-%\begin{figure}[h]
-%\center
-%\includegraphics[width=0.35\textwidth]{rw_perf_O.eps}
-%\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
-%in \emph{flock} and \emph{convoy}.
-When $K=4$, none of the two patterns can be discovered.
-(b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}.
-The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
-%\label{fig:platoon_weakpoint}
-%\end{figure}
-
+\begin{table} \scriptsize
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline 
+Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
+\hline 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
+\hline 
+convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
+\hline 
+swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
+\hline 
+group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
+\hline 
+platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
+\hline 
+\end{tabular} 
+\caption{Constraints and complexity of co-movement patterns.
+The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
+\label{tbl:existing_co_patterns}
+\end{table}
 The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable.
@@
 
-%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
-%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
-%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
-%Therefore, none of them can handle millions of trajectories efficiently. 
-%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
 \begin{figure}[h]
@@
 
-%Therefore, users are 
-%still able to exclude non-consecutive patterns 
-%or include loosely-connected patterns when they feel necessary.
-
-%We introduce the gap parameter $G$,
-%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
-%To cope with both of the two anomalies, we propose 
-%by introducing the gap parameter $G$,
-
-%By so doing, we gain a fine-grained control s, which As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
-%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
-%
-
 Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue.
@@
 to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
-%
-%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
-%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.
 
@@
 An advanced solution named
-\emph{star partition and mining} is presented in Section~\ref{sec:spm}.
+\emph{Star Partition and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.
 Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system.

### 2016-06-28 sec6_experiment.tex
An almost complete version
Near Done

@@
 \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
@@
     \end{subfigure}
-       \begin{subfigure}[b]{0.23\textwidth}
+       \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
@@
     \end{subfigure}
+	\begin{subfigure}[b]{0.16\textwidth}
+	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
+        \caption{Shopping vary $O_r$}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.16\textwidth}
+	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
+        \caption{Shopping vary $T_r$}
+    \end{subfigure}
 
-	\begin{subfigure}[b]{0.23\textwidth}
+	\begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
@@
     \end{subfigure}
-       \begin{subfigure}[b]{0.23\textwidth}
+       \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
@@
     \end{subfigure}       
+ 	 \begin{subfigure}[b]{0.16\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
+        \caption{Geolife vary $O_r$}
+    \end{subfigure}
+ 	\begin{subfigure}[b]{0.16\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
+        \caption{Geolife vary $T_r$}
+    \end{subfigure}
 
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
@@
     \end{subfigure}
-       \begin{subfigure}[b]{0.23\textwidth}
+       \begin{subfigure}[b]{0.16\textwidth}
         \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
@@
     \end{subfigure}   
+	 \begin{subfigure}[b]{0.16\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
+        \caption{Taxi vary $O_r$}
+    \end{subfigure}
+    	 \begin{subfigure}[b]{0.16\textwidth}
+        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
+        \caption{Taxi vary $T_r$}
+    \end{subfigure}
+
 \caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
@@
 \end{figure*}
-\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
+\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(g),(m)
 present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
@@
 
-\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(f),(j).
+\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(h),(n).
 SPARE tends to run faster, whereas the performance of TRPM degrades dramatically.
@@
 
-\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) present the performances with varying $L$.
+\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c),(i),(o) present the performances with varying $L$.
 When $L=10$, SPARE can outperform TRPM by around $10$ times.
@@
 
-\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) present the performances with increasing $G$.
+\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d),(j),(p) present the performances with increasing $G$.
 TRPM is rather sensitive to $G$.
@@
 
-\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary_OT} (a)(b)(c) present 
+\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present 
 the performances with increasing number of moving objects.
@@
 
-\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary_OT} (d)(e)(f) present 
+\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary} (f),(l),(r) present 
 the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.
 
-\begin{figure}[h]
-\centering
-	\begin{subfigure}[b]{0.22\textwidth}
-	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
-        \caption{Shopping vary $O_r$}
-    \end{subfigure}
- 	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
-        \caption{Geolife vary $O_r$}
-    \end{subfigure}
-    	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
-        \caption{Taxi vary $O_r$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.22\textwidth}
-	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
-        \caption{Shopping vary $T_r$}
-    \end{subfigure}
- 	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
-        \caption{Geolife vary $T_r$}
-    \end{subfigure}
-    	 \begin{subfigure}[b]{0.22\textwidth}
-        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
-        \caption{Taxi vary $T_r$}
-    \end{subfigure}
- \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
- \label{exp:performance_vary_OT}
-\end{figure}
+%\begin{figure}[h]
+%\centering
+%	\begin{subfigure}[b]{0.22\textwidth}
+%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
+%        \caption{Shopping vary $O_r$}
+%    \end{subfigure}
+% 	 \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
+%        \caption{Geolife vary $O_r$}
+%    \end{subfigure}
+%    	 \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
+%        \caption{Taxi vary $O_r$}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.22\textwidth}
+%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
+%        \caption{Shopping vary $T_r$}
+%    \end{subfigure}
+% 	 \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
+%        \caption{Geolife vary $T_r$}
+%    \end{subfigure}
+%    	 \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
+%        \caption{Taxi vary $T_r$}
+%    \end{subfigure}
+% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
+% \label{exp:performance_vary_OT}
+%\end{figure}
 
@@
 \begin{table}[h]
-\centering
-\begin{tabular}{|l|l|l|l|l|}
+\centering \small
+\begin{tabular}{|l|c|c|c|c|}
 \hline
 \multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
-                         & Straggler        & STD        & Straggler       & STD      \\ \hline
+                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
 Shopping                 & 295              & 41         & 237             & 21       \\ \hline
@@
 The difference is that SPARE spends additional time cost to make an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
-We also report the cost of straggler, i.e., the longest job, in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
+Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
 
@@
 \centering
-\begin{subfigure}[b]{0.32\textwidth}
+\begin{subfigure}[b]{0.31\textwidth}
     \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
@@
     \end{subfigure}
- 	 \begin{subfigure}[b]{0.32\textwidth}
+ 	 \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
@@
     \end{subfigure}
-    	 \begin{subfigure}[b]{0.32\textwidth}
+    	 \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}

### 2016-06-28 sec4_baseline.tex
Prof Tan's Comments
Comments on sec4

@@
 \caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
-(a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle, which uses TRPM to detect GCMP in parallel.}
+(a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot;  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
 \label{fig:trm}
@@
 The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
-There are two cycles of map-reduce jobs connected in a pipeline manner.
-The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining.
-In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase.
+There are two stages of map-reduce jobs connected in a pipeline manner.
+The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase.
+In particular, for the first stage, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase.
 Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.
 
-Our focus in this paper is the second map-reduce cycle of parallel mining, which essentially consists of two key questions to solve.
-The first is how to employ effective data partitioning such that the mining can be conducted independently; and the second is how to efficiently mine the valid patterns within each partition.
+Our focus in this paper is on the second map-reduce stage of parallel mining, which essentially addresses two key challenges.
+The first is to ensure effective data partitioning such that the mining can be conducted independently; and the second is to efficiently mine the valid patterns within each partition.
 
@@
 into disjoint partitions because a GCMP pattern requires $L$-consecutiveness 
-and the corresponding segments may cross multiple partitions. 
+and the corresponding segments may span multiple partitions. 
 Our strategy is to use data replication to enable parallel mining. 
@@
 certain cross-partition patterns may be missed. 
-If $\eta$ is set too large, expensive network communication and 
+If $\eta$ is too large, expensive network communication and 
 CPU processing costs would be incurred in the map and reduce phases respectively. Our objective is to find an $\eta$ that is not large but can guarantee correctness.
@@
 In our implementation, we set $\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$.
-Intuitively, $K$ timestamps generates at most $\lceil \frac{K}{L} \rceil - 1$ gaps as the length of each $L$-consecutive segment is at least $L$.
+Intuitively, with $K$ timestamps, at most $\lceil \frac{K}{L} \rceil - 1$ gaps may be generated as the length of each $L$-consecutive segment is at least $L$.
 Since the gap size is at most $G-1$, $(\lceil \frac{K}{L} \rceil - 1)*(G-1)$ is the upper bound of timestamps allocated to gaps.
-The remaining part $K+L-1$ is used to capture the upper bound allocated for the $L$-consecutive segments.
+The remaining part of the expression, $K+L-1$, is used to capture the upper bound allocated for the $L$-consecutive segments.
 We formally prove that $\eta$ can guarantee correctness.
@@
 
-Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
+Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
 form a partition.
@@
 Our next task is to design an efficient pattern mining strategy within each partition.
-We propose a line sweep algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and employ effective candidate pattern enumeration.
+Our solution includes a line sweeping algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and an effective candidate pattern enumeration mechanism.
 
@@
 
-After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
-It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
-early remove false candidates from $C$.
+After sweeping all the snapshots, all the valid patterns are stored in $C$ (Line~\ref{code:ls-valid-check}). 
+It is worth noting that $C$ continues to grow during the whole sweeping process.
+We can use three pruning rules to remove false candidates from $C$ early.
 Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered.
-Therefore, those patterns that does not appear in the $S_t$ are false candidates.
-Particularly, our
+Therefore, those patterns that do not appear in the $S_t$ are false candidates.
+In particular, our
 three pruning rules are as follows:
-First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
+First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
 candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
 Third, candidates in $C$ with the size of first segment smaller than $L$
-are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.
+are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ can be significantly reduced.
 
 The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}.
-We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
+We illustrate the workflow of the TRPM method using Figure~\ref{fig:trm} (c) and (d) with pattern
 parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
 as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
-in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
-into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
-method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
-during sweeping snapshot $S_i$.
+in Figure~\ref{fig:trm}(c), every $5$ consecutive snapshots are combined 
+into a partition in the map phase. In Figure~\ref{fig:trm}(d), a line sweep
+method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
 Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
@@
 \State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
-\State {---Map Phase---}
+\State {\textit{---Map Phase---}}
 \label{code:trm-map-start}
@@
 \label{code:trm-map-end}
-\State {---Partition and Shuffle Phase---}
+\State {\textit{---Partition and Shuffle Phase---}}
 \label{code:trm-par-start}
@@
 \label{code:trm-par-end}
-\State {---Reduce Phase---}
+\State {\textit{---Reduce Phase---}}
 \label{code:trm-red-start}

### 2016-06-29 sec1_introduction.tex
With Prof Tan's Comments
With prof's comment

@@
 and the group is normally determined by spatial proximity. 
-A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
+A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
 and driven by different mining applications, there are a bunch of variants 
@@
 
-Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving pattern s 
+Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
 with different constraints in the attributes of clustering in spatial proximity,
@@
 The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots.
-In each snapshot, we treat the clustering methods as a black-box and assume that they generate the same clusters.
+In each snapshot, we treat the clustering method as a black-box and assume that they generate the same clusters.
 Objects in proximity are grouped in the dotted circles.
@@
 \caption{Constraints and complexity of co-movement patterns.
-The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
+The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the number of descritized timestamps and $M$ is the minimum cluster cardinality.
+}
 \label{tbl:existing_co_patterns}
@@
             \includegraphics[width=\textwidth]{rw_perf_O.eps}
-		\subcaption{$1k$ timestamps}
+		\subcaption{$1k$ timestamps vary $O$} 
     \label{fig:fig1}
@@
             \includegraphics[width=\textwidth]{rw_perf_T.eps}
-         \subcaption{$1k$ objects}
+         \subcaption{$1k$ objects vary $T$}
     \label{fig:fig2}

### 2016-06-29 sec5_spm.tex
An almost complete version
Near Done
With Prof Tan's Comments
With prof's comment

@@
 \caption{Star partition and ApRiori Enumerator (SPARE).
-(a) Aggregate graph from Figure 1.
+(a) Aggregated graph from Figure 1.
 (b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
@@
 \label{sec:spm}
-The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks.
-First, the replication relies on $\eta$ which could be large.
+The aforementioned TRPM scheme replicates partitions based on the temporal dimension which suffers from two drawbacks.
+First, the replication factor is $\eta$ which can be large.
 Second, the same valid pattern may be discovered from different partitions which results in redundant works.
-To resolve the limitations caused by the replicate partitioning, 
+To resolve these limitations,
 we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
-to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
+to replace the second stage of map-reduce jobs in Figure~\ref{fig:trm}. 
 Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
@@
 An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
-is shown in Figure~\ref{fig:star_partition} (a). 
+is shown in Figure~\ref{fig:star_partition}(a). 
 As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
@@
 With the global ordering, we can guarantee that each edge is contained in a unique star partition.
-Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition} (a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition} (b).
+Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition}(a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition}(b).
 These stars are emitted from mappers to different reducers.
@@
 balance among the map-reduce jobs.
-The job incurring performance bottleneck is often known as \emph{straggler}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}.
+The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}.
 In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition.
 We use $\Gamma$ to denote the size of a partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}.
-It is straightforward that a star partitioning with small $\Gamma$ is preferred.
+Clearly, a star partitioning with small $\Gamma$ is preferred.
 For example, Figure~\ref{fig:star-alt} gives two star partitioning results under
@@
 \centering
-\includegraphics[width=0.5\textwidth]{star-alt.eps}
+\includegraphics[width=0.45\textwidth]{star-alt.eps}
 \caption{Examples of star partitioning with different vertex ordering.}
@@
 \label{THM:SPM_LB}
-Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering.
+Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering.
 With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
@@
 \subsubsection{Monotonicity}
-To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
+To ensure monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
 For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
@@
 If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$.
-Both cases lead to contradiction.
+Both cases lead to a contradiction.
 \end{proof}
@@
 
-With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
+With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} concept based on the simplified
 sequences to facilitate the pruning in the Apriori algorithm.
@@
 It is obvious that $P_2.T \subseteq P.T$.
-Based on the Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected.
+Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected.
 (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive.
@@
 	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
-		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
-		\State break;
+		\State{output $\langle O_u, T_u\rangle$, \textbf{break}} \label{code:fc-checking}
 	\EndIf \label{code:fc-checking-end}
@@
 Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation.
-In best-fit strategy, the most costly unallocated star is assigned to the most empty reducers, where we use the edges in the star as a cost estimation.
+Under the best-fit strategy, the most costly unallocated star is assigned to the most lightly loaded reducers, where we use the edges in the star as a cost estimation.
  Each reducer is an Apriori Enumerator.
@@
 \Require list of $\langle t, S_t \rangle$ pairs
-\State {---Map phase---}
+\State {\textit{---Map phase---}}
 \label{code:spm-map-start}
@@
 
-\State {---Partition and Shuffle phase---}
+\State {\textit{---Partition and Shuffle phase---}}
 \label{code:spm-shuffle-start}
@@
 
-\State {---Reduce phase---}
+\State {\textit{---Reduce phase---}}
 \label{code:spm-reduce-start}
@@
 
-Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness.
+Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness.
 In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
@@
 %that no replication is required 
-in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
+in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
 \begin{theorem}

### 2016-06-29 sec6_experiment.tex
With Prof Tan's Comments
With prof's comment

@@
 \textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster.
-We pick one machine as the Yarn's master node, and the remainings reserve one core and $2$GB memory for Yarn processes.
+We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes.
 We deploy our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
 To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
-In Spark, one of the $55$ executor is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
+In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
 All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
@@
 \textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(g),(m)
-present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
+present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over the TRPM framework, with 
+a performance gain by a factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
 $7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.
@@
 This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$.
-However, the line sweep algorithm in TRPM does not utilize such property for pruning.
-It takes longer time because more replication data has to be handled in each partition.
+However, the line sweeping algorithm in TRPM does not utilize such property for pruning.
+It takes longer time because more replicated data has to be handled in each partition.
 
@@
 This is because $\eta$ is proportional to $O(K*G/L+L)$. When $L$ is small (i.e., from $10$ to $20$),
-$\eta$ decreases drastically. As $L$ further grows, $\eta$ varies less significantly.
+$\eta$ decreases drastically. As $L$ increases, $\eta$ varies less significantly.
 
@@
 TRPM is rather sensitive to $G$.
-When $G$ is relaxed to larger values, more valid patterns would generate.
+When $G$ is relaxed to larger values, more valid patterns would be generated.
 TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$.
@@
 the performances with increasing number of moving objects.
-Both TRPM and SPARE take longer time to find patterns in a growing database.
+Both TRPM and SPARE take longer time to find patterns in a larger database.
 We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.
@@
 	  \includegraphics[width=0.3\textwidth]{/exp/spare/detail.eps}
-    \caption{Break-down cost of SPARE and SPARE-RD}
+    \caption{Breakdown of cost of SPARE and SPARE-RD}
     \label{exp:wl}
@@
 \end{tabular}
-  \caption{Statistics of execution time among executors,units are in seconds.}
+  \caption{Statistics of execution time among executors (in seconds)}
   \label{tbl:strags}
@@
 To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method.
-In best-fit, the largest unassigned star is allocated to the currently most empty reducers.
-Figure~\ref{exp:wl}(a) shows the break-down costs in the map-reduce stages for SPARE and SPARE-RD.
+In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
+Figure~\ref{exp:wl}(a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD.
 We observe that the map and shuffle time of SPARE and SPARE-RD are identical.
-The difference is that SPARE spends additional time cost to make an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
+The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
 We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
@@
 
-\subsection{Parallelism}
-Finally, we examine the parallelism of our proposed frameworks in both multi-core and multi-node environments.
+\subsection{Scalability}
+Finally, we examine the scalability of our proposed frameworks in two contexts.
 First, we use single-node mode and examine the performance with multi-cores.
-We also compare it with the  state-of-the-art solutions for swarm and platoon patterns since they were designed  to run in a centralized sever.
-Second, we examine the pattern detection time when more and more computing resources (number of machines) are available.
+We also compare it with the  state-of-the-art solutions for swarm and platoon patterns since they were designed  to run in a centralized server.
+Second, we examine the pattern detection time with increasing computing resources (number of machines).
 The results are reported in Figure~\ref{exp:scalability}.
 First, the centralized schemes are not suitable to discover patterns in large-scale trajectory databases.
-It takes nearly $16$ hours to detect \emph{platoon}s in Taxi data in a single machine.
+It takes nearly $16$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine.
 In contrast, when utilizing the multi-core environment, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively.
-Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of machines available.
+Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available.
 The running time almost decreases linearly as more machines are used.

### 2016-06-29 sec3_definitions.tex
Several minor changes
Needs to proofread more

@@
 Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive.
-On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$.
-It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is 2 (i.e., 5-3=2).
+On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring timestamps is $2$.
+It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is $2$ (i.e., $5-3=2$).
 
@@
 \begin{definition}[General Co-Movement Pattern]
-A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is L-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
+A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is $L$-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
 \end{definition}
 There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
-express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
+express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
 In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern.
@@
 We currently expose both disc-region based clustering and DBSCAN as options to the users.
-In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMP from large-scale trajectory datasets.
+In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases.
 Before we move on to the algorithmic part, we list the notations that are used in the following sections.
@@
 \hline
-Symbol & Meaning \\
+\textbf{Symbol} & \textbf{Meaning} \\
 \hline
@@
 \hline
-$M$ & object size constraint \\
+$M$ & significance constraint \\
 \hline 
@@
 \hline
+$C_t(o)$ & cluster of object $o$ at time $t$ \\
+\hline 
+$S_t$ & set of clusters at time $t$\\
+\hline 
+$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\\hline
 $\eta$ & replication factor in the TRPM framework\\
 \hline
-$C_t(o)$ & the cluster of object $o$ at time $t$ \\
+$Sr_i $ &  star partition for object $i$ \\
 \hline 
-$S_t$ & the set of clusters at time $t$\\
-\hline 
-$\lambda_t$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
-\hline
-$Sr_i $ &  the star partition for object $i$ \\
+$\Gamma$ & size of the largest star in star partition \\
 \hline

### 2016-06-29 sec4_baseline.tex
Several minor changes
Needs to proofread more

@@
 \begin{proof}
-Given a valid pattern $P$, we can always find at least one valid subsequence that is also valid.
-Let $T'$ denote the valid subsequence with the minimum length.
+Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid.
+Let $T'$ denote the valid subsequence of $P.T$ with the minimum length.
 In the worst case, $T'=P.T$.
 We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
-Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1},g_{n-1},l_n$ ($n \geq 1$),
+Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
 where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
@@
 parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
-as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
+as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
 in Figure~\ref{fig:trm}(c), every $5$ consecutive snapshots are combined 

### 2016-06-29 sec6_experiment.tex
Several minor changes
Needs to proofread more

@@
 
-\subsubsection{Load Balance}
+\subsubsection{Load balance}
 To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method.

### 2016-06-30 appendix.tex
Reformatting
Several reformats

@@
 $\Gamma$ can be formalized in a linear algebra way:
-Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
+Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
 Since a vertex order is a permutation of $J$, the adjacent matrices 
@@
 For soundness, let $P$ be a pattern enumerated by SPARE.
-Since the enumerate algorithm only reduces the time sequences, for any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$.
-By the definition of star, $\forall t \in T, C_t(o_1) = C_t(o_2)$.
-As $T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
-For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with input $Sr_s$. 
+For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$.
+By the definition of star, $\forall t \in P.T, C_t(o_1) = C_t(o_2)$.
+As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
+For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} form $Sr_s$. 
 First, based on the definition of star, every object in $P.O$ appears in $Sr_s$.
-Since $P.T$ is decomposable, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence.
-This indicates that $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.
+Since $P.T$ is decomposable, then by Lemma 3 $\forall O' \subseteq O$, the time sequence of $O'$ would not be eliminated by any $\mathtt{sim}$ operations.
 Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure.
@@
 When $level$ = 2, it obviously holds.
-If $P.O \subset O_u$ at \emph{level=$i$}, then any subset of $P.O$ with size $i$ are in the candidate set.
+If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set.
 In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$).

### 2016-06-30 sec1_introduction.tex
Reformatting
Several reformats

@@
 A crucial task of data analysis on top of trajectories is 
-to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
+to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing} 
 refers to a group of objects traveling together for a certain period of time 
-and the group is normally determined by spatial proximity. 
+and the group is normally determined by their spatial proximity. 
 A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
@@
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|l|c|l|}
 \hline 
-Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
+\textbf{Pattern} & {\tiny \textbf{Proximity}} & {\tiny \textbf{Consecutiveness}} & {\tiny \textbf{Time Complexity}}\\ 
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|(M + \log(|\mathbb{O}|)))$} \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
+convoy~\cite{jeung2008convoy} & density-based &   global & {\tiny $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
-swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
+swarm~\cite{li2010swarm} & density-based  & - & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
+group~\cite{wang2006grouppattern} & disk-based &  local & {\tiny $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
+platoon~\cite{li2015platoon} & density-based &  local & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
@@
 \begin{figure}[h]
+	\vspace{-3mm}
     \centering
@@
     \end{subfigure}
-    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
+    \vspace{-2mm}
+    \caption{Performance measures on existing co-movement patterns. A sampled Geolife dataset
     is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
@@
 In addition, our GCMP is both general and expressive.
-It can be reduced to any of the previous patterns by customizing the parameters.
+It can be reduced to any of the previous patterns by customizing its parameters.
 
@@
 In particular, with near 200 million trajectory points, 
-SPARE runs in 15 minutes using 162 cores. Whereas
-centralized solutions take near 7 hours 
-for 1 million trajectory points.
+SPARE runs in 12 minutes using 162 cores, whereas
+centralized solutions take from 10 to 30 hours.
 Moreover, our optimized SPARE methods achieves upto 10 times efficiency

### 2016-06-30 sec3_definitions.tex
Reformatting
Several reformats

@@
 \begin{definition}[General Co-Movement Pattern]
-A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is $L$-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
+A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
 \end{definition}
@@
 \end{tabular} 
-\caption{Symbols and notions used}
+\caption{Summary of the use of notations.}
 \end{table}

### 2016-06-30 sec4_baseline.tex
Reformatting
Several reformats

@@
 Our focus in this paper is on the second map-reduce stage of parallel mining, which essentially addresses two key challenges.
-The first is to ensure effective data partitioning such that the mining can be conducted independently; and the second is to efficiently mine the valid patterns within each partition.
+The first is to ensure effective data partitioning such that the mining on each partition can be conducted independently; and the second is to efficiently mine the valid patterns within each partition.
 

### 2016-06-30 sec5_spm.tex
Several minor changes
Needs to proofread more
Reformatting
Several reformats

@@
 \centering
-\includegraphics[width=0.45\textwidth]{star-alt.eps}
+\includegraphics[width=0.40\textwidth]{star-alt.eps}
 \caption{Examples of star partitioning with different vertex ordering.}
@@
 Take $T=(1,2,4,5,6,9,10,11,13)$ as an example for sequence simplification. 
-Let $L = 2, K = 4$ and $G = 2$. In the $f$-step, $T$ is reduced to $f_2(T)=(1,2,4,5,6,9,10,11)$. 
+Let $L = 2, K = 4$ and $G = 2$. In the $f$-step, $T$ is reduced to $f_2(T)=(1,2,4,5,6,9$, $10,11)$. 
 The segment $(13)$ is removed due to the constraint of $L=2$. 
@@
 
-\subsection{Put It Together}
+\subsection{Put Everything Together}
 We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows.

### 2016-06-30 sec6_experiment.tex
Reformatting
Several reformats

@@
 \end{tabular}
-\caption{Statistics of data set}
+\caption{Statistics of datasets.}
 \label{exp:dataset}
@@
 \end{tabular} 
-\caption{Variables and their default values}
+\caption{Variables and their default values.}
 \label{tbl:parameters}
@@
 \hline 
-\textbf{Data Set} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
+\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
 \hline 
@@
 
-\caption{Pruning power of SPARE}
+\caption{Pruning power of SPARE.}
 \label{tbl:pruning}
@@
 \centering
-	  \includegraphics[width=0.3\textwidth]{/exp/spare/detail.eps}
+	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail.eps}
     \caption{Breakdown of cost of SPARE and SPARE-RD}
     \label{exp:wl}
-%	\begin{subfigure}[b]{0.3\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
-%        \caption{Decomposed running time}
-%    \end{subfigure}
-%    
-% 	\begin{subfigure}[b]{0.22\textwidth}
-%       \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
-%       \caption{Workload in Shopping}
-%   \end{subfigure}
-%    \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
-%        \caption{Workload in Geolife}
-%    \end{subfigure}  
-%    \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
-%        \caption{Workload in Taxi}
-%    \end{subfigure}
-%\caption{Load balance of SPARE and SPARE-LB}
 \end{figure}
@@
 \end{tabular}
-  \caption{Statistics of execution time among executors (in seconds)}
+  \caption{Statistics of execution time among executors (in seconds).}
   \label{tbl:strags}
@@
 Finally, we examine the scalability of our proposed frameworks in two contexts. 
-First, we use single-node mode and examine the performance with multi-cores.
-We also compare it with the  state-of-the-art solutions for swarm and platoon patterns since they were designed  to run in a centralized server.
+First, we use the single-node mode and examine the performance with multi-cores. 
+We also compare it with the state-of-the-art solutions for swarm and platoon patterns 
+since they were designed to run in a centralized server. 
 Second, we examine the pattern detection time with increasing computing resources (number of machines). 
+To support swarm and platoon, we sample 60\% of each dataset for this experiments. 
 The results are reported in Figure~\ref{exp:scalability}. 
-First, the centralized schemes are not suitable to discover patterns in large-scale trajectory databases.
-It takes nearly $16$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine.
-In contrast, when utilizing the multi-core environment, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively.
-Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available.
-The running time almost decreases linearly as more machines are used.
-When there are $11$ nodes in the cluster, the performance of SPARE is $94$ times better than the state-of-the-art \emph{platoon} detector in a centralized server.
+First, the centralized schemes are not suitable to discover patterns in 
+large-scale trajectory databases. It takes nearly $30$ hours to 
+detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
+In contrast, when utilizing the multi-core environment, 
+SPARE achieves $8$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
+%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
+Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available. The running time almost decreases inversely as more machines are used. 
+When there are $11$ nodes in the cluster, 
+the performance of SPARE is $73$ times faster 
+than \emph{platoon} and $170$ times better than \emph{swarm}.
+%state-of-the-art \emph{platoon} detector in a centralized server.
 
@@
     \end{subfigure}
- \caption{Comparisons among TRMP, SPARE and Platoon}
+ \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM}
  \label{exp:scalability}

### 2016-06-30 sec3_definitions.tex
Corrected several typos
Need to add authors and affliations

@@
 
-Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity.
+Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity.
 Let $T$ be the set of timestamps in which a group of objects $O$ are clustered.
@@
 In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern.
-By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern.
+By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern.
 By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern.
-Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns.
+Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns.
 In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 

### 2016-06-30 sec4_baseline.tex
Corrected several typos
Need to add authors and affliations

@@
 Our next task is to design an efficient pattern mining strategy within each partition.
-Our solution includes a line sweeping algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and an effective candidate pattern enumeration mechanism.
+Our solution includes a line sweep algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and an effective candidate pattern enumeration mechanism.
 
@@
 We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process.
-It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot.
+It is initialized using the clusters with size no smaller than $M$ in the first snapshot.
 Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
@@
 It is worth noting that $C$ continues to grow during the whole sweeping process.
-We can use three pruning rules to remove false candidates from $C$ early.
+We can use three pruning rules to early remove false candidates from $C$.
 Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered.
@@
 First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
-candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
-Third, candidates in $C$ with the size of first segment smaller than $L$
+candidates in $C$ with the maximum timestamp no smaller than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
+Third, candidates in $C$ with the size of the first segment smaller than $L$
 are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ can be significantly reduced.

### 2016-06-30 sec5_spm.tex
Corrected several typos
Need to add authors and affliations

@@
 \label{sec:spm}
-The aforementioned TRPM scheme replicates partitions based on the temporal dimension which suffers from two drawbacks.
+The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks.
 First, the replication factor is $\eta$ which can be large.
@@
 
-Before we introduce the Apriori enumerator, we are interested to 
+Before we introduce the Apriori Enumerator, we are interested to 
 examine the issue of global ordering on the moving objects.
@@
 different star partitioning results, which will eventually affect the workload 
-balance among the map-reduce jobs.
+balance among reducers.
 The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}.
 In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition.
-We use $\Gamma$ to denote the size of a partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}.
+We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}.
 Clearly, a star partitioning with small $\Gamma$ is preferred.
@@
 
-Although it is very challenging to find the optimal vertex id ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
+Although it is very challenging to find the optimal vertex ID ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
 
@@
 \end{proof}
-Hence, we can simply use object id to determine the vertex ordering in our implementation.
+Hence, we can simply use object ID to determine the vertex ordering in our implementation.
 
@@
 \subsubsection{Monotonicity}
-To ensure monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
+To ensure monotonicity, we first introduce a procedure named \textit{sequence simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists.
 For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$.
-To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.
+To generalize the idea, we propose three concepts: \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.
 
 \begin{definition}[Maximal $G$-connected Subsequence]
-A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, i.e., $\exists i\leq j, T' = T(i,\ldots,j)$ , (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
+A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
 \end{definition}
@@
 
-\subsubsection{Apriori Enumeration}
+\subsubsection{Apriori Enumerator}
 We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition.
-The principle of Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner.
+The principle of the Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner.
 Its merit lies in the monotonic property such that if a candidate set is not valid, then all its supersets can be pruned.
@@
 The remaining two candidates (i.e., $\langle 3,4:1,2,3 \rangle$ and $\langle 3,5:2,3 \rangle$)  derive a new  $\langle 3,4,5:2,3 \rangle$ which is valid.
-By the forward closure checking, the algorithm can terminate and output $\langle 3,4,5:2,3 \rangle$ as the final closed pattern.
+By the forward closure checking, the algorithm can terminate and output $\langle 3,4,5:2,3 \rangle$ as the final pattern.
 \end{example}

### 2016-06-30 sec6_experiment.tex
Corrected several typos
Need to add authors and affliations

@@
 \label{sec:exp}
-In this section, we evaluate the efficiency and scalability of our proposed distributed GCMP detectors on real trajectory datasets.
+In this section, we evaluate the efficiency and scalability of our proposed parallel GCMP detectors on real trajectory datasets.
 All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet.
@@
 
-\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c),(i),(o) present the performances with varying $L$.
+\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c),(i),(o) present the performances with increasing $L$.
 When $L=10$, SPARE can outperform TRPM by around $10$ times.
@@
 are shuffled to the reducers and (2) the number of pairs that
-are fed to the Apirori enumeration. The difference between these two values is the number of size-$2$ candidates pruned by the sequence simplification.
+are fed to the Apirori Enumerator. The difference between these two values is the number of size-$2$ candidates pruned by the sequence simplification.
 The results in Table~\ref{tbl:pruning} show that the \emph{sequence simplification} is very powerful and eliminates nearly 90 percent of the object pairs, which significantly reduces the overhead of subsequent Apriori enumerator.
@@
 	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail.eps}
-    \caption{Breakdown of cost of SPARE and SPARE-RD}
+    \caption{Breakdown of cost of SPARE and SPARE-RD.}
     \label{exp:wl}
@@
 When there are $11$ nodes in the cluster, 
-the performance of SPARE is $73$ times faster 
-than \emph{platoon} and $170$ times better than \emph{swarm}.
+SPARE achieves at most $73$ times faster 
+than \emph{platoon} and at most $170$ times better than \emph{swarm}.
 %state-of-the-art \emph{platoon} detector in a centralized server.
@@
     \end{subfigure}
- \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM}
+ \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
  \label{exp:scalability}

### 2016-07-01 appendix.tex
Final Version
Submitted to VLDB

@@
 %\end{proof}
+%\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
+\subsection{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
+\label{apx:thm2proof}
 
-%\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
-
-\subsection{Proof of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
-\label{apx:thm2proof}
 \begin{proof}
-$\Gamma$ can be formalized in a linear algebra way:
+$\Gamma$ can be formalized using linear algebra:
 Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
@@
 where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
-In star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
 then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
@@
 denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
-as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders, that is
+as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is
 
@@
 
-Let $B^*$ be the assignment matrix wrt. the optimal vertex order.
+Let $B^*$ be the assignment matrix wrt. the optimal vertex ordering.
 Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
 $\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
-Next, for a ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
+Next, for a vertex ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
 edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
-Let $d_i$ denote the degree of vertex $i$, since ordering of vertex does not
+Let $d_i$ denote the degree of vertex $i$, since a vertex ordering does not
 affect the average degree,
@@
 \begin{split}
-	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) \\
-	 & = \exp(-2\log n) = n^{-2}
+	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
 \end{split}
@@
 		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
-		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\ 
-		&= n^{-1} = 1/n
+		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
 \end{split}
@@
 For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$.
-By the definition of star, $\forall t \in P.T, C_t(o_1) = C_t(o_2)$.
+By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$.
 As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.

### 2016-07-01 sec1_introduction.tex
Corrected several typos
Need to add authors and affliations
Final Version
Submitted to VLDB

@@
 A crucial task of data analysis on top of trajectories is 
-to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing} 
+to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
 refers to a group of objects traveling together for a certain period of time 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{related_work.eps}
-\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots.
+\includegraphics[width=0.45\textwidth]{related_work.eps}
+\caption{Trajectories and co-movement patterns.
+The example consists of six trajectories across six snapshots.
 Objects in spatial clusters are enclosed by dotted circles.
@@
 \centering
-\begin{tabular}{|c|l|c|l|}
+\begin{tabular}{|l|l|c|l|}
 \hline 
@@
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|(M + \log(|\mathbb{O}|)))$} \\ 
+flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
 \hline 
@@
 \end{tabular} 
-\caption{Constraints and complexity of co-movement patterns.
-The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the number of descritized timestamps and $M$ is the minimum cluster cardinality.
-}
+\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
+$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
 \label{tbl:existing_co_patterns}
@@
     \vspace{-2mm}
-    \caption{Performance measures on existing co-movement patterns. A sampled Geolife dataset
-    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
+    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
+    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
     \label{fig:related_work_scalability}
@@
 In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments.
-By setting a feasible $G$, the loose-connection anomaly can be avoided.
+By setting a feasible $G$, the loose-connection anomaly can be effectively controlled.
 In addition, our GCMP is both general and expressive.
@@
 First, we replicate the snapshots in multiple data chunks to support efficient parallel processing.
-Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance.
+Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance.
 For each star, an Apriori Enumerator is adopted to mine the co-movement patterns.
-Third, we leverage the \emph{temporal monotonicity} property of of GCMP
-to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
+Third, we leverage the \emph{temporal monotonicity} property of GCMP
+to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
 
-We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
+We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
 temporal points. 
@@
 centralized solutions take from 10 to 30 hours.
-Moreover, our optimized SPARE methods achieves upto 10 times efficiency
+Moreover, our optimized SPARE methods achieves upto 14 times efficiency
 as compared to the baseline algorithm with almost linear scalability.
@@
 The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
-trajectory pattern mining.
-Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining.
-Section~\ref{sec:trm} provides a baseline solution.
-An advanced solution named
-\emph{Star Partition and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.
-Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system.
-Finally Section~\ref{sec:concl} concludes the paper.
+trajectory pattern mining. Section~\ref{sec:definition} defines the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
+\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.
+Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions.
+Finally, Section~\ref{sec:concl} concludes the paper.

### 2016-07-01 sec3_definitions.tex
Final Version
Submitted to VLDB

@@
 Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension.
-A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$.
+A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$.
 Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.
@@
 \begin{definition}[$G$-connected]
-A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
- $\forall i \in (1,...,|T|-1), T[i+1]-T[i] \leq G$.
+A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$, i.e.,
+ $\forall i \in (1,\ldots,|T|-1), T[i+1]-T[i] \leq G$.
 \end{definition}
@@
 \caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
-object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
+\emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
 \label{tbl:patterns}
 \end{table}
-\eat{ 
-It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
-when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
-size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
-which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:
-
-\begin{definition}[Closed General Co-Movement Pattern]
-A general co-moving pattern $P=\langle O:T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
-\end{definition}
-
-For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
-the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern.
-This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$.
-The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.
-}
 
 Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
-We currently expose both disc-region based clustering and DBSCAN as options to the users.
+We currently expose both disk-region based clustering and DBSCAN as options to the users.
 In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases.
@@
 \hline
-$C_t(o)$ & cluster of object $o$ at time $t$ \\
+%$C_t(o)$ & cluster of object $o$ at time $t$ \\
+%\hline 
+$S_t$ & set of clusters at snapshot $t$\\
 \hline
-$S_t$ & set of clusters at time $t$\\
-\hline 
-$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\\hline
 $\eta$ & replication factor in the TRPM framework\\
 \hline 
-$Sr_i $ &  star partition for object $i$ \\
+$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
 \hline
-$\Gamma$ & size of the largest star in star partition \\
+$G_A$ & aggregated graph in SPARE framework\\
+\hline
+$Sr_i $ &  star partition for object (vertex) $i$ \\
+\hline 
+$\Gamma$ & size of the largest star partition\\
 \hline

### 2016-07-01 sec4_baseline.tex
Final Version
Submitted to VLDB

@@
 \center
-\includegraphics[width=0.9\textwidth]{trm.eps}
+\includegraphics[width=\textwidth]{trm.eps}
 \caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
-(a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot;  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
+(a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.
+(c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
 \label{fig:trm}
@@
 \label{sec:trm}
-In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining.
+In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP mining.
 The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
@@
 It is obvious that we cannot simply split the trajectory database 
-into disjoint partitions because a GCMP pattern requires $L$-consecutiveness 
+into disjoint partitions because a GCMP requires $L$-consecutiveness 
 and the corresponding segments may span multiple partitions. 
@@
 as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
-in Figure~\ref{fig:trm}(c), every $5$ consecutive snapshots are combined 
-into a partition in the map phase. In Figure~\ref{fig:trm}(d), a line sweep
+in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
+into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
 method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
@@
 $\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
-and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
+and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
 Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
@@
 \label{code:trm-par-start}
-\ForAll{key-value pairs $\langle t, S \rangle$ pair} 
+\ForAll{key-value pairs $\langle t, S \rangle$} 
 \State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
@@
 \ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
-\State call line sweep algorithm for partition $\lambda_t$
+\State call line sweep mining for partition $\lambda_t$
 \label{code:trm-red-end}

### 2016-07-01 sec5_spm.tex
Final Version
Submitted to VLDB

@@
 \includegraphics[width=0.9\textwidth]{spm.eps}
-\caption{Star partition and ApRiori Enumerator (SPARE).
-(a) Aggregated graph from Figure 1.
-(b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
+\caption{Star Partitioning and ApRiori Enumerator (SPARE).
+(a) Aggregated graph $G_A$ generated from Figure 1.
+(b) Five star partitions are generated from $G_A$.
+Star IDs are circled, vertexes and inverted lists are in the connected tables.
 (c) Apriori Enumerator with various pruning techniques.}
@@
 The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks.
-First, the replication factor is $\eta$ which can be large.
+First, the replication factor $\eta$ can be large.
 Second, the same valid pattern may be discovered from different partitions which results in redundant works.
@@
 we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
-to replace the second stage of map-reduce jobs in Figure~\ref{fig:trm}. 
+to replace the second stage of the map-reduce jobs in Figure~\ref{fig:trm}. 
 Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
 Its input is the set of clusters generated in each snapshot and the output 
-contains all the valid GCMP patterns. In the following, we explain the two major components: 
+contains all the valid GCMPs. In the following, we explain the two major components: 
 star partitioning and apriori enumerator.
@@
 An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
-is shown in Figure~\ref{fig:star_partition}(a). 
+is shown in Figure~\ref{fig:star_partition} (a). 
 As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
@@
 To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
-we enforce a global ordering among the objects and propose a concept named \textit{directed star}.
+we enforce a global vertex ordering among the objects and propose a concept named \textit{directed star}.
 
 \begin{definition}[Directed Star]
-Given a vertex with global id $s$, its directed star $Sr_s$ is defined as the set of neighboring vertices with global id $t>s$. We call $s$ the star ID.
+Given a vertex with global ID $s$, its directed star $Sr_s$ is defined as the set of neighboring vertexes with global ID $t>s$. We call $s$ the star ID.
 \end{definition}
 
-With the global ordering, we can guarantee that each edge is contained in a unique star partition.
-Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition}(a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition}(b).
+With the global vertex ordering, we can guarantee that each edge is contained in a unique star partition.
+Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition} (a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition} (b).
 These stars are emitted from mappers to different reducers.
 The key is the star ID and the value is the neighbors in the star as well as the associated inverted lists.
-The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.
+The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMPs.
 
 Before we introduce the Apriori Enumerator, we are interested to 
-examine the issue of global ordering on the moving objects.
+examine the issue of global vertex ordering on the moving objects.
 This is because assigning different IDs to the objects will result in 
@@
 \includegraphics[width=0.40\textwidth]{star-alt.eps}
-\caption{Examples of star partitioning with different vertex ordering.}
+\caption{Examples of star partitioning with different vertex orderings.}
 \label{fig:star-alt}
@@
 
-Although it is very challenging to find the optimal vertex ID ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
+Although it is very challenging to find the optimal vertex ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.
 
@@
 \begin{proof}
-In Appendix~\ref{apx:thm2proof}.
+See Appendix~\ref{apx:thm2proof}.
 \end{proof}
@@
 \subsection{Apriori Enumerator}
-Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, 
+Intuitively, given a GCMP with an object set $\{o_1,o_2,\ldots,o_m\}$, 
 all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
 be connected in the associated temporal graphs $\{G_t\}$.
-This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects.
+This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMPs starting from pairs of objects.
 However, we observe that the monotonicity property does not hold between an object set and its supersets.
@@
 
-To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$.
+To prove (2), we assume $\cup_{i=1}^{i=m} T_i$ does not cover all the timestamps in $T$.
 Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$.
@@
 If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected.
-If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$.
-Both cases lead to a contradiction.
+If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in$\cup_{i=1}^{i=m} T_i$.
+Both cases lead to contradictions.
 \end{proof}
@@
 %Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
-We provide an important property of the sequence simplification process as follows:
+We then link \emph{sequence simplification} and \emph{decomposable sequence} in the following lemma:
+%We provide an important property of the sequence simplification process as follows:
 \begin{lemma}\label{lemma:decom-sim}
@@
 \subsubsection{Apriori Enumerator}
-We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition.
+We design an Apriori based enumeration algorithm to efficiently discover all the valid patterns in a star partition.
 The principle of the Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner.
@@
 Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}).
-An indicator \emph{level} is used to control the object size for candidate set join.
+An indicator \emph{level} is used to control the result size for candidate joins.
 During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}).
-When two candidate sets $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}).
+When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}).
 To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$.
 If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}).
-This ensures that
-then all the candidates with $P.O\supseteq c'.O$ are pruned.
-If a candidate cannot generate any new candidate, then it is directly reported as a valid closed pattern (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
+This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned.
+If a candidate cannot generate any new candidate, the
+it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
 To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
@@
 \begin{example}
-As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\langle 3,6:3 \rangle $ is pruned because its simplified sequence is empty.
+As shown in Figure~\ref{fig:star_partition} (c), in the bottom level of the lattice structure, candidate $\langle 3,6:3 \rangle $ is pruned because its simplified sequence is empty.
 Thus, all the object sets containing $\langle 3,6 \rangle $ can be pruned.
@@
 \small
-\caption{Star Partition and ApRiori Enumerator}
+\caption{Star Partitioning and ApRiori Enumerator}
 \label{algo:spm_overview}
@@
 \ForAll{$\langle o, Sr_{o} \rangle$}
-\State AprioriEnumerator($Sr_o$)
+\State call Apriori Enumerator for star $Sr_o$
 \EndFor
@@
 Note that the center vertex of the star is associated with the minimum id.
-Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$.
-However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction.
+Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$.
+However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction.
 \end{proof}

### 2016-07-01 sec6_experiment.tex
Final Version
Submitted to VLDB

@@
 \begin{itemize}
-\item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}. The dataset contains
+\item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}: The dataset contains
   trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
-\item{GeoLife}~\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}. The dataset essentially keeps all the travel records of 182 users for a period
+\item{GeoLife}~\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}: The dataset essentially keeps all the travel records of 182 users for a period
 of over three years, including multiple kinds of transportation modes (walking, driving and taking public
@@
 are sampled every 1 to 5 seconds.
-\item{Taxi}. The dataset tracks the trajectories of $15,054$ taxies in Singapore over August 2008. The sampling
-rate is around 30 seconds. 
+\item{Taxi}~\footnote{Taxi is our proprietary dataset}: The dataset tracks the trajectories of $15,054$ taxies in Singapore.
+For each taxi, the GPS information are continually collected for one entire month with the sampling rate around 30 seconds.
 \end{itemize}
@@
 \textbf{Preprocessing}: We replace timestamps with global sequences (starting from $1$) for each dataset. 
-We set a fixed sampling rate for each dataset (i.e., Geolife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
+We set a fixed sampling rate for each dataset (i.e., GeoLife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
 and use linear interpolation to fill missing values.
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
-        \caption{Geolife vary $M$}
+        \caption{GeoLife vary $M$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
-        \caption{Geolife vary $K$}
+        \caption{GeoLife vary $K$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
-        \caption{Geolife vary $L$}
+        \caption{GeoLife vary $L$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
-        \caption{Geolife vary $G$}
+        \caption{GeoLife vary $G$}
     \end{subfigure}       
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
-        \caption{Geolife vary $O_r$}
+        \caption{GeoLife vary $O_r$}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
-        \caption{Geolife vary $T_r$}
+        \caption{GeoLife vary $T_r$}
     \end{subfigure}
@@
 present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over the TRPM framework, with 
-a performance gain by a factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
-$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.
+a performance gain by a factor of  $2.7$ times in Shopping, $3.1$ times in GeoLife and
+$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improve because the number of clusters in each snapshot drops, generating fewer valid candidates.
 
@@
 This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$.
-However, the line sweeping algorithm in TRPM does not utilize such property for pruning.
+However, the line sweep algorithm in TRPM does not utilize such property for pruning.
 It takes longer time because more replicated data has to be handled in each partition.
@@
 TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$.
-In contrast, with much more effective pruning strategy, our SPARE scales very well with $G$.
+In contrast, with much more effective pruning strategy, our SPARE scales well with $G$.
+Particularly, SPARE is 14 times faster than TRPM when $G=20$ in GeoLife dataset.
 
-\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present 
-the performances with increasing number of moving objects.
+\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects.
 Both TRPM and SPARE take longer time to find patterns in a larger database.
@@
 \end{tabular}
-  \caption{Statistics of execution time among executors (in seconds).}
+  \caption{Statistics of execution time (in seconds) among executors.}
   \label{tbl:strags}
@@
 In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
-Figure~\ref{exp:wl}(a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD.
+Figure~\ref{exp:wl} (a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD.
 We observe that the map and shuffle time of SPARE and SPARE-RD are identical.
@@
 Second, we examine the pattern detection time with increasing computing resources (number of machines). 
-To support swarm and platoon, we sample 60\% of each dataset for this experiments. 
+As the poor performances of swarm and platoon, we only use 60\% of each dataset for experiments. 
 The results are reported in Figure~\ref{exp:scalability}. 
@@
 In contrast, when utilizing the multi-core environment, 
-SPARE achieves $8$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
+SPARE achieves $9$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
 %our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
@@
 When there are $11$ nodes in the cluster, 
-SPARE achieves at most $73$ times faster 
+SPARE achieves at most $63$ times faster 
 than \emph{platoon} and at most $170$ times better than \emph{swarm}.
@@
         \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
-        \caption{Geolife vary $N$}
+        \caption{GeoLife vary $N$}
     \end{subfigure}

### 2016-07-01 sec7_conclusion.tex
Final Version
Submitted to VLDB

--- 2016-06-25 sec7_conclusion.tex
@@
-\section{Conclusion and Future Work}
+\section{Conclusions and Future Work}
 \label{sec:concl}
+In this paper, we proposed a generalized co-movement pattern to unify those proposed in the past literature.
+We also devised two types of parallel frameworks in Spark that can scale to support pattern detection in trajectory databases with hundreds of millions of points.
+The efficiency and scalability were verified by extensive experiments on three real datasets.
+In the future, we intend to examine co-movement pattern detection in streaming data for real-time monitoring.
+How to extend the current parallel frameworks to support other types of advanced patterns is also of our interest.

### 2016-07-01 sec1_introduction.tex
Final Final Version

@@
             \includegraphics[width=\textwidth]{rw_perf_O.eps}
-		\subcaption{$1k$ timestamps vary $O$} 
+		\subcaption{\small Varying No. of objects} 
     \label{fig:fig1}
@@
             \includegraphics[width=\textwidth]{rw_perf_T.eps}
-         \subcaption{$1k$ objects vary $T$}
+         \subcaption{\small Varying No. of timestamps}
     \label{fig:fig2}
@@
 Our technical contributions are three-fold.
-First, we replicate the snapshots in multiple data chunks to support efficient parallel processing.
-Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance.
-For each star, an Apriori Enumerator is adopted to mine the co-movement patterns.
+First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining.
+Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline.
+SPARE achieves workload balance by partitioning objects into fine granular stars.
+For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns.
 Third, we leverage the \emph{temporal monotonicity} property of GCMP
-to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
+to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.
 
@@
 temporal points. 
-The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
-In particular, with near 200 million trajectory points, 
-SPARE runs in 12 minutes using 162 cores, whereas
-centralized solutions take from 10 to 30 hours.
-Moreover, our optimized SPARE methods achieves upto 14 times efficiency
+The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
+In particular, with over 170 million trajectory points,
+SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
+Moreover, SPARE further achieves upto 14 times efficiency
 as compared to the baseline algorithm with almost linear scalability.

### 2016-07-01 sec6_experiment.tex
Final Final Version

@@
 \subsection{Analysis of SPARE framework}
-In this part, we extensively evaluate the advantage brought by the
-sequence simplification and load balancing techniques.
+In this part, we extensively evaluate SPARE from three aspects:
+(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
+%Then, we study the scalability of SPARE with increasing computing resources.
 
@@
 
-\subsection{Scalability}
-Finally, we examine the scalability of our proposed frameworks in two contexts. 
-First, we use the single-node mode and examine the performance with multi-cores. 
-We also compare it with the state-of-the-art solutions for swarm and platoon patterns 
-since they were designed to run in a centralized server. 
-Second, we examine the pattern detection time with increasing computing resources (number of machines). 
-As the poor performances of swarm and platoon, we only use 60\% of each dataset for experiments. 
-The results are reported in Figure~\ref{exp:scalability}. 
+\subsubsection{Scalability}
+When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting.
+Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation.
+To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively.
+The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}.
 First, the centralized schemes are not suitable to discover patterns in 
@@
 In contrast, when utilizing the multi-core environment, 
-SPARE achieves $9$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
+SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
 %our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
-Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available. The running time almost decreases inversely as more machines are used. 
-When there are $11$ nodes in the cluster, 
-SPARE achieves at most $63$ times faster 
-than \emph{platoon} and at most $170$ times better than \emph{swarm}.
+Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
+When all the $11$ nodes ($162$ cores) are available, 
+SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
+%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
 %state-of-the-art \emph{platoon} detector in a centralized server.

### 2016-08-26 ReviewComments/response.tex
Revision
almost completed

\documentclass{vldb}
\usepackage{url}
\newcounter{ctResp}
\newcommand{\response}[1]{
\addtocounter{ctResp}{1}
\textbf{Response \arabic{ctResp}:} #1 \\}

\begin{document}
\title{Response to reviewers' comments for Paper \# 278}
\maketitle

We are grateful to all the reviewers for the generous and insightful
comments which help us to improve this work to a better level. Hereby, 
we summarize our responses and corresponding revisions.
We wish this feedback could help to clear reviewers' concerns 
in publishing this paper.

\input{review1}
\input{review2}
\input{review3}
\input{meta}

\end{document}

### 2016-08-26 ReviewComments/meta.tex
Revision
almost completed

\section{Response to Meta Reviewer}

\emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}

\response{In addition to the points in Response 2, another novelty of our work lies in the 
techniques. 
Although the idea of star-partition and apriori-partition are well-known, 
linking them together to solve the problem in trajectory domain has not been attempted before.
Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
anti-monotonicity) which have not been proposed before.
}

\emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
on the motivation.}

\response {Similar responses with Response 3. }

\emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce. Spark has capabilities beyond MapReduce such as window functions. Please provide an implementation that uses the relevant features of Spark, or a convincing discussion of how these features can be useful and why they were not used.}

\response{Similar responses with Response 1 and 5. }

\emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew. Also provide details about how star partitioning and a priori pruning contribute to performance. Please provide references to these two methods.}

\response { The evaluations are added in Table 7 and Figure 8. Due to the space limit, we only provide the summary of performance skew in Table 9 (i.e., the longest time-taking task vs stand deviation of each task). As per our analysis, the skew is limited because every stars are of similar sizes. The references of apriori and star partition are added accordingly in Section 5.1 and Section 5.2.
}

### 2016-08-26 ReviewComments/review1.tex
Revision
almost completed

\section{Response to Reviewer 1}

\emph{The main con that I've spotted is the fact that the algorithm might have been
more nicely framed also within the Spark environment by taking advantage of
the various possibilities offered by it (e.g. caching of RDDs)}

\response{We agree that utilizing advanced Spark features would 
improve our solutions. We do not include these optimization in-depth
because in this work we set out focus on solving the challenges
in parallelizing the GCMP mining algorithms.
Nevertheless, we would improve and open-source a Spark-tailored
version of SPARE in the future.
}

### 2016-08-26 ReviewComments/review2.tex
Revision
almost completed

\section{Response to Review 2}

\emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
on consecutive segments is well-known
in sequence mining published more than
10 years ago.}

\response{
We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
modeling lies in unifying existing movement patterns in the trajectory domain. 
The gap parameter is naturally introduced to 
solve the loose-connection anomaly (as in Figure 2).
%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
In the revision, we add Section 2.5 to accredit the origin of \emph{gap} concept
and distinguish the sequential mining problem with our problem. 
}

\emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
we really interested in all sets of movements beyond a cardinality of size $M$? 
Take the Taxi dataset as an example. Let say that there are lots of taxis going
from the airport to downtown. Let say that there are 1000 such taxis. For a
given $M$, are we interested in ${1000 \choose M}$ answers? 
So this speaks to the problem of picking $M$. If $M$ is 500, what is ${1000 \choose M}$? In fact, even if the
system gives the single answer of ${1000\choose 1000}$,
I am not sure I am
interested in this pattern as I already know that there are many taxis going from
the airport to downtown. What I think I am really interested in are GCMP that
are ``anomalous'', which is much harder to define.}

\response{
We agree that if no other parameters are given, the maximum number
of patterns discovered could be as large as ${ \mathbb{O} \choose M}$, which may
be less interesting to users.
However, such a case rarely occurs due to two reasons. First,
in real trajectory mining, parameter $M$
is associated with temporal parameters $K,L,G$ and they jointly prune many false
patterns. Second, the nature of our solutions prefer 
a larger pattern when possible~\footnote{TRPM shrinks an invalid larger pattern until it is valid. SPARE grows a valid smaller pattern until it is about to be invalid. Therefore both algorithms tend to find larger patterns.}.
For example, if $(o_1,o_2,o_3)$ is 
a pattern and $M = 2$, 
then both TRPM and SPARE only output $(o_1,o_2,o_3)$ but not
any of its subsets. This effectively compresses smaller patterns.

In addition, when the temporal parameters $K,L,G$ are given,
a larger $M$ actually decreases the number of resulted patterns. 
This is because there are less patterns having more than $M$ objects. 
As shown in Figures 7 (a)(g)(m), a larger $M$ actually reduces the running time of both TRPM and SPARE.
}

\emph{Regarding the second weak point, one line of related work is the superimposition
of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}

\response{We agree that domain-specific constraints
on spatiotemporal mining could be similar to GCMP.
However, these domain-specific constraints 
are nontrivial to be generalized. Since our GCMP model as well as solutions
do not leverage domain knowledge, we can support
pattern discovery in a broader context. We add the discussion in Section 2.3.
}

### 2016-08-26 ReviewComments/review3.tex
Revision
almost completed

\section{Responses to Reviewer 3}
\emph{Though the implementation references Spark as the implementation
platform (as it also reflects in github repo provided), the algorithm design is
mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
Spark. This may have a negative impact on the baseline implementation.
Particularly, recent releases of Spark have introduced window functions that can
be applied directly in the sliding window scenario here. Certainly, the algorithm
has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
been noted that this is a very efficient way to execute window functions in
Spark}

\response{
We agree that leveraging more advanced Spark features
could further improve the performance of our solutions. 
We do not heavily leverage these features because 
we wish to focus on solving how to design parallel GCMP mining algorithms.
%to provide a general parallel framework which does not tie to Spark.
Nevertheless, we are in progress to develop and open-source 
a better SPARE version with Spark-tailored optimization.

In the revision, we try to add a DataFrame based TRPM solution 
which aims to leverage the window functions in Spark-SQL.
However, to the best of our efforts, we could not achieve this goal in a short time. 
The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
is nontrivial. Nevertheless, we expect less performance
boost from TRPM even with UDAF support. This is because the Line sweep algorithm is not
properly reducible, where Spark system would fail to leverage the partial aggregates
across multiple windows. Then, it would be equivalent to our current TRPM
implementation.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

\emph{In particular, it would be great to provide the
difference in the number of partitions/splits, the amount of processing and
memory usage (i.e., vcore and memory seconds) between TRPM and SPARE}

\response{We add Table 7 to include vcore-seconds 
and RDD memory usage for both TRPM and SPARE. We also add a clear description on partitions in Section 6.
}

\emph{A plot that breaks down the performance gain by each method would
be greatly appreciated by the readers.}

\response{We complement Figure 8 with the breakdown cost of TRPM. This
comparison showcases the benefits of both Star Partition (in mapshufle phase)
and Apriori Enumeration (in reduce phase) of SPARE.
}

\emph{Some choices of words may need to be reconsidered: for example, "a bunch
of" might not be appropriate in a technical paper.}

\response{We thank the reviewer for the correction. We have changed many unprofessional terms.
}

\emph{References to star partitioning and apriori pruning are missing. Though these
are well known, they need to clearly cited. At least the following reference is
missing:}

\response{We add the corresponding references in Section 5.1 and Section 5.2.}

\emph{In "In contrast, when utilizing the multicore
environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was "multicore"
referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}

\response{ We use all 16 cores in a single node in our settings. We revise the description in Section 6.2.3.
}

\emph{The computation of "eta" was slightly different than that in the paper}

\response{
We have updated the GitHub repository to rectify the typo in the equation.}

### 2016-08-26 sec1_introduction.tex
Revision
almost completed

@@
 A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
-and driven by different mining applications, there are a bunch of variants 
+and driven by different mining applications, there are \revised{many} variants 
 of co-movement patterns that have been developed with more advanced constraints.
@@
 various co-moment patterns in a unified way and can avoid 
-the \emph{loose-connection} anomaly.
-In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments.
+the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
+%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
+%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
 By setting a feasible $G$, the loose-connection anomaly can be effectively controlled.

### 2016-08-26 sec5_spm.tex
Revision
almost completed

@@
 
-We use \emph{star} as the data structure to capture the pair relationships. 
+We use \emph{star}~\cite{yoo2006joinless} as the data structure to capture the pair relationships. 
 To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
@@
 be connected in the associated temporal graphs $\{G_t\}$.
-This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMPs starting from pairs of objects.
+This inspires us to leverage the classic Apriori algorithm~\cite{agrawal1994fast} to enumerate all the valid GCMPs starting from pairs of objects.
 However, we observe that the monotonicity property does not hold between an object set and its supersets.
@@
 \end{theorem}
+\vspace{-5 mm}
 \begin{proof}

### 2016-08-26 sec6_experiment.tex
Revision
almost completed

@@
 We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes.
-We deploy our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
+We deploy our GCMP detector on Apache Spark 1.5.2~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
 To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
 In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
+\revised{We set the number of partitions to be $486$ to fully utilize the parallelism provided by the multi-threading of every core.}
 All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
@@
 
+\revised{
+\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken by TRPM and SPARE under the default setting.
+Both TRPM and SPARE are resource efficient as they only occupy less than 20\%
+of the available memory which reveals their potential to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues
+to the set of effective pruning procedures.
+
+\begin{table}[h]
+\small
+\begin{tabular}{|l|c|c|c|c|}
+\hline
+\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
+\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ \cline{2-5} 
+                                       & SPARE           & 334                               & 47,430                 & 8,613                \\ \hline
+\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ \cline{2-5} 
+                                       & SPARE           & 480                               & 49,835                 & 14,369               \\ \hline
+\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ \cline{2-5} 
+                                       & SPARE           & 812                               & 89,390                 & 35,912               \\ \hline
+\end{tabular}
+\caption{Resources taken for TRPM and SPARE.
+Time is in seconds representing observed performance.
+Vcore-seconds is the aggregate of time spent in each core.
+Memory is in MB representing the actual size of RDDs.}
+\label{tbl:resource}
+\end{table}
+}
 %\begin{figure}[h]
@@
 \centering
-	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail.eps}
-    \caption{Breakdown of cost of SPARE and SPARE-RD.}
+	  \includegraphics[width=0.35\textwidth]{/exp/spare/detail1.eps}
+    \caption{Breakdown of cost of TRPM, SPARE and SPARE-RD.}
     \label{exp:wl}
@@
 \centering \small
-\begin{tabular}{|l|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
+\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                          & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
@@
 In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
-Figure~\ref{exp:wl} (a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD.
-We observe that the map and shuffle time of SPARE and SPARE-RD are identical.
+Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD \revised{with TRPM as comparison}.
+We observe that the map and shuffle time of SPARE and SPARE-RD are identical .
 The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
-We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
+\revised{We further observe that TRPM takes more time in each phase, which confirms the efficiency of Star Partition and Apriori Enumeration.} We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
 Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
@@
 detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
-In contrast, when utilizing the multi-core environment, 
+In contrast, when utilizing the multi-core \revised{(i.e., single node with 3 executors)} environment, 
 SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 

### 2016-08-28 ReviewComments/review1.tex
Review Response
responses

@@
 \response{We agree that utilizing advanced Spark features would 
-improve our solutions. We do not include these optimization in-depth
-because in this work we set out focus on solving the challenges
-in parallelizing the GCMP mining algorithms.
-Nevertheless, we would improve and open-source a Spark-tailored
-version of SPARE in the future.
+improve our solutions. In this work, we do not include 
+these optimization in-depth because we set out focus 
+on solving the challenges in parallelizing the 
+GCMP mining algorithms.
+We are also in progress of open-sourcing a Spark-tailored
+version of SPARE.
 }

### 2016-08-28 ReviewComments/review2.tex
Review Response
responses

@@
 %which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
-In the revision, we add Section 2.5 to accredit the origin of \emph{gap} concept
+In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
 and distinguish the sequential mining problem with our problem. 
@@
 However, these domain-specific constraints 
-are nontrivial to be generalized. Since our GCMP model as well as solutions
+are nontrivial to be generalized. Since our GCMP model and technical solutions
 do not leverage domain knowledge, we can support
-pattern discovery in a broader context. We add the discussion in Section 2.3.
+pattern discovery in a broader context. We add a discussion in Section 2.3.
 }

### 2016-08-28 ReviewComments/review3.tex
Review Response
responses

@@
 We do not heavily leverage these features because 
-we wish to focus on solving how to design parallel GCMP mining algorithms.
+we wish to focus on designing parallel GCMP mining algorithms.
 %to provide a general parallel framework which does not tie to Spark.
-Nevertheless, we are in progress to develop and open-source 
-a better SPARE version with Spark-tailored optimization.
+Nevertheless, we are in progress in developing
+a better open-sourced version with Spark-tailored optimization.
 
 In the revision, we try to add a DataFrame based TRPM solution 
-which aims to leverage the window functions in Spark-SQL.
+which aims to leverage the window functions from Spark-SQL.
 However, to the best of our efforts, we could not achieve this goal in a short time. 
@@
 our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
-is nontrivial. Nevertheless, we expect less performance
-boost from TRPM even with UDAF support. This is because the Line sweep algorithm is not
+is nontrivial. Nonetheless, we expect less performance
+boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
 properly reducible, where Spark system would fail to leverage the partial aggregates
-across multiple windows. Then, it would be equivalent to our current TRPM
-implementation.
+across multiple windows. As a result, it would be equivalent to our current TRPM
+solution where windows are processed independently in parallel.
 %TRPM although can be modeled using window functions over data frame, the aggregates
@@
 
-\response{ We use all 16 cores in a single node in our settings. We revise the description in Section 6.2.3.
+\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
 }

### 2016-08-28 sec6_experiment.tex
Review Response
responses

@@
 detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
-In contrast, when utilizing the multi-core \revised{(i.e., single node with 3 executors)} environment, 
+In contrast, when utilizing the multi-core \revised{(i.e., a single node with four executors)} environment, 
 SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 

### 2016-08-28 ReviewComments/response.tex
Review Response
responses
New revision
...

@@
 
-We are grateful to all the reviewers for the generous and insightful
-comments which help us to improve this work to a better level. Hereby, 
-we summarize our responses and corresponding revisions.
-We wish this feedback could help to clear reviewers' concerns 
-in publishing this paper.
+We are deeply grateful to all the reviewers for the generous and insightful
+suggestions which help us to improve this work to a better level.
+In the following, we provide explicit response to each raised concern and address our corresponding revisions in the new submission.
 

### 2016-08-28 ReviewComments/review1.tex
New revision
...

@@
 
-\response{We agree that utilizing advanced Spark features would 
-improve our solutions. In this work, we do not include 
-these optimization in-depth because we set out focus 
-on solving the challenges in parallelizing the 
-GCMP mining algorithms.
-We are also in progress of open-sourcing a Spark-tailored
-version of SPARE.
+\response{
+We agree with the reviewer that utilizing advanced Spark features
+would benefit our solutions.
+In fact, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine).
+As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
+Using the DAG execution engine, we are able to adopt a Map-Planning-Reduce work flow.
+With the support of in-memory caching of RDDs,
+the Map results need not to be recomputed after the planning phase.
+As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).
+If without Spark's features, such an optimization would be hardly possible.
+
+We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
+%
+%We are unsure about whether adapting other features in Spark (e.g., Spark streaming, Spark SQL, Spark Graph) would help to improve our solutions. Since they are solutions 
+%%
+%
+%In this work, we do not include 
+%these optimization in-depth because we set out focus 
+%on solving the challenges in parallelizing the 
+%GCMP mining algorithms.
+%We are also in progress of open-sourcing a Spark-tailored
+%version of SPARE.
 }

### 2016-08-28 ReviewComments/review2.tex
New revision
...

@@
 
-\response{
+\response{We agree with the reviewer that the gap parameter is an old concept. However, we use the gap parameter merely for solve the loose-connection anomaly (as in Figure 2).
+
+However, our major contribution in modeling of GCMP is not on the gap parameter and our problem is very different from the sequence mining problem.
+
 We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in

### 2016-08-29 ReviewComments/review2.tex
Revised response
some more responses

--- 2016-08-26 ReviewComments/review2.tex
@@
 \response{
-We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
-modeling lies in unifying existing movement patterns in the trajectory domain. 
-The gap parameter is naturally introduced to 
-solve the loose-connection anomaly (as in Figure 2).
-%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
-In the revision, we add Section 2.5 to accredit the origin of \emph{gap} concept
-and distinguish the sequential mining problem with our problem. 
+We admit that the gap parameter is also used in
+mining Gap-restricted Sequential Patterns (GSP). However, the novelty
+of this paper is not merely on introducing the gap-constraint to the
+co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
+for mining various co-movement patterns with flexible constraints. With
+these constraints, users are able to define a more accurate pattern
+which are free from the anomalies (e.g., loss-connection anomaly as in Figure 2).
+
+Besides, the nature of GSP and GCMP are different. The goal of GSP 
+is to find the sequences which conform to the gap constraint and occur frequently.
+When counting the occurrence of a sequence in GSP, the object
+which a sequence belongs to does not matter. Therefore, for
+a pattern result in GSP, it cannot guarantee either the 
+distinction of involved objects or the closeness of those objects.
+In contrast, GCMP has requirements on both the spatial closeness 
+of objects and the number of distinct objects.
+Due to the unawareness of objects, techniques that are used in GSP 
+cannot be directly applied on GCMP. We also summarize the difference
+in Section 2.5.
+%
+%When counting the occurrence of a sequence, 
+%the object the sequence belongs does not matter. 
+%Therefore, a pattern in FS may corresponds to any objects where
+%the closeness or distinction of objects are not statisfied. Due
+%to this difference, FS solutions cannot be directly applied on GCMP.
+%
+%
+%We agree with the reviewer that gap parameter is 
+%also used in the Sequence Mining problem. However, 
+%Sequence mining problem is different from the GCMP mining problem. 
+%The major difference is that in sequence mining problem, the object
+%itself is not considered. In particular, the frequency of a sequence is 
+%counted as the occurrence of a sequence. Thus, an object may
+%contribute multiple occurrence of a sequence. Conversely, GCMP
+%in addition to impose the gap parameter in the temporal constraint, also 
+%require the objects in the pattern to be close. Due to this difference,
+%Sequence mining solutions cannot support GCMP mining.
+%
+%that the gap parameter is an old concept. 
+%However, the novelty of GCMP lies in the unification and generalization of existing patterns which provide
+%a one-stop solution for co-movement pattern detection. And the
+%gap parameter merely is used for solving the loose-connection anomaly (as in Figure 2). 
+%
+%Moreover, the problem of Sequence mining is also different from Trajectory mining.
+%The major difference is that sequence mining do not consider the distinction between
+%objects and the closeness among objects. This makes the solutions in Sequence mining
+%unable to be applied in GCMP. We summarize these points in Section 2.5 of the revised paper.
+%
+%We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
+%modeling lies in unifying existing movement patterns in the trajectory domain. 
+%The gap parameter is naturally introduced to 
+%solve the loose-connection anomaly (as in Figure 2).
+%%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
+%In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
+%and distinguish the sequential mining problem with our problem. 
 }
@@
 
-\response{
-We agree that if no other parameters are given, the maximum number
-of patterns discovered could be as large as ${ \mathbb{O} \choose M}$, which may
-be less interesting to users.
-However, such a case rarely occurs due to two reasons. First,
-in real trajectory mining, parameter $M$
-is associated with temporal parameters $K,L,G$ and they jointly prune many false
-patterns. Second, the nature of our solutions prefer 
-a larger pattern when possible~\footnote{TRPM shrinks an invalid larger pattern until it is valid.
+\response{We appreciate the reviewer's concerns on the 
+size of the output. 
+In fact, both TRPM and SPARE
+have considered compressing the output by only discovering 
+the patterns with larger object set. 
+Particularly,  in the Line Sweeping Mining (Algorithm 1) of TRPM, whenever
+a pattern $c$ becomes valid, it is directly outputted (Lines 14-16). This
+prohibits outputting $c$'s subset. Similarly, in the Apriori Enumerator (Algorithm 3)
+of SPARE, a pattern $c$ is outputted if non of its superset would become a valid pattern (Line 12-14).
+This prohibits the output $c$ to be a subset of any patterns.
+These mechanisms effectively condense the output size by subsuming smaller
+patterns using their supersets.
+% Nevertheless, these mechanisms are able to preserve ALL valid patterns.
+Linking to the Taxi example, if the ground truth contains 1000 taxis travel
+together, then both TRPM and SPARE tend to output the single pattern.
+In addition, real detection of ``anomalous'' co-moment pattern needs to 
+impose stringent constraints via $M,K,L,G$. This would further reduces 
+the number of potential patterns.
+%On the other hand, in reality, if users wish to detect ``anomalous'' patterns,
+%the parameters $M,K,L,G$ will be set to be very stringent. This reduces
+%the size of potential outputs. For example, when detecting the Taxi's movements
+%without ground truth of 1000 taxis, an input could be $M = 100$, $K=50$ min, $L=30$ min,
+%$G = 2$ min. Then, there would be very less patterns satisfying these constraints.
+% and the meaningfulness of the output. 
+%In terms of the output size, 
+%we certainly do not need to output every pattern.
+%In fact, both TRPM and SPARE algorithms tend to only output
+%the patterns with larger object size. That is to say, for
+%the Taxi example, the pattern containing all the 1000 taxis will
+%be outputted. To see this, in Algorithm 1, TRPM effectively 
+%starts with a temporally invalid pattern and continue
+%to shrink its object set until it is temporally valid. Then, the result
+%is the ``largest'' valid pattern for these object. Similarly,
+%in Algorithm 3, SPARE effectively starts with a temporally valid
+%pattern with small object set. Then SPARE continues to grow
+%the object set until its temporal dimension is about to be non-decomposable (Definition 5).
+%Therefore both TRPM and SPARE tends to find the ``largest'' valid
+%patterns.
+%
+%In terms of the meaningfulness, we believe that all patterns that conformed
+%to the parameters need to be outputted. 
+%This is because the parameters
+%
+%
+%We see two questions derived from this concern. First, do we need
+%to output all ${1000 \choose M}$ patterns if $1000$ taxis form a true GCMP
+%pattern? Our answer to this question is no. Therefore, the nature of both
+%of our TRPM and SPARE algorithms tend to only output the patterns containing 
+%larger sets of objects. To see this, in Algorithm 1, TRPM starts with an temporal invalid
+%pattern and continues to shrink its object set while growing its temporal dimension.
+%TRPM stops as soon as the object become valid. In an inverse way, in Algorithm 3, 
+%SPARE starts with a pattern with small objects and continues to grow its object set
+%while reducing its temporal dimension. SPARE stops as soon as the pattern is about
+%to be temporally invalid. Therefore, both TRPM and SPARE would prefer to output
+%larger pattern.
+%
+%
+%%
+%%We agree with the reviewer that if no other parameters are given, the maximum number
+%%of patterns discovered could be as large as ${ \mathbb{O} \choose M}$, which may
+%%be less interesting to users.
+%However, such a case rarely occurs due to two reasons. First,
+%in real trajectory mining, parameter $M$
+%is associated with temporal parameters $K,L,G$ and they jointly prune many false
+%patterns. Second, the nature of our solutions prefer 
+%a larger pattern when possible~\footnote{TRPM shrinks an invalid larger pattern until it is valid.
 SPARE grows a valid smaller pattern until it is about to be invalid.
 Therefore both algorithms tend to find larger patterns.}.
-For example, if $(o_1,o_2,o_3)$ is 
-a pattern and $M = 2$, 
-then both TRPM and SPARE only output $(o_1,o_2,o_3)$ but not
-any of its subsets. This effectively compresses smaller patterns.
-
-In addition, when the temporal parameters $K,L,G$ are given,
-a larger $M$ actually decreases the number of resulted patterns. 
-This is because there are less patterns having more than $M$ objects. 
-As shown in Figures 7 (a)(g)(m), a larger $M$ actually reduces the running time of both TRPM and SPARE.
+%For example, if $(o_1,o_2,o_3)$ is 
+%a pattern and $M = 2$, 
+%then both TRPM and SPARE only output $(o_1,o_2,o_3)$ but not
+%any of its subsets. This effectively compresses smaller patterns.
+%
+%In addition, when the temporal parameters $K,L,G$ are given,
+%a larger $M$ actually decreases the number of resulted patterns. 
+%This is because there are less patterns having more than $M$ objects. 
+%As shown in Figures 7 (a)(g)(m), a larger $M$ actually reduces the running time of both TRPM and SPARE.
 }
@@
 on spatiotemporal mining could be similar to GCMP.
-However, these domain-specific constraints 
-are nontrivial to be generalized. Since our GCMP model as well as solutions
-do not leverage domain knowledge, we can support
-pattern discovery in a broader context. We add the discussion in Section 2.3.
+However, the domain-specific constraints (such as directions in road networks)
+are nontrivial to be generalized. Since our GCMP model and technical solutions
+do not leverage the domain knowledge, we can support
+pattern discovery in broader scenarios such as user check-in history in social networks, visitor movements in a building and 
+passenger flows in a city. We also add the discussion in Section 2.3.
 }

### 2016-08-29 ReviewComments/review3.tex
Revised response
some more responses

@@
 \response{
-We agree that leveraging more advanced Spark features
-could further improve the performance of our solutions. 
-We do not heavily leverage these features because 
-we wish to focus on designing parallel GCMP mining algorithms.
-%to provide a general parallel framework which does not tie to Spark.
-Nevertheless, we are in progress in developing
-a better open-sourced version with Spark-tailored optimization.
+We thank the reviewer for suggesting a better way of implementing 
+the baseline algorithm (i.e., TRPM). However, this could
+hardly be done after our investigations. The major reason is
+that current version of Spark SQL (i.e., 1.6.2 released in June)
+does not support the User Defined Aggregate Function (UDAF) on window
+function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
+our Line sweep algorithm (Algorithm 1) using Spark SQL 
+primitive aggregates (e.g., sum, avg, rank and nth-tile)
+is beyond our abilities.
 
-In the revision, we try to add a DataFrame based TRPM solution 
-which aims to leverage the window functions from Spark-SQL.
-However, to the best of our efforts, we could not achieve this goal in a short time. 
-The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
-in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
-our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
-is nontrivial. Nonetheless, we expect less performance
-boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
-properly reducible, where Spark system would fail to leverage the partial aggregates
-across multiple windows. As a result, it would be equivalent to our current TRPM
-solution where windows are processed independently in parallel.
+Further, we believe the performance boost on TRPM from Spark SQL
+is very limited. The reason is that our 
+Line Sweeping Mining algorithm (Algorithm 1) is not a 
+properly reducible function. That is, the result of a 
+smaller window could not be used to compute the result of a larger
+window. In such a case, Spark SQL has to process each
+window independently in parallel, which is equivalent to our TRPM implementation.
+%We agree that leveraging more advanced Spark features
+%could further improve the performance of our solutions. 
+%We do not heavily leverage these features because 
+%we wish to focus on designing parallel GCMP mining algorithms.
+%%to provide a general parallel framework which does not tie to Spark.
+%Nevertheless, we are in progress in developing
+%a better open-sourced version with Spark-tailored optimization. 
+%In the revision, we try to add a DataFrame based TRPM solution 
+%which aims to leverage the window functions from Spark-SQL.
+%However, to the best of our efforts, we could not achieve this goal in a short time. 
+%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
+%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
+%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
+%is nontrivial. Nonetheless, we expect less performance
+%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
+%properly reducible, where Spark system would fail to leverage the partial aggregates
+%across multiple windows. As a result, it would be equivalent to our current TRPM
+%solution where windows are processed independently in parallel.
 %TRPM although can be modeled using window functions over data frame, the aggregates

### 2016-08-30 ReviewComments/meta.tex
revision comments

@@
 techniques. 
-Although the idea of star-partition and apriori-partition are well-known, 
+Although the idea of star partition and apriori enumeration are well-known, 
 linking them together to solve the problem in trajectory domain has not been attempted before.
 Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
-anti-monotonicity) which have not been proposed before.
+anti-monotonicity) which have not been previously proposed.
 }
@@
 
-\response { The evaluations are added in Table 7 and Figure 8.
-Due to the space limit, we only provide the summary of performance skew in Table 9 (i.e., the longest time-taking task vs stand deviation of each task).
-As per our analysis, the skew is limited because every stars are of similar sizes.
-The references of apriori and star partition are added accordingly in Section 5.1 and Section 5.2.
+\response { 
+Similar responses with Response 6, 7 and 9.
 }

### 2016-08-30 ReviewComments/review1.tex
revision comments

@@
 would benefit our solutions.
-In fact, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine).
+Indeed, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine).
 As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
-Using the DAG execution engine, we are able to adopt a Map-Planning-Reduce work flow.
+Using the DAG execution engine, we are able to augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow.
 With the support of in-memory caching of RDDs,
@@
 As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).
-If without Spark's features, such an optimization would be hardly possible.
+If without Spark's features, such an optimization would be hardly possible, but SPARE-RD is still more efficient than the baseline TRPM.
 
 We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
-%
-%We are unsure about whether adapting other features in Spark (e.g., Spark streaming, Spark SQL, Spark Graph) would help to improve our solutions. Since they are solutions 
-%%
-%
-%In this work, we do not include 
-%these optimization in-depth because we set out focus 
-%on solving the challenges in parallelizing the 
-%GCMP mining algorithms.
-%We are also in progress of open-sourcing a Spark-tailored
-%version of SPARE.
 }

### 2016-08-30 ReviewComments/review2.tex
revision comments

@@
 mining Gap-restricted Sequential Patterns (GSP). However, the novelty
-of this paper is not merely on introducing the gap-constraint to the
+of this paper is not merely on introducing the gap-constraint to the generalized
 co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
@@
 these constraints, users are able to define a more accurate pattern
-which are free from the anomalies (e.g., loss-connection anomaly as in Figure 2).
+which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).
 
-Besides, the nature of GSP and GCMP are different. The goal of GSP 
+Besides, the essence of GSP and GCMP are different. The goal of GSP 
 is to find the sequences which conform to the gap constraint and occur frequently.
 When counting the occurrence of a sequence in GSP, the object
-which a sequence belongs to does not matter. Therefore, for
-a pattern result in GSP, it cannot guarantee either the 
-distinction of involved objects or the closeness of those objects.
-In contrast, GCMP has requirements on both the spatial closeness 
+which a sequence belongs to does not matter. Therefore, 
+in a GSP result, the involved objects may be neither
+ distinct nor close.
+In contrast, GCMP imposes requirements on both the spatial closeness 
 of objects and the number of distinct objects.
 Due to the unawareness of objects, techniques that are used in GSP 
-cannot be directly applied on GCMP. We also summarize the difference
+cannot be directly applied on GCMP. We summarize this difference
 in Section 2.5.
@@
 prohibits outputting $c$'s subset. Similarly, in the Apriori Enumerator (Algorithm 3)
-of SPARE, a pattern $c$ is outputted if non of its superset would become a valid pattern (Line 12-14).
-This prohibits the output $c$ to be a subset of any patterns.
-These mechanisms effectively condense the output size by subsuming smaller
+of SPARE, a pattern $c$ is outputted if none of its supersets could become a valid pattern (Line 12-14).
+This ensures the output $c$ is not a subset of some pattern.
+These mechanisms effectively condense the output by subsuming smaller
 patterns using their supersets.
@@
 impose stringent constraints via $M,K,L,G$. This would further reduces 
-the number of potential patterns.
+the size of the output.
 %On the other hand, in reality, if users wish to detect ``anomalous'' patterns,
@@
 
-\response{We agree that domain-specific constraints
-on spatiotemporal mining could be similar to GCMP.
-However, the domain-specific constraints (such as directions in road networks)
-are nontrivial to be generalized. Since our GCMP model and technical solutions
+\response{We understand that spatiotemporal mining with domain-constraints
+looks similar to GCMP.
+However, those techniques often heavily utilize the domain knowledge (such as
+directions in road networks) which are nontrivial to be generalized.
+Differently, since our GCMP model and technical solutions
 do not leverage the domain knowledge, we can support
-pattern discovery in broader scenarios such as user check-in history in social networks, visitor movements in a building and 
+pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
 passenger flows in a city. We also add the discussion in Section 2.3.

### 2016-08-30 ReviewComments/review3.tex
revision comments

@@
 hardly be done after our investigations. The major reason is
-that current version of Spark SQL (i.e., 1.6.2 released in June)
+that the current version of Spark-SQL (i.e., 1.6.2 just released in June)
 does not support the User Defined Aggregate Function (UDAF) on window
 function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
-our Line sweep algorithm (Algorithm 1) using Spark SQL 
+our Line Sweep algorithm (Algorithm 1) using Spark-SQL 
 primitive aggregates (e.g., sum, avg, rank and nth-tile)
@@
 
-Further, we believe the performance boost on TRPM from Spark SQL
+Further, we believe the performance boost on TRPM from Spark-SQL
 is very limited. The reason is that our 
-Line Sweeping Mining algorithm (Algorithm 1) is not a 
+Line Sweep Mining algorithm (Algorithm 1) is not a 
 properly reducible function. That is, the result of a 
 smaller window could not be used to compute the result of a larger
-window. In such a case, Spark SQL has to process each
+window. In such a case, Spark-SQL has to process each
 window independently in parallel, which is equivalent to our TRPM implementation.
@@
 
-\response{We add Table 7 to include vcore-seconds 
-and RDD memory usage for both TRPM and SPARE. We also add a clear description on partitions in Section 6.
+\response{In our implementation, we take a fixed 486 partitions (Section 6)
+for each RDD. The partition number is determined based on 
+the parallel tuning guide by Cloudera~\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}.
+To study the load balance, we revise Section 6.2.2 by comparing TRPM, SPARE with random 
+task allocation and SPARE with best-fit task allocation (Section 5.3). We present
+the summary of the execution time for each method on longest job, shortest job and standard
+deviation of all jobs in Table 9. As the table show, SPARE has a better load balance (low deviation)
+than SPARE-RD which indicates the effectiveness of the best-fit strategy. Further, TRPM
+generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition.
+Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.
+
+Next, we add Table 7 (Section 6.1) to compare
+the resource usage (e.g., Vcore-seconds, Memory and Running Time) between SPARE and TRPM.
+The table tells that both SPARE and TRPM are resource efficient.
+In particular, the RDDs for both SPARE and TRPM only take less than 20\% of 
+the available memory. This infers the potential of SPARE and TRPM in handling 
+even larger trajectories with current system resources.
+%
+%include vcore-seconds 
+%and RDD memory usage for both TRPM and SPARE. 
+%As the table show, both TRPM and SPARE are resource efficient. 
+%The maintained RDDs only takes less than 20\% of the entire memory. 
+%We also add a clear description on partitions in Section 6.
 }
@@
 
-\response{We complement Figure 8 with the breakdown cost of TRPM. This
-comparison showcases the benefits of both Star Partition (in mapshufle phase)
-and Apriori Enumeration (in reduce phase) of SPARE.
+\response{We complement Figure 8 (Section 6.1) by including the breakdown cost of TRPM. 
+In SPARE, star partition takes place in the Map-Shuffle phase while
+Apriori enumeration takes place in the Reduce phase. As shown in the
+new Figure 8, both star partition and apriori enumeration contribute to 
+the final performance gain of SPARE. In particular, in the Map-Shuffle phase,
+SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
+less data are transformed and shuffled in the star partition.
+In the Reduce phase, SPARE saves 46\%-81\% time as compared to TRPM. This confirms 
+the efficiency of our Apriori enumerator with various optimization (e.g., sequence simplification,
+anti-monotonicity and forward closure checking).
 }
@@
 
-\response{We thank the reviewer for the correction. We have changed many unprofessional terms.
+\response{We thank the reviewer for the correction. We have changed these unprofessional terms.
 }
@@
 
-\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
+\response{ We use all cores in the single node to conduct the experiment. We revise the description in Section 6.2.3.
 }

### 2016-08-30 sec6_experiment.tex
revision comments

@@
 \revised{
-\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken by TRPM and SPARE under the default setting.
-Both TRPM and SPARE are resource efficient as they only occupy less than 20\%
-of the available memory which reveals their potential to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues
-to the set of effective pruning procedures.
+\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken 
+by TRPM and SPARE under the default setting. Both TRPM and SPARE are 
+resource efficient as they only occupy less than 20\% 
+of the available memory (i.e., 270GB) . Again, SPARE outperforms TRPM in both the execution time and the memory usage.
+
+%The result also reveals the potential of the two solutions to handle larger trajectories.
+Again, SPARE outperforms TRPM in both execution time and memory usage which dues to the set of effective pruning procedures.
 
@@
 \multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
-\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ \cline{2-5} 
-                                       & SPARE           & 334                               & 47,430                 & 8,613                \\ \hline
-\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ \cline{2-5} 
-                                       & SPARE           & 480                               & 49,835                 & 14,369               \\ \hline
-\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ \cline{2-5} 
-                                       & SPARE           & 812                               & 89,390                 & 35,912               \\ \hline
+\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ %\cline{2-5} 
+                                       & SPARE           & 237                               & 33,638                 & 8,613                \\ \hline
+\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ %\cline{2-5} 
+                                       & SPARE           & 341                               & 35,343                 & 14,369               \\ \hline
+\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ %\cline{2-5} 
+                                       & SPARE           & 580                               & 68,580                & 35,912               \\ \hline
 \end{tabular}
@@
 \centering \small
-\begin{tabular}{|c|c|c|c|c|}
+%\begin{tabular}{|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
+%                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
+%Shopping                 & 295              & 41         & 237             & 21       \\ \hline
+%GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
+%Taxi                     & 681              & 147        & 580             & 96       \\ \hline
+%\end{tabular}
+\begin{tabular}{|l|c|c|c|c|}
 \hline
-\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
-                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
-Shopping                 & 295              & 41         & 237             & 21       \\ \hline
-GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
-Taxi                     & 681              & 147        & 580             & 96       \\ \hline
+\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
+\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
+\multirow{3}{*}{Shopping}              & TRPM            &     426                          & 597                 & 35 
+\\ %\cline{2-5} 
+                                       & SPARE-RD          & 122                               &  295             & 41
+\\% \cline{2-5}                                        
+									   & SPARE           &  134                              &   237               & 21
+\\ \hline                                
+\multirow{3}{*}{GeoLife}              & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
+                                       & SPARE-RD          &  38                               &   484               & 148
+\\ %\cline{2-5}                                        
+									   & SPARE           &   107                             &     341             & 96
+\\ \hline
+\multirow{3}{*}{Taxi}              & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
+                                       & SPARE-RD          & 122                               & 681                 & 109
+\\ %\cline{2-5}                                        
+									   & SPARE           &   134                             &  580                & 56               
+\\ \hline
 \end{tabular}
-  \caption{Statistics of execution time (in seconds) among executors.}
+  \caption{Statistics of execution time (in seconds) among all executors.}
   \label{tbl:strags}
@@
 In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
-Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD \revised{with TRPM as comparison}.
+Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
+for SPARE and SPARE-RD \revised{with TRPM as comparison}.
 We observe that the map and shuffle time of SPARE and SPARE-RD are identical .
 The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
-\revised{We further observe that TRPM takes more time in each phase, which confirms the efficiency of Star Partition and Apriori Enumeration.} We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
+\revised{Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
+efficiency of the star partition and apriori enumeration.} 
+\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}.
+As the table shows, SPARE produces more balanced jobs
+than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
+maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
+However, TRPM still takes much longer time than SPARE algorithms.}
+%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+%We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
 Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

### 2016-08-31 ReviewComments/response.tex
Revised response 1

@@
 
+\section{Response to Reviewer 1}
+
+\textbf{1.1} \emph{The main con that I've spotted is the fact that the algorithm might have been
+more nicely framed also within the Spark environment by taking advantage of
+the various possibilities offered by it (e.g. caching of RDDs)}
+
+\textbf{Response:} We agree with the reviewer that utilizing advanced Spark features
+would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features: (1) caching of RDDs and (2) DAG execution engine.
+
+As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
+The best-fit strategy allocates the largest unassigned star to the most empty reducer, which balances the workload for each reducer.
+Since the strategy needs to know the sizes of all stars, it takes place after the map-phase and before the reduce the phase.
+Utilizing Spark's DAG execution engine, we can easily augment traditional map-reduce workflow to the map-planning-reduce workflow.
+Furthermore, we can utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
+during the planning phase and reuse them in the reduce phase.
+
+In Section 6.2.2 Figure 8, we validate the benefits of adopting these Spark features. In Figure 8, we compare SPARE with
+SPARE-RD. SPARE-RD is identical to SPARE except without best-fit strategy. Benefit from the two Spark features, planning
+phase only takes around 4\% of SPARE's total execution time. With the planning phase, SPARE is 15\% faster compared to SPARE-RD.
+
+%As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
+Using the DAG execution engine, we are able to augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow.
+With the support of in-memory caching of RDDs,
+%the Map results need not to be recomputed after the planning phase.
+As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).
+If without Spark's features, such an optimization would be hardly possible, but SPARE-RD is still more efficient than the baseline TRPM.
+
+We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
+
 \input{review1}

### 2016-08-31 ReviewComments/review2.tex
Revised response 1

@@
 
-\emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
+\textbf{2.1} \emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
 on consecutive segments is well-known
@@
 
-\response{
+\textbf{Response:}
 We admit that the gap parameter is also used in
-mining Gap-restricted Sequential Patterns (GSP). However, the novelty
+mining Gap-restricted Sequential Patterns (GSP). 
+However, the novelty of this paper lies
+on the one-stop solution of mining co-movement patterns.
+In modeling, we provide the generalize co-movement pattern to
+alleviate the troubles
+is not merely on introducing the gap-constraint.
+Instead, we provide a one-stop solution for mining co-movement patterns. With
+our
+
+However, the novelty
 of this paper is not merely on introducing the gap-constraint to the generalized
-co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
-for mining various co-movement patterns with flexible constraints. With
+co-movement pattern. 
+Instead, we provide a one-stop solution (both in modeling and in technical)
+for mining various co-movement patterns with flexible constraints.
+
+This solution not only alleviate the cumbersome for designing each
+individual patterns, but also
+
+ With
 these constraints, users are able to define a more accurate pattern
@@
 in Section 2.5.
-%
-%When counting the occurrence of a sequence, 
-%the object the sequence belongs does not matter. 
-%Therefore, a pattern in FS may corresponds to any objects where
-%the closeness or distinction of objects are not statisfied. Due
-%to this difference, FS solutions cannot be directly applied on GCMP.
-%
-%
-%We agree with the reviewer that gap parameter is 
-%also used in the Sequence Mining problem. However, 
-%Sequence mining problem is different from the GCMP mining problem. 
-%The major difference is that in sequence mining problem, the object
-%itself is not considered. In particular, the frequency of a sequence is 
-%counted as the occurrence of a sequence. Thus, an object may
-%contribute multiple occurrence of a sequence. Conversely, GCMP
-%in addition to impose the gap parameter in the temporal constraint, also 
-%require the objects in the pattern to be close. Due to this difference,
-%Sequence mining solutions cannot support GCMP mining.
-%
-%that the gap parameter is an old concept. 
-%However, the novelty of GCMP lies in the unification and generalization of existing patterns which provide
-%a one-stop solution for co-movement pattern detection. And the
-%gap parameter merely is used for solving the loose-connection anomaly (as in Figure 2). 
-%
-%Moreover, the problem of Sequence mining is also different from Trajectory mining.
-%The major difference is that sequence mining do not consider the distinction between
-%objects and the closeness among objects. This makes the solutions in Sequence mining
-%unable to be applied in GCMP. We summarize these points in Section 2.5 of the revised paper.
-%
-%We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
-%modeling lies in unifying existing movement patterns in the trajectory domain. 
-%The gap parameter is naturally introduced to 
-%solve the loose-connection anomaly (as in Figure 2).
-%%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
-%In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
-%and distinguish the sequential mining problem with our problem. 
-}
 
@@
 
-\emph{Regarding the second weak point, one line of related work is the superimposition
+\emph{Regarding the second weak points, one line of related work is the superimposition
 of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}

### 2016-09-01 ReviewComments/meta.tex
Another draft
Proof read before submiting

@@
 
-\emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}
+\textbf{M.1} \emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}
 
-\response{In addition to the points in Response 2, another novelty of our work lies in the 
+\textbf{Response:} In addition to the points in the response of comments 2.1, another novelty of our work lies in the 
 techniques. 
@@
 anti-monotonicity) which have not been previously proposed.
-}
 
-\emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
+\textbf{M.2} \emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
 on the motivation.}
 
-\response {Similar responses with Response 3. }
+\textbf{Response:} Addressed in the response for comments 2.2.
 
-\emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce.
+\textbf{M.3} \emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce.
 Spark has capabilities beyond MapReduce such as window functions.
@@
 
-\response{Similar responses with Response 1 and 5. }
+\textbf{Response:} Addressed in the response for comments 1.1 and 3.1.
 
-\emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew.
+\textbf{M.4} \emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew.
 Also provide details about how star partitioning and a priori pruning contribute to performance.
@@
 
-\response { 
-Similar responses with Response 6, 7 and 9.
-}
+\textbf{Response:} Addressed in the response for comments 3.2, 3.3, 3.4 and 3.6.

### 2016-09-01 ReviewComments/review2.tex
Another draft
Proof read before submiting

@@
 
-\textbf{Response:}
-We admit that the gap parameter is also used in
-mining Gap-restricted Sequential Patterns (GSP). 
-However, the novelty of this paper lies
-on the one-stop solution of mining co-movement patterns.
-In modeling, we provide the generalize co-movement pattern to
-alleviate the troubles
-is not merely on introducing the gap-constraint.
-Instead, we provide a one-stop solution for mining co-movement patterns. With
-our
+\textbf{Response:} We admit that the gap parameter
+is also used in mining Gap-restricted Sequential Patterns (GSP). 
+However, our work is the first to introduce the gap concept 
+in co-movement mining to resolve the
+loose-connection anomaly (as shown in Figure 2).  
+Moreover, we also provide
+a unified model to capture existing pattern models which 
+is also not proposed before.
+%
+%The novelty of our modeling
+%is bi-folded. First, we unify existing co-movement patterns in
+%a GCMP model. Second, we use the gap-constraint to avoid
+%the loose-connection anomaly (as shown in Figure 2) which 
+%is suffered by existing patterns.
 
-However, the novelty
-of this paper is not merely on introducing the gap-constraint to the generalized
-co-movement pattern. 
-Instead, we provide a one-stop solution (both in modeling and in technical)
-for mining various co-movement patterns with flexible constraints.
+%
+%We admit that the gap parameter is also used in
+%mining Gap-restricted Sequential Patterns (GSP). 
+%However, the novelty of this paper lies
+%on the one-stop solution of mining co-movement patterns.
+%In modeling, we provide the generalize co-movement pattern to
+%alleviate the troubles
+%is not merely on introducing the gap-constraint.
+%Instead, we provide a one-stop solution for mining co-movement patterns. With
+%our 
+%
+%However, the novelty
+%of this paper is not merely on introducing the gap-constraint to the generalized
+%co-movement pattern. 
+%Instead, we provide a one-stop solution (both in modeling and in technical)
+%for mining various co-movement patterns with flexible constraints.
+%
+%This solution not only alleviate the cumbersome for designing each
+%individual patterns, but also 
+%
+% With
+%these constraints, users are able to define a more accurate pattern
+%which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).
 
-This solution not only alleviate the cumbersome for designing each
-individual patterns, but also
+Besides, GSP and GCMP are designed with different goals. Thus it is infeasible
+to model GCMP using GSP. 
+In particular, the goal of GSP 
+is to find the frequently occurred subsequences which conform to the gap constraint.
+This definition ignores the relationships among the involved objects. 
+As a consequence, the mined GSP results cannot guarantee the spatial closeness of the involved
+objects, which contradicts with \emph{closeness} requirement of GCMP (Section 3 Definition 2). 
+For example, in the sample trajectory database in Figure 1, 
+the most frequent temporal sequence for GSP is
+$(1,2,3,4,5,6)$ because it appears in all trajectories. 
+However, the involved objects $\{o_1,o_2,o_3,o_4,o_5,o_6\}$ are NOT all
+spatially close at any of the timestamps thus these objects do not form a proper GCMP.
+We summarize this difference in Section 2.5.
 
- With
-these constraints, users are able to define a more accurate pattern
-which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).
+%
+%
+%When counting the occurrence of a subsequence, the object
+%which the subsequence belongs to does not matter. This allows an object
+%to contribute multiple times for a subsequence's occurrence (e.g., in ``$o_1:ABCDABC$", $o_1$
+%contributes twice for the subsequence $ABC$)
+%
+%As a result, GSP may double count an object if the object's sequence 
+%has two identical subsequence.
+%
+%the involved objects may be neither
+% distinct nor close.
+%In contrast, GCMP imposes requirements on both the spatial closeness 
+%of objects and the number of distinct objects.
+%Due to the unawareness of objects, techniques that are used in GSP 
+%cannot be directly applied on GCMP. We summarize this difference
+%in Section 2.5.
 
-Besides, the essence of GSP and GCMP are different. The goal of GSP 
-is to find the sequences which conform to the gap constraint and occur frequently.
-When counting the occurrence of a sequence in GSP, the object
-which a sequence belongs to does not matter. Therefore, 
-in a GSP result, the involved objects may be neither
- distinct nor close.
-In contrast, GCMP imposes requirements on both the spatial closeness 
-of objects and the number of distinct objects.
-Due to the unawareness of objects, techniques that are used in GSP 
-cannot be directly applied on GCMP. We summarize this difference
-in Section 2.5.
-
-\emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
+\textbf{2.2} \emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
 we really interested in all sets of movements beyond a cardinality of size $M$? 
@@
 
-\response{We appreciate the reviewer's concerns on the 
+\textbf{Response:} We appreciate the reviewer's concerns on the 
 size of the output. 
@@
 %As shown in Figures 7 (a)(g)(m), a larger $M$ actually reduces the running time of both TRPM and SPARE.
-}
 
-\emph{Regarding the second weak points, one line of related work is the superimposition
+\textbf{2.3} \emph{Regarding the second weak points, one line of related work is the superimposition
 of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}
 
-\response{We understand that spatiotemporal mining with domain-constraints
-looks similar to GCMP.
-However, those techniques often heavily utilize the domain knowledge (such as
-directions in road networks) which are nontrivial to be generalized.
-Differently, since our GCMP model and technical solutions
-do not leverage the domain knowledge, we can support
-pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
-passenger flows in a city. We also add the discussion in Section 2.3.
-}
+\textbf{Response:} We understand that spatiotemporal mining with 
+domain-specific constraints may look similar to GCMP.
+However, we are unaware of existing works on the same GCMP model
+ with domain-specific constraints.
+
+Generally, patterns defined with domain-specific constraints are hard to be generalized.
+This is because constraints available in one domain (e.g., road direction in road networks)
+are often not available in other domains (e.g., no road directions available for visitor movements in a shopping mall). Nevertheless,
+when deploying on a specific domain, our GCMP solutions are amendable to
+incorporate more domain-specific constraints (i.e., rewrite the $\mathtt{sim}$ operation in Algorithm 3). 
+We summarize the discussion in Section 2.3.
+
+%often rely on the specific knowledge in that domain (e.g.,
+%directions in road networks and maximum speed of traffic), which
+%are hard to be generalized. In contrast, GCMP's constraints
+%are on spatial (i.e., closeness) and temporal (e.g., max gap and min duration), 
+%which can be generalized for all trajectories. For example,
+%mining techniques on road networks fails to find patterns
+%in  
+%
+%However, existing techniques on spatiotemporal mining with domain-specific  
+%
+%
+%those techniques often heavily utilize the domain knowledge (such as
+%directions in road networks) which are nontrivial to be generalized.
+%Differently, since our GCMP model and technical solutions
+%do not leverage the domain knowledge, we can support
+%pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
+%passenger flows in a city.

### 2016-09-01 ReviewComments/review3.tex
Another draft
Proof read before submiting

--- 2016-08-29 ReviewComments/review3.tex
@@
 \section{Responses to Reviewer 3}
-\emph{Though the implementation references Spark as the implementation
+\textbf{3.1:} \emph{Though the implementation references Spark as the implementation
 platform (as it also reflects in github repo provided), the algorithm design is
@@
 been noted that this is a very efficient way to execute window functions in
-Spark}
+Spark.}
 
-\response{
+\textbf{Response:}
 We thank the reviewer for suggesting a better way of implementing 
-the baseline algorithm (i.e., TRPM). However, this could
-hardly be done after our investigations. The major reason is
-that current version of Spark SQL (i.e., 1.6.2 released in June)
-does not support the User Defined Aggregate Function (UDAF) on window
-function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
-our Line sweep algorithm (Algorithm 1) using Spark SQL 
-primitive aggregates (e.g., sum, avg, rank and nth-tile)
+the baseline algorithm (i.e., TRPM). By utilizing window functions,
+TRPM could be rewritten as in the following pseudo-code:
+\begin{equation*}
+\begin{aligned}
+ \mathtt{WindowSpec}\ ws := \mathtt{Window}&.\mathtt{orderBy}('time') \\
+ 				&.\mathtt{rangeBetween}(0, \eta); \\
+ \mathtt{Pattern}\ pt :=  LineSweep&('clusters').\mathtt{over}(ws); 
+\end{aligned}
+\end{equation*}
+
+However, the algorithm is challenging
+to be implemented after our investigations. The major reason is
+that, in current version of Spark-SQL~\footnote{Both the stable Spark 1.5.2 and the newly released Spark 1.6.2}, 
+User Defined Aggregate Function (UDAF) on window operator is not supported~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. 
+Without UDAF, we cannot attach the $\mathtt{over}$ keyword to
+the Line Sweep algorithm. A workaround is to implement the Line Sweep using only Spark-SQL primitive aggregate 
+functions (e.g., sum, avg, rank and nth-tile). But it
 is beyond our abilities.
+%
+%we cannot integrate the Line Sweep algorithm with window functions 
+%(i.e., with the $\mathtt{over}$ keyword). On the other hand,
+%implementing the Line Sweep algorithm (Algorithm 1) using Spark-SQL 
+%primitive aggregates (e.g., sum, avg, rank and nth-tile)
+%is beyond our abilities.
 
-Further, we believe the performance boost on TRPM from Spark SQL
-is very limited. The reason is that our 
-Line Sweeping Mining algorithm (Algorithm 1) is not a 
-properly reducible function. That is, the result of a 
-smaller window could not be used to compute the result of a larger
-window. In such a case, Spark SQL has to process each
+On the other hand, we believe the performance boost on TRPM from Spark-SQL
+would be very limited. The reason is that our 
+Line Sweep algorithm (Algorithm 1) is not a 
+distributive function. 
+That is the result over an input cannot be constructed from
+the result over a subset of the input. This indicates 
+that no partial results can be shared among all windows.
+In such a case, Spark-SQL has to process each
 window independently in parallel, which is equivalent to our TRPM implementation.
@@
 %We wish to convince the reviewer that current TRPM implementation is reasonable.
-}
 
-\emph{In particular, it would be great to provide the
+\textbf{3.2:} \emph{Most implementations
+on Hadoop and Spark are very sensitive to data partitions, i.e. prone to data
+skewing issues. It seems that the (starpartition)
+implementation does not take
+this into account, and only use the default partitioning. It would be very helpful
+to have a discussion on this topic.}
+
+\textbf{Response:}  We study the skewness by examining the load balance of each algorithm.
+We revise Section 6.2.2 by comparing SPARE with different data partition strategies.
+In particular, we compare SPARE which adopts a best-fit strategy (Section 5.3) and SPARE-RD
+which adopts the default random partition strategy.
+We present the summary of the execution time for each method on the longest job, the shortest job and standard
+deviation of all jobs in Table 9. As the table shows, SPARE has a better load balance (low deviation)
+than SPARE-RD which indicates the effectiveness of the best-fit strategy. 
+%Further, TRPM generally keeps a low deviation.
+This is because that TRPM always adopts the equal-size (i.e.
+$\eta$) partition.
+Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.
+
+%We revise Section 6.2.2 by comparing TRPM, SPARE with random 
+%task allocation and SPARE with best-fit task allocation (Section 5.3). We present
+%the summary of the execution time for each method on longest job, shortest job and standard
+%deviation of all jobs in Table 9. As the table show, SPARE has a better load balance (low deviation)
+%than SPARE-RD which indicates the effectiveness of the best-fit strategy. Further, TRPM
+%generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition.
+%Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.
+
+\textbf{3.3:} \emph{In particular, it would be great to provide the
 difference in the number of partitions/splits, the amount of processing and
@@
 
-\response{We add Table 7 to include vcore-seconds 
-and RDD memory usage for both TRPM and SPARE. We also add a clear description on partitions in Section 6.
-}
+\textbf{Response:} In our implementation, we take a fixed 486 partitions (Section 6)
+for each RDD. The partition number is determined according to
+the parallel tuning guide by Cloudera~\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}: there are  $3\times 54=162$ cores and each core is able to processes 3 partitions~\footnote{This number may differ for other CPU models, and can be determined empirically.}
+by multithreading.
 
-\emph{A plot that breaks down the performance gain by each method would
+Next, we add Table 7 (Section 6.1) to compare
+the resource usage (e.g., Vcore-seconds, Memory and Running Time) between SPARE and TRPM.
+The table tells that both SPARE and TRPM are resource efficient.
+In particular, the RDDs for both SPARE and TRPM only take less than 20\% of 
+the available memory. This infers the potential of SPARE and TRPM in handling 
+even larger trajectories with our current cluster resources.
+
+\textbf{3.4:} \emph{A plot that breaks down the performance gain by each method would
 be greatly appreciated by the readers.}
 
-\response{We complement Figure 8 with the breakdown cost of TRPM. This
-comparison showcases the benefits of both Star Partition (in mapshufle phase)
-and Apriori Enumeration (in reduce phase) of SPARE.
-}
+\textbf{Response:} We include the analysis of
+the breakdown cost of SPARE by taking TRPM as
+a reference in Figure 8. 
+SPARE and TRPM algorithms are of the similar structure: partitioning (Star partition v.s. $\eta$-replicate
+partition) is in the map-shuffle phase, and  mining (Apriori Enumeration v.s. Line Sweep) 
+is in the reduce phase. In our experiment, we treat the execution time
+for each phase as the cost of the corresponding methods.
 
-\emph{Some choices of words may need to be reconsidered: for example, "a bunch
+As shown in Figure 8,
+both star partition and apriori enumeration contribute to 
+the final performance gain of SPARE. In particular, in the Map-Shuffle phase,
+SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
+less data are transformed and shuffled in the Star partition.
+In the Reduce phase, SPARE saves 46\%-81\% time as compared to TRPM. This confirms 
+the efficiency of our Apriori enumerator.
+
+% with various optimization (e.g., sequence simplification, anti-monotonicity and forward closure checking).
+
+\textbf{3.5} \emph{Some choices of words may need to be reconsidered: for example, ``a bunch
 of" might not be appropriate in a technical paper.}
 
-\response{We thank the reviewer for the correction. We have changed many unprofessional terms.
-}
+\textbf{Response:} We have changed these unprofessional terms.
 
-\emph{References to star partitioning and apriori pruning are missing. Though these
-are well known, they need to clearly cited. At least the following reference is
-missing:}
+\textbf{3.6} \emph{References to star partitioning and apriori pruning are missing. Though these
+are well known, they need to  be clearly cited.}
 
-\response{We add the corresponding references in Section 5.1 and Section 5.2.}
+\textbf{Response:} We add the corresponding references in Section 5.1 and Section 5.2 when we
+describing our algorithms.
 
-\emph{In "In contrast, when utilizing the multicore
-environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was "multicore"
+\textbf{3.7} \emph{In ``In contrast, when utilizing the multicore
+environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was ``multicore"
 referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}
 
-\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
-}
+\textbf{Response:} We use all cores in the single node (i.e., 4 executors each with 3 cores) to conduct the experiment. We revise the description in Section 6.2.3.
 
-\emph{The computation of "eta" was slightly different than that in the paper}
+\textbf{3.8} \emph{The computation of "eta" was slightly different than that in the paper}
 
-\response{
-We have updated the GitHub repository to rectify the typo in the equation.}
+\textbf{Response:} We have updated the GitHub repository to rectify the typo in the equation.

### 2016-09-02 ReviewComments/response.tex
Another draft
Proof read before submiting
More revisement

@@
 \usepackage{url}
+\usepackage{amsmath}
 \newcounter{ctResp}
@@
 \textbf{Response:} We agree with the reviewer that utilizing advanced Spark features
-would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features: (1) caching of RDDs and (2) DAG execution engine.
+would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features: (1) caching of RDDs and (2) DAG execution engine, to achieve speedups.
 
 As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
-The best-fit strategy allocates the largest unassigned star to the most empty reducer, which balances the workload for each reducer.
-Since the strategy needs to know the sizes of all stars, it takes place after the map-phase and before the reduce the phase.
-Utilizing Spark's DAG execution engine, we can easily augment traditional map-reduce workflow to the map-planning-reduce workflow.
-Furthermore, we can utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
+The best-fit strategy allocates the largest unassigned star to the most empty reducer, which balances the workloads for each reducer.
+Since the strategy needs to know the sizes of all stars, it takes place after the Map phase and before the Reduce phase.
+Leveraging Spark's DAG execution engine, we can easily augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow.
+Furthermore, we utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
 during the planning phase and reuse them in the reduce phase.
 
-In Section 6.2.2 Figure 8, we validate the benefits of adopting these Spark features. In Figure 8, we compare SPARE with
-SPARE-RD. SPARE-RD is identical to SPARE except without best-fit strategy. Benefit from the two Spark features, planning
-phase only takes around 4\% of SPARE's total execution time. With the planning phase, SPARE is 15\% faster compared to SPARE-RD.
+In Section 6.2.2 Figure 8, we validate the benefits of adopting these Spark features by comparing SPARE with
+SPARE-RD. SPARE-RD is identical to SPARE except it uses random allocation rather than best-fit strategy. Benefit from the two Spark features, the SPARE the best-fit strategy
+ only takes around 4\% the total execution time. In return, SPARE gains 15\% speedup compared to SPARE-RD.
 

### 2016-09-02 ReviewComments/meta.tex
More revisement

@@
 
-\textbf{Response:} In addition to the points in the response of comments 2.1, another novelty of our work lies in the 
+\textbf{Response:} In addition to our response to comments 2.1, another novelty of our work lies in the 
 techniques. 
@@
 Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
-anti-monotonicity) which have not been previously proposed.
+anti-monotonicity) which have not been previously proposed yet.
 

### 2016-09-02 ReviewComments/review2.tex
More revisement

@@
 is also used in mining Gap-restricted Sequential Patterns (GSP). 
-However, our work is the first to introduce the gap concept 
-in co-movement mining to resolve the
+However, our work is the first to introduce the gap constraint 
+in co-movement mining in trajectory domain, and we are the first to resolve the
 loose-connection anomaly (as shown in Figure 2).  
-Moreover, we also provide
+Moreover, we provide
 a unified model to capture existing pattern models which 
@@
 the most frequent temporal sequence for GSP is
-$(1,2,3,4,5,6)$ because it appears in all trajectories. 
+$(1,2,3,4,5,6)$ because it appears in every trajectory. 
 However, the involved objects $\{o_1,o_2,o_3,o_4,o_5,o_6\}$ are NOT all

### 2016-09-02 ReviewComments/review3.tex
More revisement

@@
 \textbf{Response:}
-We thank the reviewer for suggesting a better way of implementing 
-the baseline algorithm (i.e., TRPM). By utilizing window functions,
-TRPM could be rewritten as in the following pseudo-code:
+We thank the reviewer for suggesting a better way to implement
+the baseline algorithm (i.e., TRPM). With window functions,
+TRPM could be rewritten as in the following pseudocode:
 \begin{equation*}
@@
  \mathtt{WindowSpec}\ ws := \mathtt{Window}&.\mathtt{orderBy}('time') \\
- 				&.\mathtt{rangeBetween}(0, \eta); \\
+ 				&.\mathtt{rowBetween}(0, \eta); \\
  \mathtt{Pattern}\ pt :=  LineSweep&('clusters').\mathtt{over}(ws); 
@@
 would be very limited. The reason is that our 
-Line Sweep algorithm (Algorithm 1) is not a 
-distributive function. 
+Line Sweep algorithm (Algorithm 1) is
+distributive.
 That is the result over an input cannot be constructed from
 the result over a subset of the input. This indicates 
-that no partial results can be shared among all windows.
+that no partial results could be shared among all windows.
 In such a case, Spark-SQL has to process each
@@
 We revise Section 6.2.2 by comparing SPARE with different data partition strategies.
-In particular, we compare SPARE which adopts a best-fit strategy (Section 5.3) and SPARE-RD
+In particular, we compare SPARE which contains a best-fit strategy (Section 5.3) and SPARE-RD
 which adopts the default random partition strategy.

### 2016-09-02 sec6_experiment.tex
More revisement

@@
 \\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
-\multirow{3}{*}{Shopping}              & TRPM            &     426                          & 597                 & 35 
-\\ %\cline{2-5} 
+\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
                                        & SPARE-RD          & 122                               &  295             & 41
@@
 \\ \hline                                
-\multirow{3}{*}{GeoLife}              & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
+\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
                                        & SPARE-RD          &  38                               &   484               & 148
@@
 \\ \hline
-\multirow{3}{*}{Taxi}              & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
+\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
                                        & SPARE-RD          & 122                               & 681                 & 109
@@
 Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
-for SPARE and SPARE-RD \revised{with TRPM as comparison}.
+for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
 We observe that the map and shuffle time of SPARE and SPARE-RD are identical .
@@
 efficiency of the star partition and apriori enumeration.} 
-\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}.
+%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}.
 As the table shows, SPARE produces more balanced jobs
-than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
-maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
-However, TRPM still takes much longer time than SPARE algorithms.}
-%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
-%We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std.
-Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
+%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
+%However, TRPM still takes much longer time than SPARE algorithms.}
+We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+We also report the cost of \revised{the longest job (Max), the shortest job (Min) and the standard deviation (Std. Dev.)}
+%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
+for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
 

### 2016-09-07 ReviewComments/response.tex
Revision inlcluded

--- 2016-08-28 ReviewComments/response.tex
@@
 \usepackage{url}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{epstopdf}
 \newcounter{ctResp}
+\newcommand{\eat}[1]{}
 \newcommand{\response}[1]{
 \addtocounter{ctResp}{1}
+
 \textbf{Response \arabic{ctResp}:} #1 \\}
@@
 suggestions which help us to improve this work to a better level.
-In the following, we provide explicit response to each raised concern and address our corresponding revisions in the new submission.
+In the following, we provide the explicit response to each raised concern.
+
+\section{Response to Reviewer 1}
+
+\textbf{1.1} \emph{The main con that I've spotted is the fact that the algorithm might have been
+more nicely framed also within the Spark environment by taking advantage of
+the various possibilities offered by it (e.g. caching of RDDs)}
+
+\textbf{Response:} We agree with the reviewer that the solutions could benefit from utilizing advanced Spark features.
+In fact, our SPARE algorithm has already taken advantage of two distinct features of Spark, including  DAG execution engine and caching of RDDs, to accelerate its performance:\\
+\noindent\textbf{DAG Execution Engine:} As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
+This strategy relies on the DAG execution engine, which is a distinct feature of Spark.
+The strategy can be viewed as a planning stage in the Map-Planning-Reduce workflow.
+In particular, after the Map stage, we can collect the sizes of all stars as input for better workload balance among the reducers.
+Whereas, there is no such a planning stage in Hadoop.
+\\
+\noindent\textbf{Caching of RDD: } We also utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
+during the planning stage and reuse them in the reduce stage.
+
+Nevertheless, we believe there could exist other nice features of Spark worth further exploration in our solutions.
+
+\section{Response to Review 2}
+
+\textbf{2.1} \emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
+on consecutive segments is well-known
+in sequence mining published more than
+10 years ago.}
+
+\textbf{Response:} It is indeed that the parameter of maximum gap size has been introduced in other applications to mine the frequently occurred subsequences conforming to the gap constraint.
+Whereas, we are the first to introduce this parameter in trajectory co-movement mining to resolve the loose-connection anomaly.
+It poses new challenges and we propose two types of efficient and scalable solutions for the this more generalized problem.
+
+\eat{
+We admit that the gap parameter
+is also used in mining Gap-restricted Sequential Patterns (GSP). 
+However, our work is the first to introduce the gap constraint 
+in co-movement mining in trajectory domain, and we are the first to resolve the
+loose-connection anomaly (as shown in Figure 2).  
+Moreover, we provide
+a unified model to capture existing pattern models which 
+is also not proposed before.
+%
+%The novelty of our modeling
+%is bi-folded. First, we unify existing co-movement patterns in
+%a GCMP model. Second, we use the gap-constraint to avoid
+%the loose-connection anomaly (as shown in Figure 2) which 
+%is suffered by existing patterns.
+
+%
+%We admit that the gap parameter is also used in
+%mining Gap-restricted Sequential Patterns (GSP). 
+%However, the novelty of this paper lies
+%on the one-stop solution of mining co-movement patterns.
+%In modeling, we provide the generalize co-movement pattern to
+%alleviate the troubles
+%is not merely on introducing the gap-constraint.
+%Instead, we provide a one-stop solution for mining co-movement patterns. With
+%our 
+%
+%However, the novelty
+%of this paper is not merely on introducing the gap-constraint to the generalized
+%co-movement pattern. 
+%Instead, we provide a one-stop solution (both in modeling and in technical)
+%for mining various co-movement patterns with flexible constraints.
+%
+%This solution not only alleviate the cumbersome for designing each
+%individual patterns, but also 
+%
+% With
+%these constraints, users are able to define a more accurate pattern
+%which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).
+
+Besides, GSP and GCMP are designed with different goals. Thus it is infeasible
+to model GCMP using GSP. 
+In particular, the goal of GSP 
+is to find the frequently occurred subsequences which conform to the gap constraint.
+This definition ignores the relationships among the involved objects. 
+As a consequence, the mined GSP results cannot guarantee the spatial closeness of the involved
+objects, which contradicts with \emph{closeness} requirement of GCMP (Section 3 Definition 2). 
+For example, in the sample trajectory database in Figure 1, 
+the most frequent temporal sequence for GSP is
+$(1,2,3,4,5,6)$ because it appears in every trajectory. 
+However, the involved objects $\{o_1,o_2,o_3,o_4,o_5,o_6\}$ are NOT all
+spatially close at any of the timestamps thus these objects do not form a proper GCMP.
+We summarize this difference in Section 2.5.
+
+%
+%
+%When counting the occurrence of a subsequence, the object
+%which the subsequence belongs to does not matter. This allows an object
+%to contribute multiple times for a subsequence's occurrence (e.g., in ``$o_1:ABCDABC$", $o_1$
+%contributes twice for the subsequence $ABC$)
+%
+%As a result, GSP may double count an object if the object's sequence 
+%has two identical subsequence.
+%
+%the involved objects may be neither
+% distinct nor close.
+%In contrast, GCMP imposes requirements on both the spatial closeness 
+%of objects and the number of distinct objects.
+%Due to the unawareness of objects, techniques that are used in GSP 
+%cannot be directly applied on GCMP. We summarize this difference
+%in Section 2.5.
+}
+
+\textbf{2.2} \emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
+we really interested in all sets of movements beyond a cardinality of size $M$? 
+Take the Taxi dataset as an example. Let say that there are lots of taxis going
+from the airport to downtown. Let say that there are 1000 such taxis. For a
+given $M$, are we interested in ${1000 \choose M}$ answers? 
+So this speaks to the problem of picking $M$. If $M$ is 500, what is ${1000 \choose M}$? In fact, even if the
+system gives the single answer of ${1000\choose 1000}$,
+I am not sure I am
+interested in this pattern as I already know that there are many taxis going from
+the airport to downtown. What I think I am really interested in are GCMP that
+are ``anomalous'', which is much harder to define.}
+
+\textbf{Response:} We understand the reviewer's concern and we will response this issue from several aspects.
+First, in this example, the reviewer actually has the prior knowledge that there are lots of taxis going from airport to downtown.
+Hence, the results from the co-movement patterns may not look so interesting.
+If we consider another application in which the database contains the trajectories of all the citizens and our goal is to mine social relationships among them (i.e.
+friends may exhibit co-movement patterns), setting a proper $M$ becomes quite interesting and challenging.
+This is normally solved by in an interactive way as in this case we don't have prior knowledge.
+Second, it is possible that when $M$ is not set properly, an enormous number of ``valid'' patterns will be returned, as noticed by the reviewer.
+To solve this problem, a typical way is to use the concept of ``closed'' pattern, in which only the valid superset is returned.
+This can be seen as an incremental work over our solution.
+Finally, we want to address that we simply follow the definition of co-movement patterns that are commonly adopted in the previous literature.
+
+\eat{We appreciate the reviewer's concerns on the 
+size of the output. 
+In fact, both TRPM and SPARE
+have considered compressing the output by only discovering 
+the patterns with larger object set. 
+Particularly,  in the Line Sweeping Mining (Algorithm 1) of TRPM, whenever
+a pattern $c$ becomes valid, it is directly outputted (Lines 14-16). This
+prohibits outputting $c$'s subset. Similarly, in the Apriori Enumerator (Algorithm 3)
+of SPARE, a pattern $c$ is outputted if none of its supersets could become a valid pattern (Line 12-14).
+This ensures the output $c$ is not a subset of some pattern.
+These mechanisms effectively condense the output by subsuming smaller
+patterns using their supersets.
+% Nevertheless, these mechanisms are able to preserve ALL valid patterns.
+Linking to the Taxi example, if the ground truth contains 1000 taxis travel
+together, then both TRPM and SPARE tend to output the single pattern.
+In addition, real detection of ``anomalous'' co-moment pattern needs to 
+impose stringent constraints via $M,K,L,G$. This would further reduces 
+the size of the output.
+%On the other hand, in reality, if users wish to detect ``anomalous'' patterns,
+%the parameters $M,K,L,G$ will be set to be very stringent. This reduces
+%the size of potential outputs. For example, when detecting the Taxi's movements
+%without ground truth of 1000 taxis, an input could be $M = 100$, $K=50$ min, $L=30$ min,
+%$G = 2$ min. Then, there would be very less patterns satisfying these constraints.
+% and the meaningfulness of the output. 
+%In terms of the output size, 
+%we certainly do not need to output every pattern.
+%In fact, both TRPM and SPARE algorithms tend to only output
+%the patterns with larger object size. That is to say, for
+%the Taxi example, the pattern containing all the 1000 taxis will
+%be outputted. To see this, in Algorithm 1, TRPM effectively 
+%starts with a temporally invalid pattern and continue
+%to shrink its object set until it is temporally valid. Then, the result
+%is the ``largest'' valid pattern for these object. Similarly,
+%in Algorithm 3, SPARE effectively starts with a temporally valid
+%pattern with small object set. Then SPARE continues to grow
+%the object set until its temporal dimension is about to be non-decomposable (Definition 5).
+%Therefore both TRPM and SPARE tends to find the ``largest'' valid
+%patterns.
+%
+%In terms of the meaningfulness, we believe that all patterns that conformed
+%to the parameters need to be outputted. 
+%This is because the parameters
+%
+%
+%We see two questions derived from this concern. First, do we need
+%to output all ${1000 \choose M}$ patterns if $1000$ taxis form a true GCMP
+%pattern? Our answer to this question is no. Therefore, the nature of both
+%of our TRPM and SPARE algorithms tend to only output the patterns containing 
+%larger sets of objects. To see this, in Algorithm 1, TRPM starts with an temporal invalid
+%pattern and continues to shrink its object set while growing its temporal dimension.
+%TRPM stops as soon as the object become valid. In an inverse way, in Algorithm 3, 
+%SPARE starts with a pattern with small objects and continues to grow its object set
+%while reducing its temporal dimension. SPARE stops as soon as the pattern is about
+%to be temporally invalid. Therefore, both TRPM and SPARE would prefer to output
+%larger pattern.
+%
+%
+%%
+%%We agree with the reviewer that if no other parameters are given, the maximum number
+%%of patterns discovered could be as large as ${ \mathbb{O} \choose M}$, which may
+%%be less interesting to users.
+%However, such a case rarely occurs due to two reasons. First,
+%in real trajectory mining, parameter $M$
+%is associated with temporal parameters $K,L,G$ and they jointly prune many false
+%patterns. Second, the nature of our solutions prefer 
+%a larger pattern when possible~\footnote{TRPM shrinks an invalid larger pattern until it is valid.
+SPARE grows a valid smaller pattern until it is about to be invalid.
+Therefore both algorithms tend to find larger patterns.}.
+%For example, if $(o_1,o_2,o_3)$ is 
+%a pattern and $M = 2$, 
+%then both TRPM and SPARE only output $(o_1,o_2,o_3)$ but not
+%any of its subsets. This effectively compresses smaller patterns.
+%
+%In addition, when the temporal parameters $K,L,G$ are given,
+%a larger $M$ actually decreases the number of resulted patterns. 
+%This is because there are less patterns having more than $M$ objects. 
+%As shown in Figures 7 (a)(g)(m), a larger $M$ actually reduces the running time of both TRPM and SPARE.
+}
+
+\textbf{2.3} \emph{Regarding the second weak points, one line of related work is the superimposition
+of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}
+
+\textbf{Response:} We agree with the reviewer that superimposition of constraints such as road network is an interesting research direction for our future work.
+In this paper, our goal is to first propose a unified definition of co-movement pattern that can generalize many previous works, and then design two scalable frameworks on Spark to solve this fundamental and general problem.
+We believe such a work can also attract other researchers' attention to contribute and consider more advanced scenarios with superimposition
+of constraints on spatiotemporal mining, as suggested by the reviewer.
+
+\eat{We understand that spatiotemporal mining with 
+domain-specific constraints may look similar to GCMP.
+However, we are unaware of existing works on the same GCMP model
+ with domain-specific constraints.
+
+Generally, patterns defined with domain-specific constraints are hard to be generalized.
+This is because constraints available in one domain (e.g., road direction in road networks)
+are often not available in other domains (e.g., no road directions available for visitor movements in a shopping mall). Nevertheless,
+when deploying on a specific domain, our GCMP solutions are amendable to
+incorporate more domain-specific constraints (i.e., rewrite the $\mathtt{sim}$ operation in Algorithm 3). 
+We summarize the discussion in Section 2.3.
+}
+
+%often rely on the specific knowledge in that domain (e.g.,
+%directions in road networks and maximum speed of traffic), which
+%are hard to be generalized. In contrast, GCMP's constraints
+%are on spatial (i.e., closeness) and temporal (e.g., max gap and min duration), 
+%which can be generalized for all trajectories. For example,
+%mining techniques on road networks fails to find patterns
+%in  
+%
+%However, existing techniques on spatiotemporal mining with domain-specific  
+%
+%
+%those techniques often heavily utilize the domain knowledge (such as
+%directions in road networks) which are nontrivial to be generalized.
+%Differently, since our GCMP model and technical solutions
+%do not leverage the domain knowledge, we can support
+%pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
+%passenger flows in a city.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Responses to Reviewer 3}
+\textbf{3.1:} \emph{Though the implementation references Spark as the implementation
+platform (as it also reflects in github repo provided), the algorithm design is
+mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
+Spark. This may have a negative impact on the baseline implementation.
+Particularly, recent releases of Spark have introduced window functions that can
+be applied directly in the sliding window scenario here. Certainly, the algorithm
+has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
+been noted that this is a very efficient way to execute window functions in
+Spark.}
+
+\textbf{Response:} We thank the reviewer for the constructive comment.
+% and carefully considered if applying the window-based function in the baseline algorithm is feasible.  
+We do not implement TRPM using Spark-SQL in the original submission because the latest Spark at that time (i.e., version 1.6.2 released in June)
+did not support \textit{user defined aggregate function} (UDAF) on the window operator\footnote{Window function improvements: \url{https://issues.apache.org/jira/browse/SPARK-7712}}. 
+Without UDAF, we cannot integrate the Line Sweep Mining (Algorithm 1) with the window functions.
+During our revision period, Spark 2.0.0 is released with the support of UDAF.
+Thus, we make the exploration of implementing TRPM using Spark-SQL window functions.
+
+Our Spark-SQL based TRPM (named TRPM-SQL) works as follows:
+First, we reorganize the input to form a Dataset with two columns: ``Time'' and ``Clusters''. 
+Second, we extend the UDAF class to implement the Line Sweep Mining algorithm on the ``Clusters'' column. Third, we 
+create a WindowSpec to represent a sliding window with size $\eta$ on the ``Time'' column. We compare the performance
+of original Map-Reduce based TRPM (named TRPM-MR) with the TRMP-SQL in the following figure.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{spark-sql-comp.eps}
+\caption{Performance comparison with SPARE, TRPM-MR and TRPM-SQL}
+\end{figure}
+
+The figure shows that TRPM-SQL is more than 120 times slower than TRPM-MR and 
+takes more than 1 day in the Taxi dataset. With further investigations on the query execution
+plan, 
+we found that as the TRPM-SQL window query does not have a ``partition by'' clause, the Catalyst
+optimizer treats the entire dataset as a SINGLE partition. This 
+large partition is sent to only ONE executor to process. Such a plan
+surrenders all the parallel benefits of the Spark system. Therefore, in our revised paper, we
+still use the original Map-Reduce based TRPM for the performance comparisons.
+% 
+%
+%
+%To our surprise, such a window function based implementation DOES NOT perform well. The reason is that
+%in TRPM, there is NO ``partition by'' clause. In such a case, Spark-SQL catalyst optimizer will treat
+%the entire dataset as ONE big partition and run the UDAF for every window frame in ONE executor. We observe
+%this from the physical query plan generated by Spark-Catalyst optimizer. This is no-doubt very inefficient,
+%which results in a over 150 times slower than our current TRPM implementation. This performance
+%of SPARE, TRPM-MR, TRPM-SQL for the three datasets are presented as follows:
+
+%Though it is not supported in Spark 2.0.0, processing each window frame in parallel 
+%can be easily implemented using simple Map-Reduce framework. However, such an processing logic
+%then becomes identical to our TRPM algorithm.
+
+\eat{
+First, we think it is difficult to directly apply the window-based function with existing Spark API in the current version of Spark-SQL.
+This is because in both the stable Spark 1.5.2 and the newly released Spark 1.6.2, \textit{user defined aggregate function} (UDAF) on window operator is not supported\footnote{Window function improvements: \url{https://issues.apache.org/jira/browse/SPARK-7712}}.
+Without UDAF, we cannot apply our Line Sweep algorithm on the window functions. %Nevertheless, we believe UDAF may be supported in the future release and in that case,
+
+%
+Second, the performance boost on TRPM from Spark-SQL may be limited.
+From our investigations on the current source code of Spark-SQL\footnote{Available in Github: \url{https://github.com/apache/spark/blob/master/sql}}, its implementation
+on window functions does not leverage the properties of the sliding window and the aggregate functions\footnote{Performance improvements on running window frame: \url{https://issues.apache.org/jira/browse/SPARK-8638}}.
+Instead, it treats each window frame independently and processes them separately.
+The processing logic then becomes identical to our TPRM algorithm.}
+%We agree that leveraging more advanced Spark features
+%could further improve the performance of our solutions. 
+%We do not heavily leverage these features because 
+%we wish to focus on designing parallel GCMP mining algorithms.
+%%to provide a general parallel framework which does not tie to Spark.
+%Nevertheless, we are in progress in developing
+%a better open-sourced version with Spark-tailored optimization. 
+%In the revision, we try to add a DataFrame based TRPM solution 
+%which aims to leverage the window functions from Spark-SQL.
+%However, to the best of our efforts, we could not achieve this goal in a short time. 
+%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
+%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
+%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
+%is nontrivial. Nonetheless, we expect less performance
+%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
+%properly reducible, where Spark system would fail to leverage the partial aggregates
+%across multiple windows. As a result, it would be equivalent to our current TRPM
+%solution where windows are processed independently in parallel.
+%TRPM although can be modeled using window functions over data frame, the aggregates
+%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
+%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
+%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
+%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
+%last month), UDAF does not fit with window function. We confirm these information
+%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
+%
+%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
+%not boost too much 
+%
+%we expect
+%even with UDAF support TRPM would not boost too much.  Spark system is 
+%%hard to leverage the partial aggregates acrocess
+%
+%we can analytically expect even using UDAF, TRPM would
+%not boost too much. This is because our Algorithm 1 is not reducible. That
+%is we cannot merge or share partial aggregates across different windows. In summary,
+%We wish to convince the reviewer that current TRPM implementation is reasonable.
+
+\textbf{3.2:} \emph{Most implementations
+on Hadoop and Spark are very sensitive to data partitions, i.e. prone to data
+skewing issues. It seems that the (starpartition)
+implementation does not take
+this into account, and only use the default partitioning. It would be very helpful
+to have a discussion on this topic.}
+
+\textbf{Response:} In this paper, we actually have studied the skewness issue.
+In Section 5.3, we propose a best-fit strategy for SPARE to achieve a better workload balance among the reducers because star partitioning may result in partitions with a different number of nodes.
+In the experimental study in Section 6.2.2, we compare the SPARE algorithm with SPARE-RD and the latter only adopts the default random partition strategy.
+We present the summary of the execution time for each method on the longest job and standard deviation of all jobs in Table 9.
+The results show that SPARE demonstrates better load balance (lower deviation)
+than SPARE-RD, which verifies the effectiveness of the best-fit strategy. 
+%Further, TRPM generally keeps a low deviation.
+This is because that TRPM always adopts the equal-size (i.e.
+$\eta$) partition.
+Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.
+
+%We revise Section 6.2.2 by comparing TRPM, SPARE with random 
+%task allocation and SPARE with best-fit task allocation (Section 5.3). We present
+%the summary of the execution time for each method on longest job, shortest job and standard
+%deviation of all jobs in Table 9. As the table show, SPARE has a better load balance (low deviation)
+%than SPARE-RD which indicates the effectiveness of the best-fit strategy. Further, TRPM
+%generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition.
+%Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.
+
+\textbf{3.3:} \emph{In particular, it would be great to provide the
+difference in the number of partitions/splits, the amount of processing and
+memory usage (i.e., vcore and memory seconds) between TRPM and SPARE}
+
+\textbf{Response:} In our implementation, we take a fixed 486 partitions (Section 6)
+for each RDD. The partition number is determined according to
+the parallel tuning guide by Cloudera\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}: there are  $3\times 54=162$ cores and each core is able to processes 3 partitions\footnote{This number may be different for other CPU models, and can be determined empirically.}
+by multithreading.
+
+Next, we add Table 7 (Section 6.1) to compare the resource usage between SPARE and TRPM in terms of Vcore-seconds, Memory and Running Time.
+The results show that both SPARE and TRPM are resource efficient.
+In particular, the RDDs for both SPARE and TRPM only take less than 20\% of the available memory.
+This infers that SPARE and TRPM can handle
+even larger trajectory databases with our current cluster resources.
+
+\textbf{3.4:} \emph{A plot that breaks down the performance gain by each method would
+be greatly appreciated by the readers.}
+
+\textbf{Response:} Thanks for the advice. In the revised version, we add an analysis of
+the breakdown cost in Figure 8.
+The SPARE and TRPM algorithms have similar workflow: partitioning (Star partition v.s.
+$\eta$-replicate partition) in the map-shuffle phase, and  mining (Apriori Enumeration v.s.
+Line Sweep) in the reduce phase.
+%In our experiment, we treat the execution time for each phase as the cost of the corresponding methods.
+As shown in Figure 8,
+both star partitioning and apriori enumeration contribute to 
+the final performance gain of SPARE. More specifically, in the map-shuffle phase,
+SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
+fewer data are transformed and shuffled in the star partitioning.
+In the reduce phase, SPARE saves 46\%-81\% time as compared to TRPM. This confirms 
+the efficiency of our Apriori enumerator.
+
+% with various optimization (e.g., sequence simplification, anti-monotonicity and forward closure checking).
+
+\textbf{3.5} \emph{Some choices of words may need to be reconsidered: for example, ``a bunch
+of" might not be appropriate in a technical paper.}
+
+\textbf{Response:} We have changed these unprofessional terms.
+
+\textbf{3.6} \emph{References to star partitioning and apriori pruning are missing. Though these
+are well known, they need to  be clearly cited.}
+
+\textbf{Response:} We have added the corresponding references in Section 5.1 and Section 5.2 when describing our algorithms.
+
+\textbf{3.7} \emph{In ``In contrast, when utilizing the multicore
+environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was ``multicore"
+referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}
+
+\textbf{Response:} We used all cores in the single node (i.e., 4 executors each with 3 cores) to conduct the experiment. We have revised the description in Section 6.2.3.
+
+\textbf{3.8} \emph{The computation of "eta" was slightly different than that in the paper}
+
+\textbf{Response:} Thanks for pointing this out. We have updated the GitHub repository to rectify the typo in the equation.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Response to Meta Reviewer}
+
+\textbf{M.1} \emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}
+
+\textbf{Response:} The novelty of the paper includes:
+\begin{itemize}
+\item We are the first to incorporate the parameter of maximum gap in the co-movement pattern definition.
+
+\item We are the first to deploy a distributed solution framework on Spark to solve the generalized pattern mining problem.
+
+\item There are also several novel ideas in our SPARE algorithm.
+For example, we devise a novel Star Partitioning to achieve better workload balance.
+In order to apply Apriori algorithm to overcome the exponential enumeration problem, we also devise novel concepts of sequence simplification to find a new type of monotonicity which can significantly reduce the number of candidates.
+\end{itemize}
+
+\eat{
+
+In addition to our response to comments 2.1, another novelty of our work lies in the 
+techniques. 
+Although the idea of star partition and apriori enumeration are well-known, 
+linking them together to solve the problem in trajectory domain has not been attempted before.
+Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
+anti-monotonicity) which have not been previously proposed yet.
+}
+
+\textbf{M.2} \emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
+on the motivation.}
+
+\textbf{Response:} We address this issue in Comment 2.2.
+
+\textbf{M.3} \emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce.
+Spark has capabilities beyond MapReduce such as window functions.
+Please provide an implementation that uses the relevant features of Spark, or a convincing discussion of how these features can be useful and why they were not used.}
+
+\textbf{Response:} We address this issue in Comments 1.1 and 3.1.
+
+\textbf{M.4} \emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew.
+Also provide details about how star partitioning and a priori pruning contribute to performance.
+Please provide references to these two methods.}
+
+\textbf{Response:} We address these issues in 3.2, 3.3, 3.4 and 3.6.
+
 \end{document}

### 2016-09-07 sec1_introduction.tex
Revision inlcluded

@@
 In addition, despite the generality of the \emph{platoon} (i.e., it can be reduced to other types of patterns via proper parameter settings), it suffers from the so-called \emph{loose-connection} anomaly.
-We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario.
+We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} to illustrate the scenario.
 These two objects form a \emph{platoon} pattern in timestamps $(1,2,3,102,103,104)$.
@@
 %in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
-By setting a feasible $G$, the loose-connection anomaly can be effectively controlled.
-In addition, our GCMP is both general and expressive.
+By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
 It can be reduced to any of the previous patterns by customizing its parameters.

### 2016-09-07 sec4_baseline.tex
Revision inlcluded

@@
 \center
-\includegraphics[width=\textwidth]{trm.eps}
+\includegraphics[width=0.85\textwidth]{trm.eps}
 \caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
@@
 
+\vspace{-5mm}
 \begin{algorithm}[h]
@@
 Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
-form a partition.
-In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$.
-Our next task is to design an efficient pattern mining strategy within each partition.
-Our solution includes a line sweep algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and an effective candidate pattern enumeration mechanism.
+form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. 
+Next, we aim to
+%Our next task is to 
+design an efficient pattern mining strategy within each partition. Our solution includes a line sweep algorithm to sequentially scan the $\eta$ %replicated 
+snapshots in a partition and an effective candidate pattern enumeration mechanism.
 
 Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}.
-We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process.
+We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping.
 It is initialized using the clusters with size no smaller than $M$ in the first snapshot.
 Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
-In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).
+Specifically, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).
 
 After sweeping all the snapshots, all the valid patterns are stored in $C$ (Line~\ref{code:ls-valid-check}). 
-It is worth noting that $C$ continues to grow during the whole sweeping process.
+It is worth noting that $C$ continues to grow during the whole sweeping.
 We can use three pruning rules to early remove false candidates from $C$.

### 2016-09-07 sec5_spm.tex
Revision inlcluded

@@
 \centering
-\includegraphics[width=0.9\textwidth]{spm.eps}
+\includegraphics[width=0.85\textwidth]{spm.eps}
 \caption{Star Partitioning and ApRiori Enumerator (SPARE).
@@
 First, the replication factor $\eta$ can be large.
-Second, the same valid pattern may be discovered from different partitions which results in redundant works.
+Second, the same valid pattern may be redundantly discovered from different partitions.
+%which results in redundant works.
 To resolve these limitations,
@@
 Before we introduce the Apriori Enumerator, we are interested to 
-examine the issue of global vertex ordering on the moving objects.
+examine the issue of global vertex ordering.
+% on the moving objects.
 This is because assigning different IDs to the objects will result in 
@@
 \centering
-\includegraphics[width=0.40\textwidth]{star-alt.eps}
-\caption{Examples of star partitioning with different vertex orderings.}
+\includegraphics[width=0.35\textwidth]{star-alt.eps}
+\caption{Star partitioning with different vertex orderings.}
 \label{fig:star-alt}
@@
 \end{proof}
-If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
+If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
 \begin{theorem}
@@
 \subsection{Apriori Enumerator}
-Intuitively, given a GCMP with an object set $\{o_1,o_2,\ldots,o_m\}$, 
+Intuitively, given a GCMP with an object set $\{o_1,\ldots,o_m\}$, 
 all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
@@
 \begin{lemma}\label{lemma:subset-property}
-If $T_1$ is a subset of $T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that $T_1'$ is a subset of $T_2'$.
+%If $T_1$ is a subset of $T_2$, 
+If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
+$T_1' \subseteq T_2'$.
 \end{lemma}
@@
 \end{lemma}
+
 \begin{proof}

### 2016-09-07 sec6_experiment.tex
Revision inlcluded

@@
 In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
-\revised{We set the number of partitions to be $486$ to fully utilize the parallelism provided by the multi-threading of every core.}
+\revised{We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.}
 All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
@@
 TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$.
-In contrast, with much more effective pruning strategy, our SPARE scales well with $G$.
+In contrast, with much more effective pruning strategy, SPARE scales well with $G$.
 Particularly, SPARE is 14 times faster than TRPM when $G=20$ in GeoLife dataset.
@@
 \small
+\centering
 \begin{tabular}{|l|c|c|c|c|}
 \hline
-\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
-\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ %\cline{2-5} 
-                                       & SPARE           & 237                               & 33,638                 & 8,613                \\ \hline
-\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ %\cline{2-5} 
-                                       & SPARE           & 341                               & 35,343                 & 14,369               \\ \hline
-\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ %\cline{2-5} 
-                                       & SPARE           & 580                               & 68,580                & 35,912               \\ \hline
+\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} % & \textbf{Time} 
+& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
+\multirow{2}{*}{Shopping}              & TRPM           % & 597
+                               & 90,859                 & 10,019               \\ %\cline{2-5} 
+                                       & SPARE           %& 237
+                                                                      & 33,638                 & 8,613                \\ \hline
+\multirow{2}{*}{Geolife}               & TRPM            %& 747 
+                              & 106,428                & 18,454               \\ %\cline{2-5} 
+                                       & SPARE           %& 341 
+                                                                     & 35,343                 & 14,369               \\ \hline
+\multirow{2}{*}{Taxi}                  & TRPM            %& 3,648  
+                           & 503,460                & 51,691               \\ %\cline{2-5} 
+                                       & SPARE           %& 580  
+                                                                    & 68,580                & 35,912               \\ \hline
 \end{tabular}
-\caption{Resources taken for TRPM and SPARE.
-Time is in seconds representing observed performance.
-Vcore-seconds is the aggregate of time spent in each core.
-Memory is in MB representing the actual size of RDDs.}
+\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size of RDDs.}
 \label{tbl:resource}
@@
 
+\vspace{-3mm}
 \subsection{Analysis of SPARE framework}
@@
 
+\vspace{-3mm}
 \begin{figure}[h]
 \centering
-	  \includegraphics[width=0.35\textwidth]{/exp/spare/detail1.eps}
-    \caption{Breakdown of cost of TRPM, SPARE and SPARE-RD.}
+	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
+    \caption{Cost breakdown of TRPM, SPARE and SPARE-RD.}
     \label{exp:wl}
@@
 
+\vspace{-4mm}
 \begin{table}[h]
 \centering \small
-%\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
+                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
+Shopping                 & 295              & 41         & 237             & 21       \\ \hline
+GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
+Taxi                     & 681              & 147        & 580             & 96       \\ \hline
+\end{tabular}
+%\begin{tabular}{|l|c|c|c|c|}
 %\hline
-%\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
-%                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
-%Shopping                 & 295              & 41         & 237             & 21       \\ \hline
-%GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
-%Taxi                     & 681              & 147        & 580             & 96       \\ \hline
+%\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
+%\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
+%\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
+%                                       & SPARE-RD          & 122                               &  295             & 41
+%\\% \cline{2-5}                                        
+%									   & SPARE           &  134                              &   237               & 21
+%\\ \hline                                
+%\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
+%                                       & SPARE-RD          &  38                               &   484               & 148
+%\\ %\cline{2-5}                                        
+%									   & SPARE           &   107                             &     341             & 96
+%\\ \hline
+%\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
+%                                       & SPARE-RD          & 122                               & 681                 & 109
+%\\ %\cline{2-5}                                        
+%									   & SPARE           &   134                             &  580                & 56               
+%\\ \hline
 %\end{tabular}
-\begin{tabular}{|l|c|c|c|c|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
-\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
-\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
-                                       & SPARE-RD          & 122                               &  295             & 41
-\\% \cline{2-5}                                        
-									   & SPARE           &  134                              &   237               & 21
-\\ \hline                                
-\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
-                                       & SPARE-RD          &  38                               &   484               & 148
-\\ %\cline{2-5}                                        
-									   & SPARE           &   107                             &     341             & 96
-\\ \hline
-\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
-                                       & SPARE-RD          & 122                               & 681                 & 109
-\\ %\cline{2-5}                                        
-									   & SPARE           &   134                             &  580                & 56               
-\\ \hline
-\end{tabular}
-  \caption{Statistics of execution time (in seconds) among all executors.}
+  \caption{Statistics of execution time (in seconds) among all jobs.}
   \label{tbl:strags}
@@
 
+\vspace{-2mm}
 \subsubsection{Load balance}
@@
 We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
-We also report the cost of \revised{the longest job (Max), the shortest job (Min) and the standard deviation (Std. Dev.)}
+We also report the cost of \revised{the longest job (Max) and the standard deviation (Std. Dev.)}
 %\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
@@
 \centering
-\begin{subfigure}[b]{0.31\textwidth}
+\begin{subfigure}[b]{0.3\textwidth}
     \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
@@
     \end{subfigure}
- 	 \begin{subfigure}[b]{0.31\textwidth}
+ 	 \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
@@
     \end{subfigure}
-    	 \begin{subfigure}[b]{0.31\textwidth}
+    	 \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}

### 2016-09-08 ReviewComments/response.tex
Reviewer Response

@@
 % and carefully considered if applying the window-based function in the baseline algorithm is feasible.  
-We do not implement TRPM using Spark-SQL in the original submission because the latest Spark at that time (i.e., version 1.6.2 released in June)
+We do not implement TRPM using Spark-SQL in the original submission 
+because the latest Spark at that time (i.e., version 1.6.2 released in June)
 did not support \textit{user defined aggregate function} (UDAF) on the window operator\footnote{Window function improvements: \url{https://issues.apache.org/jira/browse/SPARK-7712}}. 
 Without UDAF, we cannot integrate the Line Sweep Mining (Algorithm 1) with the window functions. 
-During our revision period, Spark 2.0.0 is released with the support of UDAF.
-Thus, we make the exploration of implementing TRPM using Spark-SQL window functions.
+During our revision period, Spark 2.0.0 is released with the support of UDAF. Thus, we make the exploration of implementing TRPM using Spark-SQL window functions.
 
-Our Spark-SQL based TRPM (named TRPM-SQL) works as follows:
-First, we reorganize the input to form a Dataset with two columns: ``Time'' and ``Clusters''. 
-Second, we extend the UDAF class to implement the Line Sweep Mining algorithm on the ``Clusters'' column. Third, we 
-create a WindowSpec to represent a sliding window with size $\eta$ on the ``Time'' column. We compare the performance
-of original Map-Reduce based TRPM (named TRPM-MR) with the TRMP-SQL in the following figure.
+Our Spark-SQL query for TRPM (referred to as TRPM-SQL) is constructed in three steps:
+First, we reorganize the input to form a Dataset\footnote{In Spark 2.0.0, Dataset is used to replace DataFrame.} with two columns: ``Time'' and ``Clusters''. 
+Second, we create a WindowSpec to represent the sliding window with size $\eta$ on the ``Time'' column.
+Last, we apply the WindowSpec and our Line Sweep Mining Algorithm (as UDAF) on the input Dataset to
+form the query.
+%we call the window function in Spark-SQL with a UDAF representing our Line Sweep Algorithm. 
+We compare the performance of TRPM-SQL with our original solutions in the following figure.
+%
+%Second, we extend the UDAF class to implement the Line Sweep Mining algorithm on the ``Clusters'' column. Third, we 
+%create a WindowSpec to represent a sliding window with size $\eta$ on the ``Time'' column. We compare the performance
+%of original Map-Reduce based TRPM (named TRPM-MR) with the TRMP-SQL in the following figure.
 
@@
 \includegraphics[width=0.4\textwidth]{spark-sql-comp.eps}
-\caption{Performance comparison with SPARE, TRPM-MR and TRPM-SQL}
+\caption{Performance comparison with SPARE, TRPM and TRPM-SQL}
 \end{figure}
 
-The figure shows that TRPM-SQL is more than 120 times slower than TRPM-MR and 
-takes more than 1 day in the Taxi dataset. With further investigations on the query execution
-plan, 
-we found that as the TRPM-SQL window query does not have a ``partition by'' clause, the Catalyst
-optimizer treats the entire dataset as a SINGLE partition. This 
-large partition is sent to only ONE executor to process. Such a plan
-surrenders all the parallel benefits of the Spark system. Therefore, in our revised paper, we
+The figure clearly shows that TRPM-SQL is inefficient with over
+120 times slower than TRPM. After investigations on its query execution
+plan, we find the slow performance of TRPM-SQL dues to the Spark-SQL Catalyst optimizer.
+Since our TRPM-SQL query does not have a ``partition by'' clause, the Catalyst optimizer
+treats the entire dataset as a SINGLE partition. Then it assigns the SINGLE partition to ONE executor,
+which surrenders the parallel benefits of Spark system.
+Due to the inefficiency of TRPM-SQL, in our revised version, we
 still use the original Map-Reduce based TRPM for the performance comparisons.
+
+%we found that Spark-SQL Catalyst optimizer assign the window query using only one
+%executor. It is because that our TRPM-SQL query does not have a ``partition by'' clause, and
+%the Catalyst optimizer treats the entire dataset as a SINGLE partition. Such a plan
+%surrenders all the parallel benefits of the Spark system. 
 % 

### 2016-09-08 sec1_introduction.tex
Revise some minor points

@@
 and driven by different mining applications, there are \revised{many} variants 
-of co-movement patterns that have been developed with more advanced constraints.
+of co-movement patterns that have been developed with additional constraints.
 
-Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
-with different constraints in the attributes of clustering in spatial proximity,
+Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
+with different constraints with respect to clustering in spatial proximity,
 consecutiveness in temporal duration and computational complexity. 
@@
 whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
-The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
-arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
+The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised approach by allowing
+arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
 They introduce a parameter $L$ to control the minimum length of each local consecutive segment.
@@
 
-Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns.
+\vspace{-2mm}
+Figure~\ref{fig:related_work} is an example to demonstrate the concepts of the various co-movement patterns.
 The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots.
-In each snapshot, we treat the clustering method as a black-box and assume that they generate the same clusters.
+In each snapshot, we treat the clustering method as a blackbox and assume that they generate the same clusters.
 Objects in proximity are grouped in the dotted circles.
@@
 Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps.
-Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  remains the only two candidates matching the patterns.
+Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  are the only two candidates matching the patterns.
 The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint.
@@
 
-\begin{table} \scriptsize
+\begin{table}[t]
 \centering
-\begin{tabular}{|l|l|c|l|}
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
 \hline 
-\textbf{Pattern} & {\tiny \textbf{Proximity}} & {\tiny \textbf{Consecutiveness}} & {\tiny \textbf{Time Complexity}}\\ 
+\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
 \hline 
-flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
+flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density-based &   global & {\tiny $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
+convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
-swarm~\cite{li2010swarm} & density-based  & - & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
+swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk-based &  local & {\tiny $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
+group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
 \hline 
-platoon~\cite{li2015platoon} & density-based &  local & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
+platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
@@
 \end{table}
+
 The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable.
@@
     \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
-    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
+    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
     \label{fig:related_work_scalability}
@@
 
-Therefore, our primary contributions in this paper are to close these two gaps. 
+Therefore, we aim to close these two gaps in this paper. 
 First, we propose the \emph{general co-movement pattern} (GCMP) which models
@@
 
-Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue.
+Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue.
 Our technical contributions are three-fold.
@@
 SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
-Moreover, SPARE further achieves upto 14 times efficiency
-as compared to the baseline algorithm with almost linear scalability.
+Moreover, SPARE further achieves almost linear scalability with upto 14 times efficiency
+as compared to the baseline algorithm.
 

### 2016-09-08 sec3_definitions.tex
Revision
almost completed
Revise some minor points

@@
 A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$.
-Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.
+Given two time sequences $T_1$ and $T_2$, we define \revised{several} commonly-used operators in this paper in Table~\ref{tbl:operators}.
 
-\begin{table}[h] \scriptsize
+\begin{table}[h]
+\vspace{-2mm}
 \centering
@@
 
+\vspace{-3mm}
 We say a sequence $T$ is consecutive 
-if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer each consecutive subsequence of $T$ as a \emph{segment}.
+if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
 It is obvious that any time sequence $T$ can be decomposed into
@@
 if the length of every segment is no smaller than $L$.
-As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem.
-To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
+As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} anomaly.
+To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
 timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:
@@
 \end{definition}
-There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
-express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
+There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
+%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
+%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
+%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
+%parameters to users to accommodate various application needs.}  
+By customizing these parameters, our pattern can 
+express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
 In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern.
@@
 In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
-It is notable that GCMP cannot be modeled by existing patterns. 
+%It is notable that GCMP cannot be modeled by existing patterns. 
 \begin{table}[h]
@@
 \hline
-Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
+Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
 \hline
-Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
+Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
 \hline 
-Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
+Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
 \hline 
-Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
+Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
 \hline 
-Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
+Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
 \hline 
 \end{tabular} 
-\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
-\emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
+\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
+% $M$ represents the  \emph{significance} constraint.
+$K$ represents the \emph{duration} constraint.
+$L$ represents the \emph{consecutiveness} constraint.
+$G$ represents the \emph{connection} constraint.
+}
 \label{tbl:patterns}
@@
 
+\vspace{-2mm}
 Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
@@
 
-\begin{table}[h]\scriptsize
+\begin{table}[h]
 \centering

### 2016-09-08 sec5_spm.tex
Revise some minor points

@@
 Instead, we simply need to emit the edges within a star to the same reducer.
-Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation.
+%Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation.
 Under the best-fit strategy, the most costly unallocated star is assigned to the most lightly loaded reducers, where we use the edges in the star as a cost estimation.
@@
 The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
+In Apache Spark, further optimization can be made by balancing the loads among reducers at runtime. 
+Leveraging
+Spark's DAG execution engine~\cite{zaharia2012resilient}, a planning phase can be inserted in between map and reduce phases.
+With knowing all map results (i.e., star sizes), a simple best-fit planning strategy can be adopted by assigning the most costly unallocated star to the most lightly loaded reducer, where the edges in a star can be used as a cost estimation.
 
 \begin{algorithm}
-\small
 \caption{Star Partitioning and ApRiori Enumerator}

### 2016-09-10 appendix.tex
Revision inlcluded
Current Version

@@
 denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
-as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is
-
+as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
+\vspace{-2mm}
 \begin{equation}
+\vspace{-2mm}
 \Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
@@
 entries in $B$ can be written as :
-
+\vspace{-2mm}
 \begin{equation*}
+\vspace{-1mm}
 b_{i,j} = \begin{cases}
@@
 $t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
-
+\vspace{-2mm}
 \begin{equation*}
+\vspace{-2mm}
 \begin{split}
@@
 $\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
+\vspace{-2mm}
 \begin{equation*}
+\vspace{-2mm}
 \begin{split}
@@
 Substitute back $t$ and $\mu$, we achieve the following concise form:
+\vspace{-2mm}
 \begin{equation*}
@@
 \end{equation*}
-This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
+This indicates the probability of $(\Gamma-d/2) \leq O(\sqrt{n\log n})$ is $(1-1/n)$. 
 Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
-the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
+$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
 When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
 the Chernoff Bound can be used to derive a tighter bound of 
-$O(\sqrt{\log n}) $ following the similar reasoning.
+$O(\sqrt{\log n}) $ following similar reasoning.
 \end{proof}

### 2016-09-10 sec1_introduction.tex
Current Version

@@
 A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
-and driven by different mining applications, there are \revised{many} variants 
+and driven by different mining applications, there are many variants 
 of co-movement patterns that have been developed with additional constraints.
@@
 \includegraphics[width=0.45\textwidth]{related_work.eps}
+\vspace{-0.5em}
 \caption{Trajectories and co-movement patterns.
@@
 \includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
+   \vspace{-0.5em}
 \caption{\emph{Loose-connection} anomaly.
@@
 \end{tabular} 
+\vspace{-0.5em}
 \caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
@@
             \includegraphics[width=\textwidth]{rw_perf_O.eps}
-		\subcaption{\small Varying No. of objects} 
+            \vspace{-1.5em}
+		\subcaption{ Varying No. of objects} 
     \label{fig:fig1}
@@
             \includegraphics[width=\textwidth]{rw_perf_T.eps}
-         \subcaption{\small Varying No. of timestamps}
+            \vspace{-1.5em}
+         \subcaption{ Varying No. of timestamps}
     \label{fig:fig2}
     \end{subfigure}
-    \vspace{-2mm}
+    \vspace{-0.5em}
     \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
@@
 
-Therefore, we aim to close these two gaps in this paper. 
+Therefore, in this paper, our contributions are to closing these two gaps.
+%In this paper, our contribution is towards closing these two gaps.
 First, we propose the \emph{general co-movement pattern} (GCMP) which models
@@
 By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
-It can be reduced to any of the previous patterns by customizing its parameters.
+It can be reduced to any of the previous pattern by customizing its parameters.
 
@@
 
-We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
+We conduct a set of extensive experiments on three large-scale real datasets with hundreds of millions of
 temporal points. 
@@
 The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
-trajectory pattern mining. Section~\ref{sec:definition} defines the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
+trajectory pattern mining.
+Section~\ref{sec:definition} states the problem of general co-movement pattern mining.
+Section~\ref{sec:trm} provides a baseline solution named \emph{Temporal Replication and Parallel Mining} (TRPM).
+An advanced solution named
 \emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.

### 2016-09-10 sec3_definitions.tex
Current Version

@@
-\section{Definitions}
+\section{Problem Statement}
 \label{sec:definition}
@@
 A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$.
-Given two time sequences $T_1$ and $T_2$, we define \revised{several} commonly-used operators in this paper in Table~\ref{tbl:operators}.
+Given two time sequences $T_1$ and $T_2$, we define commonly-used operators in this paper in Table~\ref{tbl:operators}.
 
@@
 \centering
-\begin{tabular}{|c|l|}
+\begin{tabular}{|c|p{6.5cm}|}
 \hline 
@@
 \end{tabular}
+\vspace{-0.5em}
 \caption{Operators on time sequence.} \label{tbl:operators}
@@
 
-\vspace{-3mm}
 We say a sequence $T$ is consecutive 
@@
 
-We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$.
+We take $T=(1,2,3,5,6)$ as an example.
+$T$ can be decomposed into two segments $(1,2,3)$ and $(5,6)$.
 $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$.
-Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive.
+But it is safe to say either $T$ is $1$-consecutive or $2$-consecutive.
 On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring timestamps is $2$.
@@
 \end{tabular} 
+    \vspace{-0.5em}
 \caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
@@
 }
+    \vspace{-0.5em}
 \label{tbl:patterns}
@@
 
-\vspace{-2mm}
 Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
@@
 \end{tabular} 
-\caption{Summary of the use of notations.}
+\vspace{-0.5em}
+\caption{Summary of notations.}
 \end{table}

### 2016-09-10 sec4_baseline.tex
Revise some minor points
Current Version

@@
 \includegraphics[width=0.85\textwidth]{trm.eps}
-\caption{Work flow of Temporal Replication and Parallel Mining (TRPM).
+    \vspace{-0.5em}
+\caption{Workflow of Temporal Replication and Parallel Mining (TRPM).
 (a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.
@@
 
+\vspace{-3mm}
 \section{Baseline: Temporal Replication and Parallel Mining}
 \label{sec:trm}
-In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP mining.
+In this section, we propose a baseline solution that resorts to Map-Reduce as a general, parallel and scalable paradigm for GCMP mining.
 The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
@@
 \end{theorem}
+\vspace{-2em}
 \begin{proof}
@@
 
-\vspace{-5mm}
 \begin{algorithm}[h]
-\small
 \caption{Line Sweep Mining}
@@
 The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}.
-We illustrate the workflow of the TRPM method using Figure~\ref{fig:trm} (c) and (d) with pattern
+We illustrate the workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
 parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
@@
 \begin{algorithm}[h]
-\small
 \caption{Temporal Replication and Parallel Mining}

### 2016-09-10 sec5_spm.tex
Current Version

@@
 \includegraphics[width=0.85\textwidth]{spm.eps}
+\vspace{-0.5em}
 \caption{Star Partitioning and ApRiori Enumerator (SPARE).
@@
 \includegraphics[width=0.35\textwidth]{star-alt.eps}
+\vspace{-0.5em}
 \caption{Star partitioning with different vertex orderings.}
@@
 \begin{proof}
+    \vspace{-0.5em}
 See Appendix~\ref{apx:thm2proof}.
@@
 \begin{proof}
+ \vspace{-0.5em}
 See Appendix~\ref{apx:thm2proof}.
@@
 \begin{proof}
+ \vspace{-0.5em}
 We assume $T_i\cap T_j\neq \emptyset$.
@@
 \begin{proof}
+ \vspace{-0.5em}
 Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$.
@@
 Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
-\begin{enumerate}
+\begin{enumerate}[nosep]
 \item $f$-step: remove segments of $T$ that are not $L$-consecutive;
@@
 \begin{proof}
+ \vspace{-0.5em}
 It is obvious that $\mathtt{sim}(T)$ is a one-to-one function.
@@
 \begin{proof}
+ \vspace{-0.5em}
 We prove by contradiction.
@@
 \end{theorem}
-\begin{proof}
+\begin{proof} \vspace{-0.5em}
 We prove by contradiction.
@@
 \end{theorem}
-\vspace{-5 mm}
-\begin{proof}
+\begin{proof}  \vspace{-0.5em}
 See Appendix~\ref{apx:spm_correct}.

### 2016-09-11 appendix.tex
Further revise
Squeezed everything into 12 pages..

@@
 %\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
+\vspace{-2mm}
 \subsection{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
 \label{apx:thm2proof}
-
+\vspace{-2mm}
 \begin{proof}
 $\Gamma$ can be formalized using linear algebra:
-Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
-Since a vertex order is a permutation of $J$, the adjacent matrices 
-of any reordered graphs can be represented as $PJP^T$
-where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
-In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
-then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
-represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+Let $J$ be the adjacent matrix of $G_A$.
+%Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
+A vertex order on $G_A$ can be represented as 
+%
+%Since a vertex order is a permutation of $J$, the adjacent matrices 
+%of any reordered graphs can be represented as 
+$PJP^T$
+where $P$ %$\in \mathbb{P}$ 
+is a %$n\times n$ 
+\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
+Consider an assignment matrix $B$ of star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$),
+$B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix} holds.
+% $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}, then $B$ is the assignment matrix of the star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
+%
+%In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
+%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
+%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
 Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
@@
 as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
-\vspace{-2mm}
+\vspace{-1mm}
 \begin{equation}
-\vspace{-2mm}
+\vspace{-1mm}
 \Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
@@
 
-Let $B^*$ be the assignment matrix wrt. the optimal vertex ordering.
-Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
+Let $B^*$ be the optimal assignment matrix. It follows that 
+%Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
 $\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
-Next, for a vertex ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
-edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
-Let $d_i$ denote the degree of vertex $i$, since a vertex ordering does not
-affect the average degree,
-then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
-entries in $B$ can be written as :
-\vspace{-2mm}
+Next, %for a vertex ordering $P$, 
+let $e_{i,j}$ be an entry in $PAP^T$,
+% Since  edges in graph $G$ are independent, then
+$e_{i,j}$s are independent. Further, $E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$ where $d$ is the average degree of $G_A$.
+% Let $d_i$ denote the degree of vertex $i$,
+% since a vertex ordering does not
+%affect the average degree,
+%then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. 
+%Therefore, 
+Entries in $B$ can be written as:
+\vspace{-4mm}
 \begin{equation*}
@@
 
-There are two observations. First, since $e_{i,j}$s are independent,
-$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
+%There are two observations. First, 
+%%since $e_{i,j}$s are independent,
+%$b_{i,j}$s are independent. Second, 
+Since $i>j$ and $e_{i,j}$s are independent. 
 $E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
-As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s). By linearity 
+%As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s).
+ By linearity 
 of expectations,
@@
  Let $\mu =E[c_i] = d/2$, 
-$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
-\vspace{-2mm}
+$t = \sqrt{n\log n}$, by Hoeffding Bound, the following holds:
+\vspace{-4mm}
 \begin{equation*}
-\vspace{-2mm}
+\vspace{-1mm}
 \begin{split}
@@
 
-The first step holds since all $b_{i,j}$ are 0-1 variables. 
+%The first step holds since all $b_{i,j}$ are 0-1 variables. 
 Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
 $\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
-\vspace{-2mm}
+\vspace{-1mm}
 \begin{equation*}
-\vspace{-2mm}
+\vspace{-1mm}
 \begin{split}
@@
 \end{equation*}
-Substitute back $t$ and $\mu$, we achieve the following concise form:
-\vspace{-2mm}
-\begin{equation*}
-	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
-\end{equation*}
+%Substitute back $t$ and $\mu$, we achieve the following concise form:
+%\vspace{-1mm}
+%\begin{equation*}
+%\small
+%\vspace{-1mm}
+%	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
+%\end{equation*}
 This indicates the probability of $(\Gamma-d/2) \leq O(\sqrt{n\log n})$ is $(1-1/n)$. 
-Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
-$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
+Since $\Gamma^* \geq d/2$, Theorem 2 holds.
+%it follows with probability greater than $(1-1/n)$, 
+%$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
 When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
 the Chernoff Bound can be used to derive a tighter bound of 
-$O(\sqrt{\log n}) $ following similar reasoning.
+$O(\sqrt{d\log n}) $ following similar reasoning.
 \end{proof}
@@
 \label{apx:spm_correct}
-\begin{proof}
-For soundness, let $P$ be a pattern enumerated by SPARE.
-For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$.
-By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$.
+\begin{proof}\vspace{-0.5em}
+For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. 
+%By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$. 
 As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
-For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} form $Sr_s$. 
-First, based on the definition of star, every object in $P.O$ appears in $Sr_s$.
-Since $P.T$ is decomposable, then by Lemma 3 $\forall O' \subseteq O$, the time sequence of $O'$ would not be eliminated by any $\mathtt{sim}$ operations.
+For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be outputted by Algorithm~\ref{algo:apriori_mining} from $Sr_s$. 
+First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 %$\forall O' \subseteq O$,
+the time sequence of %$O'$ 
+any subset would not be eliminated by any $\mathtt{sim}$ operations.
 Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure.
 We prove by induction.
-When $level$ = 2, it obviously holds.
+$level$ = 2 trivially holds.
 If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set.
-In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$).
+%In \emph{level} $i+1$, these subsets grow (in last iteration, they grow to $P.O$).
 This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}.
 Then, $P.O \subset U_{i+1}$ holds.
-In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
+Since $P.O$ does not pruned by simplification, monotonicity and forward closure, $P$ must be returned by SPARE.
 \end{proof}

### 2016-09-11 sec4_baseline.tex
Further revise
Squeezed everything into 12 pages..

@@
 (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
+\vspace{-0.5em}
 \label{fig:trm}
@@
 
-\vspace{-3mm}
+%\vspace{-3mm}
 \section{Baseline: Temporal Replication and Parallel Mining}
@@
 \label{THM:RP_ETA}
-$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
+$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missed.
 \end{theorem}
-\vspace{-2em}
+
 \begin{proof}
+\vspace{-0.5em}
 Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid.
@@
 We finish showing $\range(T') \leq \eta$.
-Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
+Therefore, for any valid sequence $T$, there is at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
 \end{proof}
+
+Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
+form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. 
+Next, we aim to
+%Our next task is to 
+design an efficient pattern mining strategy within each partition. Our solution includes a line sweep algorithm to sequentially scan the $\eta$ %replicated 
+snapshots in a partition and an effective candidate pattern enumeration mechanism.
 
@@
 \end{algorithm}
-
-Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
-form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. 
-Next, we aim to
-%Our next task is to 
-design an efficient pattern mining strategy within each partition. Our solution includes a line sweep algorithm to sequentially scan the $\eta$ %replicated 
-snapshots in a partition and an effective candidate pattern enumeration mechanism.
+\vspace{-1em}
 
@@
 After sweeping all the snapshots, all the valid patterns are stored in $C$ (Line~\ref{code:ls-valid-check}). 
-It is worth noting that $C$ continues to grow during the whole sweeping.
-We can use three pruning rules to early remove false candidates from $C$.
+It is worth noting that $C$ continues to grow during sweeping.
+We can use three pruning rules to remove  false candidates early from $C$.
 Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered.
@@
 three pruning rules are as follows:
-First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
+First, when sweeping snapshot $S_j$, new candidates with object set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
 candidates in $C$ with the maximum timestamp no smaller than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}).
 Third, candidates in $C$ with the size of the first segment smaller than $L$
-are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ can be significantly reduced.
-
-The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}.
-We illustrate the workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
-parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
-as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
-in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
-into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
-method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
-Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
-As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
-$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
-and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
-Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
-because its local consecutive segment $(4)$ has only $1$ element,
-which violates the $L$-consecutive constraint.
-Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned.
-Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness.
-If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.
+are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}).  
+With the three pruning rules, the size of $C$ can be significantly reduced.
 
@@
 \end{algorithm}
+\vspace{-0.5em}
+The complete picture of TRPM is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the  workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
+parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
+as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
+in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
+into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
+method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
+Initially, $C_1$ contains 
+%patterns with 
+all object sets in 
+%snapshot 
+$S_1$.
+%As we sweep the snapshots, the patterns in $C_i$ grow.
+At snapshot $S_4$, the candidate
+$\langle o_5,o_6 \rangle$ is removed because the gap between its latest timestamp (i.e., $2$)
+and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
+Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed
+because its local consecutive segment $(4)$ has only $1$ element,
+which violates the $L$-consecutive constraint.
+Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned.
+Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness.
+If $\eta$ is set to be $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

### 2016-09-11 sec5_spm.tex
Further revise
Squeezed everything into 12 pages..

@@
 \label{fig:star_partition}
+\vspace{-0.5em}
 \end{figure*}
@@
 \caption{Star partitioning with different vertex orderings.}
+\vspace{-0.5em}
 \label{fig:star-alt}
@@
 \begin{proof}
- \vspace{-0.5em}
+ %\vspace{-0.5em}
 We assume $T_i\cap T_j\neq \emptyset$.
@@
 Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$.
-If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected.
-If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in$\cup_{i=1}^{i=m} T_i$.
+If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to form a superset which is also $G$-connected.
+If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup_{i=1}^{i=m} T_i$.
 Both cases lead to contradictions.
@@
 \begin{proof}
- \vspace{-0.5em}
+ %\vspace{-0.5em}
 Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$.
@@
 because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
-In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than than $4$.
+In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than $4$.
 \end{example}
@@
 \begin{proof}
- \vspace{-0.5em}
+ %\vspace{-0.5em}
 It is obvious that $\mathtt{sim}(T)$ is a one-to-one function.
@@
 \begin{proof}
- \vspace{-0.5em}
+%\vspace{-0.5em}
 We prove by contradiction.
@@
 This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned.
-If a candidate cannot generate any new candidate, the
+If a candidate cannot generate any new candidate, then
 it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
 To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
-If yes, we can early terminate the algorithm and output the results.
+If yes, we can  terminate the algorithm early and output the results.
 
@@
 We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows.
-After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship.
+After the parallel clustering in each snapshot, for ease of presentation, we use an aggregated graph $G_A$ to capture the clustering relationship.
 However, in the implementation of the map phase, there is no need to create $G_A$ in advance.
@@
 \end{theorem}
-\begin{proof} \vspace{-0.5em}
+\begin{proof} 
+\vspace{-0.5em}
 We prove by contradiction.
@@
 However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction.
+\vspace{-0.5em}
 \end{proof}
@@
 \end{theorem}
-\begin{proof}  \vspace{-0.5em}
+\begin{proof}  
+\vspace{-0.5em}
 See Appendix~\ref{apx:spm_correct}.
+\vspace{-0.5em}
 \end{proof}

### 2016-09-11 sec6_experiment.tex
Revise some minor points
Current Version
Further revise
Squeezed everything into 12 pages..

@@
 In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
-\revised{We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.}
-All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
+We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.
+All our implementations as well as cluster setups are publicly available% in Github
+\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
 
 \textbf{Datasets}: We use three real trajectory datasets in different application scenarios:
-\begin{itemize}
+\begin{itemize}[nosep]
 \item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}: The dataset contains
@@
 
+%\vspace{-2mm}
 \begin{table} [h]
 \center
-\small
 \begin{tabular}{|l|l|l|l|}
 \hline
- \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{SingTaxi} \\ 
+ \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{Taxi} \\ 
 \hline 
@@
 \end{tabular}
+ \vspace{-0.5em}
 \caption{Statistics of datasets.}
+\vspace{-0.5em}
 \label{exp:dataset}
@@
 
-\textbf{Parameters}: To systematically study the performance of
-our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold. 
+%\vspace{-5mm}
 \begin{table}[h]
 \small
-\begin{tabular}{c|l|l}
+\begin{tabular}{c|l|p{3cm}}
 \hline 
-\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
+\textbf{Parameter} & \textbf{Meaning} & \textbf{Values} \\ 
 \hline 
-M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
+M & min  objects &  5, 10,  \textbf{15}, 20, 25 \\ 
 \hline 
@@
 \end{tabular} 
-\caption{Variables and their default values.}
+ \vspace{-0.5em}
+\caption{Parameters and their default values.}
+ \vspace{-0.5em}
 \label{tbl:parameters}
 \end{table}
+
+%\vspace{-3mm}
+\textbf{Parameters}: To systematically study the performance of
+our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold.
 
@@
     \end{subfigure}      
-
+\vspace{-0.5em}
 \caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
+\vspace{-0.5em}
 \label{exp:performance_vary}
 \end{figure*}
+
 \textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(g),(m)
@@
 
-\revised{
 \textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken 
@@
 \begin{table}[h]
-\small
 \centering
@@
 \end{tabular}
+ \vspace{-0.5em}
 \caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size of RDDs.}
+\vspace{-0.5em}
 \label{tbl:resource}
 \end{table}
-}
+
 %\begin{figure}[h]
@@
 
-\vspace{-3mm}
+%\vspace{-3mm}
 \subsection{Analysis of SPARE framework}
@@
 \end{tabular} 
-
+\vspace{-0,5em}
 \caption{Pruning power of SPARE.}
+\vspace{-0,5em}
+%\vspace{-4mm}
 \label{tbl:pruning}
@@
 
-\vspace{-3mm}
 \begin{figure}[h]
@@
 	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
-    \caption{Cost breakdown of TRPM, SPARE and SPARE-RD.}
+	 \vspace{-0.5em}
+    \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}
+   \vspace{-5mm}
     \label{exp:wl}
@@
 
-\vspace{-4mm}
+\subsubsection{Load balance}
+To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method.
+In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
+Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
+for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
+We observe that the map and shuffle time of SPARE and SPARE-RD are identical.
+The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
+Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
+efficiency of the star partition and apriori enumeration.
+%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}.
+As the table shows, SPARE produces more balanced jobs
+%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
+%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
+%However, TRPM still takes much longer time than SPARE algorithms.}
+We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+We also report the cost of the longest job (Max) and the standard deviation (Std. Dev.)
+%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
+for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+
 \begin{table}[h]
-\centering \small
+\centering 
 \begin{tabular}{|c|c|c|c|c|}
@@
 %\end{tabular}
-  \caption{Statistics of execution time (in seconds) among all jobs.}
+\vspace{-0.5em}
+  \caption{Statistics of execution time (seconds) on all jobs.}
+  \vspace{-0.5em}
   \label{tbl:strags}
@@
 
-\vspace{-2mm}
-\subsubsection{Load balance}
-To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method.
-In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
-Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
-for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
-We observe that the map and shuffle time of SPARE and SPARE-RD are identical .
-The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
-\revised{Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
-efficiency of the star partition and apriori enumeration.} 
-%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}.
-As the table shows, SPARE produces more balanced jobs
-%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
-%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
-%However, TRPM still takes much longer time than SPARE algorithms.}
-We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
-We also report the cost of \revised{the longest job (Max) and the standard deviation (Std. Dev.)}
-%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
-for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
-
+%\vspace{-5mm}
 \subsubsection{Scalability}
@@
 Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation.
-To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively.
+For a fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively.
 The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}.
@@
 detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
-In contrast, when utilizing the multi-core \revised{(i.e., a single node with four executors)} environment, 
+In contrast, when utilizing the multi-core (i.e., a single node with four executors) environment, 
 SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
@@
 %state-of-the-art \emph{platoon} detector in a centralized server.
-
+%
 \begin{figure*}[t]
@@
     \end{subfigure}
+%\vspace{-0.5em}
  \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}

### 2016-09-13 ReviewComments/response.tex
More revisions...

--- 2016-09-02 ReviewComments/response.tex
@@
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{epstopdf}
 \newcounter{ctResp}
+\newcommand{\eat}[1]{}
 \newcommand{\response}[1]{
 \addtocounter{ctResp}{1}
+
 \textbf{Response \arabic{ctResp}:} #1 \\}
@@
 \begin{document}
-\title{Response to reviewers' comments for Paper \# 278}
+\title{Responses to reviewers' comments for Paper \# 278}
 \maketitle
 
-We are deeply grateful to all the reviewers for the generous and insightful
-suggestions which help us to improve this work to a better level.
-In the following, we provide explicit response to each raised concern and address our corresponding revisions in the new submission.
+We are deeply grateful to all the reviewers for the 
+%generous and 
+insightful
+suggestions which help us to improve this work.
+In the following, we provide an explicit response to each concern raised.
 
@@
 
-\textbf{Response:} We agree with the reviewer that utilizing advanced Spark features
-would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features: (1) caching of RDDs and (2) DAG execution engine, to achieve speedups.
+\textbf{Response:} We agree with the reviewer that the solutions could benefit from utilizing advanced Spark features. 
+In our previous submission, our SPARE algorithm has already
+%In fact, our 
+%the SPARE algorithm has already 
+taken advantage of two distinct features of Spark, including  DAG execution engine and in-memory caching, to accelerate its performance:\\
+\noindent\textbf{DAG Execution Engine:} As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
+This strategy relies on the DAG execution engine, which is a distinct feature of Spark.
+The strategy can be viewed as a planning phase in the Map-Planning-Reduce workflow.
+In particular, after the Map phase, we can collect the sizes of all stars as input for better workload balance among the reducers.
+Whereas, there is no such a planning phase in Hadoop.
+\\
+\noindent\textbf{In-memory Caching:} We also utilize the in-memory caching feature of Spark to store the map result (i.e., RDDs of stars)
+during the planning phase and reuse them in the reduce phase (Section 5.3). Such a caching feature is not available in Hadoop neither.
 
-As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
-The best-fit strategy allocates the largest unassigned star to the most empty reducer, which balances the workloads for each reducer.
-Since the strategy needs to know the sizes of all stars, it takes place after the Map phase and before the Reduce phase.
-Leveraging Spark's DAG execution engine, we can easily augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow.
-Furthermore, we utilize the RDD caching feature of Spark to store the map result (i.e., RDDs of stars)
-during the planning phase and reuse them in the reduce phase.
+In our revision, we have edited Section 5.3 to explicitly clarify these points. Nevertheless, we believe there could exist other nice features of Spark worth further explorations in our solutions.
 
-In Section 6.2.2 Figure 8, we validate the benefits of adopting these Spark features by comparing SPARE with
-SPARE-RD. SPARE-RD is identical to SPARE except it uses random allocation rather than best-fit strategy. Benefit from the two Spark features, the SPARE the best-fit strategy
- only takes around 4\% the total execution time. In return, SPARE gains 15\% speedup compared to SPARE-RD.
+\section{Response to Review 2}
 
-%As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance.
-Using the DAG execution engine, we are able to augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow.
-With the support of in-memory caching of RDDs,
-%the Map results need not to be recomputed after the planning phase.
-As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).
-If without Spark's features, such an optimization would be hardly possible, but SPARE-RD is still more efficient than the baseline TRPM.
+\textbf{2.1} \emph{The GCMP generalization is not particularly novel. Putting a maximum gap size
+on consecutive segments is well-known
+in sequence mining published more than
+10 years ago.}
 
-We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
+\textbf{Response:} The idea of introducing a maximum gap size is indeed a commonly used method in sequence mining. However, 
+it has not been employed in trajectory co-movement mining to resolve the loose-connection anomaly. More importantly, incorporating
+this feature poses new challenges and we propose two types of efficient and scalable solutions for the more generalized problem.
 
-\input{review1}
-\input{review2}
-\input{review3}
-\input{meta}
+To summarize, the novelty of the paper includes:
+\begin{itemize}
+\item We are the first to incorporate the parameter of maximum gap in the co-movement pattern definition. This has made
+it possible to achieve our GCMP generalization. Such a generalization is more practical as it offers a single solution  
+for a class of co-movement patterns, in contrast to specialized solutions for each class of patterns.
 
+\item We are the first to deploy a distributed solution framework on Spark to solve the generalized pattern mining problem.
+This enables large-scale (in terms of number of objects and trajectory duration) co-movement pattern mining to be accomplished
+in a short time (in contrast to days in traditional centralized solutions).
+
+\item There are also several novel ideas in our SPARE algorithm.
+For example, we devise a novel Star Partitioning to minimize data replication and a run-time best-fit strategy to achieve better workload balance.
+In order to apply Apriori algorithm to overcome the exponential enumeration problem, we also devise a  novel concept of sequence simplification to find a new type of monotonicity which can significantly reduce the number of candidates.
+This further renders our approach practical on large-scale datasets.
+\end{itemize}
+
+\textbf{2.2} \emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
+we really interested in all sets of movements beyond a cardinality of size $M$? 
+Take the Taxi dataset as an example. Let say that there are lots of taxis going
+from the airport to downtown. Let say that there are 1000 such taxis. For a
+given $M$, are we interested in ${1000 \choose M}$ answers? 
+So this speaks to the problem of picking $M$. If $M$ is 500, what is ${1000 \choose M}$? In fact, even if the
+system gives the single answer of ${1000\choose 1000}$,
+I am not sure I am
+interested in this pattern as I already know that there are many taxis going from
+the airport to downtown. What I think I am really interested in are GCMP that
+are ``anomalous'', which is much harder to define.}
+
+\textbf{Response:} We understand the reviewer's concern and we will respond to this issue from several aspects.
+First, in this example, the reviewer actually has the prior knowledge that there are lots of taxis going from airport to downtown.
+Hence, the results from the co-movement patterns may not look so interesting.
+If we consider another application in which the database contains the trajectories of all the citizens and our goal is to mine social relationships among them (i.e.
+friends may exhibit co-movement patterns), setting a proper $M$ becomes quite interesting and challenging.
+This is normally solved in an interactive way as in this case we don't have any prior knowledge.
+Second, it is possible that when $M$ is not set properly, an enormous number of ``valid'' patterns will be returned, as noticed by the reviewer.
+To solve this problem, a typical way is to use the concept of ``closed'' pattern, in which only the valid superset is returned.
+This can be seen as an incremental post-processing over our solution.
+Finally, we want to stress that we simply follow the definitions of co-movement patterns that are commonly adopted in the previous literature.
+
+\textbf{2.3} \emph{Regarding the second weak points, one line of related work is the superimposition
+of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}
+
+\textbf{Response:}
+We agree with the reviewer that superimposition of constraints such as road network is an interesting research direction to consider.
+Despite many existing pattern discovery works in road networks~\cite{yu2016spatial,liu2013uncovering,liu2015exploring,xuTaxi2016}, we
+are unaware of co-movement pattern works in the road context. 
+In the future, we intend
+to first formalize a new co-movement pattern with practically useful ``road-aware'' constraints, and then integrate the pattern discovery techniques
+into our existing schemes. Meanwhile, we believe our work is able to attract and inspire more 
+researchers to contribute and consider advanced scenarios.
+
+%
+%Therefore, 
+%we believe co-movement patterns in the road networks is a potential interesting field and our
+%work could 
+%
+%this work
+%could attract more researchers' attention to contribute and consider more advanced scenarios. 
+%In the future, we intend
+%to formalize a new co-movement pattern with ``road-aware'' constraints, and to integrate the pattern discovery using our existing schemes.
+%%
+%%for our future work. 
+%There are quite a few works that on discovers trajectory patterns in road networks~\cite{}.
+Currently, we are unaware of co-movement pattern queries in existing works, which However, we believe our work could attract other researchers' attention to contribute and consider more advanced scenarios.
+Further, we are also interested in explore co-movement patterns with ``road-aware-constraint'' in the future.
+
+%In this paper, our goal is to first propose a unified definition of co-movement pattern that can generalize many previous works, and then design two scalable frameworks on Spark to solve this fundamental and general problem.
+We believe such a work can also attract other researchers' attention to contribute and consider more advanced scenarios with superimposition
+%of constraints on spatiotemporal mining, as suggested by the reviewer.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Responses to Reviewer 3}
+\textbf{3.1:} \emph{Though the implementation references Spark as the implementation
+platform (as it also reflects in github repo provided), the algorithm design is
+mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
+Spark. This may have a negative impact on the baseline implementation.
+Particularly, recent releases of Spark have introduced window functions that can
+be applied directly in the sliding window scenario here. Certainly, the algorithm
+has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
+been noted that this is a very efficient way to execute window functions in
+Spark.}
+
+\textbf{Response:} We thank the reviewer for the constructive comment.
+% and carefully considered if applying the window-based function in the baseline algorithm is feasible.  
+In our original submission,
+we do not implement TRPM using Spark-SQL
+because the latest Spark at that time (i.e., version 1.6.2 released in June)
+did not support \textit{user defined aggregate function} (UDAF) on the window operator\footnote{Window function improvements: \url{https://issues.apache.org/jira/browse/SPARK-7712}}. 
+Without UDAF, we cannot integrate the Line Sweep Mining (Algorithm 1) with the window functions. 
+Following the release of Spark 2.0.0 which supports UDAF, we have now explored implementing TRPM using Spark-SQL window functions.
+
+We construct a Spark-SQL query for TRPM (referred to as TRPM-SQL) in three steps:
+First, we reorganize the input to form a Dataset\footnote{In Spark 2.0.0, Dataset is used to replace DataFrame.} with two columns: ``Time'' and ``Clusters''. 
+Second, we create a WindowSpec to represent the sliding window with size $\eta$ on the ``Time'' column.
+Last, we apply the WindowSpec and our Line Sweep Mining Algorithm (as UDAF) on the input Dataset.
+%we call the window function in Spark-SQL with a UDAF representing our Line Sweep Algorithm. 
+We compare the performance of TRPM-SQL with our original solutions in the following figure.
+%
+%Second, we extend the UDAF class to implement the Line Sweep Mining algorithm on the ``Clusters'' column. Third, we 
+%create a WindowSpec to represent a sliding window with size $\eta$ on the ``Time'' column. We compare the performance
+%of original Map-Reduce based TRPM (named TRPM-MR) with the TRMP-SQL in the following figure.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{spark-sql-comp.eps}
+\caption{Performance comparison with SPARE, TRPM and TRPM-SQL}
+\end{figure}
+
+The figure clearly shows that TRPM-SQL is inefficient with over
+120 times slower than TRPM. Our investigations on the query execution
+plan identifies the root cause of  TRPM-SQL's slow performance to be the Spark-SQL Catalyst optimizer.
+Since our TRPM-SQL query does not have a ``partition by'' clause, the Catalyst optimizer
+treats the entire dataset as a SINGLE partition. Then it assigns the SINGLE partition to only ONE executor,
+which fails to benefit from the parallelism of the Spark framework. 
+Due to the inefficiency of TRPM-SQL (in Spark version 2.0.0), 
+we do not use it to replace the baseline (i.e., TRPM). 
+In our revision, we have added a footnote in Section 6 to justify our choice of implementations.
+
+\textbf{3.2:} \emph{Most implementations
+on Hadoop and Spark are very sensitive to data partitions, i.e. prone to data
+skewing issues. It seems that the (starpartition)
+implementation does not take
+this into account, and only use the default partitioning. It would be very helpful
+to have a discussion on this topic.}
+
+\textbf{Response:} In our original submission, we actually have studied the skewness issue.
+In Section 5.3, we proposed a best-fit strategy for SPARE to achieve a better workload balance among the reducers because star partitioning may result in partitions with a different number of vertices.
+In the experimental study in Section 6.2.2, we have compared the SPARE algorithm with SPARE-RD and the latter only adopts the default random partition strategy.
+We presented the summary of the execution time for each method on the longest job and the standard deviation of all jobs in Table 9.
+The results show that SPARE demonstrates better load balance (lower deviation)
+than SPARE-RD, which verifies the effectiveness of the best-fit strategy.
+
+\textbf{3.3:} \emph{In particular, it would be great to provide the
+difference in the number of partitions/splits, the amount of processing and
+memory usage (i.e., vcore and memory seconds) between TRPM and SPARE}
+
+\textbf{Response:} We thank the reviewer for the suggestion and we have explicitly clarified these points in the revision.
+
+In our implementation, we take a fixed 486 partitions (Section 6)
+for each RDD. The partition number is determined according to
+the parallel tuning guide by Cloudera\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}: there are  $3\times 54=162$ cores and each core is able to processes 3 partitions\footnote{This number may be different for other CPU models, and can be determined empirically.}
+by multithreading.
+
+Next, we have now added Table 7 (Section 6.1) to compare the resource usage between SPARE and TRPM in terms of Vcore-seconds and Memory.
+The results show that both SPARE and TRPM are resource efficient.
+In particular, the RDDs for both SPARE and TRPM only take less than 20\% of the available memory.
+This infers that SPARE and TRPM can handle
+even larger trajectory databases with our current cluster resources.
+
+\textbf{3.4:} \emph{A plot that breaks down the performance gain by each method would
+be greatly appreciated by the readers.}
+
+\textbf{Response:} We thank the reviewer for the advice. In the revision, we have added an analysis of
+the breakdown cost in Figure 8.
+The SPARE and TRPM algorithms have similar workflow: partitioning (Star partition v.s.
+$\eta$-replicate partition) in the map-shuffle phase, and  mining (Apriori Enumeration v.s.
+Line Sweep) in the reduce phase.
+%In our experiment, we treat the execution time for each phase as the cost of the corresponding methods.
+As shown in Figure 8,
+both star partitioning and apriori enumeration contribute to 
+the final performance gain of SPARE. Specifically, in the map-shuffle phase,
+SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
+fewer data are replicated and shuffled in the star partitioning.
+In the reduce phase, SPARE saves 46\%-81\% in time as compared to TRPM. This confirms 
+the efficiency of our Apriori enumerator.
+
+% with various optimization (e.g., sequence simplification, anti-monotonicity and forward closure checking).
+
+\textbf{3.5} \emph{Some choices of words may need to be reconsidered: for example, ``a bunch
+of" might not be appropriate in a technical paper.}
+
+\textbf{Response:} We have changed these unprofessional terms.
+
+\textbf{3.6} \emph{References to star partitioning and apriori pruning are missing. Though these
+are well known, they need to  be clearly cited.}
+
+\textbf{Response:} We have added the corresponding references in Section 5.1 and Section 5.2 when describing our algorithms.
+
+\textbf{3.7} \emph{In ``In contrast, when utilizing the multicore
+environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was ``multicore"
+referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}
+
+\textbf{Response:} We used all cores in the single node (i.e., 4 executors each with 3 cores) to conduct the experiment. We have revised the description in Section 6.2.3.
+
+\textbf{3.8} \emph{The computation of "eta" was slightly different than that in the paper}
+
+\textbf{Response:} Thanks for pointing this out.  We have updated the GitHub repository to rectify the typo in the equation.
+
+\section{Response to Meta Reviewer}
+
+\textbf{M.1} \emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}
+
+\textbf{Response:} We have addressed this issue in Comment 2.1.
+
+\textbf{M.2} \emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
+on the motivation.}
+
+\textbf{Response:} We have addressed this issue in Comment 2.2.
+
+\textbf{M.3} \emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce.
+Spark has capabilities beyond MapReduce such as window functions.
+Please provide an implementation that uses the relevant features of Spark, or a convincing discussion of how these features can be useful and why they were not used.}
+
+\textbf{Response:} We have addressed this issue in Comments 1.1 and 3.1.
+
+\textbf{M.4} \emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew.
+Also provide details about how star partitioning and a priori pruning contribute to performance.
+Please provide references to these two methods.}
+
+\textbf{Response:} We have addressed these issues in Comments 3.2, 3.3, 3.4 and 3.6.
+
+\bibliographystyle{IEEEtr}
+\bibliography{citations}
 \end{document}

### 2016-09-13 sec3_definitions.tex
Further revise
Squeezed everything into 12 pages..
More revisions...

@@
 \vspace{-0.5em}
-\caption{Operators on time sequence.} \label{tbl:operators}
+\caption{Operators on time sequence.}
+\vspace{-0.5em}
+\label{tbl:operators}
 \end{table}
@@
 if the length of every segment is no smaller than $L$.
-As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} anomaly.
+As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose-connection} anomaly.
 To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
@@
 Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns.
-In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
+In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose-connection} anomaly by tuning the parameter $G$. 
 %It is notable that GCMP cannot be modeled by existing patterns. 
@@
 \hline 
-$\Gamma$ & size of the largest star partition\\
-\hline
+%$\Gamma$ & size of the largest star partition\\
+%\hline
 \end{tabular} 
@@
 \caption{Summary of notations.}
+\vspace{-0.5em}
 \end{table}

### 2016-09-13 sec4_baseline.tex
More revisions...

@@
 \caption{Workflow of Temporal Replication and Parallel Mining (TRPM).
-(a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.
-(c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
+(a) and (b) correspond to the first mapreduce stage which clusters objects in each snapshot.
+(c) and (d) correspond to the second mapreduce stage, which uses TRPM to detect GCMPs in parallel.}
 \vspace{-0.5em}
@@
 \label{sec:trm}
-In this section, we propose a baseline solution that resorts to Map-Reduce as a general, parallel and scalable paradigm for GCMP mining.
+In this section, we propose a baseline solution that resorts to MapReduce as a general, parallel and scalable paradigm for GCMP mining.
 The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}.
-There are two stages of map-reduce jobs connected in a pipeline manner.
+There are two stages of mapreduce jobs connected in a pipeline manner.
 The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase.
@@
 
-Our focus in this paper is on the second map-reduce stage of parallel mining, which essentially addresses two key challenges.
+Our focus in this paper is on the second mapreduce stage of parallel mining, which essentially addresses two key challenges.
 The first is to ensure effective data partitioning such that the mining on each partition can be conducted independently; and the second is to efficiently mine the valid patterns within each partition.

### 2016-09-13 sec5_spm.tex
More revisions...

@@
 During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}).
-When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}).
+When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Line~\ref{code:join}).
 To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$.
@@
 The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.
-In Apache Spark, further optimization can be made by balancing the loads among reducers at runtime. 
-Leveraging
-Spark's DAG execution engine~\cite{zaharia2012resilient}, a planning phase can be inserted in between map and reduce phases.
-With knowing all map results (i.e., star sizes), a simple best-fit planning strategy can be adopted by assigning the most costly unallocated star to the most lightly loaded reducer, where the edges in a star can be used as a cost estimation.
+In our implementation of SPARE on Spark~\cite{zaharia2012resilient}, we take advantage of Spark features to achieve better workload balance. In particular,
+we utilize Spark DAG execution engine to inject a planning phase between map and reduce phases.
+By knowing all map results (i.e., star sizes), a simple best-fit strategy is adopted which assigns the most costly unallocated star to the most lightly loaded reducer, where the edges in a star are used as cost estimations.
+We also leverage Spark in-memory cache to avoid recomputing all stars after the planning phase.
+% 
+%In Apache Spark, further optimization can be made by balancing the loads among reducers at runtime. 
+%Leveraging
+%Spark's DAG execution engine~\cite{zaharia2012resilient}, a planning phase can be inserted in between map and reduce phases.
+%With knowing all map results (i.e., star sizes), a simple best-fit planning strategy can be adopted by assigning the most costly unallocated star to the most lightly loaded reducer, where the edges in a star can be used as a cost estimation.
 
@@
 Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$.
-However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction.
+However, $P_i$ and $P_j$ are from different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction.
 \vspace{-0.5em}

### 2016-09-13 sec6_experiment.tex
More revisions...

@@
 We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes.
-We deploy our GCMP detector on Apache Spark 1.5.2~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
+We deploy our GCMP detector on Apache Spark 1.5.2 with the remaining $11$ nodes as the computing nodes.
 To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
@@
 All our implementations as well as cluster setups are publicly available% in Github
-\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.
+\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}, we have also experimented with a query-based TRPM using Spark-SQL 2.0.0 window function. 
+We find that Spark-SQL fails to execute the query-based TRPM in parallel, which results in a 120x performance slowdown compared to mapreduce-based TRPM.
+%
+%it runs over 120 times slower than the mapreduce-based TRPM. 
+Thus we only report the performance of mapreduce-based TRPM in this paper.}.
 
@@
   trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
-\item{GeoLife}~\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}: The dataset essentially keeps all the travel records of 182 users for a period
+\item{GeoLife}\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}: The dataset essentially keeps all the travel records of 182 users for a period
 of over three years, including multiple kinds of transportation modes (walking, driving and taking public
@@
 are sampled every 1 to 5 seconds.
-\item{Taxi}~\footnote{Taxi is our proprietary dataset}: The dataset tracks the trajectories of $15,054$ taxies in Singapore.
+\item{Taxi}\footnote{Taxi is our proprietary dataset}: The dataset tracks the trajectories of $15,054$ taxies in Singapore.
 For each taxi, the GPS information are continually collected for one entire month with the sampling rate around 30 seconds.
@@
 
-%\vspace{-5mm}
 \begin{table}[h]
@@
 
-\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(h),(n).
+\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figures~\ref{exp:performance_vary} (b),(h),(n).
 SPARE tends to run faster, whereas the performance of TRPM degrades dramatically.
@@
 
-\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects.
+\textbf{Varying $O_r$}:Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects.
 Both TRPM and SPARE take longer time to find patterns in a larger database.
@@
  \vspace{-0.5em}
-\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size of RDDs.}
+\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
 \vspace{-0.5em}
@@
 \subsubsection{Power of sequence simplification}
-To study the power of sequence simplification,
+To study the power of \emph{Sequence Simplification} (SS),
 we collect two types of statistics: (1) the number of pairs that
 are shuffled to the reducers and (2) the number of pairs that
-are fed to the Apirori Enumerator. The difference between these two values is the number of size-$2$ candidates pruned by the sequence simplification.
-The results in Table~\ref{tbl:pruning} show that the \emph{sequence simplification} is very powerful and eliminates nearly 90 percent of the object pairs, which significantly reduces the overhead of subsequent Apriori enumerator.
+are fed to the Apirori Enumerator. 
+Their difference %is
+%The difference between these two values 
+is the number of size-$2$ candidates pruned by SS.
+The results in Table~\ref{tbl:pruning} show that %the \emph{sequence simplification} 
+SS is very powerful and eliminates nearly 90 percent of the object pairs, 
+which significantly reduces the overhead of %subsequent
+the Apriori enumerator.
+%Notice that SS is
+%essential for the monotonicity pruning of Apriori enumerator. 
+In fact, without SS Apriori cannot
+finish in five hours.
 
@@
 In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
-Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
+Figure~\ref{exp:wl} shows the breakdown of the costs in the mapreduce stages 
 for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
@@
 %However, TRPM still takes much longer time than SPARE algorithms.}
-We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
 We also report the cost of the longest job (Max) and the standard deviation (Std. Dev.)

### 2016-10-28 Camera-Ready/appendix.tex
Camera-Ready
Ohohoho

--- 2016-09-11 appendix.tex
@@
 \appendix
-\section{Proofs of Theorems}
-%\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
-%\label{appx:proof-rp-eta}
-%\begin{proof}
-%We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
-%In the following, when no ambiguity, we use $\rho(T)$ to represent
-%$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
-%be viewed as interleaving segments and gaps. 
-%We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
-%segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
-%Then the
-%range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
-%Since $\rho(T)$ is valid, the following constraints holds: 
-%(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
-%(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
-%$n \leq \lceil \frac{K}{L}\rceil$. 
-%This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-%If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
-%by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
-%then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
-%$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-%Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
-%since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
-%Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
-%the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
-%Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.
-%
-%For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
-%be the optimal value. Then consider the sequence $T$ generated 
-%by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
-%stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
-%It is easy to see that the minimum $\range(\rho(T))$ 
-%is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
-%$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
-%\end{proof}
-%\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
-%\begin{proof}
-%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
-%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
-%all possible valid sequence. It is easy to see that, under such a setting,
-%any valid sequence would be captured by one of the partitions in temporal
-%replication. This proves the completeness. Now, we compute the minimum value
-%of $\eta$ as follows:
-%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
-%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
-%as follows:
-%\begin{equation}
-%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
-%\end{equation}
-%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
-%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
-%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
-%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
-%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
-%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
-%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
-%conditions naturally derive
-%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
-%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
-%%with the smallest length. Note that there could be many qualified $T'$s. 
-%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
-%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
-%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
-%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
-%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
-%%If every partition is of at least such a size, then $T'$ must be
-%%captured by at least one of the partition. Thus, the pattern $P$ would 
-%%be valid in that partition. This proves the completeness.
-%\end{proof}
-%\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
-\vspace{-2mm}
-\subsection{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
+%\section{Proofs of Theorems}
+\section{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
 \label{apx:thm2proof}
-\vspace{-2mm}
 \begin{proof}
@@
 as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
-\vspace{-1mm}
 \begin{equation}
-\vspace{-1mm}
 \Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
@@
 Next, %for a vertex ordering $P$, 
-let $e_{i,j}$ be an entry in $PAP^T$,
+let $e_{i,j}$ be an entry in $PJP^T$,
 % Since  edges in graph $G$ are independent, then
@@
 %Therefore,
-Entries in $B$ can be written as:
-\vspace{-4mm}
-\begin{equation*}
-\vspace{-1mm}
-b_{i,j} = \begin{cases}
-			e_{i,j}, i>j \\
-			0, otherwise
-		  \end{cases}  
-\end{equation*}
-
+On the other hand, $b_{i,j} =e_{i,j}$ for $i > j$.
+%
+% \begin{cases}
+%			e_{i,j}, i>j \\
+%			0, otherwise
+%		  \end{cases}  $ 
+%\vspace{-4mm}
+%\begin{equation*}
+%\vspace{-1mm}
+%b_{i,j} = \begin{cases}
+%			e_{i,j}, i>j \\
+%			0, otherwise
+%		  \end{cases}  
+%\end{equation*}
+%
 %There are two observations. First, 
@@
 $t = \sqrt{n\log n}$, by Hoeffding Bound, the following holds:
-\vspace{-4mm}
 \begin{equation*}
-\vspace{-1mm}
-\begin{split}
-	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
-\end{split}
+	Pr(c_i \geq \mu + t) \leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
 \end{equation*}
@@
 $\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
-\vspace{-1mm}
 \begin{equation*}
-\vspace{-1mm}
 \begin{split}
-	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
-		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
+	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t) = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
 		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
@@
 the Chernoff Bound can be used to derive a tighter bound of 
-$O(\sqrt{d\log n}) $ following similar reasoning.
+$O(\sqrt{d\log n}) $ following a similar reasoning.
 \end{proof}
@@
 
-\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
+\section{Proof of Theorem~\ref{THM:SPM_CORRECT}}
 \label{apx:spm_correct}
-\begin{proof}\vspace{-0.5em}
+\begin{proof}
 For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. 

### 2016-10-28 Camera-Ready/p411_fan.tex
Camera-Ready
Ohohoho

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow,booktabs}
\usepackage{balance} 
\usepackage{epstopdf}
\usepackage[normalem]{ulem}
\usepackage{enumitem}
%\usepackage{pbox}
\usepackage{url}
\let\proof\relax
\let\endproof\relax
\usepackage{algorithm,amsmath,amsthm,amssymb}
\usepackage[noend]{algpseudocode} %for saving spaces

\graphicspath{ {../charts/}, {../exp/} }
\epstopdfsetup{outdir=../charts/}
\newtheorem{definition}{Definition}
\setcounter{definition}{0}
\newtheorem{theorem}{Theorem}
\setcounter{theorem}{0}
\newtheorem{example}{Example}
\setcounter{example}{0}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\triu}{triu}
\DeclareMathOperator*{\range}{range}
\newcommand*{\argminl}{\argmin\limits}
\newcommand*{\argmaxl}{\argmax\limits}
\newcommand{\eat}[1]{}
\usepackage{xcolor}
\newcommand{\revised}[1]{{\color{red}{#1}}}
\newcommand{\original}[1]{\sout{#1}}
\newtheorem{lemma}{Lemma}
\setcounter{lemma}{0}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

% ****************** TITLE ****************************************

\title{A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.
%

\author{
	\vspace{1mm}
	Qi Fan~$^\#$,
	Dongxiang Zhang~$^\natural$,
	Huayu Wu~$^\nabla$,
	Kian-Lee Tan$^{\#*}$ \\
	{\fontsize{10}{10}\selectfont $\#$ NUS Graduate School for Integrative Science and Technology, Singapore}\\
	{\fontsize{10}{10}\selectfont $^\natural$ University of Electronic Science and Technology of China, China}\\
	{\fontsize{10}{10}\selectfont $^\nabla$  Institute for Infocomm Research (I$^2$R), Singapore}\\
	{\fontsize{10}{10}\selectfont $^*$ School of Computing, NUS, Singapore}\\
	{\fontsize{10}{10}\selectfont%\ttfamily
	 fan.qi@u.nus.edu, zhangdo@uestc.edu.cn, huwu@i2r.a-star.edu.sg, tankl@comp.nus.edu.sg}
}

\maketitle

\begin{abstract}
Discovering co-movement patterns from large-scale trajectory databases is an important mining task and has a wide spectrum of applications. Previous studies have identified several types of interesting co-movement patterns and showcased their usefulness. In this paper, we make two key contributions to this research field. First, we propose a more general co-movement pattern to unify those defined in the past literature. Second, we propose two types of parallel and scalable frameworks and deploy them on Apache Spark. To the best of our knowledge, this is the first work to mine co-movement patterns in real life trajectory databases with hundreds of millions of points. Experiments on three real life large-scale trajectory datasets have verified the efficiency and scalability of our proposed solutions.
\end{abstract}

\input{sec1_introduction}
\input{sec2_relatedworks}
\input{sec3_definitions}
\input{sec4_baseline}
\input{sec5_spm}
\input{sec6_experiment}
\input{sec7_conclusion}

\noindent\textbf{Acknowledgment:}
The authors would like to thank the anonymous reviewers for their responsible feedback. 
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.

\bibliographystyle{abbrv}
\bibliography{citations}
%\balance
\input{appendix}

\end{document}

### 2016-10-28 Camera-Ready/sec1_introduction.tex
Camera-Ready
Ohohoho

--- 2016-09-10 sec1_introduction.tex
@@
 trajectories benefits a wide range of applications and services, 
-including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, to name just a few.
+including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, location-aware advertising~\cite{guo2016influence},  and social recommendations~\cite{bao2013survey}, to name just a few.
 
@@
 spatial clustering. 
-In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
-and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
+In the temporal dimension, the \emph{flock}%~\cite{gudmundsson2006flock} 
+and the \emph{convoy}%~\cite{jeung2008convoy} 
+require all the timestamps 
 of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
-whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
-The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised approach by allowing
+whereas the \emph{swarm}%~\cite{li2010swarm}
+does not impose any restriction. 
+The \emph{group}%~\cite{wang2006grouppattern} 
+and the \emph{platoon}%~\cite{li2015platoon} 
+adopt a compromised approach by allowing
 arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{related_work.eps}
-\vspace{-0.5em}
+\includegraphics[width=0.40\textwidth]{related_work.eps}
+%\vspace{-0.5em}
 \caption{Trajectories and co-movement patterns.
@@
 $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
+%\vspace{-0.5em}
 \label{fig:related_work}
@@
 
-\vspace{-2mm}
 Figure~\ref{fig:related_work} is an example to demonstrate the concepts of the various co-movement patterns.
@@
 \includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
-   \vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{\emph{Loose-connection} anomaly.
-Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
+Even though $\langle o_1, o_2\rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart.
 }
+%%\vspace{-0.5em}
 \label{fig:platoon_weakpoint}
@@
 \centering
-\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.7cm}|p{2.3cm}|}
 \hline 
-\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
+\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Conse-cutiveness}} & { \textbf{Time Complexity}}\\ 
 \hline 
-flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
+flock~\cite{gudmundsson2006flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
 \hline 
@@
 \end{tabular} 
-\vspace{-0.5em}
+%%\vspace{-0.5em}
 \caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
 $|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
+%\vspace{-0.5em}
 \label{tbl:existing_co_patterns}
@@
 \begin{figure}[h]
-	\vspace{-3mm}
     \centering
@@
             \includegraphics[width=\textwidth]{rw_perf_O.eps}
-            \vspace{-1.5em}
 		\subcaption{ Varying No. of objects} 
@@
             \includegraphics[width=\textwidth]{rw_perf_T.eps}
-            \vspace{-1.5em}
          \subcaption{ Varying No. of timestamps}
@@
     \end{subfigure}
-    \vspace{-0.5em}
+    %\vspace{-0.5em}
     \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
     is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
+    %\vspace{-0.5em}
     \label{fig:related_work_scalability}
@@
 
-Therefore, in this paper, our contributions are to closing these two gaps.
+Therefore, in this paper, our contributions are to close these two gaps.
 %In this paper, our contribution is towards closing these two gaps.
@@
 various co-moment patterns in a unified way and can avoid 
-the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
+the \emph{loose-connection} anomaly. In GCMP,
+we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
 %\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
@@
 Our technical contributions are three-fold.
-First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining.
+First, we design a baseline solution by replicating the snapshots
+%in multiple data chunks 
+to support effective parallel mining. 
 Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. 
 SPARE achieves workload balance by partitioning objects into fine granular stars. 
-For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns.
+For each partition, an Apriori Enumerator is adopted to mine the co-movement patterns. 
 Third, we leverage the \emph{temporal monotonicity} property of GCMP 
@@
 
-The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
-trajectory pattern mining.
+%The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
+%trajectory pattern mining.
 Section~\ref{sec:definition} states the problem of general co-movement pattern mining.
-Section~\ref{sec:trm} provides a baseline solution named \emph{Temporal Replication and Parallel Mining} (TRPM).
+Section~\ref{sec:trm} provides a baseline %solution named \emph{Temporal Replication and Parallel %Mining} (TRPM).
 An advanced solution named
-\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.
+%\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}.
 Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions.
 Finally, Section~\ref{sec:concl} concludes the paper.
+
+The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes related work.
+Section~\ref{sec:definition} states the problem of general co-movement pattern mining.
+Section~\ref{sec:trm} provides a baseline
+solution. % named \emph{Temporal Replication and Parallel Mining} (TRPM).
+An advanced solution named
+\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} reports our experimental evaluation.
+Finally, Section~\ref{sec:concl} concludes the paper.

### 2016-10-28 Camera-Ready/sec2_relatedworks.tex
Camera-Ready
Ohohoho

\section{Related Work}
\label{sec:related_works}
Related work can be grouped into three categories: \emph{co-movement patterns},
\emph{dynamic movement patterns} and \emph{trajectory mining frameworks}.
%The \emph{co-movement patterns} in literature consist 
%of five members, namely \emph{group}~\cite{wang2006grouppattern}, \emph{flock}~\cite{gudmundsson2004flock},
%\emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} and \emph{platoon}~\cite{li2015platoon}.
%We have demonstrated the semantics of these patterns in Table~\ref{tbl:existing_co_patterns} and Figure~\ref{fig:related_work}. 
%In this section, we distinguish the parallel GCMP mining from these concepts.
%In this section, we focus on comparing the techniques used in these works.
%For more trajectory patterns other than \emph{co-movement patterns}, 
%interested readers may move to~\cite{zheng2015survey} for a comprehensive survey.
\subsection{Co-Movement Patterns}
\subsubsection{Flock and Convoy}
The difference between \emph{flock} and \emph{convoy} lies 
in the object clustering methods. In \emph{flock},
objects are clustered based on their distances. Specifically, the
objects in the same cluster need to have a pairwise distance less than \emph{min\_dist}. 
This essentially requires the objects to be within a disk-region of delimiter less than \emph{min\_dist}.
In contrast, \emph{convoy} clusters objects using density-based spatial clustering~\cite{ester1996density}.
Technically, \emph{flock} utilizes a $m^{th}$-order Voronoi diagram~\cite{laube2005finding} to detect whether
a subset of $n$ ($n \geq m$) objects stay in a disk region.
%a subset of object with size greater than $m$ stays in a disk-region.
\emph{Convoy} employs
a trajectory simplification~\cite{douglas1973linesimplification} technique to boost pairwise distance computations in
the density-based clustering.
After clustering, both \emph{flock} and \emph{convoy} use a sequential scanning
method to examine each snapshot. 
During the scan, the object groups that do 
not appear in consecutive snapshots are pruned.
%During the scan, object
%groups that appear in consecutive timestamps are detected. Meanwhile, the object groups that do not
%match the consecutive constraint are pruned. 
However, such a method faces high complexity when supporting other patterns.
For instance, in \emph{swarm}, the candidate set during the sequential scanning grows
exponentially, and many candidates can only be pruned after the entire dataset are scanned.

\subsubsection{Group, Swarm and Platoon}
Different from \emph{flock} and \emph{convoy}, all the \emph{group},\emph{swarm} and \emph{platoon}
patterns have more relaxed constraints on the pattern duration. Therefore, their techniques of mining are of
the same skeleton. The main idea of mining is to grow an object set from an empty set
in a depth-first manner. During the growth, various pruning techniques are provided to prune 
unnecessary branches. \emph{Group} pattern uses a VG-graph to guide the pruning of false candidates~\cite{wang2006grouppattern}.
\emph{Swarm} designs two more pruning rules called backward pruning and forward pruning~\cite{li2010swarm}. \emph{Platoon}~\cite{li2015platoon}
leverages a prefix table structure to steer the depth-first search, which shows efficiency 
as compared to the other two methods.
However, the pruning rules adopted by the three patterns heavily rely on depth-first search which loses efficiency in a parallel scenario.

\subsection{Other Related Trajectory Patterns}
A closely related literature to co-movement patterns is the \emph{dynamic movement} patterns. Instead of requiring the same set of object traveling together, \emph{dynamic movement} patterns allow objects to temporally join or leave a group. Typical works include \emph{moving clusters}~\cite{kalnis2005movingclusters}, \emph{evolving convoy}~\cite{aung2010discovery}, \emph{gathering}~\cite{zheng2013gathering} etc. These works cannot model GCMP since they enforce global consecutiveness on the 
temporal domain.

\subsection{Trajectory Mining Frameworks}
Jinno et al. in~\cite{jinno2012paralleltpattern} designed a MapReduce based algorithm to efficiently support \emph{T}-pattern discovery, where a \emph{T}-pattern is a set of objects visiting the same place at simliar time. Li et al. proposed a framework of processing online \emph{evolving group} pattern~\cite{li2013onlinegroup}, which focuses on supporting efficient updates of arriving objects. 
As these works essentially differ from co-movement pattern, their techniques cannot be directly applied to discover GCMPs.

### 2016-10-28 Camera-Ready/sec3_definitions.tex
Camera-Ready
Ohohoho

--- 2016-09-13 sec3_definitions.tex
@@
 \begin{table}[h]
-\vspace{-2mm}
 \centering
@@
 \end{tabular}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Operators on time sequence.}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \label{tbl:operators}
@@
 We say a sequence $T$ is consecutive 
-if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
+if $\forall 1 \leq i < |T|, T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
 It is obvious that any time sequence $T$ can be decomposed into
@@
 \begin{definition}[$G$-connected]
-A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$, i.e.,
- $\forall i \in (1,\ldots,|T|-1), T[i+1]-T[i] \leq G$.
+A time sequence $T$ is $G$-con-nected if the gap between any of its neighboring timestamps is no greater than $G$, i.e., $\forall 1 \leq i < |T|, T[i+1]-T[i] \leq G$.
 \end{definition}
@@
 \begin{definition}[General Co-Movement Pattern]
-A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
+A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in every timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
 \end{definition}
@@
 \end{tabular} 
-   \vspace{-0.5em}
-\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
-% $M$ represents the  \emph{significance} constraint.
-$K$ represents the \emph{duration} constraint.
-$L$ represents the \emph{consecutiveness} constraint.
-$G$ represents the \emph{connection} constraint.
-}
-    \vspace{-0.5em}
+%\vspace{-0.5em}
+\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.}
+%\vspace{-0.5em}
 \label{tbl:patterns}
@@
 \end{tabular} 
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Summary of notations.}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \end{table}

### 2016-10-28 Camera-Ready/sec4_baseline.tex
Camera-Ready
Ohohoho

--- 2016-09-13 sec4_baseline.tex
@@
 \center
-\includegraphics[width=0.85\textwidth]{trm.eps}
-    \vspace{-0.5em}
+\includegraphics[width=0.8\textwidth]{trm.eps}
+%\vspace{-0.5em}
 \caption{Workflow of Temporal Replication and Parallel Mining (TRPM).
 (a) and (b) correspond to the first mapreduce stage which clusters objects in each snapshot.
-(c) and (d) correspond to the second mapreduce stage, which uses TRPM to detect GCMPs in parallel.}
-\vspace{-0.5em}
+(c) and (d) is the second mapreduce stage which uses TRPM to detect GCMPs.}
+%\vspace{-0.5em}
 \label{fig:trm}
@@
 
-%\vspace{-3mm}
 \section{Baseline: Temporal Replication and Parallel Mining}
@@
 \begin{proof}
-\vspace{-0.5em}
 Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid.
@@
 \end{algorithm}
-\vspace{-1em}
 
@@
 \end{algorithm}
-\vspace{-0.5em}
-The complete picture of TRPM is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the  workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
+
+The complete picture of TRPM is shown in Algorithm~\ref{algo:trm_overview}. We illustrate the  workflow of TRPM using Figures~\ref{fig:trm} (c) and (d) with pattern
 parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
@@
 in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
-into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
+into a partition in the map phase. In Figure~\ref{fig:trm} (d), the line sweep
 method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
@@
 %As we sweep the snapshots, the patterns in $C_i$ grow.
-At snapshot $S_4$, the candidate
+At snapshot 
+$S_4$, the candidate
 $\langle o_5,o_6 \rangle$ is removed because the gap between its latest timestamp (i.e., $2$)
 and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
-Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed
+Next, at snapshot 
+$S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed
 because its local consecutive segment $(4)$ has only $1$ element,
@@
 Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. 
-Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness.
-If $\eta$ is set to be $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.
+Note that in this example, $\eta=5$ is the minimum setting that 
+can guarantee correctness. If $\eta$ is set to be $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

### 2016-10-28 Camera-Ready/sec5_spm.tex
Camera-Ready
Ohohoho

--- 2016-09-13 sec5_spm.tex
@@
 \centering
-\includegraphics[width=0.85\textwidth]{spm.eps}
-\vspace{-0.5em}
+\includegraphics[width=0.8\textwidth]{spm.eps}
+%\vspace{-0.5em}
 \caption{Star Partitioning and ApRiori Enumerator (SPARE).
@@
 \label{fig:star_partition}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \end{figure*}
@@
 balance among reducers.
-The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}.
+The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune}.
 In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition.
@@
 \includegraphics[width=0.35\textwidth]{star-alt.eps}
-\vspace{-0.5em}
 \caption{Star partitioning with different vertex orderings.}
-\vspace{-0.5em}
 \label{fig:star-alt}
@@
 \begin{proof}
-   \vspace{-0.5em}
+%\vspace{-0.5em}
 See Appendix~\ref{apx:thm2proof}.
@@
 \begin{proof}
- \vspace{-0.5em}
+%\vspace{-0.5em}
 See Appendix~\ref{apx:thm2proof}.
@@
 because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
-In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than $4$.
+In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size  $\geq 4$.
 \end{example}
@@
 it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
-To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
+To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
 If yes, we can  terminate the algorithm early and output the results.
@@
 \begin{proof} 
-\vspace{-0.5em}
+%\vspace{-0.5em}
 We prove by contradiction.
@@
 However, $P_i$ and $P_j$ are from different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction.
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \end{proof}
@@
 \begin{proof}  
-\vspace{-0.5em}
+%\vspace{-0.5em}
 See Appendix~\ref{apx:spm_correct}.
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \end{proof}

### 2016-10-28 Camera-Ready/sec6_experiment.tex
Camera-Ready
Ohohoho

--- 2016-09-13 sec6_experiment.tex
@@
 In this section, we evaluate the efficiency and scalability of our proposed parallel GCMP detectors on real trajectory datasets.
-All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet.
+All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and Gigabit Ethernet.
 
@@
 We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes.
-We deploy our GCMP detector on Apache Spark 1.5.2 with the remaining $11$ nodes as the computing nodes.
+We deploy our GCMP detector on Apache Spark 1.5.2\footnote{We have experimented with a query-based TRPM using Spark-SQL 2.0.0 window function.
+We find that Spark-SQL fails to execute the query-based TRPM in parallel, which results in a 120x performance slowdown compared to mapreduce-based TRPM.
+Thus we only report the performance of mapreduce-based TRPM in this paper.} with the remaining $11$ nodes as the computing nodes.
 To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory.
@@
 All our implementations as well as cluster setups are publicly available% in Github
-\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}, we have also experimented with a query-based TRPM using Spark-SQL 2.0.0 window function. 
-We find that Spark-SQL fails to execute the query-based TRPM in parallel, which results in a 120x performance slowdown compared to mapreduce-based TRPM.
-%
-%it runs over 120 times slower than the mapreduce-based TRPM. 
-Thus we only report the performance of mapreduce-based TRPM in this paper.}.
+\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}.}.
 
-\textbf{Datasets}: We use three real trajectory datasets in different application scenarios:
+\textbf{Datasets}: We use three real trajectory datasets that are collected from different applications:
 \begin{itemize}[nosep]
@@
 We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset.
-Note that other clustering methods or settings can also be applied.
+%Note that other clustering methods or settings can also be applied. 
 %The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
@@
 \end{tabular}
- \vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Statistics of datasets.}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \label{exp:dataset}
@@
 \begin{table}[h]
-\small
-\begin{tabular}{c|l|p{3cm}}
+\begin{tabular}{c|l|p{3.3cm}}
 \hline 
-\textbf{Parameter} & \textbf{Meaning} & \textbf{Values} \\ 
+\textbf{Param.} & \textbf{Meaning} & \textbf{Values} \\ 
 \hline 
@@
 \hline
-$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
-$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
+$O_r$ & ratio of objects & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
+%$O_r$ & ratio of objects & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
+$T_r$ & ratio of snapshots & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
+%$T_r$ & ratio of snapshots & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
 N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
@@
 \end{tabular} 
- \vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Parameters and their default values.}
- \vspace{-0.5em}
+ %\vspace{-0.5em}
 \label{tbl:parameters}
@@
 
-%\vspace{-3mm}
 \textbf{Parameters}: To systematically study the performance of
@@
     \end{subfigure}      
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \label{exp:performance_vary}
@@
 
-%The result also reveals the potential of the two solutions to handle larger trajectories.
-Again, SPARE outperforms TRPM in both execution time and memory usage which dues to the set of effective pruning procedures.
-
 \begin{table}[h]
@@
 \hline
-\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} % & \textbf{Time} 
+\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} 
 & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
-\multirow{2}{*}{Shopping}              & TRPM           % & 597
-                               & 90,859                 & 10,019               \\ %\cline{2-5} 
-                                       & SPARE           %& 237
+\multirow{2}{*}{Shopping}              & TRPM           
+                               & 90,859                 & 10,019               \\ 
+                                       & SPARE           
                                                                       & 33,638                 & 8,613                \\ \hline
-\multirow{2}{*}{Geolife}               & TRPM            %& 747 
-                              & 106,428                & 18,454               \\ %\cline{2-5} 
-                                       & SPARE           %& 341 
+\multirow{2}{*}{Geolife}               & TRPM            
+                              & 106,428                & 18,454               \\
+                                       & SPARE            
                                                                      & 35,343                 & 14,369               \\ \hline
-\multirow{2}{*}{Taxi}                  & TRPM            %& 3,648  
-                           & 503,460                & 51,691               \\ %\cline{2-5} 
-                                       & SPARE           %& 580  
+\multirow{2}{*}{Taxi}                  & TRPM            
+                           & 503,460                & 51,691               \\ 
+                                       & SPARE           
                                                                     & 68,580                & 35,912               \\ \hline
 \end{tabular}
- \vspace{-0.5em}
+%\vspace{-0.5em}
 \caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \label{tbl:resource}
@@
 
-%\begin{figure}[h]
-%\centering
-%	\begin{subfigure}[b]{0.22\textwidth}
-%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
-%        \caption{Shopping vary $O_r$}
-%    \end{subfigure}
-% 	 \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
-%        \caption{Geolife vary $O_r$}
-%    \end{subfigure}
-%    	 \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
-%        \caption{Taxi vary $O_r$}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.22\textwidth}
-%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
-%        \caption{Shopping vary $T_r$}
-%    \end{subfigure}
-% 	 \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
-%        \caption{Geolife vary $T_r$}
-%    \end{subfigure}
-%    	 \begin{subfigure}[b]{0.22\textwidth}
-%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
-%        \caption{Taxi vary $T_r$}
-%    \end{subfigure}
-% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
-% \label{exp:performance_vary_OT}
-%\end{figure}
-
-%\vspace{-3mm}
 \subsection{Analysis of SPARE framework}
@@
 \end{tabular} 
-\vspace{-0,5em}
+%\vspace{-0.5em}
 \caption{Pruning power of SPARE.}
-\vspace{-0,5em}
-%\vspace{-4mm}
+%\vspace{-0.5em}
 \label{tbl:pruning}
@@
 
-\begin{figure}[h]
-\centering
-	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
-	 \vspace{-0.5em}
-    \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}
-   \vspace{-5mm}
-    \label{exp:wl}
-\end{figure}
-
+%\vspace{1em}
 \subsubsection{Load balance}
@@
 The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost).
-Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
+Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This shows the 
 efficiency of the star partition and apriori enumeration.
@@
 for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
+%
+%\begin{figure}[h]
+%\centering
+%	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
+%	 %\vspace{-0.5em}
+%    \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}
+%    \label{exp:wl}
+%    %\vspace{-0.5em}
+%\end{figure}
+
+%\begin{table*}
+%\centering
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%
+%\includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
+% &      &       &      \\ \hline
+%  & 1     & 2     & 3    \\ \hline
+%  & \multicolumn{3}{l|}{}
+%\\\hline
+%\end{tabular}
+%\end{table*}
+
+%\begin{figure*}
+%\centering
+%\begin{tabular}{cccc}
+%\begin{subfigure}[b]{0.22\textwidth}
+% \includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
+% \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}   
+%\end{subfigure}
+% &  \begin{subfigure}[b]{0.22\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
+%        \caption{Shopping vary $N$}
+%    \end{subfigure}    &  \begin{subfigure}[b]{0.22\textwidth}  \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}\caption{GeoLife vary $N$} \end{subfigure}    &   \begin{subfigure}[b]{0.22\textwidth}       \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}\caption{Taxi vary $N$}\end{subfigure}    \\
+%       & \multicolumn{3}{c}{}
+%\end{tabular}
+%\end{figure*}
+
+\begin{figure*}
+\begin{minipage}{0.3\textwidth}
+\includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
+ \caption{Cost breakdown of TRPM, SPARE-RD and SPARE.}
+    \label{exp:wl}
+\end{minipage}
+\begin{minipage}{0.74\textwidth}
+\centering
+	 \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
+        \caption{Shopping vary $N$}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
+        \caption{GeoLife vary $N$}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
+        \caption{Taxi vary $N$}
+    \end{subfigure} 
+ \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
+ \label{exp:scalability}
+\end{minipage}
+\end{figure*}
 
@@
 \end{tabular}
-%\begin{tabular}{|l|c|c|c|c|}
-%\hline
-%\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
-%\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
-%\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
-%                                       & SPARE-RD          & 122                               &  295             & 41
-%\\% \cline{2-5}                                        
-%									   & SPARE           &  134                              &   237               & 21
-%\\ \hline                                
-%\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
-%                                       & SPARE-RD          &  38                               &   484               & 148
-%\\ %\cline{2-5}                                        
-%									   & SPARE           &   107                             &     341             & 96
-%\\ \hline
-%\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
-%                                       & SPARE-RD          & 122                               & 681                 & 109
-%\\ %\cline{2-5}                                        
-%									   & SPARE           &   134                             &  580                & 56               
-%\\ \hline
-%\end{tabular}
-\vspace{-0.5em}
+%\vspace{-0.5em}
   \caption{Statistics of execution time (seconds) on all jobs.}
-  \vspace{-0.5em}
+%\vspace{-0.5em}
   \label{tbl:strags}
@@
 %
-\begin{figure*}[t]
-\centering
-\begin{subfigure}[b]{0.3\textwidth}
-    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
-        \caption{Shopping vary $N$}
-    \end{subfigure}
- 	 \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
-        \caption{GeoLife vary $N$}
-    \end{subfigure}
-    	 \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
-        \caption{Taxi vary $N$}
-    \end{subfigure}
-%\vspace{-0.5em}
- \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
- \label{exp:scalability}
-\end{figure*}
+%\begin{figure}[t]
+%\centering
+%\begin{subfigure}[b]{0.15\textwidth}
+%    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
+%        \caption{Shopping vary $N$}
+%    \end{subfigure}
+% 	 \begin{subfigure}[b]{0.15\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
+%        \caption{GeoLife vary $N$}
+%    \end{subfigure}
+%    	 \begin{subfigure}[b]{0.15\textwidth}
+%        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
+%        \caption{Taxi vary $N$}
+%    \end{subfigure}
+%%\vspace{-0.5em}
+% \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
+% %\vspace{-0.5em}
+% \label{exp:scalability}
+%\end{figure}

### 2016-10-29 Camera-Ready/sec1_introduction.tex
Camera-Ready
Wait to be submitted

@@
 Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
-records, are continually generated from animal telemetry chips, 
+records, are continually being generated from animal telemetry chips, 
 vehicle GPSs and wearable devices. Data analysis on large-scale 
@@
 A crucial task of data analysis on top of trajectories is 
-to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
+to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013effective,zheng2015survey} 
 refers to a group of objects traveling together for a certain period of time 
@@
 \end{figure}
-
-Therefore, in this paper, our contributions are to close these two gaps.
-%In this paper, our contribution is towards closing these two gaps.
+%
+%Therefore, in this paper, our contributions are closing
+%these two gaps.
+%
+%to close these two gaps.
+%
+%Therefore, in this paper, our aim is to close these two gaps 
+%via the following contributions.
+%we aim to close these two gaps by making two contributions. 
+In this paper, we resolve these two gaps by making the following contributions.
 First, we propose the \emph{general co-movement pattern} (GCMP) which models
@@
 we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
-%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
-%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
-By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
+By setting a feasible $G$, the loose-connection anomaly can be effectively controlled.
+In addition, our GCMP is also general.
 It can be reduced to any of the previous pattern by customizing its parameters.
@@
 Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue.
-Our technical contributions are three-fold.
+Our technical contributions are threefold.
 First, we design a baseline solution by replicating the snapshots

### 2016-10-29 Camera-Ready/sec5_spm.tex
Camera-Ready
Wait to be submitted

@@
 it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
-To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
+To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}).
 If yes, we can  terminate the algorithm early and output the results.

### 2017-04-26 Camera-Ready/appendix.tex
uptodate

@@
 is a %$n\times n$ 
-\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
+\emph{permutation matrix}~\footnote{An identity matrix with rows shuffled}.
 Consider an assignment matrix $B$ of star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$),
-$B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix} holds.
+$B=\triu(PJP^T)$~\footnote{$\mathtt{triu}$ is the upper triangle part of a matrix} holds.
 % $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}, then $B$ is the assignment matrix of the star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
@@
 %represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
-Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
+Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
 vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
@@
 \begin{split}
-	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t) = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
+	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t) \\ &= Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
 		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
@@
 As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
-For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be outputted by Algorithm~\ref{algo:apriori_mining} from $Sr_s$. 
+For completeness, let $P$ be a true pattern. Let $s$ be the object with the smallest ID in $P.O$. We prove that $P$ must be outputted by Algorithm~\ref{algo:apriori_mining} from $Sr_s$. 
 First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 %$\forall O' \subseteq O$,

### 2017-04-26 Camera-Ready/sec1_introduction.tex
uptodate

@@
 \section{Introduction}
-The prevalence of positioning devices has drastically boosted 
+The prevalence of positioning devices has drastically expanded 
 the scale and spectrum of trajectory collection to an unprecedented level. 
@@
 spatial clustering. 
-In the temporal dimension, the \emph{flock}%~\cite{gudmundsson2006flock} 
-and the \emph{convoy}%~\cite{jeung2008convoy} 
+In the temporal dimension, the \emph{flock} %~\cite{gudmundsson2006flock} 
+and the \emph{convoy} %~\cite{jeung2008convoy} 
 require all the timestamps 
 of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
-whereas the \emph{swarm}%~\cite{li2010swarm}
+whereas the \emph{swarm} %~\cite{li2010swarm}
 does not impose any restriction. 
-The \emph{group}%~\cite{wang2006grouppattern} 
-and the \emph{platoon}%~\cite{li2015platoon} 
+The \emph{group} %~\cite{wang2006grouppattern} 
+and the \emph{platoon} %~\cite{li2015platoon} 
 adopt a compromised approach by allowing
@@
 \centering
-\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.7cm}|p{2.3cm}|}
+\caption{Constraints and complexities of co-movement patterns.
+The complexity indicates the worst case performance, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
+\label{tbl:existing_co_patterns}
+\begin{tabular}{|p{1.5cm}|p{1.4cm}|p{1.7cm}|p{2.2cm}|}
 \hline 
-\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Conse-cutiveness}} & { \textbf{Time Complexity}}\\ 
+{\small \textbf{Pattern}} & {\small \textbf{Proximity}} & {\small \textbf{Consecutive}} & {\small \textbf{Complexity}}\\ 
 \hline 
-flock~\cite{gudmundsson2006flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
+flock~\cite{gudmundsson2006flock} & disk &  global & {\small $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
 \hline 
-convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
+convoy~\cite{jeung2008convoy} & density &   global & {\small $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
-swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
+swarm~\cite{li2010swarm} & density  & - & {\small $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
 \hline 
-group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
+group~\cite{wang2006grouppattern} & disk &  local & {\small $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
 \hline 
-platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
+platoon~\cite{li2015platoon} & density &  local & {\small $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
 \hline 
 \end{tabular} 
-%%\vspace{-0.5em}
-\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
-$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
-%\vspace{-0.5em}
-\label{tbl:existing_co_patterns}
 \end{table}
@@
 %we aim to close these two gaps by making two contributions. 
-In this paper, we resolve these two gaps by making the following contributions.
+In this paper, we close these two gaps by making the following contributions.
 First, we propose the \emph{general co-movement pattern} (GCMP) which models
@@
 
-Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue.
+Second, we investigate deploying our GCMP detector on the modern MapReduce platform (i.e., Apache Spark) to tackle the scalability issue.
 Our technical contributions are threefold.

### 2017-04-26 Camera-Ready/sec5_spm.tex
uptodate

@@
 
-\section{SPARE: Star Partitioning and Apriori Enumerator}
+\section{SPARE: Star Partitioning and \\ Apriori Enumerator}
 \label{sec:spm}
@@
 we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
-to replace the second stage of the map-reduce jobs in Figure~\ref{fig:trm}. 
+to replace the second stage of the mapreduce jobs in Figure~\ref{fig:trm}. 
 Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
@@
 % on the moving objects.
-This is because assigning different IDs to the objects will result in 
+This is because assigning different IDs to the objects will produce 
 different star partitioning results, which will eventually affect the workload 
@@
 Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$.
-Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$.
+Let $T[y]=\min\{T_i[1],T_j[1]\}$ i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$.
 Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$.

### 2017-04-26 Camera-Ready/sec6_experiment.tex
uptodate

@@
 %\vspace{-2mm}
-\begin{table} [h]
-\center
+\begin{table} [t]
+\centering
+%\vspace{-0.5em}
+\caption{Statistics of datasets.}
+%\vspace{-0.5em}
+\label{exp:dataset}
 \begin{tabular}{|l|l|l|l|}
@@
 \end{tabular}
-%\vspace{-0.5em}
-\caption{Statistics of datasets.}
-%\vspace{-0.5em}
-\label{exp:dataset}
 \end{table}
@@
 \begin{table}[h]
+%\vspace{-0.5em}
+\caption{Parameters and their default values.}
+ %\vspace{-0.5em}
+\label{tbl:parameters}
 \begin{tabular}{c|l|p{3.3cm}}
@@
 \end{tabular} 
-%\vspace{-0.5em}
-\caption{Parameters and their default values.}
- %\vspace{-0.5em}
-\label{tbl:parameters}
 \end{table}
@@
 
-\textbf{Varying $O_r$}:Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects.
+\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects.
 Both TRPM and SPARE take longer time to find patterns in a larger database.
@@
 \textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary} (f),(l),(r) present 
-the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.
+the performances with increasing number of snapshots. When $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.
 
@@
 \centering
+%\vspace{-0.5em}
+\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
+%\vspace{-0.5em}
+\label{tbl:resource}
 \begin{tabular}{|l|c|c|c|c|}
@@
 \end{tabular}
-%\vspace{-0.5em}
-\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
-%\vspace{-0.5em}
-\label{tbl:resource}
 \end{table}
@@
 \centering
+%\vspace{-0.5em}
+\caption{Pruning power of SPARE.}
+%\vspace{-0.5em}
+\label{tbl:pruning}
 \begin{tabular}{|l|c|c|c|}
@@
 \end{tabular} 
-%\vspace{-0.5em}
-\caption{Pruning power of SPARE.}
-%\vspace{-0.5em}
-\label{tbl:pruning}
 \end{table}
@@
 \end{minipage}
-\begin{minipage}{0.74\textwidth}
+\begin{minipage}{0.7\textwidth}
 \centering
@@
 \centering 
+%\vspace{-0.5em}
+  \caption{Statistics of execution time (seconds) on all jobs.}
+%\vspace{-0.5em}
+  \label{tbl:strags}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-%\vspace{-0.5em}
-  \caption{Statistics of execution time (seconds) on all jobs.}
-%\vspace{-0.5em}
-  \label{tbl:strags}
 \end{table}
